### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Add ROSMAP Process Script

---
title: Covariate and differential expression analysis of ROSMAP reprocessed counts Using Diagnosis as a covariate for TWAS
author: "JKG - Adapted from: Thanneer Perumal"
editor_options:
  chunk_output_type: console
---
Date of analysis update: "`r date()`"

syn3382527.7
syn4300313.1
syn8449369.2
syn7116000.1
syn8691134.1
syn3191087.3
syn8698240.2

### Load Libraries
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synLogin}
synLogin()
```

### Data download
Obtain count matrix and metadata from synapse
```{r download.data}
# Download expression data
COUNT_ID <- 'syn8691134';
ALL_USED_IDs <- COUNT_ID
COUNT_OBJ <- synGet(COUNT_ID, version = 1)
COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
COUNT[,grep('150_120419', colnames(COUNT))[2]] = NULL
# Convert rownames of counts from tracking id to ensemble gene id
tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
  dplyr::mutate(ID = Gene.ID) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
rownames(tmp) = tmp$Gene.ID
rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
# Get clinical metadata
METADATA.CLINICAL_ID <- 'syn3191087'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID
METADATA.CLINICAL_OBJ <- synGet(METADATA.CLINICAL_ID, version = 3)
METADATA.CLINICAL <- read.table(METADATA.CLINICAL_OBJ$path,sep=',',header=T)
# Get clinical metadata with uncensored ages
METADATA.CLINICAL_ID1 <- 'syn7116000'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID1
METADATA.CLINICAL_OBJ1 <- synGet(METADATA.CLINICAL_ID1, version = 1)
METADATA.CLINICAL1 <- read.table(METADATA.CLINICAL_OBJ1$path,sep=',',header=T)
# Get technical covariates
METADATA.TECH_ID <- 'syn4300313'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.TECH_ID
METADATA.TECH_OBJ <- synGet(METADATA.TECH_ID, version = 1)
METADATA.TECH <- read.table(METADATA.TECH_OBJ$path,sep='\t',header=T)
# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8698240';
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD <- synGet(METADATA.PICARD_ID, version = 2)$path %>%
  data.table::fread() %>%
  dplyr::rename(Sampleid = sample)
# Fix error in technical covariates data
KEY_ID <- 'syn3382527'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = KEY_ID  
KEY <- synGet(KEY_ID, version = 7)$path %>%
  read.csv %>% 
  dplyr::filter(!is.na(rnaseq_id)) %>%
  dplyr::select(projid, rnaseq_id) %>%
  tidyr::separate(rnaseq_id, c('a','b','batch'), sep = '_') %>% 
  unite(Sampleid, a, b) %>%
  dplyr::select(-batch) %>%
  unique
# Match technical and clinical covariates
METADATA <- METADATA.TECH %>%
  dplyr::left_join(METADATA.PICARD) %>%
  dplyr::select(-projid) %>%
  dplyr::left_join(KEY) %>%
  dplyr::left_join(METADATA.CLINICAL) %>%
  dplyr::select(-age_first_ad_dx, -age_death, -age_at_visit_max) %>%
  dplyr::left_join(METADATA.CLINICAL1)
# Pick higher quality RIN batch for sample 492_120515
METADATA <- METADATA %>%
  dplyr::group_by(Sampleid) %>%
  dplyr::top_n(1, RINcontinuous)
colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))
colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
# Get gene specific parameters from synapse
GENE.PARAM = synGet('syn8449369', version = 2)$path %>%
  data.table::fread(data.table = FALSE)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% 
  unique() 
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% 
  unique() 
rownames(GENE.GC) = GENE.GC$ensembl_gene_id 
```

### Data preprocessing
```{r preprocess.data, cache=TRUE}
# Remove samples with no cogdx, RIN, PMI scores and age_death
METADATA <- METADATA %>%
  ungroup %>%
  dplyr::filter(Sampleid %in% colnames(COUNT)) %>%
  dplyr::filter(!is.na(cogdx), !is.na(braaksc), !is.na(ceradsc)) %>%
  dplyr::filter(!is.na(RINcontinuous)) %>%
  dplyr::filter(!is.na(pmi)) %>%
  #dplyr::filter(!is.na(PCT_INTRONIC_BASES)) %>%
  dplyr::filter(!is.na(age_death)) %>%
  as.data.frame()
# Add harmonised case-control status
METADATA$Diagnosis = 'OTHER'
METADATA$Diagnosis[METADATA$cogdx == 1 & METADATA$braaksc <= 3 & METADATA$ceradsc >= 3] = 'CONTROL'
METADATA$Diagnosis[METADATA$cogdx == 4 & METADATA$braaksc >= 4 & METADATA$ceradsc <= 2] = 'AD'
# Add sex variable 
METADATA$Sex = 'FEMALE'
METADATA$Sex[METADATA$msex == 1] = 'MALE'
# Add apoe4 genotype (0, 1, 2)
METADATA$APOE4 = 0
METADATA$APOE4[METADATA$apoe_genotype %in% c(24, 34)] = 1
METADATA$APOE4[METADATA$apoe_genotype %in% c(44)] = 2
# METADATA$APOE4[is.na(METADATA$apoe_genotype)] = NA
# Get square of RIN
METADATA$RINcontinuous2 = METADATA$RINcontinuous^2
# Match covariates to expression data
indToRetain = intersect(METADATA$Sampleid, colnames(COUNT))
removedIDs = setdiff(colnames(COUNT), METADATA$Sampleid)
COUNT = COUNT[,indToRetain]
rownames(METADATA) = METADATA$Sampleid
METADATA = METADATA[indToRetain,]
```
Dorsolateral prefrontal cortex of `r dim(COUNT)[2]` subjects from the ROS and MAP cohorts are used for the analysis. Following sample are removed due to missing metadata `r paste(removedIDs, collapse = ',')`

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering, cache=TRUE}
primaryVariable <- c("cogdx", "Diagnosis", "APOE4")
FactorCovariates <- c("Batch", "Sex", "race", "spanish", "cogdx", "Diagnosis", "APOE4")
ContCovariates <- c("RINcontinuous", "RINcontinuous2", "age_death", "pmi", "educ", 
                    "PCT_PF_READS_ALIGNED", "PCT_CODING_BASES",
                    "PCT_INTERGENIC_BASES", "PCT_INTRONIC_BASES", 
                    "PCT_RIBOSOMAL_BASES")
# Find inter relation between factor covariates
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
COVARIATES <- data.frame(lapply(COVARIATES,function(x){x <- sapply(x,function(y){str_replace_all(as.character(y),'\\+','')})}))
rownames(COVARIATES) <- METADATA$Sampleid
# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```

Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=9, fig.height=6}
COVARIATES.CORRELATION = CovariateAnalysis::getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left', padding  = unit(c(18,2,2,18), 'mm'))
```

### Explore metadata
```{r data.explore, fig.width = 10, fig.height = 14}
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Diagnosis, y = RINcontinuous)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + theme(legend.position = 'top')
# AgeAtDeath
p[[2]] = ggplot(COVARIATES, aes(x = Diagnosis, y = age_death)) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('AgeOfDeath') + theme(legend.position = 'top')
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Diagnosis, y = pmi)) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI') + theme(legend.position = 'top')
# Education
p[[4]] = ggplot(COVARIATES, aes(x = Diagnosis, y = educ)) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Education') + theme(legend.position = 'top')
# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = Diagnosis, y = PCT_INTRONIC_BASES)) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + theme(legend.position = 'top')
# Ribosomal bases
p[[6]] = ggplot(COVARIATES, aes(x = Diagnosis, y = PCT_RIBOSOMAL_BASES)) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Ribosomal Bases') + theme(legend.position = 'top')
multiplot(plotlist = p, cols = 2)
```

### Filter genes
* Remove genes that have less than 1 cpm counts in at least 50% of samples per Diagnosis
* Remove genes with missing gene length and percentage GC content
```{r filter.genes}
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('Sampleid') %>%
  dlply(.(Diagnosis), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$Sampleid],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)
genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gc_content)]) %>%
  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene.length)]) %>%
  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
                                                 MIN_GENE_CPM=0, 
                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
# Check gene biotype
## Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "dec2016.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
## Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "gene_biotype"),
                       filters = "ensembl_gene_id", 
                       values = PROCESSED_COUNTS$filteredExprMatrix$genes,
                       mart = mart)
summary(factor(Ensemble2HGNC$gene_biotype)) %>%
  rownameToFirstColumn('Biotype') %>%
  dplyr::rename(fraction = DF) %>%
  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
  dplyr::filter(fraction >= 0.01) %>%
  kable
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

### Library Normalisation
Library normalisation is performed using cqn (conditional quantile normalisation)
```{r cqn}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'gene.length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Outlier Analysis
#### Sample outliers
Outlier analysis is performed before library normalisation with raw cpm counts
```{r outlier.analysis, cache = FALSE, fig.width = 10}
indToRemove = c('380_120503', '500_120515')
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- dplyr::left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  dplyr::mutate(label = SampleID)
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Batch, shape=Diagnosis, size=RINcontinuous))
p <- p + theme_bw() + theme(legend.position="right")
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  dplyr::left_join(COVARIATES %>%
                     rownameToFirstColumn('SampleID'))
p = ggplot(tmp1 %>%
             dplyr::filter(SampleID %in% indToRemove),
           aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'top')
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = COVARIATES %>%
  dplyr::group_by(Diagnosis, cogdx) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are: `r kable(tmp)`

#### Gene outliers
Assign NA values to genes that are above and below 3 std deviation of its distribution
```{r winsorise.data}
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
CQN.GENE_EXPRESSION$E = LOG.CPM
CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6
```

### Sample clustering
PCA based clustering of samples
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID'))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Batch, shape=cogdx, size=RINcontinuous))
p <- p + theme_bw() + theme(legend.position="right")
p
```

Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("Batch", "Sex", "Diagnosis")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.no.na)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE, fig.height=10, fig.width=20}
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID'))
p = ggplot(tmp1, aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'NONE') + facet_grid(.~Diagnosis, scale = 'free')
p
```

Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.no.na))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
```{r preadj.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preadj.covariates.plot, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Normalisation (iterative design)
Since many covariates are correlated, re-normalising and re-adjusting COUNTS with an iterative design matrix
1. Adding Batch and Sex a priori to variable selection
2. Primary variable of interest Diagnosis is excluded from the pool of available covariates for selection
```{r iterative.norm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Batch', 'Sex');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
#_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
postAdjustCovars = c(postAdjustCovars, "Diagnosis", names(which.max(covariatesEffects))) %>% unique()
loopCount = 0 
while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
  writeLines(paste('Using following covariates in the model:',
                   paste(postAdjustCovars, collapse=', '),
                   'as fixed effects'))

  # Post adjusted design matrix
  DM1 = getDesignMatrix(COVARIATES[,postAdjustCovars,drop=F],Intercept = F)
  DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

  # Estimate voom weights for dispersion control
  cnts = NEW.COUNTS
  cnts[is.na(cnts)] = 0
  VOOM.GENE_EXPRESSION = voom(cnts, 
                              design=DM1$design, 
                              plot=F,
                              na.rm = T)

  # Fit linear model using new weights and new design
  VOOM.ADJUSTED.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                            design = DM1$design,
                            weights = VOOM.GENE_EXPRESSION$weights)

  # Residuals after normalisation
  RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,
                                                CQN.GENE_EXPRESSION$E)

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates), c(postAdjustCovars, primaryVariable))

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  expr = RESIDUAL.GENE_EXPRESSION
  expr[is.na(expr)] = 0
  residualSigCovars = runPCAandPlotCorrelations(expr, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

  # Add postadjusted covariates (if any)
  residCovars = setdiff(residualSigCovars$significantCovars, c(postAdjustCovars, primaryVariable))
  covariatesEffects = residualSigCovars$Effects.significantCovars[residCovars]

  postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects)))
  loopCount = loopCount + 1
}
modelStr <- paste(paste(gsub('_','\\\\_',postAdjustCovars), collapse=', '),
                  'as fixed effects')
tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`

### Sanity check
```{r residual.adj, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(expr, 
                                              COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
residualSigCovars[["PC_res"]][[2]]$plotData
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(expr))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
PCA of residual data
```{r decompse.normalise.data2.1, fig.height=6, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(expr, scale.=T, center = T)
# Plot first 4 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID'))
p <- ggplot(plotdata, aes(x=PC1, y=PC2)) 
p <- p + geom_point(aes(color=Batch, shape=Diagnosis, size=RINcontinuous))
p <- p + theme_bw() + theme(legend.position="right")
p
```
Tree based clustering of residual data
```{r decompse.normalise.data2.2, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c('Batch', 'Sex', primaryVariable)])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(expr)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Adjust data with covariates for Network Analysis
Identified covariates are regressed out from the expression matrix for network analysis
```{r network.adjust}
# Get design matrix
DESIGN.NET = getDesignMatrix(COVARIATES[, postAdjustCovars, drop = F], Intercept = F)
DESIGN.NET = DESIGN.NET$design[,linColumnFinder(DESIGN.NET$design)$indepCols]
# Estimate voom weights for dispersion control
cnts = NEW.COUNTS
cnts[is.na(cnts)] = 0
VOOM.NET.WEIGHTS = voom(cnts, design=DESIGN.NET, plot=F)
# Fit linear model using new weights and new design
VOOM.NET.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                     design = DESIGN.NET,
                     weights = VOOM.NET.WEIGHTS$weights)
# Residuals after normalisation
RESIDUAL.NET.GENE_EXPRESSION = residuals.MArrayLM(VOOM.NET.FIT,
                                                  CQN.GENE_EXPRESSION$E)
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
cnts = NEW.COUNTS
cnts[is.na(cnts)] = 0
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Fit linear model using new weights and new design
FIT = lmFit(CQN.GENE_EXPRESSION$E,
            design = DESIGN$design,
            weights = VOOM.WEIGHTS$weights)
# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]
# Calculate the number of surrogate variables (be method)
# NUM.SV = sva::num.sv(CQN.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456, B = 30)
# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$E)
# Compute actual variance of all principal components
expr = RESIDUAL.SVA.GENE_EXPRESSION
expr[is.na(expr)] = 0
tmp = svd(expr)
actual.var = tmp$d^2/sum(tmp$d^2)
# Compute permuted variance of all principal components
permuted.var = foreach(i = 1:20, .combine = rbind) %dopar% {
  tmp.residual = t(apply(expr, 1, sample, replace = FALSE))
  tmp = svd(tmp.residual)
  permuted.var = tmp$d^2/sum(tmp$d^2)
}
permuted.var = apply(permuted.var, 2, mean)
NUM.SV = sum(actual.var >= permuted.var[1])
# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.3)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p
# Estimate surrogate variables
SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$E.no.na, 
                    MODEL1, MODEL0, n.sv = NUM.SV, B = 30)$sv
SURR.VAR = data.frame(SURR.VAR)
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(MODEL1)
# Re-estimate voom weights
VOOM.SVA.WEIGHTS = voom(cnts, 
                        design = cbind(MODEL1, SURR.VAR), plot=F)
# Fit linear model using new weights and new design
VOOM.SVA.FIT = lmFit(CQN.GENE_EXPRESSION$E, 
                     design = cbind(MODEL1, SURR.VAR),
                     weights = VOOM.SVA.WEIGHTS$weights)
# Residuals after normalisation
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(VOOM.SVA.FIT,
                                                  CQN.GENE_EXPRESSION$E)
# Add variable of interest back to the residuals
varsToAddIn = grep("Diagnosis", colnames(MODEL1), value = T)
RESIDUAL.SVA.GENE_EXPRESSION = RESIDUAL.SVA.GENE_EXPRESSION + 
  VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
```

### Save Environment and SVA.GENE_EXPRESSION
```{r SAVE and Wrap, eval = F}
save.image("ROSMAP.RData")
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = "ROSMAP_SVA_Diagnosis_Corrected.tsv", row.names = T, col.names = T, sep ="\t", quote=F)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn20798014';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
# Github link
thisRepo <- getRepo(repository = "kelshmo/Brain_Reg_Net", ref="branch", refName='CMC')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
#Set Used SynIDs For Provenance
Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
  "syn8691134", "syn3191087", "syn8698240"
)

# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  tissueTypeAbrv	= 'DLPFC', 
  study = 'ROSMAP', 
  organism = 'HomoSapiens',
  consortium	= 'ROSMAP',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh37'
)

#Store file:
activity <- Activity(
    'Fancy Processing',
    description='No seriously, really fancy processing',
    used=c('syn1906480', 'http://data_r_us.com/fancy/data.txt'),
    executed='syn1917825')
file <- File('/path/to/data/file.xyz', description='Fancy new data', parent=project)
file <- synStore(file, activity=activity)

# Function to change entity ACL (also creates new acls if it doesn't exist)
synChangeEntityACL <- function(id, new.racl){
  tryCatch({ 
    # If old acl exist update
    old.acl = synGetEntityACL(id)
    old.acl@resourceAccess = new.racl
    synUpdateEntityACL(old.acl)
  }, error = function(e){ 
    # If not create a new acl
    new.acl = AccessControlList(id = id, resourceAccess = new.racl)
    synCreateEntityACL(new.acl)
  })
}

# Create new resource acls
new.racl = synapser::synSetPermissions(principalId = '3319864', 
                          accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
                                         'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS')) %>%
  ResourceAccessList() %>%
  synapseClient::append(synSetPermissions(principalId = '273995', 
                                       accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
                                                      'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS'))) %>%
  synapseClient::append(synSetPermissions(principalId = '3344250', 
                                       accessType = c('READ', 'DOWNLOAD')))
# Get annotations
all.annotations = annotations(COUNT_OBJ)
# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq (Normalised) Diagnosis Removed", parentId = parentId)
CODE <- synStore(CODE)
old.acl = synGetEntityACL(CODE@properties$id)
synChangeEntityACL(CODE@properties$id, new.racl)
# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'ROSMAP_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('ROSMAP_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$normalizationStatus	= TRUE
all.annotations@annotations@stringAnnotations$normalizationType	= 'CQN'
all.annotations@annotations@stringAnnotations$fileFormat = 'tsv'
all.annotations@annotations@stringAnnotations$dataSubType = 'covariates'
annotations(COV_OBJ) = all.annotations
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName,
                   executed = thisFile, activityDescription = activityDescription)
synChangeEntityACL(COV_OBJ@properties$id, new.racl)
# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('ROSMAP_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'filteredCounts'
annotations(COUNT_OBJ) = all.annotations
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# Store filtered counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_eCounts.tsv', sep = '\t', row.names=F, quote=F)
ECOUNT_OBJ = File('ROSMAP_DLPFC_eCounts.tsv', name = 'Counts (estimated)', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'estimatedCounts'
annotations(ECOUNT_OBJ) = all.annotations
ECOUNT_OBJ = synStore(ECOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('ROSMAP_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'filteredLCPM'
annotations(LCOUNT_OBJ) = all.annotations
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('ROSMAP_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'offset'
annotations(OFFSET_OBJ) = all.annotations
OFFSET_OBJ = synStore(OFFSET_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('ROSMAP_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'designMatrix'
annotations(DM_OBJ) = all.annotations
DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
synChangeEntityACL(DM_OBJ@properties$id, new.racl)
# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_SurVar.tsv', sep = '\t', row.names=F, quote=F)
SURR_OBJ = File('ROSMAP_DLPFC_SurVar.tsv', name = 'Surrogate Variables', parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'surrogateVariables'
annotations(SURR_OBJ) = all.annotations
SURR_OBJ = synStore(SURR_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# Store residual gene expression for eQTL analysis
RESIDUAL.SVA.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_eQTLResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
eEXP_OBJ = File('ROSMAP_DLPFC_eQTLResidualExpression.tsv', 
                name = 'Normalised, covariates, surrogate and Diagnosisvariable adjusted residual expression (for eQTL)',
                parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'residualGeneExpForeQTL'
annotations(eEXP_OBJ) = all.annotations
eEXP_OBJ = synStore(eEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('ROSMAP_DLPFC_netResidualExpression.tsv', 
                name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
                parentId = CODE$properties$id)
all.annotations@annotations@stringAnnotations$dataSubType = 'residualGeneExpForNetAnlz'
annotations(nEXP_OBJ) = all.annotations
nEXP_OBJ = synStore(nEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Delete folder acl
synChangeEntityACL(CODE@properties$id, old.acl@resourceAccess)
stopCluster(cl)
```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapseClient)
library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
synapseLogin()
knit2synapse::knitfile2synapse(file = "./ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
                                 owner = "syn20798014")#,
                                 #entityName = 'ROSMAP Reprocessed RNASeq (Normalised) Diagnosis Regressed Using #Diagnosis as Covariate')
```

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Add In SynStore Steps

@@
 parentId = 'syn20798014';
-activityName = 'Covariate adjustments';
+activityName = 'Covariate and Diagnosis Regression';
 activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
@@
 # Github link
-thisRepo <- getRepo(repository = "kelshmo/Brain_Reg_Net", ref="branch", refName='CMC')
-thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
+thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
 ```
@@
 ```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
+activityName = 'Covariate and Diagnosis Regression';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
+
+# Code WTF is this??
+CODE <- Folder(name = "DLPFC - RSEM - EXPECTED COUNTS - GRCh37 - CQN - SVAandDiagnosisRegress - JKG", parentId = parentId)
+CODE <- synStore(CODE)
+
 #Set Used SynIDs For Provenance
@@
 )
+
+# Store enrichment results
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Corrected.tsv', 
+                  name = 'SVA and Diagnosis Regressed Data', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'SVA_Diagnosis_Regressed'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
 

### 2019-09-17 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
SynStore Fix

---
title: Covariate and differential expression analysis of MSSM reprocessed counts
author: Thanneer Perumal
editor_options:
  chunk_output_type: console
---
  Date of analysis update: "`r date()`"

  syn8691099.1
syn10156693.3
syn8698270.1
syn8449369.2
syn6100548.7
syn6101474.4

The [markdown](https://www.synapse.org/#!Synapse:syn8484987) produced for this publication is available on Synapse with files linked via Provenance.

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(synapser)
library(knitr)
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('./utilityFunctions/parallelDuplicateCorrelation.R')
source('./utilityFunctions/irwsva.build.R')
source('./utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synLogin}
synLogin()
```

### Data download
Obtain count matrix and metadata from synapse
```{r download.data}
# Get reprocessed sample counts for temporal cortex
COUNT_ID <- 'syn8691099';
ALL_USED_IDs <- COUNT_ID
COUNT <- synapser::synGet(COUNT_ID, version = 1)$path %>%
  read.table(header=T, sep='\t', check.names = F, row.names = 1)
# Convert rownames of counts from tracking id to ensemble gene id
tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
  dplyr::mutate(ID = Gene.ID) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
rownames(tmp) = tmp$Gene.ID
rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
# Get sample ids
SampleID = data.frame(SampleID = colnames(COUNT),
                      ID = colnames(COUNT)) %>% 
  tidyr::separate(ID, c('A','B','ID'), sep = '_') %>%
  dplyr::select(SampleID, ID) %>%
  dplyr::mutate(ID = as.numeric(ID))
# Get technical metadata
METADATA_TECH_ID <- 'syn6100548'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_TECH_ID
METADATA_TECH <- synapser::synGet(METADATA_TECH_ID, version = 7)$path %>%
  read.table(sep=',',header=T, row.names=1) %>%
  group_by(sampleIdentifier) %>%
  top_n(1, -rRNA.rate) %>%
  dplyr::select(sampleIdentifier, BrodmannArea, barcode, individualIdentifier, batch, RIN) %>%
  unique %>%
  ddply(.(barcode), .fun = function(x){
    x = dplyr::mutate(x, batch = paste(batch, collapse = ''), RIN = sum(RIN, na.rm = T))  
  }) 
# Get 90+ age
METADATA_AGE_ID = 'syn10156693'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_AGE_ID
METADATA_AGE <- synapser::synGet(METADATA_AGE_ID, version = 3)$path %>%
  read.table(sep='\t', header=T)
# Get clinical metadata
METADATA_CLINICAL_ID <- 'syn6101474'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_CLINICAL_ID
METADATA_CLINICAL <- synapser::synGet(METADATA_CLINICAL_ID, version = 4)$path %>%
  read.csv(header = T)
# Get picard metrics from synapse
METADATA.PICARD_ID <- 'syn8698270';
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
METADATA.PICARD <- synGet(METADATA.PICARD_ID, version = 1)$path %>%
  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
  dplyr::rename(sampleIdentifier = sample)
METADATA <- dplyr::full_join(METADATA_TECH, METADATA_CLINICAL) %>%
  dplyr::inner_join(METADATA.PICARD) %>%
  dplyr::select(-AOD) %>%
  dplyr::left_join(METADATA_AGE)
colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))
colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
# Get gene specific parameters from synapse
GENE.PARAM = synGet('syn8449369', version = 2)$path %>% 
    read.table(sep='\t', header=T, stringsAsFactors=F)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% unique()
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% unique()
rownames(GENE.GC) = GENE.GC$ensembl_gene_id
```

### Data preprocessing
```{r preprocess.data,cache=FALSE, echo=TRUE}
# Choose samples with rRNA rate less than 5% and more PF_READS_ALIGNED
METADATA = as_tibble(METADATA, .name_repair = "unique") %>%
  plyr::ddply(.(barcode), .fun = function(x){
    x %>%
      dplyr::filter(PCT_RIBOSOMAL_BASES < 0.05) %>%
      dplyr::top_n(1, PF_READS_ALIGNED)
  }) %>%
  dplyr::filter(!is.na(BrodmannArea), 
                !is.na(CDR), 
                !is.na(PMI), 
                !is.na(RIN),
                !is.na(bbscore),
                !is.na(NP.1),
                !is.na(sampleIdentifier),
                RIN >= 5,
                BrodmannArea %in% c('BM10', 'BM22', 'BM36', 'BM44'))
# Fix metadata
METADATA = METADATA %>%
  dplyr::rename(Sex = SEX) %>%
  dplyr::mutate(AOD = gsub('\\+','',AOD),
                Tissue = factor(BrodmannArea,
                                     levels = c('BM10', 'BM22', 'BM36', 'BM44'),
                                     labels = c('BM10' = 'FP', 'BM22' = 'STG', 
                                                'BM36' = 'PHG', 'BM44' = 'IFG')), 
                RIN2 = RIN^2, 
                Sex = factor(Sex, levels = c('M','F'), labels = c('MALE', 'FEMALE')),
                Tissue1 = Tissue)
rownames(METADATA) = METADATA$sampleIdentifier
# Get harmonised case control definition
METADATA$Diagnosis = 'OTHER'
METADATA$Diagnosis[METADATA$CDR <= 0.5 & METADATA$bbscore <= 3 & METADATA$NP.1 <= 1] = 'CONTROL'
METADATA$Diagnosis[METADATA$CDR >= 1 & METADATA$bbscore >= 4 & METADATA$NP.1 >= 2] = 'AD'
METADATA$Tissue.Diagnosis = paste(METADATA$Tissue, METADATA$Diagnosis, sep = '.')
# Fix missing batch
levels(METADATA$batch)[levels(METADATA$batch) == ''] = 'NoBatch'
# Introduce ApoE4
METADATA$APOE4 = 0
METADATA$APOE4[METADATA$Apo1 == 4 | METADATA$Apo2 == 4] = 1
METADATA$APOE4[METADATA$Apo1 == 4 & METADATA$Apo2 == 4] = 2
METADATA$Tissue.APOE4 = paste(METADATA$Tissue, METADATA$APOE4, sep = '.')
# Match covariates to expression data
indToRetain = intersect(METADATA$sampleIdentifier, colnames(COUNT))
indRemoved = setdiff(colnames(COUNT), METADATA$sampleIdentifier)
COUNT <- COUNT[, indToRetain]
METADATA = as.data.frame(METADATA)
rownames(METADATA) = METADATA$sampleIdentifier
METADATA = METADATA[indToRetain,]
```
`r dim(COUNT)[2]` samples from `r length(unique(METADATA$individualIdentifier))` subjects were obtained from the MSSM cohorts in AMP-AD reprocessed rnaseq project.

Following `r length(indRemoved)` samples were removed: `r indRemoved`

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering}
primaryVariable <- c("CDR", "Tissue.Diagnosis", "Tissue.APOE4")

#_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
FactorCovariates <- c("individualIdentifier", "batch", "RACE", "Sex", "Tissue.Diagnosis", "Tissue.APOE4", "Diagnosis")
ContCovariates <- c("CDR", "RIN", "RIN2", "AOD","PMI",  "PCT_PF_READS_ALIGNED", "PCT_CODING_BASES",
                    "PCT_INTERGENIC_BASES", "PCT_INTRONIC_BASES", "PCT_RIBOSOMAL_BASES")
METADATA$Diagnosis <- as.factor(METADATA$Diagnosis)
# Find inter relation between factor covariates
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
rownames(COVARIATES) <- METADATA$sampleIdentifier
# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=6}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left', padding  = unit(c(18,2,2,18), 'mm'))
```
### Explore metadata
```{r data.explore, fig.width = 12, fig.height = 8}
my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = RIN)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + my.theme
# Age Of Death
p[[2]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(AOD))) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('AOD') + my.theme
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PMI))) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI') + my.theme
# Ribosomal bases
p[[4]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PCT_RIBOSOMAL_BASES))) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Fraction of Ribosomal Bases') + my.theme
# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PCT_INTRONIC_BASES))) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + my.theme
# Intergenic bases
p[[6]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PCT_INTERGENIC_BASES))) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Intergenic Bases') + my.theme
multiplot(plotlist = p, cols = 3)
```

### Filter genes
* Remove genes that have less than 1 cpm counts in at least 50% of samples per Tissue x Diagnosis
* Remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Tissue.Diagnosis), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)
genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gc_content)]) %>%
  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene.length)]) %>%
  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
                                                 MIN_GENE_CPM=0, 
                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
# Check gene biotype
## Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "dec2016.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
## Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "gene_biotype"),
                       filters = "ensembl_gene_id", 
                       values = PROCESSED_COUNTS$filteredExprMatrix$genes,
                       mart = mart)
summary(factor(Ensemble2HGNC$gene_biotype)) %>%
  rownameToFirstColumn('Biotype') %>%
  dplyr::rename(fraction = DF) %>%
  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
  dplyr::filter(fraction >= 0.01) %>%
  kable
```

### Library Normalisation
Library normalisation is performed using cqn (conditional quantile normalisation)
```{r cqn}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'gene.length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Outlier Analysis
#### Sample outliers
Outlier analysis is performed before library normalisation with raw cpm counts
```{r outlier.analysis, cache = FALSE, fig.width = 10}
indToRemove = c('hB_RNA_10622')
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  dplyr::mutate(label = SampleID) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Diagnosis, size=RIN, shape = Sex))
p <- p + theme_bw() + theme(legend.position="right")
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
p = ggplot(tmp1 %>%
             dplyr::filter(SampleID %in% indToRemove),
           aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'top') + facet_grid(Diagnosis+.~Tissue)
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = COVARIATES %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.') %>%
  group_by(Tissue, Diagnosis) %>%
  summarise(count = n()) %>%
  spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are: `r kable(tmp)`

#### Gene outliers
Assign NA values to genes that are above and below 3 std deviation of its distribution
```{r winsorise.data}
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
CQN.GENE_EXPRESSION$E = LOG.CPM
CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6
```
### Sample clustering
PCA based clustering of samples
```{r decompse.normalise.data1.1, fig.height=5, fig.width=10, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Region','Diagnosis'), sep = '\\.') %>% 
  dplyr::mutate(Region = factor(Region), batch = factor(batch))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Diagnosis, size=RIN, shape = Sex))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(.~Region, scales = 'free_y')
p
```
Tree based classification of samples
```{r decompse.normalise.data1.2, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = (COVARIATES[,c(FactorCovariates), drop = F])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.no.na)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.no.na))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
```{r preadj.covariates}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preadj.covariates.plot, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Normalisation (iterative design)
Since many covariates are correlated, re-normalising and re-adjusting COUNTS with an iterative design matrix.

NOTE:
1. Using a mixed effect model where random effect is chosen as individualIdentifier
2. Adding batch and Sex a priori to variable selection
3. Primary variable of interest Tissue.Diagnosis is excluded from the pool of available covariates for selection
```{r iterative.norm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('batch', 'Sex');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, 
                         c(postAdjustCovars, primaryVariable, 'individualIdentifier'))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
loopCount = 0 
while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
  writeLines(paste('Using following covariates in the model:',
                   paste(postAdjustCovars, collapse=', '),
                   'as fixed effects and individualIdentifier as random effect'))

  # Post adjusted design matrix
  DM1 = getDesignMatrix(COVARIATES[,postAdjustCovars,drop=F],Intercept = F)
  DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

  # Estimate voom weights for dispersion control
  cnts = NEW.COUNTS; cnts[is.na(cnts)] = 0
  VOOM.GENE_EXPRESSION = voom(cnts, design=DM1$design, 
                              plot=F, na.rm = T)

  # Calculate correlation values of random effects
  correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
                                             block = COVARIATES$individualIdentifier,
                                             method = 'lmer')
  # correlation = list(); correlation$cor = 0.3819258

  # Re-estimate voom weights
  if (!is.nan(correlation$cor)){
    # Re-estimate voom weights
    VOOM.GENE_EXPRESSION = voom(cnts, 
                                design=DM1$design, plot=F, 
                                block = COVARIATES$individualIdentifier, 
                                correlation = correlation$cor)

    # Fit linear model using new weights and new design
    VOOM.ADJUSTED.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                              design = DM1$design,
                              weights = VOOM.GENE_EXPRESSION$weights,
                              block = COVARIATES$individualIdentifier, 
                              correlation = correlation$cor)

    # Residuals after normalisation
    RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,
                                                  CQN.GENE_EXPRESSION$E)
  } else {
    notEstimable = c(notEstimable, postAdjustCovars[length(postAdjustCovars)])
    postAdjustCovars = postAdjustCovars[1:(length(postAdjustCovars)-1)]
  }

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates),
                         c(postAdjustCovars, primaryVariable, 'individualIdentifier'))

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  expr = RESIDUAL.GENE_EXPRESSION; expr[is.na(expr)] = 0; expr = expr[rowSums(expr)!=0,]
  residualSigCovars = runPCAandPlotCorrelations(expr, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

  # Add postadjusted covariates (if any)
  covariatesEffects = residualSigCovars$Effects.significantCovars[residCovars]

  postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects)))
  loopCount = loopCount + 1
  # print(loopCount)
}
modelStr <- paste(paste(gsub('_','\\\\_',postAdjustCovars), collapse=', '),
                  'as fixed effects')
tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`

### Sanity check
```{r residual.adj, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(expr, 
                                              COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
residualSigCovars[["PC_res"]][[2]]$plotData
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(expr))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
PCA of residual data
```{r decompse.normalise.data2.1, fig.height=6, fig.width=10, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(expr, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Region','Diagnosis'), sep = '\\.') %>% 
  dplyr::mutate(Region = factor(Region))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Diagnosis, size=RIN, shape = Sex))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(.~Region, scales = 'free_y')
p
```
Tree based clustering of residual data
```{r decompse.normalise.data2.2, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,FactorCovariates])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(expr)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Adjust data with covariates for Network Analysis
Identified covariates are regressed out from the expression matrix for network analysis
```{r network.adjust}
# Get design matrix
DESIGN.NET = getDesignMatrix(COVARIATES[, postAdjustCovars, drop = F], Intercept = F)
DESIGN.NET = DESIGN.NET$design[,linColumnFinder(DESIGN.NET$design)$indepCols]
# Re-estimate voom weights
VOOM.NET.WEIGHTS = voom(cnts, 
                        design = DESIGN.NET, plot=F,
                        block = COVARIATES$individualIdentifier, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.NET.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.NET.FIT = lmFit(VOOM.NET.WEIGHTS)
# Residuals after normalisation
RESIDUAL.NET.GENE_EXPRESSION = residuals.MArrayLM(VOOM.NET.FIT,
                                                  CQN.GENE_EXPRESSION$E)
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (Tissue.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts, 
                    design = MODEL1, plot=F,
                    block = COVARIATES$individualIdentifier, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS)
# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$E)
# Compute actual variance of all principal components
expr = RESIDUAL.SVA.GENE_EXPRESSION;
expr[is.na(expr)] = 0
tmp = svd(expr)
actual.var = tmp$d^2/sum(tmp$d^2)
# Compute permuted variance of all principal components
permuted.var = foreach(i = 1:20, .combine = rbind) %dopar% {
  tmp.residual = t(apply(expr, 1, sample, replace = FALSE))
  tmp = svd(tmp.residual)
  permuted.var = tmp$d^2/sum(tmp$d^2)
}
permuted.var = apply(permuted.var, 2, mean)
NUM.SV = sum(actual.var >= permuted.var[1])
# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.2)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p
# Estimate surrogate variables
SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$E.no.na,
                    MODEL1, MODEL0, n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(MODEL1)
# Re-estimate voom weights
VOOM.SVA.WEIGHTS = voom(cnts, 
                        design = cbind(MODEL1, SURR.VAR), plot=F,
                        block = COVARIATES$individualIdentifier, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.SVA.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.SVA.FIT = lmFit(VOOM.SVA.WEIGHTS)
# Residuals after normalisation
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(VOOM.SVA.FIT,
                                                  CQN.GENE_EXPRESSION$E)
# Add variable of interest back to the residuals
varsToAddIn = grep("Tissue.Diagnosis", colnames(MODEL1), value = T)
RESIDUAL.SVA.GENE_EXPRESSION = RESIDUAL.SVA.GENE_EXPRESSION + 
  VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
```

### Save Environment and SVA.GENE_EXPRESSION
```{r SAVE and Wrap}
save.image("MSBB.RData")
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = "MSBB_SVA_Diagnosis_Corrected.tsv", row.names = T, col.names = T, sep ="\t", quote=F)
```

### 2019-09-17 code/Mayo_RegressDiagnosis_4_TWAS.Rmd
SynStore Fix

---
title: Covariate and differential expression analysis of MAYO reprocessed counts
output: html_notebook
---
Date of analysis update: "`r date()`"

| *Synapse ID* | *File Name* |
|  -----------------------------------------  |   ---------                      |
| syn5223705.5 | | 
| syn8698211.1 | | 
| syn3817650.8 | | 
| syn8690904.1 | | 
| syn6126119.3 | | 
| syn8698214.1 | | 
| syn8449369.2 | | 
| syn6126114.3 | | 
| syn6145639.5 | | 
| syn8690799.1 | |

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(synapser)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')
library(knitr)
library(doParallel)
library(foreach)
library(sva)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('./utilityFunctions/parallelDuplicateCorrelation.R')
source('./utilityFunctions/irwsva.build.R')
source('./utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synLogin}
synLogin()
```

### Data download
Obtain count matrix and metadata from Synapse
```{r download.data}
# Get reprocessed sample counts for temporal cortex
COUNT_TC_ID <- 'syn8690799';
ALL_USED_IDs <- COUNT_TC_ID
COUNT_TC <- synGet(COUNT_TC_ID, version = 1)$path %>%
  read.table(header=T, sep='\t', check.names = F, row.names = 1)
# Get reprocessed sample counts for cerebellum
COUNT_CE_ID <- 'syn8690904';
ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_CE_ID
COUNT_CE <- synGet(COUNT_CE_ID, version = 1)$path %>%
  read.table(header=T, sep='\t', check.names = F, row.names = 1)
# Combine TCX and CBE counts
COUNT = cbind(COUNT_TC, COUNT_CE[rownames(COUNT_TC),])
# Convert rownames of counts from tracking id to ensemble gene id
tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
  dplyr::mutate(ID = Gene.ID) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
rownames(tmp) = tmp$Gene.ID
rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
# Get clinical metadata
METADATA_TC_ID <- 'syn3817650'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_TC_ID
METADATA_TC <- synGet(METADATA_TC_ID, version = 8)$path %>%
  read.table(sep=',',header=T, stringsAsFactors=F) %>%
  tidyr::separate(ID, c('Donor_ID', 'Tissue'), sep = '_') %>%
  dplyr::mutate(ID = paste(Donor_ID, Tissue, sep = '_'))
# Get clinical metadata
METADATA_CE_ID <- 'syn5223705'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_CE_ID
METADATA_CE <- synGet(METADATA_CE_ID, version = 5)$path %>%
  read.table(sep=',',header=T, stringsAsFactors=F) %>%
  tidyr::separate(SampleID, c('Donor_ID', 'Tissue')) %>%
  dplyr::mutate(ID = paste(Donor_ID, Tissue, sep = '_')) %>%
  dplyr::rename(Gender = Sex, FLOWCELL = Flowcell)
# Get picard metrics from synapse
METADATA_PICARD_CE_ID <- 'syn8698214';
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_CE_ID
METADATA_PICARD_CE <- synGet(METADATA_PICARD_CE_ID, version = 1)$path %>%
  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
  dplyr::rename(ID = sample)
# colnames(METADATA_PICARD_CE) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA_PICARD_CE))
# colnames(METADATA_PICARD_CE) = gsub('RnaSeqMetrics__','',colnames(METADATA_PICARD_CE))
METADATA_PICARD_TC_ID <- 'syn8698211';
ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_TC_ID
METADATA_PICARD_TC <- synGet(METADATA_PICARD_TC_ID, version = 1)$path %>%
  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
  dplyr::rename(ID = sample)
# colnames(METADATA_PICARD_TC) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA_PICARD_TC))
# colnames(METADATA_PICARD_TC) = gsub('RnaSeqMetrics__','',colnames(METADATA_PICARD_TC))
# Merge all metadata
METADATA = list(METADATA_TC, METADATA_CE) %>%
  data.table::rbindlist(use.names = T, fill = T) %>%
  dplyr::inner_join(list(METADATA_PICARD_TC, METADATA_PICARD_CE) %>% 
                      data.table::rbindlist(use.names = T, fill = T)) %>%
  as.data.frame
colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))
colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
# Get gene specific parameters from synapse
GENE.PARAM = synGet('syn8449369', version = 2)$path %>% 
  read.table(sep = '\t', header = T, stringsAsFactors = F)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% unique()
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% unique()
rownames(GENE.GC) = GENE.GC$ensembl_gene_id
# Samples excluded by MAYO investigators
SAMPLES.EXCLUDE = c(read.table(synGet('syn6126119', version = 3)$path, sep = '\t', header = T, stringsAsFactors = F)$Sample.Name,
                    read.table(synGet('syn6126114', version = 3)$path, sep = '\t', header = T, stringsAsFactors = F)$Sample.Name)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn6126119', 'syn6126114')
```
Following `r length(SAMPLES.EXCLUDE)` samples were removed from analysis as original investigators tagged them as outliers for various reasons as described here syn6126119, syn6126114
Samples removed are `r paste(SAMPLES.EXCLUDE, collapse = ', ')`

### Data preprocessing
```{r preprocess.data, echo=TRUE}
# Filter metadata
METADATA = as_tibble(METADATA, .name_repair = "unique") %>%
  dplyr::filter(ID %in% colnames(COUNT)) %>%
  dplyr::filter(!is.na(RIN)) %>%
  dplyr::filter(!is.na(PCT_INTRONIC_BASES)) %>%
  dplyr::filter(!is.na(AgeAtDeath)) %>%
  dplyr::filter(!is.na(Source)) %>%
  dplyr::filter(!(ID %in% SAMPLES.EXCLUDE)) %>%
  as.data.frame()
# Fix Tissue
METADATA$Tissue = gsub('CER', 'CBE', METADATA$Tissue)
# Fix AgeAtDeath
METADATA = METADATA %>%
  dplyr::mutate(AgeAtDeath = gsub("_or_above", "", AgeAtDeath))
# Fix Diagnosis
METADATA = METADATA %>%
  dplyr::mutate(Source.Diagnosis = Diagnosis) %>%
  dplyr::mutate(Source.Diagnosis = factor(Source.Diagnosis,
                                          levels = c('AD', 'Control', 'Pathologic Aging', 'PSP'),
                                          labels = c('AD', 'CONTROL', 'PATH_AGE', 'PSP'))) %>%
  dplyr::mutate(Diagnosis = gsub("Pathologic Aging", "OTHER", Diagnosis),
                Diagnosis = gsub("PSP", "OTHER", Diagnosis),
                Diagnosis = factor(Diagnosis, 
                                   levels = c("AD", "Control", "OTHER"),
                                   labels = c('AD', 'CONTROL', 'OTHER'))) %>%
  dplyr::mutate(Tissue.Diagnosis = paste(Tissue, Diagnosis, sep = '.'),
                Tissue.SourceDiagnosis = paste(Tissue, Source.Diagnosis, sep = '.'))
# Fix Gender
METADATA = METADATA %>%
  dplyr::mutate(Sex = Gender,
                Sex = factor(Sex, levels = c('F','M'), labels = c('FEMALE','MALE')))
# Get RIN square
METADATA = METADATA %>%
  dplyr::mutate(RIN2 = RIN^2)
# Add apoe4 genotype (0, 1, 2)
METADATA$APOE4 = 0
METADATA$APOE4[METADATA$ApoE %in% c(24, 34)] = 1
METADATA$APOE4[METADATA$ApoE %in% c(44)] = 2
METADATA$Tissue.APOE4 = paste(METADATA$Tissue, METADATA$APOE4, sep = '.')
# Match covariates to expression data
indToRetain = intersect(METADATA$ID, colnames(COUNT))
indRemoved = setdiff(colnames(COUNT), METADATA$ID)
COUNT <- COUNT[, indToRetain]
rownames(METADATA) = METADATA$ID
METADATA = METADATA[indToRetain,]
```
`r dim(COUNT)[2]` samples from `r length(unique(METADATA$Donor_ID))` subjects were obtained from the Mayo cohorts in AMP-AD reprocessed rnaseq project.

Following samples were removed `r indRemoved`

### Predict missing PMI
```{r predict.pmi}
# Get PMI
PMI = METADATA[,c('PMI', 'ID', 'Donor_ID'), drop = F]
PMI$PMI = PMI$PMI
# Get expression (convert counts to cpm)
expr = voom(COUNT, design = NULL)$E
ind = which(rowSums(expr>=1)/dim(expr)[2] >= 0.5)
expr = expr[ind,]
# Combine expression from different regions of brain of an individual into one
expr = plyr::dlply(PMI, .(Donor_ID), .fun = function(x, expr){
  data.frame(value = rowMeans(expr[,x$ID,drop = F], na.rm = T)) %>%
    plyr::rename(c('value' = unique(x$Donor_ID)))
}, expr, .parallel = F) %>%
  do.call(cbind,.)
# Split data into training and prediction set
PMI = dplyr::select(PMI, Donor_ID, PMI) %>% unique()
rownames(PMI) = PMI$Donor_ID
PMI = PMI[colnames(expr),]
# Fit a logistic regression model
x.train = expr[,!is.na(PMI$PMI)]
x.predict = expr[,is.na(PMI$PMI)]
y.train = PMI[!is.na(PMI$PMI),]
y.train = y.train[colnames(x.train), 'PMI']
plr.model = cv.glmnet(t(x.train), y.train, family = 'gaussian')
coeff = as.matrix(coef.glmnet(plr.model, s = 'lambda.min'))
ssres = sum((predict(plr.model, t(x.train), s = 'lambda.min', type = 'response') - y.train)^2)
sstot = sum((y.train-mean(y.train, na.rm = T))^2, na.rm = T)
R2.allgenes = 1-(ssres/sstot)
y.predict.all = predict(plr.model, t(x.predict), s = 'lambda.min', type = 'response') %>%
  rownameToFirstColumn('Donor_ID') %>%
  plyr::rename(c('1' = 'PMI'))
# Get genes that are predictors of PMI and use them as control probes
CONTROL.PROBES_ID = 'syn6145639'
ALL_USED_IDs = c(ALL_USED_IDs, CONTROL.PROBES_ID)
CONTROL.PROBES = fread(synGet(CONTROL.PROBES_ID, version = 5)$path, data.table = F) %>%
  dplyr::mutate(ID = x) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
# Initial normalisation of gene expression
ind = rownames(expr) %in% CONTROL.PROBES$ensembl_gene_id 
expr = expr[ind,]
# Fit a logistic regression model
x.train = expr[,!is.na(PMI$PMI)]
x.predict = expr[,is.na(PMI$PMI)]
y.train = PMI[!is.na(PMI$PMI),]
y.train = y.train[colnames(x.train), 'PMI']
plr.model = cv.glmnet(t(x.train), y.train, family = 'gaussian')
coeff = as.matrix(coef.glmnet(plr.model, s = 'lambda.min'))
ssres = sum((predict(plr.model, t(x.train), s = 'lambda.min', type = 'response') - y.train)^2)
sstot = sum((y.train-mean(y.train, na.rm = T))^2, na.rm = T)
R2.smallgenes = 1-(ssres/sstot)
y.predict = predict(plr.model, t(x.predict), s = 'lambda.min', type = 'response') %>%
  rownameToFirstColumn('Donor_ID') %>%
  plyr::rename(c('1' = 'PMI'))
PMI = PMI %>% 
  dplyr::select(Donor_ID, PMI) %>%
  dplyr::filter(!is.na(PMI)) %>%
  list(y.predict) %>%
  data.table::rbindlist(use.names = T, fill = T)
PMI$PMI[PMI$PMI < 0] = 0
METADATA = METADATA %>% 
  dplyr::select(-PMI) %>%
  dplyr::left_join(PMI)
```
Fitted R2 values are, (i) with all gx features `r round(R2.allgenes, 3)`, (ii) with small set of inferred gx features `r round(R2.smallgenes,3)`

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering}
primaryVariable <- c("Tissue.SourceDiagnosis", "Tissue.Diagnosis", "Tissue.APOE4")
#_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
FactorCovariates <- c("Donor_ID", "Source", "Sex", "FLOWCELL", "Tissue.SourceDiagnosis", "Tissue.Diagnosis", "Tissue.APOE4", "Diagnosis")
ContCovariates <- c("RIN", "RIN2", "AgeAtDeath","PMI", "PCT_PF_READS_ALIGNED", "PCT_CODING_BASES",
                    "PCT_INTERGENIC_BASES", "PCT_INTRONIC_BASES", "PCT_RIBOSOMAL_BASES")
# Find inter relation between factor covariates
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
rownames(COVARIATES) <- METADATA$ID
# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=6}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left', padding  = unit(c(18,2,2,18), 'mm'))
```
### Explore metadata
```{r data.explore, fig.width = 12, fig.height = 8}
my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = RIN)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + my.theme
# AgeAtDeath
p[[2]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(AgeAtDeath))) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('AgeAtDeath') + my.theme
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PMI))) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI') + my.theme
# Ribosomal bases
p[[4]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PCT_RIBOSOMAL_BASES))) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Fraction of Ribosomal Bases') + my.theme
# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PCT_INTRONIC_BASES))) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + my.theme
# Intergenic bases
p[[6]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(PCT_INTERGENIC_BASES))) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Intergenic Bases') + my.theme
multiplot(plotlist = p, cols = 3)
```

### Filter genes
* Remove genes that have less than 1 cpm counts in at least 50% of samples per Tissue x Diagnosis
* Remove genes with missing gene length and percentage GC content
```{r filter.genes}
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Tissue.Diagnosis), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)
genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gc_content)]) %>%
  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene.length)]) %>%
  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
                                                 MIN_GENE_CPM=0, 
                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
# Check gene biotype
## Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "dec2016.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
## Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "gene_biotype"),
                       filters = "ensembl_gene_id", 
                       values = PROCESSED_COUNTS$filteredExprMatrix$genes,
                       mart = mart)
summary(factor(Ensemble2HGNC$gene_biotype)) %>%
  rownameToFirstColumn('Biotype') %>%
  dplyr::rename(fraction = DF) %>%
  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
  dplyr::filter(fraction >= 0.01) %>%
  kable
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

### Library Normalisation
Library normalisation is performed using cqn (conditional quantile normalisation)
```{r cqn}
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'gene.length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Outlier Analysis
#### Sample outliers
Outlier analysis is performed before library normalisation with raw cpm counts
```{r outlier.analysis, cache = FALSE, fig.width = 10}
indToRemove = c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX",
                '1950_TCX', '1950_CER', '1925_TCX', '1957_CER')
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  dplyr::mutate(label = SampleID) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Source, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") 
p <- p + facet_grid(Tissue~.+Diagnosis, scales = 'free')
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
p = ggplot(tmp1 %>%
             dplyr::filter(SampleID %in% indToRemove) %>%
             droplevels(),
           aes(x = logCPM)) + geom_density() 
p = p + theme(legend.position = 'top') + facet_grid(Tissue~.+Diagnosis)
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = COVARIATES %>%
  dplyr::group_by(Tissue.Diagnosis) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.') %>%
  tidyr::spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are: `r kable(tmp)`

#### Gene outliers
Assign NA values to genes that are above and below 3 std deviation of its distribution
```{r winsorise.data}
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
CQN.GENE_EXPRESSION$E = LOG.CPM
CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6
```

### Sample clustering
PCA based clustering of samples
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Source, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") + facet_grid(Tissue+.~Diagnosis, scales = 'free_y')
p
```

Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
COVARIATES.tmp = (COVARIATES[,c(FactorCovariates), drop = F])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.no.na)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE, fig.height=10, fig.width=20}
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
p = ggplot(tmp1, aes(x = logCPM)) + geom_density() 
p = p + theme(legend.position = 'NONE') + facet_grid(Tissue+.~Diagnosis, scale = 'free')
p
```

Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.no.na))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
```{r preadj.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preadj.covariates.plot, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Normalisation (iterative design)
Since many covariates are correlated, re-normalising and re-adjusting COUNTS with an iterative design matrix.

NOTE:
1. Using a mixed effect model where random effect is chosen as Donor_ID
2. Adding Source, FLOWCELL and Gender a priori to variable selection
3. Primary variable of interest Tissue.Diagnosis is excluded from the pool of available covariates for selection
```{r iterative.norm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Source', 'FLOWCELL', 'Sex');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, 
                         c(postAdjustCovars, primaryVariable, 'Donor_ID'))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
notEstimable = c()
loopCount = 0 
while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
  writeLines(paste('Using following covariates in the model:',
                   paste(postAdjustCovars, collapse=', '),
                   'as fixed effects and Donor_ID as random effect'))

  # Post adjusted design matrix
  DM1 = getDesignMatrix(COVARIATES[,postAdjustCovars,drop=F],Intercept = F)
  DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

  # Estimate voom weights for dispersion control
  cnts = NEW.COUNTS; cnts[is.na(cnts)] = 0
  VOOM.GENE_EXPRESSION = voom(cnts, design=DM1$design, 
                              plot=F, na.rm = T)

  # Calculate correlation values of random effects
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E
  correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
                                             block = COVARIATES$Donor_ID,
                                             method = 'lmer')
  # correlation = list(); correlation$cor = 0.3819258

  if (!is.nan(correlation$cor)){
    # Re-estimate voom weights
    VOOM.GENE_EXPRESSION = voom(cnts, 
                                design=DM1$design, plot=F, 
                                block = COVARIATES$Donor_ID, 
                                correlation = correlation$cor)

    # Fit linear model using new weights and new design
    VOOM.ADJUSTED.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                              design = DM1$design,
                              weights = VOOM.GENE_EXPRESSION$weights,
                              block = COVARIATES$Donor_ID, 
                              correlation = correlation$cor)

    # Residuals after normalisation
    RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,
                                                  CQN.GENE_EXPRESSION$E)
  } else {
    notEstimable = c(notEstimable, postAdjustCovars[length(postAdjustCovars)])
    postAdjustCovars = postAdjustCovars[1:(length(postAdjustCovars)-1)]
  }

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates),
                         c(postAdjustCovars, primaryVariable, 'Donor_ID', notEstimable))

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  expr = RESIDUAL.GENE_EXPRESSION; expr[is.na(expr)] = 0
  residualSigCovars = runPCAandPlotCorrelations(expr, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

  # Add postadjusted covariates (if any)
  residCovars = setdiff(residualSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, notEstimable))
  covariatesEffects = residualSigCovars$Effects.significantCovars[residCovars]

  postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects)))
  loopCount = loopCount + 1
}
modelStr <- paste(paste(gsub('_','\\\\_',postAdjustCovars), collapse=', '),
                  'as fixed effects')
tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`

### Sanity check
```{r residual.adj, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(expr, 
                                              COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
residualSigCovars[["PC_res"]][[2]]$plotData
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(expr))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
PCA of residual data
```{r decompse.normalise.data2.1, fig.height=10, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(expr, scale.=T, center = T)
# Plot first 4 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Tissue.Diagnosis, c('Region','Diagnosis'), sep = '\\.') %>% 
  dplyr::mutate(Region = factor(Region),
                Source = factor(Source))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Source, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Region~., scales = 'free_y')
p
```
Tree based clustering of residual data
```{r decompse.normalise.data2.2, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,FactorCovariates])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(expr)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Adjust data with covariates for Network Analysis
Identified covariates are regressed out from the expression matrix for network analysis
```{r network.adjust}
# Get design matrix
DESIGN.NET = getDesignMatrix(COVARIATES[, postAdjustCovars, drop = F], Intercept = F)
DESIGN.NET = DESIGN.NET$design[,linColumnFinder(DESIGN.NET$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.NET.WEIGHTS = voom(cnts, design=DESIGN.NET, plot=F)
# Re-estimate voom weights
VOOM.NET.WEIGHTS = voom(cnts, 
                        design = DESIGN.NET, plot=F,
                        block = COVARIATES$Donor_ID, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.NET.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.NET.FIT = lmFit(VOOM.NET.WEIGHTS$E,
                     weights = VOOM.NET.WEIGHTS$weights,
                     design = VOOM.NET.WEIGHTS$design,
                     block = COVARIATES$Donor_ID, 
                     correlation = correlation$cor)
# Residuals after normalisation
RESIDUAL.NET.GENE_EXPRESSION = residuals.MArrayLM(VOOM.NET.FIT,
                                                  CQN.GENE_EXPRESSION$E)
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (Tissue.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES$Donor_ID, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS$E,
            weights = VOOM.WEIGHTS$weights,
            design = VOOM.WEIGHTS$design,
            block = COVARIATES$Donor_ID, 
            correlation = correlation$cor)
# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]
# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$E)
# Compute actual variance of all principal components
expr = RESIDUAL.SVA.GENE_EXPRESSION
expr[is.na(expr)] = 0
tmp = svd(expr)
actual.var = tmp$d^2/sum(tmp$d^2)
# Compute permuted variance of all principal components
permuted.var = foreach(i = 1:20, .combine = rbind) %dopar% {
  tmp.residual = t(apply(expr, 1, sample, replace = FALSE))
  tmp = svd(tmp.residual)
  permuted.var = tmp$d^2/sum(tmp$d^2)
}
permuted.var = apply(permuted.var, 2, mean)
NUM.SV = sum(actual.var >= permuted.var[1])
# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.2)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p
# Estimate surrogate variables
SURR.VAR = irwsva.build(CQN.GENE_EXPRESSION$E.no.na,
                        MODEL1, MODEL0, n.sv = NUM.SV, 
                        B = 30, tol = 1e-20)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(MODEL1)
# Estimate voom weights for dispersion control
VOOM.SVA.WEIGHTS = voom(cnts, design=cbind(MODEL1, SURR.VAR), plot=F)
# Re-estimate voom weights
VOOM.SVA.WEIGHTS = voom(cnts, 
                        design = cbind(MODEL1, SURR.VAR), plot=F,
                        block = COVARIATES$Donor_ID, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.SVA.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.SVA.FIT = lmFit(VOOM.SVA.WEIGHTS$E,
                     weights = VOOM.SVA.WEIGHTS$weights,
                     design = VOOM.SVA.WEIGHTS$design,
                     block = COVARIATES$Donor_ID, 
                     correlation = correlation$cor)
# Residuals after normalisation
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(VOOM.SVA.FIT,
                                                  CQN.GENE_EXPRESSION$E)
# Add variable of interest back to the residuals
varsToAddIn = grep("Tissue.Diagnosis", colnames(MODEL1), value = T)
RESIDUAL.SVA.GENE_EXPRESSION = RESIDUAL.SVA.GENE_EXPRESSION + 
  VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
```

### Save Environment and SVA.GENE_EXPRESSION
```{r SAVE and Wrap}
save.image("MAYO.RData")
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = "MAYO_SVA_Diagnosis_Corrected.tsv", row.names = T, col.names = T, sep ="\t", quote=F)

```

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
SynStore Fix

@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn20798014';
+parentId = 'syn20798011';
 activityName = 'Covariate and Diagnosis Regression';
@@
 # Code WTF is this??
-CODE <- Folder(name = "DLPFC - RSEM - EXPECTED COUNTS - GRCh37 - CQN - SVAandDiagnosisRegress - JKG", parentId = parentId)
+CODE <- Folder(name = "ROSMAP", parentId = parentId)
 CODE <- synStore(CODE)

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Full Store Implemented

@@
 
-# Store enrichment results
+# Store SVA results
 write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
 ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Corrected.tsv', 
-                  name = 'SVA and Diagnosis Regressed Data', 
+                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
                   parentId = CODE$properties$id)
@@
                       executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'SVA_Diagnosis_Regressed'
+all.annotations$dataSubType = 'residualGeneExpForeQTL'
 synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
-#Store file:
-activity <- Activity(
-    'Fancy Processing',
-    description='No seriously, really fancy processing',
-    used=c('syn1906480', 'http://data_r_us.com/fancy/data.txt'),
-    executed='syn1917825')
-file <- File('/path/to/data/file.xyz', description='Fancy new data', parent=project)
-file <- synStore(file, activity=activity)
-
-# Function to change entity ACL (also creates new acls if it doesn't exist)
-synChangeEntityACL <- function(id, new.racl){
-  tryCatch({ 
-    # If old acl exist update
-    old.acl = synGetEntityACL(id)
-    old.acl@resourceAccess = new.racl
-    synUpdateEntityACL(old.acl)
-  }, error = function(e){ 
-    # If not create a new acl
-    new.acl = AccessControlList(id = id, resourceAccess = new.racl)
-    synCreateEntityACL(new.acl)
-  })
-}
-
-# Create new resource acls
-new.racl = synapser::synSetPermissions(principalId = '3319864', 
-                          accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
-                                         'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS')) %>%
-  ResourceAccessList() %>%
-  synapseClient::append(synSetPermissions(principalId = '273995', 
-                                       accessType = c('UPDATE', 'CHANGE_SETTINGS', 'DELETE', 'READ', 
-                                                      'DOWNLOAD', 'MODERATE', 'CREATE', 'CHANGE_PERMISSIONS'))) %>%
-  synapseClient::append(synSetPermissions(principalId = '3344250', 
-                                       accessType = c('READ', 'DOWNLOAD')))
-# Get annotations
-all.annotations = annotations(COUNT_OBJ)
-# Code
-CODE <- Folder(name = "ROSMAP Reprocessed RNASeq (Normalised) Diagnosis Removed", parentId = parentId)
-CODE <- synStore(CODE)
-old.acl = synGetEntityACL(CODE@properties$id)
-synChangeEntityACL(CODE@properties$id, new.racl)
 # Store covariates
 COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
-write.table(COVARIATES, file = 'ROSMAP_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
-COV_OBJ = File('ROSMAP_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$normalizationStatus	= TRUE
-all.annotations@annotations@stringAnnotations$normalizationType	= 'CQN'
-all.annotations@annotations@stringAnnotations$fileFormat = 'tsv'
-all.annotations@annotations@stringAnnotations$dataSubType = 'covariates'
-annotations(COV_OBJ) = all.annotations
-COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName,
+write.table(COVARIATES, file = 'ROSMAP_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Covariates.tsv', 
+                  name = 'Covariates', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
                       executed = thisFile, activityDescription = activityDescription)
-synChangeEntityACL(COV_OBJ@properties$id, new.racl)
+all.annotations$dataSubType = 'covariates'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 # Store filtered counts
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
-COUNT_OBJ = File('ROSMAP_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'filteredCounts'
-annotations(COUNT_OBJ) = all.annotations
-COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
-# Store filtered counts
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', 
+                  name = 'Counts (filtered raw)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'filteredCounts'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store Estimated counts
 NEW.COUNTS %>%
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ECOUNT_OBJ = File('ROSMAP_DLPFC_eCounts.tsv', name = 'Counts (estimated)', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'estimatedCounts'
-annotations(ECOUNT_OBJ) = all.annotations
-ECOUNT_OBJ = synStore(ECOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', 
+                  name = 'Counts (estimated)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'estimatedCounts'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 # Store logCPM
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-LCOUNT_OBJ = File('ROSMAP_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'filteredLCPM'
-annotations(LCOUNT_OBJ) = all.annotations
-LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', 
+                  name = 'Counts (filtered logCPM)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'filteredLCPM'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 # Store cqn offsets
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
-OFFSET_OBJ = File('ROSMAP_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'offset'
-annotations(OFFSET_OBJ) = all.annotations
-OFFSET_OBJ = synStore(OFFSET_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', 
+                  name = 'Gene length and GC content offset', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'offset'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 # Store design matrix
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
-DM_OBJ = File('ROSMAP_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'designMatrix'
-annotations(DM_OBJ) = all.annotations
-DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
-synChangeEntityACL(DM_OBJ@properties$id, new.racl)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', 
+                  name = 'Design Matrix', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'designMatrix'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 # Store surrogate variables
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_DLPFC_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-SURR_OBJ = File('ROSMAP_DLPFC_SurVar.tsv', name = 'Surrogate Variables', parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'surrogateVariables'
-annotations(SURR_OBJ) = all.annotations
-SURR_OBJ = synStore(SURR_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
-# Store residual gene expression for eQTL analysis
-RESIDUAL.SVA.GENE_EXPRESSION %>%
-  rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_eQTLResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-eEXP_OBJ = File('ROSMAP_DLPFC_eQTLResidualExpression.tsv', 
-                name = 'Normalised, covariates, surrogate and Diagnosisvariable adjusted residual expression (for eQTL)',
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', 
+                  name = 'Surrogate Variables', 
                   parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'residualGeneExpForeQTL'
-annotations(eEXP_OBJ) = all.annotations
-eEXP_OBJ = synStore(eEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'surrogateVariables'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 # Store residual gene expression for network analysis
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-nEXP_OBJ = File('ROSMAP_DLPFC_netResidualExpression.tsv', 
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', 
                   name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
                   parentId = CODE$properties$id)
-all.annotations@annotations@stringAnnotations$dataSubType = 'residualGeneExpForNetAnlz'
-annotations(nEXP_OBJ) = all.annotations
-nEXP_OBJ = synStore(nEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
-# Delete folder acl
-synChangeEntityACL(CODE@properties$id, old.acl@resourceAccess)
 stopCluster(cl)
@@
 knit2synapse::knitfile2synapse(file = "./ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
-                                 owner = "syn20798014")#,
-                                 #entityName = 'ROSMAP Reprocessed RNASeq (Normalised) Diagnosis Regressed Using #Diagnosis as Covariate')
+                                 owner = "syn20798014")
 ```

### 2019-09-17 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Catch up Mayo MSBB

@@
 syn6101474.4
-
-The [markdown](https://www.synapse.org/#!Synapse:syn8484987) produced for this publication is available on Synapse with files linked via Provenance.
 
@@
 
-### Save Environment and SVA.GENE_EXPRESSION
-```{r SAVE and Wrap}
-save.image("MSBB.RData")
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = "MSBB_SVA_Diagnosis_Corrected.tsv", row.names = T, col.names = T, sep ="\t", quote=F)
+```{r synapse.parameters, include=FALSE, cache=TRUE}
+parentId = 'syn20798011';
+activityName = 'Covariate and Diagnosis Regression';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (IFG, STG, FP, PHG)';
+thisFileName <- 'MSBB_RegressDiagnosis_4_TWAS.Rmd'
+# Github link
+thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
 ```
+
+### Store files in synapse
+```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
+activityName = 'Covariate and Diagnosis Regression';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (IFG, STG, FP, PHG)';
+
+# Code WTF is this??
+CODE <- Folder(name = "MSBB", parentId = parentId)
+CODE <- synStore(CODE)
+
+#Set Used SynIDs For Provenance
+Syns_Used <- c("syn8691099", "syn10156693", "syn8698270", 
+               "syn8449369", "syn6100548", "syn6101474"
+)
+
+# Set annotations
+all.annotations = list(
+  dataType = 'mRNA',
+  dataSubType = 'geneExp',
+  summaryLevel = 'gene',
+  assay	 = 'RNAseq',
+  tissueTypeAbrv	= c('IFG', 'STG', 'FP', 'PHG'), 
+  study = 'MSBB', 
+  organism = 'HomoSapiens',
+  consortium	= 'AMPAD',
+  normalizationStatus	= TRUE,
+  normalizationType	= 'CQN',
+  rnaquantification = 'RSEM',
+  genomeAssemblyID = 'GRCh37'
+)
+
+# Store SVA results
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MSBB_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ = File('MSBB_SVA_Diagnosis_Corrected.tsv', 
+                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'residualGeneExpForeQTL'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store covariates
+COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
+write.table(COVARIATES, file = 'MSBB_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ = File('MSBB_SVA_Diagnosis_Covariates.tsv', 
+                  name = 'Covariates', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'covariates'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store filtered counts
+PROCESSED_COUNTS$filteredExprMatrix$counts %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_Counts.tsv', 
+                  name = 'Counts (filtered raw)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'filteredCounts'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store Estimated counts
+NEW.COUNTS %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_Counts.tsv', 
+                  name = 'Counts (estimated)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'estimatedCounts'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store logCPM
+CQN.GENE_EXPRESSION$y %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_logCPM.tsv', 
+                  name = 'Counts (filtered logCPM)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'filteredLCPM'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store cqn offsets
+CQN.GENE_EXPRESSION$offset %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_offset.tsv', 
+                  name = 'Gene length and GC content offset', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'offset'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store design matrix
+MODEL1 %>%
+  rownameToFirstColumn('SampleID') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_Design.tsv', 
+                  name = 'Design Matrix', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'designMatrix'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store surrogate variables
+SURR.VAR %>%
+  rownameToFirstColumn('SampleID') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_SurVar.tsv', 
+                  name = 'Surrogate Variables', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'surrogateVariables'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store residual gene expression for network analysis
+RESIDUAL.NET.GENE_EXPRESSION %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MSBB_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_netResidualExpression.tsv', 
+                  name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+stopCluster(cl)
+```
+
+### R Source Code
+[Github](`r thisFile`)
+
+```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
+library(synapseClient)
+library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
+synapseLogin()
+knit2synapse::knitfile2synapse(file = "~/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",
+                                 owner = "syn20798012")
+```

### 2019-09-17 code/Mayo_RegressDiagnosis_4_TWAS.Rmd
Catch up Mayo MSBB

@@
 
-### Save Environment and SVA.GENE_EXPRESSION
-```{r SAVE and Wrap}
-save.image("MAYO.RData")
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = "MAYO_SVA_Diagnosis_Corrected.tsv", row.names = T, col.names = T, sep ="\t", quote=F)
+```{r synapse.parameters, include=FALSE, cache=TRUE}
+parentId = 'syn20798011';
+activityName = 'Covariate and Diagnosis Regression';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
+thisFileName <- 'Mayo_RegressDiagnosis_4_TWAS.Rmd'
+# Github link
+thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+```
 
+### Store files in synapse
+```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
+activityName = 'Covariate and Diagnosis Regression';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (CBE, TCX)';
+
+# Code WTF is this??
+CODE <- Folder(name = "Mayo", parentId = parentId)
+CODE <- synStore(CODE)
+
+#Set Used SynIDs For Provenance
+Syns_Used <- c("syn5223705", "syn8698211", "syn3817650", "syn8690904", 
+"syn6126119", "syn8698214", "syn8449369", "syn6126114", "syn6145639", "syn8690799"
+)
+
+# Set annotations
+all.annotations = list(
+  dataType = 'mRNA',
+  dataSubType = 'geneExp',
+  summaryLevel = 'gene',
+  assay	 = 'RNAseq',
+  tissueTypeAbrv	= c('TCX', 'CBE'), 
+  study = 'MAYO', 
+  organism = 'HomoSapiens',
+  consortium	= 'AMPAD',
+  normalizationStatus	= TRUE,
+  normalizationType	= 'CQN',
+  rnaquantification = 'RSEM',
+  genomeAssemblyID = 'GRCh37'
+)
+
+# Store SVA results
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MAYO_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ = File('MAYO_SVA_Diagnosis_Corrected.tsv', 
+                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'residualGeneExpForeQTL'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store covariates
+COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
+write.table(COVARIATES, file = 'MAYO_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ = File('MAYO_SVA_Diagnosis_Covariates.tsv', 
+                  name = 'Covariates', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'covariates'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store filtered counts
+PROCESSED_COUNTS$filteredExprMatrix$counts %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_Counts.tsv', 
+                  name = 'Counts (filtered raw)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'filteredCounts'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store Estimated counts
+NEW.COUNTS %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_Counts.tsv', 
+                  name = 'Counts (estimated)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'estimatedCounts'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store logCPM
+CQN.GENE_EXPRESSION$y %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_logCPM.tsv', 
+                  name = 'Counts (filtered logCPM)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'filteredLCPM'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store cqn offsets
+CQN.GENE_EXPRESSION$offset %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_offset.tsv', 
+                  name = 'Gene length and GC content offset', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'offset'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store design matrix
+MODEL1 %>%
+  rownameToFirstColumn('SampleID') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_Design.tsv', 
+                  name = 'Design Matrix', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'designMatrix'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store surrogate variables
+SURR.VAR %>%
+  rownameToFirstColumn('SampleID') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_SurVar.tsv', 
+                  name = 'Surrogate Variables', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'surrogateVariables'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store residual gene expression for network analysis
+RESIDUAL.NET.GENE_EXPRESSION %>%
+  rownameToFirstColumn('ensembl_gene_id') %>%
+  write.table(file = 'MAYO_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_netResidualExpression.tsv', 
+                  name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+stopCluster(cl)
 ```
+
+### R Source Code
+[Github](`r thisFile`)
+
+```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
+library(synapseClient)
+library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
+synapseLogin()
+knit2synapse::knitfile2synapse(file = "~/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
+                                 owner = "syn20798012")
+```

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Catch up Mayo MSBB

@@
 ---
-title: Covariate and differential expression analysis of ROSMAP reprocessed counts Using Diagnosis as a covariate for TWAS
-author: "JKG - Adapted from: Thanneer Perumal"
+title: Covariate and differential expression analysis of ROSMAP reprocessed counts
+  Using Diagnosis as a covariate for TWAS
+author: 'JKG - Adapted from: Thanneer Perumal'
+output: pdf_document
 editor_options:
@@
   dplyr::filter(!is.na(RINcontinuous)) %>%
+  dplyr::filter(!is.na(PCT_INTRONIC_BASES)) %>%
   dplyr::filter(!is.na(pmi)) %>%
-  #dplyr::filter(!is.na(PCT_INTRONIC_BASES)) %>%
   dplyr::filter(!is.na(age_death)) %>%
@@
 
-### Save Environment and SVA.GENE_EXPRESSION
-```{r SAVE and Wrap, eval = F}
-save.image("ROSMAP.RData")
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = "ROSMAP_SVA_Diagnosis_Corrected.tsv", row.names = T, col.names = T, sep ="\t", quote=F)
-```
-
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
@@
 synapseLogin()
-knit2synapse::knitfile2synapse(file = "./ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
-                                 owner = "syn20798014")
+knit2synapse::knitfile2synapse(file = "~/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
+                                 owner = "syn20800296")
 ```

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

@@
 # Remove samples with no cogdx, RIN, PMI scores and age_death
+names(METADATA)[13] <- "PF_ALIGNED_BASES_alt"
 METADATA <- METADATA %>%

### 2019-09-17 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

@@
 library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synapseLogin()
+synLogin()
 knit2synapse::knitfile2synapse(file = "~/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",

### 2019-09-17 code/Mayo_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

@@
 library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synapseLogin()
+synLogin()
 knit2synapse::knitfile2synapse(file = "~/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",

### 2019-09-17 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Fix PF_Bases in ROSMAP

@@
 library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synapseLogin()
+synLogin()
 knit2synapse::knitfile2synapse(file = "~/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd", 

### 2019-09-18 code/Ancestry_PCA.Rmd
AWS CLI

---
title: "Process Genotypes For Ancestry Analysis"
author: "JKG"
date: "9/18/2019"
output: pdf_document
  chunk_output_type: console
---

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)

```

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
CORES=$(nproc)

wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel

grep CEU integrated_call_samples.20101123.ALL.panel | cut -f1 > CEU.samples.list
grep YRI integrated_call_samples.20101123.ALL.panel | cut -f1 > YRI.samples.list
grep CHB integrated_call_samples.20101123.ALL.panel | cut -f1 > CHB.samples.list
grep JPT integrated_call_samples.20101123.ALL.panel | cut -f1 > JPT.samples.list

tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz

for i in {1..22}
do
    tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
done

bcftools concat --threads $CORES chr22.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr21.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr20.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr19.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr18.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr17.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr16.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr15.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr14.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr13.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr12.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr9.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr11.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr10.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr8.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr7.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr6.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr5.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr4.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr3.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr2.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr1.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz -O z > phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz

rm chr*.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz

plink --vcf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz --threads $CORES --make-bed --out 1000Genomes
rm phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz

###Takeout INDV for PCA Population
cat CEU.samples.list YRI.samples.list CHB.samples.list JPT.samples.list > 1000G_IDV.list
paste 1000G_IDV.list 1000G_IDV.list > foo.txt;
mv foo.txt 1000G_IDV.list

rm *.samples.list;

plink --threads $CORES --bfile 1000Genomes --snps-only --keep 1000G_IDV.list --make-bed --out INDV_1000G_Pops
rm 1000Genomes.*
```

## Process MSBB WGS Data
* Pull VCFs from Synapse
* Convert to plink
* Merge across chromosomes
* Filter for 1000G SNPs
```{bash ProcessMSBB, echo=FALSE}
CORES=$(nproc)
##Pull VCF Files from Synapse
synapse get -r syn11707204 --downloadLocation VCF/

##Convert VCFs to plink
mkdir GWAS_Plink

for i in {22..1}
do
  vcftools --gzvcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i.recalibrated_variants.MSSM.vcf.gz --plink --out GWAS_Plink/MSSB_Chr_$i

  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i.recalibrated_variants.MSSM.vcf.gz

  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --out GWAS_Plink/MSSB_Chr_$i

  rm GWAS_Plink/*$i.ped
  rm GWAS_Plink/*$i.map
done

rm GWAS_Plink/*.tbi

##Merge Chromsomes in Plink Format 
for i in {2..22} 
do 
    echo GWAS_Plink/MSSB_Chr_$i >> MergedGWAS.txt
done 
plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --make-bed --allow-no-sex --out GWASTotal
rm -r WGS_Plink/

#Write SNP List for LDREF Data
#plink --threads $CORES --bfile INDV_1000G_Pops --write-snplist --out LDREF_SNPs

#Reformat SNP List for plink filter.txt
 awk '{ print $1"\t"$4"\t"$4"\t"$2 }' INDV_1000G_Pops.bim > LDREF_SNPs.txt

##Filter for SNPs in 1000G - LDREF_FiltSNPs
plink --threads $CORES --bfile GWASTotal --extract LDREF_SNPs.txt --make-bed --allow-no-sex --out MSBB_LDREF_FiltSNPs

#Rename Snps with rsIDs & Centimorgan Distance
#python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
```

### 2019-09-18 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
AWS CLI

@@
 ---
-title: Covariate and differential expression analysis of MSSM reprocessed counts
-author: Thanneer Perumal
+title: Covariate and analysis of MSSM reprocessed counts Regressing out Diagnosis as well for TWAS
+author: 'JKG - Adapted from: Thanneer Perumal'
+output: html_notebook
 editor_options:
@@
 # Source modified utility functions from limma and sva package
-source('./utilityFunctions/parallelDuplicateCorrelation.R')
-source('./utilityFunctions/irwsva.build.R')
-source('./utilityFunctions/f.pvalue.R')
+source('../utilityFunctions/parallelDuplicateCorrelation.R')
+source('../utilityFunctions/irwsva.build.R')
+source('../utilityFunctions/f.pvalue.R')
 knitr::opts_chunk$set(
@@
 ### Data preprocessing
-```{r preprocess.data,cache=FALSE, echo=TRUE}
+```{r preprocess.data,cache=FALSE, echo=FALSE}
 # Choose samples with rRNA rate less than 5% and more PF_READS_ALIGNED
@@
 Correlation/association between covariates at an FDR <= 0.1
-```{r covariates.correlation, fig.width=10, fig.height=6}
+```{r covariates.correlation, cache=FALSE, fig.width=10, fig.height=6}
 COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
@@
 ### Explore metadata
-```{r data.explore, fig.width = 12, fig.height = 8}
+```{r data.explore, cache=FALSE, fig.width = 12, fig.height = 8}
 my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
@@
 PCA based clustering of samples
-```{r decompse.normalise.data1.1, fig.height=5, fig.width=10, results='asis'}
+```{r decompse.normalise.data1.1, cache=FALSE, fig.height=5, fig.width=10, results='asis'}
 # Find principal components of expression to plot
@@
 Tree based classification of samples
-```{r decompse.normalise.data1.2, fig.height=6, fig.width=10, results='asis'}
+```{r decompse.normalise.data1.2, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
 # Eucledian tree based analysis
@@
 Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
-```{r preadj.covariates.plot, fig.width=12, fig.height=8}
+```{r preadj.covariates.plot, cache=FALSE, fig.width=12, fig.height=8}
 preAdjustedSigCovars[["PC_res"]][[2]]$plotData
@@
 ### Sanity check
-```{r residual.adj, fig.width=12, fig.height=8}
+```{r residual.adj, cache=FALSE, fig.width=12, fig.height=8}
 # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
@@
 PCA of residual data
-```{r decompse.normalise.data2.1, fig.height=6, fig.width=10, results='asis'}
+```{r decompse.normalise.data2.1, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
 # Find principal components of expression to plot
@@
 Tree based clustering of residual data
-```{r decompse.normalise.data2.2, fig.height=8, fig.width=12, results='asis'}
+```{r decompse.normalise.data2.2, cache=FALSE, fig.height=8, fig.width=12, results='asis'}
 # Eucledian tree based analysis
@@
 Conditioned on primary variable (Tissue.Diagnosis) and identified covariates estimate surrogate variables using SVA package
-```{r sva.adjust}
+```{r sva.adjust, cache=FALSE}
 # Get design matrix
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapseClient)
+library(synapser)
 library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
 synLogin()
-knit2synapse::knitfile2synapse(file = "~/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",
-                                 owner = "syn20798012")
+knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",
+                                          parentId ="syn20798011",
+                                          folderName = 'MSBB')
 ```

### 2019-09-18 code/Mayo_RegressDiagnosis_4_TWAS.Rmd
AWS CLI

@@
 ---
-title: Covariate and differential expression analysis of MAYO reprocessed counts
+title: Covariate Analysis of MAYO Reprocessed counts Regressing out Diagnosis as well for TWAS
+author: 'JKG - Adapted from: Thanneer Perumal'
 output: html_notebook
+editor_options:
+  chunk_output_type: console
 ---
@@
 ### Data preprocessing
-```{r preprocess.data, echo=TRUE}
+```{r preprocess.data, echo=FALSE}
 # Filter metadata
@@
 PCA based clustering of samples
-```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
+```{r decompse.normalise.data, cache=FALSE, fig.height=8, fig.width=8, results='asis', cache=FALSE}
 # Find principal components of expression to plot
@@
 Tree based clustering of samples
-```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
+```{r decompse.normalise.data.1, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
 COVARIATES.tmp = (COVARIATES[,c(FactorCovariates), drop = F])
@@
 PCA of residual data
-```{r decompse.normalise.data2.1, fig.height=10, fig.width=8, results='asis'}
+```{r decompse.normalise.data2.1, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
 # Find principal components of expression to plot
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapseClient)
+library(synapser)
 library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
 synLogin()
-knit2synapse::knitfile2synapse(file = "~/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
-                                 owner = "syn20798012")
+knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
+                                          parentId ="syn20798011",
+                                          folderName = 'Mayo')
 ```

### 2019-09-18 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
AWS CLI

@@
 ---
-title: Covariate and differential expression analysis of ROSMAP reprocessed counts
-  Using Diagnosis as a covariate for TWAS
+title: Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS
+
 author: 'JKG - Adapted from: Thanneer Perumal'
-output: pdf_document
+output: html_notebook
 editor_options:
@@
 Determine relationship between covariates
-```{r covariates.clustering, cache=TRUE}
+```{r covariates.clustering, cache=FALSE}
 primaryVariable <- c("cogdx", "Diagnosis", "APOE4")
@@
 Correlation/association between covariates at an FDR <= 0.1
-```{r covariates.correlation, fig.width=9, fig.height=6}
+```{r covariates.correlation, cache=FALSE, fig.width=9, fig.height=6}
 COVARIATES.CORRELATION = CovariateAnalysis::getAssociationStatistics(COVARIATES, PVAL = 0.05)
@@
 ### Explore metadata
-```{r data.explore, fig.width = 10, fig.height = 14}
+```{r data.explore, cache=FALSE, fig.width = 10, fig.height = 14}
 # RIN
@@
 PCA based clustering of samples
-```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
+```{r decompse.normalise.data, cache=FALSE, fig.height=8, fig.width=8, results='asis'}
 # Find principal components of expression to plot
@@
 Tree based clustering of samples
-```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
+```{r decompse.normalise.data.1, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
 # Eucledian tree based analysis
@@
 Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
-```{r preadj.covariates, cache=TRUE}
+```{r preadj.covariates, cache=FALSE}
 # Find correlation between PC's of gene expression with covariates
@@
 2. Primary variable of interest Diagnosis is excluded from the pool of available covariates for selection
-```{r iterative.norm, results='asis'}
+```{r iterative.norm, cache=FALSE, results='asis'}
 # Primary variable of interest
@@
 PCA of residual data
-```{r decompse.normalise.data2.1, fig.height=6, fig.width=8, results='asis'}
+```{r decompse.normalise.data2.1, cache=FALSE, fig.height=6, fig.width=8, results='asis'}
 # Find principal components of expression to plot
@@
 Tree based clustering of residual data
-```{r decompse.normalise.data2.2, fig.height=8, fig.width=12, results='asis'}
+```{r decompse.normalise.data2.2, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
 # Eucledian tree based analysis
@@
 Conditioned on primary variable (Diagnosis) and identified covariates estimate surrogate variables using SVA package
-```{r sva.adjust}
+```{r sva.adjust, cache=FALSE }
 # Get design matrix
@@
 ### Store files in synapse
-```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
+```{r synapse.store, include=FALSE, eval=TRUE, cache=TRUE}
 activityName = 'Covariate and Diagnosis Regression';
@@
 
-stopCluster(cl)
+#stopCluster(cl)
 ```
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapseClient)
+library(synapser)
 library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
 synLogin()
-knit2synapse::knitfile2synapse(file = "~/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd", 
-                               owner = "syn20800296")
+knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
+                                          parentId ="syn20798011",
+                                          folderName = 'ROSMAP')
 ```

### 2019-09-18 utilityFunctions/collateDiffExp.R

@@ -1,0 +1,72 @@
+### R function to combine all differential expression results
+## Load libraries
+library(synapseClient) library(knitr) library(githubr) library(CovariateAnalysis) 
+library(data.table) library(plyr) library(tidyverse) synapseLogin() diff.exp = lapply(c(MAYO = 
+'syn8468023',
+                    MSSM = 'syn10526259',
+                    ROSMAP = 'syn8456721'),
+                  function(id){
+                    fread(synGet(id)@filePath, data.table = FALSE, header = T)
+                  })
+############################################
+## Combine all differential expression results
+#### Organise model names
+diff.exp$MSSM$Model = factor(diff.exp$MSSM$Model) diff.exp$MAYO$Model = 
+factor(diff.exp$MAYO$Model) diff.exp$ROSMAP$Model = factor(diff.exp$ROSMAP$Model) 
+levels(diff.exp$ROSMAP$Model) = c("APOE4", "SourceDiagnosis", "Diagnosis", "Diagnosis.AOD", 
+"Diagnosis.Sex")
+#### Organise tissue names
+diff.exp$MSSM$Tissue = factor(diff.exp$MSSM$Tissue) setnames(diff.exp$MAYO, 'Tissue.ref', 
+'Tissue') diff.exp$MAYO$Tissue.ag = NULL diff.exp$MAYO$Tissue = factor(diff.exp$MAYO$Tissue) 
+setnames(diff.exp$ROSMAP, 'Region', 'Tissue') diff.exp$ROSMAP$Tissue = 
+factor(diff.exp$ROSMAP$Tissue)
+#### Organise Sex and fix comparison
+diff.exp$ROSMAP$Sex = 'ALL' diff.exp$ROSMAP$Sex[diff.exp$ROSMAP$Comparison == 
+"AD-CONTROL.IN.FEMALE"] = "FEMALE" diff.exp$ROSMAP$Sex[diff.exp$ROSMAP$Comparison == 
+"AD-CONTROL.IN.MALE"] = "MALE" diff.exp$ROSMAP$Comparison = factor(diff.exp$ROSMAP$Comparison) 
+levels(diff.exp$ROSMAP$Comparison) = c("AD-CONTROL", "AD-CONTROL", "AD-CONTROL.IN.FEMALE-MALE", 
+"AD-CONTROL",
+                                       "AOD", "AD-CONTROL", "1-0", "2-0", "2-1", "2-1", "4-1", 
+"4-2",
[…]

### 2019-09-18 utilityFunctions/f.pvalue.R

@@ -1,0 +1,19 @@
+f.pvalue <- function (dat, mod, mod0, tol = 1e-18) {
+  n <- dim(dat)[2]
+  m <- dim(dat)[1]
+  df1 <- dim(mod)[2]
+  df0 <- dim(mod0)[2]
+  p <- rep(0, m)
+  Id <- diag(n)
+  resid <- dat %*% (Id - mod %*% solve(t(mod) %*% mod, tol = tol) %*%
+                      t(mod))
+  rss1 <- rowSums(resid * resid)
+  rm(resid)
+  resid0 <- dat %*% (Id - mod0 %*% solve(t(mod0) %*% mod0, tol = tol) %*%
+                       t(mod0))
+  rss0 <- rowSums(resid0 * resid0)
+  rm(resid0)
+  fstats <- ((rss0 - rss1)/(df1 - df0))/(rss1/(n - df1))
+  p <- 1 - pf(fstats, df1 = (df1 - df0), df2 = (n - df1))
+  return(p)
+}

### 2019-09-18 utilityFunctions/irwsva.build.R

@@ -1,0 +1,39 @@
+irwsva.build <- function (dat, mod, mod0 = NULL, n.sv, B = 5, tol = 1e-18) {
+  n <- ncol(dat)
+  m <- nrow(dat)
+  if (is.null(mod0)) {
+    mod0 <- mod[, 1]
+  }
+  Id <- diag(n)
+  resid <- dat %*% (Id - mod %*% solve(t(mod) %*% mod, tol = tol) %*%
+                      t(mod))
+  uu <- eigen(t(resid) %*% resid)
+  vv <- uu$vectors
+  ndf <- n - dim(mod)[2]
+  pprob <- rep(1, m)
+  one <- rep(1, n)
+  Id <- diag(n)
+  df1 <- dim(mod)[2] + n.sv
+  df0 <- dim(mod0)[2] + n.sv
+  rm(resid)
+  cat(paste("Iteration (out of", B, "):"))
+  for (i in 1:B) {
+    mod.b <- cbind(mod, uu$vectors[, 1:n.sv])
+    mod0.b <- cbind(mod0, uu$vectors[, 1:n.sv])
+    ptmp <- f.pvalue(dat, mod.b, mod0.b, tol=tol)
+    pprob.b <- (1 - edge.lfdr(ptmp))
+    mod.gam <- cbind(mod0, uu$vectors[, 1:n.sv])
+    mod0.gam <- cbind(mod0)
+    ptmp <- f.pvalue(dat, mod.gam, mod0.gam, tol = tol)
+    pprob.gam <- (1 - edge.lfdr(ptmp))
+    pprob <- pprob.gam * (1 - pprob.b)
+    dats <- dat * pprob
+    dats <- dats - rowMeans(dats)
+    uu <- eigen(t(dats) %*% dats)
+    cat(paste(i, " "))
+  }
+  sv = svd(dats)$v[, 1:n.sv]
+  retval <- list(sv = sv, pprob.gam = pprob.gam, pprob.b = pprob.b,
+                 n.sv = n.sv)
+  return(retval)
+}

### 2019-09-18 utilityFunctions/parallelDuplicateCorrelation.R

@@ -1,0 +1,211 @@
+parallelDuplicateCorrelation.lmer <- function (object, design = NULL, ndups = 2, spacing = 1, 
+block = NULL,
+                                               trim = 0.15, weights = NULL) {
+  y <- getEAWP(object)
+  M <- y$exprs
+  ngenes <- nrow(M)
+  narrays <- ncol(M)
+  if (is.null(design))
+    design <- y$design
+  if (is.null(design))
+    design <- matrix(1, ncol(y$exprs), 1)
+  else {
+    design <- as.matrix(design)
+    if (mode(design) != "numeric")
+      stop("design must be a numeric matrix")
+  }
+  if (nrow(design) != narrays)
+    stop("Number of rows of design matrix does not match number of arrays")
+  ne <- nonEstimable(design)
+  if (!is.null(ne))
+    cat("Coefficients not estimable:", paste(ne, collapse = " "),
+        "\n")
+  nbeta <- ncol(design)
+  if (missing(ndups) && !is.null(y$printer$ndups))
+    ndups <- y$printer$ndups
+  if (missing(spacing) && !is.null(y$printer$spacing))
+    spacing <- y$printer$spacing
+  if (missing(weights) && !is.null(y$weights))
+    weights <- y$weights
+  if (!is.null(weights)) {
+    weights <- as.matrix(weights)
+    if (any(dim(weights) != dim(M)))
+      weights <- array(weights, dim(M))
+    M[weights < 1e-15] <- NA
+    weights[weights < 1e-15] <- NA
+  }
+  if (is.null(block)) {
+    if (ndups < 2) {
+      warning("No duplicates: correlation between duplicates not estimable")
+      return(list(cor = NA, cor.genes = rep(NA, nrow(M))))
+    }
+    if (is.character(spacing)) {
+      if (spacing == "columns")
+        spacing <- 1
+      if (spacing == "rows")
+        spacing <- object$printer$nspot.c
+      if (spacing == "topbottom")
+        spacing <- nrow(M)/2
+    }
+    Array <- rep(1:narrays, rep(ndups, narrays))
+  }
+  else {
+    ndups <- 1
+    nspacing <- 1
+    Array <- block
+  }
+  if (is.null(block)) {
+    M <- unwrapdups(M, ndups = ndups, spacing = spacing)
+    ngenes <- nrow(M)
+    if (!is.null(weights))
+      weights <- unwrapdups(weights, ndups = ndups, spacing = spacing)
[…]

### 2019-09-18 code/Ancestry_PCA.Rmd
Finished Diagnosis Regression

@@
 
+#ID Sample list of needed Ref Populations
 wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel
@@
 
-tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz
-
 for i in {1..22}
 do
-    tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
+    wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr1.integrated_phase$i\_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+     wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr1.integrated_phase$i\_v3.20101123.snps_indels_svs.genotypes.vcf.gz.tbi
+    #tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
 done
+
+```
+
+#tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz
 

### 2019-09-19 code/Ancestry_PCA-copy.Rmd
Final Regress

--- 2019-09-18 code/Ancestry_PCA.Rmd
@@
 ```{bash pull_1000Genomes, echo=FALSE}
-CORES=$(nproc)
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/plink-1.07-x86_64/
 
-wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel
+CORES=`expr $(nproc) - 2`
+
+#ID Sample list of needed Ref Populations
+wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel
+
+ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/
 
@@
 
-tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz
-
+#i=22
 for i in {1..22}
 do
-    tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
+	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+
+    gunzip ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+    rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+
+    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --threads $CORES --make-bed --out 1000Genomes_chr$i
+  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf
+
 done
+
+#Merge All Plink Files into genome wide
+for i in {2..22}
+do
+  echo 1000Genomes_chr$i >> Merge.List
+done
+
+```
+
+#tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz
 

### 2019-09-19 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Final Regress

@@
 library(foreach)
+library(githubr)
+
 cl = makeCluster(detectCores()-2)

### 2019-09-19 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Final Regress

@@
 title: Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS
-
 author: 'JKG - Adapted from: Thanneer Perumal'

### 2019-09-19 code/Ancestry_PCA.Rmd
Clean

--- 2019-09-18 code/Ancestry_PCA.Rmd
@@
 ```{bash pull_1000Genomes, echo=FALSE}
-CORES=$(nproc)
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
 
-wget ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel
+CORES=`expr $(nproc) - 2`
+
+#ID Sample list of needed Ref Populations
+wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/integrated_call_samples.20101123.ALL.panel
+
+ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/
 
@@
 
-tar -xvf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz.tgz
-
+#i=22
 for i in {1..22}
 do
-    tabix -p vcf chr$i\.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
+	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+
+    gunzip ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+    rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+
+    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
+  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf
+
 done
 
-bcftools concat --threads $CORES chr22.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr21.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr20.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr19.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr18.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr17.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr16.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr15.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr14.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr13.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr12.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr9.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr11.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr10.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr8.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr7.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr6.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr5.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr4.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr3.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr2.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz chr1.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz -O z > phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
+#Merge All Plink Files into genome wide
+for i in {2..22}
+do
+  echo 1000Genomes_chr$i >> Merge.List
+done
 
-rm chr*.phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
+plink --bfile 1000Genomes_chr1 --merge-list Merge.List --make-bed --out 1000Genomes_Merged
+rm 1000Genomes_chr*
 
-plink --vcf phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz --threads $CORES --make-bed --out 1000Genomes
-rm phase1_release_v3.20101123.snps_indels_svs.genotypes.refpanel.ALL.vcf.gz
+```
 

### 2019-09-19 code/Ancestry_PCA.Rmd
Ancestry Chunk1v1

@@
 
-#i=22
+#Make Plink IDV List of all 1000G Ref Samps to pull
+cat CEU.samples.list YRI.samples.list CHB.samples.list JPT.samples.list > 1000G_IDV.list
+paste 1000G_IDV.list 1000G_IDV.list > foo.txt
+mv foo.txt 1000G_IDV.list
+
+#Pull 1000G Data, convert to plink, Filt for INDV and SNPs
 for i in {1..22}
@@
   rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf
-
 done
 
-#Merge All Plink Files into genome wide
+#Merge All Plink Chr Files 
 for i in {2..22}
 do
-  echo 1000Genomes_chr$i >> Merge.List
+  echo 1000Genomes_chr$i >> Merge.list
 done
 
-plink --bfile 1000Genomes_chr1 --merge-list Merge.List --make-bed --out 1000Genomes_Merged
+plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
+
 rm 1000Genomes_chr*
-
+rm *.list
 ```

### 2019-09-19 code/Ancestry_PCA.Rmd
Ancestry Chunk1v2

@@
 
-    gunzip ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
+    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
   rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
-
-    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
-  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf
 done
@@
 rm *.list
-```
+rm *.panel
 
-###Takeout INDV for PCA Population
-cat CEU.samples.list YRI.samples.list CHB.samples.list JPT.samples.list > 1000G_IDV.list
-paste 1000G_IDV.list 1000G_IDV.list > foo.txt;
-mv foo.txt 1000G_IDV.list
-
-rm *.samples.list;
-
-plink --threads $CORES --bfile 1000Genomes --snps-only --keep 1000G_IDV.list --make-bed --out INDV_1000G_Pops
-rm 1000Genomes.*
 ```
@@
 ##Pull VCF Files from Synapse
+mkdir VCF
 synapse get -r syn11707204 --downloadLocation VCF/
@@
 
-  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --out GWAS_Plink/MSSB_Chr_$i
+  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
 

### 2019-09-19 code/Ancestry_PCA.Rmd
Chunk1v3

@@
 
+##Pull The LDREF Panel SNPS
+#Pull LDREF Data
+wget https://data.broadinstitute.org/alkesgroup/FUSION/LDREF.tar.bz2
+tar xjvf LDREF.tar.bz2
+
+#Merge  LDREF Data
+for i in {2..22} 
+do 
+    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
+done 
+plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef
+
+#Write SNP List for LDREF Data
+plink --threads $CORES --bfile TotalLDRef --write-snplist --out LDREF_SNPs
+
+#Reformat SNP List for plink filter.txt
+ awk '{ print $1"\t"$4"\t"$4"\t"$2 }' TotalLDRef.bim > LDREF_SNPs.txt
+
+rm -r LDREF/
+
 #Pull 1000G Data, convert to plink, Filt for INDV and SNPs
 for i in {1..22}
+#for i in {20..22}
 do
@@
 
-    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
+    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
   rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
@@
 for i in {2..22}
+#for i in {21..22}
 do
@@
 
-plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
+#_#plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
+plink --bfile 1000Genomes_chr20 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
 
-rm 1000Genomes_chr*
+#rm 1000Genomes_chr*
 rm *.list
 rm *.panel
+rm LDREF.tar.bz2
+rm MergedChrs.txt
 
@@
 
+#Merge  LDREF Data
+for i in {2..22} 
+do 
+    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
+done 
+plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef
+
 #Write SNP List for LDREF Data
@@
 #Reformat SNP List for plink filter.txt
- awk '{ print $1"\t"$4"\t"$4"\t"$2 }' INDV_1000G_Pops.bim > LDREF_SNPs.txt
+awk '{ print $1"\t"$4"\t"$4"\t"$2 }' 1000Genomes_Merged.bim > LDREF_SNPs.txt
 
@@
 ```
+
+## ReName the MSBB SNPS so the can be combined
+```{python ReNamer}
+import sys
+import os
+import re
+
+###This Script reannotates bim file name from a snp list
+#Usage:
+# python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
+
+InFile = TotalLDRef.bim       #sys.argv[1];
+#Gene_Annots/hg19/Merged_hg19_Filt_ENGS.bed
+InFileb = LDREF_FiltSNPs.bim  #sys.argv[2];
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
+
+	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
+	print >>OUT, Entry
+
+F1.close()
+```

### 2019-09-20 code/Ancestry_PCA.Rmd
Chunk2V1

@@
 for i in {1..22}
-#for i in {20..22}
 do
@@
 for i in {2..22}
-#for i in {21..22}
 do
@@
 
-#_#plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
-plink --bfile 1000Genomes_chr20 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
+plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
 
-#rm 1000Genomes_chr*
+rm 1000Genomes_chr*
 rm *.list
@@
 rm MergedChrs.txt
-
 ```
@@
 ```{bash ProcessMSBB, echo=FALSE}
-CORES=$(nproc)
+CORES=`expr $(nproc) - 2`
+PATH=$PATH:/home/jgockley/TWAS/bin/
 ##Pull VCF Files from Synapse
@@
 
+rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_X*
+rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_Y*
+rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_others*
+rm -r VCF/WGS_JointCalling/
+rm VCF/SYNAPSE_METADATA_MANIFEST.tsv
+
+#Convert to PLINK
 for i in {22..1}
 do
-  vcftools --gzvcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i.recalibrated_variants.MSSM.vcf.gz --plink --out GWAS_Plink/MSSB_Chr_$i
+  plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
+  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
+done
+rm -r VCF/
 
-  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i.recalibrated_variants.MSSM.vcf.gz
-
-  plink --file GWAS_Plink/MSSB_Chr_$i --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
-
-  rm GWAS_Plink/*$i.ped
-  rm GWAS_Plink/*$i.map
+#Replace the "." IDs with a uniq ID
+for i in {22..1}
+do
+  awk '{ print $1"\t"$1"_"$4"\t"$3"\t"$4"\t"$5"\t"$6 }' GWAS_Plink/MSSB_Chr_$i\.bim > foo.txt
+  mv foo.txt GWAS_Plink/MSSB_Chr_$i\.bim
 done
 
-rm GWAS_Plink/*.tbi
+#Make an LD_Ref SNPList with matching name Schema
+awk '{print $1"\t"$2"\t"$3"\t"$1"_"$2 }' LDREF_SNPs.txt > MSBB_LD_SNPS.txt
+
+##Merge Chromsomes in Plink Format 
+for i in {2..22} 
+do 
+    echo GWAS_Plink/MSSB_Chr_$i >> MergedGWAS.txt
+done
+
+CORES=`expr $(nproc) - 2`
+PATH=$PATH:/home/jgockley/TWAS/bin/
+plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
+#rm -r WGS_Plink/
+
+#Rename Snps with rsIDs & Centimorgan Distance
+#python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
+```
+
+## Process MAYO Genotyping Data
+```{bash MAYO}
+CORES=`expr $(nproc) - 2`
+#Download
+mkdir Mayo
+synapse get -r syn8650955 --downloadLocation Mayo/
+
+plink --bfile Mayo/MayoRNAseq_RNAseq_Genome-Wide_Genotypes_HRCimputed --threads $CORES --extract LDREF_SNPs.txt --range --make-bed --out Mayo_LDREF_Filt
+
+rm -r Mayo/
+#SNPS REMAINING COMPARED TO TOTAL LDREF SET:
+##1,187,249 out of 1,190,321 (  99.74% )
+
+#Rename Snps with rsIDs & Centimorgan Distance
+python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim
+mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim
+
+```
 

### 2019-09-20 code/Ancestry_PCA.Rmd
Update

@@
   tidy = FALSE,
-  cache = TRUE)
-
+  cache = TRUE,
+  results='hide')
 ```
@@
 PATH=$PATH:/home/jgockley/TWAS/bin/
-
 CORES=`expr $(nproc) - 2`
@@
 done 
-plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef
+plink --bfile LDREF/1000G.EUR.1 --threads $CORES --silent --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef
 
 #Write SNP List for LDREF Data
-plink --threads $CORES --bfile TotalLDRef --write-snplist --out LDREF_SNPs
+plink --threads $CORES --bfile TotalLDRef --silent --write-snplist --out LDREF_SNPs
 
@@
 
-    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
+    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --silent --threads $CORES --make-bed --out 1000Genomes_chr$i
   rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
 done
+```
+
+```{bash FOO}
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
+CORES=`expr $(nproc) - 2`
 
@@
 
-plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
+plink --bfile 1000Genomes_chr1 --merge-list Merge.list --silent --make-bed --out 1000Genomes_Merged
 
@@
 ```{bash ProcessMSBB, echo=FALSE}
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
 CORES=`expr $(nproc) - 2`
-PATH=$PATH:/home/jgockley/TWAS/bin/
 ##Pull VCF Files from Synapse
@@
 do
-  plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
+  plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --silent --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
   rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
@@
 
-CORES=`expr $(nproc) - 2`
-PATH=$PATH:/home/jgockley/TWAS/bin/
-plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
-#rm -r WGS_Plink/
+plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --silent --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
+rm -r WGS_Plink/
 
@@
 
-## Process MAYO Genotyping Data
-```{bash MAYO}
-CORES=`expr $(nproc) - 2`
-#Download
-mkdir Mayo
-synapse get -r syn8650955 --downloadLocation Mayo/
-
-plink --bfile Mayo/MayoRNAseq_RNAseq_Genome-Wide_Genotypes_HRCimputed --threads $CORES --extract LDREF_SNPs.txt --range --make-bed --out Mayo_LDREF_Filt
-
-rm -r Mayo/
-#SNPS REMAINING COMPARED TO TOTAL LDREF SET:
-##1,187,249 out of 1,190,321 (  99.74% )
-
-#Rename Snps with rsIDs & Centimorgan Distance
-python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim
-mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim
-
-```
-
-##Merge Chromsomes in Plink Format 
-for i in {2..22} 
-do 
-    echo GWAS_Plink/MSSB_Chr_$i >> MergedGWAS.txt
-done 
-plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --merge-list MergedGWAS.txt --make-bed --allow-no-sex --out GWASTotal
-rm -r WGS_Plink/
-
-#Merge  LDREF Data
-for i in {2..22} 
-do 
-    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
-done 
-plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef
-
-#Write SNP List for LDREF Data
-#plink --threads $CORES --bfile INDV_1000G_Pops --write-snplist --out LDREF_SNPs
-
-#Reformat SNP List for plink filter.txt
-awk '{ print $1"\t"$4"\t"$4"\t"$2 }' 1000Genomes_Merged.bim > LDREF_SNPs.txt
-
-##Filter for SNPs in 1000G - LDREF_FiltSNPs
-plink --threads $CORES --bfile GWASTotal --extract LDREF_SNPs.txt --make-bed --allow-no-sex --out MSBB_LDREF_FiltSNPs
-
-#Rename Snps with rsIDs & Centimorgan Distance
-#python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
-```
-
-## ReName the MSBB SNPS so the can be combined
+### ReName the MSBB SNPS so the can be combined
 ```{python ReNamer}
@@
 ```
+
+### Finalize the MSBB LD SNP-Set Derived from WGS
+```{bash FinalizeMSBB }
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+#Replace BIM File
+mv MSBB_LDREF_FiltSNPsRenamed.bim MSBB_LDREF_FiltSNPs.bim
+
+#Check the SNP-Set
+##These numbers should be equal:
+grep 'rs' MSBB_LDREF_FiltSNPs.bim | wc -l
+wc -l MSBB_LDREF_FiltSNPs.bim
+
+##This Number should be zero:
+grep '.' MSBB_LDREF_FiltSNPs.bim | wc -l
+```
+
+## Process MAYO Genotyping Data
+```{bash MAYO}
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+#Download
+mkdir Mayo
+synapse get -r syn8650955 --downloadLocation Mayo/
+
+plink --bfile Mayo/MayoRNAseq_RNAseq_Genome-Wide_Genotypes_HRCimputed --threads $CORES --extract LDREF_SNPs.txt --range --make-bed --out Mayo_LDREF_Filt
+
+rm -r Mayo/
+#SNPS REMAINING COMPARED TO TOTAL LDREF SET:
+##1,187,249 out of 1,190,321 (  99.74% )
+
+#Rename Snps with rsIDs & Centimorgan Distance
+#python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim
+
+```
+
+### ReName the Mayo SNPS so the can be combined
+```{python ReNamerMayo}
+import sys
+import os
+import re
+
+###This Script reannotates bim file name from a snp list
+#Usage:
+# python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
+
+InFile = TotalLDRef.bim       #sys.argv[1];
+#Gene_Annots/hg19/Merged_hg19_Filt_ENGS.bed
+InFileb = Mayo_LDREF_Filt.bim  #sys.argv[2];
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
+
+	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
+	print >>OUT, Entry
+
+F1.close()
+```
+
+### Finalize the Mayo LD SNP-Set Derived from imputed genotyping
+```{bash CheckMayo}
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim
+#Check the SNP-Set
+##These numbers should be equal:
+grep 'rs' Mayo_LDREF_Filt.bim | wc -l
+wc -l Mayo_LDREF_Filt.bim
+
+##This Number should be zero:
+grep '.' Mayo_LDREF_Filt.bim | wc -l
+```
+
+## Process ROSMAP Genotyping Data
+```{bash DosageToHardCalls}
+source ~/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+#Synapse gets:
+declare -A SynArr
+arr["1"]=syn5879161
+arr["10"]=syn5879677
+arr["11"]=syn5879748
+arr["12"]=syn5879792
+arr["13"]=syn5879812
+arr["14"]=syn5879827
+arr["15"]=syn5879828
+arr["16"]=syn5879830
+arr["17"]=syn5879832
+arr["18"]=syn5879834
+arr["19"]=syn5879835
+arr["2"]=syn5879456
+arr["20"]=syn5879836
+arr["21"]=syn5879837
+arr["22"]=syn5879838
+arr["3"]=syn5879461
+arr["4"]=syn5879463
+arr["5"]=syn5879470
+arr["6"]=syn5879472
+arr["7"]=syn5879473
+arr["8"]=syn5879559
+arr["9"]=syn5879628
+
+#Pull FAM File
+synapse get syn20809809
+
+#Loop Through chromosomes and Process
+for i in {1..22}
+do
+
+	synapse get ${arr[$i]}
+
+	chr=$i
+	echo "1 AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr"$chr".dosage.gz" > b.txt
+
+  #Write a Dosage File
+	plink --threads $CORES --fam Updated_Actual_Fam.fam --dosage b.txt list noheader format=1 --write-dosage
+
+  #Convert to plink hard calls 
+	plink2 --threads $CORES --fam Updated_Actual_Fam.fam --import-dosage plink.out.dosage format=1 --hard-call-threshold 0.1 --make-bed --out AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$chr
+
+	rm plink.out.dosage
+
+done
+rm b.txt
+
+##Merge Chromsomes in Plink Format 
+for i in {2..22} 
+do 
+    echo AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i >> MergedGWAS.txt
+done
+
+plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr1 --silent --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out ROSMAPTotal
+rm -r AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr*
+
+#Check the SNP-Set
+##These numbers should be equal:
+grep 'rs' ROSMAPTotal.bim | wc -l
+wc -l ROSMAPTotal.bim
+
+##This Number should be zero:
+grep '.' ROSMAPTotal.bim | wc -l
+```
+
+##Merge the Genotype Sets and Preform PCA
+```{bash MergeAndCall}
+
+```

### 2019-09-20 code/Ancestry_PCA.Rmd
Update Ancestry

@@
 PATH=$PATH:/home/jgockley/TWAS/bin/
+#PATH=$PATH:TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```
-
 ```{bash FOO}
@@
 ```
+
+##Plot PCA
+```{r PlotPCA}
+
+```
+
+## Cluster Based on Ancestry
+```{bash CLustPrep}
+plink --bfile Final_Merge --threads 32 --geno 0.0000001 --recode12 --compound-genotypes --out AllSnps4GemClust
+#777864
+
+#Remove non-snp data in the ped file
+awk '{$1=$2=$3=$4=$5=$6=""; print $0}' AllSnps4GemClust.ped > foo.txt
+perl -pe 's/([^\s]+)\s+([^\s]+)/$1$2/g' foo.txt > poo.txt
+awk '{ print $1"_"$2 }' AllSnps4GemClust.ped > foo.txt
+paste foo.txt poo.txt > AllGenos4GemClust.txt
+
+cp poo.txt test.txt
+sed -i 's/22/2/g' test.txt
+sed -i 's/00/3/g' test.txt
+sed -i 's/12/1/g' test.txt
+sed -i 's/11/0/g' test.txt
+
+paste foo.txt test.txt > AllGenos4GemClust.txt
+sed -i 's/\t/ /g' AllGenos4GemClust.txt
+sed -i 's/  */ /g' AllGenos4GemClust.txt
+
+```

### 2019-09-20 code/Ancestry_PCA.Rmd
Update CacheStatus

@@
 * Pull out reference populations (CEU, YRI, CHB, JPT)
-```{bash pull_1000Genomes, echo=FALSE}
+```{bash pull_1000Genomes, cache = FALSE, echo=FALSE}
 source ~/.bashrc
@@
 done
-```
-```{bash FOO}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
-CORES=`expr $(nproc) - 2`
 
@@
 * Filter for 1000G SNPs
-```{bash ProcessMSBB, echo=FALSE}
+```{bash ProcessMSBB, cache = FALSE, echo=FALSE}
 source ~/.bashrc
@@
 ### Finalize the MSBB LD SNP-Set Derived from WGS
-```{bash FinalizeMSBB }
+```{bash FinalizeMSBB, cache = FALSE  }
 source ~/.bashrc
@@
 ## Process MAYO Genotyping Data
-```{bash MAYO}
+```{bash MAYO, cache = FALSE}
 source ~/.bashrc
@@
 ### Finalize the Mayo LD SNP-Set Derived from imputed genotyping
-```{bash CheckMayo}
+```{bash CheckMayo, cache = FALSE}
 source ~/.bashrc
@@
 ## Process ROSMAP Genotyping Data
-```{bash DosageToHardCalls}
+```{bash DosageToHardCalls, cache = FALSE}
 source ~/.bashrc
@@
 ##Merge the Genotype Sets and Preform PCA
-```{bash MergeAndCall}
+```{bash MergeAndCall, cache = FALSE}
 
@@
 ##Plot PCA
-```{r PlotPCA}
+```{r PlotPCA, cache = FALSE}
 
@@
 ## Cluster Based on Ancestry
-```{bash CLustPrep}
+```{bash CLustPrep, cache = FALSE}
 plink --bfile Final_Merge --threads 32 --geno 0.0000001 --recode12 --compound-genotypes --out AllSnps4GemClust

### 2019-09-25 code/Ancestry_PCA.Rmd
Ancestry Update

--- 2019-09-20 code/Ancestry_PCA.Rmd
@@
   results='hide')
+library(reticulate)
 ```
+##Before running 
+Run the following in docker exec -it <CONTAINER> /bin/bash 
+chmod 777 /root
+mv TWAS/ /home/<USR>/TWAS/
+chown -hR <GID>:<USR> /home/<USR>/TWAS/
 
+## Login to Synapse Will need to replace with your credentials
+```{bash Login, echo=T, results='hide', eval=FALSE}
+source /root/.bashrc
+synapse login -u <USR> -p <PSWD> --rememberMe
+
+#Alternativly you can setup a credentials file as such:
+touch ~/.synapseConfig
+echo "[authentication]" >> ~/.synapseConfig
+echo "username = <USR>" >> ~/.synapseConfig
+echo "password = <PASWD>" >> ~/.synapseConfig
+```
 ## Pull 1000Genomes down and process
 * Pull out reference populations (CEU, YRI, CHB, JPT)
-```{bash pull_1000Genomes, echo=FALSE}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
+```{bash pull_1000Genomes, echo=T, results='hide', cache = FALSE, echo=FALSE}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#PATH=$PATH:TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 done
-```
-
-```{bash FOO}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
-CORES=`expr $(nproc) - 2`
 
@@
 
+#Store 1000G Populations
+mkdir 1000G_RefSamps
+mv CEU.samples.list 1000G_RefSamps/
+mv YRI.samples.list 1000G_RefSamps/
+mv JPT.samples.list 1000G_RefSamps/
+mv CHB.samples.list 1000G_RefSamps/
+
+#Clean Working Directory
 rm 1000Genomes_chr*
@@
 * Filter for 1000G SNPs
-```{bash ProcessMSBB, echo=FALSE}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
+```{bash ProcessMSBB, echo=T, results='hide', cache = FALSE}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
 CORES=`expr $(nproc) - 2`
+
 ##Pull VCF Files from Synapse
@@
 plink --threads $CORES --bfile GWAS_Plink/MSSB_Chr_1 --silent --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out GWASTotal
-rm -r WGS_Plink/
+#rm -r GWAS_Plink/
+rm MergedGWAS.txt
 
-#Rename Snps with rsIDs & Centimorgan Distance
-#python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
 ```
@@
 ### ReName the MSBB SNPS so the can be combined
-```{python ReNamer}
+```{python ReNamer, echo=T, results='hide'}
 import sys
@@
 
-###This Script reannotates bim file name from a snp list
-#Usage:
-# python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
-
-InFile = TotalLDRef.bim       #sys.argv[1];
-#Gene_Annots/hg19/Merged_hg19_Filt_ENGS.bed
-InFileb = LDREF_FiltSNPs.bim  #sys.argv[2];
+InFile = 'TotalLDRef.bim'
+InFileb = 'GWASTotal.bim' #LDREF_FiltSNPs.bim
 
@@
 F1.close()
+OUT.close()
 ```
@@
 ### Finalize the MSBB LD SNP-Set Derived from WGS
-```{bash FinalizeMSBB }
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
+```{bash FinalizeMSBB, echo=T, results='hide', cache = FALSE  }
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
 CORES=`expr $(nproc) - 2`
-
-#Replace BIM File
-mv MSBB_LDREF_FiltSNPsRenamed.bim MSBB_LDREF_FiltSNPs.bim
 
@@
 ##These numbers should be equal:
-grep 'rs' MSBB_LDREF_FiltSNPs.bim | wc -l
-wc -l MSBB_LDREF_FiltSNPs.bim
+grep 'rs' GWASTotalRenamed.bim | wc -l
+cat GWASTotalRenamed.bim | wc -l
 
 ##This Number should be zero:
-grep '.' MSBB_LDREF_FiltSNPs.bim | wc -l
+Repod=$(awk '{print $2}' GWASTotalRenamed.bim | grep "\." - | wc -l)
+if [ "$Repod" -eq "0" ]; then
+   mv GWASTotalRenamed.bim GWASTotal.bim;
+fi
+if [ "$Repod" -ne "0" ]; then
+   echo $Repod" lines could've failed Translation"
+fi
+plink --bfile GWASTotal --silent --threads $CORES --make-bed --out MSBB_Preliminary_Genos
+rm GWASTotal.*
 ```
@@
 ## Process MAYO Genotyping Data
-```{bash MAYO}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
+```{bash MAYO, echo=T, results='hide', cache = FALSE}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ##1,187,249 out of 1,190,321 (  99.74% )
-
-#Rename Snps with rsIDs & Centimorgan Distance
-#python BimAnotator.py TotalLDRef.bim Mayo_LDREF_Filt.bim
-
 ```
@@
 ### ReName the Mayo SNPS so the can be combined
-```{python ReNamerMayo}
+```{python ReNamerMayo, echo=T, results='hide'}
 import sys
@@
 
-###This Script reannotates bim file name from a snp list
-#Usage:
-# python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim
-
-InFile = TotalLDRef.bim       #sys.argv[1];
-#Gene_Annots/hg19/Merged_hg19_Filt_ENGS.bed
-InFileb = Mayo_LDREF_Filt.bim  #sys.argv[2];
+InFile = 'TotalLDRef.bim'
+InFileb = 'Mayo_LDREF_Filt.bim'
 
@@
 ### Finalize the Mayo LD SNP-Set Derived from imputed genotyping
-```{bash CheckMayo}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
+```{bash CheckMayo, echo=T, results='hide', cache = FALSE}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
 CORES=`expr $(nproc) - 2`
 
-mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim
 #Check the SNP-Set
 ##These numbers should be equal:
-grep 'rs' Mayo_LDREF_Filt.bim | wc -l
-wc -l Mayo_LDREF_Filt.bim
+grep 'rs' Mayo_LDREF_FiltRenamed.bim | wc -l
+cat Mayo_LDREF_Filt.bim | wc -l
 
 ##This Number should be zero:
-grep '.' Mayo_LDREF_Filt.bim | wc -l
+Repod=$(awk '{print $2}' Mayo_LDREF_FiltRenamed.bim | grep "\." - | wc -l)
+if [ "$Repod" -eq "0" ]; then
+   mv Mayo_LDREF_FiltRenamed.bim Mayo_LDREF_Filt.bim;
+fi
+if [ "$Repod" -ne "0" ]; then
+   echo $Repod" lines could've failed Translation"
+fi
+plink --bfile Mayo_LDREF_Filt --silent --threads $CORES --make-bed --out Mayo_Preliminary_Genos
+rm Mayo_LDREF_Filt.*
 ```
@@
 ## Process ROSMAP Genotyping Data
-```{bash DosageToHardCalls}
-source ~/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/bin/
+```{bash DosageToHardCalls, echo=T, results='hide', cache = FALSE}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 arr["1"]=syn5879161
+arr["2"]=syn5879456
+arr["3"]=syn5879461
+arr["4"]=syn5879463
+arr["5"]=syn5879470
+arr["6"]=syn5879472
+arr["7"]=syn5879473
+arr["8"]=syn5879559
+arr["9"]=syn5879628
 arr["10"]=syn5879677
@@
 arr["19"]=syn5879835
-arr["2"]=syn5879456
 arr["20"]=syn5879836
@@
 arr["22"]=syn5879838
-arr["3"]=syn5879461
-arr["4"]=syn5879463
-arr["5"]=syn5879470
-arr["6"]=syn5879472
-arr["7"]=syn5879473
-arr["8"]=syn5879559
-arr["9"]=syn5879628
 
@@
   #Write a Dosage File
-	plink --threads $CORES --fam Updated_Actual_Fam.fam --dosage b.txt list noheader format=1 --write-dosage
+	plink --threads $CORES --fam Updated_Actual_Fam.fam --silent --dosage b.txt list noheader format=1 --write-dosage
 
   #Convert to plink hard calls 
-	plink2 --threads $CORES --fam Updated_Actual_Fam.fam --import-dosage plink.out.dosage format=1 --hard-call-threshold 0.1 --make-bed --out AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$chr
+	plink2 --threads $CORES --fam Updated_Actual_Fam.fam --silent --import-dosage plink.out.dosage format=1 --hard-call-threshold 0.1 --make-bed --out AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$chr
 
+	#Clean out dosage to save disk space!
 	rm plink.out.dosage
-
+  rm AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i\.dosage.gz
 done
 rm b.txt
-
 ##Merge Chromsomes in Plink Format 
-for i in {2..22} 
+echo AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr2 > MergedGWAS.txt
+for i in {3..22} 
 do 
@@
 
-plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr1 --silent --merge-list MergedGWAS.txt --extract MSBB_LD_SNPS.txt --make-bed --allow-no-sex --out ROSMAPTotal
+plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr1 --silent --merge-list MergedGWAS.txt  --make-bed --allow-no-sex --out ROSMAP_Temp
+
 rm -r AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr*
+rm MergedGWAS.txt
 
-#Check the SNP-Set
-##These numbers should be equal:
-grep 'rs' ROSMAPTotal.bim | wc -l
-wc -l ROSMAPTotal.bim
+grep 'rs' ROSMAP_Temp.bim | awk '{ print $2 }' - | sort - > RSIDS.txt
+awk '{ print $4 }' LDREF_SNPs.txt | sort - > RefIDs.txt
 
-##This Number should be zero:
-grep '.' ROSMAPTotal.bim | wc -l
+comm -12 RefIDs.txt RSIDS.txt > RosMapKeeps.txt
+
+plink --threads $CORES --bfile ROSMAP_Temp --extract RosMapKeeps.txt --silent --make-bed --allow-no-sex --out ROSMAP_temp
+rm ROSMAP_Temp.*
+rm RSIDS.txt
+rm RefIDs.txt
+#1705 people pass mind
+#1068685 of 1187582 snps pass --geno 0.1
+```
+
+### ReName the Mayo SNPS so the can be combined
+```{python ReNamerRosMap, echo=T, results='hide'}
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'ROSMAP_temp.bim'
+
+RS_Chr = {}
+RS_Pos = {}
+RS_BP ={}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_Chr[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[0]
+	RS_Pos[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[2]
+	RS_BP[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[3]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+OUT2 = open( 'FailedSNPS.txt', 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	LOC = ''.join([ lst[1], '_', lst[4], '_', lst[5] ])
+	chrm = RS_Chr.get( LOC, None )
+	pos = RS_Pos.get( LOC, None )
+	bp = RS_BP.get( LOC, None )
+
+	if( chrm == None ):
+	  print >>OUT, LINE
+	  print >>OUT2, lst[1]
+	else:
+	  Entry = '\t'.join([ chrm, lst[1], pos, bp, lst[4], lst[5] ])
+	  print >>OUT, Entry
+
+F1.close()
+OUT.close()
+OUT2.close()
 ```
@@
 ##Merge the Genotype Sets and Preform PCA
-```{bash MergeAndCall}
+```{bash MergeAndCall, cache = FALSE, echo=T, results='hide'}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+mv ROSMAP_tempRenamed.bim ROSMAP_temp.bim
+plink --threads $CORES --bfile ROSMAP_temp --silent --exclude FailedSNPS.txt --make-bed --allow-no-sex --out ROSMAP_Temp
+#rm ROSMAP_temp.*
+
+#Check ROSMAP SNP-Set
+##These numbers should be equal:
+grep 'rs' ROSMAP_Temp.bim | wc -l
+wc -l ROSMAP_Temp.bim
+
+##This Number should be zero:
+Repod=$(awk '{print $2}' ROSMAP_Temp.bim | grep "\." - | wc -l)
+
+if [ "$Repod" -eq "0" ]; then
+  plink --threads $CORES --bfile ROSMAP_Temp --silent --make-bed --allow-no-sex --out ROSMAP_Preliminary_Genos
+  rm ROSMAP_Temp.*
+fi
+if [ "$Repod" -ne "0" ]; then
+   echo $Repod" lines could've failed Translation"
+fi
+
+#Overly Cautious ID of common SNPs as the 1000G Data set is much smaller
+##Write & sort SNP List
+plink --threads $CORES --silent --bfile ROSMAP_Preliminary_Genos --write-snplist --out RosMap
+plink --threads $CORES --silent --bfile MSBB_Preliminary_Genos --write-snplist --out MSBB
+plink --threads $CORES --silent --bfile Mayo_Preliminary_Genos --write-snplist --out Mayo
+plink --threads $CORES --silent --bfile 1000Genomes_Merged --write-snplist --out 1000G
+
+cat MSBB.snplist | sort > MSBB.srt.snplist
+cat RosMap.snplist | sort > RosMap.srt.snplist
+cat Mayo.snplist | sort > Mayo.srt.snplist
+cat 1000G.snplist | sort > 1000G.srt.snplist
+
+#ID Common SNPS in all datasets
+comm -12 MSBB.srt.snplist 1000G.srt.snplist | comm -12 Mayo.srt.snplist - | comm -12 RosMap.srt.snplist - > All_CommonSNPs.snplist
+wc -l All_CommonSNPs.snplist
+
+##ID A/T C/G SNPS for removal (Not sure if I need to do this for the TWAS as well..)
+#Find and remove A/T C/G SNPS
+grep -P "A\tT$" 1000Genomes_Merged.bim | awk '{ print $2 }' - > remove.snplist
+grep -P "T\tA$" 1000Genomes_Merged.bim | awk '{ print $2 }' - >> remove.snplist
+grep -P "G\tC$" 1000Genomes_Merged.bim | awk '{ print $2 }' - >> remove.snplist
+grep -P "C\tG$" 1000Genomes_Merged.bim | awk '{ print $2 }' - >> remove.snplist
+wc -l remove.snplist
+
+echo "ROSMAP_Preliminary_Genos" > Merge.list
+echo "MSBB_Preliminary_Genos" >> Merge.list
+echo "Mayo_Preliminary_Genos" >> Merge.list
+
+plink --threads $CORES --bfile 1000Genomes_Merged --silent --merge-list Merge.list --allow-no-sex --exclude remove.snplist --extract All_CommonSNPs.snplist --make-bed --out Merged_GenoTypes
+
+cat Merged_GenoTypes-merge.missnp remove.snplist > Total_Remove.snplist
+wc -l Total_Remove.snplist
+
+##Try removing from all sets independently....
+plink --threads $CORES --bfile 1000Genomes_Merged --silent --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out 1000_4_Merge
+plink --threads $CORES --bfile ROSMAP_Preliminary_Genos --silent --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out ROSMAP_4_Merge
+plink --threads $CORES --bfile MSBB_Preliminary_Genos --silent --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out MSBB_4_Merge
+plink --threads $CORES --bfile Mayo_Preliminary_Genos --silent --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out Mayo_4_Merge
+
+echo "ROSMAP_4_Merge" > Merge.list
+echo "MSBB_4_Merge" >> Merge.list
+echo "Mayo_4_Merge" >> Merge.list
+
+plink --threads $CORES --bfile 1000_4_Merge --silent --merge-list Merge.list --allow-no-sex --maf 0.01 --mind 0.1 --geno 0.1 --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out Merged_GenoTypes
+rm *_Preliminary_Genos.*
+
+#PCA
+plink --bfile Merged_GenoTypes --silent --threads $CORES --maf 0.01 --mind 0.1 --max-maf 0.4 --indep-pairwise 50 5 0.2 --pca var-wts --out Total_PCA
+```
+
+## Prep Input for Cluster Based on Ancestry
+```{bash CLustPrep, cache = FALSE}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+wget http://www.compgen.pitt.edu/GemTools/GemTools.R
+
+plink --bfile Merged_GenoTypes --threads $CORES --geno 0.0000001 --maf 0.01 --mind 0.1 --hwe 0.00001 --max-maf 0.4  --indep-pairwise 50 5 0.2 --silent --recode12 --compound-genotypes --out AllSnps4GemClust
+
+#Re-Code in 0-1-2 Allele State
+cut -d" " -f7- AllSnps4GemClust.ped > peds.txt
+perl -pe 's/([^\s]+)\s+([^\s]+)/$1$2/g' peds.txt > PEDS.txt
+cut -d" " -f 1 AllSnps4GemClust.ped > FID.txt
+cut -d" " -f 2 AllSnps4GemClust.ped > IID.txt
+paste -d " " FID.txt IID.txt > Names.txt
+
+sed -i 's/22/2/g' PEDS.txt
+sed -i 's/00/3/g' PEDS.txt
+sed -i 's/12/1/g' PEDS.txt
+sed -i 's/11/0/g' PEDS.txt
+
+paste Names.txt PEDS.txt > GemClustAllGenos.txt
+sed -i 's/\t/ /g' GemClustAllGenos.txt
+sed -i 's/  */ /g' GemClustAllGenos.txt
+
+rm peds.txt
+rm Names.txt
+rm PEDS.txt
+AllSnps4GemClust.*
+```
+
+##Plot PCA -- Needs Work...
+```{r PlotPCA, cache = FALSE, echo=FALSE}
+library(ggplot2)
+library(plotrix)
+library(scater)
+library(data.table)
+source('GemTools.R')
+
+#Load Eigne Vals and Calc Percent Var for first 2 Comps.
+Comps <- as.vector(read.table(file="Total_PCA.eigenval"))
+PC1_Var_exp <- Comps[1,1]/sum(Comps[,1])
+PC2_Var_exp <- Comps[2,1]/sum(Comps[,1])
+
+#Load Populations
+CEU <- read.table(file = "1000G_RefSamps/CEU.samples.list", header =F, sep ="\t")
+row.names(CEU) <- paste0(CEU[,1], "_",CEU[,1] )
+YRI <- read.table(file = "1000G_RefSamps/YRI.samples.list", header =F, sep ="\t")
+row.names(YRI) <- paste0(YRI[,1], "_",YRI[,1] )
+CHB <- read.table(file = "1000G_RefSamps/CHB.samples.list", header =F, sep ="\t")
+row.names(CHB) <- paste0(CHB[,1], "_",CHB[,1] )
+JPT <- read.table(file = "1000G_RefSamps/JPT.samples.list", header =F, sep ="\t")
+row.names(JPT) <- paste0(JPT[,1], "_",JPT[,1] )
+
+ROSMAP <- read.table(file = "ROSMAP_4_Merge.fam", header =F, sep =" ")
+row.names(ROSMAP) <- paste0(ROSMAP[,1], "_",ROSMAP[,2] )
+MSBB <- read.table(file = "MSBB_4_Merge.fam", header =F, sep =" ")
+row.names(MSBB) <- paste0(MSBB[,1], "_",MSBB[,2] )
+Mayo <- read.table(file = "Mayo_4_Merge.fam", header =F, sep =" ")
+row.names(Mayo) <- paste0(Mayo[,1], "_",Mayo[,2] )
+Ref1000G <- read.table(file = "1000_4_Merge.fam", header =F, sep =" ")
+row.names(Ref1000G) <- paste0(Ref1000G[,1], "_",Ref1000G[,2] )
+
+pcs = read.table( file="Total_PCA.eigenvec")
+row.names(pcs) <- paste0(pcs$V1, "_", pcs$V2)
+pcs <- as.data.frame( pcs[,1:4] )
+colnames(pcs) <- c( "FID", "IID", "PC1", "PC2")
+
+RMs <- rep( "ROSMAP", length(row.names(ROSMAP)) )
+names(RMs) <- row.names(ROSMAP)
+MSBs = rep("MSBB", length(row.names(MSBB)) )
+names(MSBs) <- row.names(MSBB)     
+Mays <- rep( "MAYO", length(row.names(Mayo)) )
+names(Mays) <- row.names(Mayo)
+Gs = rep("1000G", length(row.names(Ref1000G)) )
+names(Gs) <- row.names(Ref1000G)
+
+CEUs <- rep( 'CEU', length(row.names(CEU)) )
+names(CEUs) <- row.names(CEU)
+YRIs <- rep( 'YRI', length(row.names(YRI)) )
+names(YRIs) <- row.names(YRI)
+CHBs <- rep( 'CHB', length(row.names(CHB)) )
+names(CHBs) <- row.names(CHB)
+JPTs <- rep( 'JPT', length(row.names(JPT)) )
+names(JPTs) <- row.names(JPT)
+
+SampleCohort <- c( RMs, MSBs, Mays, CEUs, YRIs, CHBs, JPTs)
+pcs$SampleCohort <- as.factor( SampleCohort[ row.names(pcs) ] )
+pcs$SampleCohort <- factor(pcs$SampleCohort, levels = c("MAYO", "MSBB", "ROSMAP", "YRI", "CHB", "CEU", "JPT"))
+
+SampleType <- c( RMs, MSBs, Mays, Gs )
+pcs$SampleType <- as.factor( SampleType[ row.names(pcs) ] )
+
+P <- ggplot(pcs, aes( PC1, PC2) ) + geom_point( aes(colour = SampleCohort, shape = SampleType), cex=.8, alpha = 4/10) 
+P <- P + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+P <- P + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" )) 
+P <- P + ggtitle("Ancestry PCA Analysis") + theme(plot.title = element_text(hjust = 0.5))
+P
+
+##Plot independent cohorts
+p = list()
+p[[1]] = ggplot(pcs[pcs$SampleCohort %in% c( 'CEU', 'JPT', 'CHB', 'YRI', 'MSBB' ),], aes( PC1, PC2) ) + geom_point( aes(colour = SampleCohort, shape = SampleType), cex=.8, alpha = 4/10)
+p[[1]] = p[[1]] + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+p[[1]] = p[[1]] + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+p[[1]] = p[[1]] + ggtitle("MSBB Ancestry PCA Analysis") + theme(plot.title = element_text(hjust = 0.5))
+
+p[[2]] = ggplot(pcs[pcs$SampleCohort %in% c( 'CEU', 'JPT', 'CHB', 'YRI', 'MAYO' ),], aes( PC1, PC2) ) + geom_point( aes(colour = SampleCohort, shape = SampleType), cex=.8, alpha = 4/10)
+p[[2]] = p[[2]] + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+p[[2]] = p[[2]] + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+p[[2]] = p[[2]] + ggtitle("Mayo Ancestry PCA Analysis") + theme(plot.title = element_text(hjust = 0.5))
+
+p[[3]] = ggplot(pcs[pcs$SampleCohort %in% c( 'CEU', 'JPT', 'CHB', 'YRI', 'ROSMAP' ),], aes( PC1, PC2) ) + geom_point( aes(colour = SampleCohort, shape = SampleType), cex=.8, alpha = 4/10)
+p[[3]] = p[[3]] + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+p[[3]] = p[[3]] + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+p[[3]] = p[[3]] + ggtitle("ROSMAP Ancestry PCA Analysis") + theme(plot.title = element_text(hjust = 0.5))
+#multiplot(plotlist = p, rows = 3)
+p[[1]]
+p[[2]]
+p[[3]]
+
+##Clustering All Samples 
+gnt <- as.matrix( fread("PEDS.txt", header = F, sep =" ") )
+id <- read.table("Names.txt", header = F, sep =" ")
+gnt[gnt <  0 | gnt > 2] = NA
+#293,239 SNPS
+
+ids <- paste0( id[,1], "_", id[,2] )
+row.names(gnt) <- ids
+#pcs_Clust = read.table( file="GemClustAllGenos.txt", sep=" ", header=F)
+
+#Only Consider Comps that explain > 1% of Variance
+Upper <- as.numeric(table(Comps[,1]/sum(Comps[,1])>0.01)["TRUE"])
+EC_foo.cluster = clusterGem(gnt = gnt, id = ids, min.dim = 3, max.dim = Upper)
+
+Refs <- pcs[ pcs$SampleType == '1000G', ]
+Refs$SampleCohort <- paste0( '1000G', '_', Refs$SampleCohort)
+CEU_Clusters <- c(names( table(EC_foo.cluster$clusters[ names(EC_foo.cluster$clusters) %in% names(CEUs) == T ]) ))
+pcs <- cbind( pcs, Cluster = EC_foo.cluster$clusters)
+
+pcs$Ancestry <- "NonCEU"
+pcs[ (pcs$Cluster %in% CEU_Clusters) == T,]$Ancestry <- "CEU"
+pcs[ row.names(Refs), ]$Ancestry <- Refs$SampleCohort
+
+P <- ggplot(pcs, aes( PC1, PC2) ) + geom_point( aes(colour = Cluster, shape = SampleType), cex=.8, alpha = 4/10) 
+P <- P + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+P <- P + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+P <- P + ggtitle("Ancestry Clustering Analysis") + theme(plot.title = element_text(hjust = 0.5))
+P
+
+mydf$task <- factor(mydf$task, levels = c("up", "down", "left", "right", "front", "back"))
+P <- ggplot(pcs, aes( PC1, PC2) ) + geom_point( aes(colour = Ancestry, shape = SampleType), cex=.8, alpha = 4/10) 
+P <- P + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+P <- P + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+P <- P + ggtitle("Ancestry Cluster Analysis CEU vs NonCEU") + theme(plot.title = element_text(hjust = 0.5))
+P
+
+CEUs <- pcs[ ( pcs$Ancestry %in% c('CEU', "1000G_CEU", "1000G_CHB", "1000G_YRI", "1000G_JPT") ) == T, ]
+P <- ggplot(CEUs, aes( PC1, PC2) ) + geom_point( aes(colour = Ancestry, shape = SampleType), cex=.8, alpha = 4/10)
+P <- P + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+P <- P + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+P <- P + ggtitle("Ancestry Cluster Analysis CEU") + theme(plot.title = element_text(hjust = 0.5))
+P
+
+CEUs <- pcs[ ( pcs$Ancestry %in% c('CEU', "1000G_CEU") ) == T, ]
+P <- ggplot(CEUs, aes( PC1, PC2) ) + geom_point( aes(colour = Ancestry, shape = SampleType), cex=.8, alpha = 4/10)
+P <- P + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+P <- P + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+P <- P + ggtitle("Ancestry Analysis: CEU Clustered Samples") + theme(plot.title = element_text(hjust = 0.5))
+P
+#Write INDV to Keep to a File:
+write.table( file = "CEU_AncestryClustered_INDVs.tsv", CEUs[ CEUs$Ancestry == 'CEU', c(1,2) ], col.names = F, row.names = F, quote = F, sep = "\t")
+```
+
+## Filter Genotypes for CEU Ancestry 
+```{bash FIlterAncestry, cache=FALSE, echo=TRUE, results='hide'}
+source /root/.bashrc
+PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+plink --threads $CORES --bfile Merged_GenoTypes --keep CEU_AncestryClustered_INDVs.tsv --make-bed --out CEU_AncestryMatched_Genotypes
+```
+
+```{r synapse.parameters, include=FALSE, cache=TRUE}
+parentId = 'syn20798011';
+activityName = 'Ancestry Analysis';
+activityDescription = 'Processing and Analysis of WGS and Genotype data along with ancestry analysis with 1000 genome\'s CEU, CHB, YRI, and JPT populations';
+thisFileName <- 'Ancestry_PCA.Rmd'
+# Github link
+thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+```
+
+```{r Store, cache = FALSE, echo=FALSE, results='hide'}
+parentId = 'syn20798011';
+activityName = 'Ancestry Analysis';
+activityDescription = 'Processing and Analysis of WGS and Genotype data along with ancestry analysis with 1000 genome\'s CEU, CHB, YRI, and JPT populations';
+
+# Code WTF is this??
+CODE <- Folder(name = "Ancestry_Analysis", parentId = parentId)
+CODE <- synStore(CODE)
+
+#Set Used SynIDs For Provenance
+Syns_Used <- c("syn11707204", "syn8650955", "syn5879161", "syn5879456", "syn5879461", 
+               "syn5879463", "syn5879470", "syn5879472", "syn5879473", "syn5879559", 
+               "syn5879628", "syn5879677", "syn5879748", "syn5879792","syn5879812", 
+               "syn5879827", "syn5879828", "syn5879830", "syn5879832", "syn5879834", 
+               "syn5879835", "syn5879836", "syn5879837", "syn5879838", "syn20809809")
+
+# Set annotations
+all.annotations = list(
+  dataType = 'GWAS',
+  dataSubType = 'DNAVars',
+  summaryLevel = 'SNP',
+  assay	 = c('Genotype Array', "WGS"),
+  tissueTypeAbrv	= c('TCX', "FP", 'IFG', 'PHG', 'STG', 'DLPFC', 'CBE'), 
+  study = c('MAYO', 'ROSMAP', 'MSBB'), 
+  organism = 'HomoSapiens',
+  consortium	= 'AMPAD',
+  normalizationStatus	= TRUE,
+  normalizationType	= '',
+  rnaquantification = '',
+  genomeAssemblyID = 'GRCh37'
+)
+
+#STORE
+#CEU Indvs
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryClustered_INDVs.tsv', sep = '\t', quote=F)
+ENRICH_OBJ = File('CEU_AncestryClustered_INDVs.tsv', 
+                  name = 'Samples Clustered to CEU Ancestry', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'CEU_INDV'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+#PCA EginVecs
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenvec', sep = '\t', quote=F)
+ENRICH_OBJ = File('Total_PCA.eigenvec', 
+                  name = 'PCA Eigen Vectors', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'EigenVecs'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+#PCA EginVecs
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenval', sep = '\t', quote=F)
+ENRICH_OBJ = File('Total_PCA.eigenval', 
+                  name = 'PCA Eigen Values', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'EigenValues'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+###Store Genos Seperatly 
+CODE <- Folder(name = "Ancestry_Clustered_Genotypes", parentId = parentId)
+CODE <- synStore(CODE)
+
+#Geno Bed
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bed', sep = '\t', quote=F)
+ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.bed', 
+                  name = 'Genotype Bed File', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'GWAS'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+#Geno Bim
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bim', sep = '\t', quote=F)
+ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.bim', 
+                  name = 'Genotype Bim File', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'GWAS'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+#Geno Fam
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.fam', sep = '\t', quote=F)
+ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.fam', 
+                  name = 'Genotype Fam File', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'GWAS'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+#Geno nosex
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.nosex', sep = '\t', quote=F)
+ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.nosex', 
+                  name = 'Genotype nosex File', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'GWAS'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+#Geno nosex
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.log', sep = '\t', quote=F)
+ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.log', 
+                  name = 'Genotype log File', 
+                  parentId = CODE$properties$id)
+ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
+                      executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'GWAS'
+synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+```
+### R Source Code
+[Github](`r thisFile`)
+
+```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
+library(synapser)
+library(knit2synapse) 
+#install.packages("reticulate")
+library(reticulate)
+
+# get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
+synLogin()
+knit2synapse::createAndKnitToFolderEntity(file = "Ancestry_PCA.Rmd",
+                                          parentId ="syn20798011",
+                                          folderName = 'Ancestry_Analysis')
 

### 2019-09-27 code/Ancestry_PCA.Rmd
Break Out Python

@@
 knitr::opts_chunk$set(
+  #python.reticulate=FALSE,
   echo=FALSE,
@@
   results='hide')
-library(reticulate)
 ```
@@
 chown -hR <GID>:<USR> /home/<USR>/TWAS/
+maybe# ln -s /usr/bin/python /usr/local/bin/python
 
@@
 ```
+
 ## Pull 1000Genomes down and process
 * Pull out reference populations (CEU, YRI, CHB, JPT)
-```{bash pull_1000Genomes, echo=T, results='hide', cache = FALSE, echo=FALSE}
+```{bash pull_1000Genomes, echo=T, results='hide', cache = FALSE}
 source /root/.bashrc
@@
   plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --silent --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
-  rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
+  #rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
 done
-rm -r VCF/
+#rm -r VCF/
 
@@
 #rm -r GWAS_Plink/
-rm MergedGWAS.txt
+#rm MergedGWAS.txt
 
@@
 ### ReName the MSBB SNPS so the can be combined
-```{python ReNamer, echo=T, results='hide'}
-import sys
-import os
-import re
-
-InFile = 'TotalLDRef.bim'
-InFileb = 'GWASTotal.bim' #LDREF_FiltSNPs.bim
-
-RS_IDs = {}
-RS_Pos = {}
-
-F1 = open(InFile)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
-	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
-F1.close()
-
-#Open Output
-OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
-
-F1 = open(InFileb)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
-	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
-
-	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
-	print >>OUT, Entry
-
-F1.close()
-OUT.close()
+```{r ReNamer_ONE, echo=F, results='hide'}
+system("python Python/First_Rename.py")
 ```
@@
 if [ "$Repod" -eq "0" ]; then
-   mv GWASTotalRenamed.bim GWASTotal.bim;
+   cp GWASTotalRenamed.bim GWASTotal.bim;
 fi
@@
 plink --bfile GWASTotal --silent --threads $CORES --make-bed --out MSBB_Preliminary_Genos
-rm GWASTotal.*
+#rm GWASTotal.*
 ```
@@
 ### ReName the Mayo SNPS so the can be combined
-```{python ReNamerMayo, echo=T, results='hide'}
-import sys
-import os
-import re
-
-InFile = 'TotalLDRef.bim'
-InFileb = 'Mayo_LDREF_Filt.bim'
-
-RS_IDs = {}
-RS_Pos = {}
-
-F1 = open(InFile)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
-	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
-F1.close()
-
-#Open Output
-OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
-
-F1 = open(InFileb)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
-	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
-
-	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
-	print >>OUT, Entry
-
-F1.close()
-OUT.close()
+```{r ReNamer_Two_Mayo, echo=T, results='hide'}
+system("python Python/Second_Rename.py")
 ```
@@
 ### ReName the Mayo SNPS so the can be combined
-```{python ReNamerRosMap, echo=T, results='hide'}
-import sys
-import os
-import re
-
-InFile = 'TotalLDRef.bim'
-InFileb = 'ROSMAP_temp.bim'
-
-RS_Chr = {}
-RS_Pos = {}
-RS_BP ={}
-
-F1 = open(InFile)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	RS_Chr[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[0]
-	RS_Pos[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[2]
-	RS_BP[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[3]
-F1.close()
-
-#Open Output
-OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
-OUT2 = open( 'FailedSNPS.txt', 'w' )
-
-F1 = open(InFileb)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-	LOC = ''.join([ lst[1], '_', lst[4], '_', lst[5] ])
-	chrm = RS_Chr.get( LOC, None )
-	pos = RS_Pos.get( LOC, None )
-	bp = RS_BP.get( LOC, None )
-
-	if( chrm == None ):
-	  print >>OUT, LINE
-	  print >>OUT2, lst[1]
-	else:
-	  Entry = '\t'.join([ chrm, lst[1], pos, bp, lst[4], lst[5] ])
-	  print >>OUT, Entry
-
-F1.close()
-OUT.close()
-OUT2.close()
+```{r ReNamer_Three_Rosmap, echo=T, results='hide'}
+system("python Python/Third_Rename.py")
 ```
@@
 rm peds.txt
-rm Names.txt
-rm PEDS.txt
 AllSnps4GemClust.*
@@
 
-##Plot PCA -- Needs Work...
+##Plot PCA
 ```{r PlotPCA, cache = FALSE, echo=FALSE}
@@
 
-mydf$task <- factor(mydf$task, levels = c("up", "down", "left", "right", "front", "back"))
+#mydf$task <- factor(mydf$task, levels = c("up", "down", "left", "right", "front", "back"))
 P <- ggplot(pcs, aes( PC1, PC2) ) + geom_point( aes(colour = Ancestry, shape = SampleType), cex=.8, alpha = 4/10) 
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn20798011';
+library(githubr)
+parentId = 'syn18936948';
 activityName = 'Ancestry Analysis';
@@
 
-```{r Store, cache = FALSE, echo=FALSE, results='hide'}
-parentId = 'syn20798011';
+```{r Store, cache = FALSE, echo=FALSE, results='hide', eval=FALSE}
+parentId = 'syn18936948';
 activityName = 'Ancestry Analysis';
@@
 #CEU Indvs
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryClustered_INDVs.tsv', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryClustered_INDVs.tsv', sep = '\t', quote=F)
 ENRICH_OBJ = File('CEU_AncestryClustered_INDVs.tsv', 
@@
 #PCA EginVecs
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenvec', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenvec', sep = '\t', quote=F)
 ENRICH_OBJ = File('Total_PCA.eigenvec', 
@@
 #PCA EginVecs
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenval', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenval', sep = '\t', quote=F)
 ENRICH_OBJ = File('Total_PCA.eigenval', 
@@
 #Geno Bed
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bed', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bed', sep = '\t', quote=F)
 ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.bed', 
@@
 #Geno Bim
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bim', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bim', sep = '\t', quote=F)
 ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.bim', 
@@
 #Geno Fam
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.fam', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.fam', sep = '\t', quote=F)
 ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.fam', 
@@
 #Geno nosex
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.nosex', sep = '\t', quote=F)
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.nosex', sep = '\t', quote=F)
 ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.nosex', 
@@
 
-#Geno nosex
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.log', sep = '\t', quote=F)
+#Geno log
+#write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.log', sep = '\t', quote=F)
 ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.log', 
@@
 library(knit2synapse)
-#install.packages("reticulate")
-library(reticulate)
 
-# get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
 synLogin()
 knit2synapse::createAndKnitToFolderEntity(file = "Ancestry_PCA.Rmd",
-                                          parentId ="syn20798011",
+                                          parentId ="syn18936948",
                                           folderName = 'Ancestry_Analysis')

### 2019-09-27 code/Python/First_Rename.py

@@ -1,0 +1,35 @@
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'GWASTotal.bim' #LDREF_FiltSNPs.bim
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
+
+	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
+	print >>OUT, Entry
+
+F1.close()
+OUT.close()

### 2019-09-27 code/Python/Second_Rename.py

@@ -1,0 +1,36 @@
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'Mayo_LDREF_Filt.bim'
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
+
+	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
+	print >>OUT, Entry
+
+F1.close()
+OUT.close()

### 2019-09-27 code/Python/Third_Rename.py

@@ -1,0 +1,44 @@
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'ROSMAP_temp.bim'
+
+RS_Chr = {}
+RS_Pos = {}
+RS_BP ={}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_Chr[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[0]
+	RS_Pos[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[2]
+	RS_BP[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[3]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+OUT2 = open( 'FailedSNPS.txt', 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	LOC = ''.join([ lst[1], '_', lst[4], '_', lst[5] ])
+	chrm = RS_Chr.get( LOC, None )
+	pos = RS_Pos.get( LOC, None )
+	bp = RS_BP.get( LOC, None )
+
+	if( chrm == None ):
+	  print >>OUT, LINE
+	  print >>OUT2, lst[1]
+	else:
+	  Entry = '\t'.join([ chrm, lst[1], pos, bp, lst[4], lst[5] ])
+	  print >>OUT, Entry
+
+F1.close()
+OUT.close()
+OUT2.close()

### 2019-10-02 code/Ancestry_PCA.Rmd
Update the SynapseClient Nonsens

@@
 ### ReName the MSBB SNPS so the can be combined
-```{r ReNamer_ONE, echo=F, results='hide'}
-system("python Python/First_Rename.py")
+```{python ReNamer_ONE, echo=F, results='hide'}
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'GWASTotal.bim' #LDREF_FiltSNPs.bim
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
+
+	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
+	print >>OUT, Entry
+
+F1.close()
+OUT.close()
 ```
@@
 ### ReName the Mayo SNPS so the can be combined
-```{r ReNamer_Two_Mayo, echo=T, results='hide'}
-system("python Python/Second_Rename.py")
+```{python ReNamer_Two_Mayo, echo=T, results='hide'}
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'Mayo_LDREF_Filt.bim'
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
+
+	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
+	print >>OUT, Entry
+
+F1.close()
+OUT.close()
 ```
@@
 ### ReName the Mayo SNPS so the can be combined
-```{r ReNamer_Three_Rosmap, echo=T, results='hide'}
-system("python Python/Third_Rename.py")
+```{python ReNamer_Three_Rosmap, echo=T, results='hide'}
+import sys
+import os
+import re
+
+InFile = 'TotalLDRef.bim'
+InFileb = 'ROSMAP_temp.bim'
+
+RS_Chr = {}
+RS_Pos = {}
+RS_BP ={}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+
+	RS_Chr[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[0]
+	RS_Pos[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[2]
+	RS_BP[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[3]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+OUT2 = open( 'FailedSNPS.txt', 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	LOC = ''.join([ lst[1], '_', lst[4], '_', lst[5] ])
+	chrm = RS_Chr.get( LOC, None )
+	pos = RS_Pos.get( LOC, None )
+	bp = RS_BP.get( LOC, None )
+
+	if( chrm == None ):
+	  print >>OUT, LINE
+	  print >>OUT2, lst[1]
+	else:
+	  Entry = '\t'.join([ chrm, lst[1], pos, bp, lst[4], lst[5] ])
+	  print >>OUT, Entry
+
+F1.close()
+OUT.close()
+OUT2.close()
 ```
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapser)
+#library(synapser)
 library(knit2synapse)
@@
 synLogin()
-knit2synapse::createAndKnitToFolderEntity(file = "Ancestry_PCA.Rmd",
-                                          parentId ="syn18936948",
-                                          folderName = 'Ancestry_Analysis')
+#knit2synapse::createAndKnitToFolderEntity(file = "Ancestry_PCA.Rmd",
+#                                          parentId ="syn18936948",
+#                                          folderName = 'Ancestry_Analysis')
 

### 2019-10-02 code/ProcessData.Rmd
Update the SynapseClient Nonsens

---
title: "Process RNA-Seq and Genotype Data for TWAS"
author: "JKG"
date: "9/25/2019"
output: pdf_document
  chunk_output_type: console
---

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')
#library(reticulate)
```
##Before running 
Run the following in docker exec -it <CONTAINER> /bin/bash 
chmod 777 /root
mv TWAS/ /home/<USR>/TWAS/
chown -hR <GID>:<USR> /home/<USR>/TWAS/

## Login to Synapse Will need to replace with your credentials
```{bash Login, echo=T, results='hide', eval=FALSE}
source /root/.bashrc
synapse login -u <USR> -p <PSWD> --rememberMe

#Alternativly you can setup a credentials file as such:
touch ~/.synapseConfig
echo "[authentication]" >> ~/.synapseConfig
echo "username = <USR>" >> ~/.synapseConfig
echo "password = <PASWD>" >> ~/.synapseConfig
```

## MSBB RNA-Seq: Average Across Brain Regions, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
```{r MSBBRNA, echo=F, results='hide', cache = FALSE}
library(data.table)

Process_MSBB <- function( dna, exp, id){
  #'@dna synID of Geno samples eg 'syn11384608'
  #'@exp synID of expression data eg 'syn8485026'
  #'@id synID of id translators  eg. 'syn6100548'
  #dna<-'syn11384608'
  #exp<-'syn8485026'
  #id<-'syn6100548'

  DNA <- fread(synGet(dna)$path)
  Expression <- read.table(synGet(exp)$path, header=T)
  IDs <- fread(synGet(id)$path)
  IDs <- IDs[ grepl( 'accepted_hits.sort.coord.bam', IDs$fileName ) == T, ]
  IDs <- IDs[ (IDs$sampleIdentifier %in% colnames(Expression)) == T, ]

  INDVs <- IDs$individualIdentifier[ !duplicated(IDs$individualIdentifier) ]

  if( 'ensembl_gene_id' %in% colnames(Expression) ){
    Averaged <- as.data.frame( Expression$ensembl_gene_id )
  }else{
    Averaged <- as.data.frame( row.names(Expression) )
    colnames(Averaged) <- 'ensembl_gene_id'
  }

  Ave <- function( ID, DF, Exp ){
    #'@ID Sample ID eg. 'AMPAD_MSSM_0000007155'
    #'@DF the target dataframe eg. 'IDs'
    #'@Exp the expression set to filter eg Expression

    Exp <- as.data.frame( Exp )
    COLS <- DF[ DF$individualIdentifier == ID, ]$sampleIdentifier
    Small <- Exp[ , COLS ]

    if( dim(as.matrix(Small))[2] > 1 ){
      eval(parse( text = paste0( 'return( ', ID, ' = rowMeans(Small) )')))
    }else{
      eval(parse( text = paste0( 'return( ', ID, ' = Small)')))
    }
  }

  for( i in INDVs ){
    eval(parse( text = paste0( 'Averaged$', i, ' <- Ave(i, IDs, Expression )') ))
  }

  GWAS_ID <- as.data.frame( DNA[ (DNA$individualIdentifier %in% colnames(Averaged)) == T , ] )
  row.names(GWAS_ID) <- GWAS_ID$individualIdentifier
  if( 'ensembl_gene_id' %in% colnames(Averaged) ){
    Averaged <- Averaged[ , c( 'ensembl_gene_id', row.names(GWAS_ID) )]
  }else{
    Averaged <- Averaged[ , c( 'Expression$ensembl_gene_id', row.names(GWAS_ID) )]
    colnames(Averaged[1]) <- 'ensembl_gene_id'
  }
  colnames(Averaged) <- paste0(GWAS_ID[ colnames(Averaged), ]$sampleIdentifier, "_", GWAS_ID[ colnames(Averaged), ]$sampleIdentifier)
  colnames(Averaged)[1] <- "ensembl_gene_id"
  return( Averaged )
}

Norm_Resid_MSBB <- Process_MSBB('syn11384608', 'syn8485026', 'syn6100548')
dCorrect_Resid_MSBB <- Process_MSBB('syn11384608', 'syn20801798', 'syn6100548')
```

## Mayo RNA-Seq: Remove Cerebellum, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
```{r MayoRNA, echo=T, results='hide', cache = FALSE, echo=FALSE}
#Get Geno Names From FAM File
FAM <- as.data.frame(fread( synGet('syn20820122')$path))
FAM <- FAM[ (grepl('ROS', FAM[,1])) == F , ]
FAM <- FAM[ (grepl('MAP', FAM[,1])) == F , ]
FAM <- FAM[ (grepl('ROS', FAM[,2])) == F , ]
FAM <- FAM[ (grepl('MAP', FAM[,2])) == F , ]
FAM <- FAM[ FAM[,1] == 0, ]

#Filter Expression Samples by Presence of a Genotype
Mayo_filt <- function( syn, fam, Type ){
  #'@syn A synID for the RNA Seq eg. 'syn20801999' or 'syn20801991'
  #'@fam A fam file eg. FAM
  #'@Type fread = 0 read.table=1

  fam <- FAM
  if( Type == 0){
    RNA <- read.table( synGet(syn)$path)
    colnames(RNA) <- gsub('_TCX', '_a', colnames(RNA))
    colnames(RNA) <- gsub('X', '', colnames(RNA))
    colnames(RNA) <- gsub('_a', '_TCX', colnames(RNA))
    RNA <- cbind( 'ensembl_gene_id' = row.names(RNA), RNA[,colnames(RNA)] )
  }else{
    RNA <- as.data.frame( fread( synGet(syn)$path ) )
  }
  RNA <- RNA[ , c('ensembl_gene_id', colnames(RNA)[(grepl('_TCX', colnames(RNA))==T)]) ]
  colnames( RNA ) <- gsub( '_TCX', '', colnames( RNA ) )
  colnames( RNA )[2:length(colnames( RNA ))] <- paste0( '0_', colnames( RNA )[2:length(colnames( RNA ))] )

  RNA <- RNA[ , c( "ensembl_gene_id", colnames(RNA)[ (colnames(RNA) %in% paste0( FAM[,1], "_", FAM[,2] )) == T ]) ]
  return(RNA)
}

Norm_Resid_MAYO <- Mayo_filt( 'syn8466825', FAM, 1 )
dCorrect_Resid_MAYO <- Mayo_filt( 'syn20801991', FAM, 0 )
```

## ROSMAP RNA-Seq: Filter for INDV. w/Genotype Data and Rename Samples with Genotype ID 
```{r ROSMAPoRNA, echo=T, results='hide', cache = FALSE, echo=FALSE}
#SVA: 'syn8456704'
#SVA+Diag: 'syn20800652'
Ros_Filt <- function(Exp, name, Trans, Fam, Var){
  #'@Exp the expression matrix eg. 'syn8456704'
  #'@name another name file eg. 'syn5879839'
  #'@Trans 'syn3382527'
  #'@Fam a .fam file of the ROS samps syn20820122
  #'@Var 1=Nondiagnosis correcte 0=Diagnosis Corrected

  # eg. Ros_Filt( 'syn8456704', 'syn5879839', 'syn3382527','syn20820122')

  FAM <- as.data.frame(fread( synGet(Fam)$path))
  Fam <- FAM[ (grepl('ROS', FAM[,1])) == T | (grepl('MAP', FAM[,1])) == T | (grepl('ROS', FAM[,2])) == T | (grepl('MAP', FAM[,2])) == T, ]
  InvFam <- FAM[ (grepl('ROS', FAM[,1])) == F & (grepl('MAP', FAM[,1])) == F & (grepl('ROS', FAM[,2])) == F & (grepl('MAP', FAM[,2])) == F, ]
  Fam[,1] <- Fam[,2]

  #Need to assign sex to MSBB and Mayo
  NAMED_FAM <- rbind( InvFam[1:dim(InvFam)[1], ],  Fam[1:dim(Fam)[1], ] )

  if(Var == 1){
    Exp <- as.data.frame( fread(synGet(Exp)$path) )
  }else{
    if(Var == 0){
        Exp <- as.data.frame( read.table(synGet('syn20800652')$path) )
        colnames(Exp) <- gsub('X','', colnames(Exp))
        Exp <- cbind(row.names(Exp), Exp[1:dim(Exp)[2]])
        colnames(Exp)[1] <- 'ensembl_gene_id'
    }else{}
  }
  Trans <- fread(synGet(Trans)$path)
  Trans <- Trans[ Trans$gwas_id != "", ]
  names <- as.data.frame(fread(synGet(name)$path))
  Trans <- Trans[ (Trans$gwas_id  %in%  names[,2]) == T, ]
  Trans <- Trans[ (Trans$rnaseq_id == "") == F, ]
  Trans <- Trans[ !duplicated(Trans$rnaseq_id), ]

  #Filter for matched RNA-Seq and GWAS samples
  Exp <- Exp[ ,c('ensembl_gene_id', colnames(Exp)[ (colnames(Exp) %in% Trans$rnaseq_id) == T]) ]
  Trans <- as.data.frame( Trans[ (Trans$rnaseq_id %in% colnames(Exp)) == T,  ] )
  row.names(Trans) <- Trans$rnaseq_id

  colnames(Exp) <- c('ensembl_gene_id', paste0( Trans[colnames(Exp)[2:length(colnames(Exp))],]$gwas_id, "_",  Trans[colnames(Exp)[2:length(colnames(Exp))],]$gwas_id))
  return(Exp)
}

Norm_Resid_RM <-Ros_Filt( 'syn8456704', 'syn5879839', 'syn3382527','syn20820122', 1)
dNorm_Resid_RM <-Ros_Filt( 'syn20800652', 'syn5879839', 'syn3382527','syn20820122', 0)
```

## Merge RNA-Seq: Merge and Annotate RNA-Seq
* Remove genes on Chr X, Chr Y, Chr M 
* Check for no Patch Contig Nonsense
* Print Sample ID List
* Filter Genotypes for RNA Samples
```{r Merge RNASeq, echo=T, results='hide', cache = FALSE, echo=FALSE}
#Common Genes:
GNames <- names( table(c( as.character(Norm_Resid_MSBB$ensembl_gene_id), as.character(Norm_Resid_MAYO$ensembl_gene_id), as.character(Norm_Resid_RM$ensembl_gene_id)  ))[ table(c( as.character(Norm_Resid_MSBB$ensembl_gene_id), as.character(Norm_Resid_MAYO$ensembl_gene_id), as.character(Norm_Resid_RM$ensembl_gene_id)  )) == 3] )

#Combine Into One DataFrame
Comb <- function( MSBB, Mayo, RM, Names){
  #MSBB <- Norm_Resid_MSBB
  #Mayo <- Norm_Resid_MAYO
  #RM <- Norm_Resid_RM
  #Names <- GNames

  row.names(MSBB) <- as.character(MSBB$ensembl_gene_id)
  row.names(Mayo) <- as.character(Mayo$ensembl_gene_id)
  row.names(RM) <- as.character(RM$ensembl_gene_id)

  MSBB <- MSBB[ GNames ,2:dim(MSBB)[2] ]
  Mayo <- Mayo[ GNames ,2:dim(Mayo)[2] ]
  RM <- RM[ GNames ,2:dim(RM)[2] ]

  Out <- cbind( MSBB[GNames,][ ,1:dim(MSBB)[2] ],
                Mayo[GNames, ][ ,1:dim(Mayo)[2] ],
                RM[GNames, ][, 1:dim(RM)[2] ]
  )

  return( Out )
}

Norm_Resid <- Comb( Norm_Resid_MSBB, Norm_Resid_MAYO, Norm_Resid_RM, GNames )
Diag_Resid <- Comb( dCorrect_Resid_MSBB,  dCorrect_Resid_MAYO, dNorm_Resid_RM, GNames )

#Annotate for TWAS
hg19 <- as.data.frame(fread(synGet('syn20826610')$path))
hg19 <- hg19[ hg19[,1] %in% row.names( Norm_Resid ), ]
row.names(hg19) <- hg19[,1]

#Filter out the 231 Genes that don't have coherent annotations between GRCH38 and GRCH 37
Norm_Resid <- Norm_Resid[ (row.names(Norm_Resid) %in% row.names(hg19)) == T, ]
Diag_Resid <- Diag_Resid[ (row.names(Diag_Resid) %in% row.names(hg19)) == T, ]

#Finalize
Norm_Resid <- as.data.frame( cbind( 
               TargetID = row.names(Norm_Resid), 
               Gene_Symbol = row.names(Norm_Resid),
               Chr = hg19[row.names(Norm_Resid), ][,2] , 
               Coord = hg19[ row.names(Norm_Resid), ][,3],
               Norm_Resid[ ,1:dim(Norm_Resid)[2]
             ]) )

Diag_Resid <- as.data.frame(cbind( 
               TargetID = row.names(Diag_Resid), 
               Gene_Symbol = row.names(Diag_Resid),
               Chr = hg19[row.names(Diag_Resid), ][,2] , 
               Coord = hg19[ row.names(Diag_Resid), ][,3],
               Diag_Resid[ ,1:dim(Diag_Resid)[2]
             ]) )

#Filter out the ~ 480 ChrX genes
Norm_Resid <- Norm_Resid[ (Norm_Resid$Chr %in% 'X') == F, ]
Diag_Resid <- Diag_Resid[ (Diag_Resid$Chr %in% 'X') == F, ]

#Order:
Norm_Resid <- Norm_Resid[ with(Norm_Resid, order( Chr, Coord)), ]
Diag_Resid <- Diag_Resid[ with(Diag_Resid, order( Chr, Coord)), ]
write.table(Norm_Resid, file="ALL_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
write.table(Diag_Resid, file="ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)

#Filter for CEU Ancestry Matched Training Cohort
CEU_Samps <- do.call( rbind, strsplit( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))],  "_" ))
write.table(CEU_Samps, file="ALL_CEU_SamplesToTrain.tsv", col.names =F, row.names=F, sep="\t", quote=F)

#Output the ROSMAP INDV CEU Matched Training Cohort
ROS <- colnames(Norm_Resid)[ grepl('ROS', colnames(Norm_Resid)) == T | grepl('MAP', colnames(Norm_Resid)) == T ]
ROS_Norm_Resid <- Norm_Resid[ ,c("TargetID", "Gene_Symbol", "Chr", "Coord", ROS) ]
ROS_Diag_Resid <- Diag_Resid[ ,c("TargetID", "Gene_Symbol", "Chr", "Coord", ROS) ]

write.table(ROS_Norm_Resid, file="ROS_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
write.table(ROS_Diag_Resid, file="ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)

ROS_Samps <- do.call( rbind, strsplit( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],  "_" ))
write.table(ROS_Samps, file="ROS_CEU_SamplesToTrain.tsv", col.names =F, row.names=F, sep="\t", quote=F)
```

## Fix FamFile
```{r FamFix, cache=TRUE}
FAM <- as.data.frame(fread( synGet(Fam)$path))

```

## Push Results to Synapse
```{r synapse.parameters, include=FALSE, cache=TRUE}

FAM <- as.data.frame(fread( synGet('syn20820122')$path))
MSBB <-  as.data.frame(fread( synGet('syn11384608')$path))
ROSMAP <- as.data.frame(fread( synGet('syn3191087')$path))
row.names(ROSMAP) <- ROSMAP$projid
ROSMAP_ID <- as.data.frame(fread( synGet('syn3382527')$path))
#mayo <- as.data.frame(fread( synGet('syn3817650')$path))
#MAYO <- as.data.frame(fread( synGet('syn10648406')$path))
MAYO <- as.data.frame(fread( synGet('syn19164046')$path))
mayo <- as.data.frame(fread( synGet('syn19164050')$path))

#MSBB 
row.names(MSBB) <- MSBB$sampleIdentifier
name <- FAM[ FAM$V2 %in% row.names(MSBB) == T, ]$V2
MSBB <- MSBB[name,]

Sex<-c(1,2)
names(Sex) <- c('M', 'F')
MSBB$SEX.inferred <- Sex[MSBB$SEX.inferred]
row.names(FAM)<-FAM$V2
FAM[ row.names(MSBB), ]$V5 <- MSBB$SEX.inferred

#Mayo --Needs Work
mayo <- mayo[complete.cases(mayo$Gender),]
MAYO <- MAYO[complete.cases(MAYO$Sex),]

NewMayo <- as.data.frame( rbind( cbind( MAYO$SampleID,MAYO$Sex), cbind( mayo$SampleID,mayo$Gender)) )
NewMayo<- NewMayo[!duplicated(NewMayo),]
NewMayo <- as.data.frame( cbind( as.character(NewMayo$V1),as.character(NewMayo$V2), gsub("_CER","",gsub("_TCX","",NewMayo$V1))) )
NewMayo$V2 <- Sex[as.character( NewMayo$V2 )]

names <- FAM[ FAM$V1 == 0 ,]$V2
#table(names %in% NewMayo$V3)

NewMayo <- NewMayo[ !duplicated(NewMayo$V3), ]
row.names(NewMayo) <- NewMayo$V3
NewMayo <- NewMayo[ names, ]

FAM[ names ,]$V5 <- NewMayo[ names, ]$V2
FAM$V5[is.na(FAM$V5)] <- 0
##Missing Sex
#1950 excluded from RNA-Sequncing - Pathology not meeting control criteria (BRAAK>3.0)
#1957 excluded from RNA-Sequncing - Pathology not meeting control criteria (BRAAK>3.0)

```

##Knit to Synapse
```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
library(synapser)
library(knit2synapse)

synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "",
                                          parentId ="",
                                          folderName = '')
```

### 2019-10-02 code/Python/First_Rename.py

@@ -1,35 +1,0 @@
-import sys
-import os
-import re
-
-InFile = 'TotalLDRef.bim'
-InFileb = 'GWASTotal.bim' #LDREF_FiltSNPs.bim
-
-RS_IDs = {}
-RS_Pos = {}
-
-F1 = open(InFile)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
-	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
-F1.close()
-
-#Open Output
-OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
-
-F1 = open(InFileb)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
-	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
-
-	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
-	print >>OUT, Entry
-
-F1.close()
-OUT.close()

### 2019-10-02 code/Python/Second_Rename.py

@@ -1,36 +1,0 @@
-import sys
-import os
-import re
-
-InFile = 'TotalLDRef.bim'
-InFileb = 'Mayo_LDREF_Filt.bim'
-
-RS_IDs = {}
-RS_Pos = {}
-
-F1 = open(InFile)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
-	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
-F1.close()
-
-
-#Open Output
-OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
-
-F1 = open(InFileb)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
-	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]
-
-	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
-	print >>OUT, Entry
-
-F1.close()
-OUT.close()

### 2019-10-02 code/Python/Third_Rename.py

@@ -1,44 +1,0 @@
-import sys
-import os
-import re
-
-InFile = 'TotalLDRef.bim'
-InFileb = 'ROSMAP_temp.bim'
-
-RS_Chr = {}
-RS_Pos = {}
-RS_BP ={}
-
-F1 = open(InFile)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-
-	RS_Chr[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[0]
-	RS_Pos[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[2]
-	RS_BP[ ''.join([lst[1], '_', lst[4], '_', lst[5]]) ] = lst[3]
-F1.close()
-
-#Open Output
-OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
-OUT2 = open( 'FailedSNPS.txt', 'w' )
-
-F1 = open(InFileb)
-for line in F1:
-	LINE = line.rstrip('\r\n')
-	lst = LINE.split('\t')
-	LOC = ''.join([ lst[1], '_', lst[4], '_', lst[5] ])
-	chrm = RS_Chr.get( LOC, None )
-	pos = RS_Pos.get( LOC, None )
-	bp = RS_BP.get( LOC, None )
-
-	if( chrm == None ):
-	  print >>OUT, LINE
-	  print >>OUT2, lst[1]
-	else:
-	  Entry = '\t'.join([ chrm, lst[1], pos, bp, lst[4], lst[5] ])
-	  print >>OUT, Entry
-
-F1.close()
-OUT.close()
-OUT2.close()

### 2019-10-03 code/ProcessData.Rmd
Processed Data Code

@@
 Run the following in docker exec -it <CONTAINER> /bin/bash 
-chmod 777 /root
+chmod 777 /root/
 mv TWAS/ /home/<USR>/TWAS/
 chown -hR <GID>:<USR> /home/<USR>/TWAS/
+Create a ~/.synapseConfig file in the container, but do not push a container containing your credentials file to Docker Hub!!!
 
@@
 echo "password = <PASWD>" >> ~/.synapseConfig
+```
+
+```{bash PLINKSetup, echo=F, include = T, results='hide', eval=T }
+mkdir ~/TWAS/bin
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20190617.zip 
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
+wget -q -P ~/TWAS/bin  http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191002.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191002.zip
+
+rm ~/TWAS/bin/*.zip
+rm ~/TWAS/bin/toy.*
+rm ~/TWAS/bin/LICENSE
 ```
@@
 
-  DNA <- fread(synGet(dna)$path)
-  Expression <- read.table(synGet(exp)$path, header=T)
-  IDs <- fread(synGet(id)$path)
+  DNA <- fread(syn_temp$get(dna)$path)
+  Expression <- read.table(syn_temp$get(exp)$path, header=T)
+  IDs <- fread(syn_temp$get(id)$path)
   IDs <- IDs[ grepl( 'accepted_hits.sort.coord.bam', IDs$fileName ) == T, ]
@@
 #Get Geno Names From FAM File
-FAM <- as.data.frame(fread( synGet('syn20820122')$path))
+FAM <- as.data.frame(fread( syn_temp$get('syn20820122')$path))
 FAM <- FAM[ (grepl('ROS', FAM[,1])) == F , ]
@@
   if( Type == 0){
-    RNA <- read.table( synGet(syn)$path)
+    RNA <- read.table( syn_temp$get(syn)$path)
     colnames(RNA) <- gsub('_TCX', '_a', colnames(RNA))
@@
   }else{
-    RNA <- as.data.frame( fread( synGet(syn)$path ) )
+    RNA <- as.data.frame( fread( syn_temp$get(syn)$path ) )
   }
@@
 }
-
 Norm_Resid_MAYO <- Mayo_filt( 'syn8466825', FAM, 1 )
@@
 
-  FAM <- as.data.frame(fread( synGet(Fam)$path))
+  FAM <- as.data.frame(fread( syn_temp$get(Fam)$path))
   Fam <- FAM[ (grepl('ROS', FAM[,1])) == T | (grepl('MAP', FAM[,1])) == T | (grepl('ROS', FAM[,2])) == T | (grepl('MAP', FAM[,2])) == T, ]
@@
   if(Var == 1){
-    Exp <- as.data.frame( fread(synGet(Exp)$path) )
+    Exp <- as.data.frame( fread(syn_temp$get(Exp)$path) )
   }else{
     if(Var == 0){
-        Exp <- as.data.frame( read.table(synGet('syn20800652')$path) )
+        Exp <- as.data.frame( read.table(syn_temp$get('syn20800652')$path) )
         colnames(Exp) <- gsub('X','', colnames(Exp))
@@
   }
-  Trans <- fread(synGet(Trans)$path)
+  Trans <- fread(syn_temp$get(Trans)$path)
   Trans <- Trans[ Trans$gwas_id != "", ]
-  names <- as.data.frame(fread(synGet(name)$path))
+  names <- as.data.frame(fread(syn_temp$get(name)$path))
   Trans <- Trans[ (Trans$gwas_id  %in%  names[,2]) == T, ]
@@
 #Annotate for TWAS
-hg19 <- as.data.frame(fread(synGet('syn20826610')$path))
+hg19 <- as.data.frame(fread(syn_temp$get('syn20826610')$path))
 hg19 <- hg19[ hg19[,1] %in% row.names( Norm_Resid ), ]
@@
 Diag_Resid <- Diag_Resid[ with(Diag_Resid, order( Chr, Coord)), ]
-write.table(Norm_Resid, file="ALL_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
-write.table(Diag_Resid, file="ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
 
 #Filter for CEU Ancestry Matched Training Cohort
-CEU_Samps <- do.call( rbind, strsplit( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))],  "_" ))
-write.table(CEU_Samps, file="ALL_CEU_SamplesToTrain.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Tot_Samps <- do.call( rbind, strsplit( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))],  "_" ))
+write.table(Tot_Samps, file="ALL_RNASamplesComb.tsv", col.names =F, row.names=F, sep=" ", quote=F)
 
@@
 
-write.table(ROS_Norm_Resid, file="ROS_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
-write.table(ROS_Diag_Resid, file="ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
-
 ROS_Samps <- do.call( rbind, strsplit( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],  "_" ))
-write.table(ROS_Samps, file="ROS_CEU_SamplesToTrain.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(ROS_Samps, file="ROS_RNASamples.tsv", col.names =F, row.names=F, sep=" ", quote=F)
 ```
@@
 ```{r FamFix, cache=TRUE}
-FAM <- as.data.frame(fread( synGet(Fam)$path))
-
-```
-
-## Push Results to Synapse
-```{r synapse.parameters, include=FALSE, cache=TRUE}
-
-FAM <- as.data.frame(fread( synGet('syn20820122')$path))
-MSBB <-  as.data.frame(fread( synGet('syn11384608')$path))
-ROSMAP <- as.data.frame(fread( synGet('syn3191087')$path))
+FAM <- as.data.frame(fread( syn_temp$get('syn20820122')$path))
+MSBB <-  as.data.frame(fread( syn_temp$get('syn11384608')$path))
+MSBB_Clin <- as.data.frame(fread( syn_temp$get('syn6101474')$path))
+ROSMAP <- as.data.frame(fread( syn_temp$get('syn3191087')$path))
 row.names(ROSMAP) <- ROSMAP$projid
-ROSMAP_ID <- as.data.frame(fread( synGet('syn3382527')$path))
-#mayo <- as.data.frame(fread( synGet('syn3817650')$path))
-#MAYO <- as.data.frame(fread( synGet('syn10648406')$path))
-MAYO <- as.data.frame(fread( synGet('syn19164046')$path))
-mayo <- as.data.frame(fread( synGet('syn19164050')$path))
+ROSMAP_ID <- as.data.frame(fread( syn_temp$get('syn3382527')$path))
+MAYO <- as.data.frame(fread( syn_temp$get('syn19164046')$path))
+mayo <- as.data.frame(fread( syn_temp$get('syn19164050')$path))
 
@@
 
+row.names(MSBB_Clin) <- MSBB_Clin$individualIdentifier
+
+MSBB_Clin <- cbind(MSBB_Clin[MSBB$individualIdentifier,1:dim(MSBB_Clin)[2]], MSBB[,1:dim(MSBB)[2] ] )
+row.names(MSBB_Clin) <- MSBB_Clin$sampleIdentifier
+
+MSBB_Clin$Diagnosis <- -9
+for( i in 1:length(row.names(MSBB_Clin))){
+  if( is.na(MSBB_Clin[ i,]$CDR) ==  F & is.na(MSBB_Clin[ i,]$bbscore) ==  F & is.na(MSBB_Clin[ i,]$NP.1) ==  F ){
+    if( MSBB_Clin[ i,]$CDR >= 1 & MSBB_Clin[ i,]$bbscore > 3 & MSBB_Clin[ i,]$NP.1 > 1 ){
+      MSBB_Clin[ i,]$Diagnosis <- 2
+    }else{
+      if(MSBB_Clin[ i,]$CDR < 1 & MSBB_Clin[ i,]$bbscore < 4 & MSBB_Clin[ i,]$NP.1 < 2){
+        MSBB_Clin[ i,]$Diagnosis <- 1
+      }else{}
+    }
+  }
+}
+
 Sex<-c(1,2)
@@
 FAM[ row.names(MSBB), ]$V5 <- MSBB$SEX.inferred
+FAM[ row.names(MSBB_Clin), ]$V6 <- MSBB_Clin$Diagnosis
 
-#Mayo --Needs Work
+#Mayo
 mayo <- mayo[complete.cases(mayo$Gender),]
@@
 
-NewMayo <- as.data.frame( rbind( cbind( MAYO$SampleID,MAYO$Sex), cbind( mayo$SampleID,mayo$Gender)) )
+NewMayo <- as.data.frame( rbind( cbind( MAYO$SampleID,MAYO$Sex,as.character(MAYO$Diagnosis)), cbind( mayo$SampleID,mayo$Gender, as.character(mayo$Diagnosis))) )
 NewMayo<- NewMayo[!duplicated(NewMayo),]
-NewMayo <- as.data.frame( cbind( as.character(NewMayo$V1),as.character(NewMayo$V2), gsub("_CER","",gsub("_TCX","",NewMayo$V1))) )
+NewMayo <- as.data.frame( cbind( as.character(NewMayo$V1),as.character(NewMayo$V2), gsub("_CER","",gsub("_TCX","",NewMayo$V1)), as.character(NewMayo$V3)) )
 NewMayo$V2 <- Sex[as.character( NewMayo$V2 )]
@@
 names <- FAM[ FAM$V1 == 0 ,]$V2
-#table(names %in% NewMayo$V3)
-
 NewMayo <- NewMayo[ !duplicated(NewMayo$V3), ]
@@
 
+Aff <- c(-9,-9,1,2)
+names(Aff) <- c("Pathologic Aging", "PSP", "Control", "AD")
+FAM[ names ,]$V6 <- as.numeric(Aff[as.character(NewMayo[ names, ]$V4)])
 FAM[ names ,]$V5 <- NewMayo[ names, ]$V2
-FAM$V5[is.na(FAM$V5)] <- 0
-##Missing Sex
-#1950 excluded from RNA-Sequncing - Pathology not meeting control criteria (BRAAK>3.0)
-#1957 excluded from RNA-Sequncing - Pathology not meeting control criteria (BRAAK>3.0)
+
+#Fix the Final
+FAM[ '1957',]$V5 <- 2
+FAM[ '1957',]$V6 <- -9
+FAM[ '1950',]$V5 <- 2
+FAM[ '1950',]$V6 <- -9
+
+#Fix ROSMAP Names
+FAM[ grepl('ROS', FAM$V2) == T  | grepl('MAP', FAM$V2) == T , ]$V1 <- FAM[ grepl('ROS', FAM$V2) == T  | grepl('MAP', FAM$V2) == T , ]$V2
+
+#Write New FAM to file
+write.table(FAM, file='New_Fam.fam', row.names = F, col.names=F, quote=F, sep=" ")
+```
+
+## Filter Genotype data
+```{bash FilterGenos, include=FALSE, cache=TRUE}
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+#Pull Geno-data
+synapse get syn20820120
+synapse get syn20820121
+synapse get syn20820122
+
+#Copy over FAM File with Sex Info:
+mv New_Fam.fam CEU_AncestryMatched_Genotypes.fam
+
+#Extract CEU
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ALL_RNASamplesComb.tsv --silent --make-bed --out All_CEU_ToTrainForTWAS
+
+#Extract ROS_Only:
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROS_RNASamples.tsv --make-bed --out ROSMAPonly_CEU_ToTrainForTWAS
+```
+
+```{r sanity check}
+FAM <- as.data.frame(fread('All_CEU_ToTrainForTWAS.fam'))
+row.names(FAM) <- paste0( FAM[,1], '_', FAM[,2] )
+table(row.names(FAM) %in% colnames(Diag_Resid))
+Diag_Resid_train <- Diag_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]
+Norm_Resid_train <- Norm_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]
+
+FAM <- as.data.frame(fread('ROSMAPonly_CEU_ToTrainForTWAS.fam'))
+row.names(FAM) <- paste0( FAM[,1], '_', FAM[,2] )
+table(row.names(FAM) %in% colnames(ROS_Diag_Resid))
+ROS_Diag_Resid_train <- ROS_Diag_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]
+ROS_Norm_Resid_train <- ROS_Norm_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]
+
+```
+
+## Push Results to Synapse
+```{r synapse.parameters.head, include=FALSE, cache=TRUE}
+parentId = 'syn18936948';
+activityName = 'Processed TWAS Training Data';
+activityDescription = 'Data from processing and hamonizing CEU ancestry matched Genotypes with available RNA-Seq profiles which were aligned to GRCh38 but annotated with hg19 TSS sites here';
+thisFileName <- 'ProcessData.Rmd'
+# Github link
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+```
+
+```{r synapse.parameters, include=FALSE, cache=TRUE}
+activityName = 'Processed TWAS Training Data';
+activityDescription = 'Data from processing and hamonizing CEU ancestry matched Genotypes with available RNA-Seq profiles';
+
+CODE <- syn_temp$store(synapseclient$Folder(name = "Processed_TWAS_Training_Data", parentId = parentId))
+
+#Set Used SynIDs For Provenance
+Syns_Used <- c("syn5223705", "syn8698211", "syn3817650", "syn8690904", 
+"syn6126119", "syn8698214", "syn8449369", "syn6126114", "syn6145639", "syn8690799"
+)
+
+# Set annotations
+EXP.all.annotations = list(
+  dataType = 'mRNA',
+  dataSubType = 'geneExp',
+  summaryLevel = 'gene',
+  assay	 = 'RNAseq',
+  tissueTypeAbrv	= c('TCX', 'DLPFC', 'PFG', 'STG', 'IFG', 'FP'), 
+  study = c('MAYO','MSBB', 'ROSMAP'), 
+  organism = 'HomoSapiens',
+  consortium	= 'AMPAD',
+  normalizationStatus	= TRUE,
+  normalizationType	= 'CQN',
+  rnaquantification = 'RSEM',
+  genomeAssemblyID = 'GRCh38'
+)
+# Set annotations
+Var.all.annotations = list(
+  dataType = 'Variant',
+  dataSubType = 'SNP',
+  summaryLevel = 'Nucleotide',
+  assay	 = 'Genotype Array',
+  tissueTypeAbrv	= c('Whole Blood'), 
+  study = c('MAYO','MSBB', 'ROSMAP'), 
+  organism = 'HomoSapiens',
+  consortium	= 'AMPAD',
+  genomeAssemblyID = 'GRCh37'
+)
+
+Basic.annotations = list(
+  dataType = 'Induvidual List',
+  dataSubType = 'Plink PatientID Filter',
+  study = c('MAYO','MSBB', 'ROSMAP'), 
+  organism = 'HomoSapiens',
+  consortium	= 'AMPAD'
+)
+
+## TOTAL SVA-only Exp
+write.table(Norm_Resid, file="ALL_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Syns_Used_SVA_EXP <- c('syn11384608', 'syn8485026', 'syn6100548', 'syn8456704', 'syn5879839', 'syn3382527','syn20820122', 'syn8466825', 'syn20820122')
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted.tsv', name = 'Total Merged and region Avereaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+## TOTAL Diagnosis Exp
+write.table(Diag_Resid, file="ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Syns_Used_Diagnosis_EXP <- c('syn20801991', 'syn11384608', 'syn20801798', 'syn6100548',  'syn20800652', 'syn5879839', 'syn3382527','syn20820122', 'syn20820122')
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'Total Merged and region Avereaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+    EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
+    syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+## CEU SVA-only Exp
+write.table(Norm_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Syns_Used_SVA_EXP <- c('syn11384608', 'syn8485026', 'syn6100548', 'syn8456704', 'syn5879839', 'syn3382527','syn20820122', 'syn8466825', 'syn20820122')
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU Merged and region Avereaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+## CEU Diagnosis Exp
+write.table(Diag_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Syns_Used_Diagnosis_EXP <- c('syn20801991', 'syn11384608', 'syn20801798', 'syn6100548',  'syn20800652', 'syn5879839', 'syn3382527','syn20820122', 'syn20820122')
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU Merged and region Avereaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+#ROSMAP only Expression
+  ## CEU SVA-only Exp -- ROSMAP Only
+write.table(ROS_Norm_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Syns_Used_SVA_EXP <- c('syn8456704', 'syn5879839', 'syn3382527','syn20820122' )
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ROS_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU ROSMAP Only RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
+  EXP.all.annotations$tissueTypeAbrv = 'DLPFC'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+  ## CEU Diagnosis Exp -- ROSMAP Only
+write.table(ROS_Diag_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+Syns_Used_Diagnosis_EXP <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn20820122')
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU ROSMAP Only RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
+  EXP.all.annotations$tissueTypeAbrv = 'DLPFC'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+#ALL INDV
+ ##Check that order is correct between file lists
+  #table(paste0(Tot_Samps[,1], '_', Tot_Samps[,2]) == colnames(Diag_Resid)[ 5:length(colnames(Diag_Resid))])
+Syns <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn20820122')
+ENRICH_OBJ_Tot_list <- syn_temp$store( synapseclient$File( path='ALL_RNASamplesComb.tsv', name = 'All Indv with RNA-Seq Profiles in AMP-Ad For Filtering', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  syn_temp$setAnnotations(ENRICH_OBJ_Tot_list, annotations = Basic.annotations)
+
+#ROSMAP INDV
+ ##Check that order is correct between file lists
+  #table(paste0(ROS_Samps[,1], '_', ROS_Samps[,2]) == colnames(ROS_Norm_Resid)[ 5:length(colnames(ROS_Norm_Resid))])
+Syns <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn20820122')
+ENRICH_OBJ_RM_List <- syn_temp$store( synapseclient$File( path='ROS_RNASamples.tsv', name = 'ROSMAP Indv with RNA-Seq Profiles in AMP-Ad For Filtering', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  syn_temp$setAnnotations(ENRICH_OBJ_RM_List, annotations = Basic.annotations)
+
+#PLINK ALL -- STORE IN SEPERATE FOLDER INCASE PHI LIMITATIONS APPLY LATER
+  CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Clustered_Genotypes", parentId = parentId))
+  Syns <- c( 'syn20820120', 'syn20820121', 'syn20820122', ENRICH_OBJ_Tot_list$properties$id  )
+#FAM  
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.fam', name = 'All Matched CEU Genotype FAM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#BED
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.bed', name = 'All Matched CEU Genotype BED', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#LOG
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.log', name = 'All Matched CEU Genotype LOG', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#BIM
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.bim', name = 'All Matched CEU Genotype BIM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#PLINK Rosmap
+  Syns <- c( 'syn20800652', 'syn5879839', 'syn3382527', ENRICH_OBJ_RM_List$properties$id)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.fam', name = 'ROSMAP Matched CEU Genotype FAM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#BED
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.bed', name = 'ROSMAP Matched CEU Genotype BED', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#LOG
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.log', name = 'ROSMAP Matched CEU Genotype LOG', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+#BIM
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.bim', name = 'ROSMAP Matched CEU Genotype BIM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
 
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapser)
-library(knit2synapse)
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
 
-synLogin()
-knit2synapse::createAndKnitToFolderEntity(file = "",
-                                          parentId ="",
-                                          folderName = '')
+library(data.table)
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+
+createAndKnitToFolderEntityClient(file = "ProcessData.Rmd",
+                                          parentId ="syn18936948",
+                                          folderName = 'Processed_TWAS_Training_Data')
 ```

### 2019-10-03 utilityFunctions/hook_synapseMdSyntax_plot.R
Add SynapseClient Hooks

@@ -1,0 +1,63 @@
+hook_synapseMdSyntax_plot <- function(x, options){
+  synPlotMdOpts <- character()
+  
+  ## SET URL ENCODING STRINGS
+  urlEncodings <- c('{' = "%7B",
+                    '}' = "%7D",
+                    '-' = "%2D",
+                    '_' = "%5F",
+                    '.' = "%2E",
+                    '!' = "%21",
+                    '~' = "%7E",
+                    '*' = "%2A",
+                    '`' = "%60",
+                    '\'' = "%27",
+                    '(' = "%28",
+                    ')' = "%29",
+                    '[' = "%5B",
+                    ']' = "%5D",
+                    ':' = "%3A",
+                    ';' = "%3B",
+                    '\n' = "%0A",
+                    '\r' = "%0D",
+                    '/' = "%2F",
+                    '?' = "%3F",
+                    '&' = "%26",
+                    '=' = "%3D",
+                    '+' = "%2B",
+                    ',' = "%2C",
+                    '#' = "%23",
+                    '$' = "%24")
+  
+  ## CHECK FOR ALIGN OPTION BEING SET
+  if( any(names(options) == "align") ){
+    ## CHECKS FOR ALIGN OPTION
+    if( !is.character(options$align) ){
+      stop("align must be one of none, left, right, or center")
+    }
+    if( !(options$align %in% c("none", "left", "right", "center")) ){
+      stop("align must be one of none, left, right, or center")
+    }
+    synPlotMdOpts <- paste(synPlotMdOpts, "&align=", options$align, sep="")
+  } else{
+    synPlotMdOpts <- paste(synPlotMdOpts, "&align=none", sep="")
+  }
+  
+  ## CHECK FOR SCALE OPTION BEING SET
+  if( any(names(options) == "scale") ){
+    ## RANGE CHECKS FOR SCALE OPTION
+    if( !is.numeric(options$scale) ){
+      stop("scale option must be numeric")
+    }
+    if( options$scale <= 0 | options$scale > 500 ){
+      stop("scale option must be greater than 0 and less than 500")
+    }
+    
+    synPlotMdOpts <- paste(synPlotMdOpts, "&scale=", options$scale, sep="")
+  } else{
+    synPlotMdOpts <- paste(synPlotMdOpts, "&scale=100", sep="")
+  }
+  
[…]

### 2019-10-04 code/Ancestry_PCA.Rmd
Make Ancestry Script Py Complient

@@
 ```{bash Login, echo=T, results='hide', eval=FALSE}
-source /root/.bashrc
+#source /root/.bashrc
 synapse login -u <USR> -p <PSWD> --rememberMe
@@
 
+## Pull Plink and Plink2
+```{bash PLINKSetup, results='hide', echo=TRUE}
+mkdir ~/TWAS/bin
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20190617.zip 
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
+wget -q -P ~/TWAS/bin  http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191002.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191002.zip
+
+rm ~/TWAS/bin/*.zip
+rm ~/TWAS/bin/toy.*
+rm ~/TWAS/bin/LICENSE
+```
+
 ## Pull 1000Genomes down and process
@@
 ```{bash pull_1000Genomes, echo=T, results='hide', cache = FALSE}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 #PATH=$PATH:TWAS/bin/
@@
 ```{bash ProcessMSBB, echo=T, results='hide', cache = FALSE}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```{bash FinalizeMSBB, echo=T, results='hide', cache = FALSE  }
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```{bash MAYO, echo=T, results='hide', cache = FALSE}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```{bash CheckMayo, echo=T, results='hide', cache = FALSE}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```{bash DosageToHardCalls, echo=T, results='hide', cache = FALSE}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```{bash MergeAndCall, cache = FALSE, echo=T, results='hide'}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 ```{bash FIlterAncestry, cache=FALSE, echo=TRUE, results='hide'}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 
-```{r synapse.parameters, include=FALSE, cache=TRUE}
+```{r synapse.parameters, include=FALSE, echo=FALSE, results='hide', cache=TRUE}
 library(githubr)
@@
 # Github link
-thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
-thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
 ```
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryClustered_INDVs.tsv', sep = '\t', quote=F)
-ENRICH_OBJ = File('CEU_AncestryClustered_INDVs.tsv', 
-                  name = 'Samples Clustered to CEU Ancestry', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'CEU_INDV'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryClustered_INDVs.tsv', name = 'Samples Clustered to CEU Ancestry', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+EXP.all.annotations$dataSubType = 'CEU_INDV'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenvec', sep = '\t', quote=F)
-ENRICH_OBJ = File('Total_PCA.eigenvec', 
-                  name = 'PCA Eigen Vectors', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'EigenVecs'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Total_PCA.eigenvec', name = 'PCA Eigen Vectors', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+EXP.all.annotations$dataSubType = 'EigenVecs'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'Total_PCA.eigenval', sep = '\t', quote=F)
-ENRICH_OBJ = File('Total_PCA.eigenval', 
-                  name = 'PCA Eigen Values', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'EigenValues'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Total_PCA.eigenval', name = 'PCA Eigen Values', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+EXP.all.annotations$dataSubType = 'EigenValues'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bed', sep = '\t', quote=F)
-ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.bed', 
-                  name = 'Genotype Bed File', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'GWAS'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.bed', name = 'Genotype Bed File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+EXP.all.annotations$dataSubType = 'GWAS'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.bim', sep = '\t', quote=F)
-ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.bim', 
-                  name = 'Genotype Bim File', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'GWAS'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.bim', name = 'Genotype Bim File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+EXP.all.annotations$dataSubType = 'GWAS'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.fam', sep = '\t', quote=F)
-ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.fam', 
-                  name = 'Genotype Fam File', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'GWAS'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.fam', name = 'Genotype Fam File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'GWAS'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.nosex', sep = '\t', quote=F)
-ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.nosex', 
-                  name = 'Genotype nosex File', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'GWAS'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.nosex', name = 'Genotype nosex File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'GWAS'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 #write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CEU_AncestryMatched_Genotypes.log', sep = '\t', quote=F)
-ENRICH_OBJ = File('CEU_AncestryMatched_Genotypes.log', 
-                  name = 'Genotype log File', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
-all.annotations$dataSubType = 'GWAS'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.log', name = 'Genotype log File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  EXP.all.annotations$dataSubType = 'GWAS'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 ```
+
+```{bash Clean, echo=T, eval=F, results='hide'}
+rm -r ~/TWAS/bin/
+rm *.bed
+rm *.fam
+rm *.bim
+rm *.log
+rm *.tsv
+rm *list
+rm -r VCF/
+rm -r GWAS_Plink/
+```
+
 ### R Source Code
@@
 
+##Knit to Synapse
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-#library(synapser)
-library(knit2synapse)
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
 
-synLogin()
-#knit2synapse::createAndKnitToFolderEntity(file = "Ancestry_PCA.Rmd",
-#                                          parentId ="syn18936948",
-#                                          folderName = 'Ancestry_Analysis')
+library(data.table)
+library(githubr)
+library(ggplot2)
+library(plotrix)
+library(scater)
+library(data.table)
 
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+
+createAndKnitToFolderEntityClient(file = "Ancestry_PCA.Rmd",
+                                          parentId ="syn18936948",
+                                          folderName = 'Ancestry_Analysis')
 ```

### 2019-10-04 code/ProcessData.Rmd
Make Ancestry Script Py Complient

@@
 
-```{bash PLINKSetup, echo=F, include = T, results='hide', eval=T }
+```{bash PLINKSetup, results='hide', echo=TRUE}
 mkdir ~/TWAS/bin
@@
 ## MSBB RNA-Seq: Average Across Brain Regions, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
-```{r MSBBRNA, echo=F, results='hide', cache = FALSE}
+```{r MSBBRNA, results='hide', echo=TRUE, cache = FALSE}
 library(data.table)
@@
 ## Mayo RNA-Seq: Remove Cerebellum, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
-```{r MayoRNA, echo=T, results='hide', cache = FALSE, echo=FALSE}
+```{r MayoRNA, results='hide', echo=TRUE, cache = FALSE}
 #Get Geno Names From FAM File
@@
 ## ROSMAP RNA-Seq: Filter for INDV. w/Genotype Data and Rename Samples with Genotype ID 
-```{r ROSMAPoRNA, echo=T, results='hide', cache = FALSE, echo=FALSE}
+```{r ROSMAPoRNA, results='hide', echo=TRUE, cache = FALSE}
 #SVA: 'syn8456704'
@@
 * Filter Genotypes for RNA Samples
-```{r Merge RNASeq, echo=T, results='hide', cache = FALSE, echo=FALSE}
+```{r Merge RNASeq, results='hide', echo=TRUE, cache = FALSE}
 #Common Genes:
@@
 ## Fix FamFile
-```{r FamFix, cache=TRUE}
+```{r FamFix, results='hide', echo=TRUE, cache=TRUE}
 FAM <- as.data.frame(fread( syn_temp$get('syn20820122')$path))
@@
 ## Filter Genotype data
-```{bash FilterGenos, include=FALSE, cache=TRUE}
+```{bash FilterGenos, results='hide', echo=TRUE, cache=TRUE}
 #source /root/.bashrc
@@
 
-```{r sanity check}
+```{r sanitycheck, include=TRUE, echo=TRUE}
 FAM <- as.data.frame(fread('All_CEU_ToTrainForTWAS.fam'))
@@
 
-## Push Results to Synapse
-```{r synapse.parameters.head, include=FALSE, cache=TRUE}
+## Push Results to Synapse -- Contained in ProcessData.Rmd if needed for reference
+```{r synapse.parameters.head, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
 parentId = 'syn18936948';
@@
 
-```{r synapse.parameters, include=FALSE, cache=TRUE}
+```{r synapse.parameters, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
 activityName = 'Processed TWAS Training Data';
@@
 
+```{bash Clean, echo=T, results='hide'}
+rm -r ~/TWAS/bin/
+rm *.bed
+rm *.fam
+rm *.bim
+rm *.log
+rm *.tsv
+```
+
+### R Source Code
+[Github](`r thisFile`)
+
 ##Knit to Synapse
@@
 source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
 

### 2019-10-07 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Finalize Data Processing

--- 2019-09-18 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
@@
 ---
-title: Covariate and analysis of MSSM reprocessed counts Regressing out Diagnosis as well for TWAS
+title: Covariate and analysis of MSBB reprocessed counts Regressing out Diagnosis as well for TWAS
 author: 'JKG - Adapted from: Thanneer Perumal'
@@
 library(glmnet)
-library(synapser)
 library(knitr)
@@
 library(foreach)
+library(githubr)
 cl = makeCluster(detectCores()-2)
@@
 
-```{r synLogin}
-synLogin()
-```
-
 ### Data download
@@
 ALL_USED_IDs <- COUNT_ID
-COUNT <- synapser::synGet(COUNT_ID, version = 1)$path %>%
+COUNT <- syn_temp$get(COUNT_ID, version = 1)$path %>%
   read.table(header=T, sep='\t', check.names = F, row.names = 1)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_TECH_ID
-METADATA_TECH <- synapser::synGet(METADATA_TECH_ID, version = 7)$path %>%
+METADATA_TECH <- syn_temp$get(METADATA_TECH_ID, version = 7)$path %>%
   read.table(sep=',',header=T, row.names=1) %>%
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_AGE_ID
-METADATA_AGE <- synapser::synGet(METADATA_AGE_ID, version = 3)$path %>%
+METADATA_AGE <- syn_temp$get(METADATA_AGE_ID, version = 3)$path %>%
   read.table(sep='\t', header=T)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_CLINICAL_ID
-METADATA_CLINICAL <- synapser::synGet(METADATA_CLINICAL_ID, version = 4)$path %>%
+METADATA_CLINICAL <- syn_temp$get(METADATA_CLINICAL_ID, version = 4)$path %>%
   read.csv(header = T)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
-METADATA.PICARD <- synGet(METADATA.PICARD_ID, version = 1)$path %>%
+METADATA.PICARD <- syn_temp$get(METADATA.PICARD_ID, version = 1)$path %>%
   read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
@@
 # Get gene specific parameters from synapse
-GENE.PARAM = synGet('syn8449369', version = 2)$path %>% 
+GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>% 
     read.table(sep='\t', header=T, stringsAsFactors=F)
@@
 primaryVariable <- c("CDR", "Tissue.Diagnosis", "Tissue.APOE4")
-
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
@@
 
-# Code WTF is this??
-CODE <- Folder(name = "MSBB", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "MSBB", parentId = parentId))
 
@@
 )
-
 # Set annotations
@@
 write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MSBB_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ = File('MSBB_SVA_Diagnosis_Corrected.tsv', 
-                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 write.table(COVARIATES, file = 'MSBB_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ = File('MSBB_SVA_Diagnosis_Covariates.tsv', 
-                  name = 'Covariates', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_Counts.tsv', 
-                  name = 'Counts (filtered raw)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_Counts.tsv', 
-                  name = 'Counts (estimated)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_eCounts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_logCPM.tsv', 
-                  name = 'Counts (filtered logCPM)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_offset.tsv', 
-                  name = 'Gene length and GC content offset', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_Design.tsv', 
-                  name = 'Design Matrix', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_SurVar.tsv', 
-                  name = 'Surrogate Variables', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MSBB_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MSBB_Diagnosis_Regressed_netResidualExpression.tsv', 
-                  name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 
+```{r DelFiles, echo=T, results='hide'}
+system('rm *.tsv')
+```
 ### R Source Code
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapser)
-library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synLogin()
-knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/MSBB_RegressDiagnosis_4_TWAS.Rmd",
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+
+createAndKnitToFolderEntityClient(file = "MSBB_RegressDiagnosis_4_TWAS.Rmd",
                                           parentId ="syn20798011",

### 2019-10-07 code/ProcessData.Rmd
Finalize Data Processing

@@
 
-```{bash PLINKSetup, results='hide', echo=TRUE}
+```{bash PLINKSetup, results='hide', eval=F, echo=TRUE}
 mkdir ~/TWAS/bin
@@
 unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
-wget -q -P ~/TWAS/bin  http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191002.zip
-unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191002.zip
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191006.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191006.zip
 
@@
   #'@id synID of id translators  eg. 'syn6100548'
-  #dna<-'syn11384608'
-  #exp<-'syn8485026'
-  #id<-'syn6100548'
 
@@
   #'@Var 1=Nondiagnosis correcte 0=Diagnosis Corrected
-
   # eg. Ros_Filt( 'syn8456704', 'syn5879839', 'syn3382527','syn20820122')
@@
 Comb <- function( MSBB, Mayo, RM, Names){
-  #MSBB <- Norm_Resid_MSBB
-  #Mayo <- Norm_Resid_MAYO
-  #RM <- Norm_Resid_RM
-  #Names <- GNames
+  #'@MSBB The MSBB Expression Set Data Frame
+  #'@Mayo The Mayo Expression Set Data Frame
+  #'@RM The ROSMAP Expression Set Data Frame
+  #'@Names Gene names Vector
 
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted.tsv', name = 'Total Merged and region Avereaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted.tsv', name = 'Total Merged and region Averaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
 EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'Total Merged and region Avereaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'Total Merged and region Averaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
     EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU Merged and region Avereaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU Merged and region Averaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU Merged and region Avereaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU Merged and region Averaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
@@
 
-#PLINK ALL -- STORE IN SEPERATE FOLDER INCASE PHI LIMITATIONS APPLY LATER
+###PLINK ALL -- STORE IN SEPERATE FOLDER INCASE PHI LIMITATIONS APPLY LATER
   CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Clustered_Genotypes", parentId = parentId))

### 2019-10-07 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
Finalize Data Processing

@@
 library(cqn)
-library(synapser)
 library(knitr)
@@
 library(githubr)
-
 cl = makeCluster(detectCores()-2)
@@
 ALL_USED_IDs <- COUNT_ID
-COUNT_OBJ <- synGet(COUNT_ID, version = 1)
+COUNT_OBJ <- syn_temp$get(COUNT_ID, version = 1)
 COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID
-METADATA.CLINICAL_OBJ <- synGet(METADATA.CLINICAL_ID, version = 3)
+METADATA.CLINICAL_OBJ <- syn_temp$get(METADATA.CLINICAL_ID, version = 3)
 METADATA.CLINICAL <- read.table(METADATA.CLINICAL_OBJ$path,sep=',',header=T)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.CLINICAL_ID1
-METADATA.CLINICAL_OBJ1 <- synGet(METADATA.CLINICAL_ID1, version = 1)
+METADATA.CLINICAL_OBJ1 <- syn_temp$get(METADATA.CLINICAL_ID1, version = 1)
 METADATA.CLINICAL1 <- read.table(METADATA.CLINICAL_OBJ1$path,sep=',',header=T)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.TECH_ID
-METADATA.TECH_OBJ <- synGet(METADATA.TECH_ID, version = 1)
+METADATA.TECH_OBJ <- syn_temp$get(METADATA.TECH_ID, version = 1)
 METADATA.TECH <- read.table(METADATA.TECH_OBJ$path,sep='\t',header=T)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
-METADATA.PICARD <- synGet(METADATA.PICARD_ID, version = 2)$path %>%
+METADATA.PICARD <- syn_temp$get(METADATA.PICARD_ID, version = 2)$path %>%
   data.table::fread() %>%
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = KEY_ID  
-KEY <- synGet(KEY_ID, version = 7)$path %>%
+KEY <- syn_temp$get(KEY_ID, version = 7)$path %>%
   read.csv %>% 
@@
 # Get gene specific parameters from synapse
-GENE.PARAM = synGet('syn8449369', version = 2)$path %>%
+GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>%
   data.table::fread(data.table = FALSE)
@@
 
-# Code WTF is this??
-CODE <- Folder(name = "ROSMAP", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))
 
@@
 )
-
 # Store SVA results
 write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Corrected.tsv', 
-                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 write.table(COVARIATES, file = 'ROSMAP_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ = File('ROSMAP_SVA_Diagnosis_Covariates.tsv', 
-                  name = 'Covariates', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', 
-                  name = 'Counts (filtered raw)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', 
-                  name = 'Counts (estimated)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', 
-                  name = 'Counts (filtered logCPM)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', 
-                  name = 'Gene length and GC content offset', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', 
-                  name = 'Design Matrix', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', 
-                  name = 'Surrogate Variables', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', 
-                  name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
-#stopCluster(cl)
+stopCluster(cl)
 ```
 
+```{r DelFiles, echo=T, results='hide'}
+system('rm *.tsv')
+```
 ### R Source Code
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapser)
-library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synLogin()
-knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+
+createAndKnitToFolderEntityClient(file = "ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
                                           parentId ="syn20798011",
                                           folderName = 'ROSMAP')
+
 ```

### 2019-10-07 code/FUSION.compute_weights_Parallel.R
Training Dockerfile

@@ -1,0 +1,384 @@
+# ==== TODO
+# * Make sure BLUP/BSLMM weights are being scaled properly based on MAF
+
+suppressMessages(library("optparse"))
+suppressMessages(library('plink2R'))
+suppressMessages(library('glmnet'))
+suppressMessages(library('methods'))
+
+option_list = list(
+  make_option("--bfile", action="store", default=NA, type='character',
+              help="Path to PLINK binary input file prefix (minus bed/bim/fam) [required]"),
+  make_option("--out", action="store", default=NA, type='character',
+              help="Path to output files [required]"),
+  make_option("--tmp", action="store", default=NA, type='character',
+              help="Path to temporary files [required]"),
+  make_option("--pheno", action="store", default=NA, type='character',
+              help="Path to molecular phenotype file (PLINK format) [optional, taken from bfile otherwise]"),
+  make_option("--PATH_plink", action="store", default="plink", type='character',
+              help="Path to plink executable [%default]"),
+  make_option("--PATH_gcta", action="store", default="gcta_nr_robust", type='character',
+              help="Path to plink executable [%default]"),
+  make_option("--PATH_gemma", action="store", default="gemma", type='character',
+              help="Path to plink executable [%default]"),
+  make_option("--covar", action="store", default=NA, type='character',
+              help="Path to quantitative covariates (PLINK format) [optional]"),
+  make_option("--resid", action="store_true", default=FALSE,
+              help="Also regress the covariates out of the genotypes [default: %default]"),              
+  make_option("--hsq_p", action="store", default=0.01, type='double',
+              help="Minimum heritability p-value for which to compute weights [default: %default]"),
[…]

### 2019-10-08 code/Multi_Threaded_Weights.py
TWAS Code

@@ -1,0 +1,111 @@
+#!/usr/bin/python
+
+import sys
+import os
+import re
+#from pprint import pprint as pp
+import subprocess32 as subprocess
+import multiprocessing as mp
+from multiprocessing.pool import ThreadPool
+import datetime
+
+#Runs the WEight calculation in parallel
+##Must set all variables
+##Must have Ordered IDs file in run location!!!!
+
+#'@USAGE: python Run_Weights.py <EXPRESSION Data SET> <Geno Prefix> <wc -l EXPRESSION Data SET>
+INPT_Exp = sys.argv[1]
+INPT_Geno = sys.argv[2]
+NumberOfGenes = sys.argv[3]
+
+#Set All Configurations 
+GCTA='/gcta_1.92.4beta/gcta64'
+PLINK='/usr/local/bin/plink2'
+PLINKa='/usr/bin/plink1'
+PLIN='/plink'
+
+GEMMA="/fusion_twas-master/gemma-0.98.1-linux-static"
+#GEMMA='/usr/local/bin/gemma'
+LDREF='/fusion_twas-master/LDREF'
+
+PRE_GEXP=INPT_Exp
+PRE_GENO=INPT_Geno
+      
+#PATH TO OUTPUT DIRECTORY (population-specific subdirs will be made)
+OUT_DIR='Training_CV_Groups/All_Data'
+
+#ROWS IN THE MATRIX TO ANALYZE (FOR BATCHED RUNS)
+BATCH_START='1'
+BATCH_END=NumberOfGenes
+NR= str(BATCH_START) + '_' + str(NumberOfGenes)
+
+CMD = ''.join([ 'mkdir --parents tmp/', NR ])
+subprocess.Popen(CMD, shell=True).wait()
+CMD = ''.join([ 'mkdir --parents hsq/', NR ])
+subprocess.Popen(CMD, shell=True).wait()
+CMD = ''.join([ 'mkdir --parents out/', NR ])
+subprocess.Popen(CMD, shell=True).wait()
+
+##Runs on a single core!
+def process( foo ):
+	if( 'TSS' in foo):
+		pass
+	else:
+		LINE = foo.rstrip('\r\n')
+		lst = LINE.split('\t')
+
+		CHR=lst[2]
+		C=lst[2]
+		P0=int(lst[3])-500000
+		P1=int(lst[3])+500000
+		GNAME=lst[1]
[…]

### 2019-10-08 code/ProcessData.Rmd
Catch Code Up
FixEXPHeaders

@@
 ## TOTAL SVA-only Exp
-write.table(Norm_Resid, file="ALL_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(Norm_Resid, file="ALL_RNA_Seq_SVAadusted.tsv", col.names =T, row.names=F, sep="\t", quote=F)
 Syns_Used_SVA_EXP <- c('syn11384608', 'syn8485026', 'syn6100548', 'syn8456704', 'syn5879839', 'syn3382527','syn20820122', 'syn8466825', 'syn20820122')
@@
 ## TOTAL Diagnosis Exp
-write.table(Diag_Resid, file="ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(Diag_Resid, file="ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =T, row.names=F, sep="\t", quote=F)
 Syns_Used_Diagnosis_EXP <- c('syn20801991', 'syn11384608', 'syn20801798', 'syn6100548',  'syn20800652', 'syn5879839', 'syn3382527','syn20820122', 'syn20820122')
@@
 ## CEU SVA-only Exp
-write.table(Norm_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(Norm_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted.tsv", col.names =T, row.names=F, sep="\t", quote=F)
 Syns_Used_SVA_EXP <- c('syn11384608', 'syn8485026', 'syn6100548', 'syn8456704', 'syn5879839', 'syn3382527','syn20820122', 'syn8466825', 'syn20820122')
@@
 ## CEU Diagnosis Exp
-write.table(Diag_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(Diag_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =T, row.names=F, sep="\t", quote=F)
 Syns_Used_Diagnosis_EXP <- c('syn20801991', 'syn11384608', 'syn20801798', 'syn6100548',  'syn20800652', 'syn5879839', 'syn3382527','syn20820122', 'syn20820122')
@@
   ## CEU SVA-only Exp -- ROSMAP Only
-write.table(ROS_Norm_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(ROS_Norm_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted.tsv", col.names =T, row.names=F, sep="\t", quote=F)
 Syns_Used_SVA_EXP <- c('syn8456704', 'syn5879839', 'syn3382527','syn20820122' )
@@
   ## CEU Diagnosis Exp -- ROSMAP Only
-write.table(ROS_Diag_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =F, row.names=F, sep="\t", quote=F)
+write.table(ROS_Diag_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =T, row.names=F, sep="\t", quote=F)
 Syns_Used_Diagnosis_EXP <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn20820122')

### 2019-10-08 code/ProcessData.Rmd
Fix Process

@@
 
+Diag_Resid_train <- Diag_Resid_train[ (Diag_Resid_train$Chr %in% c(1:22)) == T, ]
+Norm_Resid_train <- Norm_Resid_train[ (Norm_Resid_train$Chr %in% c(1:22)) == T, ]
+
+ROS_Diag_Resid_train <- ROS_Diag_Resid_train[ (ROS_Diag_Resid_train$Chr %in% c(1:22)) == T, ]
+ROS_Norm_Resid_train <- ROS_Norm_Resid_train[ (ROS_Norm_Resid_train$Chr %in% c(1:22)) == T, ]
+
+colnames(Diag_Resid_train) <- c( colnames(Diag_Resid_train[1:4]), do.call( rbind, strsplit( colnames(Diag_Resid_train[ 5:length(colnames(Diag_Resid_train)) ]), "_") )[,2] )
+
+colnames(Norm_Resid_train) <- c( colnames(Norm_Resid_train[1:4]), do.call( rbind, strsplit( colnames(Norm_Resid_train[ 5:length(colnames(Norm_Resid_train)) ]), "_") )[,2] )
+
+colnames(ROS_Diag_Resid_train) <- c( colnames(ROS_Diag_Resid_train[1:4]), do.call( rbind, strsplit( colnames(ROS_Diag_Resid_train[ 5:length(colnames(ROS_Diag_Resid_train)) ]), "_") )[,2] )
+
+colnames(ROS_Norm_Resid_train) <- c( colnames(ROS_Norm_Resid_train[1:4]), do.call( rbind, strsplit( colnames(ROS_Norm_Resid_train[ 5:length(colnames(ROS_Norm_Resid_train)) ]), "_") )[,2] )
+
 ```

### 2019-10-09 code/Multi_Threaded_Weights.py
ReDo Weights Script

@@ -1,111 +1,0 @@
-#!/usr/bin/python
-
-import sys
-import os
-import re
-#from pprint import pprint as pp
-import subprocess32 as subprocess
-import multiprocessing as mp
-from multiprocessing.pool import ThreadPool
-import datetime
-
-#Runs the WEight calculation in parallel
-##Must set all variables
-##Must have Ordered IDs file in run location!!!!
-
-#'@USAGE: python Run_Weights.py <EXPRESSION Data SET> <Geno Prefix> <wc -l EXPRESSION Data SET>
-INPT_Exp = sys.argv[1]
-INPT_Geno = sys.argv[2]
-NumberOfGenes = sys.argv[3]
-
-#Set All Configurations 
-GCTA='/gcta_1.92.4beta/gcta64'
-PLINK='/usr/local/bin/plink2'
-PLINKa='/usr/bin/plink1'
-PLIN='/plink'
-
-GEMMA="/fusion_twas-master/gemma-0.98.1-linux-static"
-#GEMMA='/usr/local/bin/gemma'
-LDREF='/fusion_twas-master/LDREF'
-
-PRE_GEXP=INPT_Exp
-PRE_GENO=INPT_Geno
-      
-#PATH TO OUTPUT DIRECTORY (population-specific subdirs will be made)
-OUT_DIR='Training_CV_Groups/All_Data'
-
-#ROWS IN THE MATRIX TO ANALYZE (FOR BATCHED RUNS)
-BATCH_START='1'
-BATCH_END=NumberOfGenes
-NR= str(BATCH_START) + '_' + str(NumberOfGenes)
-
-CMD = ''.join([ 'mkdir --parents tmp/', NR ])
-subprocess.Popen(CMD, shell=True).wait()
-CMD = ''.join([ 'mkdir --parents hsq/', NR ])
-subprocess.Popen(CMD, shell=True).wait()
-CMD = ''.join([ 'mkdir --parents out/', NR ])
-subprocess.Popen(CMD, shell=True).wait()
-
-##Runs on a single core!
-def process( foo ):
-	if( 'TSS' in foo):
-		pass
-	else:
-		LINE = foo.rstrip('\r\n')
-		lst = LINE.split('\t')
-
-		CHR=lst[2]
-		C=lst[2]
-		P0=int(lst[3])-500000
-		P1=int(lst[3])+500000
-		GNAME=lst[1]
[…]

### 2019-10-09 code/WorksMultiThreaded.py

@@ -1,0 +1,184 @@
+#!/usr/bin/python
+import sys
+import os
+import re
+import subprocess32 as subprocess
+import multiprocessing as mp
+from multiprocessing.pool import ThreadPool
+import datetime
+import shlex, subprocess
+
+#Runs the WEight calculation in parallel
+##Must set all variables
+##Must have Ordered IDs file in run location!!!!
+
+
+#Set All Configurations 
+GCTA='/gcta_1.92.4beta/gcta64'
+PLINK='/usr/local/bin/plink2'
+PLINKa='/usr/bin/plink1'
+PLIN='/plink'
+GEMMA="/fusion_twas-master/gemma-0.98.1-linux-static"
+LDREF='/fusion_twas-master/LDREF'
+
+#PRE_GEXP='Processed_ROSMAP_DLPFC_eQTLResidualExpression_Chr21.tsv'
+#PRE_GENO='Processed_ROSMAP_DLPFC_eQTLResidualExpression.tsv'
+   
+#INDV IDs to keep for analysis:
+INDV_ID='/fusion_twas-master/Total_IDs.txt'
+#PATH TO OUTPUT DIRECTORY (population-specific subdirs will be made)
+OUT_DIR='All_Data'
+
+#Number of rows in the gene expression 
+##Will loop through one gene at a time and run in parallel 
+BATCH_START='1'
+BATCH_END='13651'
+NR='1_13651'
+#BATCH_END=$(wc -l $PRE_GEXP | awk '{ print $1 }' -)
+
+CMD = 'mkdir Genos'
+subprocess.Popen(CMD, shell=True).wait()
+
+#This is how I pull the input data from S3 into EC2
+#CMD = ''.join([ 'aws s3 cp s3://jkg-s3-synapseencryptedexternalbucket-zszdd03ghnb2/ROSMAP/TWAS_CEU/FINAL_LDREF_CEU_MatchedEXP.bim . --recursive' ])
+#subprocess.Popen(CMD, shell=True).wait()
+
+#CMD = ''.join([ 'aws s3 cp s3://jkg-s3-synapseencryptedexternalbucket-zszdd03ghnb2/ROSMAP/TWAS_CEU/FINAL_LDREF_CEU_MatchedEXP.bed . --recursive' ])
+#subprocess.Popen(CMD, shell=True).wait()
+
[…]

### 2019-10-16 code/ProcessData.Rmd
Annotate MSBB By Brain Region

@@
 unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
-wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191006.zip
-unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191006.zip
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191012.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191012.zip
 
@@
 
-## MSBB RNA-Seq: Average Across Brain Regions, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
+## MSBB RNA-Seq: Label Brain Regions, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
 ```{r MSBBRNA, results='hide', echo=TRUE, cache = FALSE}
@@
   #'@exp synID of expression data eg 'syn8485026'
-  #'@id synID of id translators  eg. 'syn6100548'
+  #'@id synID of RNA id translators  eg. 'syn6100548'
 
   DNA <- fread(syn_temp$get(dna)$path)
-  Expression <- read.table(syn_temp$get(exp)$path, header=T)
+  Expression <- read.table(syn_temp$get(exp)$path, header=T, row.names = 1)
   IDs <- fread(syn_temp$get(id)$path)
-  IDs <- IDs[ grepl( 'accepted_hits.sort.coord.bam', IDs$fileName ) == T, ]
-  IDs <- IDs[ (IDs$sampleIdentifier %in% colnames(Expression)) == T, ]
+  sink <- Expression
 
-  INDVs <- IDs$individualIdentifier[ !duplicated(IDs$individualIdentifier) ]
-
-  if( 'ensembl_gene_id' %in% colnames(Expression) ){
-    Averaged <- as.data.frame( Expression$ensembl_gene_id )
-  }else{
-    Averaged <- as.data.frame( row.names(Expression) )
-    colnames(Averaged) <- 'ensembl_gene_id'
+  #Make sample IDs the row names
+  IDs <- IDs[ IDs$Action != 'Exclude', ]
+    ###Convert to Z-Value by Tissue
+  Regions <- names( table(IDs$BrodmannArea) ) 
+  for( BM in Regions ){
+    temp <- Expression[ ,colnames(Expression)[ colnames(Expression) %in% IDs[ IDs$BrodmannArea == BM, ]$sampleIdentifier] ]
+    foo <- apply(temp, 1, scale)
+    foo <- t(foo)
+    colnames(foo) <- colnames(temp)
+    Expression[ , colnames(foo)] <- foo [, colnames(foo)]
   }
 
-  Ave <- function( ID, DF, Exp ){
-    #'@ID Sample ID eg. 'AMPAD_MSSM_0000007155'
-    #'@DF the target dataframe eg. 'IDs'
-    #'@Exp the expression set to filter eg Expression
+  IDs <- IDs[ (IDs$sampleIdentifier %in% colnames(Expression)) == T, ]
+  Expression <- Expression[ , colnames(Expression)[(colnames(Expression) %in% IDs$sampleIdentifier) == T] ]
+  INDVs <- IDs[ IDs$fileType=='fastq' , ]
 
-    Exp <- as.data.frame( Exp )
-    COLS <- DF[ DF$individualIdentifier == ID, ]$sampleIdentifier
-    Small <- Exp[ , COLS ]
+  DNA <- as.data.frame(DNA)
+  DNA[ is.na(DNA$individualIdentifier)==T,]$individualIdentifier <- DNA[ is.na(DNA$individualIdentifier)==T,]$individualIdentifier.inferred
+  DNA <- DNA[ complete.cases(DNA$individualIdentifier), ]
+  DNA <- DNA[ DNA$Action != "Exclude", ]
+  row.names(DNA) <- DNA$individualIdentifier
 
-    if( dim(as.matrix(Small))[2] > 1 ){
-      eval(parse( text = paste0( 'return( ', ID, ' = rowMeans(Small) )')))
-    }else{
-      eval(parse( text = paste0( 'return( ', ID, ' = Small)')))
-    }
-  }
+  INDVs <- IDs[ !duplicated(IDs$sampleIdentifier) ]
+  INDVs <- INDVs[ (INDVs$individualIdentifier %in% DNA$individualIdentifier) == T, ]
 
-  for( i in INDVs ){
-    eval(parse( text = paste0( 'Averaged$', i, ' <- Ave(i, IDs, Expression )') ))
-  }
+  DNA <- as.data.frame(DNA)
+  DNA <- DNA[ complete.cases(DNA$individualIdentifier), ]
+  row.names(DNA) <- DNA$individualIdentifier
 
-  GWAS_ID <- as.data.frame( DNA[ (DNA$individualIdentifier %in% colnames(Averaged)) == T , ] )
-  row.names(GWAS_ID) <- GWAS_ID$individualIdentifier
-  if( 'ensembl_gene_id' %in% colnames(Averaged) ){
-    Averaged <- Averaged[ , c( 'ensembl_gene_id', row.names(GWAS_ID) )]
-  }else{
-    Averaged <- Averaged[ , c( 'Expression$ensembl_gene_id', row.names(GWAS_ID) )]
-    colnames(Averaged[1]) <- 'ensembl_gene_id'
-  }
-  colnames(Averaged) <- paste0(GWAS_ID[ colnames(Averaged), ]$sampleIdentifier, "_", GWAS_ID[ colnames(Averaged), ]$sampleIdentifier)
-  colnames(Averaged)[1] <- "ensembl_gene_id"
-  return( Averaged )
+  INDVs <- as.data.frame(INDVs)
+  INDVs$GenoID <- DNA[ INDVs$individualIdentifier, ]$sampleIdentifier
+  INDVs$NewID <- paste0(INDVs$GenoID, '_', INDVs$BrodmannArea )
+  row.names(INDVs) <- INDVs$sampleIdentifier
+  INDVs[ colnames(Expression), ]$NewID
+
+  Expression <- Expression[ , colnames(Expression)[(colnames(Expression) %in% INDVs$sampleIdentifier) == T] ]
+  INDVs <- as.data.frame(INDVs)
+  row.names(INDVs) <- INDVs$sampleIdentifier
+  colnames(Expression) <- INDVs[ colnames(Expression), ]$NewID
+
+  return( Expression )
 }
@@
 
+  #syn <- 'syn20801991'
+  #fam <- FAM
+  #Type <- 1
+
   fam <- FAM
@@
     RNA <- cbind( 'ensembl_gene_id' = row.names(RNA), RNA[,colnames(RNA)] )
+    RNA <- RNA[ , colnames(RNA)[(grepl('_TCX', colnames(RNA))==T)] ]
   }else{
     RNA <- as.data.frame( fread( syn_temp$get(syn)$path ) )
+    row.names(RNA) <- RNA$ensembl_gene_id
+    RNA <- RNA[ , colnames(RNA)[(grepl('_TCX', colnames(RNA))==T)] ]
   }
-  RNA <- RNA[ , c('ensembl_gene_id', colnames(RNA)[(grepl('_TCX', colnames(RNA))==T)]) ]
   colnames( RNA ) <- gsub( '_TCX', '', colnames( RNA ) )
-  colnames( RNA )[2:length(colnames( RNA ))] <- paste0( '0_', colnames( RNA )[2:length(colnames( RNA ))] )
+  colnames( RNA ) <- paste0( '0_', colnames( RNA ) )
 
-  RNA <- RNA[ , c( "ensembl_gene_id", colnames(RNA)[ (colnames(RNA) %in% paste0( FAM[,1], "_", FAM[,2] )) == T ]) ]
+  ## Z-Scale
+  foo <- as.matrix(RNA)
+  foo <- apply(RNA, 1, scale)
+  foo <- t(foo)
+  colnames(foo) <- colnames(RNA)
+  #Expression[ , colnames(foo)] <- foo [, colnames(foo)]
+
+  RNA <- foo[ , colnames(foo)[ (colnames(foo) %in% paste0( FAM[,1], "_", FAM[,2] )) == T ] ]
   return(RNA)
@@
 
+  ## Z-Scale
+  row.names( Exp ) <- Exp$ensembl_gene_id
+  Exp <- Exp[ , (colnames( Exp ) %in% "ensembl_gene_id") == F ]
+  foo <- as.matrix(Exp)
+  foo <- apply(Exp, 1, scale)
+  foo <- t(foo)
+  colnames(foo) <- colnames(Exp)
+
   #Filter for matched RNA-Seq and GWAS samples
-  Exp <- Exp[ ,c('ensembl_gene_id', colnames(Exp)[ (colnames(Exp) %in% Trans$rnaseq_id) == T]) ]
+  Exp <- foo[ , colnames(foo)[ (colnames(foo) %in% Trans$rnaseq_id) == T] ]
   Trans <- as.data.frame( Trans[ (Trans$rnaseq_id %in% colnames(Exp)) == T,  ] )
@@
 
-  colnames(Exp) <- c('ensembl_gene_id', paste0( Trans[colnames(Exp)[2:length(colnames(Exp))],]$gwas_id, "_",  Trans[colnames(Exp)[2:length(colnames(Exp))],]$gwas_id))
+  colnames(Exp) <- c( paste0( Trans[colnames(Exp)[1:length(colnames(Exp))],]$gwas_id, "_",  Trans[colnames(Exp)[1:length(colnames(Exp))],]$gwas_id))
   return(Exp)
@@
 #Common Genes:
-GNames <- names( table(c( as.character(Norm_Resid_MSBB$ensembl_gene_id), as.character(Norm_Resid_MAYO$ensembl_gene_id), as.character(Norm_Resid_RM$ensembl_gene_id)  ))[ table(c( as.character(Norm_Resid_MSBB$ensembl_gene_id), as.character(Norm_Resid_MAYO$ensembl_gene_id), as.character(Norm_Resid_RM$ensembl_gene_id)  )) == 3] )
+GNames <- names( table(c( row.names(Norm_Resid_MSBB), row.names(Norm_Resid_MAYO), row.names(Norm_Resid_RM)  ))[ table(c( row.names(Norm_Resid_MSBB), row.names(Norm_Resid_MAYO), row.names(Norm_Resid_RM)  )) == 3] )
 
@@
 
-  row.names(MSBB) <- as.character(MSBB$ensembl_gene_id)
-  row.names(Mayo) <- as.character(Mayo$ensembl_gene_id)
-  row.names(RM) <- as.character(RM$ensembl_gene_id)
+  #row.names(MSBB) <- as.character(MSBB$ensembl_gene_id)
+  #row.names(Mayo) <- as.character(Mayo$ensembl_gene_id)
+  #row.names(RM) <- as.character(RM$ensembl_gene_id)
 
@@
 
-#Filter out the ~ 480 ChrX genes
-Norm_Resid <- Norm_Resid[ (Norm_Resid$Chr %in% 'X') == F, ]
-Diag_Resid <- Diag_Resid[ (Diag_Resid$Chr %in% 'X') == F, ]
+#Filter out the ~ ChrX, MT, and Patch genes
+Norm_Resid <- Norm_Resid[ (as.character(Norm_Resid$Chr) %in% c('MT', 'X', as.character(Norm_Resid$Chr)[ grepl('PATCH', as.character(Norm_Resid$Chr)) == T])) == F, ]
+Diag_Resid <- Diag_Resid[ (as.character(Diag_Resid$Chr) %in% c('MT', 'X', as.character(Diag_Resid$Chr)[ grepl('PATCH', as.character(Diag_Resid$Chr)) == T])) == F, ]
 
@@
 write.table(FAM, file='New_Fam.fam', row.names = F, col.names=F, quote=F, sep=" ")
+
+tail(FAM[ FAM$V1[ grepl('ROS', FAM$V1) == F ] $ FAM$V1[ grepl('MAP', FAM$V1) == F ] ,])
+# & FAM$V1[ grepl('ROS', FAM$V1) == F ]
+MSBB_List <- FAM[ FAM$V1 != '0', ] 
+MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('MAP', MSBB_List$V1) == F ] ,]
+MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('ROS', MSBB_List$V1) == F ] ,]
+write.table( MSBB_List[,1:2], file="MSBB_SamplesToExpand.txt", quote = F, row.names = F, col.names = F, sep = "\t" )
 ```
@@
 #source /root/.bashrc
-PATH=$PATH:~/TWAS/bin/
+export PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
@@
 mv New_Fam.fam CEU_AncestryMatched_Genotypes.fam
+
+#Extract the MSBB Samples to duplicate and rename to match tissues
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep MSBB_SamplesToExpand.txt --recode --out MSBB_Intermediate
+
+#Repeat the rows in the ped file 4 times
+awk '{for(i=0;i<4;i++)print}' MSBB_Intermediate.ped > temp
+
+gawk -v m=1 -v n=2 -v el='BM10' 'NR % m == 0 { $n = el } 1' temp > foo
+gawk -v m=2 -v n=2 -v el='BM22' 'NR % m == 0 { $n = el } 1' foo > temp
+gawk -v m=3 -v n=2 -v el='BM36' 'NR % m == 0 { $n = el } 1' temp > foo
+gawk -v m=4 -v n=2 -v el='BM44' 'NR % m == 0 { $n = el } 1' foo > temp
+mv temp MSBB_Intermediate.ped
+rm foo
+
+plink --threads $CORES --file MSBB_Intermediate --make-bed --out MSBB_Expanded
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --bmerge MSBB_Expanded --make-bed --out Rebuilt
+plink --threads $CORES --bfile Rebuilt --make-bed --out CEU_AncestryMatched_Genotypes
+
+rm Rebuilt.*
+rm MSBB_Expanded.*
 

### 2019-10-16 code/ProcessData.Rmd
Finalize Process

@@
 
-tail(FAM[ FAM$V1[ grepl('ROS', FAM$V1) == F ] $ FAM$V1[ grepl('MAP', FAM$V1) == F ] ,])
+#tail(FAM[ FAM$V1[ grepl('ROS', FAM$V1) == F ] $ FAM$V1[ grepl('MAP', FAM$V1) == F ] ,])
 # & FAM$V1[ grepl('ROS', FAM$V1) == F ]
@@
 rm *.tsv
+rm MSBB_SamplesToExpand.txt
+rm *.map
+rm *.ped
 ```

### 2019-10-18 code/TestFusion.Rmd
Add Fusion Test Script

---
title: "Test Fusion"
author: "JKG"
date: "10/18/2019"
output: pdf_document
  chunk_output_type: console
---

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')
#library(reticulate)
```
##Before running 
Run the following in docker exec -it <CONTAINER> /bin/bash 
chmod 777 /root/
mv TWAS/ /home/<USR>/TWAS/
chown -hR <GID>:<USR> /home/<USR>/TWAS/
Create a ~/.synapseConfig file in the container, but do not push a container containing your credentials file to Docker Hub!!!

## Login to Synapse Will need to replace with your credentials
```{bash Login, echo=T, results='hide', eval=FALSE}
#source /root/.bashrc
synapse login -u <USR> -p <PSWD> --rememberMe
#apt-get install gfortran
apt-get install -y --no-install-recommends apt-utils libblas-dev liblapack-dev gfortran aptitude build-essential libcurl4-openssl-dev libxml2-dev libxml2-dev libssl-dev nano python-dev plink git curl

#Alternativly you can setup a credentials file as such:
touch ~/.synapseConfig
echo "[authentication]" >> ~/.synapseConfig
echo "username = <USR>" >> ~/.synapseConfig
echo "password = <PASWD>" >> ~/.synapseConfig
```

```{bash SetUp, echo=T, results='hide', eval=FALSE}

mkdir ~/TWAS/bin

wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20190617.zip 
unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191015.zip
unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191015.zip

rm ~/TWAS/bin/*.zip
rm ~/TWAS/bin/toy.*
rm ~/TWAS/bin/LICENSE

cd ~/TWAS/bin

wget https://github.com/genetics-statistics/GEMMA/releases/download/0.98.1/gemma-0.98.1-linux-static.gz 
gunzip gemma-0.98.1-linux-static.gz
chmod 777 gemma-0.98.1-linux-static

git clone https://github.com/bulik/ldsc.git

wget http://zzz.bwh.harvard.edu/plink/dist/plink-1.07-x86_64.zip
unzip plink-1.07-x86_64.zip

wget https://cnsgenomics.com/software/gcta/bin/gcta_1.92.4beta.zip
unzip gcta_1.92.4beta.zip

wget https://data.broadinstitute.org/alkesgroup/FUSION/LDREF.tar.bz2 
tar xjvf LDREF.tar.bz2

cd ~/TWAS/code
synapse get syn20835005
synapse get syn20835007
synapse get syn20834996

synapse get syn21011186

##MAKE the test transcription file
head -n 1 ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv > Test_Transcription.tsv

grep 'ENSG00000259431' ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv >> Test_Transcription.tsv
grep 'ENSG00000215788' ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv >> Test_Transcription.tsv
grep 'ENSG00000162825' ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv >> Test_Transcription.tsv
grep 'ENSG00000166135' ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv >> Test_Transcription.tsv
grep 'ENSG00000162636' ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv >> Test_Transcription.tsv

head -n 1 ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv | awk '{$1=$2=$3=$4=""; print $0}' - > Foo.txt
tr ' ' '\n' < Foo.txt > Poo.txt
tr '_' '\t' < Poo.txt > Foo.txt
awk '{ print $1"_"$2"\t"$2 }' Foo.txt > ~/TWAS/bin/Total_IDs.txt
rm Foo.txt
rm Poo.txt
```

```{python SetUp, echo=T}
import sys
import os
import re
import subprocess32 as subprocess
import multiprocessing as mp
from multiprocessing.pool import ThreadPool
import datetime
import shlex, subprocess

#Set All Configurations
GCTA='~/TWAS/bin/gcta_1.92.4beta/gcta64'
PLINK='~/TWAS/bin/plink2'
#v1.07
PLINKa='~/TWAS/bin/plink-1.07-x86_64/plink'
#PLINKa='~/TWAS/bin/plink'
#v1.90
#PLIN='~/TWAS/bin/plink-1.07-x86_64/plink'
PLIN='~/TWAS/bin/plink'
GEMMA="~/TWAS/bin/gemma-0.98.1-linux-static"
LDREF='~/TWAS/bin/LDREF'

INDV_ID='~/TWAS/bin/Total_IDs.txt'
#PATH TO OUTPUT DIRECTORY (population-specific subdirs will be made)
OUT_DIR='All_Data'

BATCH_START='1'
BATCH_END='6'
NR='1_6'

CMD = 'mkdir Genos'
subprocess.Popen(CMD, shell=True).wait()

for C in range(1,23):
        #split by chr
        CMD = ''.join([ PLIN, ' --bfile All_CEU_ToTrainForTWAS --keep ', str(INDV_ID), ' --chr ', str(C), ' --threads 72 --make-bed --out Genos/AMP-AD_ROSMAP_Imputed_chr', str(C) ])
        subprocess.Popen(CMD, shell=True).wait()

CMD = ''.join([ 'mkdir All_Data' ])
subprocess.Popen(CMD, shell=True).wait()

# Make the neccesary file paths below the run directory
CMD = ''.join([ 'mkdir temp_pheno' ])
subprocess.Popen(CMD, shell=True).wait()

CMD = ''.join([ 'mkdir All_Data/Genotype' ])
subprocess.Popen(CMD, shell=True).wait()

CMD = ''.join([ 'mkdir All_Data/WEIGHTS' ])
subprocess.Popen(CMD, shell=True).wait()

#CMD = ''.join([ 'mkdir tmp/', str(NR), '/netResidual_Chrom_Expression/' ])
#subprocess.Popen(CMD, shell=True).wait()
CMD = 'mkdir  --parents All_Data/ALL/netResidual_Chrom_Expression'
subprocess.Popen(CMD, shell=True).wait()

CMD = ''.join([ 'mkdir --parents tmp/', str(NR), '/netResidual_Chrom_Expression/' ])
subprocess.Popen(CMD, shell=True).wait()
CMD = ''.join([ 'mkdir --parents hsq/', str(NR), '/netResidual_Chrom_Expression/' ])
subprocess.Popen(CMD, shell=True).wait()
CMD = ''.join([ 'mkdir --parents out/', str(NR), '/netResidual_Chrom_Expression/' ])
subprocess.Popen(CMD, shell=True).wait()

# THIS IS DIRECTORY WHERE THE OUTPUT WILL GO:
CMD = ''.join([ 'mkdir --parents ', str(OUT_DIR) ])
subprocess.Popen(CMD, shell=True).wait()

#CMD = ''.join(['mkdir ', str(OUT_DIR), '/ALL/' ])
#subprocess.Popen(CMD, shell=True).wait()
```

```{python SetUp2, echo=T}
import sys
import os
import re
import subprocess32 as subprocess
import multiprocessing as mp
from multiprocessing.pool import ThreadPool
import datetime
import shlex, subprocess

#Set All Configurations
GCTA='~/TWAS/bin/gcta_1.92.4beta/gcta64'
PLINK='~/TWAS/bin/plink2'
#v1.07
PLINKa='~/TWAS/bin/plink-1.07-x86_64/plink'
#PLINKa='~/TWAS/bin/plink'
#v1.90
#PLIN='~/TWAS/bin/plink-1.07-x86_64/plink'
PLIN='~/TWAS/bin/plink'

GEMMA="~/TWAS/bin/gemma-0.98.1-linux-static"
LDREF='~/TWAS/bin/LDREF'

INDV_ID='~/TWAS/bin/Total_IDs.txt'
#PATH TO OUTPUT DIRECTORY (population-specific subdirs will be made)
OUT_DIR='All_Data'

BATCH_START='1'
BATCH_END='6'
NR='1_6'

INPT = str('Test_Transcription.tsv')
skip = 1
F1 = open(INPT)
for line in F1:
  #if( 'TSS' in str(line) ):
  if( skip == 1 ):
    skip+=1
    pass
  else:
    LINE = line.rstrip('\r\n')
    lst = LINE.split('\t')

    CHR=lst[2]
    C=lst[2]

    #Define the genomic region of SNPs around the gene
    if(int(lst[3]) < 500000):
      P0 = 1
    else:
      P0=int(lst[3])-500000

    P1=int(lst[3])+500000
    GNAME=lst[1]

    OUT=''.join([ 'tmp/', str(NR), '/netResidual_Chrom_Expression/CEU_AncestralMapped_chr', str(C), '.tsv', '.', GNAME ])
    PRE_GENO = ''.join([ 'Genos/AMP-AD_ROSMAP_Imputed_chr', str(C) ])
    PRE_GEXP=str('Test_Transcription.tsv')

    #time log Start
    dt_started = datetime.datetime.utcnow()

    #Pull Gene Expression
    CMD = ''.join([ 'cp ', INDV_ID,' temp_pheno/', str(GNAME), '_foo.txt' ])
    subprocess.Popen(CMD, shell=True).wait()

    #Pull Gene Expression
    CMD = ''.join([ 'grep ', str(GNAME), ' ', str(PRE_GEXP), ' | sed \'s/\\t/\\n/g\' | sed 1,4d | paste temp_pheno/', str(GNAME), '_foo.txt - > ', str(OUT), '.pheno' ])
    #print CMD
    subprocess.Popen(CMD, shell=True).wait()

    #Pull The Genotype Data
    CMD = ''.join([ str(PLIN), ' --bfile ', str(PRE_GENO), ' --pheno ', str(OUT), '.pheno --make-bed --keep ', str(OUT), '.pheno --threads 8 --silent --chr ', str(C), ' --from-bp ', str(P0), ' --to-bp ', str(P1), ' --extract ', str(LDREF), '/1000G.EUR.', str(C), '.bim --out ', str(OUT), '.filt' ])
    #print CMD
    subprocess.Popen(CMD, shell=True).wait()

    #Make the Geno-typing data
    FINAL_OUT = ''.join([ str(OUT_DIR), '/ALL/', str(GNAME) ])

    #Run the Modified Weights Calculations
    CMD = ''.join([ 'Rscript FUSION.compute_weights_Parallel.R --bfile ', str(OUT), '.filt --tmp ', str(OUT), ' --out ', str(FINAL_OUT), ' --verbose 0 --save_hsq --noclean --hsq_p 0.01 --PATH_plink ', str(PLIN), ' --PATH_gcta ', str(GCTA), ' --PATH_gemma ', str(GEMMA), ' --models blup,bslmm,lasso,top1,enet' ])
    print CMD

```

Rscript FUSION.compute_weights_Parallel.R --bfile tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr14.tsv.ENSG00000259431.filt --tmp tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr14.tsv.ENSG00000259431 --out All_Data/ALL/ENSG00000259431 --verbose 0 --save_hsq --noclean --hsq_p 0.01 --PATH_plink ~/TWAS/bin/plink-1.07-x86_64/plink --PATH_gcta ~/TWAS/bin/gcta_1.92.4beta/gcta64 --PATH_gemma ~/TWAS/bin/gemma-0.98.1-linux-static --models blup,bslmm,lasso,top1,enet

Rscript FUSION.compute_weights_Parallel.R --bfile tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000215788.filt --tmp tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000215788 --out All_Data/ALL/ENSG00000215788 --verbose 0 --save_hsq --noclean --hsq_p 0.01 --PATH_plink ~/TWAS/bin/plink-1.07-x86_64/plink --PATH_gcta ~/TWAS/bin/gcta_1.92.4beta/gcta64 --PATH_gemma ~/TWAS/bin/gemma-0.98.1-linux-static --models blup,bslmm,lasso,top1,enet

Rscript FUSION.compute_weights_Parallel.R --bfile tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000162825.filt --tmp tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000162825 --out All_Data/ALL/ENSG00000162825 --verbose 0 --save_hsq --noclean --hsq_p 0.01 --PATH_plink ~/TWAS/bin/plink-1.07-x86_64/plink --PATH_gcta ~/TWAS/bin/gcta_1.92.4beta/gcta64 --PATH_gemma ~/TWAS/bin/gemma-0.98.1-linux-static --models blup,bslmm,lasso,top1,enet

Rscript FUSION.compute_weights_Parallel.R --bfile tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr10.tsv.ENSG00000166135.filt --tmp tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr10.tsv.ENSG00000166135 --out All_Data/ALL/ENSG00000166135 --verbose 0 --save_hsq --noclean --hsq_p 0.01 --PATH_plink ~/TWAS/bin/plink-1.07-x86_64/plink --PATH_gcta ~/TWAS/bin/gcta_1.92.4beta/gcta64 --PATH_gemma ~/TWAS/bin/gemma-0.98.1-linux-static --models blup,bslmm,lasso,top1,enet

Rscript FUSION.compute_weights_Parallel.R --bfile tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000162636.filt --tmp tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000162636 --out All_Data/ALL/ENSG00000162636 --verbose 0 --save_hsq --noclean --hsq_p 0.01 --PATH_plink ~/TWAS/bin/plink-1.07-x86_64/plink --PATH_gcta ~/TWAS/bin/gcta_1.92.4beta/gcta64 --PATH_gemma ~/TWAS/bin/gemma-0.98.1-linux-static --models blup,bslmm,lasso,top1,enet

```{r FUSION, echo=T}
# ==== TODO
# * Make sure BLUP/BSLMM weights are being scaled properly based on MAF

suppressMessages(library("optparse"))
suppressMessages(library('plink2R'))
suppressMessages(library('glmnet'))
suppressMessages(library('methods'))

option_list = list(
  make_option("--bfile", action="store", default=NA, type='character',
              help="Path to PLINK binary input file prefix (minus bed/bim/fam) [required]"),
  make_option("--out", action="store", default=NA, type='character',
              help="Path to output files [required]"),
  make_option("--tmp", action="store", default=NA, type='character',
              help="Path to temporary files [required]"),
  make_option("--pheno", action="store", default=NA, type='character',
              help="Path to molecular phenotype file (PLINK format) [optional, taken from bfile otherwise]"),
  make_option("--PATH_plink", action="store", default="plink", type='character',
              help="Path to plink executable [%default]"),
  make_option("--PATH_gcta", action="store", default="gcta_nr_robust", type='character',
              help="Path to plink executable [%default]"),
  make_option("--PATH_gemma", action="store", default="gemma", type='character',
              help="Path to plink executable [%default]"),
  make_option("--covar", action="store", default=NA, type='character',
              help="Path to quantitative covariates (PLINK format) [optional]"),
  make_option("--resid", action="store_true", default=FALSE,
              help="Also regress the covariates out of the genotypes [default: %default]"),              
  make_option("--hsq_p", action="store", default=0.01, type='double',
              help="Minimum heritability p-value for which to compute weights [default: %default]"),
  make_option("--hsq_set", action="store", default=NA, type='double',
              help="Skip heritability estimation and set hsq estimate to this value [optional]"),
  make_option("--crossval", action="store", default=5, type='double',
              help="How many folds of cross-validation, 0 to skip [default: %default]"),
  make_option("--verbose", action="store", default=1, type="integer",
              help="How much chatter to print: 0=nothing; 1=minimal; 2=all [default: %default]"),
  make_option("--noclean", action="store_true", default=FALSE,
              help="Do not delete any temporary files (for debugging) [default: %default]"),
  make_option("--rn", action="store_true", default=FALSE,
              help="Rank-normalize the phenotype after all QC: [default: %default]"),
  make_option("--save_hsq", action="store_true", default=FALSE,
              help="Save heritability results even if weights are not computed [default: %default]"),			  
  make_option("--models", action="store", default="blup,lasso,top1,enet", type='character',
              help="Comma-separated list of prediction models [default: %default]\n
					Available models:\n
					top1:\tTop eQTL (standard marginal eQTL Z-scores always computed and stored)\n
					blup:\t Best Unbiased Linear Predictor (dual of ridge regression)\n
					bslmm:\t Bayesian Sparse Linear Model (spike/slab MCMC)\n
					lasso:\t LASSO regression (with heritability used as lambda)\n
					enet:\t Elastic-net regression (with mixing parameter of 0.5)\n")
)

opt = parse_args(OptionParser(option_list=option_list))

#############################################################
opt = list( bfile= 'tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000162636.filt',
            out = 'All_Data/ALL/ENSG00000162636',
            tmp = 'tmp/1_6/netResidual_Chrom_Expression/CEU_AncestralMapped_chr1.tsv.ENSG00000162636',
            pheno = NA,
            PATH_plink = '~/TWAS/bin/plink-1.07-x86_64/plink',
            PATH_gcta  = '~/TWAS/bin/gcta_1.92.4beta/gcta64 ',
            PATH_gemma = "~/TWAS/bin/gemma-0.98.1-linux-static",
            covar = NA,
            resid = FALSE,
            hsq_p = 0.01,
            hsq_set = NA,
            crossval = 5,
            verbose = 0,
            noclean = TRUE,
            rn = FALSE,
            save_hsq = TRUE,
            models = "blup,bslmm,lasso,top1,enet")

models = unique( c(unlist(strsplit(opt$models,',')),"top1") )
M = length(models)

if ( opt$verbose == 2 ) {
  SYS_PRINT = F
} else {
  SYS_PRINT = T
}

# --- PREDICTION MODELS

# BSLMM
weights.bslmm = function( input , bv_type , snp , out=NA ) {
	if ( is.na(out) ) out = paste(input,".BSLMM",sep='')

	String <- strsplit(out, '/')[[1]]
        outE <- String[ length(String) ]
        outpref <- paste( String[ 1:(length(String)-1) ], collapse = '/' )

        arg = paste( opt$PATH_gemma , " -miss 1 -maf 0 -r2 1 -rpace 1000 -wpace 1000 -bfile " , input , " -bslmm " , bv_type ," -outdir ", outpref, " -o " , outE , sep='' )

	#arg = paste( opt$PATH_gemma , " -miss 1 -maf 0 -r2 1 -rpace 1000 -wpace 1000 -bfile " , input , " -bslmm " , bv_type , " -o " , out , sep='' )
	system( arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)
	eff = read.table( paste(out,".param.txt",sep=''),head=T,as.is=T)
	eff.wgt = rep(NA,length(snp))
	m = match( snp , eff$rs )
	m.keep = !is.na(m)
	m = m[m.keep]
	eff.wgt[m.keep] = (eff$alpha + eff$beta * eff$gamma)[m]
	return( eff.wgt )
}

# PLINK: LASSO
weights.lasso = function( input , hsq , snp , out=NA ) {
	if ( is.na(out) ) out = paste(input,".LASSO",sep='')

	arg = paste( opt$PATH_plink , " --allow-no-sex --bfile " , input , " --lasso " , hsq , " --threads 5 --silent --out " , out , sep='' )
	system( arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT )
	if ( !file.exists(paste(out,".lasso",sep='')) ) {
	cat( paste(out,".lasso",sep='') , " LASSO output did not exist\n" )
	eff.wgt = rep(NA,length(snp))
	} else {
	eff = read.table( paste(out,".lasso",sep=''),head=T,as.is=T)
	eff.wgt = rep(0,length(snp))
	m = match( snp , eff$SNP )
	m.keep = !is.na(m)	
	m = m[m.keep]
	eff.wgt[m.keep] = eff$EFFECT[m]
	}
	return( eff.wgt )
}

# Marginal Z-scores (used for top1)
weights.marginal = function( genos , pheno , beta=F ) {
	if ( beta ) eff.wgt = t( genos ) %*% (pheno) / ( nrow(pheno) - 1)
	else eff.wgt = t( genos ) %*% (pheno) / sqrt( nrow(pheno) - 1 )
	return( eff.wgt )
}

# Elastic Net
weights.enet = function( genos , pheno , alpha=0.5 ) {
	eff.wgt = matrix( 0 , ncol=1 , nrow=ncol(genos) )
	# remove monomorphics
	sds = apply( genos  , 2 , sd )
	keep = sds != 0 & !is.na(sds)
	#_# Added parallel = T
	enet = cv.glmnet( x=genos[,keep] , parallel=T, y=pheno , alpha=alpha , nfold=5 , intercept=T , standardize=F )
	eff.wgt[ keep ] = coef( enet , s = "lambda.min")[2:(sum(keep)+1)]
	return( eff.wgt )
}

# --- CLEANUP
cleanup = function() {
	if ( ! opt$noclean ) {
		arg = paste("rm -f " , opt$tmp , "*", sep='')
		system(arg)
	}
}

# Perform i/o checks here:
files = paste(opt$bfile,c(".bed",".bim",".fam"),sep='')
if ( !is.na(opt$pheno) ) files = c(files,opt$pheno)
if ( !is.na(opt$covar) ) files = c(files,opt$covar)

for ( f in files ) {
	if ( !file.exists(f) ){
		cat( "ERROR: ", f , " input file does not exist\n" , sep='', file=stderr() )
		cleanup()
		q()
	}
}

if ( system( paste(opt$PATH_plink,"--help") , ignore.stdout=T,ignore.stderr=T ) != 0 ) {
	cat( "ERROR: plink could not be executed, set with --PATH_plink\n" , sep='', file=stderr() )
	cleanup()
	q()
}

if ( !is.na(opt$hsq_set) && system( opt$PATH_gcta , ignore.stdout=T,ignore.stderr=T ) != 0 ){
	cat( "ERROR: gcta could not be executed, set with --PATH_gcta\n" , sep='', file=stderr() )
	cleanup()
	q()
}

if ( sum(models=="bslmm" | models=="blup") != 0 && system( paste(opt$PATH_gemma,"-h") , ignore.stdout=T,ignore.stderr=T ) != 0 ){
	cat( "ERROR: gemma could not be executed, set with --PATH_gemma or remove 'bslmm' and 'blup' from models\n" , sep='', file=stderr() )
	cleanup()
	q()
}
# ---

fam = read.table(paste(opt$bfile,".fam",sep=''),as.is=T)

# Make/fetch the phenotype file
if ( !is.na(opt$pheno) ) {
	pheno.file = opt$pheno
	pheno = read.table(pheno.file,as.is=T)
	# Match up data
	m = match( paste(fam[,1],fam[,2]) , paste(pheno[,1],pheno[,2]) )
	m.keep = !is.na(m)
	fam = fam[m.keep,]
	m = m[m.keep]
	pheno = pheno[m,]
} else {
	pheno.file = paste(opt$tmp,".pheno",sep='')
	pheno = fam[,c(1,2,6)]
	write.table(pheno,quote=F,row.names=F,col.names=F,file=pheno.file)
}

if ( opt$rn ) {
	library('GenABEL')
	library(preprocessCore)
	pheno[,3] = rntransform( pheno[,3] )
	write.table(pheno,quote=F,row.names=F,col.names=F,file=pheno.file)
}

# Load in the covariates if needed
if ( !is.na(opt$covar) ) {
	covar = ( read.table(opt$covar,as.is=T,head=T) )
	if ( opt$verbose >= 1 ) cat( "Loaded",ncol(covar)-2,"covariates\n")
	# Match up data
	m = match( paste(fam[,1],fam[,2]) , paste(covar[,1],covar[,2]) )
	m.keep = !is.na(m)
	fam = fam[m.keep,]
	pheno = pheno[m.keep,]
	m = m[m.keep]
	covar = covar[m,]
	reg = summary(lm( pheno[,3] ~ as.matrix(covar[,3:ncol(covar)]) ))
	if ( opt$verbose >= 1 ) cat( reg$r.sq , "variance in phenotype explained by covariates\n" )

	#_#JKG Pheno RNA-Seq Data input is already Scaled may need to remove if this scales the expression!
	pheno[,3] = scale(reg$resid)
	raw.pheno.file = pheno.file
	pheno.file = paste(pheno.file,".resid",sep='')
	write.table(pheno,quote=F,row.names=F,col.names=F,file=pheno.file)
}

geno.file = opt$tmp
# recode to the intersection of samples and new phenotype
arg = paste( opt$PATH_plink ," --allow-no-sex --bfile ",opt$bfile," --pheno ",pheno.file," --keep ",pheno.file," --threads 5 --silent --make-bed --out ",geno.file,sep='')
system(arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)

# --- HERITABILITY ANALYSIS
if ( is.na(opt$hsq_set) ) {
if ( opt$verbose >= 1 ) cat("### Estimating heritability\n")

# 1. generate GRM
arg = paste( opt$PATH_plink," --allow-no-sex --bfile ",opt$tmp," --make-grm-bin --threads 5 --silent --out ",opt$tmp,sep='')
system(arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)

# 2. estimate heritability
if ( !is.na(opt$covar) ) {
arg = paste( opt$PATH_gcta ," --grm ",opt$tmp," --pheno ",raw.pheno.file," --qcovar ",opt$covar," --out ",opt$tmp," --reml --reml-no-constrain --reml-lrt 1",sep='')
} else {
arg = paste( opt$PATH_gcta ," --grm ",opt$tmp," --pheno ",pheno.file," --out ",opt$tmp," --reml --reml-no-constrain --reml-lrt 1",sep='')
}
system(arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)

# 3. evaluate LRT and V(G)/Vp
if ( !file.exists( paste(opt$tmp,".hsq",sep='') ) ) {
	cat(opt$tmp,"does not exist, likely GCTA could not converge, skipping gene\n",file=stderr())
	cleanup()
	q()
}

hsq.file = read.table(file=paste(opt$tmp,".hsq",sep=''),as.is=T,fill=T)
hsq = as.numeric(unlist(hsq.file[hsq.file[,1] == "V(G)/Vp",2:3]))
hsq.pv = as.numeric(unlist(hsq.file[hsq.file[,1] == "Pval",2]))

if ( opt$verbose >= 1 ) cat("Heritability (se):",hsq,"LRT P-value:",hsq.pv,'\n')
if ( opt$save_hsq ) cat( opt$out , hsq , hsq.pv , '\n' , file=paste(opt$out,".hsq",sep='') )

# 4. stop if insufficient
if ( hsq[1] < 0 || hsq.pv > opt$hsq_p ) {
	cat(opt$tmp," : heritability ",hsq[1],"; LRT P-value ",hsq.pv," : skipping gene\n",sep='',file=stderr())
	cleanup()
	q()
}

} else {
if ( opt$verbose >= 1 ) cat("### Skipping heritability estimate\n")
hsq = opt$hsq_set
hsq.pv = NA
}

# read in genotypes
genos = read_plink(geno.file,impute="avg")
mafs = apply(genos$bed,2,mean)/2
sds = apply(genos$bed,2,sd)
# important : genotypes are standardized and scaled here:
genos$bed = scale(genos$bed)
pheno = genos$fam[,c(1,2,6)]
#_#JKG Pheno RNA-Seq Data input is already Scaled may need to remove if this scales the expression!
pheno[,3] = scale(pheno[,3])

# check if any genotypes are NA
nasnps = apply( is.na(genos$bed) , 2 , sum )
if ( sum(nasnps) != 0 ) {
	cat( "WARNING :",sum(nasnps != 0),"SNPs could not be scaled and were zeroed out, make sure all SNPs are polymorphic\n" , file=stderr())
	genos$bed[,nasnps != 0] = 0
}

# regress covariates out of the genotypes as well (this is more accurate but slower)
if ( !is.na(opt$covar) && opt$resid ) {
	if ( opt$verbose >= 1 ) cat("regressing covariates out of the genotypes\n")
	for ( i in 1:ncol(genos$bed) ) {
		genos$bed[,i] = summary(lm( genos$bed[,i] ~ as.matrix(covar[,3:ncol(covar)]) ))$resid
	}
	genos$bed = scale(genos$bed)
}

N.tot = nrow(genos$bed)
if ( opt$verbose >= 1 ) cat(nrow(pheno),"phenotyped samples, ",nrow(genos$bed),"genotyped samples, ",ncol(genos$bed)," markers\n")

# --- CROSSVALIDATION ANALYSES
set.seed(1)
cv.performance = matrix(NA,nrow=2,ncol=M)
rownames(cv.performance) = c("rsq","pval")
colnames(cv.performance) = models

if ( opt$crossval <= 1 ) {
if ( opt$verbose >= 1 ) cat("### Skipping cross-validation\n")
} else {
if ( opt$verbose >= 1 ) cat("### Performing",opt$crossval,"fold cross-validation\n")
cv.all = pheno
N = nrow(cv.all)
cv.sample = sample(N)
cv.all = cv.all[ cv.sample , ]
folds = cut(seq(1,N),breaks=opt$crossval,labels=FALSE)

cv.calls = matrix(NA,nrow=N,ncol=M)

for ( i in 1:opt$crossval ) {
	if ( opt$verbose >= 1 ) cat("- Crossval fold",i,"\n")
	indx = which(folds==i,arr.ind=TRUE)
	cv.train = cv.all[-indx,]
	# store intercept
	intercept = mean( cv.train[,3] )
	#_#JKG Pheno RNA-Seq Data input is already Scaled may need to remove if this scales the expression!
	cv.train[,3] = scale(cv.train[,3])

	# hide current fold
	cv.file = paste(opt$tmp,".cv",sep='')
	write.table( cv.train , quote=F , row.names=F , col.names=F , file=paste(cv.file,".keep",sep=''))	
	arg = paste( opt$PATH_plink ," --allow-no-sex --bfile ",opt$tmp," --keep ",cv.file,".keep --threads 5 --silent --out ",cv.file," --make-bed",sep='')
	system(arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)

	for ( mod in 1:M ) {
		if ( models[mod] == "blup" ) {
			pred.wgt = weights.bslmm( cv.file , bv_type=2 , snp=genos$bim[,2] )
		}
		else if ( models[mod] == "bslmm" ) {
			pred.wgt = weights.bslmm( cv.file , bv_type=1 , snp=genos$bim[,2] )
		}		
		else if ( models[mod] == "lasso" ) {
			pred.wgt = weights.lasso( cv.file , hsq[1] , snp=genos$bim[,2] )
		}
		else if ( models[mod] == "enet" ) {
			pred.wgt = weights.enet( genos$bed[ cv.sample[ -indx ],] , as.matrix(cv.train[,3]) , alpha=0.5 )
		}		
		else if ( models[mod] == "top1" ) {
			pred.wgt = weights.marginal( genos$bed[ cv.sample[ -indx ],] , as.matrix(cv.train[,3,drop=F]) , beta=T )
			pred.wgt[ - which.max( pred.wgt^2 ) ] = 0
		}

		# predict from weights into sample
		pred.wgt[ is.na(pred.wgt) ] = 0
		cv.calls[ indx , mod ] = genos$bed[ cv.sample[ indx ] , ] %*% pred.wgt
	}
}

# compute rsq + P-value for each model
for ( mod in 1:M ) {
	if ( !is.na(sd(cv.calls[,mod])) && sd(cv.calls[,mod]) != 0 ) {
		reg = summary(lm( cv.all[,3] ~ cv.calls[,mod] ))
		cv.performance[ 1, mod ] = reg$adj.r.sq
		cv.performance[ 2, mod ] = reg$coef[2,4]
	} else {
		cv.performance[ 1, mod ] = NA
		cv.performance[ 2, mod ] = NA
	}
}
if ( opt$verbose >= 1 ) write.table(cv.performance,quote=F,sep='\t')
}

# --- FULL ANALYSES
if ( opt$verbose >= 1 ) cat("Computing full-sample weights\n")

# call models to get weights
wgt.matrix = matrix(0,nrow=nrow(genos$bim),ncol=M)
colnames(wgt.matrix) = models
rownames(wgt.matrix) = genos$bim[,2]
for ( mod in 1:M ) {
	if ( models[mod] == "blup" ) {
		wgt.matrix[,mod] = weights.bslmm( geno.file , bv_type=2 , snp=genos$bim[,2] , out=opt$tmp )
	}
	else if ( models[mod] == "bslmm" ) {
		wgt.matrix[,mod] = weights.bslmm( geno.file , bv_type=1 , snp=genos$bim[,2] , out=opt$tmp )
	}		
	else if ( models[mod] == "lasso" ) {
		wgt.matrix[,mod] = weights.lasso( geno.file , hsq[1] , snp=genos$bim[,2] , out=opt$tmp )
	}
	else if ( models[mod] == "enet" ) {
		wgt.matrix[,mod] = weights.enet( genos$bed , as.matrix(pheno[,3]) , alpha=0.5 )
	}	
	else if ( models[mod] == "top1" ) {
		wgt.matrix[,mod] = weights.marginal( genos$bed , as.matrix(pheno[,3]) , beta=F )
	}
}

# save weights, rsq, p-value for each model, and hsq to output
snps = genos$bim
save( wgt.matrix , snps , cv.performance , hsq, hsq.pv, N.tot , file = paste( opt$out , ".wgt.RDat" , sep='' ) )
# --- CLEAN-UP
if ( opt$verbose >= 1 ) cat("Cleaning up\n")
cleanup()

```

### 2019-11-06 code/ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd
Add hg38

--- 2019-10-07 code/ROSMAP_RegressDiagnosis_4_TWAS.Rmd
@@
 syn7116000.1
-syn8691134.1
+#_#OLDCOUNTS syn8691134.1
+syn21075911
+
+#SynID Translator
+syn21075913
+
 syn3191087.3
-syn8698240.2
+#_#OLDMetrics syn8698240.2 Version 2
+syn21075912 
+#^^^ Version 1
 
@@
 # Download expression data
-COUNT_ID <- 'syn8691134';
+COUNT_ID <- 'syn21075911';
 ALL_USED_IDs <- COUNT_ID
@@
 COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
+
+Provenance <- 'syn21075913'
+Prov <- syn_temp$get(Provenance, version = 1)
+Translator <- read.csv(Prov$path, header=T, row.names = 1)
+colnames(COUNT) <- as.character( Translator[ colnames(COUNT), ][,2] )
+
+COUNT <- COUNT[ row.names(COUNT)[ (row.names(COUNT) %in% c('N_unmapped', 'N_multimapping', 'N_noFeature', 'N_ambiguous'))==F] , ]
+
 COUNT[,grep('150_120419', colnames(COUNT))[2]] = NULL
+
+#Need to filter low counts here to remove the PAR_Y Regions
+COUNT <- COUNT[ rowSums(COUNT[,] > 0) / (ncol(COUNT)) >= 0.05, ]
+
 # Convert rownames of counts from tracking id to ensemble gene id
@@
 rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
+
 # Get clinical metadata
@@
 METADATA.TECH <- read.table(METADATA.TECH_OBJ$path,sep='\t',header=T)
+
 # Get picard metrics from synapse
-METADATA.PICARD_ID <- 'syn8698240';
+METADATA.PICARD_ID <- 'syn21075912';
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
-METADATA.PICARD <- syn_temp$get(METADATA.PICARD_ID, version = 2)$path %>%
+METADATA.PICARD <- syn_temp$get(METADATA.PICARD_ID, version = 1)$path %>%
   data.table::fread() %>%
   dplyr::rename(Sampleid = sample)
+###fix sampleID Column:
+METADATA.PICARD$Sampleid <- as.character( Translator[ METADATA.PICARD$Sampleid, ][,2] )
+
 # Fix error in technical covariates data
@@
 colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
-# Get gene specific parameters from synapse
+
 GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>%
@@
 COUNT = COUNT[,indToRetain]
+#Remove duplicated row for sampleid:150_120419
+METADATA <- METADATA[!duplicated(METADATA),]
 rownames(METADATA) = METADATA$Sampleid
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn20798011';
+parentId = 'syn21136908';
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
-thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS.Rmd'
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
+thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd'
 # Github link
@@
 
-#Set Used SynIDs For Provenance
 Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
-  "syn8691134", "syn3191087", "syn8698240"
+  "syn21075911", "syn3191087", "syn21075913", "syn21075912"
 )
@@
 
-createAndKnitToFolderEntityClient(file = "ROSMAP_RegressDiagnosis_4_TWAS.Rmd",
-                                          parentId ="syn20798011",
+createAndKnitToFolderEntityClient(file = "ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd",
+                                          parentId ="syn21136908",
                                           folderName = 'ROSMAP')

### 2019-11-07 code/ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd
Gene Lengths

@@
 COUNT = COUNT[,indToRetain]
-#Remove duplicated row for sampleid:150_120419
+#Remove duplicated row for sampleid:
 METADATA <- METADATA[!duplicated(METADATA),]

### 2019-11-07 code/GeneLengthQuant.R

@@ -1,0 +1,143 @@
+library(readr)
+library(BioMart)
+
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+#countz <- readr::read_tsv(syn_temp$get(foo, version = 1))
+COUNT_OBJ <- syn_temp$get("syn21075911", version = 1)
+countz <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F)
+
+myGetGeneLengthAndGCContent <- function(id){
+  
+  org = 'hsa'
+  id.type = 'ensembl_gene_id'
+  host = 'sep2019.archive.ensembl.org'
+  
+  message("Connecting to BioMart ...")
+  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
+  ds <- listDatasets(ensembl)[, "dataset"]
+  ds <- grep(paste0("^", org), ds, value = TRUE)
+  
+  if (length(ds) == 0){
+    stop(paste("Mart not found for:", org))
+  } else if (length(ds) > 1) {
+    message("Found several marts")
+    sapply(ds, function(d) message(paste(which(ds == d), d, sep = ": ")))
+    n <- readline(paste0("Choose mart (1-", length(ds), ") : "))
+    ds <- ds[as.integer(n)]
+  }
+  
+  ensembl <- useDataset(ds, mart = ensembl)
+  message(paste0("Downloading sequence", ifelse(length(id) > 1, "s", ""), " ..."))
+  if (length(id) > 100)
+    message("This may take a few minutes ...")
+  attrs <- c(id.type, "ensembl_exon_id", "chromosome_name", "exon_chrom_start", "exon_chrom_end")
+  coords <- getBM(filters = id.type, attributes = attrs, values = id, mart = ensembl)
+  id <- unique(coords[, id.type])
+  coords <- sapply(id, function(i) {
+    i.coords <- coords[coords[, 1] == i, 3:5]
+    g <- GRanges(i.coords[, 1], IRanges(i.coords[, 2], i.coords[, 3]))
+    return(g)
+  })
+  coords <- lapply(coords[id], reduce)
+  len <- plyr::ldply(coords, function(x) sum(IRanges::width(x)), .id = 'ensembl_gene_id') %>%
+    dplyr::rename(gne.length = V1)
+  
[…]

### 2019-11-07 code/GeneLengthQuant.R
geneLengths

@@ -81,63 +81,7 @@ all.annotations = list(
   genomeAssemblyID = 'GRCh38.p12'
 )
 # Store Length and GC results
-write.table(Temp, file = 'GeneLengthsGCcontent.tsv', sep = '\t', quote=F)
+write.table(Temp, file = 'GeneLengthsGCcontent.tsv', sep = '\t', quote=F, row.names = F)
 ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='GeneLengthsGCcontent.tsv', name = 'Gene Lengths and GC content hg38.p12', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
 all.annotations$dataSubType = 'ReferenceData'
 syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
-
-
-
-
-###########
-temp <- myGetGeneLengthAndGCContent( ENSGs )
-Temp <- as.data.frame( cbind( paste0(temp$ensembl_gene_id, '.', temp$version), temp[,1:5]))
-colnames(Temp) <- c("Gene.ID", "ensembl_gene_id", "position", "hgnc_symbol", "percentage_gc_content", "gene.length")
-
-table( biomart$ensembl_gene_id %in% Temp$ensembl_gene_id)
-table( countz$feature %in% Temp$Gene.ID)
-
-##################
-org = 'hsa'
-id.type = 'ensembl_gene_id'
-host = 'jul2019.archive.ensembl.org'
-ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
-NewVersion <- getBM( attributes = c(id.type, 'ensembl_gene_id', 'ensembl_gene_id_version', 'hgnc_symbol'), values = id, mart = ensembl)
-
-table(as.character(countz$feature)[ 5:dim(countz)[1] ] %in% NewVersion$ensembl_gene_id_version)
-
-Ver_ENSGs <- countz$feature[ as.character(countz$feature) %in% c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous" ) == F ]
[…]

### 2019-11-08 code/Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd
Mayo hg38

--- 2019-09-18 code/Mayo_RegressDiagnosis_4_TWAS.Rmd
@@
 | syn3817650.8 | | 
-| syn8690904.1 | | 
+| Oldcounts------syn8690904.1 | | 
 | syn6126119.3 | | 
@@
 | syn6145639.5 | | 
-| syn8690799.1 | |
+| OldCounts------syn8690799.1 | | 
+|syn20830935.1 | |
+|syn20825567.1 | |
 
@@
 library(glmnet)
-library(synapser)
 library(githubr) # get the package from devtools::install_github('brian-bot/githubr')
@@
 # Source modified utility functions from limma and sva package
-source('../utilityFunctions/parallelDuplicateCorrelation.R')
-source('../utilityFunctions/irwsva.build.R')
-source('../utilityFunctions/f.pvalue.R')
+source('~/TWAS/utilityFunctions/parallelDuplicateCorrelation.R')
+source('~/TWAS/utilityFunctions/irwsva.build.R')
+source('~/TWAS/utilityFunctions/f.pvalue.R')
 knitr::opts_chunk$set(
@@
 # Get reprocessed sample counts for temporal cortex
-COUNT_TC_ID <- 'syn8690799';
-ALL_USED_IDs <- COUNT_TC_ID
-COUNT_TC <- synGet(COUNT_TC_ID, version = 1)$path %>%
+
+#_#OLD:COUNT_TC_ID <- 'syn8690799';
+#_#OLD:ALL_USED_IDs <- COUNT_TC_ID
+#_#OLD:COUNT_TC <- syn_temp$get(COUNT_TC_ID, version = 1)$path %>%
+#_#OLD:  read.table(header=T, sep='\t', check.names = F, row.names = 1)
+#_#OLD:# Get reprocessed sample counts for cerebellum
+#_#OLD:COUNT_CE_ID <- 'syn8690904';
+#_#OLD:ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_CE_ID
+#_#OLD:COUNT_CE <- syn_temp$get(COUNT_CE_ID, version = 1)$path %>%
+#_#OLD:  read.table(header=T, sep='\t', check.names = F, row.names = 1)
+
+COUNT_ID <- 'syn20830935';
+ALL_USED_IDs <- 'syn20830935'
+#ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_ID
+COUNT <- syn_temp$get(COUNT_ID, version = 1)$path %>%
   read.table(header=T, sep='\t', check.names = F, row.names = 1)
-# Get reprocessed sample counts for cerebellum
-COUNT_CE_ID <- 'syn8690904';
-ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_CE_ID
-COUNT_CE <- synGet(COUNT_CE_ID, version = 1)$path %>%
-  read.table(header=T, sep='\t', check.names = F, row.names = 1)
+
+#Translate SynIDs
+Provenance <- 'syn20825567'
+ALL_USED_IDs[length(ALL_USED_IDs)+1] <- Provenance
+Prov <- syn_temp$get(Provenance, version = 1)
+Translator <- read.csv(Prov$path, header=T, row.names = 1)
+colnames(COUNT) <- as.character( Translator[ colnames(COUNT), ][,2] )
+COUNT <- COUNT[ row.names(COUNT)[ (row.names(COUNT) %in% c('N_unmapped', 'N_multimapping', 'N_noFeature', 'N_ambiguous'))==F] , ]
+
+#Need to filter low counts here to remove the PAR_Y Regions
+COUNT <- COUNT[ rowSums(COUNT[,] > 0) / (ncol(COUNT)) >= 0.05, ]
+
 # Combine TCX and CBE counts
-COUNT = cbind(COUNT_TC, COUNT_CE[rownames(COUNT_TC),])
+#_#OLD:COUNT = cbind(COUNT_TC, COUNT_CE[rownames(COUNT_TC),])
 # Convert rownames of counts from tracking id to ensemble gene id
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_TC_ID
-METADATA_TC <- synGet(METADATA_TC_ID, version = 8)$path %>%
+METADATA_TC <- syn_temp$get(METADATA_TC_ID, version = 8)$path %>%
   read.table(sep=',',header=T, stringsAsFactors=F) %>%
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_CE_ID
-METADATA_CE <- synGet(METADATA_CE_ID, version = 5)$path %>%
+METADATA_CE <- syn_temp$get(METADATA_CE_ID, version = 5)$path %>%
   read.table(sep=',',header=T, stringsAsFactors=F) %>%
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_CE_ID
-METADATA_PICARD_CE <- synGet(METADATA_PICARD_CE_ID, version = 1)$path %>%
+METADATA_PICARD_CE <- syn_temp$get(METADATA_PICARD_CE_ID, version = 1)$path %>%
   read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_TC_ID
-METADATA_PICARD_TC <- synGet(METADATA_PICARD_TC_ID, version = 1)$path %>%
+METADATA_PICARD_TC <- syn_temp$get(METADATA_PICARD_TC_ID, version = 1)$path %>%
   read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
@@
 # Get gene specific parameters from synapse
-GENE.PARAM = synGet('syn8449369', version = 2)$path %>% 
+GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>% 
   read.table(sep = '\t', header = T, stringsAsFactors = F)
@@
 # Samples excluded by MAYO investigators
-SAMPLES.EXCLUDE = c(read.table(synGet('syn6126119', version = 3)$path, sep = '\t', header = T, stringsAsFactors = F)$Sample.Name,
-                    read.table(synGet('syn6126114', version = 3)$path, sep = '\t', header = T, stringsAsFactors = F)$Sample.Name)
+SAMPLES.EXCLUDE = c(read.table(syn_temp$get('syn6126119', version = 3)$path, sep = '\t', header = T, stringsAsFactors = F)$Sample.Name,
+                    read.table(syn_temp$get('syn6126114', version = 3)$path, sep = '\t', header = T, stringsAsFactors = F)$Sample.Name)
 ALL_USED_IDs = c(ALL_USED_IDs, 'syn6126119', 'syn6126114')
@@
 ALL_USED_IDs = c(ALL_USED_IDs, CONTROL.PROBES_ID)
-CONTROL.PROBES = fread(synGet(CONTROL.PROBES_ID, version = 5)$path, data.table = F) %>%
+CONTROL.PROBES = fread(syn_temp$get(CONTROL.PROBES_ID, version = 5)$path, data.table = F) %>%
   dplyr::mutate(ID = x) %>%
@@
 ## Define biomart object
-mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "dec2016.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
+mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "sep2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
 ## Query biomart
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn20798011';
+parentId = 'syn21136908';
 activityName = 'Covariate and Diagnosis Regression';
 activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
-thisFileName <- 'Mayo_RegressDiagnosis_4_TWAS.Rmd'
+thisFileName <- 'Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd'
 # Github link
-thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
-thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
 ```
@@
 
-# Code WTF is this??
-CODE <- Folder(name = "Mayo", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "Mayo", parentId = parentId))
 
 #Set Used SynIDs For Provenance
-Syns_Used <- c("syn5223705", "syn8698211", "syn3817650", "syn8690904", 
-"syn6126119", "syn8698214", "syn8449369", "syn6126114", "syn6145639", "syn8690799"
+Syns_Used <- c("syn5223705", "syn8698211", "syn3817650", "syn20825567",
+"syn6126119", "syn8698214", "syn8449369", "syn6126114", "syn6145639", "syn20830935"
 )
@@
 write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MAYO_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ = File('MAYO_SVA_Diagnosis_Corrected.tsv', 
-                  name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 write.table(COVARIATES, file = 'MAYO_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ = File('MAYO_SVA_Diagnosis_Covariates.tsv', 
-                  name = 'Covariates', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_Counts.tsv', 
-                  name = 'Counts (filtered raw)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_Counts.tsv', 
-                  name = 'Counts (estimated)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_logCPM.tsv', 
-                  name = 'Counts (filtered logCPM)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_offset.tsv', 
-                  name = 'Gene length and GC content offset', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_Design.tsv', 
-                  name = 'Design Matrix', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_SurVar.tsv', 
-                  name = 'Surrogate Variables', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
   write.table(file = 'MAYO_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ = File('MAYO_Diagnosis_Regressed_netResidualExpression.tsv', 
-                  name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', 
-                  parentId = CODE$properties$id)
-ENRICH_OBJ = synStore(ENRICH_OBJ, used = Syns_Used, activityName = activityName, 
-                      executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
-synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapser)
-library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synLogin()
-knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
-                                          parentId ="syn20798011",
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+
+createAndKnitToFolderEntityClient(file = "Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd",
+                                          parentId ="syn21136908",
                                           folderName = 'Mayo')
+
 ```

### 2019-11-08 code/ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd
Mayo hg38

@@
 syn4300313.1
-syn8449369.2
+----Old Lengths syn8449369.2
+syn21156161
 syn7116000.1
-#_#OLDCOUNTS syn8691134.1
+----OLDCOUNTS syn8691134.1
 syn21075911
-
-#SynID Translator
+----SynID Translator
 syn21075913
-
 syn3191087.3
-#_#OLDMetrics syn8698240.2 Version 2
+----OLDMetrics syn8698240.2 Version 2
 syn21075912
-#^^^ Version 1
 
@@
 
-GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>%
+GENE.PARAM = syn_temp$get('syn21156161', version = 2)$path %>%
   data.table::fread(data.table = FALSE)
-ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
+ALL_USED_IDs = c(ALL_USED_IDs, 'syn21156161')
 GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% 
@@
 
-Syns_Used <- c("syn3382527", "syn4300313", "syn8449369", "syn7116000",
+Syns_Used <- c("syn3382527", "syn4300313", "syn21156161", "syn7116000",
   "syn21075911", "syn3191087", "syn21075913", "syn21075912"

### 2019-11-09 code/MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd
hg38 Update

--- 2019-10-07 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
@@
 
-syn8691099.1
-syn10156693.3
-syn8698270.1
-syn8449369.2
-syn6100548.7
-syn6101474.4
+| *Synapse ID* | *File Name* |
+|  -----------------------------------------  |   ---------                      |
+| Old Count Matrix ------syn8691099.1 | |
+| syn20963389 | |
+| syn20963390 | |
+| syn10156693.3 | | 
+| syn8698270.1 | | 
+| Old Length GC Data-----syn8449369.2 | | 
+| syn21156161 | |
+| syn6100548.7 | | 
+| syn6101474.4 | |
 
@@
 # Get reprocessed sample counts for temporal cortex
-COUNT_ID <- 'syn8691099';
+COUNT_ID <- 'syn20963390';
 ALL_USED_IDs <- COUNT_ID
@@
   read.table(header=T, sep='\t', check.names = F, row.names = 1)
+
+Provenance <- 'syn20963389'
+Prov <- syn_temp$get(Provenance, version = 1)
+ALL_USED_IDs[length(ALL_USED_IDs)+1] = Provenance
+Translator <- read.csv(Prov$path, header=T, row.names = 1)
+colnames(COUNT) <- as.character( Translator[ colnames(COUNT), ][,2] )
+
+COUNT <- COUNT[ row.names(COUNT)[ (row.names(COUNT) %in% c('N_unmapped', 'N_multimapping', 'N_noFeature', 'N_ambiguous'))==F] , ]
+
+#Need to filter low counts here to remove the PAR_Y Regions
+COUNT <- COUNT[ rowSums(COUNT[,] > 0) / (ncol(COUNT)) >= 0.05, ]
+
 # Convert rownames of counts from tracking id to ensemble gene id
@@
 # Get gene specific parameters from synapse
-GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>% 
+GENE.PARAM = syn_temp$get('syn21156161', version = 3)$path %>% 
     read.table(sep='\t', header=T, stringsAsFactors=F)
-ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
+ALL_USED_IDs = c(ALL_USED_IDs, 'syn21156161')
 GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% unique()
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn20798011';
+parentId = 'syn21136908';
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (IFG, STG, FP, PHG)';
-thisFileName <- 'MSBB_RegressDiagnosis_4_TWAS.Rmd'
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (IFG, STG, FP, PHG)';
+thisFileName <- 'MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd'
 # Github link
@@
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (IFG, STG, FP, PHG)';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (IFG, STG, FP, PHG)';
 
@@
 #Set Used SynIDs For Provenance
-Syns_Used <- c("syn8691099", "syn10156693", "syn8698270", 
-               "syn8449369", "syn6100548", "syn6101474"
+Syns_Used <- c("syn20963390", "syn10156693", "syn8698270", 
+               "syn21156161", "syn6100548", "syn6101474", "syn20963389"
 )
@@
   rnaquantification = 'RSEM',
-  genomeAssemblyID = 'GRCh37'
+  genomeAssemblyID = 'GRCh38'
 )
@@
 
-createAndKnitToFolderEntityClient(file = "MSBB_RegressDiagnosis_4_TWAS.Rmd",
-                                          parentId ="syn20798011",
+createAndKnitToFolderEntityClient(file = "MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd",
+                                          parentId ="syn21136908",
                                           folderName = 'MSBB')

### 2019-11-09 code/Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd
hg38 Update

@@
 | syn8698214.1 | | 
-| syn8449369.2 | | 
+| OldGeneModel------syn8449369.2 | | 
 | syn6126114.3 | | 
@@
 |syn20825567.1 | |
+|syn21156161.2 | |
 
@@
 # Get gene specific parameters from synapse
-GENE.PARAM = syn_temp$get('syn8449369', version = 2)$path %>% 
+GENE.PARAM = syn_temp$get('syn21156161', version = 3)$path %>% 
   read.table(sep = '\t', header = T, stringsAsFactors = F)
-ALL_USED_IDs = c(ALL_USED_IDs, 'syn8449369')
+ALL_USED_IDs = c(ALL_USED_IDs, 'syn21156161')
 GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% unique()
@@
 # Find inter relation between factor covariates
+METADATA <- METADATA[ !duplicated(METADATA), ]
 COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
@@
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
 thisFileName <- 'Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd'
@@
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (CBE, TCX)';
+activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (CBE, TCX)';
 

### 2019-11-09 code/GeneLengthQuant.R

@@ -9,11 +9,11 @@ syn_temp$login()
 COUNT_OBJ <- syn_temp$get("syn21075911", version = 1)
 countz <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F)
 
-myGetGeneLengthAndGCContent <- function(id){
+myGetGeneLengthAndGCContent <- function(id, ver){
   
   org = 'hsa'
   id.type = 'ensembl_gene_id'
-  host = 'sep2019.archive.ensembl.org'
+  host = ver
   
   message("Connecting to BioMart ...")
   ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
@@ -53,9 +53,15 @@ myGetGeneLengthAndGCContent <- function(id){
 
 ENSGs <- do.call(rbind, strsplit(as.character(countz$feature)[5:dim(countz)[1]], "[.]"))
 
-temp <- myGetGeneLengthAndGCContent( ENSGs )
+temp_Jul <- myGetGeneLengthAndGCContent( ENSGs, 'jul2019.archive.ensembl.org' )
+temp_Sep <- myGetGeneLengthAndGCContent( ENSGs, 'sep2019.archive.ensembl.org' )
+
+#temp <- myGetGeneLengthAndGCContent( ENSGs )
+temp <- rbind( temp_Sep[1:dim(temp_Sep)[1],], temp_Jul[ (temp_Jul$ensembl_gene_id %in% temp_Sep$ensembl_gene_id) ==F,]  )
+
 Temp <- as.data.frame( cbind( paste0(temp$ensembl_gene_id, '.', temp$version), temp[,1:5]))
 colnames(Temp) <- c("Gene.ID", "ensembl_gene_id", "position", "hgnc_symbol", "percentage_gc_content", "gene.length")
+
 
 parentId = 'syn21136908';
 activityName = 'Gene Lengths and GC content hg38.p12';

### 2019-11-20 code/MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd
NonDiagnosis

@@
 library(edgeR)
+#BiocManager::install("biomaRt")
 library(biomaRt)
@@
 loopCount = 0
-while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
+
+notEstimable <- NULL
+Start <- Sys.time()
+foo <- 0
+while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 8){ #_# <= 20
   writeLines(paste('Using following covariates in the model:',
@@
   } else {
+    #_#TryThis Out
+    #if( isTRUE(exists("notEstimable")) ){
+      message( paste0( "LoopCount: ", loopCount," is NaN"))
       notEstimable = c(notEstimable, postAdjustCovars[length(postAdjustCovars)])
       postAdjustCovars = postAdjustCovars[1:(length(postAdjustCovars)-1)]
+    #}else{
+      #notEstimable = postAdjustCovars[length(postAdjustCovars)]
+      #postAdjustCovars = postAdjustCovars[1:(length(postAdjustCovars)-1)]
+      #}
   }
@@
   # print(loopCount)
+  message( paste0( loopCount, " Time: ", Sys.time()-Start ))
+  message( paste0( "Residual Significant Covars: ", c(residualSigCovars$significantCovars )) )
+  if( residualSigCovars$significantCovars == 'PCT_RIBOSOMAL_BASES' & isTRUE(length(residualSigCovars$significantCovars) == 1)){
+    foo <- foo + 1 
+  }
+  if( foo > 2){
+    loopCount <- 22
+  }else{
+
+  }
 }

### 2019-11-20 code/MSBB_Regress_hg38.Rmd
NonDiagnosis

--- 2019-11-20 code/MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd
@@
 ---
-title: Covariate and analysis of MSBB reprocessed counts Regressing out Diagnosis as well for TWAS
+title: Covariate and analysis of MSBB reprocessed counts
 author: 'JKG - Adapted from: Thanneer Perumal'
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
-FactorCovariates <- c("individualIdentifier", "batch", "RACE", "Sex", "Tissue.Diagnosis", "Tissue.APOE4", "Diagnosis")
+FactorCovariates <- c("individualIdentifier", "batch", "RACE", "Sex", "Tissue.Diagnosis", "Tissue.APOE4")
 ContCovariates <- c("CDR", "RIN", "RIN2", "AOD","PMI",  "PCT_PF_READS_ALIGNED", "PCT_CODING_BASES",
@@
 ## Define biomart object
-mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "sep2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
+mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
+#mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "hsapiens_gene_ensembl")
+
 ## Query biomart
@@
   message( paste0( "Residual Significant Covars: ", c(residualSigCovars$significantCovars )) )
-  if( residualSigCovars$significantCovars == 'PCT_RIBOSOMAL_BASES' & isTRUE(length(residualSigCovars$significantCovars) == 1)){
-    foo <- foo + 1 
-  }
-  if( foo > 2){
-    loopCount <- 22
-  }else{
 
-  }
 }
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn21136908';
-activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (IFG, STG, FP, PHG)';
-thisFileName <- 'MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd'
+parentId = 'syn21277617';
+activityName = 'Covariate Regression';
+activityDescription = 'Covariate analysis and Regrsison of AD of aligned effective counts with GRCh38 with CQN normalisation (IFG, STG, FP, PHG)';
+thisFileName <- 'MSBB_Regress_hg38.Rmd'
 # Github link
@@
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (IFG, STG, FP, PHG)';
+activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (IFG, STG, FP, PHG)';
 
@@
 # Store SVA results
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MSBB_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MSBB_SVA_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_SVA_Corrected.tsv', name = 'Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
-write.table(COVARIATES, file = 'MSBB_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(COVARIATES, file = 'MSBB_SVA_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_SVA_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_eCounts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_eCounts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MSBB_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MSBB_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSBB_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 
-createAndKnitToFolderEntityClient(file = "MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd",
-                                          parentId ="syn21136908",
+createAndKnitToFolderEntityClient(file = "MSBB_Regress_hg38.Rmd",
+                                          parentId ="syn21277617",
                                           folderName = 'MSBB')

### 2019-11-20 code/Mayo_Regress_hg38.Rmd
NonDiagnosis

--- 2019-11-09 code/Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd
@@
 ---
-title: Covariate Analysis of MAYO Reprocessed counts Regressing out Diagnosis as well for TWAS
+title: Covariate Analysis of MAYO Reprocessed counts
 author: 'JKG - Adapted from: Thanneer Perumal'
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
-FactorCovariates <- c("Donor_ID", "Source", "Sex", "FLOWCELL", "Tissue.SourceDiagnosis", "Tissue.Diagnosis", "Tissue.APOE4", "Diagnosis")
+FactorCovariates <- c("Donor_ID", "Source", "Sex", "FLOWCELL", "Tissue.SourceDiagnosis", "Tissue.Diagnosis", "Tissue.APOE4")
 ContCovariates <- c("RIN", "RIN2", "AgeAtDeath","PMI", "PCT_PF_READS_ALIGNED", "PCT_CODING_BASES",
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn21136908';
-activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- 'Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd'
+parentId = 'syn21277617';
+activityName = 'Covariate Regression';
+activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
+thisFileName <- 'Mayo_Regress_hg38.Rmd'
 # Github link
@@
 ```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
-activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (CBE, TCX)';
+activityName = 'Covariate Regression';
+activityDescription = 'Covariate analysis of aligned effective counts with GRCh38 with CQN normalisation (CBE, TCX)';
 
@@
 # Store SVA results
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MAYO_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'MAYO_SVA_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_SVA_Corrected.tsv', name = 'Normalised, covariates, and surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
-write.table(COVARIATES, file = 'MAYO_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(COVARIATES, file = 'MAYO_SVA_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_SVA_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'MAYO_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'MAYO_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 
-createAndKnitToFolderEntityClient(file = "Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd",
-                                          parentId ="syn21136908",
+createAndKnitToFolderEntityClient(file = "Mayo_Regress_hg38.Rmd",
+                                          parentId ="syn21277617",
                                           folderName = 'Mayo')

### 2019-11-20 code/ROSMAP_Regress_hg38.Rmd
NonDiagnosis

--- 2019-11-08 code/ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd
@@
 ---
-title: Covariate Analysis of ROSMAP Reprocessed counts Regressing out Diagnosis as well for TWAS
+title: Covariate Analysis of ROSMAP Reprocessed counts
 author: 'JKG - Adapted from: Thanneer Perumal'
@@
 
-syn3382527.7
-syn4300313.1
-----Old Lengths syn8449369.2
-syn21156161
-syn7116000.1
-----OLDCOUNTS syn8691134.1
-syn21075911
-----SynID Translator
-syn21075913
-syn3191087.3
-----OLDMetrics syn8698240.2 Version 2
-syn21075912
+| *Synapse ID* | *File Name* |
+|  -----------------------------------------  |   ---------                      |
+| syn3382527.7 | | 
+| syn4300313.1 | | 
+| ----Old Lengths syn8449369.2 | | 
+| syn21156161 | | 
+| syn7116000.1 | | 
+| ----OLDCOUNTS syn8691134.1 | | 
+| syn21075911 | | 
+| ----SynID Translator | | 
+| syn21075913 | | 
+| syn3191087.3 | | 
+| ----OLDMetrics syn8698240.2 Version 2 | | 
+| syn21075912  | |
 
@@
 Prov <- syn_temp$get(Provenance, version = 1)
+ALL_USED_IDs[length(ALL_USED_IDs)+1] = Provenance
 Translator <- read.csv(Prov$path, header=T, row.names = 1)
@@
 primaryVariable <- c("cogdx", "Diagnosis", "APOE4")
+
 FactorCovariates <- c("Batch", "Sex", "race", "spanish", "cogdx", "Diagnosis", "APOE4")
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
-postAdjustCovars = c(postAdjustCovars, "Diagnosis", names(which.max(covariatesEffects))) %>% unique()
+postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
 loopCount = 0 
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn21136908';
-activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- 'ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd'
+parentId = 'syn21277617';
+activityName = 'Covariate Regression';
+activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
+thisFileName <- 'ROSMAP_Regress_hg38.Rmd'
 # Github link
@@
 ```{r synapse.store, include=FALSE, eval=TRUE, cache=TRUE}
-activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
+activityName = 'Covariate Regression';
+activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh37 with CQN normalisation (DLPFC)';
 
@@
 # Store SVA results
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Corrected.tsv', name = 'Normalised, covariates, and surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
-write.table(COVARIATES, file = 'ROSMAP_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(COVARIATES, file = 'ROSMAP_SVA_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 
-createAndKnitToFolderEntityClient(file = "ROSMAP_RegressDiagnosis_4_TWAS_hg38.Rmd",
-                                          parentId ="syn21136908",
+createAndKnitToFolderEntityClient(file = "ROSMAP_Regress_hg38.Rmd",
+                                          parentId ="syn21277617",
                                           folderName = 'ROSMAP')

### 2019-11-20 code/MSBB_RegressDiagnosis_4_TWAS.Rmd
Fix metrics File PointerID

@@
 
-syn8691099.1
-syn10156693.3
-syn8698270.1
-syn8449369.2
-syn6100548.7
-syn6101474.4
+| syn8691099.1
+| syn10156693.3
+| syn8698270.1
+| syn8449369.2
+| syn6100548.7
+| syn6101474.4
 
@@
                            groupLabels = colnames(COVARIATES.tmp))
+#HG19_Exp <- CQN.GENE_EXPRESSION$E.no.na
+#saveRDS(HG19_Exp, file = "HG19_Exp.RDS")
 ```

### 2019-11-20 code/MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd
Fix metrics File PointerID

@@
 | syn10156693.3 | | 
-| syn8698270.1 | | 
+| Old Metrics------syn8698270.1 | |
+| syn20963391 | | 
 | Old Length GC Data-----syn8449369.2 | | 
@@
 # Get picard metrics from synapse
-METADATA.PICARD_ID <- 'syn8698270';
+METADATA.PICARD_ID <- 'syn20963391';
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD_ID
@@
 #Set Used SynIDs For Provenance
-Syns_Used <- c("syn20963390", "syn10156693", "syn8698270", 
+Syns_Used <- c("syn20963390", "syn10156693", "syn20963391", 
                "syn21156161", "syn6100548", "syn6101474", "syn20963389"

### 2019-11-20 code/MSBB_Regress_hg38.Rmd
Fix metrics File PointerID

@@
 | syn10156693.3 | | 
-| syn8698270.1 | | 
+| syn20963391 ||
+| Old Picard Metrics-----syn8698270.1 | | 
 | Old Length GC Data-----syn8449369.2 | | 

### 2019-11-20 code/Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd
Fix metrics File PointerID

@@
 | syn6126119.3 | | 
-| syn8698214.1 | | 
+| OldMetrics--------syn8698214.1 | | 
 | OldGeneModel------syn8449369.2 | | 
@@
 | OldCounts------syn8690799.1 | | 
-|syn20830935.1 | |
-|syn20825567.1 | |
-|syn21156161.2 | |
+| syn20830935.1 | |
+| syn20825567.1 | |
+| syn21156161.2 | |
 
@@
 # Get picard metrics from synapse
-METADATA_PICARD_CE_ID <- 'syn8698214';
+METADATA_PICARD_CE_ID <- 'syn20831294';
 ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_CE_ID
@@
 Syns_Used <- c("syn5223705", "syn8698211", "syn3817650", "syn20825567",
-"syn6126119", "syn8698214", "syn8449369", "syn6126114", "syn6145639", "syn20830935"
+"syn6126119", "syn20831294", "syn8449369", "syn6126114", "syn6145639", "syn20830935"
 )

### 2019-11-20 code/Mayo_Regress_hg38.Rmd
Fix metrics File PointerID

@@
 | syn6126119.3 | | 
-| syn8698214.1 | | 
+| syn20831294 ||
+| OldMetrics--------syn8698214.1 | | 
 | OldGeneModel------syn8449369.2 | | 
@@
 ## Define biomart object
-mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "sep2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
+mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
 ## Query biomart

### 2019-11-23 code/MSBB_RegressDiagnosis_4_TWAS_hg38.Rmd
catch code Up

@@
   dplyr::rename(sampleIdentifier = sample)
+#REplace Syn IDs
+row.names(METADATA.PICARD) <- as.character( Translator[ METADATA.PICARD$sampleIdentifier , ][,2] )
+METADATA.PICARD$sampleIdentifier <- row.names(METADATA.PICARD)
+
 METADATA <- dplyr::full_join(METADATA_TECH, METADATA_CLINICAL) %>%
@@
 foo <- 0
-while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 8){ #_# <= 20
+while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){ #_# <= 8
   writeLines(paste('Using following covariates in the model:',
@@
   message( paste0( "Residual Significant Covars: ", c(residualSigCovars$significantCovars )) )
-  if( residualSigCovars$significantCovars == 'PCT_RIBOSOMAL_BASES' & isTRUE(length(residualSigCovars$significantCovars) == 1)){
-    foo <- foo + 1 
-  }
-  if( foo > 2){
-    loopCount <- 22
-  }else{
+  #if( residualSigCovars$significantCovars == 'PCT_RIBOSOMAL_BASES' & isTRUE(length(residualSigCovars$significantCovars) == 1)){
+   # foo <- foo + 1 
+  #}
+  #if( foo > 2){
+   # loopCount <- 22
+  #}else{
 
-  }
+  #}
 }
@@
 # Estimate surrogate variables
-SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$E.no.na,
-                    MODEL1, MODEL0, n.sv = NUM.SV, B = 30)$sv
+##JKG Add in in case lack of valuse adds singularity issue
+if( length(table(MODEL0[,'PCT_RIBOSOMAL_BASES'])) < .05*dim(MODEL0)[1] ){
+  MODEL0 <- MODEL0[,colnames(MODEL0)[colnames(MODEL0)!='PCT_RIBOSOMAL_BASES'] ]
+}else{}
+if( length(table(MODEL1[,'PCT_RIBOSOMAL_BASES'])) < .05*dim(MODEL1)[1] ){
+  MODEL1 <- MODEL1[,colnames(MODEL1)[colnames(MODEL1)!='PCT_RIBOSOMAL_BASES'] ]
+}else{}
+
+SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$E.no.na, MODEL1, MODEL0, n.sv = NUM.SV, B = 30)$sv
+
 colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

### 2019-11-23 code/MSBB_Regress_hg38.Rmd
catch code Up

@@
 
+### Differential expression analysis (with Tissue.CDR as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of Tissue.CDR
+1. FP.CDR: change in CDR in frontal pole where 0 no cognitive decline and 5 severe cognitive decline
+2. IFG.CDR: change in CDR in inferior frontal gyrus where 0 no cognitive decline and 5 severe cognitive decline
+3. PHG.CDR: change in CDR in parahippocampal gyrus where 0 no cognitive decline and 5 severe cognitive decline
+4. STG.CDR: change in CDR in superior temporal gyrus where 0 no cognitive decline and 5 severe cognitive decline
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp, fig.height=6, fig.width=15}
+# Get design matrix
+COVARIATES.tmp = COVARIATES %>%
+  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.') %>%
+  dplyr::mutate(Tissue = factor(Tissue))
+DESIGN = getDesignMatrix(COVARIATES.tmp[, c('Tissue', postAdjustCovars), drop = F], Intercept = F)
+ind = grep('Tissue', colnames(DESIGN$design))
+DESIGN$design[,ind] = DESIGN$design[,ind] * as.numeric(COVARIATES.tmp[,'CDR'])
+colnames(DESIGN$design)[ind] = paste0(colnames(DESIGN$design),'.CDR')
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$individualIdentifier, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
+FIT = lmFit(VOOM.WEIGHTS)
+# Fit contrast
+contrast = makeContrasts(contrasts = c("TissueFP.CDR", 
+                                       "TissueIFG.CDR", 
+                                       "TissuePHG.CDR", 
+                                       "TissueSTG.CDR"),
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:4, function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue','',Comparison),
+                Study = 'MSSM',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  dplyr::rename(Tissue = Comparison) %>%
+  dplyr::mutate(Comparison = 'CDR') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue) %>%
+  group_by(Tissue, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position = 'top')
+p = p + facet_grid(Comparison+.~Tissue, scales = 'free')
+p
+all.diff.exp = list(CDR = DE)
+all.fit = list(CDR = FIT)
+```
+
+### Differential expression analysis (with Tissue.Diagnosis as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of Tissue.Diagnosis
+1. FP.AD: Samples from frontal pole region with CDR >= 1 and bbscore >= 4 and NP.1 >= 2
+2. FP.CONTROL: Samples from frontal pole region with CDR <= 0.5 and bbscore <= 3 and NP.1 <= 1
+3. FP.OTHER: All the other frontal pole samples
+4. PHG.AD: Samples from parahippocampal gyrus region with CDR >= 1 and bbscore >= 4 and NP.1 >= 2
+5. PHG.CONTROL: Samples from parahippocampal gyrus region with CDR <= 0.5 and bbscore <= 3 and NP.1 <= 1
+6. PHG.OTHER:All the other parahippocampal gyrus samples
+7. STG.AD: Samples from frontal superior temporal gyrus with CDR >= 1 and bbscore >= 4 and NP.1 >= 2
+8. STG.CONTROL: Samples from superior temporal gyrus region with CDR <= 0.5 and bbscore <= 3 and NP.1 <= 1
+9. STG.OTHER: All the other superior temporal gyrus samples
+10. IFG.AD: Samples from inferior frontal gyrus region with CDR >= 1 and bbscore >= 4 and NP.1 >= 2
+11. IFG.CONTROL: Samples from inferior frontal gyrus region with CDR <= 0.5 and bbscore <= 3 and NP.1 <= 1
+12. IFG.OTHER: All the other inferior frontal gyrus samples
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp1, fig.height=15, fig.width=13}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$individualIdentifier, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
+FIT = lmFit(VOOM.WEIGHTS)
+# Fit contrast
+cntr = c()
+for (region in c('FP', 'STG', 'PHG', 'IFG')){
+  tmp = combn(paste0('Tissue.Diagnosis', region, '.', c('AD', 'OTHER', 'CONTROL')),2)
+  cntr = c(cntr, apply(tmp, 2, paste, collapse = '-'))
+}
+contrast = makeContrasts(contrasts=cntr,
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:12, function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
+                Study = 'MSSM',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue','reference'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue1','against'), sep = '\\.') %>%
+  dplyr::mutate(Comparison = paste(reference, against, sep = '-')) %>%
+  dplyr::select(-Tissue1) %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue) %>%
+  group_by(Tissue, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
+p = p + facet_grid(Tissue+.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis = DE))
+all.fit = c(all.fit, list(Diagnosis = FIT))
+```
+
+### Associate differential expression results with gc content, gene length and average expression
+```{r associate.de, fig.height=15, fig.width=15}
+pl = list()
+pl[[1]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
+                 aes(x = log10(gene.length), y = logFC, color = Direction)) + geom_point() 
+pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene.length), y = logFC))
+pl[[1]] = pl[[1]] + facet_grid(Tissue~.+Comparison) + scale_color_manual(values = c('green','grey','red'))
+pl[[1]] = pl[[1]] + theme(legend.position = 'top')
+pl[[2]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
+                 aes(x = percentage_gc_content, y = logFC, color = Direction)) + geom_point()
+pl[[2]] = pl[[2]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = percentage_gc_content, y = logFC))
+pl[[2]] = pl[[2]] + facet_grid(Tissue~.+Comparison) + scale_color_manual(values = c('green','grey','red'))
+pl[[2]] = pl[[2]] + theme(legend.position = 'top')
+pl[[3]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
+                 aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
+pl[[3]] = pl[[3]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = AveExpr, y = logFC))
+pl[[3]] = pl[[3]] + facet_grid(Tissue~.+Comparison) + scale_color_manual(values = c('green','grey','red'))
+pl[[3]] = pl[[3]] + theme(legend.position = 'top')
+multiplot(plotlist = pl, cols = 3)
+```
+
+### Differential expression analysis (with Tissue.APOE4 as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp2, fig.height=15, fig.width=13}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[3], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$individualIdentifier, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
+FIT = lmFit(VOOM.WEIGHTS)
+# Fit contrast
+cntr = c()
+for (region in c('FP', 'STG', 'PHG', 'IFG')){
+  tmp = combn(paste0('Tissue.APOE4', region, '.', c('0', '1', '2')),2)
+  cntr = c(cntr, apply(tmp, 2, paste, collapse = '-'))
+}
+contrast = makeContrasts(contrasts=cntr,
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.APOE4','',Comparison),
+                Study = 'MSSM',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue','reference'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue1','against'), sep = '\\.') %>%
+  dplyr::mutate(Comparison = paste(reference, against, sep = '-')) %>%
+  dplyr::select(-Tissue1) %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue) %>%
+  group_by(Tissue, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
+p = p + facet_grid(Tissue+.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(APOE4 = DE))
+all.fit = c(all.fit, list(APOE4 = FIT))
+```
+
+### Differential expression analysis (with Tissue.Diagnosis and Gender)
+Differential expression is performed on the Tissue.Diagnosis x Gender variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
+```{r diff.exp3, fig.height=15, fig.width=13}
+## Modeling Diagnosis, msex and age_death conjointly
+COVARIATES$Tissue.Diagnosis.SEX = paste(COVARIATES$Tissue.Diagnosis,COVARIATES$Sex, sep = '.') %>% factor
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c('Tissue.Diagnosis.SEX', setdiff(postAdjustCovars, 'SEX')), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$individualIdentifier, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
+FIT = lmFit(VOOM.WEIGHTS)
+# Fit contrast
+cntr = c('Tissue.Diagnosis.SEXIFG.AD.MALE-Tissue.Diagnosis.SEXIFG.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXIFG.AD.FEMALE-Tissue.Diagnosis.SEXIFG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXIFG.AD.MALE+0.5*Tissue.Diagnosis.SEXIFG.AD.FEMALE
+         -0.5*Tissue.Diagnosis.SEXIFG.CONTROL.MALE-0.5*Tissue.Diagnosis.SEXIFG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXIFG.AD.FEMALE+0.5*Tissue.Diagnosis.SEXIFG.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXIFG.AD.MALE-0.5*Tissue.Diagnosis.SEXIFG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXIFG.AD.FEMALE-0.5*Tissue.Diagnosis.SEXIFG.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXIFG.AD.MALE+0.5*Tissue.Diagnosis.SEXIFG.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXFP.AD.MALE-Tissue.Diagnosis.SEXFP.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXFP.AD.FEMALE-Tissue.Diagnosis.SEXFP.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXFP.AD.MALE+0.5*Tissue.Diagnosis.SEXFP.AD.FEMALE
+         -0.5*Tissue.Diagnosis.SEXFP.CONTROL.MALE-0.5*Tissue.Diagnosis.SEXFP.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXFP.AD.FEMALE+0.5*Tissue.Diagnosis.SEXFP.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXFP.AD.MALE-0.5*Tissue.Diagnosis.SEXFP.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXFP.AD.FEMALE-0.5*Tissue.Diagnosis.SEXFP.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXFP.AD.MALE+0.5*Tissue.Diagnosis.SEXFP.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXPHG.AD.MALE-Tissue.Diagnosis.SEXPHG.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXPHG.AD.FEMALE-Tissue.Diagnosis.SEXPHG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXPHG.AD.MALE+0.5*Tissue.Diagnosis.SEXPHG.AD.FEMALE
+         -0.5*Tissue.Diagnosis.SEXPHG.CONTROL.MALE-0.5*Tissue.Diagnosis.SEXPHG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXPHG.AD.FEMALE+0.5*Tissue.Diagnosis.SEXPHG.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXPHG.AD.MALE-0.5*Tissue.Diagnosis.SEXPHG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXPHG.AD.FEMALE-0.5*Tissue.Diagnosis.SEXPHG.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXPHG.AD.MALE+0.5*Tissue.Diagnosis.SEXPHG.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXSTG.AD.MALE-Tissue.Diagnosis.SEXSTG.CONTROL.MALE',
+         'Tissue.Diagnosis.SEXSTG.AD.FEMALE-Tissue.Diagnosis.SEXSTG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXSTG.AD.MALE+0.5*Tissue.Diagnosis.SEXSTG.AD.FEMALE
+         -0.5*Tissue.Diagnosis.SEXSTG.CONTROL.MALE-0.5*Tissue.Diagnosis.SEXSTG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXSTG.AD.FEMALE+0.5*Tissue.Diagnosis.SEXSTG.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXSTG.AD.MALE-0.5*Tissue.Diagnosis.SEXSTG.CONTROL.FEMALE',
+         '0.5*Tissue.Diagnosis.SEXSTG.AD.FEMALE-0.5*Tissue.Diagnosis.SEXSTG.CONTROL.FEMALE
+         -0.5*Tissue.Diagnosis.SEXSTG.AD.MALE+0.5*Tissue.Diagnosis.SEXSTG.CONTROL.MALE')
+contrast = makeContrasts(contrasts=cntr,
+                         levels = colnames(FIT$coefficients))
+colnames(contrast) = c('IFG.AD.MALE-IFG.CONTROL.MALE',
+                       'IFG.AD.FEMALE-IFG.CONTROL.FEMALE',
+                       'IFG.AD.ALL-IFG.CONTROL.ALL',
+                       'IFG.ALL.FEMALE-IFG.ALL.MALE',
+                       'IFG.ALL.ALL-IFG.ALL.ALL',
+                       'FP.AD.MALE-FP.CONTROL.MALE',
+                       'FP.AD.FEMALE-FP.CONTROL.FEMALE',
+                       'FP.AD.ALL-FP.CONTROL.ALL',
+                       'FP.ALL.FEMALE-FP.ALL.MALE',
+                       'FP.ALL.ALL-FP.ALL.ALL',
+                       'PHG.AD.MALE-PHG.CONTROL.MALE',
+                       'PHG.AD.FEMALE-PHG.CONTROL.FEMALE',
+                       'PHG.AD.ALL-PHG.CONTROL.ALL',
+                       'PHG.ALL.FEMALE-PHG.ALL.MALE',
+                       'PHG.ALL.ALL-PHG.ALL.ALL',
+                       'STG.AD.MALE-STG.CONTROL.MALE',
+                       'STG.AD.FEMALE-STG.CONTROL.FEMALE',
+                       'STG.AD.ALL-STG.CONTROL.ALL',
+                       'STG.ALL.FEMALE-STG.ALL.MALE',
+                       'STG.ALL.ALL-STG.ALL.ALL')
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
+                Study = 'MSSM',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+all.diff.exp = c(all.diff.exp, list(Diagnosis.SEX = DE))
+all.fit = c(all.fit, list(Diagnosis.SEX = FIT))
+```
+
+### Differential expression analysis (with Tissue.Diagnosis and AOD)
+Differential expression is performed on the Tissue.Diagnosis x AOD variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
+```{r diff.exp4, fig.height=15, fig.width=13}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], setdiff(postAdjustCovars, 'AOD')), drop = F], Intercept = F)
+ind = grep('Diagnosis', colnames(DESIGN$design))
+DESIGN$design[,ind] = DESIGN$design[,ind] * COVARIATES[rownames(DESIGN$design),'AOD']
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+colnames(DESIGN$design)[ind] = gsub('Tissue.Diagnosis', '', paste0(colnames(DESIGN$design)[ind], '.AOD'))
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$individualIdentifier, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
+FIT = lmFit(VOOM.WEIGHTS)
+# Fit contrast
+cntr = c("FP.AD.AOD-FP.CONTROL.AOD",
+         "0.5*FP.AD.AOD+0.5*FP.CONTROL.AOD",
+         "IFG.AD.AOD-IFG.CONTROL.AOD",
+         "0.5*IFG.AD.AOD+0.5*IFG.CONTROL.AOD",
+         "PHG.AD.AOD-PHG.CONTROL.AOD",
+         "0.5*PHG.AD.AOD+0.5*PHG.CONTROL.AOD",
+         "STG.AD.AOD-STG.CONTROL.AOD",
+         "0.5*STG.AD.AOD+0.5*STG.CONTROL.AOD")
+contrast = makeContrasts(contrasts=cntr,
+                         levels = colnames(FIT$coefficients))
+colnames(contrast) = c("FP.AD.AOD-FP.CONTROL.AOD",
+                       "FP.ALL.AOD",
+                       "IFG.AD.AOD-IFG.CONTROL.AOD",
+                       "IFG.ALL.AOD",
+                       "PHG.AD.AOD-PHG.CONTROL.AOD",
+                       "PHG.ALL.AOD",
+                       "STG.AD.AOD-STG.CONTROL.AOD",
+                       "STG.ALL.AOD")
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
+                Study = 'MSSM',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+all.diff.exp = c(all.diff.exp, list(Diagnosis.AOD = DE))
+all.fit = c(all.fit, list(Diagnosis.AOD = FIT))
+```
+
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
@@
 
+# Store differential expression results
+rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
+  write.table(file = 'MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', name = 'Differential Expression Results (Tissue.Diagnosis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'diffExp'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store all differential expression models
+save(all.fit, file = 'MSSM_FP_STG_PHG_IFG_Models.RData')
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MSSM_FP_STG_PHG_IFG_Models.RData', name = 'All Limma Models', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'modelFits'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 stopCluster(cl)

### 2019-11-23 code/Mayo_RegressDiagnosis_4_TWAS_hg38.Rmd
catch code Up

@@
 # Get picard metrics from synapse
-METADATA_PICARD_CE_ID <- 'syn20831294';
-ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_CE_ID
-METADATA_PICARD_CE <- syn_temp$get(METADATA_PICARD_CE_ID, version = 1)$path %>%
-  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
-  dplyr::rename(ID = sample)
+#METADATA_PICARD_CE_ID <- 'syn20831294';
+#ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_CE_ID
+#METADATA_PICARD_CE <- syn_temp$get(METADATA_PICARD_CE_ID, version = 1)$path %>%
+#  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
+#  dplyr::rename(ID = sample)
 # colnames(METADATA_PICARD_CE) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA_PICARD_CE))
 # colnames(METADATA_PICARD_CE) = gsub('RnaSeqMetrics__','',colnames(METADATA_PICARD_CE))
-METADATA_PICARD_TC_ID <- 'syn8698211';
-ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_TC_ID
-METADATA_PICARD_TC <- syn_temp$get(METADATA_PICARD_TC_ID, version = 1)$path %>%
-  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
-  dplyr::rename(ID = sample)
+#METADATA_PICARD_TC_ID <- 'syn8698211';
+#ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA_PICARD_TC_ID
+#METADATA_PICARD_TC <- syn_temp$get(METADATA_PICARD_TC_ID, version = 1)$path %>%
+#  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
+#  dplyr::rename(ID = sample)
 # colnames(METADATA_PICARD_TC) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA_PICARD_TC))
@@
 # Merge all metadata
+#METADATA = list(METADATA_TC, METADATA_CE) %>%
+#  data.table::rbindlist(use.names = T, fill = T) %>%
+#  dplyr::inner_join(list(METADATA_PICARD_TC, METADATA_PICARD_CE) %>% 
+#                      data.table::rbindlist(use.names = T, fill = T)) %>%
+#  as.data.frame
+
+METADATA.PICARD <- 'syn20831294';
+ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD
+METADATA.PICARD <- syn_temp$get(METADATA.PICARD, version = 1)$path %>%
+  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
+  dplyr::rename(ID = sample)
+
+#REplace Syn IDs
+row.names(METADATA.PICARD) <- as.character( Translator[ METADATA.PICARD$ID , ][,2] )
+METADATA.PICARD$ID <- row.names(METADATA.PICARD)
+
 METADATA = list(METADATA_TC, METADATA_CE) %>%
   data.table::rbindlist(use.names = T, fill = T) %>%
-  dplyr::inner_join(list(METADATA_PICARD_TC, METADATA_PICARD_CE) %>% 
+  dplyr::inner_join(list(METADATA.PICARD) %>% 
                       data.table::rbindlist(use.names = T, fill = T)) %>%
   as.data.frame
+
 colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))

### 2019-11-23 code/Mayo_Regress_hg38.Rmd
catch code Up

@@
 # Merge all metadata
+
+METADATA.PICARD <- 'syn20831294';
+ALL_USED_IDs[length(ALL_USED_IDs)+1] = METADATA.PICARD
+METADATA.PICARD <- syn_temp$get(METADATA.PICARD, version = 1)$path %>%
+  read.table(sep='\t', header=T, stringsAsFactors=F) %>% 
+  dplyr::rename(ID = sample)
+
+#REplace Syn IDs
+row.names(METADATA.PICARD) <- as.character( Translator[ METADATA.PICARD$ID , ][,2] )
+METADATA.PICARD$ID <- row.names(METADATA.PICARD)
+
 METADATA = list(METADATA_TC, METADATA_CE) %>%
   data.table::rbindlist(use.names = T, fill = T) %>%
-  dplyr::inner_join(list(METADATA_PICARD_TC, METADATA_PICARD_CE) %>% 
+  dplyr::inner_join(list(METADATA.PICARD) %>% 
                       data.table::rbindlist(use.names = T, fill = T)) %>%
   as.data.frame
+
 colnames(METADATA) = gsub('AlignmentSummaryMetrics__','',colnames(METADATA))
 colnames(METADATA) = gsub('RnaSeqMetrics__','',colnames(METADATA))
+
 # Get gene specific parameters from synapse
@@
 
+### Differential expression analysis (with Tissue.SourceDiagnosis as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of Tissue.SourceDiagnosis
+1. CBE.AD: Alzheimers Disease samples from Cerebellum region
+2. CBE.CONTROL: Control samples from Cerebellum region
+3. CBE.PATH_AGE: Pathological ageing samples from Cerebellum region
+4. CBE.PSP: Palsy samples from Cerebellum region
+5. TCX.AD: Alzheimers Disease samples from temporal cortex region
+6. TCX.CONTROL: Control samples from temporal cortex region
+7. TCX.PATH_AGE: Pathalogical ageing samples from temporal cortex region
+8. TCX.PSP: Palsy samples from temporal cortex region
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp, fig.height=10, fig.width=18}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[1], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$Donor_ID, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            weights = VOOM.WEIGHTS$weights,
+            design = VOOM.WEIGHTS$design,
+            block = COVARIATES$Donor_ID, 
+            correlation = correlation$cor)
+# Fit contrast
+contrast = makeContrasts(contrasts=c(
+  "Tissue.SourceDiagnosisCBE.AD-Tissue.SourceDiagnosisCBE.CONTROL",
+  "Tissue.SourceDiagnosisCBE.PATH_AGE-Tissue.SourceDiagnosisCBE.CONTROL",
+  "Tissue.SourceDiagnosisCBE.PSP-Tissue.SourceDiagnosisCBE.CONTROL",
+  "Tissue.SourceDiagnosisCBE.AD-Tissue.SourceDiagnosisCBE.PATH_AGE",
+  "Tissue.SourceDiagnosisTCX.AD-Tissue.SourceDiagnosisTCX.CONTROL",
+  "Tissue.SourceDiagnosisTCX.PATH_AGE-Tissue.SourceDiagnosisTCX.CONTROL",
+  "Tissue.SourceDiagnosisTCX.PSP-Tissue.SourceDiagnosisTCX.CONTROL",
+  "Tissue.SourceDiagnosisTCX.AD-Tissue.SourceDiagnosisTCX.PATH_AGE"),
+  levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.SourceDiagnosis','',Comparison),
+                Study = 'MAYO',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue.ref','reference'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue.ag','against'), sep = '\\.') %>%
+  tidyr::unite(Comparison, reference, against, sep = '-') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue.ref) %>%
+  group_by(Tissue.ref, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(Tissue.ref+.~Comparison, scales = 'fixed')
+p
+all.diff.exp = list(SourceDiagnosis = DE)
+all.fit = list(SourceDiagnosis = FIT)
+```
+
+### Differential expression analysis (with Tissue.Diagnosis as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of Tissue.Diagnosis
+1. CER.AD: Alzheimers disease samples from cerebellum region
+2. CER.CONTROL: Control samples from cerebellum region
+3. CER.OTHER: Progressive supranuclear palsy and pathological aging samples from Cerebellum region
+4. TCX.AD: Alzheimers disease samples from temporal cortex region
+5. TCX.CONTROL: Control samples from temporal cortex region
+6. TCX.OTHER: Progressive supranuclear palsy and pathological aging samples from temporal cortex region
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp.1, fig.height=10, fig.width=18}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$Donor_ID, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            weights = VOOM.WEIGHTS$weights,
+            design = VOOM.WEIGHTS$design,
+            block = COVARIATES$Donor_ID, 
+            correlation = correlation$cor)
+# Fit contrast
+contrast = makeContrasts(contrasts=c(
+  "Tissue.DiagnosisCBE.AD-Tissue.DiagnosisCBE.CONTROL",
+  "Tissue.DiagnosisCBE.AD-Tissue.DiagnosisCBE.OTHER",
+  "Tissue.DiagnosisCBE.OTHER-Tissue.DiagnosisCBE.CONTROL",
+  "Tissue.DiagnosisTCX.AD-Tissue.DiagnosisTCX.CONTROL",
+  "Tissue.DiagnosisTCX.AD-Tissue.DiagnosisTCX.OTHER",
+  "Tissue.DiagnosisTCX.OTHER-Tissue.DiagnosisTCX.CONTROL"),
+  levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
+                Study = 'MAYO',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue.ref','reference'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue.ag','against'), sep = '\\.') %>%
+  tidyr::unite(Comparison, reference, against, sep = '-') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue.ref) %>%
+  group_by(Tissue.ref, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(Tissue.ref+.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis = DE))
+all.fit = c(all.fit, list(Diagnosis = FIT))
+```
+
+### Associate differential expression results with gc content, gene length and average expression
+```{r associate.de, fig.height=10, fig.width=15}
+pl = list()
+pl[[1]] = ggplot(DE %>%
+                   dplyr::filter(Comparison == 'AD-CONTROL'), 
+                 aes(x = log10(gene.length), y = logFC, color = Direction)) + geom_point() 
+pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene.length), y = logFC))
+pl[[1]] = pl[[1]] + facet_grid(Tissue.ref+.~Comparison) + scale_color_manual(values = c('green','grey','red'))
+pl[[1]] = pl[[1]] + theme(legend.position = 'top')
+pl[[2]] = ggplot(DE %>%
+                   dplyr::filter(Comparison == 'AD-CONTROL'), 
+                 aes(x = percentage_gc_content, y = logFC, color = Direction)) + geom_point()
+pl[[2]] = pl[[2]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = percentage_gc_content, y = logFC))
+pl[[2]] = pl[[2]] + facet_grid(Tissue.ref+.~Comparison) + scale_color_manual(values = c('green','grey','red'))
+pl[[2]] = pl[[2]] + theme(legend.position = 'top')
+pl[[3]] = ggplot(DE %>%
+                   dplyr::filter(Comparison == 'AD-CONTROL'), 
+                 aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
+pl[[3]] = pl[[3]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = AveExpr, y = logFC))
+pl[[3]] = pl[[3]] + facet_grid(Tissue.ref+.~Comparison) + scale_color_manual(values = c('green','grey','red'))
+pl[[3]] = pl[[3]] + theme(legend.position = 'top')
+multiplot(plotlist = pl, cols = 3)
+```
+
+### Differential expression analysis (with Tissue.APOE as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of Tissue.Diagnosis
+1. CBE.0: No APOE4 allele in cerebellum
+2. CBE.1: 1 APOE4 allele in cerebellum
+3. CBE.2: 2 APOE4 allele in cerebellum
+4. TCX.0: No APOE4 allele in temporal cortex
+5. TCX.1: 1 APOE4 allele in temporal cortex
+6. TCX.2: 2 APOE4 allele in temporal cortex
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp.2, fig.height=10, fig.width=18}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[3], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$Donor_ID, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            weights = VOOM.WEIGHTS$weights,
+            design = VOOM.WEIGHTS$design,
+            block = COVARIATES$Donor_ID, 
+            correlation = correlation$cor)
+# Fit contrast
+contrast = makeContrasts(contrasts=c(
+  "Tissue.APOE4CBE.2-Tissue.APOE4CBE.0",
+  "Tissue.APOE4CBE.2-Tissue.APOE4CBE.1",
+  "Tissue.APOE4CBE.1-Tissue.APOE4CBE.0",
+  "Tissue.APOE4TCX.2-Tissue.APOE4TCX.0",
+  "Tissue.APOE4TCX.2-Tissue.APOE4TCX.1",
+  "Tissue.APOE4TCX.1-Tissue.APOE4TCX.0"),
+  levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.APOE4','',Comparison),
+                Study = 'MAYO',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue.ref','reference'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue.ag','against'), sep = '\\.') %>%
+  dplyr::mutate(reference = paste0('APOE4',reference),
+                against = paste0('APOE4',against)) %>%
+  tidyr::unite(Comparison, reference, against, sep = '-') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue.ref) %>%
+  group_by(Tissue.ref, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(Tissue.ref+.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(APOE4 = DE))
+all.fit = c(all.fit, list(APOE4 = FIT))
+```
+
+### Differential expression analysis (with Tissue.Diagnosis x Sex as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp2, fig.height=5, fig.width=18}
+# Get design matrix
+COVARIATES$Tissue.Diagnosis.Sex = paste(COVARIATES$Tissue.Diagnosis, COVARIATES$Sex, sep = '.') %>%
+  factor()
+DESIGN = getDesignMatrix(COVARIATES[, c('Tissue.Diagnosis.Sex', setdiff(postAdjustCovars, 'Sex')), drop = F], 
+                         Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$Donor_ID, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            weights = VOOM.WEIGHTS$weights,
+            design = VOOM.WEIGHTS$design,
+            block = COVARIATES$Donor_ID, 
+            correlation = correlation$cor)
+# Fit contrast
+contrast = makeContrasts(contrasts=c(
+  "Tissue.Diagnosis.SexCBE.AD.FEMALE-Tissue.Diagnosis.SexCBE.CONTROL.FEMALE",
+  "Tissue.Diagnosis.SexCBE.AD.MALE-Tissue.Diagnosis.SexCBE.CONTROL.MALE",
+
+  "Tissue.Diagnosis.SexTCX.AD.FEMALE-Tissue.Diagnosis.SexTCX.CONTROL.FEMALE",
+  "Tissue.Diagnosis.SexTCX.AD.MALE-Tissue.Diagnosis.SexTCX.CONTROL.MALE"),
+  levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis.Sex','',Comparison),
+                Study = 'MAYO',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue.ref','Dx.ref','Sex.ref'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue.ag','Dx.ag','Sex.ag'), sep = '\\.') %>%
+  tidyr::unite(Comparison, Dx.ref, Dx.ag, sep = '-') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue.ref, Sex.ref) %>%
+  group_by(Tissue.ref, Sex.ref, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(Comparison+.~Tissue.ref+Sex.ref, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis.Sex = DE))
+all.fit = c(all.fit, list(Diagnosis.Sex = FIT))
+```
+
+### Differential expression analysis (with Tissue.Diagnosis x AgeAtDeath as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp3, fig.height=5, fig.width=18, cache = FALSE}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c('Tissue.Diagnosis', setdiff(postAdjustCovars, 'AgeAtDeath')), drop = F], 
+                         Intercept = F)
+DESIGN$design[,grep('Tissue.Diagnosis',colnames(DESIGN$design))] = DESIGN$design[,grep('Tissue.Diagnosis',colnames(DESIGN$design))] * COVARIATES[,'AgeAtDeath']
+colnames(DESIGN$design)[grep('Tissue.Diagnosis',colnames(DESIGN$design))] = 
+  paste(colnames(DESIGN$design)[grep('Tissue.Diagnosis',colnames(DESIGN$design))],'AOD', sep = '.')
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Re-estimate voom weights
+VOOM.WEIGHTS = voom(cnts,
+                    design=DESIGN$design, plot=F,
+                    block = COVARIATES$Donor_ID, 
+                    correlation = correlation$cor)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            weights = VOOM.WEIGHTS$weights,
+            design = VOOM.WEIGHTS$design,
+            block = COVARIATES$Donor_ID, 
+            correlation = correlation$cor)
+# Fit contrast
+contrast = makeContrasts(contrasts=c(
+  "Tissue.DiagnosisCBE.AD.AOD-Tissue.DiagnosisCBE.CONTROL.AOD",
+  "Tissue.DiagnosisTCX.AD.AOD-Tissue.DiagnosisTCX.CONTROL.AOD"),
+  levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
+                Study = 'MAYO',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction)) %>%
+  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
+  tidyr::separate(from.state, c('Tissue.ref','Dx.ref','AOD.ref'), sep = '\\.') %>%
+  tidyr::separate(to.state, c('Tissue.ag','Dx.ag','AOD.ag'), sep = '\\.') %>%
+  tidyr::unite(Comparison, Dx.ref, Dx.ag, sep = '-') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique())
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue.ref, AOD.ref) %>%
+  group_by(Tissue.ref, AOD.ref, Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(Comparison+.~Tissue.ref+AOD.ref, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis.AOD = DE))
+all.fit = c(all.fit, list(Diagnosis.AOD = FIT))
+```
+
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
@@
 
+# Store differential expression results
+rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
+  write.table(file = 'MAYO_CBE_TCX_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_CBE_TCX_DiffExpression.tsv', name = 'Differential Expression Results (Tissue.Diagnosis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'diffExp'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store all model fits
+save(list = 'all.fit', file = 'MAYO_CBE_TCX_allfits.RData')
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='MAYO_CBE_TCX_allfits.RData', name = 'All model fits (Tissue.Diagnosis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'modelFits'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 stopCluster(cl)

### 2019-11-23 code/ROSMAP_Regress_hg38.Rmd
catch code Up

@@
 p
+
+##JKG Add in in case lack of valuse adds singularity issue
+#if( length(table(MODEL0[,'PCT_RIBOSOMAL_BASES'])) < .05*dim(MODEL0)[1] ){
+#  MODEL0 <- MODEL0[,colnames(MODEL0)[colnames(MODEL0)!='PCT_RIBOSOMAL_BASES'] ]
+#}else{}
+#if( length(table(MODEL1[,'PCT_RIBOSOMAL_BASES'])) < .05*dim(MODEL1)[1] ){
+#  MODEL1 <- MODEL1[,colnames(MODEL1)[colnames(MODEL1)!='PCT_RIBOSOMAL_BASES'] ]
+#}else{}
+
 # Estimate surrogate variables
@@
   VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
+```
+
+### Differential expression analysis (with cogdx as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of cogdx scores
+1. NCI, No cognitive impairment (No impaired domains)
+2. MCI, Mild cognitive impairment (One impaired domain) and NO other cause of CI
+3. MCI, Mild cognitive impairment (One impaired domain) AND another cause of CI
+4. AD, Alzheimer's disease and NO other cause of CI (NINCDS PROB AD)
+5. AD, Alzheimer's disease AND another cause of CI (NINCDS POSS AD)
+6. Other dementia. Other primary cause of dementia
+
+Genes that are differentially expressed at an FDR <= 0.05 are
+```{r diff.exp, fig.height=6, fig.width=18, cache=FALSE}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[1], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Estimate voom weights for dispersion control
+VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            design = DESIGN$design,
+            weights = VOOM.WEIGHTS$weights)
+# Fit contrast
+contrast = makeContrasts(contrasts=c("cogdx2-cogdx1",
+                                     "cogdx4-cogdx1",
+                                     "cogdx4-cogdx2"),
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:3, function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  dplyr::left_join(GENE.PARAM %>%
+                     dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+                     unique()) %>%
+  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction))
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(.~Comparison, scales = 'fixed')
+p
+all.diff.exp = list(cogdx = DE)
+all.fit = list(cogdx = FIT)
+```
+
+### Differential expression analysis (with Diagnosis as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of Diagnosis
+1. AD: cogdx = 4, braaksc >= 4 and ceradsc <= 2
+2. CONTROL: cogdx = 1, braaksc <= 3 and ceradsc >= 3
+3. OTHER: All the other samples
+
+Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
+```{r diff.exp1, fig.height=6, fig.width=18, cache=FALSE}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+# Estimate voom weights for dispersion control
+VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            design = DESIGN$design,
+            weights = VOOM.WEIGHTS$weights)
+# Fit contrast
+contrast = makeContrasts(contrasts=c("DiagnosisAD-DiagnosisCONTROL",
+                                     "SexFEMALE"),
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = c('AD-CONTROL','FEMALE-MALE')
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique()) %>%
+  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction))
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = DE %>% dplyr::filter(Comparison == 'AD-CONTROL') %>% 
+  ggplot(aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis = DE))
+all.fit = c(all.fit, list(Diagnosis = FIT))
+```
+
+### Associate differential expression results with gc content, gene length and average expression
+```{r associate.de, fig.height=10, fig.width=15}
+pl = list()
+DE = DE %>% dplyr::filter(Comparison == 'AD-CONTROL')
+pl[[1]] = ggplot(DE, aes(x = log10(gene.length), y = logFC, color = Direction)) + geom_point() 
+pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene.length), y = logFC))
+pl[[1]] = pl[[1]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
+pl[[1]] = pl[[1]] + theme(legend.position = 'top')
+pl[[2]] = ggplot(DE, aes(x = percentage_gc_content, y = logFC, color = Direction)) + geom_point()
+pl[[2]] = pl[[2]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = percentage_gc_content, y = logFC))
+pl[[2]] = pl[[2]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
+pl[[2]] = pl[[2]] + theme(legend.position = 'top')
+pl[[3]] = ggplot(DE, aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
+pl[[3]] = pl[[3]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = AveExpr, y = logFC))
+pl[[3]] = pl[[3]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
+pl[[3]] = pl[[3]] + theme(legend.position = 'top')
+multiplot(plotlist = pl, cols = 3)
+```
+
+### Differential expression analysis (with APOE status as primary variable)
+Differential expression is performed on the primary variable by controlling for covariates identified above
+
+Interpretation of apoe_genotype
+1. 0: No apoe4 allele
+2. 1: 1 apoe4 allele
+3. 2: 2 apoe4 allele
+
+Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
+```{r diff.exp2, fig.height=6, fig.width=18, cache=FALSE}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[3], postAdjustCovars), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+DESIGN$design = na.omit(DESIGN$design)
+# Estimate voom weights for dispersion control
+VOOM.WEIGHTS = voom(cnts[,rownames(DESIGN$design)], design=DESIGN$design, plot=F)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E[,rownames(DESIGN$design)],
+            design = DESIGN$design,
+            weights = VOOM.WEIGHTS$weights)
+# Fit contrast
+contrast = makeContrasts(contrasts=c("APOE42-APOE40", "APOE42-APOE41", "APOE41-APOE40"),
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = colnames(contrast)
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique()) %>%
+  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction))
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Apoe = DE))
+all.fit = c(all.fit, list(Apoe = FIT))
+```
+
+### Differential expression analysis (with Diagnosis and Sex)
+Differential expression is performed on the Diagnosis x Sex variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
+```{r diff.exp3, fig.height=6, fig.width=18, cache=FALSE}
+## Modeling Diagnosis, msex and age_death conjointly
+COVARIATES$Diagnosis.Sex = paste(COVARIATES$Diagnosis,COVARIATES$Sex, sep = '.') %>%
+  factor
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c('Diagnosis.Sex', setdiff(postAdjustCovars, 'Sex')), drop = F], Intercept = F)
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+colnames(DESIGN$design) = gsub('Diagnosis.Sex','',colnames(DESIGN$design))
+# Estimate voom weights for dispersion control
+VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            design = DESIGN$design,
+            weights = VOOM.WEIGHTS$weights)
+# Fit contrast
+contrast = makeContrasts(contrasts=c("(AD.FEMALE+AD.MALE)/2-(CONTROL.FEMALE+CONTROL.MALE)/2",
+                                     "(AD.FEMALE+CONTROL.FEMALE)/2-(AD.MALE+CONTROL.MALE)/2",
+                                     "(AD.FEMALE-CONTROL.FEMALE)/2-(AD.MALE-CONTROL.MALE)/2",
+                                     "AD.FEMALE-CONTROL.FEMALE",
+                                     "AD.MALE-CONTROL.MALE"),
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differnetial expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = c('AD-CONTROL','FEMALE-MALE','AD-CONTROL.IN.FEMALE-MALE','AD-CONTROL.IN.FEMALE', 'AD-CONTROL.IN.MALE')
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique()) %>%
+  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction))
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(.~Comparison, scales = 'fixed')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis.Sex = DE))
+all.fit = c(all.fit, list(Diagnosis.Sex = FIT))
+```
+
+### Differential expression analysis (with Diagnosis and AOD)
+Differential expression is performed on the Diagnosis x AOD variable by controlling for covariates identified above
+
+Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
+```{r diff.exp4, fig.height=6, fig.width=18, cache=FALSE}
+# Get design matrix
+DESIGN = getDesignMatrix(COVARIATES[, c('Diagnosis', setdiff(postAdjustCovars, 'age_death')), drop = F], Intercept = F)
+ind = grep('Diagnosis', colnames(DESIGN$design))
+DESIGN$design[,ind] = DESIGN$design[,ind] * COVARIATES[rownames(DESIGN$design),'age_death']
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+colnames(DESIGN$design) = gsub('Diagnosis','AOD.',colnames(DESIGN$design))
+# Estimate voom weights for dispersion control
+VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
+# Fit linear model using new weights and new design
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            design = DESIGN$design,
+            weights = VOOM.WEIGHTS$weights)
+# Fit contrast
+contrast = makeContrasts(contrasts=c("AOD.AD-AOD.CONTROL",
+                                     "(AOD.AD+AOD.CONTROL)/2"),
+                         levels = colnames(FIT$coefficients))
+FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
+FIT.CONTR = eBayes(FIT.CONTR)
+# Get differential expression
+DE = lapply(1:dim(contrast)[2], function(i, FIT){
+  topTable(FIT, coef=i, number = 50000, confint = T) %>%
+    rownameToFirstColumn('ensembl_gene_id')
+}, FIT.CONTR)
+names(DE) = c('AOD.AD-AOD.CONTROL','AOD')
+DE = DE %>% 
+  rbindlist(idcol = 'Comparison') %>%
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gc_content, gene.length) %>%
+              unique()) %>%
+  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
+                Direction = logFC/abs(logFC),
+                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
+                Direction = as.character(Direction))
+DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
+writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
+tmp = DE %>%
+  dplyr::select(ensembl_gene_id, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
+  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
+  spread(Direction, FDR_0_05_FC_1.2) 
+kable(tmp)
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point()
+p = p + scale_color_manual(values = c('green','grey','red'))
+p = p + facet_grid(.~Comparison, scales = 'free_x')
+p
+all.diff.exp = c(all.diff.exp, list(Diagnosis.AOD = DE))
+all.fit = c(all.fit, list(Diagnosis.AOD = FIT))
 ```
@@
 # Store SVA results
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_Corrected.tsv', sep = '\t', quote=F)
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Corrected.tsv', sep = '\t', quote=F)
 ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Corrected.tsv', name = 'Normalised, covariates, and surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
@@
 
+# Store differential expression results
+rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
+  write.table(file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'Diff_Exp'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# Store all differential expression models
+save(all.fit, file = 'ROSMAP_Models.RData')
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Models.RData', name = 'All Limma Models', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'RData'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 stopCluster(cl)

### 2019-11-25 code/metaAnalysisForDiffExp_hg38.Rmd
Add Meta Analysis

---
title: "Meta analysis of reprocessed RNASeq data from AMP-AD for hg38 Reprocessed Data (all 7 brain regions)"
author: "Adapted from Thanneer Perumal's code"
date: "`r date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis)
library(data.table)
library(plyr)
library(tidyverse)
#library(synapser)
library(knitr)
library(githubr)
#synLogin()
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21313899';
activityName = 'Meta analysis of differential expression';
activityDescription = 'Fixed and random effect meta-analysis of AMP-AD data hg38 Reprocessed Data (all 7 brain regions)';
thisFileName <- 'metaAnalysisForDiffExp_hg38.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='geneLevelAnalysis')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

## Data download
### Get study specific covariates and adjusted expression from synapse

```{r get.exp}
# Function to read tsv/csv files from synapse
downloadFile <- function(id){ 
  fread(syn_temp$get(id)$path, data.table = F)
}
# Read covariates
covar.ids = c(ROSMAP = 'syn8456631', MSSM = 'syn8484996', MAYO = 'syn8466814')
all.used.ids = as.character(covar.ids)
covar =  covar.ids %>%
  lapply(downloadFile)
# Read adjusted expression
#_#expr.ids = c(ROSMAP = 'syn8456719', MSSM = 'syn8485027', MAYO = 'syn8466826')
expr.ids = c(ROSMAP = 'syn21292041', MSSM = 'syn21285564', MAYO = 'syn21291908')
all.used.ids = c(all.used.ids, as.character(expr.ids))
expr =  expr.ids %>%
  lapply(downloadFile) %>%
  plyr::join_all(type = 'inner')
```

```{r modify.covar}
covar$ROSMAP = covar$ROSMAP %>%
  dplyr::select(SampleID, Sex, Diagnosis, APOE4) %>%
  dplyr::mutate(Tissue = 'DLPFC')
covar$MSSM = covar$MSSM %>%
  dplyr::select(SampleID, SEX, Tissue.Diagnosis, Tissue.APOE4) %>%
  dplyr::rename(Sex = SEX) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue1', 'Diagnosis'), sep = '\\.') %>%
  tidyr::separate(Tissue.APOE4, c('Tissue', 'APOE4'), sep = '\\.')
covar$MAYO = covar$MAYO %>%
  dplyr::select(SampleID, Sex, Tissue.Diagnosis, Tissue.APOE4) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue1', 'Diagnosis'), sep = '\\.') %>%
  tidyr::separate(Tissue.APOE4, c('Tissue', 'APOE4'), sep = '\\.')
covar = covar %>%
  data.table::rbindlist(use.names = T, fill = T, idcol = 'Study') %>%
  dplyr::select(-Tissue1)
```

## Perform fixed and random effect meta-analysis for each gene across 7 different brain regions
#### Meta-analysis of AD-CONTROL
```{r ad.cntrl}
# Mean and sd of gene expression in each tissue x diagnosis group
tissue.dx.summary = plyr::ddply(covar, .(Tissue, Diagnosis), .fun = function(x, y){
  data.frame(ensembl_gene_id = y$ensembl_gene_id,
             n = dim(x)[1],
             mn = rowMeans(y[,x$SampleID], na.rm = T),
             sd = apply(y[,x$SampleID], 1, sd, na.rm = T))
}, expr)
# Perform meta-analysis for AD-CONTROL comparison
meta.anlz.ad_cntrl = plyr::ddply(tissue.dx.summary, .(ensembl_gene_id), .fun = function(x){
  exp.effect = dplyr::filter(x, Diagnosis == 'AD')
  rownames(exp.effect) = exp.effect$Tissue
  cntrl.effect = dplyr::filter(x, Diagnosis == 'CONTROL')
  rownames(cntrl.effect) = cntrl.effect$Tissue
  cntrl.effect = cntrl.effect[rownames(exp.effect), ]

  tmp = metacont(exp.effect$n, exp.effect$mn, exp.effect$sd, 
                 cntrl.effect$n, cntrl.effect$mn, cntrl.effect$sd,
                 studlab = exp.effect$Tissue,
                 sm = 'SMD', method.smd = 'Hedges',
                 method.tau = 'REML')

  return(data.frame(tmp[c('TE.fixed', 'seTE.fixed', 'lower.fixed', 'upper.fixed', 'zval.fixed', 'pval.fixed',
                   'TE.random', 'seTE.random', 'lower.random', 'upper.random', 'zval.random', 'pval.random',
                   'Q', 'tau', 'H', 'I2')]))
}, .parallel = TRUE, .paropts = list(.packages = c('meta', 'dplyr'))) %>%
  dplyr::mutate(fdr.fixed = p.adjust(pval.fixed, method = 'fdr'),
                fdr.random = p.adjust(pval.random, method = 'fdr'))
p = list()
p[[1]] = ggplot(meta.anlz.ad_cntrl, aes(x = -log10(fdr.fixed), y = -log10(fdr.random)))+geom_point()
p[[2]] = ggplot(meta.anlz.ad_cntrl, aes(y = -log10(fdr.fixed), x = TE.fixed))+geom_point()+geom_hline(yintercept = -log10(0.05), color = 'red')
p[[3]] = ggplot(meta.anlz.ad_cntrl, aes(y = -log10(fdr.random), x = TE.random))+geom_point()+geom_hline(yintercept = -log10(0.05), color = 'red')
ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
# Get gene sets
tmp = meta.anlz.ad_cntrl %>%
  dplyr::select(ensembl_gene_id, TE.fixed, TE.random, fdr.fixed, fdr.random) %>%
  tidyr::gather(Feature, Value, -ensembl_gene_id) %>%
  tidyr::separate(Feature, c('Feature1', 'Model'), sep = '\\.') %>%
  tidyr::spread(Feature1, Value) %>%
  dplyr::filter(fdr <= 0.05, abs(TE) >= 0.2)
tmp$Direction[tmp$TE <= 0] = 'DOWN'
tmp$Direction[tmp$TE >= 0] = 'UP'
gs = tmp %>%
  plyr::dlply(.(Model, Direction), .fun = function(x){
    unique(x$ensembl_gene_id)
  })
names(gs) = paste0('ad.control.', names(gs))
all.gs = gs
```

#### Meta-analysis of AD-CONTROL (sex specific)
```{r ad.cntrl.sex}
# Mean and sd of gene expression in each tissue x diagnosis x sex group
tissue.dx.sex.summary = plyr::ddply(covar, .(Tissue, Diagnosis, Sex), .fun = function(x, y){
  data.frame(ensembl_gene_id = y$ensembl_gene_id,
             n = dim(x)[1],
             mn = rowMeans(y[,x$SampleID], na.rm = T),
             sd = apply(y[,x$SampleID], 1, sd, na.rm = T))
}, expr)
# Perform meta-analysis for AD-CONTROL comparison (sex specific)
meta.anlz.ad_cntrl.sex = plyr::ddply(tissue.dx.sex.summary, .(ensembl_gene_id, Sex), .fun = function(x){
  exp.effect = dplyr::filter(x, Diagnosis == 'AD')
  rownames(exp.effect) = exp.effect$Tissue
  cntrl.effect = dplyr::filter(x, Diagnosis == 'CONTROL')
  rownames(cntrl.effect) = cntrl.effect$Tissue
  cntrl.effect = cntrl.effect[rownames(exp.effect), ]

  tmp = metacont(exp.effect$n, exp.effect$mn, exp.effect$sd, 
                 cntrl.effect$n, cntrl.effect$mn, cntrl.effect$sd,
                 studlab = exp.effect$Tissue,
                 sm = 'SMD', method.smd = 'Hedges',
                 method.tau = 'REML')

  return(data.frame(tmp[c('TE.fixed', 'seTE.fixed', 'lower.fixed', 'upper.fixed', 'zval.fixed', 'pval.fixed',
                   'TE.random', 'seTE.random', 'lower.random', 'upper.random', 'zval.random', 'pval.random',
                   'Q', 'tau', 'H', 'I2')]))
}, .parallel = TRUE, .paropts = list(.packages = c('meta', 'dplyr'))) %>%
  dplyr::mutate(fdr.fixed = p.adjust(pval.fixed, method = 'fdr'),
                fdr.random = p.adjust(pval.random, method = 'fdr'))
p = list()
p[[1]] = ggplot(meta.anlz.ad_cntrl.sex, aes(x = -log10(fdr.fixed), y = -log10(fdr.random)))
p[[1]] = p[[1]] + geom_point() + facet_grid(.~Sex)
p[[2]] = ggplot(meta.anlz.ad_cntrl.sex, aes(y = -log10(fdr.fixed), x = TE.fixed))
p[[2]] = p[[2]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red') + facet_grid(.~Sex)
p[[3]] = ggplot(meta.anlz.ad_cntrl.sex, aes(y = -log10(fdr.random), x = TE.random))
p[[3]] = p[[3]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red') + facet_grid(.~Sex)
ggpubr::ggarrange(plotlist = p, ncol = 1, nrow = 3)
# Get gene sets
tmp = meta.anlz.ad_cntrl.sex %>%
  dplyr::select(ensembl_gene_id, Sex, TE.fixed, TE.random, fdr.fixed, fdr.random) %>%
  tidyr::gather(Feature, Value, -ensembl_gene_id, -Sex) %>%
  tidyr::separate(Feature, c('Feature1', 'Model'), sep = '\\.') %>%
  tidyr::spread(Feature1, Value) %>%
  dplyr::filter(fdr <= 0.05, abs(TE) >= 0.2)
tmp$Direction[tmp$TE <= 0] = 'DOWN'
tmp$Direction[tmp$TE >= 0] = 'UP'
gs = tmp %>%
  plyr::dlply(.(Sex, Model, Direction), .fun = function(x){
    unique(x$ensembl_gene_id)
  })
names(gs) = paste0('ad.control.', names(gs))
all.gs = c(all.gs, gs)
```

#### Meta-analysis of APOE42-APOE40
```{r apoe2.0}
# Mean and sd of gene expression in each Tissue x APOE4 category
tissue.apoe4.summary = plyr::ddply(covar, .(Tissue, APOE4), .fun = function(x, y){
  data.frame(ensembl_gene_id = y$ensembl_gene_id,
             n = dim(x)[1],
             mn = rowMeans(y[,x$SampleID], na.rm = T),
             sd = apply(y[,x$SampleID], 1, sd, na.rm = T))
}, expr)
# Perform meta-analysis for AD-CONTROL comparison (apoe4 2 vs 0)
meta.anlz.apoe4_2_0 = plyr::ddply(tissue.apoe4.summary, .(ensembl_gene_id), .fun = function(x){
  exp.effect = dplyr::filter(x, APOE4 == '2')
  rownames(exp.effect) = exp.effect$Tissue
  cntrl.effect = dplyr::filter(x, APOE4 == '0')
  rownames(cntrl.effect) = cntrl.effect$Tissue
  cntrl.effect = cntrl.effect[rownames(exp.effect), ]

  tmp = metacont(exp.effect$n, exp.effect$mn, exp.effect$sd, 
                 cntrl.effect$n, cntrl.effect$mn, cntrl.effect$sd,
                 studlab = exp.effect$Tissue,
                 sm = 'SMD', method.smd = 'Hedges',
                 method.tau = 'REML')

  return(data.frame(tmp[c('TE.fixed', 'seTE.fixed', 'lower.fixed', 'upper.fixed', 'zval.fixed', 'pval.fixed',
                   'TE.random', 'seTE.random', 'lower.random', 'upper.random', 'zval.random', 'pval.random',
                   'Q', 'tau', 'H', 'I2')]))
}, .parallel = TRUE, .paropts = list(.packages = c('meta', 'dplyr'))) %>%
  dplyr::mutate(fdr.fixed = p.adjust(pval.fixed, method = 'fdr'),
                fdr.random = p.adjust(pval.random, method = 'fdr'))
p = list()
p[[1]] = ggplot(meta.anlz.apoe4_2_0, aes(x = -log10(fdr.fixed), y = -log10(fdr.random)))
p[[1]] = p[[1]] + geom_point()
p[[2]] = ggplot(meta.anlz.apoe4_2_0, aes(y = -log10(fdr.fixed), x = TE.fixed))
p[[2]] = p[[2]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red')
p[[3]] = ggplot(meta.anlz.apoe4_2_0, aes(y = -log10(fdr.random), x = TE.random))
p[[3]] = p[[3]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red')
ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
# Get gene sets
tmp = meta.anlz.apoe4_2_0 %>%
  dplyr::select(ensembl_gene_id, TE.fixed, TE.random, fdr.fixed, fdr.random) %>%
  tidyr::gather(Feature, Value, -ensembl_gene_id) %>%
  tidyr::separate(Feature, c('Feature1', 'Model'), sep = '\\.') %>%
  tidyr::spread(Feature1, Value) %>%
  dplyr::filter(fdr <= 0.05, abs(TE) >= 0.2)
tmp$Direction[tmp$TE <= 0] = 'DOWN'
tmp$Direction[tmp$TE >= 0] = 'UP'
gs = tmp %>%
  plyr::dlply(.(Model, Direction), .fun = function(x){
    unique(x$ensembl_gene_id)
  })
names(gs) = paste0('apoe4.2.0.', names(gs))
all.gs = c(all.gs, gs)
```

## Store results in synapse
```{r syn.store, cache = FALSE, include=FALSE}
# Create folder to store results in synapse
CODE = Folder(name = 'Meta Analysis', parentId = parentId)
CODE = synStore(CODE)
# Write results to files
fwrite(meta.anlz.ad_cntrl, file = 'meta.anlz.ad_cntrl.tsv', sep = '\t', row.names = F, quote = F)
obj = File('meta.anlz.ad_cntrl.tsv', 
           name = 'AD-Control meta-analysis across 7 brain regions', 
           parentId = CODE$properties$id)
obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
               used = all.used.ids, executed = thisFile)
# Write results to files
fwrite(meta.anlz.ad_cntrl.sex, file = 'meta.anlz.ad_cntrl.sex.tsv', sep = '\t', row.names = F, quote = F)
obj = File('meta.anlz.ad_cntrl.sex.tsv', 
           name = 'AD-Control meta-analysis across 7 brain regions (sex specific)', 
           parentId = CODE$properties$id)
obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
               used = all.used.ids, executed = thisFile)
# Write results to files
fwrite(meta.anlz.apoe4_2_0, file = 'meta.anlz.apoe4_2_0.sex.tsv', sep = '\t', row.names = F, quote = F)
obj = File('meta.anlz.apoe4_2_0.sex.tsv', 
           name = 'AD-Control meta-analysis across 7 brain regions (APOE4)', 
           parentId = CODE$properties$id)
obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
               used = all.used.ids, executed = thisFile)
# Write results to files
save(list = c('all.gs'), file = 'all.gensets.RData')
obj = File('all.gensets.RData', 
           name = 'All gene sets (in RData format)', 
           parentId = CODE$properties$id)
obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
               used = all.used.ids, executed = thisFile)
```

```{r knit2synapse, eval=FALSE}
#library(synapser)
#library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
#synLogin()
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()

syn_temp$login()
setwd("~/TWAS/code/")

knit2synapse::knitToFolderEntity(file = "metaAnalysisForDiffExp_hg38.Rmd",
                                 parentId = "syn21313899",
                                 entityName = "Meta Analysis")
```

## Source code
[Source code in github](`r thisFile`)

### 2019-11-25 code/metaAnalysisForDiffExp_hg38.Rmd
Final Meta Analysis

@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn21313899';
-activityName = 'Meta analysis of differential expression';
+parentId = 'syn18936948';
+activityName = 'Meta analysis of differential expression hg38 Reprocessed';
 activityDescription = 'Fixed and random effect meta-analysis of AMP-AD data hg38 Reprocessed Data (all 7 brain regions)';
@@
 # Github link
-thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='geneLevelAnalysis')
+thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
 thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
@@
 covar$MSSM = covar$MSSM %>%
-  dplyr::select(SampleID, SEX, Tissue.Diagnosis, Tissue.APOE4) %>%
-  dplyr::rename(Sex = SEX) %>%
+  dplyr::select(SampleID, Sex, Tissue.Diagnosis, Tissue.APOE4) %>%
+  dplyr::rename(Sex = Sex) %>%
   tidyr::separate(Tissue.Diagnosis, c('Tissue1', 'Diagnosis'), sep = '\\.') %>%
@@
 # Create folder to store results in synapse
-CODE = Folder(name = 'Meta Analysis', parentId = parentId)
-CODE = synStore(CODE)
+#CODE = Folder(name = 'MetaAnalysis', parentId = parentId)
+#CODE = synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "MetaAnalysis", parentId = parentId))
+
+Syns_Used <- c( 'syn8456631', 'syn8484996', 'syn8466814', 'syn21292041', 'syn21285564', 'syn21291908' )
 # Write results to files
 fwrite(meta.anlz.ad_cntrl, file = 'meta.anlz.ad_cntrl.tsv', sep = '\t', row.names = F, quote = F)
-obj = File('meta.anlz.ad_cntrl.tsv', 
-           name = 'AD-Control meta-analysis across 7 brain regions', 
-           parentId = CODE$properties$id)
-obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
-               used = all.used.ids, executed = thisFile)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.ad_cntrl.tsv', name = 'AD-Control meta-analysis across 7 brain regions hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
 # Write results to files
 fwrite(meta.anlz.ad_cntrl.sex, file = 'meta.anlz.ad_cntrl.sex.tsv', sep = '\t', row.names = F, quote = F)
-obj = File('meta.anlz.ad_cntrl.sex.tsv', 
-           name = 'AD-Control meta-analysis across 7 brain regions (sex specific)', 
-           parentId = CODE$properties$id)
-obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
-               used = all.used.ids, executed = thisFile)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.ad_cntrl.sex.tsv', name = 'AD-Control meta-analysis across 7 brain regions (sex specific) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
 # Write results to files
 fwrite(meta.anlz.apoe4_2_0, file = 'meta.anlz.apoe4_2_0.sex.tsv', sep = '\t', row.names = F, quote = F)
-obj = File('meta.anlz.apoe4_2_0.sex.tsv', 
-           name = 'AD-Control meta-analysis across 7 brain regions (APOE4)', 
-           parentId = CODE$properties$id)
-obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
-               used = all.used.ids, executed = thisFile)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.apoe4_2_0.sex.tsv', name = 'AD-Control meta-analysis across 7 brain regions (APOE4) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
 # Write results to files
 save(list = c('all.gs'), file = 'all.gensets.RData')
-obj = File('all.gensets.RData', 
-           name = 'All gene sets (in RData format)', 
-           parentId = CODE$properties$id)
-obj = synStore(obj, activityName = activityName, activityDescription = activityDescription,
-               used = all.used.ids, executed = thisFile)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='all.gensets.RData', name = 'All gene sets (in RData format) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
 ```
@@
 ```{r knit2synapse, eval=FALSE}
-#library(synapser)
-#library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-#synLogin()
 synapseclient <- reticulate::import("synapseclient")
 syn_temp <- synapseclient$Synapse()
+syn_temp$login()
 
-syn_temp$login()
 setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
 
-knit2synapse::knitToFolderEntity(file = "metaAnalysisForDiffExp_hg38.Rmd",
-                                 parentId = "syn21313899",
-                                 entityName = "Meta Analysis")
+createAndKnitToFolderEntityClient(file = "metaAnalysisForDiffExp_hg38.Rmd",
+                                 parentId = "syn18936948",
+                                 folderName = "MetaAnalysis")
 ```

### 2019-11-25 code/metaAnalysisForDiffExp_NoCBE.Rmd
Add NoCBE

---
title: "Meta analysis of reprocessed RNASeq data from AMP-AD (all 6 brain regions)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis)
library(data.table)
library(plyr)
library(tidyverse)
#library(synapser)
library(knitr)
library(githubr)
#synapser::synLogin()
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

```{r synapse.parameters, include=FALSE, eval=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'Meta analysis of differential expression (No CBE)';
activityDescription = 'Fixed and random effect meta-analysis of AMP-AD data (all 6 brain regions)';
thisFileName <- 'metaAnalysisForDiffExp_NoCBE.Rmd'
# Github link
thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

## Data download
### Get study specific covariates and adjusted expression from synapse

```{r get.exp}
# Read covariates
# covar.ids = tibble(study = c("ROSMAP", "MSSM", "MAYO"), 
#                    synid = c("syn8456631", "syn8484996", "syn8466814"), 
#                    version = c("27", "20", "20"))
# covar.md =  covar.ids %>%
#   dplyr::mutate(data = map2(synid, version, 
#                             ~ readr::read_tsv(synGet(.x, version = .y)$path, col_types = cols(.default = "c"))))
# covar = unnest(covar.md, data) 
# Read adjusted expression
covar.ids = c(ROSMAP = 'syn8456631', MSSM = 'syn8484996', MAYO = 'syn8466814')
all.used.ids = as.character(covar.ids)
covar =  covar.ids %>%
  lapply(function(x) readr::read_tsv(syn_temp$get(x)$path, col_types = cols(.default = "c")))
#_#expr.ids = c(ROSMAP = 'syn8456719', MSSM = 'syn8485027', MAYO = 'syn8466826')
expr.ids = c(ROSMAP = 'syn21292041', MSSM = 'syn21285564', MAYO = 'syn21291908')
all.used.ids = c(all.used.ids, as.character(expr.ids))
expr =  expr.ids %>%
  lapply(function(x) readr::read_tsv(syn_temp$get(x)$path, col_types = cols(.default = "c"))) %>%
  plyr::join_all(type = 'inner')
```

```{r modify.covar}
covar$ROSMAP = covar$ROSMAP %>%
  dplyr::select(SampleID, Sex, Diagnosis, APOE4) %>%
  dplyr::mutate(Tissue = 'DLPFC')
covar$MSSM = covar$MSSM %>%
  dplyr::select(SampleID, Sex, Tissue.Diagnosis, Tissue.APOE4) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue1', 'Diagnosis'), sep = '\\.') %>%
  tidyr::separate(Tissue.APOE4, c('Tissue', 'APOE4'), sep = '\\.')
covar$MAYO = covar$MAYO %>%
  dplyr::select(SampleID, Sex, Tissue.Diagnosis, Tissue.APOE4) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue1', 'Diagnosis'), sep = '\\.') %>%
  tidyr::separate(Tissue.APOE4, c('Tissue', 'APOE4'), sep = '\\.')
covar = covar %>%
  data.table::rbindlist(use.names = T, fill = T, idcol = 'Study') %>%
  dplyr::select(-Tissue1)

#Remove CBE
covar <- covar[(covar$Tissue == 'CBE') == F, ]
#row.names(expr) <- expr$ensembl_gene_id
expr <- expr[, c('ensembl_gene_id', covar$SampleID) ]
for(i in 2:dim(expr)[2]){
  expr[,i] <- as.numeric(expr[,i])
}

```

## Perform fixed and random effect meta-analysis for each gene across 7 different brain regions
#### Meta-analysis of AD-CONTROL
```{r ad.cntrl}
# Mean and sd of gene expression in each tissue x diagnosis group
tissue.dx.summary = plyr::ddply(covar, .(Tissue, Diagnosis), .fun = function(x, y){
  data.frame(ensembl_gene_id = y$ensembl_gene_id,
             n = dim(x)[1],
             mn = rowMeans(y[,x$SampleID], na.rm = T),
             sd = apply(y[,x$SampleID], 1, sd, na.rm = T))
}, expr)
# Perform meta-analysis for AD-CONTROL comparison
meta.anlz.ad_cntrl = plyr::ddply(tissue.dx.summary, .(ensembl_gene_id), .fun = function(x){
  exp.effect = dplyr::filter(x, Diagnosis == 'AD')
  rownames(exp.effect) = exp.effect$Tissue
  cntrl.effect = dplyr::filter(x, Diagnosis == 'CONTROL')
  rownames(cntrl.effect) = cntrl.effect$Tissue
  cntrl.effect = cntrl.effect[rownames(exp.effect), ]

  tmp = metacont(exp.effect$n, exp.effect$mn, exp.effect$sd, 
                 cntrl.effect$n, cntrl.effect$mn, cntrl.effect$sd,
                 studlab = exp.effect$Tissue,
                 sm = 'SMD', method.smd = 'Hedges',
                 method.tau = 'REML')

  return(data.frame(tmp[c('TE.fixed', 'seTE.fixed', 'lower.fixed', 'upper.fixed', 'zval.fixed', 'pval.fixed',
                   'TE.random', 'seTE.random', 'lower.random', 'upper.random', 'zval.random', 'pval.random',
                   'Q', 'tau', 'H', 'I2')]))
}, .parallel = TRUE, .paropts = list(.packages = c('meta', 'dplyr'))) %>%
  dplyr::mutate(fdr.fixed = p.adjust(pval.fixed, method = 'fdr'),
                fdr.random = p.adjust(pval.random, method = 'fdr'))
p = list()
p[[1]] = ggplot(meta.anlz.ad_cntrl, aes(x = -log10(fdr.fixed), y = -log10(fdr.random)))+geom_point()
p[[2]] = ggplot(meta.anlz.ad_cntrl, aes(y = -log10(fdr.fixed), x = TE.fixed))+geom_point()+geom_hline(yintercept = -log10(0.05), color = 'red')
p[[3]] = ggplot(meta.anlz.ad_cntrl, aes(y = -log10(fdr.random), x = TE.random))+geom_point()+geom_hline(yintercept = -log10(0.05), color = 'red')
#ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
# Get gene sets
tmp = meta.anlz.ad_cntrl %>%
  dplyr::select(ensembl_gene_id, TE.fixed, TE.random, fdr.fixed, fdr.random) %>%
  tidyr::gather(Feature, Value, -ensembl_gene_id) %>%
  tidyr::separate(Feature, c('Feature1', 'Model'), sep = '\\.') %>%
  tidyr::spread(Feature1, Value) %>%
  dplyr::filter(fdr <= 0.05, abs(TE) >= 0.2)
tmp$Direction[tmp$TE <= 0] = 'DOWN'
tmp$Direction[tmp$TE >= 0] = 'UP'
gs = tmp %>%
  plyr::dlply(.(Model, Direction), .fun = function(x){
    unique(x$ensembl_gene_id)
  })
names(gs) = paste0('ad.control.', names(gs))
all.gs = gs
```

#### Meta-analysis of AD-CONTROL (sex specific)
```{r ad.cntrl.sex}
# Mean and sd of gene expression in each tissue x diagnosis x sex group
tissue.dx.sex.summary = plyr::ddply(covar, .(Tissue, Diagnosis, Sex), .fun = function(x, y){
  data.frame(ensembl_gene_id = y$ensembl_gene_id,
             n = dim(x)[1],
             mn = rowMeans(y[,x$SampleID], na.rm = T),
             sd = apply(y[,x$SampleID], 1, sd, na.rm = T))
}, expr)
# Perform meta-analysis for AD-CONTROL comparison (sex specific)
meta.anlz.ad_cntrl.sex = plyr::ddply(tissue.dx.sex.summary, .(ensembl_gene_id, Sex), .fun = function(x){
  exp.effect = dplyr::filter(x, Diagnosis == 'AD')
  rownames(exp.effect) = exp.effect$Tissue
  cntrl.effect = dplyr::filter(x, Diagnosis == 'CONTROL')
  rownames(cntrl.effect) = cntrl.effect$Tissue
  cntrl.effect = cntrl.effect[rownames(exp.effect), ]

  tmp = metacont(exp.effect$n, exp.effect$mn, exp.effect$sd, 
                 cntrl.effect$n, cntrl.effect$mn, cntrl.effect$sd,
                 studlab = exp.effect$Tissue,
                 sm = 'SMD', method.smd = 'Hedges',
                 method.tau = 'REML')

  return(data.frame(tmp[c('TE.fixed', 'seTE.fixed', 'lower.fixed', 'upper.fixed', 'zval.fixed', 'pval.fixed',
                   'TE.random', 'seTE.random', 'lower.random', 'upper.random', 'zval.random', 'pval.random',
                   'Q', 'tau', 'H', 'I2')]))
}, .parallel = TRUE, .paropts = list(.packages = c('meta', 'dplyr'))) %>%
  dplyr::mutate(fdr.fixed = p.adjust(pval.fixed, method = 'fdr'),
                fdr.random = p.adjust(pval.random, method = 'fdr'))
p = list()
p[[1]] = ggplot(meta.anlz.ad_cntrl.sex, aes(x = -log10(fdr.fixed), y = -log10(fdr.random)))
p[[1]] = p[[1]] + geom_point() + facet_grid(.~Sex)
p[[2]] = ggplot(meta.anlz.ad_cntrl.sex, aes(y = -log10(fdr.fixed), x = TE.fixed))
p[[2]] = p[[2]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red') + facet_grid(.~Sex)
p[[3]] = ggplot(meta.anlz.ad_cntrl.sex, aes(y = -log10(fdr.random), x = TE.random))
p[[3]] = p[[3]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red') + facet_grid(.~Sex)
#ggpubr::ggarrange(plotlist = p, ncol = 1, nrow = 3)
# Get gene sets
tmp = meta.anlz.ad_cntrl.sex %>%
  dplyr::select(ensembl_gene_id, Sex, TE.fixed, TE.random, fdr.fixed, fdr.random) %>%
  tidyr::gather(Feature, Value, -ensembl_gene_id, -Sex) %>%
  tidyr::separate(Feature, c('Feature1', 'Model'), sep = '\\.') %>%
  tidyr::spread(Feature1, Value) %>%
  dplyr::filter(fdr <= 0.05, abs(TE) >= 0.2)
tmp$Direction[tmp$TE <= 0] = 'DOWN'
tmp$Direction[tmp$TE >= 0] = 'UP'
gs = tmp %>%
  plyr::dlply(.(Sex, Model, Direction), .fun = function(x){
    unique(x$ensembl_gene_id)
  })
names(gs) = paste0('ad.control.', names(gs))
all.gs = c(all.gs, gs)
```

#### Meta-analysis of APOE42-APOE40
```{r apoe2.0}
library(meta)

# Mean and sd of gene expression in each Tissue x APOE4 category
tissue.apoe4.summary = plyr::ddply(covar, .(Tissue, APOE4), .fun = function(x, y){
  data.frame(ensembl_gene_id = y$ensembl_gene_id,
             n = dim(x)[1],
             mn = rowMeans(y[,x$SampleID], na.rm = T),
             sd = apply(y[,x$SampleID], 1, sd, na.rm = T))
}, expr)
tissue.apoe4.summary$APOE4 <- as.factor(tissue.apoe4.summary$APOE4)

# Perform meta-analysis for AD-CONTROL comparison (apoe4 2 vs 0)
exp.effect = plyr::ddply(tissue.apoe4.summary, .(ensembl_gene_id), .fun = function(x){
  exp.effect = dplyr::filter(x, APOE4 == '2')
  rownames(exp.effect) = paste0( exp.effect$ensembl_gene_id , "_", exp.effect$Tissue)
  return(EXP=exp.effect)
})
cntrl.effect = plyr::ddply(tissue.apoe4.summary, .(ensembl_gene_id), .fun = function(x){
  cntrl.effect = dplyr::filter(x, APOE4 == '0')
  rownames(cntrl.effect) = paste0( cntrl.effect$ensembl_gene_id , "_", cntrl.effect$Tissue )
  return(CNTRL=cntrl.effect)
}) 
cntrl.effect = cntrl.effect[rownames(exp.effect), ]

START <- seq.int(1, dim(exp.effect)[1], 6)
END <- seq.int(6, dim(exp.effect)[1], 6)
FOO<-as.data.frame(matrix(0, 0, 17))

for( i in 1:length(START) ){ 
  #This gene Doesn't Converge and Breaks the whole damn loop
  if( i %in% c(225)){}
  else{
    tmp = metacont(exp.effect$n[ START[i]:END[i] ], exp.effect$mn[ START[i]:END[i] ], exp.effect$sd[ START[i]:END[i] ], 
                 cntrl.effect$n[ START[i]:END[i] ], cntrl.effect$mn[ START[i]:END[i] ], cntrl.effect$sd[ START[i]:END[i] ],
                 studlab = exp.effect$Tissue[ START[i]:END[i] ],
                 sm = 'SMD', method.smd = 'Hedges',
                 method.tau = 'REML')

    FOO <- rbind(FOO, data.frame(ensembl_gene_id=exp.effect$ensembl_gene_id[START[i]], tmp[c('TE.fixed', 'seTE.fixed', 'lower.fixed', 'upper.fixed', 'zval.fixed', 'pval.fixed',
                   'TE.random', 'seTE.random', 'lower.random', 'upper.random', 'zval.random', 'pval.random',
                   'Q', 'tau', 'H', 'I2')])[1,])
  }
}

meta.anlz.apoe4_2_0 <- as.data.frame(FOO) %>%
  dplyr::mutate(fdr.fixed = p.adjust(pval.fixed, method = 'fdr'),
                fdr.random = p.adjust(pval.random, method = 'fdr'))

p = list()
p[[1]] = ggplot(meta.anlz.apoe4_2_0, aes(x = -log10(fdr.fixed), y = -log10(fdr.random)))
p[[1]] = p[[1]] + geom_point()
p[[2]] = ggplot(meta.anlz.apoe4_2_0, aes(y = -log10(fdr.fixed), x = TE.fixed))
p[[2]] = p[[2]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red')
p[[3]] = ggplot(meta.anlz.apoe4_2_0, aes(y = -log10(fdr.random), x = TE.random))
p[[3]] = p[[3]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red')
#ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
# Get gene sets
tmp = meta.anlz.apoe4_2_0 %>%
  dplyr::select(ensembl_gene_id, TE.fixed, TE.random, fdr.fixed, fdr.random) %>%
  tidyr::gather(Feature, Value, -ensembl_gene_id) %>%
  tidyr::separate(Feature, c('Feature1', 'Model'), sep = '\\.') %>%
  tidyr::spread(Feature1, Value) %>%
  dplyr::filter(fdr <= 0.05, abs(TE) >= 0.2)
tmp$Direction[tmp$TE <= 0] = 'DOWN'
tmp$Direction[tmp$TE >= 0] = 'UP'
gs = tmp %>%
  plyr::dlply(.(Model, Direction), .fun = function(x){
    unique(x$ensembl_gene_id)
  })
names(gs) = paste0('apoe4.2.0.', names(gs))
all.gs = c(all.gs, gs)
```

## Store results in synapse
```{r syn.store, cache = FALSE, eval=FALSE, include=FALSE}
# Create folder to store results in synapse
CODE <- syn_temp$store(synapseclient$Folder(name = "MetaAnalysis", parentId = parentId))
Syns_Used <- c( 'syn8456631', 'syn8484996', 'syn8466814', 'syn21292041', 'syn21285564', 'syn21291908' )

# Write results to files
fwrite(meta.anlz.ad_cntrl, file = 'meta.anlz.ad_cntrl.tsv', sep = '\t', row.names = F, quote = F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.ad_cntrl.tsv', name = 'AD-Control meta-analysis across 6 brain regions hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)

# Write results to files
fwrite(meta.anlz.ad_cntrl.sex, file = 'meta.anlz.ad_cntrl.sex.tsv', sep = '\t', row.names = F, quote = F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.ad_cntrl.sex.tsv', name = 'AD-Control meta-analysis across 6 brain regions (sex specific) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)

# Write results to files
fwrite(meta.anlz.apoe4_2_0, file = 'meta.anlz.apoe4_2_0.sex.tsv', sep = '\t', row.names = F, quote = F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='meta.anlz.apoe4_2_0.sex.tsv', name = 'AD-Control meta-analysis across 6 brain regions (APOE4) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)

# Write results to files
save(list = c('all.gs'), file = 'all.gensets.RData')
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='all.gensets.RData', name = 'All gene sets (in RData format) hg38 Reprocessed Data', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
```

```{r knit2synapse, eval=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "metaAnalysisForDiffExp_NoCBE.Rmd",
                                 parentId = "syn18936948",
                                 folderName = "MetaAnalysis_NoCBE")
```

## Source code
[Source code in github](`r thisFile`)

### 2019-11-25 code/metaAnalysisForDiffExp_NoCBE.Rmd
Add NoCBE

@@
 
+parentId = 'syn18936948';
+activityName = 'Meta analysis of differential expression (No CBE)';
+activityDescription = 'Fixed and random effect meta-analysis of AMP-AD data (all 6 brain regions)';
+thisFileName <- 'metaAnalysisForDiffExp_NoCBE.Rmd'
+# Github link
+thisRepo <- getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+
 createAndKnitToFolderEntityClient(file = "metaAnalysisForDiffExp_NoCBE.Rmd",

### 2019-11-25 code/metaAnalysisForDiffExp_NoCBE.Rmd
Fix Meta hg38 NoCBE Plots

@@
 p[[3]] = ggplot(meta.anlz.ad_cntrl, aes(y = -log10(fdr.random), x = TE.random))+geom_point()+geom_hline(yintercept = -log10(0.05), color = 'red')
-#ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
+ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
 # Get gene sets
@@
 p[[3]] = p[[3]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red') + facet_grid(.~Sex)
-#ggpubr::ggarrange(plotlist = p, ncol = 1, nrow = 3)
+ggpubr::ggarrange(plotlist = p, ncol = 1, nrow = 3)
 # Get gene sets
@@
 p[[3]] = p[[3]] + geom_point() + geom_hline(yintercept = -log10(0.05), color = 'red')
-#ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
+ggpubr::ggarrange(plotlist = p, ncol = 3, nrow = 1)
 # Get gene sets

### 2019-11-25 code/metaAnalysisForDiffExp_NoCBE.Rmd
Final Meta

@@
 ## Store results in synapse
-```{r syn.store, cache = FALSE, eval=FALSE, include=FALSE}
+```{r syn.store, cache = FALSE, eval=TRUE, include=FALSE}
 # Create folder to store results in synapse
-CODE <- syn_temp$store(synapseclient$Folder(name = "MetaAnalysis", parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = "MetaAnalysis_NoCBE", parentId = parentId))
 Syns_Used <- c( 'syn8456631', 'syn8484996', 'syn8466814', 'syn21292041', 'syn21285564', 'syn21291908' )

### 2019-12-05 code/GTExPreProcess.Rmd
Start GTEx

---
title: "Clean GTEx Genotypes for TWAS Expression Imputation"
author: 'JKG'
output: html_notebook
editor_options:
  chunk_output_type: console
---

Date of analysis update: "`r date()`"

| *Synapse ID* | *File Name* |
|  -----------------------------------------  |   ---------                      |
| syn21385083 | | 
| syn20835005 | |
| syn20835007 | |
| syn20834996 | |

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2019-12-07 code/GTExPreProcess.Rmd
GTEx Fun

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r libs, include=FALSE}
+knitr::opts_chunk$set(
+  echo=FALSE,
+  warning=FALSE,
+  message=FALSE,
+  error = FALSE,
+  tidy = FALSE,
+  cache = TRUE,
+  results='hide')
+#library(reticulate)
+```
+##Before running 
+Run the following in docker exec -it <CONTAINER> /bin/bash 
+chmod 777 /root/
+mv TWAS/ /home/<USR>/TWAS/
+chown -hR <GID>:<USR> /home/<USR>/TWAS/
+Create a ~/.synapseConfig file in the container, but do not push a container containing your credentials file to Docker Hub!!!
+
+## Login to Synapse Will need to replace with your credentials
+```{bash Login, echo=T, results='hide', eval=FALSE}
+#source /root/.bashrc
+synapse login -u <USR> -p <PSWD> --rememberMe
+
+#Alternativly you can setup a credentials file as such:
+touch ~/.synapseConfig
+echo "[authentication]" >> ~/.synapseConfig
+echo "username = <USR>" >> ~/.synapseConfig
+echo "password = <PASWD>" >> ~/.synapseConfig
 ```
 
-## R Markdown
+```{bash PLINKSetup, results='hide', eval=F, echo=TRUE}
+mkdir ~/TWAS/bin
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20190617.zip 
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191015.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191015.zip
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+rm ~/TWAS/bin/*.zip
+rm ~/TWAS/bin/toy.*
+rm ~/TWAS/bin/LICENSE
 ```
 
-## Including Plots
+## Pull GTEx Data From Synapse and Prep for Imputation
+```{bash Synapse, results='hide', echo=TRUE, cache=TRUE}
+synapse get syn21385083
+tar -xvf phg000219.v4.GTEx_Pilot_Imputation.genotype-imputed-data.c1.GRU.tar.gz
 
-You can also embed plots, for example:
+rm phg000219.v4.GTEx_Pilot_Imputation.genotype-imputed-data.c1.GRU.tar.gz
+cd phg000219.v4.GTEx_Pilot_Imputation.genotype-imputed-data.c1/
+#tar -xvf phased.vcf.tgz
+#tar -xvf info4.maf05.vcf.tgz
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+#Pull Data with needed SNPS only and fiter GTEx for that SNP List
+synapse get syn20835005
+synapse get syn20835007
+synapse get syn20834996
+
+~/TWAS/bin/plink --threads 10 --bfile All_CEU_ToTrainForTWAS --write-snplist
+
+tar -xvf all.SNPs.tgz
+touch merge.txt
+touch Log.txt
+for i in {22..1}
+  do
+    tar -xvf chr$i.all.tgz
+
+    rm chr$i.dosage
+    rm chr$i.tped
+    rm data_imputed.chr$i.gen
+    rm data_imputed.chr$i.info
+    rm chr$i.info4.exclusion.snplist.txt
+    rm chr$i.info4.maf05.exclusion.snplist.txt
+
+    vcftools --vcf chr$i.vcf --plink --out chr$i
+
+    echo $(ls -ltr chr$i.vcf) >> Log.txt
+    rm chr$i.vcf
+
+    ~/TWAS/bin/plink --threads 10 --file chr$i --extract plink.snplist -make-bed --out chr$i\_filt
+    rm chr$i.ped
+    rm chr$i.map
+    rm chr$i.log
+
+    echo "chr"$i"_filt.bed chr"$i"_filt.bim chr"$i"_filt.fam" >> merge.txt
+  done
+grep -v 'chr1_filt.bed' merge.txt > foo.txt
+mv foo.txt merge.txt
+
+~/TWAS/bin/plink --threads 10 --bfile chr1_filt --merge-list merge.txt --make-bed --out GTEx_FiltSNP_Data
+rm merge.txt
+rm Log.txt 
+rm chr*_filt.*
+
+#Move files up to code directory and then clean up 
+mv GTEx_FiltSNP_Data.* ../
+mv All_CEU_ToTrainForTWAS.* ../
+mv plink.snplist ../SNPs_for_Impute.snplist
+cd ..
+
+rm -r phg000219.v4.GTEx_Pilot_Imputation.genotype-imputed-data.c1/
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Push Results to Synapse -- Contained in ProcessData.Rmd if needed for reference
+```{r synapse.parameters.head, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
+parentId = 'syn18936948';
+activityName = 'Processed GTEx Genotypes TWAS';
+activityDescription = 'Proccessed and Filtered GTEx Genotype Data';
+thisFileName <- 'GTExPreProcess.Rmd'
+# Github link
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+```
+
+```{r synapse.parameters, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
+
+activityName = 'Processed GTEx Genotypes TWAS';
+activityDescription = 'Proccessed and Filtered GTEx Genotype Data';
+
+CODE <- syn_temp$store(synapseclient$Folder(name = "GTExGenotypes", parentId = parentId))
+
+#Set Used SynIDs For Provenance
+Syns_Used <- c("syn21385083", "syn20835005", "syn20835007", "syn20834996")
+
+# Set annotations
+Var.all.annotations = list(
+  dataType = 'Variant',
+  dataSubType = 'SNP',
+  summaryLevel = 'Nucleotide',
+  assay  = 'Genotype Array',
+  tissueTypeAbrv  = c('Mixed Tissues'), 
+  study = 'GTEx', 
+  organism = 'HomoSapiens',
+  consortium  = 'GTEx',
+  genomeAssemblyID = 'GRCh37'
+)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='GTEx_FiltSNP_Data.fam', name = 'Filtered GTEx Genotype FAM file for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='GTEx_FiltSNP_Data.bim', name = 'Filtered GTEx Genotype BIM file for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='GTEx_FiltSNP_Data.bed', name = 'Filtered GTEx Genotype BED file for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+```
+
+```{bash CleanClean, results='hide', echo=TRUE, cache=TRUE}
+rm *.bed
+rm *.fam
+rm *.bim
+rm *.nosex
+rm *.log
+rm *.snplist
+```
+
+### R Source Code
+[Github](`r thisFile`)
+
+```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+
+createAndKnitToFolderEntityClient(file = "GTExPreProcess.Rmd",
+                                          parentId ="syn18936948",
+                                          folderName = 'GTExPreProcess')
+
+```

### 2019-12-11 code/GTExPreProcess.Rmd
GTEx Processing

@@
   results='hide')
-#library(reticulate)
+library(reticulate)
+#BiocManager::install("Rgraphviz")
+#BiocManager::install("graph")
+#install.packages('CePa')
+#BiocManager::install("phantasus")
 ```
@@
 
-~/TWAS/bin/plink --threads 10 --bfile All_CEU_ToTrainForTWAS --write-snplist
+~/TWAS/bin/plink --threads 12 --bfile All_CEU_ToTrainForTWAS --write-snplist
 
@@
 
-    ~/TWAS/bin/plink --threads 10 --file chr$i --extract plink.snplist -make-bed --out chr$i\_filt
+    ~/TWAS/bin/plink --threads 12 --file chr$i --extract plink.snplist -make-bed --out chr$i\_filt
     rm chr$i.ped
@@
 
-~/TWAS/bin/plink --threads 10 --bfile chr1_filt --merge-list merge.txt --make-bed --out GTEx_FiltSNP_Data
+~/TWAS/bin/plink --threads 12 --bfile chr1_filt --merge-list merge.txt --make-bed --out GTEx_FiltSNP_Data
 rm merge.txt
@@
 rm -r phg000219.v4.GTEx_Pilot_Imputation.genotype-imputed-data.c1/
+```
+
+## Pull GTEx WGS Data From Synapse and Prep for Imputation
+This will need a bunch of space!
+```{bash Pull_WGS, results='hide', echo=TRUE, cache=TRUE}
+synapse get syn21417881
+gunzip GTEx_Analysis_2016-01-15_v7_WholeGenomeSeq_635Ind_PASS_AB02_GQ20_HETX_MISS15_PLINKQC.vcf.gz
+
+synapse get syn20835007
+
+awk '{ print $1"\t"$4 }' All_CEU_ToTrainForTWAS.bim > Positions.txt
+
+vcftools --gzvcf GTEx_Analysis_2016-01-15_v7_WholeGenomeSeq_635Ind_PASS_AB02_GQ20_HETX_MISS15_PLINKQC.vcf.gz --positions Positions.txt --plink --out Init_Filtered
+
+~/TWAS/bin/plink --threads 12 --file Init_Filtered --make-bed --out temp
+
+```
+
+### ReName the MSBB SNPS so the can be combined
+```{python ReNamer_ONE, echo=F, results='hide'}
+import sys
+import os
+import re
+
+InFile = 'All_CEU_ToTrainForTWAS.bim'
+InFileb = 'temp.bim' #LDREF_FiltSNPs.bim
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	RS_IDs[ ''.join([lst[0], '_', lst[3], ':', lst[4], '-', lst[5]] ) ] = lst[1]
+	RS_IDs[ ''.join([lst[0], '_', lst[3], ':', lst[5], '-', lst[4]] ) ] = lst[1]
+	#RS_IDs[ ''.join([lst[0], '_', lst[3]] ) ] = lst[1]
+	#RS_Pos[ ''.join([lst[0], '_', lst[3], ':', lst[4], '-', lst[5]] ) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+#OUT2 = open( ''.join([ InFileb.replace(".bim", ""), 'WTF.bim']), 'w' )
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	foo = ''.join([lst[0], '_', lst[3], ':', lst[5], '-', lst[4]] )
+	#foo = ''.join([lst[0], '_', lst[3] ] ) 
+	if foo in RS_IDs:
+	  Name = RS_IDs[  ''.join([lst[0], '_', lst[3], ':', lst[4], '-', lst[5] ] ) ]
+	  #Name = RS_IDs[  ''.join([lst[0], '_', lst[3] ] ) ]
+	  Entry = '\t'.join([ lst[0], Name, lst[2], lst[3], lst[4], lst[5] ])
+	  print >>OUT, Entry
+	else:
+	  print >>OUT, Entry
+
+F1.close()
+OUT.close()
+#OUT2.close()
+```
+
+```{bash FinalizeGenoType, results='hide', echo=TRUE, cache=TRUE}
+mv tempRenamed.bim temp.bim
+
+#Remove all Repeated SNPs 9I have no Idea how imputation will handle them
+~/TWAS/bin/plink --threads 12 --bfile All_CEU_ToTrainForTWAS --write-snplist
+~/TWAS/bin/plink --threads 12 --bfile temp --extract plink.snplist --list-duplicate-vars --make-bed --out Test
+~/TWAS/bin/plink --threads 12 --bfile Test --list-duplicate-vars suppress-first --out Duplicates
+~/TWAS/bin/plink --threads 12 --bfile Test --exclude Duplicates.dupvar --make-bed --out UniqueGTEx_GWAS_ForImpute
+
+rm Test*
+rm *.snplist
+rm temp.*
+rm Init_Filtered.*
+rm Duplicates.*
+rm positions.txt
+
+## Pull MetaData & Expression
+#_# wget https://storage.googleapis.com/gtex_analysis_v8/multi_tissue_eqtl_data/GTEx_Analysis_v8.metasoft.txt.gz
+#_# gunzip GTEx_Analysis_v8.metasoft.txt.gz
+
+wget https://storage.googleapis.com/gtex_analysis_v8/annotations/GTEx_Analysis_v8_Annotations_SampleAttributesDS.txt
+
+wget https://storage.googleapis.com/gtex_analysis_v8/rna_seq_data/GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_tpm.gct.gz
+gunzip GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_tpm.gct.gz
+```
+
+```{r GTExPheno, cache=FALSE, echo=FALSE}
+#ID Brain INDV
+Meta <- as.data.frame( data.table::fread(file='GTEx_Analysis_v8_Annotations_SampleAttributesDS.txt', header=T) )
+table(Meta$SMTS)
+
+TissueTypes <- names( table(Meta[ Meta$SMTS == 'Brain', ]$SMTSD) )
+TissueTypes <- TissueTypes[ grepl( "Cerebell", TissueTypes ) == F ]
+
+BrainMeta <- Meta[ Meta$SMTSD %in% TissueTypes, ]
+IDs <- BrainMeta$SAMPID
+
+GTEX_IDs <- paste0( do.call( rbind, strsplit( IDs,'-' ))[,1], '-', do.call( rbind, strsplit( IDs,'-' ))[,2] )
+uGTEX_IDs <-GTEX_IDs[ !duplicated(GTEX_IDs) ]
+
+FAM <- as.data.frame( data.table::fread(file='UniqueGTEx_GWAS_ForImpute.fam', header=F) )
+row.names(FAM) <- FAM$V1
+
+BRAIN_INDV <- FAM[ (FAM$V1 %in% uGTEX_IDs) == T, 1:2 ]
+write.table( BRAIN_INDV, file = "GTEX_Plink_Indvs.txt", row.names = F, col.names = F, sep='\t', quote=F)
+
+####################################################################################################
+#Get Expression
+EXP <- phantasus::read.gct('GTEx_Analysis_2017-06-05_v8_RNASeQCv1.1.9_gene_tpm.gct')
+
+exp <- EXP@assayData$exprs
+bMeta <- Meta[ Meta$SAMPID %in% IDs, ]
+bexp <- exp[ , (colnames(exp) %in% IDs) ==T ] 
+row.names( bMeta ) <- bMeta$SAMPID
+bMeta <- bMeta[ colnames(bexp), ]
+
+#Filter for relevant genes
+row.names(bexp) <- do.call( rbind, strsplit(row.names(bexp), '\\.'))[,1]
+Genes <- as.character(as.data.frame(data.table::fread( syn_temp$get('syn21011180')$path, header = T))[,1])
+bexp <- bexp[ Genes[ Genes %in% row.names(bexp) ], ]
+
+#Scale the values
+ScalerTable <- table( bMeta$SAMPID, bMeta$SMTSD)
+ScalerTable <- as.data.frame(ScalerTable)
+
+Scaled_bexp <- as.data.frame( matrix(0,dim(bexp)[1],0) )
+row.names( Scaled_bexp ) <- row.names(bexp)
+
+Scaled_bexp_Log2 <- as.data.frame( matrix(0,dim(bexp)[1],0) )
+row.names( Scaled_bexp_Log2 ) <- row.names(bexp)
+
+for( Type in names(table(ScalerTable$Var2)) ){
+  #print(head( bexp[ ,as.character(ScalerTable[ ScalerTable$Var2 == Type & ScalerTable$Freq == 1,  ]$Var1) ][,1:5]))
+  Scal <- t(scale(t(bexp[ ,as.character(ScalerTable[ ScalerTable$Var2 == Type & ScalerTable$Freq == 1,  ]$Var1)] ))) 
+  Scaled_bexp <- cbind(Scaled_bexp, Scal)
+
+  Scal_log <- t(scale(t(log2(bexp[ ,as.character(ScalerTable[ ScalerTable$Var2 == Type & ScalerTable$Freq == 1,  ]$Var1) ]+1)))) 
+  Scaled_bexp_Log2 <- cbind(Scaled_bexp_Log2, Scal_log)
+}
+
+hist(as.numeric(Scaled_bexp['ENSG00000225630',]), breaks =80)
+hist(as.numeric(Scaled_bexp_Log2['ENSG00000225630',]), breaks =80)
+
+write.table(Scaled_bexp, file = "Init_GETx_Scaled_Expression.tsv", sep="\t", row.names = T, col.names = T, quote = F)
+write.table(Scaled_bexp_Log2, file = "Init_GETx_ScaledLog2Plus1_Expression.tsv", sep="\t", row.names = T, col.names = T, quote = F)
+
+bMeta$PTID <- paste0( do.call( rbind, strsplit( colnames(Scaled_bexp), '-'))[,1], '-', do.call( rbind, strsplit( colnames(Scaled_bexp), '-'))[,2] )
+write.table(bMeta, file = "GETx_BrainMeta.tsv", sep="\t", row.names = T, col.names = T, quote = F)
+
+table(FAM$V1 %in% bMeta$PTID)
+
 ```
@@
 CODE <- syn_temp$store(synapseclient$Folder(name = "GTExGenotypes", parentId = parentId))
+CODEalt <- syn_temp$store(synapseclient$Folder(name = "GTExPreProcess", parentId = parentId))
 
@@
 
+# Set annotations
+EXP.all.annotations = list(
+  dataType = 'mRNA',
+  dataSubType = 'geneExp',
+  summaryLevel = 'gene',
+  assay  = 'RNAseq',
+  tissueTypeAbrv  = c(gsub( 'Brain - ', "", names(table(bMeta$SMTSD)))), 
+  study = 'GTEx', 
+  organism = 'HomoSapiens',
+  consortium  = 'GTEx',
+  normalizationStatus = TRUE,
+  normalizationType = 'Scaled TPM',
+  rnaquantification = 'UNK',
+  genomeAssemblyID = 'GRCh38'
+)
+
+Basic.annotations = list(
+  dataType = 'MetaData',
+  dataSubType = 'GTEx Sample Meta Data',
+  study = 'GTEx', 
+  organism = 'HomoSapiens',
+  consortium  = 'GTEx'
+)
+
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='GTEx_FiltSNP_Data.fam', name = 'Filtered GTEx Genotype FAM file for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
@@
 
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='UniqueGTEx_GWAS_ForImpute.fam', name = 'Filtered GTEx Genotype FAM file from GWAS Data for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='UniqueGTEx_GWAS_ForImpute.bed', name = 'Filtered GTEx Genotype BIM file from GWAS Data for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='UniqueGTEx_GWAS_ForImpute.bim', name = 'Filtered GTEx Genotype BED file from GWAS Data for TWAS Imputation', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Init_GETx_Scaled_Expression.tsv', name = 'TPM GTEx Brain Expression for all Profiles Z-Scaled within Tissue', parentId=CODEalt$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Init_GETx_ScaledLog2Plus1_Expression.tsv', name = 'Log2 TPM+1 GTEx Brain Expression for all Profiles Z-Scaled within Tissue', parentId=CODEalt$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='GETx_BrainMeta.tsv', name = 'Brain Sample Meta Data', parentId=CODEalt$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Basic.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='GTEX_Plink_Indvs.txt', name = 'Genotype IIDs with a BrainExpression Profile', parentId=CODEalt$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
 ```
@@
 rm *.snplist
+rm *.tsv
+rm *.txt
+rm *.gct
+rm *.gz
 ```

### 2019-12-12 code/CMC_DataProcessing.Rmd
Begin CMC Processing

---
title: "CMC_DataCleaning"
author: 'JKG'
output: html_notebook
editor_options:
  chunk_output_type: console
---

Date of analysis update: "`r date()`"

| *Synapse ID* | *File Name* |
|  -----------------------------------------  |   ---------                      |
| syn21385083 | | 
| syn20835005 | |
| syn20835007 | |
| syn20834996 | |
| syn10887100 | |
| syn10887068 | |
| syn10887117 | |
| syn10887048 | |
| syn10887106 | |
| syn10887111 | |
| syn10887027 | |
| syn10887033 | |
| syn10887101 | |
| syn10887029 | |
| syn10887044 | |
| syn11273049 | |
| syn10887084 | |
| syn10887091 | |
| syn10887078 | |
| syn10887115 | |
| syn10887041 | |
| syn10887071 | |
| syn10887037 | |
| syn10887103 | |
| syn10887102 | |
| syn10887030 | |
| syn11273048 | |
| syn10887059 | |
| syn10887040 | |
| syn10887057 | |
| syn10887065 | |
| syn10887055 | |
| syn10887119 | |
| syn10887073 | |
| syn10887050 | |
| syn10887014 | |
| syn10887021 | |
| syn10887062 | |
| syn10887107 | |
| syn10887096 | |
| syn11273047 | |
| syn10887049 | |
| syn10887058 | |
| syn10887020 | |
| syn10887031 | |
| syn10887108 | |
| syn10887056 | |
| syn11273044 | |
| syn10887032 | |
| syn10887094 | |
| syn10887069 | |
| syn10887077 | |
| syn10887019 | |
| syn10887104 | |

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')
library(reticulate)
#BiocManager::install("Rgraphviz")
#BiocManager::install("graph")
#install.packages('CePa')
#BiocManager::install("phantasus")
```
##Before running 
Run the following in docker exec -it <CONTAINER> /bin/bash 
chmod 777 /root/
mv TWAS/ /home/<USR>/TWAS/
chown -hR <GID>:<USR> /home/<USR>/TWAS/
Create a ~/.synapseConfig file in the container, but do not push a container containing your credentials file to Docker Hub!!!

## Login to Synapse Will need to replace with your credentials
```{bash Login, echo=T, results='hide', eval=FALSE}
#source /root/.bashrc
synapse login -u <USR> -p <PSWD> --rememberMe

#Alternativly you can setup a credentials file as such:
touch ~/.synapseConfig
echo "[authentication]" >> ~/.synapseConfig
echo "username = <USR>" >> ~/.synapseConfig
echo "password = <PASWD>" >> ~/.synapseConfig
```

```{bash PLINKSetup, results='hide', eval=F, echo=TRUE}
mkdir ~/TWAS/bin
wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20190617.zip 
unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191015.zip
unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191015.zip

rm ~/TWAS/bin/*.zip
rm ~/TWAS/bin/toy.*
rm ~/TWAS/bin/LICENSE
```

## Pull CMC Data From Synapse and Prep for Imputation - 
This data is protected

```{r synapse.parameters.head, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'Processed CMC Genotypes TWAS';
activityDescription = 'Proccessed and Filtered CMC Genotype Data';
thisFileName <- 'CMC_DataCProcessing.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

```{r synapse.parameters, include=FALSE, results='hide', echo=FALSE, cache=TRUE}

activityName = 'Processed GTEx Genotypes TWAS';
activityDescription = 'Proccessed and Filtered GTEx Genotype Data';

CODE <- syn_temp$store(synapseclient$Folder(name = "GTExGenotypes", parentId = parentId))
CODEalt <- syn_temp$store(synapseclient$Folder(name = "GTExPreProcess", parentId = parentId))

#Set Used SynIDs For Provenance
Syns_Used <- c("syn21385083", "syn20835005", "syn20835007", "syn20834996", "syn10887100", "syn10887068", "syn10887117", "syn10887048", "syn10887106", "syn10887111", "syn10887027", "syn10887033", "syn10887101", "syn10887029", "syn10887044", "syn11273049", "syn10887084", "syn10887091", "syn10887078", "syn10887115", "syn10887041", "syn10887071", "syn10887037", "syn10887103", "syn10887102", "syn10887030", "syn11273048", "syn10887059", "syn10887040", "syn10887057", "syn10887065", "syn10887055", "syn10887119", "syn10887073", "syn10887050", "syn10887014", "syn10887021", "syn10887062", "syn10887107", "syn10887096", "syn11273047", "syn10887049", "syn10887058", "syn10887020", "syn10887031", "syn10887108", "syn10887056", "syn11273044", "syn10887032", "syn10887094", "syn10887069", "syn10887077", "syn10887019", "syn10887104"
)

# Set annotations
Var.all.annotations = list(
  dataType = 'Variant',
  dataSubType = 'SNP',
  summaryLevel = 'Nucleotide',
  assay  = 'Genotype Array',
  tissueTypeAbrv  = c('Mixed Tissues'), 
  study = 'CMC', 
  organism = 'HomoSapiens',
  consortium  = 'CMC',
  genomeAssemblyID = 'GRCh37'
)

# Set annotations
EXP.all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay  = 'RNAseq',
  tissueTypeAbrv  = c(gsub( 'Brain - ', "", names(table(bMeta$SMTSD)))), 
  study = 'CMC', 
  organism = 'HomoSapiens',
  consortium  = 'CMC',
  normalizationStatus = TRUE,
  normalizationType = 'Scaled TPM',
  rnaquantification = 'UNK',
  genomeAssemblyID = 'GRCh38'
)

Basic.annotations = list(
  dataType = 'MetaData',
  dataSubType = 'CMC Sample Meta Data',
  study = 'CMC', 
  organism = 'HomoSapiens',
  consortium  = 'CMC'
)

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='REPLACE TEST VALUE', name = 'REPLACE TEST VALUE', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "CMC_DataProcessing.Rmd",
                                          parentId ="syn18936948",
                                          folderName = 'CMC_FilteredGenotypes')

```

### 2019-12-16 code/CMC_DataProcessing.Rmd
CMC version 2

@@
 ## Pull CMC Data From Synapse and Prep for Imputation - 
-This data is protected
+This data is protected, you wil be required to apply for access through PhsycEncode
+```{bash Pull_WGS, results='hide', echo=TRUE, cache=TRUE}
+CORES=`expr $(nproc) - 2`
+#Pull Data with needed SNPS only and fiter GTEx for that SNP List
+synapse get syn20835005
+synapse get syn20835007
+synapse get syn20834996
+~/TWAS/bin/plink --threads $CORES --bfile All_CEU_ToTrainForTWAS --write-snplist
+
+mkdir CMC_Genos
+synapse get syn10537112 --recursive --downloadLocation CMC_Genos/
+
+mkdir CMC_Filt_Genos
+touch merge.txt
+#Pull out Snps
+for i in {1..22}
+  do
+    #--positions plink.snplist 
+    bcftools norm --threads $CORES --rm-dup snps -Oz CMC_Genos/CMC_chr$i.dose.vcf.gz > CMC_Filt_Genos/Filt_CMC_chr$i.dose.vcf.gz
+    vcftools --gzvcf CMC_Filt_Genos/Filt_CMC_chr$i.dose.vcf.gz --plink --out CMC_Filt_Genos/Init_Filtered_chr$i
+    echo 'CMC_Filt_Genos/Init_Filtered_chr'$i'.ped CMC_Filt_Genos/Init_Filtered_chr'$i'.map' >> merge.txt
+  done
+grep -v 'chr1.ped' merge.txt > foo
+mv foo merge.txt
+
+#Merge Genotype
+~/TWAS/bin/plink --threads $CORES --file CMC_Filt_Genos/Init_Filtered_chr1 --merge-list merge.txt --make-bed --out Merged_Initial_CMC_Geno
+
+#Remove old Map/Ped Files
+rm CMC_Filt_Genos/Init_Filtered_chr*.map
+rm CMC_Filt_Genos/Init_Filtered_chr*.ped
+```
+
+### ReName the MSBB SNPS so the can be combined
+```{python ReNamer_ONE, echo=F, results='hide',python.reticulate=T}
+import sys
+import os
+import re
+
+InFile = 'All_CEU_ToTrainForTWAS.bim'
+InFileb = 'Merged_Initial_CMC_Geno.bim' #LDREF_FiltSNPs.bim
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	if( ''.join([ lst[0], "_", lst[3] ]) in RS_IDs):
+		Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+		Entry = '\t'.join([ lst[0], Name, lst[2], lst[3], lst[4], lst[5] ])
+		print >>OUT, Entry
+	else:
+		print >>OUT, LINE
+
+F1.close()
+OUT.close()
+```
+
+## Pull Imputation SNPS - 
+```{bash Pull_impute, results='hide', echo=TRUE, cache=TRUE}
+CORES=`expr $(nproc) - 2`
+
+mv Merged_Initial_CMC_GenoRenamed.bim Merged_Initial_CMC_Geno.bim
+~/TWAS/bin/plink --threads $CORES --bfile Merged_Initial_CMC_Geno --extract plink.snplist --make-bed --out CMC_Genos_For_Impute
+
+```
 
@@
 
-activityName = 'Processed GTEx Genotypes TWAS';
-activityDescription = 'Proccessed and Filtered GTEx Genotype Data';
+activityName = 'Processed CMC Genotypes TWAS';
+activityDescription = 'Proccessed and Filtered CMC Genotype Data';
 
-CODE <- syn_temp$store(synapseclient$Folder(name = "GTExGenotypes", parentId = parentId))
-CODEalt <- syn_temp$store(synapseclient$Folder(name = "GTExPreProcess", parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = "CMC_FilteredGenotypes", parentId = parentId))
+#CODEalt <- syn_temp$store(synapseclient$Folder(name = "CMC_FilteredGenotypes", parentId = parentId))
 
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='REPLACE TEST VALUE', name = 'REPLACE TEST VALUE', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CMC_Genos_For_Impute.bim', name = 'CMC Genotypes For Imputing exp BIM', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
 syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CMC_Genos_For_Impute.fam', name = 'CMC Genotypes For Imputing exp FAM', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CMC_Genos_For_Impute.bed', name = 'CMC Genotypes For Imputing exp BED ', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)
+```
+
+## Clean
+
+```{bash Pull_WGS, results='hide', echo=TRUE, cache=TRUE}
+rm *.fam
+rm *.bed
+rm *.bim
+rm *.fam
+rm *.nosex
+rm *.ped
+rm *.map
+rm *.missnp
+rm *.log
+rm *.snplist
+rm merge.txt
+rm -r CMC_Genos/
+rm -r CMC_Filt_Genos/
 ```

### 2019-12-31 code/CMC_Exp_DataProcessing.Rmd
CMC

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Iterative Model"
author: "Addapted from Kelsey Montgomery"
date: "11/8/2019"
output: html_document
---

Date of analysis update: "`r date()`"

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(stringr)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')
library(knitr)
library(doParallel)
library(foreach)
library(sva)
#library(reticulate)
library(R.utils)

cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('~/TWAS/utilityFunctions/parallelDuplicateCorrelation.R')
source('~/TWAS/utilityFunctions/irwsva.build.R')
source('~/TWAS/utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

### Problem Genes in the iterative normalization:
```{r prob.genes, cache=TRUE, include=FALSE}

ProbGenes <- c('ENSG00000227232', 'ENSG00000248527', 'ENSG00000285812', 'ENSG00000272455', 'ENSG00000215915', 'ENSG00000269737', 'ENSG00000157911', 'ENSG00000226029', 'ENSG00000121775', 'ENSG00000225828', 'ENSG00000116525', 'ENSG00000197982', 'ENSG00000285728', 'ENSG00000225767', 'ENSG00000229359', 'ENSG00000270629', 'ENSG00000160679', 'ENSG00000177954', 'ENSG00000227741', 'ENSG00000143257', 'ENSG00000236535', 'ENSG00000118194', 'ENSG00000143862', 'ENSG00000240219', 'ENSG00000123838', 'ENSG00000272645', 'ENSG00000143643', 'ENSG00000223694', 'ENSG00000272865', 'ENSG00000286216', 'ENSG00000179270', 'ENSG00000235760', 'ENSG00000144031', 'ENSG00000115282', 'ENSG00000232931', 'ENSG00000236440', 'ENSG00000227331', 'ENSG00000272211', 'ENSG00000229056', 'ENSG00000144410', 'ENSG00000144452', 'ENSG00000152056', 'ENSG00000183977', 'ENSG00000230409', 'ENSG00000172940', 'ENSG00000232354', 'ENSG00000281691', 'ENSG00000162267', 'ENSG00000189283', 'ENSG00000239926', 'ENSG00000239997', 'ENSG00000279349', 'ENSG00000285943', 'ENSG00000241278', 'ENSG00000240695', 'ENSG00000114113', 'ENSG00000240875', 'ENSG00000206120', 'ENSG00000229638', 'ENSG00000225473', 'ENSG00000230732', 'ENSG00000242686', 'ENSG00000249592', 'ENSG00000013810', 'ENSG00000284727', 'ENSG00000249212', 'ENSG00000251022', 'ENSG00000250361', 'ENSG00000250910', 'ENSG00000164105', 'ENSG00000283355', 'ENSG00000261360', 'ENSG00000274441', 'ENSG00000152669', 'ENSG00000205571', 'ENSG00000251634', 'ENSG00000171530', 'ENSG00000061455', 'ENSG00000164406', 'ENSG00000285605', 'ENSG00000241112', 'ENSG00000285868', 'ENSG00000241956', 'ENSG00000124588', 'ENSG00000189134', 'ENSG00000206341', 'ENSG00000204227', 'ENSG00000156639', 'ENSG00000272137', 'ENSG00000146242', 'ENSG00000255330', 'ENSG00000118514', 'ENSG00000146576', 'ENSG00000235859', 'ENSG00000183696', 'ENSG00000228735', 'ENSG00000234500', 'ENSG00000274080', 'ENSG00000205485', 'ENSG00000121716', 'ENSG00000271664', 'ENSG00000260555', 'ENSG00000236018', 'ENSG00000260721', 'ENSG00000249258', 'ENSG00000158815', 'ENSG00000197181', 'ENSG00000253200', 'ENSG00000134013', 'ENSG00000250979', 'ENSG00000253948', 'ENSG00000169946', 'ENSG00000253372', 'ENSG00000104529', 'ENSG00000234740', 'ENSG00000164970', 'ENSG00000237159', 'ENSG00000274026', 'ENSG00000136925', 'ENSG00000237461', 'ENSG00000196739', 'ENSG00000182752', 'ENSG00000286196', 'ENSG00000234771', 'ENSG00000280474', 'ENSG00000214402', 'ENSG00000197070', 'ENSG00000205696', 'ENSG00000285852', 'ENSG00000285737', 'ENSG00000188234', 'ENSG00000204172', 'ENSG00000178440', 'ENSG00000166343', 'ENSG00000229990', 'ENSG00000236552', 'ENSG00000155287', 'ENSG00000107819', 'ENSG00000273521', 'ENSG00000203772', 'ENSG00000177595', 'ENSG00000117983', 'ENSG00000247595', 'ENSG00000254622', 'ENSG00000162236', 'ENSG00000213465', 'ENSG00000110025', 'ENSG00000131620', 'ENSG00000241170', 'ENSG00000186174', 'ENSG00000186166', 'ENSG00000240970', 'ENSG00000254428', 'ENSG00000254909', 'ENSG00000110811', 'ENSG00000111664', 'ENSG00000111678', 'ENSG00000205885', 'ENSG00000256589', 'ENSG00000256682', 'ENSG00000247903', 'ENSG00000257433', 'ENSG00000139631', 'ENSG00000185482', 'ENSG00000123329', 'ENSG00000166987', 'ENSG00000178498', 'ENSG00000224713', 'ENSG00000213363', 'ENSG00000110887', 'ENSG00000257097', 'ENSG00000251497', 'ENSG00000279500', 'ENSG00000279283', 'ENSG00000198553', 'ENSG00000043355', 'ENSG00000126216', 'ENSG00000233695', 'ENSG00000258515', 'ENSG00000270433', 'ENSG00000276698', 'ENSG00000257986', 'ENSG00000258648', 'ENSG00000258682', 'ENSG00000196553', 'ENSG00000100632', 'ENSG00000258376', 'ENSG00000258891', 'ENSG00000183648', 'ENSG00000202191', 'ENSG00000223403', 'ENSG00000246451', 'ENSG00000201992', 'ENSG00000215252', 'ENSG00000243789', 'ENSG00000242866', 'ENSG00000250130', 'ENSG00000259619', 'ENSG00000247982', 'ENSG00000255346', 'ENSG00000246877', 'ENSG00000169752', 'ENSG00000274376', 'ENSG00000255769', 'ENSG00000249487', 'ENSG00000261505', 'ENSG00000261123', 'ENSG00000259895', 'ENSG00000279520', 'ENSG00000262312', 'ENSG00000188897', 'ENSG00000243716', 'ENSG00000166851', 'ENSG00000224310')

 tmp<-c(              'ENSG00000262155', 'ENSG00000260853', 'ENSG00000279789', 'ENSG00000156858', 'ENSG00000261439', 'ENSG00000089505', 'ENSG00000280334', 'ENSG00000280214', 'ENSG00000196436', 'ENSG00000140905', 'ENSG00000280182', 'ENSG00000226180', 'ENSG00000224888', 'ENSG00000170296', 'ENSG00000263934', 'ENSG00000266385', 'ENSG00000073605', 'ENSG00000236194', 'ENSG00000266967', 'ENSG00000262265', 'ENSG00000121104', 'ENSG00000243678', 'ENSG00000263089', 'ENSG00000263499', 'ENSG00000213246', 'ENSG00000172809', 'ENSG00000279382', 'ENSG00000262580', 'ENSG00000235552', 'ENSG00000263847', 'ENSG00000278983', 'ENSG00000278971', 'ENSG00000273218', 'ENSG00000268189', 'ENSG00000279203', 'ENSG00000279716', 'ENSG00000280332', 'ENSG00000267419', 'ENSG00000105185', 'ENSG00000239382', 'ENSG00000267053', 'ENSG00000233527', 'ENSG00000267254', 'ENSG00000171777', 'ENSG00000105221', 'ENSG00000268460', 'ENSG00000063177', 'ENSG00000104852', 'ENSG00000074219', 'ENSG00000167608', 'ENSG00000267838', 'ENSG00000177732', 'ENSG00000088832', 'ENSG00000131044', 'ENSG00000101421', 'ENSG00000222460', 'ENSG00000183798', 'ENSG00000101104', 'ENSG00000124172', 'ENSG00000286018', 'ENSG00000160224', 'ENSG00000223901', 'ENSG00000239415', 'ENSG00000234409', 'ENSG00000250479', 'ENSG00000279738', 'ENSG00000205702', 'ENSG00000226450', 'ENSG00000182841', 'ENSG00000279175', 'ENSG00000280434', 'ENSG00000235347', 'ENSG00000170638', 'ENSG00000185448', 'ENSG00000271199', 'ENSG00000198960', 'ENSG00000286000', 'ENSG00000241489', 'ENSG00000213397', 'ENSG00000198938', 'ENSG00000137970', 'ENSG00000230470', 'ENSG00000234781', 'ENSG00000233204', 'ENSG00000214389', 'ENSG00000235631', 'ENSG00000280379', 'ENSG00000279628', 'ENSG00000276663', 'ENSG00000263551', 'ENSG00000265316', 'ENSG00000231875', 'ENSG00000235790', 'ENSG00000242516', 'ENSG00000272040', 'ENSG00000250472', 'ENSG00000281706', 'ENSG00000184616', 'ENSG00000285581', 'ENSG00000238184', 'ENSG00000258136', 'ENSG00000136378', 'ENSG00000140682', 'ENSG00000279251', 'ENSG00000108375', 'ENSG00000279917', 'ENSG00000269318', 'ENSG00000270804', 'ENSG00000274322', 'ENSG00000235958', 'ENSG00000235038', 'ENSG00000228686', 'ENSG00000058673', 'ENSG00000234601', 'ENSG00000236549', 'ENSG00000091181', 'ENSG00000145020', 'ENSG00000248734', 'ENSG00000277769', 'ENSG00000146285', 'ENSG00000232131', 'ENSG00000228495', 'ENSG00000231760', 'ENSG00000272076', 'ENSG00000168828', 'ENSG00000279822', 'ENSG00000235010', 'ENSG00000250397', 'ENSG00000255159', 'ENSG00000258102', 'ENSG00000286067', 'ENSG00000274317', 'ENSG00000180662', 'ENSG00000259499', 'ENSG00000261207', 'ENSG00000175311', 'ENSG00000260751', 'ENSG00000261291', 'ENSG00000278668', 'ENSG00000266598', 'ENSG00000280248', 'ENSG00000276952', 'ENSG00000277829', 'ENSG00000223799', 'ENSG00000213790', 'ENSG00000271916', 'ENSG00000249863', 'ENSG00000267655', 'ENSG00000133872', 'ENSG00000224689','ENSG00000255389', 'ENSG00000253230', 'ENSG00000247137', 'ENSG00000170906', 'ENSG00000182195' )

 ProbGenes <- c(ProbGenes,tmp)
```

### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(syn_temp$get(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(syn_temp$get(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
counts = 'syn21071622'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL
# Parse gene lengths
gene_lengths = counts[,c("Geneid", "Length")]
counts$Length <- NULL
gene_lengths <- rename(gene_lengths, gene_id = Geneid)
# Get ancestry vector calculated using gemtools
ANCESTRY_ID = 'syn2511399'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = ANCESTRY_ID
ANCESTRY = downloadFile(ANCESTRY_ID) %>% 
  plyr::rename(c('DNA_report..Genotyping.Sample_ID' = 'SNP_report:Genotyping_Sample_ID'))
# Get genotype ids from synapse
GENOTYPE_ID = 'syn16816490'
ALL_USED_IDs = c(ALL_USED_IDs, GENOTYPE_ID)
GENOTYPE = downloadFile(GENOTYPE_ID) %>% 
  dplyr::select(Individual_ID, `SNP_report:Genotyping_Sample_ID`) %>%
  dplyr::inner_join(ANCESTRY)
#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 13)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, Ethnicity, Age_of_Death, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))
METADATA = metadata %>%
  dplyr::left_join(GENOTYPE) %>%
  dplyr::rename(PMI = `PMI_(in_hours)`,
                Sample_ID = Sample_RNA_ID,
                ReportExclude = `rnaSeq_report:Exclude?`,
                SampleID = Sample_RNA_ID,
                LibraryBatch = `rnaSeq_report:Library_Batch`,
                FlowcellBatch = `rnaSeq_report:Flowcell_Batch`,
                RibozeroBatch = `rnaSeq_report:Ribozero_Batch`,
                Tissue = `rnaSeq_dissection:Brain_Region`,
                MappedReads = `rnaSeq_report:Mapped_Reads`,
                IntragenicRate = `rnaSeq_report:Intragenic_Rate`, 
                IntronicRate = `rnaSeq_report:Intronic_Rate`, 
                IntergenicRate = `rnaSeq_report:Intergenic_Rate`, 
                GenesDetected = `rnaSeq_report:Genes_Detected`,
                ExpProfEfficiency = `rnaSeq_report:Expression_Profiling_Efficiency`, 
                rRNARate = `rnaSeq_report:rRNA_Rate`,
                TotalReads = `rnaSeq_report:Total_Reads`, 
                AlignmentRate = `rnaSeq_report:Percent_Aligned`,
                RIN = `rnaSeq_isolation:RIN`) %>%
  dplyr::select(SampleID, Individual_ID, Institution, Reported_Gender,Sex, Ethnicity, Age_of_Death, PMI, Dx, 
                RIN, ReportExclude, EV.1, EV.2, EV.3, EV.4, EV.5,
                LibraryBatch, FlowcellBatch, RibozeroBatch, Tissue, MappedReads, TotalReads, GenesDetected, AlignmentRate,
                IntragenicRate, IntergenicRate, IntronicRate, ExpProfEfficiency, rRNARate) %>% 
  dplyr::filter(Institution %in% c("MSSM", "Penn", "Pitt")) %>% 
  dplyr::filter(SampleID %in% colnames(counts), !is.na(SampleID)) %>%
  dplyr::mutate(Dx = forcats::fct_recode(Dx,  Other = "AFF", Other = "BP", Control = "Control", SCZ = "SCZ"))
```

### Data preprocessing
```{r preprocess.data}
ind = METADATA$SampleID[which(METADATA$ReportExclude == 1)]
writeLines(paste('Following',length(ind),'samples are marked exclude'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Ethnicity) | is.na(METADATA$Institution) | is.na(METADATA$Dx)]
writeLines(paste('Following', length(ind), 'counts are missing clinical metadata'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$PMI)]
writeLines(paste('Following', length(ind), 'counts are missing PMI'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Reported_Gender)]
writeLines(paste('Following', length(ind), 'counts are missing gender'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Age_of_Death)]
writeLines(paste('Following', length(ind), 'counts are missing age of death'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind))
ind = METADATA$SampleID [is.na(METADATA$EV.1)]
writeLines(paste('Following', length(ind), 'counts are missing ancestry information'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind))
```

```{r preprocess.data1, results='asis'}
# Match covariates to expression data
indToRetain = intersect(METADATA$SampleID, colnames(counts))
rownames(counts) <- counts$Geneid
counts = counts[,indToRetain]
rownames(METADATA) = METADATA$SampleID
METADATA = METADATA[indToRetain,]
METADATA %>% 
  group_by(Dx, Tissue) %>% 
  summarise(count = n()) %>% 
  spread(Tissue, count) %>%
  kable()
#_# Add in Dx.TissueSource
METADATA = METADATA %>%
  dplyr::mutate(Dx.Tissue = paste(Dx, Tissue, sep = '.')) %>%
  dplyr::mutate(Dx.TissueSource = paste(Dx, Tissue, Institution, sep = '.'))
```
Following sample are removed `r paste(removedIDs, collapse = ',')`

```{r gene.param}
## Get GC content from biomart
backgroundGenes = data.frame(gene_id = rownames(counts)) %>%
  dplyr::mutate(id = gene_id) %>%
  tidyr::separate(id, c('ensembl_gene_id','position'), sep = '\\.')
# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "percentage_gene_gc_content", "gene_biotype", "chromosome_name"),
                       filters = "ensembl_gene_id", values = backgroundGenes$ensembl_gene_id,
                       mart = mart)
GENE.GC.CONT = Ensemble2HGNC %>%
  dplyr::left_join(backgroundGenes) %>% 
  dplyr::select(gene_id, percentage_gene_gc_content, chromosome_name) %>%
  unique
rownames(GENE.GC.CONT) = GENE.GC.CONT$gene_id
```

### Sex Check
```{r Reported_Gender_plots}
counts$gene_id = rownames(counts) 
REPORTED.GENDER.COUNTS = GENE.GC.CONT %>% 
  left_join(counts) %>%
  dplyr::select(-one_of("percentage_gene_gc_content")) %>%
  filter(chromosome_name == "X" |chromosome_name == "Y") %>% 
  tidyr::gather(key = item, value = value, -c(gene_id, chromosome_name)) %>%
  mutate(value = log(value)) %>%
  rename(`counts(log)`= value) %>% 
  rename(SampleID = item) %>%
  left_join(METADATA[,c("SampleID", "Reported_Gender")]) %>% 
  rename(`Reported Gender` = Reported_Gender) 
##XIST and UTY expression 
#ENSG00000229807.10 and ENSG00000183878.15 
#ENSG00000229807.11
FILT <- REPORTED.GENDER.COUNTS %>% 
  filter(gene_id == "ENSG00000229807.11" | gene_id == "ENSG00000183878.15") %>% 
  dplyr::select(-one_of("chromosome_name")) %>% 
  tidyr::spread(key = gene_id, value = `counts(log)`) %>% 
  mutate(XIST = as.numeric(`ENSG00000229807.11`)) %>% 
  mutate(UTY = as.numeric(`ENSG00000183878.15`))
p = ggplot(FILT, aes (x= XIST, y = UTY)) 
p = p + geom_point(aes(color=`Reported Gender`)) 
p
```

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering}
#primaryVariable <- c("Tissue.SourceDiagnosis", "Tissue.Diagnosis", "Tissue.APOE4")
primaryVariable <- c("Dx.TissueSource", "Dx.Tissue")
#_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
FactorCovariates <- c('Individual_ID','FlowcellBatch', "Institution", "Reported_Gender", "LibraryBatch", "Tissue", "Dx.Tissue", "Dx", "RibozeroBatch")
#_#FactorCovariates <- c('Individual_ID', "Institution","Dx.Tissue", "Reported_Gender", "Dx", "RibozeroBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

#METADATA <- METADATA[ METADATA$Tissue == 'DLPFC', ]
#counts <- counts[ , METADATA$SampleID]

# Find inter relation between factor covariates
METADATA <- METADATA[ !duplicated(METADATA), ]
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
rownames(COVARIATES) <- METADATA$ID
# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, cache=FALSE, fig.width=10, fig.height=6}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left', padding  = unit(c(18,2,2,18), 'mm'))
```
### Explore metadata
```{r data.explore, cache=FALSE, fig.width = 12, fig.height = 8}

METADATA <- METADATA[ METADATA$Tissue == 'DLPFC', ]
counts <- counts[ , METADATA$SampleID]
COVARIATES=COVARIATES[ COVARIATES$Tissue == 'DLPFC' ,]
my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = RIN)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + my.theme
# AgeAtDeath
p[[2]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(Age_of_Death))) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('Age_of_Death') + my.theme
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(PMI))) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI') + my.theme
# Ribosomal bases
p[[4]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(rRNARate))) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Fraction of Ribosomal Bases') + my.theme
# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(IntronicRate))) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + my.theme
# Intergenic bases
p[[6]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(IntergenicRate))) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Intergenic Bases') + my.theme
multiplot(plotlist = p, cols = 3)
```

### Filter genes
* Remove genes that have less than 1 cpm counts in at least 50% of samples per Tissue x Diagnosis
* Remove genes with missing gene length and percentage GC content
```{r filter.genes}
COUNT<-counts[,METADATA$SampleID]
row.names(COVARIATES) <- METADATA$SampleID

Unis <- do.call(rbind, strsplit(as.character(row.names(COUNT)), '\\.'))[,1]
dups <- Unis[ duplicated(Unis) ]
Prosps <- do.call(rbind, strsplit(as.character(row.names(COUNT)), '\\.'))
Prosps <- Prosps[ (Prosps[,1] %in% dups) == F,]
keeps <- paste0( Prosps[,1], '.', Prosps[,2] )

COUNT <- COUNT[ keeps, ]

row.names(COUNT) <- do.call(rbind, strsplit(as.character(row.names(COUNT)), '\\.'))[,1]

#colnames(COVARIATES)[1] <- 'SampleID'
#colnames(COUNT) <- paste0( "CMC_", gsub("RNA_BP_PFC_","",colnames(COUNT)) )
#colnames(COUNT) <- gsub("RNA_PFC_","",colnames(COUNT)) 
#colnames(COUNT) <- gsub("RNA_ACC_","",colnames(COUNT)) 
#colnames(COUNT) <- gsub("BP_","",colnames(COUNT)) 
#tmp <- do.call(rbind, strsplit(colnames(COUNT), '_'))
#tmp[,3] <- str_pad(tmp[,3], 3, pad = "0")
#colnames(COUNT) <- paste0(tmp[,1], '_', tmp[,2], '_',tmp[,3])
#COVARIATES$SampleID <- as.character(COVARIATES$SampleID)
#row.names(COVARIATES) <- COVARIATES$SampleID
#table(METADATA$SampleID %in% colnames(COUNT))
#table(colnames(COUNT) %in% METADATA$SampleID )

genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Dx.Tissue), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)

    #processed.counts = getGeneFilteredGeneExprMatrix(COUNT[,METADATA$SampleID],
                                                     #MIN_GENE_CPM=1, 
                                                     #MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)

GENE.PARAM = syn_temp$get('syn21156161', version = 3)$path %>% 
  read.table(sep = '\t', header = T, stringsAsFactors = F)
#row.names(GENE.PARAM) <- GENE.PARAM$ensembl_gene_id
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% unique()
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% unique()
rownames(GENE.GC) = GENE.GC$ensembl_gene_id

genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gc_content)]) %>%
  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene.length)]) %>%
  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))

PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
                                                 MIN_GENE_CPM=0, 
                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
# Check gene biotype
## Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
## Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "gene_biotype"),
                       filters = "ensembl_gene_id", 
                       values = PROCESSED_COUNTS$filteredExprMatrix$genes,
                       mart = mart)
summary(factor(Ensemble2HGNC$gene_biotype)) %>%
  rownameToFirstColumn('Biotype') %>%
  dplyr::rename(fraction = DF) %>%
  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
  dplyr::filter(fraction >= 0.01) %>%
  kable
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

### Library Normalisation
Library normalisation is performed using cqn (conditional quantile normalisation)
```{r cqn}
row.names(GENE.GC) <- GENE.GC$ensembl_gene_id
row.names(GENE.LEN) <- GENE.LEN$ensembl_gene_id
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'gene.length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Outlier Analysis
#### Sample outliers
Outlier analysis is performed before library normalisation with raw cpm counts
```{r outlier.analysis, cache = FALSE, fig.width = 10}
#indToRemove = c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX",
#                '1950_TCX', '1950_CER', '1925_TCX', '1957_CER')
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  dplyr::mutate(label = SampleID) %>%
  tidyr::separate(Dx.Tissue, c('Diagnosis', 'Tissue'), sep = '\\.')
#plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Institution, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") 
p <- p + facet_grid(Tissue~.+Diagnosis, scales = 'free')
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Tissue', 'Diagnosis'), sep = '\\.')
indToRemove <- ''
p = ggplot(tmp1 %>%
             #dplyr::filter(SampleID %in% indToRemove) %>%
             droplevels(),
           aes(x = logCPM)) + geom_density() 
p = p + theme(legend.position = 'top') + facet_grid(Tissue~.+Diagnosis)
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = COVARIATES %>%
  dplyr::group_by(Dx.Tissue) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::separate(Dx.Tissue, c('Diagnosis', 'Tissue'), sep = '\\.') %>%
  tidyr::spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are: `r kable(tmp)`

#### Gene outliers
Assign NA values to genes that are above and below 3 std deviation of its distribution
```{r winsorise.data}
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
CQN.GENE_EXPRESSION$E = LOG.CPM[ (row.names(LOG.CPM) %in% ProbGenes) == F, ]
CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6

dim(NEW.COUNTS)
NEW.COUNTS <- NEW.COUNTS[ (row.names(NEW.COUNTS) %in% ProbGenes) == F, ]
dim(NEW.COUNTS)
```

### Sample clustering
PCA based clustering of samples
```{r decompse.normalise.data, cache=FALSE, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c( 'Diagnosis', 'Tissue'), sep = '\\.')
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Institution, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") + facet_grid(Tissue+.~Diagnosis, scales = 'free_y')
p
```

Tree based clustering of samples
```{r decompse.normalise.data.1, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
COVARIATES.tmp = (COVARIATES[,c(FactorCovariates), drop = F])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.no.na)))
for( i in 1:dim(COVARIATES.tmp)[2]){
  COVARIATES.tmp[,i] <- as.numeric(COVARIATES.tmp[,i])
}
COVARIATES.tmp <- COVARIATES.tmp[,2:dim(COVARIATES.tmp)[2]]
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE, fig.height=10, fig.width=20}
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Dx.Tissue, c( 'Diagnosis', 'Tissue' ), sep = '\\.')
p = ggplot(tmp1, aes(x = logCPM)) + geom_density() 
p = p + theme(legend.position = 'NONE') + facet_grid(Tissue+.~Diagnosis, scale = 'free')
p
```

Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.no.na))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
```{r preadj.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
#CQN.GENE_EXPRESSION$E.no.na <- as.data.frame(CQN.GENE_EXPRESSION$E.no.na)
COVARIATES1 <- COVARIATES[ , (colnames(COVARIATES) %in% 'Tissue') == F]
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
                                                 COVARIATES1,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preadj.covariates.plot, cache=FALSE, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Normalisation (iterative design)
Since many covariates are correlated, re-normalising and re-adjusting COUNTS with an iterative design matrix.

NOTE:
1. Using a mixed effect model where random effect is chosen as Individual_ID
2. Adding Source, FLOWCELL and Gender a priori to variable selection
3. Primary variable of interest Tissue.Diagnosis is excluded from the pool of available covariates for selection
```{r iterative.norm, results='asis'}
# Primary variable of interest
postAdjustCovars = c('Institution', 'FlowcellBatch', 'Reported_Gender');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, 
                         c(postAdjustCovars, primaryVariable, 'Individual_ID'))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
notEstimable = c()

loopCount = 0 
while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
  writeLines(paste0('Working on Loop: ', loopCount))
  writeLines(paste('Using following covariates in the model:',
                   paste(postAdjustCovars, collapse=', '),
                   'as fixed effects and Individual_ID as random effect'))

  # Post adjusted design matrix
  DM1 = getDesignMatrix(COVARIATES1[,postAdjustCovars,drop=F],Intercept = F)
  DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

  # Estimate voom weights for dispersion control
  cnts = NEW.COUNTS; cnts[is.na(cnts)] = 0
  VOOM.GENE_EXPRESSION = voom(cnts, design=DM1$design, 
                              plot=F, na.rm = T)

  # Calculate correlation values of random effects
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E
  correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
                                             block = COVARIATES1$Individual_ID,
                                             method = 'lmer')
  # correlation = list(); correlation$cor = 0.3819258

  if (!is.nan(correlation$cor)){
    # Re-estimate voom weights
    VOOM.GENE_EXPRESSION = voom(cnts, 
                                design=DM1$design, plot=F, 
                                block = COVARIATES1$Individual_ID, 
                                correlation = correlation$cor)

    # Fit linear model using new weights and new design
    VOOM.ADJUSTED.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                              design = DM1$design,
                              weights = VOOM.GENE_EXPRESSION$weights,
                              block = COVARIATES1$Individual_ID, 
                              correlation = correlation$cor)

    # Residuals after normalisation
    RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,
                                                  CQN.GENE_EXPRESSION$E)
  } else {
    notEstimable = c(notEstimable, postAdjustCovars[length(postAdjustCovars)])
    postAdjustCovars = postAdjustCovars[1:(length(postAdjustCovars)-1)]
  }

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates),
                         c(postAdjustCovars, primaryVariable, 'Individual_ID', notEstimable))
  residCovars <- residCovars[ (residCovars == 'Tissue') == F ]

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  expr = RESIDUAL.GENE_EXPRESSION; expr[is.na(expr)] = 0

  residualSigCovars = runPCAandPlotCorrelations(expr, 
                                                COVARIATES1[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

  # Add postadjusted covariates (if any)
  residCovars = setdiff(residualSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, notEstimable))
  covariatesEffects = residualSigCovars$Effects.significantCovars[residCovars]

  postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects)))
  loopCount = loopCount + 1
}
modelStr <- paste(paste(gsub('_','\\\\_',postAdjustCovars), collapse=', '),
                  'as fixed effects')
tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`

### Sanity check
```{r residual.adj, cache=FALSE, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(expr, 
                                              COVARIATES1,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
residualSigCovars[["PC_res"]][[2]]$plotData
```

Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(expr))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
PCA of residual data
```{r decompse.normalise.data2.1, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(expr, scale.=T, center = T)
# Plot first 4 PCs
plotdata <- data.frame(Individual_ID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
#COVARIATES$SampleID <- COVARIATES$Individual_ID
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'Individual_ID')) %>%
  tidyr::separate(Dx.Tissue, c('Diagnosis','Region'), sep = '\\.') %>% 
  dplyr::mutate(Region = factor(Region),
                Institution = factor(Institution))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Institution, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Region~., scales = 'free_y')
p
```
Tree based clustering of residual data
```{r decompse.normalise.data2.2, cache=FALSE, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,FactorCovariates])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(expr)))
COVARIATES.tmp <- COVARIATES.tmp[,2:dim(COVARIATES.tmp)[2]]
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Adjust data with covariates for Network Analysis
Identified covariates are regressed out from the expression matrix for network analysis
```{r network.adjust}
# Get design matrix
DESIGN.NET = getDesignMatrix(COVARIATES[, postAdjustCovars, drop = F], Intercept = F)
DESIGN.NET = DESIGN.NET$design[,linColumnFinder(DESIGN.NET$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.NET.WEIGHTS = voom(cnts, design=DESIGN.NET, plot=F)
# Re-estimate voom weights
VOOM.NET.WEIGHTS = voom(cnts, 
                        design = DESIGN.NET, plot=F,
                        block = COVARIATES$Donor_ID, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.NET.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.NET.FIT = lmFit(VOOM.NET.WEIGHTS$E,
                     weights = VOOM.NET.WEIGHTS$weights,
                     design = VOOM.NET.WEIGHTS$design,
                     block = COVARIATES$Donor_ID, 
                     correlation = correlation$cor)
# Residuals after normalisation
RESIDUAL.NET.GENE_EXPRESSION = residuals.MArrayLM(VOOM.NET.FIT,
                                                  CQN.GENE_EXPRESSION$E)
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (Tissue.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust}

FactorCovariates <- c("Individual_ID", "FlowcellBatch", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

# Find inter relation between factor covariates
#METADATA <- METADATA[ !duplicated(METADATA), ]
#COVARIATES1 = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
#rownames(COVARIATES1) <- METADATA$ID
# Convert factor covariates to factors
COVARIATES1[,FactorCovariates] = lapply(COVARIATES1[,FactorCovariates], factor)
COVARIATES1[,ContCovariates] = lapply(COVARIATES1[,ContCovariates], as.character)
COVARIATES1[,ContCovariates] = lapply(COVARIATES1[,ContCovariates], as.numeric)

# Get design matrix
DESIGN = getDesignMatrix(COVARIATES1[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)

#_#DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES1$Donor_ID, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS$E,
            weights = VOOM.WEIGHTS$weights,
            design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
            block = COVARIATES$Donor_ID, 
            correlation = correlation$cor)

# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]
# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$E)
# Compute actual variance of all principal components
expr = RESIDUAL.SVA.GENE_EXPRESSION
expr[is.na(expr)] = 0
tmp = svd(expr)
actual.var = tmp$d^2/sum(tmp$d^2)
# Compute permuted variance of all principal components
permuted.var = foreach(i = 1:20, .combine = rbind) %dopar% {
  tmp.residual = t(apply(expr, 1, sample, replace = FALSE))
  tmp = svd(tmp.residual)
  permuted.var = tmp$d^2/sum(tmp$d^2)
}
permuted.var = apply(permuted.var, 2, mean)
NUM.SV = sum(actual.var >= permuted.var[1])
# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.2)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p
# Estimate surrogate variables
SURR.VAR = irwsva.build(CQN.GENE_EXPRESSION$E.no.na,
                        MODEL1, MODEL0, n.sv = NUM.SV, 
                        B = 30, tol = 1e-20)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(MODEL1)
# Estimate voom weights for dispersion control
VOOM.SVA.WEIGHTS = voom(cnts, design=cbind(MODEL1, SURR.VAR), plot=F)
# Re-estimate voom weights
VOOM.SVA.WEIGHTS = voom(cnts, 
                        design = cbind(MODEL1, SURR.VAR), plot=F,
                        block = COVARIATES1$Donor_ID, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.SVA.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.SVA.FIT = lmFit(VOOM.SVA.WEIGHTS$E,
                     weights = VOOM.SVA.WEIGHTS$weights,
                     design = VOOM.SVA.WEIGHTS$design,
                     block = COVARIATES1$Donor_ID, 
                     correlation = correlation$cor)
# Residuals after normalisation
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(VOOM.SVA.FIT,
                                                  CQN.GENE_EXPRESSION$E)
# Add variable of interest back to the residuals
varsToAddIn = grep("Tissue.Diagnosis", colnames(MODEL1), value = T)
RESIDUAL.SVA.GENE_EXPRESSION = RESIDUAL.SVA.GENE_EXPRESSION + 
  VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21470292';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'CMCCovariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
thisFileName <- 'CMC_Exp_DataProcessing.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'CMC Covariate and Diagnosis Regression';
activityDescription = 'CMC Covariate analysis and Regrssion of Diagnosis of aligned effective counts with GRCh38 with CQN normalisation CMC';
CODE <- syn_temp$store(synapseclient$Folder(name = "Iterative_DLPFC_Normalization", parentId = parentId))
#Set Used SynIDs For Provenance
Syns_Used <- c("")

# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  tissueTypeAbrv	= c('DLPFC'), 
  study = 'CMC', 
  organism = 'HomoSapiens',
  consortium	= 'CMC',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh38'
)
# Store SVA results
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CMC_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForeQTL'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "",
                                          parentId ="syn21136908",
                                          folderName = 'CMC_AnalysisExp')
```

### 2019-12-31 code/Test.Rmd
CMC

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model"
author: "Adapted from Kelsey Montgomery"
date: "11/8/2019"
output: html_document
---

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(tidyr)
library(plyr)
library(edgeR)
library(dplyr)
library(stringr)
library(R.utils)
library(ggplot2)
library(limma)
library(psych)
library(edgeR)
library(cqn)
library(lme4)
library(biomaRt)
library(knitr)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')
library(doParallel)
library(foreach)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')
library(reticulate)
```

### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(syn_temp$get(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(syn_temp$get(id, version = version)$path, data.table = F)
}

# Download reprocessed counts
counts = 'syn21071622'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL
# Parse gene lengths
gene_lengths = counts[,c("Geneid", "Length")]
counts$Length <- NULL
gene_lengths <- rename(gene_lengths, gene_id = Geneid)
# Get ancestry vector calculated using gemtools
ANCESTRY_ID = 'syn2511399'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = ANCESTRY_ID
ANCESTRY = downloadFile(ANCESTRY_ID) %>% 
  plyr::rename(c('DNA_report..Genotyping.Sample_ID' = 'SNP_report:Genotyping_Sample_ID'))
# Get genotype ids from synapse
GENOTYPE_ID = 'syn16816490'
ALL_USED_IDs = c(ALL_USED_IDs, GENOTYPE_ID)
GENOTYPE = downloadFile(GENOTYPE_ID) %>% 
  dplyr::select(Individual_ID, `SNP_report:Genotyping_Sample_ID`) %>%
  dplyr::inner_join(ANCESTRY)
#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 13)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, Ethnicity, Age_of_Death, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))
METADATA = metadata %>%
  dplyr::left_join(GENOTYPE) %>%
  dplyr::rename(PMI = `PMI_(in_hours)`,
                ReportExclude = `rnaSeq_report:Exclude?`,
                SampleID = Sample_RNA_ID,
                LibraryBatch = `rnaSeq_report:Library_Batch`,
                FlowcellBatch = `rnaSeq_report:Flowcell_Batch`,
                RibozeroBatch = `rnaSeq_report:Ribozero_Batch`,
                Tissue = `rnaSeq_dissection:Brain_Region`,
                MappedReads = `rnaSeq_report:Mapped_Reads`,
                IntragenicRate = `rnaSeq_report:Intragenic_Rate`, 
                IntronicRate = `rnaSeq_report:Intronic_Rate`, 
                IntergenicRate = `rnaSeq_report:Intergenic_Rate`, 
                GenesDetected = `rnaSeq_report:Genes_Detected`,
                ExpProfEfficiency = `rnaSeq_report:Expression_Profiling_Efficiency`, 
                rRNARate = `rnaSeq_report:rRNA_Rate`,
                TotalReads = `rnaSeq_report:Total_Reads`, 
                AlignmentRate = `rnaSeq_report:Percent_Aligned`,
                RIN = `rnaSeq_isolation:RIN`) %>%
  dplyr::select(SampleID, Individual_ID, Institution, Reported_Gender,Sex, Ethnicity, Age_of_Death, PMI, Dx, 
                RIN, ReportExclude, EV.1, EV.2, EV.3, EV.4, EV.5,
                LibraryBatch, FlowcellBatch, RibozeroBatch, Tissue, MappedReads, TotalReads, GenesDetected, AlignmentRate,
                IntragenicRate, IntergenicRate, IntronicRate, ExpProfEfficiency, rRNARate) %>% 
  dplyr::filter(Institution %in% c("MSSM", "Penn", "Pitt")) %>% 
  dplyr::filter(SampleID %in% colnames(counts), !is.na(SampleID)) %>%
  dplyr::mutate(Dx = forcats::fct_recode(Dx,  Other = "AFF", Other = "BP", Control = "Control", SCZ = "SCZ"))
```

### Data preprocessing
```{r preprocess.data}
ind = METADATA$SampleID[which(METADATA$ReportExclude == 1)]
writeLines(paste('Following',length(ind),'samples are marked exclude'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Ethnicity) | is.na(METADATA$Institution) | is.na(METADATA$Dx)]
writeLines(paste('Following', length(ind), 'counts are missing clinical metadata'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$PMI)]
writeLines(paste('Following', length(ind), 'counts are missing PMI'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Reported_Gender)]
writeLines(paste('Following', length(ind), 'counts are missing gender'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Age_of_Death)]
writeLines(paste('Following', length(ind), 'counts are missing age of death'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind))
ind = METADATA$SampleID [is.na(METADATA$EV.1)]
writeLines(paste('Following', length(ind), 'counts are missing ancestry information'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind))
```

```{r preprocess.data1, results='asis'}
# Match covariates to expression data
indToRetain = intersect(METADATA$SampleID, colnames(counts))
rownames(counts) <- counts$Geneid
counts = counts[,indToRetain]
rownames(METADATA) = METADATA$SampleID
METADATA = METADATA[indToRetain,]
METADATA %>% 
  group_by(Dx, Tissue) %>% 
  summarise(count = n()) %>% 
  spread(Tissue, count) %>%
  kable()
METADATA = METADATA %>%
  dplyr::mutate(Dx.Tissue = paste(Dx, Tissue, sep = '.'))
```
Following sample are removed `r paste(removedIDs, collapse = ',')`

```{r gene.param}
## Get GC content from biomart
backgroundGenes = data.frame(gene_id = rownames(counts)) %>%
  dplyr::mutate(id = gene_id) %>%
  tidyr::separate(id, c('ensembl_gene_id','position'), sep = '\\.')
# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "percentage_gene_gc_content", "gene_biotype", "chromosome_name"),
                       filters = "ensembl_gene_id", values = backgroundGenes$ensembl_gene_id,
                       mart = mart)
GENE.GC.CONT = Ensemble2HGNC %>%
  dplyr::left_join(backgroundGenes) %>% 
  dplyr::select(gene_id, percentage_gene_gc_content, chromosome_name) %>%
  unique
rownames(GENE.GC.CONT) = GENE.GC.CONT$gene_id
```

### Sex Check
```{r Reported_Gender_plots}
counts$gene_id = rownames(counts) 
REPORTED.GENDER.COUNTS = GENE.GC.CONT %>% 
  left_join(counts) %>%
  dplyr::select(-one_of("percentage_gene_gc_content")) %>%
  filter(chromosome_name == "X" |chromosome_name == "Y") %>% 
  tidyr::gather(key = item, value = value, -c(gene_id, chromosome_name)) %>%
  mutate(value = log(value)) %>%
  rename(`counts(log)`= value) %>% 
  rename(SampleID = item) %>%
  left_join(METADATA[,c("SampleID", "Reported_Gender")]) %>% 
  rename(`Reported Gender` = Reported_Gender) 
##XIST and UTY expression 
#ENSG00000229807.10 (sep), .11(jul) and ENSG00000183878.15

FILT <- REPORTED.GENDER.COUNTS %>% 
  filter(gene_id == "ENSG00000229807.11" | gene_id == "ENSG00000183878.15") %>% 
  dplyr::select(-one_of("chromosome_name")) %>% 
  tidyr::spread(key = gene_id, value = `counts(log)`) %>% 
  mutate(XIST = as.numeric(`ENSG00000229807.11`)) %>% 
  mutate(UTY = as.numeric(`ENSG00000183878.15`))
p = ggplot(FILT, aes (x= XIST, y = UTY)) 
p = p + geom_point(aes(color=`Reported Gender`)) 
p
```
### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
####_# Add diagnosis in here: (Dx)
FactorCovariates <- c('Individual_ID', "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "RibozeroBatch", 'Dx', "FlowcellBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", 
                     "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
# Find inter relation between factor covariates
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
COVARIATES[,FactorCovariates] <- data.frame(lapply(COVARIATES[,FactorCovariates],function(x){
  x <- sapply(x,function(y){str_replace_all(as.character(y),'[^[:alnum:]]','_')})}))
rownames(COVARIATES) <- METADATA$SampleID
# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], function(x){
  x = as.numeric(as.character(gsub('[\\,\\%]','',x)))
})
# Add in RIN^2 values
COVARIATES$RIN2 = COVARIATES$RIN^2
ContCovariates = c(ContCovariates, 'RIN2')
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, fig.width=10, fig.height=8}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
tmp = COVARIATES.CORRELATION$ESTIMATE
tmp[COVARIATES.CORRELATION$PVAL > 0.05] = 0
h = Heatmap(tmp, col = colorRamp2(c(-1,0,1), c('blue','white','red')), name = 'AssocEstimate')
draw(h, heatmap_legend_side = 'left')
```

## Explore metatdata
```{r data.explore, fig.width = 12, fig.height = 12}
my.theme <- theme_bw() %+replace% theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1), plot.title=element_text(hjust=0.5))
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = RIN)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + my.theme
# Age of Death
p[[2]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = Age_of_Death)) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('AgeOfDeath') + my.theme
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = PMI)) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI (in hours)') + my.theme
# Intronic Rate
p[[4]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = IntronicRate)) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Intronic Rate') + my.theme
# IntergenicRate
p[[5]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = IntergenicRate)) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Intergenic Rate') + my.theme
# Transcripts Detected
p[[6]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = IntragenicRate)) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Intragenic Rate') + my.theme
# Mapped Reads
p[[7]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = MappedReads)) + geom_boxplot()
p[[7]] = p[[7]] + ggtitle('Mapped Reads') + my.theme
# PercentAligned
p[[8]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = TotalReads)) + geom_boxplot()
p[[8]] = p[[8]] + ggtitle('Total Reads') + my.theme
# rRNARate
p[[9]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = rRNARate)) + geom_boxplot()
p[[9]] = p[[9]] + ggtitle('rRNARate') + my.theme
multiplot(plotlist = p, cols = 3)
# Institution
# vcd::mosaic(~ Institution + Dx.Tissue, data = COVARIATES)
# Gender
# vcd::mosaic(~ Gender + Dx.Tissue, data = COVARIATES)
```
### Filter genes
Remove genes that have less than 1 cpm counts in at least 50% of samples per Dx.Tissue. Also remove genes with missing gene length and percentage GC content
```{r cpmnormalisation}
counts$gene_id = NULL
genesToAnalyze = dlply(METADATA, .(Dx.Tissue, Reported_Gender), .fun = function(mtd, count){
  processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                   MIN_GENE_CPM=1, 
                                                   MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
  processed.counts$filteredExprMatrix$genes
}, counts)
genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC.CONT$gene_id[!is.na(GENE.GC.CONT$percentage_gene_gc_content)]) %>%
  intersect(gene_lengths$gene_id[!is.na(gene_lengths$Length)])
#Subset union of all genes and convert subset to logcpm values 
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(counts[genesToAnalyze, ], MIN_GENE_CPM=0, MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
pct.pc = PROCESSED_COUNTS$filteredExprMatrix$genes %>%
  dplyr::rename(gene_id = genes) %>%
  left_join(backgroundGenes) %>%
  left_join(Ensemble2HGNC) %>%
  group_by(gene_biotype) %>%
  summarise(fraction  = n()) %>%
  filter(fraction > 100) %>%
  dplyr::mutate(fraction = fraction/length(PROCESSED_COUNTS$filteredExprMatrix$genes[,1]))
```
`r dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]` genes are used for the analysis.

Following is the distribution of biotypes
`r kable(pct.pc)`

### Outlier analysis
Detect outlier samples based on their expression (logCPM) pattern
```{r detect.outliers, fig.height=8, fig.width=8, results='asis', cache = FALSE}
indToRemove = c('MSSM_RNA_ACC_BP_24', 'MSSM_RNA_ACC_375', 'MSSM_RNA_ACC_170', 'MSSM_RNA_ACC_315', 'MSSM_RNA_ACC_250',
                'MSSM_RNA_ACC_21', 'MSSM_RNA_ACC_356', 'MSSM_RNA_ACC_318', 'MSSM_RNA_ACC_222', 'MSSM_RNA_ACC_220',
                'MSSM_RNA_ACC_379', 'MSSM_RNA_PFC_133', 'MSSM_RNA_PFC_139', 'MSSM_RNA_PFC_163', 'MSSM_RNA_PFC_260',
                'MSSM_RNA_PFC_299', 'MSSM_RNA_PFC_361', 'MSSM_RNA_PFC_89', 'MSSM_RNA_PFC_319', 'MSSM_RNA_PFC_348',
                'MSSM_RNA_PFC_354', 'MSSM_RNA_PFC_60', 'PENN_RNA_PFC_71', 'PENN_RNA_PFC_56',  "MSSM_RNA_ACC_310",
                "MSSM_RNA_ACC_51",  "MSSM_RNA_ACC_254", "MSSM_RNA_ACC_28", "MSSM_RNA_ACC_293", "MSSM_RNA_ACC_233",
                "MSSM_RNA_ACC_167", "MSSM_RNA_ACC_353", "MSSM_RNA_ACC_355", "MSSM_RNA_ACC_211", "PENN_RNA_ACC_122",
                "PENN_RNA_ACC_049", "PENN_RNA_ACC_052", "PENN_RNA_ACC_068", "PENN_RNA_ACC_070", "PITT_RNA_ACC_10020",
                "PITT_RNA_ACC_1240", "PITT_RNA_ACC_1284", "PITT_RNA_ACC_700", "PITT_RNA_ACC_857", "PITT_RNA_ACC_BP_1589",
                "MSSM_RNA_PFC_230", "MSSM_RNA_PFC_304", "MSSM_RNA_PFC_309", "MSSM_RNA_PFC_329", "MSSM_RNA_PFC_82",
                "PENN_RNA_PFC_5", "PENN_RNA_PFC_58", "PENN_RNA_PFC_99", "PITT_RNA_PFC_1284")
indToRemove = c(indToRemove, c("MSSM_RNA_ACC_224", "MSSM_RNA_ACC_240", "MSSM_RNA_ACC_BP_11", "MSSM_RNA_ACC_42", "MSSM_RNA_ACC_BP_15", "PENN_RNA_ACC_003", "MSSM_RNA_ACC_374"))
indToRemove = c(indToRemove, "PITT_RNA_BP_PFC_1770")
# Find principal components of expression to plot
PC <- prcomp(voom(PROCESSED_COUNTS$filteredExprMatrix$counts)$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID)
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
# Plot abberent distribution of logcpm counts
tmp1 = voom(PROCESSED_COUNTS$filteredExprMatrix$counts)$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  tidyr::gather(SampleID, logCPM, -ensembl_gene_id) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID') %>%
              tidyr::separate(Dx.Tissue, c('Dx', 'Tissue'), sep = '_'))
p = ggplot(tmp1 %>%
             dplyr::filter(SampleID %in% indToRemove),
           aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'top') + facet_grid(Dx+.~Tissue, scale = 'free')
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = tidyr::separate(COVARIATES, Dx.Tissue, c('Dx', 'Tissue'), sep = '_') %>%
  group_by(Dx, Tissue) %>%
  summarise(count = n()) %>%
  spread(Tissue, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples from `r length(unique(COVARIATES$Individual_ID))` unique individuals

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are:
`r kable(tmp)`

### Winsorise counts (Gene outliers in samples)
```{r winsorise.data}
LOG.CPM = cpm(PROCESSED_COUNTS$filteredExprMatrix$counts, log = T)
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(LOG.CPM, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  ind.low = which(x == max(x[which(x <= mn-3*std.dev)], na.rm = T))
  ind.high = which(x == min(x[which(x >= mn+3*std.dev)], na.rm = T))

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
# Back calculate counts for further analysis
NEW.COUNTS = PROCESSED_COUNTS$filteredExprMatrix$counts
NEW.COUNTS[is.na(LOG.CPM)] = 0
```

### Library Normalisation
Initial library normalisation usign cqn
```{r cqn}
# Compute offset for gene length and gc content
gene_lengths = tibble::column_to_rownames(gene_lengths, var = 'gene_id') %>% as.data.frame()
CQN.GENE_EXPRESSION = cqn(NEW.COUNTS, 
                          x = GENE.GC.CONT[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gene_gc_content'],
                          lengths = gene_lengths[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'Length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
# Set gene counts in specific samples that are deviating 3 sd from other samples to 0
log.mat = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)
  return((x < (mn-3*std.dev)) | (x > (mn+3*std.dev)))
}) %>% t
NEW.COUNTS[log.mat] = NA
CQN.GENE_EXPRESSION$E[log.mat] = NA
```

### Co-expression distribution
Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
cr = cor(t(tmp))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Sample clustering
```{r decompse.normalise.data, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
PC <- prcomp(tmp, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_')
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~.)
# p <- p + geom_text(aes(label= SampleID), size=4, hjust=0)
p
```
Tree based clustering of samples
```{r decompse.normalise.data.1, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
tree = hclust(as.dist(t(tmp)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```
```{r temp, include = F}
dev.off()
gc()
```

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE}
# Plot abberent distribution of logcpm counts
tmp1 = (CQN.GENE_EXPRESSION$E) %>%
  rownameToFirstColumn('gene_id') %>%
  tidyr::gather(SampleID, logCPM, -gene_id) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID'))
p = ggplot(tmp1, aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme_bw() %+replace% theme(legend.position = 'NONE') + facet_grid(.~Dx.Tissue, scale = 'free')
p
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
preAdjustedSigCovars = runPCAandPlotCorrelations(tmp, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preAdjustedSigCovars.NULL, fig.width=20, fig.height=12}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Model Identification
```{r fxn}
# Function to fit a mixed effect model and return BIC
fitMixedEffectModel <- function(varsToFit, groupingVar, lcpm, cnt, covars){

  # Get design matrix
  designMat = getDesignMatrix(covars[colnames(lcpm), varsToFit, drop=F], Intercept = F)
  designMat = designMat$design[,linColumnFinder(designMat$design)$indepCols]

  # Estimate voom weights
  cnt[is.na(cnt)] = 0
  voomWeights = limma::voom(cnt, design = designMat, plot=F)$weights

  modelBIC = foreach::foreach(i = 1:dim(lcpm)[1],
                              .combine = rbind,
                              .packages = c('lme4', 'dplyr'),
                              .export = c('voomWeights')) %dopar% {

                                # Perform weighted mixed linear models for every gene
                                expr = data.frame(Gx = lcpm[i,])
                                data = cbind(expr,
                                             designMat[rownames(expr),],
                                             Individual_ID = groupingVar)
                                formula = paste(setdiff(colnames(data), c('Gx', 'Individual_ID')), collapse = '+') %>%
                                  paste('Gx ~',.,'+ (1|Individual_ID)', collapse = ' ')

                                weights = voomWeights[i,]
                                BIC = NA
                                tryCatch({
                                  mdl = lmer(formula = formula, 
                                             data = data, 
                                             weights = weights)
                                  BIC = BIC(mdl)
                                }, error = function(e){
                                  BIC = NA
                                })
                              return(data.frame(ensembl_gene_id = rownames(lcpm)[i],
                                                BIC = BIC))
                            }
  return(modelBIC)
  }
# Function to select covariates in a step-wise regression fashion
selectCovarsToAdjust <- function(covarsToSelect, adjustCovars, covars, lcpm, cnt, baseModelBIC){

  varsSelected = c()
  pkgs = c('CovariateAnalysis', 'data.table', 'dplyr', 'plyr',
           'edgeR', 'limma', 'lme4', 'foreach', 'doParallel')
  while(length(covarsToSelect) != 0){
    allModelBIC = foreach(i = 1:length(covarsToSelect),
                          .combine = c,
                          .packages = pkgs,
                          .export = c('fitMixedEffectModel')) %dopar% {

                            # Fit a mixed effect linear model and get all BIC
                            modelBIC = fitMixedEffectModel(c(adjustCovars, covarsToSelect[i]),
                                                           covars[colnames(cnt),'Individual_ID'], 
                                                           lcpm, 
                                                           cnt, 
                                                           covars) %>%
                            plyr::rename(c('BIC' = covarsToSelect[i]))

                            return(list(modelBIC))
                          }
    allModelBIC = plyr::join_all(allModelBIC)

    # Find number of genes that are changed based on BIC
    nChange = allModelBIC %>%
      tidyr::gather(ModelName, Value, -ensembl_gene_id) %>%
      dplyr::left_join(baseModelBIC) %>%
      dplyr::mutate(diff = baseModel - Value) %>%
      dplyr::group_by(ModelName) %>%
      dplyr::summarise(better = sum(diff >= 5), 
                       worse = sum(diff <= -5)) %>%
      dplyr::mutate(nchange = better - worse)

    print(nChange)

    # Select variable
    tmp = nChange %>%
      dplyr::filter(nchange > round(dim(cnt)[1]*0.01)) %>%
      dplyr::top_n(1, nchange)

    if (dim(tmp)[1] == 0){
      covarsToSelect = c()
    } else {
      baseModelBIC = allModelBIC %>%
        dplyr::select(ensembl_gene_id, one_of(tmp$ModelName))
      colnames(baseModelBIC)[2] = 'baseModel'
      varsSelected = c(varsSelected, tmp$ModelName)
      covarsToSelect = setdiff(covarsToSelect, tmp$ModelName)
      print(paste('Variable chosen to be added:',tmp$ModelName))
    }
  }

  return(varsSelected)
}
```
#### Phase I (clinical, ancestry and sample specific technical variables)
```{r phase1}
# Fit a base model with the following covariates
adjust.covars = c('Dx.Tissue')
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   CQN.GENE_EXPRESSION$E, 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
#_# Add in Dx
phase1.covars = c('Institution', 'Reported_Gender', 'PMI', 'Age_of_Death', 'Dx', 'RIN', 'RIN2', 'EV.1', 'EV.2', 'EV.3', 'EV.4', 'EV.5')
vars.selected = selectCovarsToAdjust(phase1.covars, adjust.covars, 
                                     COVARIATES, CQN.GENE_EXPRESSION$E, 
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical and technical variables selected in phase I are `r paste(adjust.covars, collapse = ', ')`

#### Phase II (batch effects)
```{r phase2}
# Fit a base model with the following covariates
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   CQN.GENE_EXPRESSION$E, 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase2.covars = c('LibraryBatch', 'FlowcellBatch')
vars.selected = selectCovarsToAdjust(phase2.covars, adjust.covars, 
                                     COVARIATES, CQN.GENE_EXPRESSION$E, 
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical, technical and batch variables selected after phase I and II of model identification are `r paste(adjust.covars, collapse = ', ')`

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
# Fit a base model with the following covariates
baseModelBIC = fitMixedEffectModel(adjust.covars, 
                                   COVARIATES[colnames(NEW.COUNTS),'Individual_ID'], 
                                   CQN.GENE_EXPRESSION$E, 
                                   NEW.COUNTS, 
                                   COVARIATES) %>%
  dplyr::rename(baseModel = BIC)
# Iteratively identify covariates in phase I
phase3.covars = c("MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "rRNARate", "TotalReads")
vars.selected = selectCovarsToAdjust(phase3.covars, adjust.covars, 
                                     COVARIATES, CQN.GENE_EXPRESSION$E, 
                                     NEW.COUNTS, baseModelBIC)
adjust.covars = c(adjust.covars, vars.selected)
```
Clinical, technical and batch variables selected after phase I, II and III of model identification are `r paste(adjust.covars, collapse = ', ')`

### Normalisation
1. Dx.Tissue is chosen as the primary variable of interest (i.e., covariate adjustments is conditioned on diagnosis and tissue)
2. Individual_ID is chosen as random effect
```{r iterative.normalisation, results='asis'}
writeLines(paste('Using following covariates in the model:',
                 paste(adjust.covars, collapse=', '),
                 'as fixed effects and Individual_ID is chosen as random effect'))

# Post adjusted design matrix
DM1 = getDesignMatrix(COVARIATES[,adjust.covars,drop=F],Intercept = F)
DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

# Estimate voom weights
tmp = NEW.COUNTS
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION = voom(tmp, design=DM1$design, plot=F)
# Estimate consensus correlation coefficient
correlation <- parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION, block = COVARIATES$Individual_ID)

# Re-calculate voom weights with correlation of random effects
VOOM.GENE_EXPRESSION = voom(tmp, 
                            design=DM1$design, plot=F,
                            block = COVARIATES$Individual_ID, 
                            correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E
ADJUSTED.FIT = lmFit(VOOM.GENE_EXPRESSION)

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(ADJUSTED.FIT, CQN.GENE_EXPRESSION$E)
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
tmp = RESIDUAL.GENE_EXPRESSION
tmp[is.na(tmp)] = 0
residualSigCovars = runPCAandPlotCorrelations(tmp, COVARIATES,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
```

### Sanity check
```{r residualSigCovars.manual, fig.width=12, fig.height=8}
residualSigCovars[["PC_res"]][[2]]$plotData
```

### Residual calculation
Calculate weighted residuals and add back "Dx.Tissue" to the residuals
```{r varsToAddBack}
# Add variable of interest back to the residuals
varsToAddIn = grep("Dx.Tissue", colnames(DM1$design), value = T)
RESIDUAL.GENE_EXPRESSION = RESIDUAL.GENE_EXPRESSION +
  ADJUSTED.FIT$coefficients[,varsToAddIn] %*% t(DM1$design[,varsToAddIn])
```

### Coexpression of residual expression 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
tmp = RESIDUAL.GENE_EXPRESSION
tmp[is.na(tmp)] = 0
cr = cor(t(tmp))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Clustering residual data
```{r decompse.normalise.data2, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(tmp, scale.=T, center = T)
# Plot first 4 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_')
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=Institution, shape=Tissue, size=Age_of_Death))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Tissue~., scales = 'free_y')
p
```

```{r decompse.normalise.data2.1, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c('Dx.Tissue','Institution')])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(tmp)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp[,c('Dx.Tissue','Institution')]))
```

```{r temp1, include=F}
dev.off()
gc()
```

### Differential expression analysis
Genes that are differentially expressed at an FDR <= 0.05 are
```{r diffExp, fig.height=10, fig.width=15}
# Fit contrast
contrast = makeContrasts(contrasts=c("Dx.TissueOther_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueControl_ACC",
                                     "Dx.TissueSCZ_ACC-Dx.TissueOther_ACC",
                                     "Dx.TissueOther_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueControl_DLPFC",
                                     "Dx.TissueSCZ_DLPFC-Dx.TissueOther_DLPFC"),
                         levels = colnames(ADJUSTED.FIT$coefficients))
FIT.CONTR = contrasts.fit(ADJUSTED.FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
# Get differnetial expression
DE = lapply(1:6, function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = TRUE) %>%
    rownameToFirstColumn('gene_id') %>% 
    left_join(backgroundGenes)
}, FIT.CONTR) 
names(DE) = colnames(contrast)
DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('Dx.Tissue','',Comparison),
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  tidyr::separate(Comparison, into = c('ref.state','to.state'), sep = '-') %>%
  tidyr::separate(ref.state, into = c('Dx1','Tissue'), sep = '_') %>%
  tidyr::separate(to.state, into = c('Dx2','Tissue'), sep = '_') %>%
  tidyr::unite(Comparison, Dx1, Dx2, sep = '_vs_') %>%
  left_join(Ensemble2HGNC) %>%
  left_join(gene_lengths %>% rownameToFirstColumn('gene_id'))
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
tmp = DE %>%
  dplyr::filter(adj.P.Val <= 0.05) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue) %>%
  group_by(Comparison, Tissue) %>%
  dplyr::summarise(FDR_0_05 = length(unique(ensembl_gene_id)))
tmp1 = DE %>%
  dplyr::filter(adj.P.Val <= 0.05, abs(logFC) >= log2(1.2)) %>%
  dplyr::select(ensembl_gene_id, Comparison, Tissue) %>%
  group_by(Comparison, Tissue) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id)))
kable(full_join(tmp,tmp1))
p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme_bw() %+replace% theme(legend.position = 'top')
p = p + facet_grid(Tissue+.~Comparison, scales = 'fixed')
p
```

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height=10, fig.width=15}
pl = list()
pl[[1]] = ggplot(DE %>% 
                   arrange(match(Direction, c("NONE", "UP", "DOWN"))), aes(x = log10(Length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(Length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')
pl[[2]] = ggplot(DE %>% 
                   arrange(match(Direction, c("NONE", "UP", "DOWN"))), aes(x = percentage_gene_gc_content, y = logFC, color = Direction)) + geom_point()
pl[[2]] = pl[[2]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = percentage_gene_gc_content, y = logFC))
pl[[2]] = pl[[2]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
pl[[2]] = pl[[2]] + theme(legend.position = 'top')
pl[[3]] = ggplot(DE %>% 
                    arrange(match(Direction, c("NONE", "UP", "DOWN"))), aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
pl[[3]] = pl[[3]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = AveExpr, y = logFC))
pl[[3]] = pl[[3]] + facet_grid(Comparison~.) + scale_color_manual(values = c('green','grey','red'))
pl[[3]] = pl[[3]] + theme(legend.position = 'top')
multiplot(plotlist = pl, cols = 3)
```

### Gene set enrichment analysis
Using Fisher's exact test for gene set enrichment analysis
```{r enrich.de, fig.height=16, fig.width=16}
diffexp.genes = DE %>%
  dlply(.(Comparison, Tissue), .fun = function(x){
    tmp = x$hgnc_symbol[x$adj.P.Val <= 0.05] %>% unique
    tmp = tmp[!is.na(tmp)]
  })
diffexp.genes = diffexp.genes[sapply(diffexp.genes, length) > 20]
backgroundGenes = unique(DE$hgnc_symbol)
# Download all related genesets from synapse
geneset.files = synGetChildren("syn3240583", includeTypes=list("file"))$asList()
genesets.to.test = purrr::map(geneset.files, .f = function(fileList){
  tmp = downloadFile(fileList$id) %>%
    dlply(.(Name), .fun = function(x){
      str_split(x$symBeforeOverlap, '\\|') %>% unlist %>% unique
    })
  }) %>%
  CovariateAnalysis::filterGeneSets(backgroundGenes) %>%
  do.call(c,.)
# Perform enrichment analysis
enrichment.results = llply(diffexp.genes, .fun = function(x, genesetsToTest, backgroundGenes){
   ldply(genesetsToTest, .fun = function(y,x,backgroundGenes){
     CovariateAnalysis::fisherEnrichment(x, y, backgroundGenes)
    }, x, backgroundGenes, .parallel = TRUE) %>%
    dplyr::mutate(fdr = p.adjust(pval, method = 'fdr'))
}, genesets.to.test, backgroundGenes) %>%
  rbindlist(idcol = 'Comparison', use.names = T, fill = T) %>%
  tidyr::separate(Comparison, c('Name', 'Region'), sep = '\\.') %>%
  dplyr::rename(Comparison = Name, Category = .id)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn9872607';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of GRCh38 feature counts with CQN normalisation (ACC and DLPFC)';
thisFileName <- 'MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Set annotations
all.annotations = list(
  dataType = 'geneExpression',
  dataSubtype = 'processed',
  assay	 = 'rnaSeq',

  tissue	= 'dorsolateral prefrontal cortex, anterior cingulate cortex', 
  study = 'CMC', 
  species = 'Human',
  consortium	= 'CMC',

  analysisType	= "data normalization",

  transcriptNormalizationMethod	= 'CQN',
  transcriptQuantificationMethod = 'featureCounts',
  referenceSet = 'GRCh38'
)
# Code
CODE <- Folder(name = "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model", parentId = parentId)
CODE <- synStore(CODE)
# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = synapser::File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(COV_OBJ, annotations = all.annotations)
# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
synSetAnnotations(COUNT_OBJ, annotations = all.annotations)
# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
LCOUNT_OBJ = synStore(LCOUNT_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(LCOUNT_OBJ, annotations = all.annotations)
# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
OFFSET_OBJ = synStore(OFFSET_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(OFFSET_OBJ, annotations = all.annotations)
# Store design matrix
DM1$design %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'CMC_ACC_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('CMC_ACC_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
DM_OBJ = synStore(DM_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                  executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(DM_OBJ, annotations = all.annotations)
# Store residual gene expression for network analysis
RESIDUAL.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
nEXP_OBJ = File('CMC_ACC_DLPFC_netResidualExpression.tsv', 
                name = 'Normalised, covariates removed residual expression (for network analysis)', 
                parentId = CODE$properties$id)
nEXP_OBJ = synStore(nEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(nEXP_OBJ, annotations = all.annotations)
# Store differential expression results
write.table(DE, file = 'CMC_ACC_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('CMC_ACC_DLPFC_DiffExpression.tsv', 
                name = 'Differential Expression Results (Dx.Tissue)', 
                parentId = CODE$properties$id)
DEXP_OBJ = synStore(DEXP_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                    executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(DEXP_OBJ, annotations = all.annotations)
# Store enrichment results
write.table(enrichment.results, file = 'CMC_ACC_DLPFC_EnrichResults.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ = File('CMC_ACC_DLPFC_EnrichResults.tsv', 
                  name = 'Enrichment Analysis Results (Dx.Tissue)', 
                  parentId = CODE$properties$id)
ENRICH_OBJ = synStore(ENRICH_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)
synSetAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

```{r knit2synapse, eval=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                 parentId ="",
                                 folderName = "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model")
```

```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |
|  Enrichment Analysis                        |  `r ENRICH_OBJ$properties$id`    |
### Source Rmd
[Source markdown](`r thisFile`)

### 2020-02-07 code/CMC_ACC_Exp_DataProcessing.Rmd
again

--- 2019-12-31 code/CMC_Exp_DataProcessing.Rmd
@@
 
-cl = makeCluster(detectCores()-2)
+cl = makeCluster(14)
 registerDoParallel(cl)
@@
 ```
-Following sample are removed `r paste(removedIDs, collapse = ',')`
 
@@
 
-METADATA <- METADATA[ METADATA$Tissue == 'DLPFC', ]
+METADATA <- METADATA[ METADATA$Tissue == 'ACC', ]
 counts <- counts[ , METADATA$SampleID]
-COVARIATES=COVARIATES[ COVARIATES$Tissue == 'DLPFC' ,]
+COVARIATES=COVARIATES[ COVARIATES$Tissue == 'ACC' ,]
 my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn21470292';
+parentId = 'syn21478397';
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'CMCCovariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- 'CMC_Exp_DataProcessing.Rmd'
+activityDescription = 'CMCCovariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (ACC)';
+thisFileName <- 'CMC_DataProcessing.Rmd'
 # Github link
@@
 activityDescription = 'CMC Covariate analysis and Regrssion of Diagnosis of aligned effective counts with GRCh38 with CQN normalisation CMC';
-CODE <- syn_temp$store(synapseclient$Folder(name = "Iterative_DLPFC_Normalization", parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = "Iterative_ACC_Normalization", parentId = parentId))
+
 #Set Used SynIDs For Provenance
-Syns_Used <- c("")
+#Syns_Used <- c("")
 
@@
   assay	 = 'RNAseq',
-  tissueTypeAbrv	= c('DLPFC'), 
+  tissueTypeAbrv	= c('ACC'), 
   study = 'CMC', 
@@
 )
+
+#TODO add provenance used = Syns_Used,
+
 # Store SVA results
 write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CMC_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
   write.table(file = 'CMC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
-createAndKnitToFolderEntityClient(file = "",
-                                          parentId ="syn21136908",
-                                          folderName = 'CMC_AnalysisExp')
+createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing",
+                                          parentId ="syn21478397",
+                                          folderName = 'ACC')
 ```

### 2020-02-07 code/CMC_ACC_Exp_DataProcessing_V2.Rmd
again

--- 2020-02-07 code/CMC_ACC_Exp_DataProcessing.Rmd
@@
 
-cl = makeCluster(14)
+cl = makeCluster(detectCores()-2)
 registerDoParallel(cl)
@@
 
-ProbGenes <- c('ENSG00000227232', 'ENSG00000248527', 'ENSG00000285812', 'ENSG00000272455', 'ENSG00000215915', 'ENSG00000269737', 'ENSG00000157911', 'ENSG00000226029', 'ENSG00000121775', 'ENSG00000225828', 'ENSG00000116525', 'ENSG00000197982', 'ENSG00000285728', 'ENSG00000225767', 'ENSG00000229359', 'ENSG00000270629', 'ENSG00000160679', 'ENSG00000177954', 'ENSG00000227741', 'ENSG00000143257', 'ENSG00000236535', 'ENSG00000118194', 'ENSG00000143862', 'ENSG00000240219', 'ENSG00000123838', 'ENSG00000272645', 'ENSG00000143643', 'ENSG00000223694', 'ENSG00000272865', 'ENSG00000286216', 'ENSG00000179270', 'ENSG00000235760', 'ENSG00000144031', 'ENSG00000115282', 'ENSG00000232931', 'ENSG00000236440', 'ENSG00000227331', 'ENSG00000272211', 'ENSG00000229056', 'ENSG00000144410', 'ENSG00000144452', 'ENSG00000152056', 'ENSG00000183977', 'ENSG00000230409', 'ENSG00000172940', 'ENSG00000232354', 'ENSG00000281691', 'ENSG00000162267', 'ENSG00000189283', 'ENSG00000239926', 'ENSG00000239997', 'ENSG00000279349', 'ENSG00000285943', 'ENSG00000241278', 'ENSG00000240695', 'ENSG00000114113', 'ENSG00000240875', 'ENSG00000206120', 'ENSG00000229638', 'ENSG00000225473', 'ENSG00000230732', 'ENSG00000242686', 'ENSG00000249592', 'ENSG00000013810', 'ENSG00000284727', 'ENSG00000249212', 'ENSG00000251022', 'ENSG00000250361', 'ENSG00000250910', 'ENSG00000164105', 'ENSG00000283355', 'ENSG00000261360', 'ENSG00000274441', 'ENSG00000152669', 'ENSG00000205571', 'ENSG00000251634', 'ENSG00000171530', 'ENSG00000061455', 'ENSG00000164406', 'ENSG00000285605', 'ENSG00000241112', 'ENSG00000285868', 'ENSG00000241956', 'ENSG00000124588', 'ENSG00000189134', 'ENSG00000206341', 'ENSG00000204227', 'ENSG00000156639', 'ENSG00000272137', 'ENSG00000146242', 'ENSG00000255330', 'ENSG00000118514', 'ENSG00000146576', 'ENSG00000235859', 'ENSG00000183696', 'ENSG00000228735', 'ENSG00000234500', 'ENSG00000274080', 'ENSG00000205485', 'ENSG00000121716', 'ENSG00000271664', 'ENSG00000260555', 'ENSG00000236018', 'ENSG00000260721', 'ENSG00000249258', 'ENSG00000158815', 'ENSG00000197181', 'ENSG00000253200', 'ENSG00000134013', 'ENSG00000250979', 'ENSG00000253948', 'ENSG00000169946', 'ENSG00000253372', 'ENSG00000104529', 'ENSG00000234740', 'ENSG00000164970', 'ENSG00000237159', 'ENSG00000274026', 'ENSG00000136925', 'ENSG00000237461', 'ENSG00000196739', 'ENSG00000182752', 'ENSG00000286196', 'ENSG00000234771', 'ENSG00000280474', 'ENSG00000214402', 'ENSG00000197070', 'ENSG00000205696', 'ENSG00000285852', 'ENSG00000285737', 'ENSG00000188234', 'ENSG00000204172', 'ENSG00000178440', 'ENSG00000166343', 'ENSG00000229990', 'ENSG00000236552', 'ENSG00000155287', 'ENSG00000107819', 'ENSG00000273521', 'ENSG00000203772', 'ENSG00000177595', 'ENSG00000117983', 'ENSG00000247595', 'ENSG00000254622', 'ENSG00000162236', 'ENSG00000213465', 'ENSG00000110025', 'ENSG00000131620', 'ENSG00000241170', 'ENSG00000186174', 'ENSG00000186166', 'ENSG00000240970', 'ENSG00000254428', 'ENSG00000254909', 'ENSG00000110811', 'ENSG00000111664', 'ENSG00000111678', 'ENSG00000205885', 'ENSG00000256589', 'ENSG00000256682', 'ENSG00000247903', 'ENSG00000257433', 'ENSG00000139631', 'ENSG00000185482', 'ENSG00000123329', 'ENSG00000166987', 'ENSG00000178498', 'ENSG00000224713', 'ENSG00000213363', 'ENSG00000110887', 'ENSG00000257097', 'ENSG00000251497', 'ENSG00000279500', 'ENSG00000279283', 'ENSG00000198553', 'ENSG00000043355', 'ENSG00000126216', 'ENSG00000233695', 'ENSG00000258515', 'ENSG00000270433', 'ENSG00000276698', 'ENSG00000257986', 'ENSG00000258648', 'ENSG00000258682', 'ENSG00000196553', 'ENSG00000100632', 'ENSG00000258376', 'ENSG00000258891', 'ENSG00000183648', 'ENSG00000202191', 'ENSG00000223403', 'ENSG00000246451', 'ENSG00000201992', 'ENSG00000215252', 'ENSG00000243789', 'ENSG00000242866', 'ENSG00000250130', 'ENSG00000259619', 'ENSG00000247982', 'ENSG00000255346', 'ENSG00000246877', 'ENSG00000169752', 'ENSG00000274376', 'ENSG00000255769', 'ENSG00000249487', 'ENSG00000261505', 'ENSG00000261123', 'ENSG00000259895', 'ENSG00000279520', 'ENSG00000262312', 'ENSG00000188897', 'ENSG00000243716', 'ENSG00000166851', 'ENSG00000224310')
+ProbGenes <- c("ENSG00000234593", "ENSG00000092847", "ENSG00000232878", "ENSG00000134256", "ENSG00000143393", "ENSG00000162736", "ENSG00000143156", "ENSG00000203737", "ENSG00000232036", "ENSG00000153827","ENSG00000234661", "ENSG00000131370", "ENSG00000281708", "ENSG00000242103", "ENSG00000279311", "ENSG00000249252", "ENSG00000170180", "ENSG00000240083", "ENSG00000249175", "ENSG00000229688", "ENSG00000105953", "ENSG00000146707", "ENSG00000253420", "ENSG00000279608", "ENSG00000232807", "ENSG00000119946", "ENSG00000236991", "ENSG00000177951", "ENSG00000250644", "ENSG00000158077", "ENSG00000110104", "ENSG00000149452", "ENSG00000255345", "ENSG00000254705", "ENSG00000256533", "ENSG00000249028", "ENSG00000285627", "ENSG00000111215", "ENSG00000212128", "ENSG00000066117", "ENSG00000123297", "ENSG00000270048", "ENSG00000251536", "ENSG00000237263", "ENSG00000102796", "ENSG00000258469", "ENSG00000140009", "ENSG00000259370", "ENSG00000137764", "ENSG00000127578", "ENSG00000263072", "ENSG00000261528", "ENSG00000261872", "ENSG00000198453", "ENSG00000189164", "ENSG00000149488", "ENSG00000233993", "ENSG00000100991", "ENSG00000100982", "ENSG00000243646", "ENSG00000239282", "ENSG00000068354", "ENSG00000271356", "ENSG00000241101", "ENSG00000248624", "ENSG00000227017", "ENSG00000240395", "ENSG00000285933", "ENSG00000256064", "ENSG00000177699", "ENSG00000278090", "ENSG00000264529", "ENSG00000243978", "ENSG00000225828", "ENSG00000116525", "ENSG00000225767", "ENSG00000229359", "ENSG00000143257", "ENSG00000143643", "ENSG00000272865", "ENSG00000235760", "ENSG00000227331", "ENSG00000229056", "ENSG00000183977", "ENSG00000239926", "ENSG00000239997", "ENSG00000279349", "ENSG00000229638", "ENSG00000250243", "ENSG00000249212", "ENSG00000250361", "ENSG00000250910", "ENSG00000283355", "ENSG00000251634", "ENSG00000061455", "ENSG00000285605", "ENSG00000285868", "ENSG00000235859", "ENSG00000228735", "ENSG00000205485", "ENSG00000236018", "ENSG00000260721", "ENSG00000169946", "ENSG00000234740", "ENSG00000136925", "ENSG00000237461", "ENSG00000182752", "ENSG00000205696", "ENSG00000285852", "ENSG00000178440", "ENSG00000107819", "ENSG00000131620", "ENSG00000256589", "ENSG00000256682", "ENSG00000213363", "ENSG00000110887", "ENSG00000126216", "ENSG00000258648", "ENSG00000196553", "ENSG00000250130", "ENSG00000259619", "ENSG00000236194", "ENSG00000263089", "ENSG00000235552", "ENSG00000278971", "ENSG00000222460", "ENSG00000235347", "ENSG00000185448", "ENSG00000233204", "ENSG00000184616", "ENSG00000238184", "ENSG00000274322", "ENSG00000235038", "ENSG00000230470", "ENSG00000234601", "ENSG00000277769", "ENSG00000232131", "ENSG00000235631", "ENSG00000272076", "ENSG00000168828", "ENSG00000279822", "ENSG00000235010", "ENSG00000280379", "ENSG00000286067", "ENSG00000279628", "ENSG00000265316", "ENSG00000277829", "ENSG00000223799", "ENSG00000231875", "ENSG00000227232", "ENSG00000160679", "ENSG00000236440", "ENSG00000206341", "ENSG00000138071", "ENSG00000131507", "ENSG00000179151", "ENSG00000263326", "ENSG00000109111", "ENSG00000166317", "ENSG00000219433" )
+
+fooOld <- c('ENSG00000227232', 'ENSG00000248527', 'ENSG00000285812', 'ENSG00000272455', 'ENSG00000215915', 'ENSG00000269737', 'ENSG00000157911', 'ENSG00000226029', 'ENSG00000121775', 'ENSG00000225828', 'ENSG00000116525', 'ENSG00000197982', 'ENSG00000285728', 'ENSG00000225767', 'ENSG00000229359', 'ENSG00000270629', 'ENSG00000160679', 'ENSG00000177954', 'ENSG00000227741', 'ENSG00000143257', 'ENSG00000236535', 'ENSG00000118194', 'ENSG00000143862', 'ENSG00000240219', 'ENSG00000123838', 'ENSG00000272645', 'ENSG00000143643', 'ENSG00000223694', 'ENSG00000272865', 'ENSG00000286216', 'ENSG00000179270', 'ENSG00000235760', 'ENSG00000144031', 'ENSG00000115282', 'ENSG00000232931', 'ENSG00000236440', 'ENSG00000227331', 'ENSG00000272211', 'ENSG00000229056', 'ENSG00000144410', 'ENSG00000144452', 'ENSG00000152056', 'ENSG00000183977', 'ENSG00000230409', 'ENSG00000172940', 'ENSG00000232354', 'ENSG00000281691', 'ENSG00000162267', 'ENSG00000189283', 'ENSG00000239926', 'ENSG00000239997', 'ENSG00000279349', 'ENSG00000285943', 'ENSG00000241278', 'ENSG00000240695', 'ENSG00000114113', 'ENSG00000240875', 'ENSG00000206120', 'ENSG00000229638', 'ENSG00000225473', 'ENSG00000230732', 'ENSG00000242686', 'ENSG00000249592', 'ENSG00000013810', 'ENSG00000284727', 'ENSG00000249212', 'ENSG00000251022', 'ENSG00000250361', 'ENSG00000250910', 'ENSG00000164105', 'ENSG00000283355', 'ENSG00000261360', 'ENSG00000274441', 'ENSG00000152669', 'ENSG00000205571', 'ENSG00000251634', 'ENSG00000171530', 'ENSG00000061455', 'ENSG00000164406', 'ENSG00000285605', 'ENSG00000241112', 'ENSG00000285868', 'ENSG00000241956', 'ENSG00000124588', 'ENSG00000189134', 'ENSG00000206341', 'ENSG00000204227', 'ENSG00000156639', 'ENSG00000272137', 'ENSG00000146242', 'ENSG00000255330', 'ENSG00000118514', 'ENSG00000146576', 'ENSG00000235859', 'ENSG00000183696', 'ENSG00000228735', 'ENSG00000234500', 'ENSG00000274080', 'ENSG00000205485', 'ENSG00000121716', 'ENSG00000271664', 'ENSG00000260555', 'ENSG00000236018', 'ENSG00000260721', 'ENSG00000249258', 'ENSG00000158815', 'ENSG00000197181', 'ENSG00000253200', 'ENSG00000134013', 'ENSG00000250979', 'ENSG00000253948', 'ENSG00000169946', 'ENSG00000253372', 'ENSG00000104529', 'ENSG00000234740', 'ENSG00000164970', 'ENSG00000237159', 'ENSG00000274026', 'ENSG00000136925', 'ENSG00000237461', 'ENSG00000196739', 'ENSG00000182752', 'ENSG00000286196', 'ENSG00000234771', 'ENSG00000280474', 'ENSG00000214402', 'ENSG00000197070', 'ENSG00000205696', 'ENSG00000285852', 'ENSG00000285737', 'ENSG00000188234', 'ENSG00000204172', 'ENSG00000178440', 'ENSG00000166343', 'ENSG00000229990', 'ENSG00000236552', 'ENSG00000155287', 'ENSG00000107819', 'ENSG00000273521', 'ENSG00000203772', 'ENSG00000177595', 'ENSG00000117983', 'ENSG00000247595', 'ENSG00000254622', 'ENSG00000162236', 'ENSG00000213465', 'ENSG00000110025', 'ENSG00000131620', 'ENSG00000241170', 'ENSG00000186174', 'ENSG00000186166', 'ENSG00000240970', 'ENSG00000254428', 'ENSG00000254909', 'ENSG00000110811', 'ENSG00000111664', 'ENSG00000111678', 'ENSG00000205885', 'ENSG00000256589', 'ENSG00000256682', 'ENSG00000247903', 'ENSG00000257433', 'ENSG00000139631', 'ENSG00000185482', 'ENSG00000123329', 'ENSG00000166987', 'ENSG00000178498', 'ENSG00000224713', 'ENSG00000213363', 'ENSG00000110887', 'ENSG00000257097', 'ENSG00000251497', 'ENSG00000279500', 'ENSG00000279283', 'ENSG00000198553', 'ENSG00000043355', 'ENSG00000126216', 'ENSG00000233695', 'ENSG00000258515', 'ENSG00000270433', 'ENSG00000276698', 'ENSG00000257986', 'ENSG00000258648', 'ENSG00000258682', 'ENSG00000196553', 'ENSG00000100632', 'ENSG00000258376', 'ENSG00000258891', 'ENSG00000183648', 'ENSG00000202191', 'ENSG00000223403', 'ENSG00000246451', 'ENSG00000201992', 'ENSG00000215252', 'ENSG00000243789', 'ENSG00000242866', 'ENSG00000250130', 'ENSG00000259619', 'ENSG00000247982', 'ENSG00000255346', 'ENSG00000246877', 'ENSG00000169752', 'ENSG00000274376', 'ENSG00000255769', 'ENSG00000249487', 'ENSG00000261505', 'ENSG00000261123', 'ENSG00000259895', 'ENSG00000279520', 'ENSG00000262312', 'ENSG00000188897', 'ENSG00000243716', 'ENSG00000166851', 'ENSG00000224310')
 
@@
 
- ProbGenes <- c(ProbGenes,tmp)
+ #ProbGenes <- c(ProbGenes,tmp)
 ```
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
+
 FactorCovariates <- c('Individual_ID','FlowcellBatch', "Institution", "Reported_Gender", "LibraryBatch", "Tissue", "Dx.Tissue", "Dx", "RibozeroBatch")
@@
 ```{r filter.genes}
+
 COUNT<-counts[,METADATA$SampleID]
@@
 #CQN.GENE_EXPRESSION$E.no.na <- as.data.frame(CQN.GENE_EXPRESSION$E.no.na)
+
+row.names(METADATA) <- METADATA$SampleID
 COVARIATES1 <- COVARIATES[ , (colnames(COVARIATES) %in% 'Tissue') == F]
+
+COVARIATES1$Institution <- as.factor(as.character(COVARIATES1$Institution))
+COVARIATES1$Individual_ID <- as.factor(as.character(COVARIATES1$Individual_ID))
+COVARIATES1$FlowcellBatch <- as.factor(as.character(COVARIATES1$FlowcellBatch))
+COVARIATES1$Reported_Gender <- as.factor(as.character(COVARIATES1$Reported_Gender))
+COVARIATES1$Dx.Tissue <- as.factor(as.character(COVARIATES1$Dx.Tissue))
+COVARIATES1$RibozeroBatch <- as.factor(as.character(COVARIATES1$RibozeroBatch))
+COVARIATES1$LibraryBatch <- as.factor(as.character(COVARIATES1$LibraryBatch))
+COVARIATES1$SampID <- as.factor(as.character(row.names(COVARIATES1)))
+COVARIATES1$Ancestry <- as.factor(as.character(METADATA[row.names(COVARIATES1),]$Ethnicity))
+
 preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
@@
 ```{r iterative.norm, results='asis'}
+
 # Primary variable of interest
 postAdjustCovars = c('Institution', 'FlowcellBatch', 'Reported_Gender');
+#postAdjustCovars = c('Institution', 'Reported_Gender');
 # Assign residual covariates
@@
 
+COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 485, replace = TRUE, prob = NULL)))
+
 loopCount = 0 
 while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
+  COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 485, replace = TRUE, prob = NULL)))
   writeLines(paste0('Working on Loop: ', loopCount))
@@
                    paste(postAdjustCovars, collapse=', '),
-                   'as fixed effects and Individual_ID as random effect'))
+                   'as fixed effects and Individual_ID/Institution as random effect'))
 
@@
   correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
-                                             block = COVARIATES1$Individual_ID,
+
+                                             block = COVARIATES1$Block,
                                              method = 'lmer')
@@
                                 design=DM1$design, plot=F,
-                                block = COVARIATES1$Individual_ID, 
+
+                                block = COVARIATES1$Block, 
                                 correlation = correlation$cor)
@@
                               weights = VOOM.GENE_EXPRESSION$weights,
-                              block = COVARIATES1$Individual_ID, 
+
+                              block = COVARIATES1$Block, 
                               correlation = correlation$cor)
@@
                          c(postAdjustCovars, primaryVariable, 'Individual_ID', notEstimable))
+
   residCovars <- residCovars[ (residCovars == 'Tissue') == F ]
@@
 
+  #residualSigCovars = runPCAandPlotCorrelations(expr[ (row.names(expr) %in% ProbGenes) == F, ], 
+                                        #        COVARIATES1[, residCovars, drop=F], 
+                                        #        'adjusted design(voom-normalized)',
+                                        #        isKeyPlot=TRUE)
+  writeLines(paste0('Residule Calc for Loop: ', loopCount))
   residualSigCovars = runPCAandPlotCorrelations(expr,
-                                                COVARIATES1[, residCovars, drop=F], 
+
+                                                COVARIATES[, residCovars, drop=F], 
                                                 'adjusted design(voom-normalized)',
@@
 ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
-
-# Find inter relation between factor covariates
-#METADATA <- METADATA[ !duplicated(METADATA), ]
-#COVARIATES1 = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
-#rownames(COVARIATES1) <- METADATA$ID
-# Convert factor covariates to factors
 COVARIATES1[,FactorCovariates] = lapply(COVARIATES1[,FactorCovariates], factor)
@@
                     design=DESIGN$design, plot=F,
-                    block = COVARIATES1$Donor_ID, 
+
+                    block = COVARIATES1$Block, 
                     correlation = correlation$cor)
@@
             design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
-            block = COVARIATES$Donor_ID, 
+            block = COVARIATES1$Block, 
             correlation = correlation$cor)
@@
                         design = cbind(MODEL1, SURR.VAR), plot=F,
-                        block = COVARIATES1$Donor_ID, 
+                        block = COVARIATES1$Block, 
                         correlation = correlation$cor)
@@
                      design = VOOM.SVA.WEIGHTS$design,
-                     block = COVARIATES1$Donor_ID, 
+                     block = COVARIATES1$Block, 
                      correlation = correlation$cor)
@@
 activityName = 'Covariate and Diagnosis Regression';
-activityDescription = 'CMCCovariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (ACC)';
+activityDescription = 'CMC Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (ACC)';
 thisFileName <- 'CMC_DataProcessing.Rmd'
@@
 # Store SVA results
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CMC_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CMC_SVA_ACC_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_ACC_Diagnosis_Corrected.tsv', name = 'ACC Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'CMC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'CMC_ACC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_ACC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'ACC Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
-createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing",
+createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing_V2.Rmd",
+
                                           parentId ="syn21478397",

### 2020-02-07 code/ResultsPlots.Rmd
again

---
title: "Plot Results"
output: html_document
---
---
title: "Manhattan and qqplot results"
author: "JKG"
date: "07/02/2020"
output: pdf_document
  chunk_output_type: console
---

```{r libs, include=FALSE}
library(qqman)
library(ggplot2)
library(ggrepel)
library(dplyr)

knitr::opts_chunk$set(
  #python.reticulate=FALSE,
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')

```

```{r Prep, include=FALSE}

Values <- read.table( syn_temp$get('syn21529460')$path, header = T, sep='\t' )
Assoc <- read.table( syn_temp$get('syn21577463')$path, header = T, sep='\t' )
row.names(Values) <- Values$probeID

Assoc$Gene <- Assoc$ID
GenesOfInterest <- c("MTCH2",
                     "EED",
                     "KNOP1",
                     "CD2AP",
                     "APOC1",
                     "CLPTM1",
                     "TREM2",
                     "CEACAM19")
JCP <- c("PVRL2",
         "PVR",
         "TMEM223",
         "NUP160",
         "PTPRJ",
         "C1QTNF4")

JCPval <- c( "POLR2E",
             "POLR2G",
             "ZNF660",
             "MADD"
)

Assoc<-Assoc[,(colnames(Assoc) %in% 'PANEL')==F]

Assoc<-Assoc[complete.cases(Assoc),]
Assoc$TWAS.P <- as.numeric(as.character(Assoc$TWAS.P))
Assoc$FDR_TWAS.P <- p.adjust( Assoc$TWAS.P, method='fdr', dim(Assoc)[1])
don <- Assoc %>%

  # Compute chromosome size
  group_by(CHR) %>% 
  summarise(chr_len=max(P0)) %>%

  # Calculate cumulative position of each chromosome
  mutate(tot=cumsum(as.numeric(chr_len))-as.numeric(chr_len)) %>%
  select(-chr_len) %>%

  # Add this info to the initial dataset
  left_join(Assoc, ., by=c("CHR"="CHR")) %>%

  # Add a cumulative position of each SNP
  arrange(CHR, P0) %>%
  mutate( BPcum=P0+tot) %>%

  # Add highlight and annotation information
  mutate( is_highlight=ifelse(Gene %in% GenesOfInterest, "yes", 
                                ifelse(Gene %in% JCP, "drop", 
                                       ifelse(Gene %in% JCPval, "NS", "no")) )) %>%

  mutate( is_annotate=ifelse( FDR_TWAS.P < 0.05 , "yes", "no"))

# Prepare X axis
axisdf <- don %>% group_by(CHR) %>% summarize(center=( max(BPcum) + min(BPcum) ) / 2 )

#don$is_annotate <- don$is_highlight
```

```{r Plot}
# Make the plot
ggplot(don, aes(x=BPcum, y=-log10(TWAS.P))) +

  #AddSigLine
  geom_hline(yintercept = -log10( max(Assoc[Assoc$FDR_TWAS.P < 0.05,]$TWAS.P) )) +
  #p.adjust(7.467145e-06, method='fdr', dim(Assoc)[1] )

  # Show all points
  geom_point( aes(color=as.factor(CHR)), alpha=0.8, size=1.3) +
  scale_color_manual(values = rep(c("grey", "black"), 22 )) +

  # custom X axis:
  scale_x_continuous( name="Chromosome", label = axisdf$CHR, breaks= axisdf$center ) +
  scale_y_continuous(name="-Log10( TWAS Association P-Value )", expand = c(0, 0), limits=c(0,38) ) +     # remove space between plot area and x axis

  # Add highlighted points
  geom_point(data = subset(don, is_highlight=="yes"), color="orange", size=2) +
  geom_point(data = subset(don, is_highlight=="drop"), color="lightslateblue", size=2) +
  geom_point(data = subset(don, is_highlight=="NS"), color="mediumturquoise", size=2) +

  # Add label using ggrepel to avoid overlapping
  geom_label_repel( data=subset(don, is_annotate=="yes"), aes(label=Gene), size=2) +

  # Custom the theme:
  theme_bw() +
  theme( 
    legend.position="none",
    panel.border = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
  )

qq(Assoc$TWAS.P, bty='n', las=1)
```

```{r SavePlot,include=FALSE}
# Make the plot
pdf(file = "TWAS_Manhattan.pdf")

  ggplot(don, aes(x=BPcum, y=-log10(TWAS.P))) +

    #AddSigLine
    geom_hline(yintercept = -log10( max(Assoc[Assoc$FDR_TWAS.P < 0.05,]$TWAS.P) )) +
    #p.adjust(7.467145e-06, method='fdr', dim(Assoc)[1] )

    # Show all points
    geom_point( aes(color=as.factor(CHR)), alpha=0.8, size=1.3) +
    scale_color_manual(values = rep(c("grey", "black"), 22 )) +

    # custom X axis:
    scale_x_continuous( name="Chromosome", label = axisdf$CHR, breaks= axisdf$center ) +
    scale_y_continuous(name="-Log10( TWAS Association P-Value )", expand = c(0, 0), limits=c(0,38) ) +     # remove space between plot area and x axis

    # Add highlighted points
    geom_point(data = subset(don, is_highlight=="yes"), color="orange", size=2) +
    geom_point(data = subset(don, is_highlight=="drop"), color="lightslateblue", size=2) +
    geom_point(data = subset(don, is_highlight=="NS"), color="mediumturquoise", size=2) +

    # Add label using ggrepel to avoid overlapping
    geom_label_repel( data=subset(don, is_annotate=="yes"), aes(label=Gene), size=2) +

    # Custom the theme:
    theme_bw() +
    theme( 
      legend.position="none",
      panel.border = element_blank(),
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
    )
dev.off()

pdf(file = "TWAS_qq.pdf")
qq(Assoc$TWAS.P, bty='n', las=1)
dev.off()
```

```{r PushToSynapse,include=FALSE}

```

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp  <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "ResultsPlots.Rmd",
                                          parentId ="syn18936948",
                                          folderName = 'TWAS Results Figures')
```

### 2020-02-07 code/SMR.Rmd
again

---
  title: "Summary-data-based Mendelian Randomization" author: "Jake Gockley" date: "01/17/2019" header-includes:
  - \usepackage{multicol} - \newcommand{\btwocol}{\begin{multicols}{2}} - \newcommand{\etwocol}{\end{multicols}} output:
  html_document: default pdf_document: default ---

```{r setup, include=FALSE} knitr::opts_chunk$set(echo = F) library(readr) library(snpStats) library(sem) ``` ```{r code, eval=TRUE, cache=FALSE, 
include=TRUE}
#Pull eQTL Data
system( 'synapse get syn16984815' )
#Pull Weights
system('aws s3 cp s3://jkg-s3-synapseencryptedexternalbucket-zszdd03ghnb2/ROSMAP/TWAS_2019_12_02_PanCortex_DiagnosisRegressed_Weights/ All_Data/ALL/ 
--recursive') system('rm All_Data/ALL/*.hsq')
#PullGenos
system('synapse get syn20820120 --downloadLocation Binary_Cleaned/') system('synapse get syn20820121 --downloadLocation Binary_Cleaned/') system('synapse 
get syn20820122 --downloadLocation Binary_Cleaned/')
#GWAS
system('synapse get syn18999109 --downloadLocation .')
#Expression
system('synapse get syn21011186 --downloadLocation .') Exp <- read.table('ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', header = T, sep='\t')
#LoadKunkle
Kunk <- read.table('Kunkle_etal_2019_IGAP_Summary_statistics.with_allelefreqs.txt', header =T, sep="")
#Try the MR for one gene
load("All_Data/ALL/ENSG00000130208.wgt.RDat") PLINK <- read.plink(bed = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bed' ,
                    bim = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bim',
                    fam = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.fam' )
#Filter Kunkle for relevant SNPS by their IDS
K <- Kunk[ Kunk$MarkerName %in% PLINK$map$snp.name, ] row.names(K) <- K$MarkerName mygwas<-K[,c(3:5,9,6:8)] colnames(mygwas) <- c("SNP", "A1", 'A2', "freq", 
"b", "se", "p" ) mygwas$n <- rep( 2003, dim(mygwas)[1] ) write.table(snps$V2, 'snp.list', row.names=F, col.names=F, quote=F, sep='\t') write.table(mygwas, 
'mygwas.ma', row.names=F, col.names=T, quote=F, sep='\t') system( 'plink -bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --extract snp.list --make-bed 
--out Temp_plink') system( './smr_Linux --bfile Temp_plink --gwas-summary mygwas.ma --beqtl-summary myeqtl --out mymulti --smr-multi')
#make the eqtl data into BESD format
EQTL <- read.csv( 'Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv', header = T ) EQTl <- EQTL[ as.character(EQTL$snpid ) %in% 
as.character(PLINK$map$snp.name) , ] EQtl <- EQTl[ as.character(EQTl$gene ) %in% as.character(Exp$TargetID) , ] EQTL_sink <- EQTL EQTL <- EQtl
#SNP gene beta t-stat p-value FDR
EQTL$geneSymbol <- as.character(EQTL$geneSymbol) EQTL$gene <- as.character(EQTL$gene) EQTL[ as.character(EQTL$geneSymbol) =="",]$geneSymbol <- EQTL[ 
as.character(EQTL$geneSymbol) =="",]$gene EQTL$snpid <- as.character(EQTL$snpid) EQTL$DUP <- paste0( as.character(EQTL$snpid), '_', as.character(EQTL$gene)) 
EQTL_deDup <- EQTL[ !duplicated(EQTL$DUP), ]
##LOAD EXPRESSION AND BIM
###FILTER FOR RELEVANT SNP-GENEs
wExp <- read.table(file = 'WeightList/MaterWeight.lst', sep = "", header = T)
#EQTL_deDup <- EQTL_deDup[ EQTL_deDup$snpid %in% as.character(PLINK$bim[,2]), ] EQTL_deDup <- EQTL_deDup[ EQTL_deDup$gene %in% as.character(Exp[,2]), ]
Repo <- function( n ){
  #'@Mat eg. EQTL_deDup '@n eg a number
  if( EQTL_deDup[n,]$geneSymbol == ""){
    EQTL_deDup[n,]$geneSymbol <- EQTL_deDup[n,]$gene
  }else{}
}
REPS <- row.names( EQTL_deDup[ EQTL_deDup$geneSymbol == "", ] ) eqtl <- EQTL_deDup[ , c('snpid', 'geneSymbol', 'beta', 'statistic', 'pvalue', 'beta') ] 
colnames(eqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 'p-value', 'FDR' ) write.table( eqtl, file = 'mateQTL_geneN.txt', col.names = T, row.names=F, quote=F, 
sep='\t' ) Eeqtl <- EQTL_deDup[ , c('snpid', 'gene', 'beta', 'statistic', 'pvalue', 'beta') ] colnames(Eeqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 
'p-value', 'FDR' ) write.table( Eeqtl, file = 'mateQTL_ensgN.txt', col.names = T, row.names=F, quote=F, sep='\t' ) system( './smr_Linux --eqtl-summary 
mateQTL_ensgN.txt --matrix-eqtl-format --make-besd --out mybesd_ensgN' ) system( './smr_Linux --eqtl-summary mateQTL_geneN.txt --matrix-eqtl-format 
--make-besd --out mybesd_geneN' )
##Fix the ,esi and .epi files
AleleSelect <- function( Row ){
  if( Row[4] > 0 ){
    Eff <- as.character(Row[9])
    Unaff <- as.character(c(Row[6],Row[7])[ (c(Row[6],Row[7]) %in% Eff) == F ])
  }else{
    Unaff <- as.character(Row[9])
    Eff <- as.character(c(Row[6],Row[7])[ (c(Row[6],Row[7]) %in% Unaff) == F ])
  }
  if(Eff == Row[7]){
    Freq <- Row[8]
  }else{
    Freq <- 1-as.numeric(Row[8])
  }

  return( c(as.character(Eff),as.character(Unaff),as.character(Freq)) )
}
ESiProcess <- function( Fil ){
  #'@Fil the loaded .esi file (ie File)
  ESi_info <- EQTL_deDup[ !duplicated(EQTL_deDup$snpid), c("chromosome", "snpLocation", "snpid", "statistic", "beta", "A1", "A2", "A2freq", 
"expressionIncreasingAllele")]
  row.names(ESi_info) <- ESi_info$snpid
  Fil$V1 <- as.character(ESi_info[ as.character( Fil$V2 ), ]$chromosome)
  Fil$V4 <- as.character(ESi_info[ as.character( Fil$V2 ), ]$snpLocation)

  ESi_info$A1 <- as.character(ESi_info$A1)
  ESi_info$A2 <- as.character(ESi_info$A2)
  ESi_info$expressionIncreasingAllele <- as.character(ESi_info$expressionIncreasingAllele)

  temp <- t( apply(ESi_info, 1, AleleSelect) )
  Fil[,5:7] <- temp[ as.character(Fil$V2),]
  return(Fil)
}
File <- read.table(file='mybesd_ensgN.esi', header=F, sep='\t') File2 <- ESiProcess( File ) write.table(File2, file='mybesd_ensgN.esi', col.names=F, 
row.names = F, quote=F, sep='\t') File <- read.table(file='mybesd_geneN.esi', header=F, sep='\t') File2 <- ESiProcess( File ) write.table(File2, 
file='mybesd_geneN.esi', col.names=F, row.names = F, quote=F, sep='\t')
#ESPI
row.names(Exp) <- as.character(Exp$TargetID) Exp$TargetID <- as.character(Exp$TargetID) Exp$Gene_Symbol <- as.character(Exp$Gene_Symbol) EQTL_deDup$gene <- 
as.character(EQTL_deDup$gene) EQTL_deDup$geneSymbol <- as.character(EQTL_deDup$geneSymbol) EQTL_deDup$chromosome <- as.character(EQTL_deDup$chromosome) 
EQTL_deDup$strand <- as.character(EQTL_deDup$strand)
#Split EQTL_deDup into special data frames to reference
EQTL_deDup_GN <- EQTL_deDup[ !duplicated(EQTL_deDup$geneSymbol), ] EQTL_deDup_ENSG <- EQTL_deDup[ !duplicated(EQTL_deDup$gene), ]

ESpProcess <- function( Name ){
  #'@Name row with gene name or ENSG in column 2
  if(Name[2] %in% EQTL_deDup_ENSG$gene){
    Row <- EQTL_deDup_ENSG[ EQTL_deDup_ENSG$gene %in% Name[2], ][1,]
  }else{
    Row <- EQTL_deDup_GN[ EQTL_deDup_GN$geneSymbol %in% Name[2], ][1,]
  }
  st <- c('+', '-')
  names(st) <- c("1","-1")

  return( c( as.character(Row[1]),
             as.character(Name[2]),
             as.character("0"),
             as.character(Exp[ as.character(Row[5]), 4]),
             as.character(Name[2]),
             as.character(st[Row[,15]])
             )
          )
}
File <- read.table(file='mybesd_geneN.epi', header=F, sep='\t') File$V2 <- as.character(File$V2) foo <- t( apply(File, 1, ESpProcess ) ) write.table( foo, 
file='mybesd_geneN.epi', row.names=F, col.names=F, quote = F, sep='\t' ) File <- read.table(file='mybesd_ensgN.epi', header=F, sep='\t') File$V2 <- 
as.character(File$V2) foo <- t( apply(File, 1, ESpProcess ) ) write.table( foo, file='mybesd_ensgN.epi', row.names=F, col.names=F, quote = F, sep='\t' ) 
Genes <- c("APOC1", "EED", "CD2AP", "CEACAM19", "CLPTM1", "MTCH2", "TREM2", "KNOP1", "POLR2E", "POLR2G", "ZNF660", "MADD", "PVRL2", "PVR", "TMEM223", 
"NUP160", "PTPRJ", "C1QTNF4") ENSG <- c write.table(EQTL_deDup_GN[ EQTL_deDup_GN$geneSymbol %in% Genes, ]$gene, "myprobe.list", row.names=F, col.names=F, 
quote=F, sep='\t') library(doParallel) library(foreach)
#Start Master File
system( 'echo "probeID ProbeChr Gene Probe_bp topSNP topSNP_chr topSNP_bp A1 A2 Freq b_GWAS se_GWAS tp_GWAS b_eQTL se_eQTL p_eQTL b_SMR se_SMR p_SMR 
p_SMR_multi p_HEIDI nsnp_HEIDI" > Compiled_SMR.tsv') List <- read.table( 'WeightList/MaterWeight.lst', header = T, sep='')
#i <- 1
Runner <- function( i ){
  #Load Gene Info
  load(as.character( List$WGT )[i])
  Probe <- as.character( List$ID )[i]
  SNPs <- snps$V2
  #Save Temp Files
  write.table(Probe, paste0("myprobe_", Probe, ".list"), row.names=F, col.names=F, sep="\t", quote=F)
  write.table(SNPs, paste0("mysnp_", Probe, ".list"), row.names=F, col.names=F, sep="\t", quote=F)
  #Run Model
  system( paste0("./smr_Linux --bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --gwas-summary mygwas.ma --thread-num 1 --beqtl-summary mybesd_ensgN 
--ld-upper-limit 1 --out temp_Ensg_", Probe, " --extract-snp mysnp_", Probe, ".list --extract-probe myprobe_", Probe, ".list --peqtl-heidi 0 --ld-multi-snp 
1 --smr-multi --peqtl-smr 1 --set-wind 2000 "))
  #Pull Info
  system( paste0("grep -v 'probeID' temp_Ensg_", Probe, ".msmr >> Compiled_SMR.tsv") )
  #remove Temp Info
  system( paste0("rm myprobe_", Probe, ".list") )
  system( paste0("rm mysnp_", Probe, ".list") )
  system( paste0("rm temp_Ensg_", Probe, ".*") )
}
cl <- makeCluster( detectCores()-2 ) registerDoParallel(cl) foo <- Sys.time()
  foreach(i=1:dim(List)[1]) %dopar% Runner( i ) Sys.time()-foo stopCluster(cl) Table<-read.table(file='Compiled_SMR.tsv', sep='\t', header=T) system( 'awk 
-F \',\' \'{ print $5"\t"$6 }\' Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv | sort | uniq | grep -v \'geneSymbol\' > Translate.txt') Trans 
<- read.table( file='Translate.txt', sep ="\t", header=F) row.names(Trans) <- Trans$V1 Trans$V1 <- as.character(Trans$V1) Trans$V2 <- as.character(Trans$V2) 
Trans[ is.na(Trans$V2), ]$V2 <- Trans[ is.na(Trans$V2), ]$V1 Trans[ Trans$V2 == "", ]$V2 <- Trans[ Trans$V2 == "", ]$V1 Table$Gene <- 
as.character(Table$Gene) Table$probeID <- as.character(Table$probeID) Table$Gene <- Trans[Table$probeID,]$V2
write.table(Table, file='Final_SMR_TWAS_Validation.tsv', row.names=F, col.names=T, quote=F, sep ='\t') ```

```{r synapse.parameters, include=FALSE, cache=TRUE} 
parentId = 'syn18936948'; activityName = 'Mendelian Randomization'; activityDescription = 'Validation of TWAS 
associations via SMR analysis'; thisFileName <- ''
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master') thisFile <- githubr::getPermlink(repository = thisRepo, 
repositoryPath=paste0('code/',thisFileName)) ```
### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE} activityName = 'Mendelian Randomization'; activityDescription = 'Validation of TWAS associations 
via SMR analysis'; CODE <- syn_temp$store(synapseclient$Folder(name = "Summary-data-based Mendelian Randomization", parentId = parentId))
# Set annotations
all.annotations = list(
  dataType = 'analysis',
  dataSubType = 'SMR_Validation_Tests',
  summaryLevel = 'gene',
  assay = 'TWAS',
  tissueTypeAbrv = c('NA'),
  study = c('ROSMAP','MSBB', 'Mayo')
  organism = 'HomoSapiens',
  consortium = c('ROSMAP','MSBB', 'Mayo') ,
  normalizationStatus	= TRUE,
  normalizationType	= 'NA',
  rnaquantification = 'NA',
  genomeAssemblyID = 'hg19' )
# Store SMR
ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Final_SMR_TWAS_Validation.tsv', name = 'SMR Values', parentId=CODE$properties$id ), activityName = 
activityName, executed = thisFile, activityDescription = activityDescription) all.annotations$dataSubType = 'Summary Stats' 
syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations) ```
### R Source Code
[Github](`r thisFile`) ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE} reticulate::use_python("/usr/bin/python", required = TRUE) synapseclient <- 
reticulate::import("synapseclient") syn_temp <- synapseclient$Synapse() syn_temp$login() setwd("~/TWAS/code/") 
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R") source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R") 
createAndKnitToFolderEntityClient(file = "SMR.Rmd",
                                  parentId ="syn18936948",
                                  folderName = 'Summary-data-based Mendelian Randomization') 
```

### 2020-02-07 code/ResultsPlots.Rmd
again

@@
 
-```{r PushToSynapse,include=FALSE}
+```{r synapse.parameters, include=FALSE, cache=TRUE}
+parentId = 'syn18936948';
+activityName = 'TWAS Results';
+activityDescription = 'Results Plots from TWAS Analysis';
+thisFileName <- 'ResultsPlots.Rmd'
+# Github link
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+```
+
+### Store files in synapse
+```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
+activityName = 'TWAS Results';
+activityDescription = 'Results Plots from TWAS Analysis';
+CODE <- syn_temp$store(synapseclient$Folder(name = "TWAS Results Figures", parentId = parentId))
+
+#Set Used SynIDs For Provenance
+#Syns_Used <- c("")
+
+# Set annotations
+all.annotations = list(
+  dataType = 'pdf',
+  dataSubType = 'geneExp',
+  summaryLevel = 'gene',
+  assay	 = 'TWAS',
+  study = 'TWAS', 
+  organism = 'HomoSapiens',
+  consortium	= c( 'ROSMAP', 'MSBB','Mayo' ),
+  normalizationStatus	= TRUE,
+  normalizationType	= 'CQN',
+  genomeAssemblyID = 'GRCh37'
+)
+
+#TODO add provenance used = Syns_Used,
+
+# Store SVA results
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.pdf', name = 'Twas Gene Association Manhattan Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'Manhattan Plot'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_qq.pdf', name = 'Twas Gene Association QQ-Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'QQ-Plot'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
 

### 2020-02-11 code/CMC_Validation.Rmd
CMC Validation

---
title: "CMC Validation"
output: html_document
---

Date of analysis update: "`r date()`"

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(ggplot2)
library(stringr)

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('~/TWAS/utilityFunctions/parallelDuplicateCorrelation.R')
source('~/TWAS/utilityFunctions/irwsva.build.R')
source('~/TWAS/utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

## Validation

```{r Val}

################################################################################################################
#CMC DLPFC DATA
Impute <-  as.data.frame( read.table( syn_temp$get('syn21442621')$path, header = T, sep = '\t', row.names = 1 ))
row.names(Impute)  <- Impute$IID
Impute <- Impute[ , colnames(Impute)[ (grepl("ENSG", colnames(Impute))) == T ] ]
Impute <- as.data.frame(t(Impute))

#Exp
Exp <- as.data.frame( read.table( syn_temp$get('syn21470926')$path, header = T, sep = '\t', row.names = 1 ))
rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
Exp_ACC <- Exp[ ,(grepl("_ACC_", colnames(Exp)))==T ]
Exp_PFC <- Exp[ ,(grepl("_PFC_", colnames(Exp)))==T ]

#ID--
ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )
table(colnames(Exp_ACC) %in% ID$RNAseq.Sample_RNA_ID )
table(colnames(Exp_PFC) %in% ID$RNAseq.Sample_RNA_ID )

ID_GENO <- ID[( ID$Genotypes.Genotyping_Sample_ID) %in% gsub( '0_', '', colnames(Impute) )  == T , ]
dups <- ID[ ID$Individual_ID %in% names(table(ID_GENO$Individual_ID)[table(ID_GENO$Individual_ID)>1]), ]
ID_GENO <- ID_GENO[ (ID_GENO$RNAseq.Sample_RNA_ID %in% dups$RNAseq.Sample_RNA_ID[grepl("_BP_", dups$RNAseq.Sample_RNA_ID)]) == F, ]
row.names(ID_GENO) <- as.character( ID_GENO$Genotypes.Genotyping_Sample_ID )

#Replace columnn names
colnames(Impute) <- as.character( ID_GENO[ gsub( '0_', '', colnames(Impute) ), ]$Individual_ID )

ID_RNA <- ID[ ID$RNAseq.Sample_RNA_ID  %in% colnames(Exp_PFC), ]
row.names(ID_RNA) <- ID_RNA$RNAseq.Sample_RNA_ID
ID_RNA$Individual_ID <- as.character(ID_RNA$Individual_ID)
colnames(Exp_PFC) <- as.character( ID_RNA[ colnames(Exp_PFC), ]$Individual_ID)

FinNames <- colnames(Exp_PFC)[ colnames(Exp_PFC)  %in% colnames(Impute) ]
Impute_comp<-Impute[, FinNames ]
Exp_PFC<-Exp_PFC[, FinNames ]
table( colnames(Impute_comp) %in% colnames(Exp_PFC) )

#Filter Row names
keepers <- row.names(Exp_PFC)[ row.names(Exp_PFC) %in% row.names(Impute_comp) ]
Impute_comp <- Impute_comp[ keepers, ]
Exp_PFC <- Exp_PFC[ keepers, ]
table( row.names(Impute_comp) %in% row.names(Exp_PFC) )

Scaled_PFC_Exp <- t(scale(t(Exp_PFC)))

Correlation <- matrix(0, dim(Scaled_PFC_Exp)[1], 3)
row.names(Correlation) <- row.names(Impute_comp)
colnames(Correlation) <- c( "Z", "Correlation", "P-Val")

for( Gene in row.names(Impute_comp) ){
  foo <- cor.test( as.numeric(Impute_comp[Gene,]), as.numeric(Scaled_PFC_Exp[Gene,]) , method = "kendall")
  Correlation[ Gene, ] <- c( as.numeric(foo$statistic), as.numeric(foo$estimate), as.numeric(foo$p.value) )
}

Correlation <- cbind( Correlation, "Log10_Pval"= -log10(Correlation[,3]))
Correlation <- cbind( Correlation, "FDR"= p.adjust( Correlation[,3], method = "fdr", n = 13650) )
Correlation <- cbind( Correlation, "BH"= p.adjust( Correlation[,3], method = "BH", n = 13650) )
Correlation <- cbind( Correlation, "BF"= p.adjust( Correlation[,3], method = "bonferroni", n = 13650) )

Correlation <- cbind( Correlation, "FDR_W_Only"= p.adjust( Correlation[,3], method = "fdr", n = 6643) )
Correlation <- cbind( Correlation, "BH_W_Only"= p.adjust( Correlation[,3], method = "BH", n = 6643) )
Correlation <- cbind( Correlation, "BF_W_Only"= p.adjust( Correlation[,3], method = "bonferroni", n = 6643) )

Correlation <- as.data.frame(Correlation)
Correlation$Sig <- 'NO'
Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'

setEPS()
postscript("DLPFC_Val.eps", onefile = TRUE)
  ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
    geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
    theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
dev.off()
ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
    geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
    theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)")

table( Correlation$Sig )
dim(Correlation[ Correlation$FDR_W_Only < 0.05, ] )
table( Correlation$`P-Val` < 0.05 )

VWs <- row.names( Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0, ] )
length(VWs)/dim(Correlation)[1]
# 71.08234 % $

setEPS()
postscript("DLPFC_Cor_All.eps", onefile = TRUE)
  hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1,
      main="Correlation of All 6643 Matched Genes in CMC DLPFC")
dev.off()

hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1,
      main="Correlation of All 6643 Matched Genes in CMC DLPFC")

setEPS()
postscript("DLFPFC_Cor_gt5Perc.eps", onefile = TRUE)
  hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
dev.off()
hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
################################################################################
#CMC ACC DATA
library(stringr)

Impute <-  as.data.frame( read.table(syn_temp$get('syn21442621')$path, header = T, sep = '\t', row.names = 1 ))
row.names(Impute)  <- Impute$IID
Impute <- Impute[ , colnames(Impute)[ (grepl("ENSG", colnames(Impute))) == T ] ]
Impute <- as.data.frame(t(Impute))
colnames(Impute) <- gsub( "BP_", "", gsub("0_", "CMC_", colnames(Impute) ))

#Exp--
Exp <- as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
Exp_ACC <- Exp[ ,(grepl("_ACC_", colnames(Exp)))==T ]

#ID--
ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )

colnames(Exp_ACC) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_ACC) ))))
Exp <- Exp_ACC
#Sync Names
Padder <- function( names ){
  #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
  foo <- do.call( rbind, strsplit(names, '_'))
  foo[,3] <- str_pad(foo[,3], 5, pad = "0")
  return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
}
colnames(Exp) <- Padder( colnames(Exp) )
colnames(Impute) <- Padder( colnames(Impute) )

#Align Matices
Impute <- Impute[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
Exp <- Exp[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
Impute <- Impute[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
Exp <- Exp[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]

Correlation <- matrix(0, dim(Exp)[1], 3)
row.names(Correlation) <- row.names(Impute)
colnames(Correlation) <- c( "Z", "Correlation", "P-Val")

Exp <- Exp[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
Impute <- Impute[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]

for( Gene in row.names(Impute) ){
  temp <- na.omit(cbind( as.numeric(Impute[Gene,]), as.numeric(Exp[Gene,]) ))
  foo <- cor.test( temp[,1], temp[,2] , method = "kendall")
  Correlation[ Gene, ] <- c( as.numeric(foo$statistic), as.numeric(foo$estimate), as.numeric(foo$p.value) )
}

Correlation <- cbind( Correlation, "Log10_Pval"= -log10(Correlation[,3]))
Correlation <- cbind( Correlation, "FDR"= p.adjust( Correlation[,3], method = "fdr", n = 13650) )
Correlation <- cbind( Correlation, "BH"= p.adjust( Correlation[,3], method = "BH", n = 13650) )
Correlation <- cbind( Correlation, "BF"= p.adjust( Correlation[,3], method = "bonferroni", n = 13650) )

Correlation <- cbind( Correlation, "FDR_W_Only"= p.adjust( Correlation[,3], method = "fdr", n = 6708) )
Correlation <- cbind( Correlation, "BH_W_Only"= p.adjust( Correlation[,3], method = "BH", n = 6708) )
Correlation <- cbind( Correlation, "BF_W_Only"= p.adjust( Correlation[,3], method = "bonferroni", n = 6708) )

Correlation <- as.data.frame(Correlation)
Correlation$Sig <- 'NO'
Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'
table(Correlation$Sig)

setEPS()
postscript("ACC_Val.eps", onefile = TRUE)
  ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
    geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
    theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
dev.off()
ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
    geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
    theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)")

setEPS()
postscript("ACC_Cor_All.eps", onefile = TRUE)
  hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1,
      main="Correlation of All 6643 Matched Genes in CMC ACC")
dev.off()
hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1,
      main="Correlation of All 6643 Matched Genes in CMC ACC")

setEPS()
postscript("ACC_Cor_gt5Perc.eps", onefile = TRUE)
  hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
dev.off()
hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
      breaks = 100, 
      xlab = 'Correlation', 
      las = 1,
      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn21478397';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'CMC Covariate analysis and Regrsison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation (ACC)';
thisFileName <- 'CMC_DataProcessing.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'ACC Validation';
activityDescription = 'CMC Validation of Imputed Expression';
CODE <- syn_temp$store(synapseclient$Folder(name = "ACC Validation", parentId = parentId))

#Set Used SynIDs For Provenance
#Syns_Used <- c("")

# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'TWAS',
  summaryLevel = 'Correlation',
  assay	 = 'TWAS imputation',
  tissueTypeAbrv	= NULL, 
  study = 'CMC', 
  organism = 'HomoSapiens',
  consortium	= 'CMC',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh37'
)

# Store results
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='DLPFC_Val.eps', name = 'DLPFC Correlation vs PValue', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='DLPFC_Cor_All.eps', name = 'DLPFC Correlation Distributions', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='DLPFC_Cor_gt5Perc.eps', name = 'DLPFC Sig Correlation Distributions', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='DLPFC_Val.eps', name = 'DLPFC Correlation vs PValue', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_All.eps', name = 'ACC Correlation Distributions', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_gt5Perc.eps', name = 'ACC Sig Correlation Distributions', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "CMC_Validation.Rmd",
                                          parentId ="syn18936948",
                                          folderName = 'ACC Validation')
```

### 2020-02-11 code/CMC_Validation.Rmd
CMC Validation

@@
 setEPS()
-postscript("DLFPFC_Cor_gt5Perc.eps", onefile = TRUE)
+postscript("DLPFC_Cor_gt5Perc.eps", onefile = TRUE)
   hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn21478397';
+parentId = 'syn18936948';
 activityName = 'Covariate and Diagnosis Regression';

### 2020-02-11 code/CMC_Validation.Rmd
CMC Validation

@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='DLPFC_Val.eps', name = 'DLPFC Correlation vs PValue', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.eps', name = 'ACC Correlation vs PValue', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'ACC'

### 2020-03-23 code/GeneSet_Expansion.Rmd
GeneSet Expansion

---
title: "GeneSet_Expansion"
output: html_document
---

```{r setup, include=FALSE}
# Source modified utility functions from limma and sva package
source("~/TWAS/code/utilityFunctions/Parallel_vbsrBootstrap.R")
library(parallel)
library(doParallel)
library(spike)
library(reshape2)

source('~/TWAS/utilityFunctions/parallelDuplicateCorrelation.R')
source('~/TWAS/utilityFunctions/irwsva.build.R')
source('~/TWAS/utilityFunctions/f.pvalue.R')
library(biomaRt)

knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

## Load in Regions and build genesets from BioMart
```{r Load}
Regions <- read.table( file='../Reference_Files/Gene_Hit_Regions.bed', header=F, sep='\t')

Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V2<-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V2+500000
Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V3<-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V3-500000

mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")
#mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
#mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", dataset = "hsapiens_gene_ensembl")

row.names(Regions) <- Regions$V4

Candidates <- list()
for( name in as.character(Regions$V4) ){
  filterlist <- paste0( Regions[ name, ]$V1, ':', Regions[ name, ]$V2, ':', Regions[ name, ]$V3 )

  ## Query biomart
  eval(parse(text= paste0( 'Candidates$', name, ' <- getBM(attributes = c(\'ensembl_gene_id\', 
                                        \'hgnc_symbol\', 
                                        \'chromosome_name\', 
                                        \'start_position\', 
                                        \'end_position\'),
                        filters = c(\'chromosomal_region\'), 
                        values = filterlist,
                        mart = mart)'
  )))
}

for( name in as.character(Regions$V4) ){
  eval(parse(text= paste0( 'Candidates$', name, ' <- Candidates$', name, '[ (Candidates$', name, '$hgnc_symbol == \'\') == F, ]' )))
}
```

## Expand Target List
```{r Expand, echo=FALSE}

reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

#SynIDs of expression data to pull from
ExpressionDS <- c('syn21292041','syn21285564','syn21285564','syn21285564','syn21285564','syn21291908')
names( ExpressionDS ) <- c( 'DLPFC', 'FP', 'IFG', 'PHG', 'STG', 'TCX')

#Study ID Translator
Study <- c( 'RosMap', 'Mayo', 'MSBB', 'MSBB', 'MSBB', 'MSBB')
names(Study) <- c('DLPFC', 'TCX', 'FP', 'IFG', 'PHG', 'STG')

Syn <- list('DLPFC', 'TCX', 'FP', 'IFG', 'PHG', 'STG')

Partials <- list()

library(parallel)
library(doParallel)
#detach("package:doParallel", unload=TRUE)
#detach("package:parallel", unload=TRUE)
cores <- detectCores()-2 
cl <- makePSOCKcluster(cores)
registerDoParallel(cl)

mark <- Sys.time()
for( name in as.character(Regions$V4) ){
 #for( Tissue in names(ExpressionDS)){
 for( Tissue in c('FP','TCX')){
  message(paste0("Working on: ", Tissue))
  #Tissue<-'DLPFC'

  #Load expression for tissue
  exp <- read.table(syn_temp$get(as.character(ExpressionDS[Tissue]))$path, header =T, sep ='\t', row.names=1)
  colnames( exp ) <- gsub( "X", "", colnames( exp ) )
  #Seperate exp by tissue
  if( Tissue == 'DLPFC'){
  }else{
    if( Tissue == 'TCX' | Tissue == 'CBE' ){
      if( Tissue == 'CBE' ){
        slec <- 'CER'
      }else{ slec <- 'TCX' }
      colnames( exp ) <- gsub( "TC", "TCX", colnames( exp ) )
      exp <- exp[ , grepl( slec, colnames(exp)) ]
    }else{
      if( Tissue %in% c('FP', 'IFG', 'PHG', 'STG') ){
        Meta <- read.table( syn_temp$get('syn21285520')$path, header =T, sep ='\t', row.names=1 )
        exp <- exp[ colnames(exp) %in% row.names(Meta[grepl( Tissue, Meta$Tissue.Diagnosis),])]
      }else{
        stop(paste0("ERROR: SOURCE=Config.yaml Issue=Tissue: ", Tissue," is improper must be one of: CBE, DLPFC, FP, IFG, PHG, STG, TCX"))
      }
    }
  }

  #Impute svalues for given gene-patient NA values
  exp <- exp[rowSums(is.na(exp))<ncol(exp), ]

  foo <- bcv::impute.svd( t(exp) )
  Exp <- foo$x
  row.names(Exp) <- row.names(t(exp)) 
  colnames(Exp) <- colnames(t(exp))

  #Prep for partial correlation detection
  Final <- data.frame()

  source("~/TWAS/code/utilityFunctions/Parallel_vbsrBootstrap.R")
  #Run Partial correlations for each gene

  RUNNe <- function( i=i, x=Exp ){ 
    library(parallel)
    library(doParallel)
    source("~/TWAS/code/utilityFunctions/Parallel_vbsrBootstrap.R")
    OBS <- i
    y <- as.matrix(x[,OBS]) 
    colnames(y) <- i
    X <- x[,(colnames(x) %in% OBS) == F ]
    att <- pvbsrBootstrap( y=y, x=X, nsamp=100, cores=1 )
    names( att ) <- gsub( "intercept", OBS, names(att) )
    att <- c( 'SeedGene' = OBS, att[ colnames(x) ]) 
    return( att[c( 'SeedGene', colnames(x) )] )
    #return(eval(parse( text = paste( c( OBS,att[colnames(x)]), sep='\t') )))
  }

  LIST <- eval( parse( text= paste0( 'Candidates$',name,'$ensembl_gene_id' )))  
  LIST  <- LIST[ (LIST %in% colnames(Exp) ) ==T ]

  mark <- Sys.time()
    foo <- t( parApply(cl, as.matrix( LIST[1:length(LIST)] ), 1, RUNNe, Exp) )
  message( paste0( Sys.time()-mark ))

  eval(parse(text=paste0( 'Partials$', name, '$', Tissue, '<- foo' )))

  message(paste0( "Finished Tissue: ", Tissue, ' For Gene: ', name ))
 }
  message(paste0( "Completed All Tissues Finished Seed Gene: ", name ))
}
mark-Sys.time()
#sink<-Partials

```
```{r SDcutOff }
library(doParallel)
library(parallel)

#Core Correlation:
Narrow <- list()

#Filter out un-named genes:
for( Gene in names(Candidates)){
  eval(parse(text=paste0( 'Candidates$', Gene, ' <- Candidates$', Gene, '[ (Candidates$', Gene, '$hgnc_symbol == \'\' )==F, ]' )))
}

Trans  <- c("ENSG00000095970", "ENSG00000198087", "ENSG00000109919", "ENSG00000074266", "ENSG00000130208", "ENSG00000103550")
names(Trans) <- c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1", 'KNOP1')

#Find Partials to Nominated Target gene:
##Filter out un-named genes (Wont work in Enrichr):
for( Gene in names(Candidates) ){
  for( Tissue in names(Study) ){
    eval(parse(text=paste0( 'Candidates$', Gene, '$', Tissue, ' <- NA')))
    eval(parse(text=paste0( 'row.names( Candidates$', Gene, ') <- Candidates$', Gene, '$ensembl_gene_id')))

    for( G in eval(parse(text=paste0( 'Candidates$', Gene, '$ensembl_gene_id' ))) ){
      #[\'', G ,'\' ]

      eval(parse(text=paste0( 'Temp <- Partials$', Gene , '$', Tissue, '[ Partials$', Gene , '$', Tissue, '[,\'SeedGene\'] == \'', Trans[Gene],'\',]' )))
      if( (G %in% names( Temp ))==TRUE){
        eval(parse(text=paste0( 'Candidates$', Gene, '[ \'',G,'\',\'', Tissue, '\'] <- as.numeric(Temp[\'',G,'\'])' )))
      }else{}

    }
  }
}

#Average Partial Correlation to Nominated Target accross the 6 tissues
for( Gene in names(Candidates) ){
  eval(parse(text=paste0( 'Candidates$', Gene,'$MEAN <- apply( Candidates$', Gene,'[,c(\'DLPFC\', \'TCX\', \'FP\', \'IFG\', \'PHG\', \'STG\')], 1, mean)')))
}

for( Gene in names(Partials)){
  eval(parse(text=paste0( 'Narrow$', Gene, ' <- vector()' )))
  #OK#_eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.01, ]' )))

  #OK#_eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.004, ]' )))
  eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.1, ]' )))
  #eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.002, ]' )))
  Keepz <- Keepz[ complete.cases(Keepz),]
  Keeps <- Keepz$ensembl_gene_id

  for(Tissue in names( ExpressionDS ) ){
    eval(parse(text=paste0( 'Tarz <- colnames(Partials$', Gene,'$', Tissue,')[ colnames(Partials$', Gene,'$', Tissue,') %in% Keeps]')))

    #eval(parse(text=paste0('TarENS <- Candidates$', Gene, '[ Candidates$', Gene, '$hgnc_symbol == \'', Gene, '\' ,]$ensembl_gene_id' )))
    eval(parse(text=paste0( 'Lookup <- Partials$', Gene,'$', Tissue, '[ Partials$', Gene,'$', Tissue, '[,\'SeedGene\'] == \'', Tarz, '\', Tarz ]' )))

    eval(parse(text=paste0( 'Narrow$', Gene, ' <- c( Narrow$', Gene, ', names( Lookup))' )))
  }
  eval(parse(text=paste0( 'Narrow$', Gene, ' <- Narrow$', Gene, '[ !duplicated(Narrow$', Gene, ')]' )))
}

##Isolate Narrow Partials Or not.. 
NewPartials <- list()
for( Gene in names(Partials)){
  eval(parse(text=paste0( 'NewPartials$', Gene, ' <- list()' )))
  for(Tissue in names( ExpressionDS ) ){
    eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue, ' <-  Partials$', Gene, '$', Tissue, '[ Partials$', Gene, '$', Tissue, '[,\'SeedGene\'] %in% Narrow$', Gene, ', ]')))
    #eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue, ' <- Partials$', Gene, '$', Tissue)))
  }
}

####Only keep genes with all 6 tissue correlations
for( Gene in names(NewPartials)){
  if( is.matrix( eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue ))) ) ){
    eval(parse(text=paste0( 'foo <- c( NewPartials$', Gene, '$DLPFC[,\'SeedGene\'], NewPartials$', Gene, '$TCX[,\'SeedGene\'], NewPartials$', Gene, '$FP[,\'SeedGene\'], NewPartials$', Gene, '$IFG[,\'SeedGene\'], NewPartials$', Gene, '$STG[,\'SeedGene\'], NewPartials$', Gene, '$PHG[,\'SeedGene\'])')))
  }else{
    eval(parse(text=paste0( 'foo <- c( NewPartials$', Gene, '$DLPFC[\'SeedGene\'], NewPartials$', Gene, '$TCX[\'SeedGene\'], NewPartials$', Gene, '$FP[\'SeedGene\'], NewPartials$', Gene, '$IFG[\'SeedGene\'], NewPartials$', Gene, '$STG[\'SeedGene\'], NewPartials$', Gene, '$PHG[\'SeedGene\'])')))
  }
  foo <- foo[ !duplicated(foo) ]
  Tib <- rep(0, length(foo))
  names(Tib) <- foo

  for(Tissue in names( ExpressionDS ) ){
    if( is.matrix( eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue ))) ) ){
      eval(parse(text=paste0( 'Tib[ NewPartials$', Gene, '$', Tissue, '[ ,\'SeedGene\' ]] <- Tib[ NewPartials$', Gene, '$', Tissue, '[ ,\'SeedGene\' ]] + 1')))
    }else{
      eval(parse(text=paste0( 'Tib[ NewPartials$', Gene, '$', Tissue, '[ \'SeedGene\' ]] <- as.numeric( Tib[ NewPartials$', Gene, '$', Tissue, '[ \'SeedGene\' ]]) + 1')))
    }
  }
  for(Tissue in names( ExpressionDS ) ){
      if( is.matrix( eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue ))) ) ){
        eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue, '<- NewPartials$', Gene, '$', Tissue, '[ NewPartials$', Gene, '$', Tissue, '[ ,\'SeedGene\' ] %in% names(Tib[Tib>3]),]')))
      }else{
        eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue, ' <- NewPartials$', Gene, '$', Tissue, '[ NewPartials$', Gene, '$', Tissue, '[ \'SeedGene\' ] %in% names(Tib[Tib>3])]')))
        eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue, ' <- t(as.matrix( NewPartials$', Gene, '$', Tissue, '))')))
      }
  }
}

Cuts <- matrix(0, 101,6)
colnames( Cuts ) <- names(Partials)
row.names( Cuts ) <-  seq( from=0, to=10, by=.1 )

mark<-Sys.time()
#_#Target <- list()
Y <- foreach( i=row.names( Cuts ), .combine=rbind ) %dopar% {
  Tar <- vector()
  Target <- list()
  for( Gene in names(NewPartials)){
  #_#eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
  #foreach( i=row.names( Cuts ), .combine=rbind ) %dopar% {
    #_#
    eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
    #_#
    for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
      Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))

      if( dim(Temp)[1] > 1 ){
        row.names(Temp) <- Temp[, 'SeedGene']
        Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
        Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
      }else{
        #row.names(Temp) <- as.character( Temp[, 'SeedGene'] )
        Cs<-as.character( Temp[, 'SeedGene'] )
        Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
        Rs <- row.names(Temp)
        Temp <- data.table::transpose(Temp)
        row.names(Temp) <- Cs
        colnames(Temp) <- Rs

        Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
      }

      for( RName in row.names(Temp) ){
        Selct <- Temp[ RName, Temp[ RName, ]>0 ]
        Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
        Vals <- c( Vals, -1*Vals )
        M <- mean( Vals )
        S <- sd( Vals )
        Lim <- M+as.numeric(i)*S
        Adds <- colnames( Selct[ , Selct > Lim ] )
        #Throw in any genes with more than 1 Parital corelation to the core set
       # if( dim(Temp)[1] > 1){
       #   Adds <- c(Adds, names(Temp[, colSums(Temp != 0) > 2 ]) )
        #  Adds <- Adds[ !duplicated(Adds) ]
        #}
        eval(parse(text=paste0( 'Target$', Gene, ' <- c(Target$', Gene, ', Adds)'  )))
      }
    }
    #Log Gene Lengths

  } 
  for(Ok in names(NewPartials)){
      eval(parse(text=paste0( 'LENG <-length(Target$', Ok, '[!duplicated(Target$', Ok, ')])'  )))
      eval(parse(text=paste0(  'Tar <- c(Tar, ',  LENG,')')))
  }
    names(Tar) <- names(NewPartials)
    Extra <- 'StDevs'
    eval(parse(text=paste0(  'Tar[\'', Extra, '\'] <- ',  i)))
    return( Tar )
}
Sys.time()-mark
#Narrow_sink <- Y
data.table::fwrite(Y, file='NarrowPartial_Expanded_Numbers.csv', row.names=F, col.names=T)

APOC1_Names <- list()
for(Tissue in names(NewPartials$APOC1) ){
  eval(parse(text=paste0('foo <- NewPartials$APOC1$', Tissue)))
  row.names( foo ) <- foo[,'SeedGene']
  foo <- foo[ , (colnames(foo) %in% 'SeedGene') == F ]
  foo <- as.data.frame(foo)
  foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))

  Count <- do.call( rbind, lapply(foo, function(x){ length(which(x==0))/length(x)}))
  eval(parse(text=paste0('APOC1_Names$',Tissue ,' <- names(Count[ Count < 0.76,])')))
}

foo <- c( APOC1_Names$DLPFC, APOC1_Names$TCX, APOC1_Names$FP, APOC1_Names$IFG, APOC1_Names$STG, APOC1_Names$PHG )
length( foo )

poo <- names( table(foo)[table(foo)>1] )
moo <-   NewPartials$APOC1$DLPFC[,"SeedGene"]

PLOT_y <- reshape::melt(as.data.frame(Y), id=c("StDevs") )
colnames(PLOT_y) <- c( "StDevs", "Seed Gene", "value" )
library(ggplot2)

###Should I Look only at genes correlated with target gene??

#10% of the targets remaining at the second Standard Deviation
CutoffVal <- round( Y[18,1:6]/10 )
LIN <- rep(0, length(names(CutoffVal)))
names(LIN) <- names(CutoffVal)
for(tar in names(CutoffVal)){
  eval(parse(text=paste0( 'LIN[\'', tar, '\'] <- Y[ Y[,\'', tar, '\'] < CutoffVal[tar], ][1,\'StDevs\']')))
}

LIN <- as.data.frame(LIN)
LIN$`Seed Gene` <- row.names(LIN)
LIN$LIN <-c( 1, 1, 1, 1, 1, 1 )
LIN$LIN <- c( 1.4, 1.5, 0.4, 1.1,1.1,1.5)

g <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
  geom_point() + 
  geom_line() +
  geom_vline(data = LIN, aes(xintercept = LIN, col=`Seed Gene`),linetype='dashed' ) +
  ylab("Partially Correlated Genes Included") +
  xlab("Standard Deviation Cutoff")

ggsave(g, file="Cutoffs.eps", device="eps")
system('synapse store --parentid syn21590299 --name Partial_Correlation_Decay Cutoffs.eps')
g

###Find Top 200 Targets:
REF <- c( 1.0, 1.3, 1.7, 1.7, 2.2, 2.2  )
names( REF ) <- names(NewPartials)

Target <- list()
for( Gene in names(NewPartials)){
  eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
  for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
    Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
    Rs <- Temp[,'SeedGene']
    row.names(Temp) <- Temp[, 'SeedGene']
    Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
    Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
     #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
    if( dim(Temp)[2] > 1 ){

    }else{
      Cs<-row.names(Temp)
      Temp <- data.table::transpose(Temp)
      row.names(Temp) <- Rs
      colnames(Temp) <- Cs
    }
    for( RName in row.names(Temp) ){

      Selct <- Temp[ RName, Temp[ RName, ]>0 ]

      Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
      Vals <- c( Vals, -1*Vals )
      M <- mean( Vals )
      S <- sd( Vals )
      #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
      FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
      SDs <- FIND[ dim(FIND)[1], 2]

      #if( Gene %in% c( "TREM2")){
        #SDs <- 0.7
      #}else{
        #if( Gene %in% c( 'APOC1')){
          #SDs <- 1.7
        #}else{
          #SDs <- 1.3
        #}
      #}
      if( Gene %in% c( "EED")){
        SDs <- 0.5
      }else{
        if( Gene %in% c( "KNOP1")){
          SDs <- 0.8
        }else{
          if( Gene %in% c( 'MTCH2') ){
            #SDs <- 0.5
            SDs <- 0.4
            #SDs <- 1.5
          }else{
            if( Gene %in% c( 'TREM2')){
              SDs <- 1.4
            }else{
              SDs <- 1.5
            }
          }
        }
      }
      Lim <- M + SDs*S
      Adds <- colnames( Selct[ , Selct > Lim ] )
      eval(parse(text=paste0( 'Target$', Gene, ' <- c(Target$', Gene, ', Adds)'  )))
    }
  }
}

for( RName in names(Target) ){
   eval(parse(text=paste0( 'Target$', RName, ' <- Target$', RName, '[!duplicated(Target$', RName, ')]'  )))
}

#```
#```{r EnrichR}

library(enrichR)
dbs <- listEnrichrDbs()

dbs <- c("GO_Molecular_Function_2018", 
         "WikiPathways_2019_Human",
         "GO_Cellular_Component_2018",
         "GO_Biological_Process_2018") #, "ProteomicsDB_2020", "KEGG_2019_Human", "DSigDB","TRRUST_Transcription_Factors_2019")

mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")

TargetGN <- list()
ENRICH <- list()

TG <- getBM(filters = 'ensembl_gene_id', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = Total_Genes, mart = mart)
TG <- TG[ TG$ensembl_gene_id !='ENSG00000265354',] 
TG$Tot <- paste0( TG$ensembl_gene_id, '_', TG$hgnc_symbol )
TG <- TG[ !duplicated(TG$Tot), ]
TG <- TG[ TG$hgnc_symbol != "", ]
row.names(TG) <- TG$hgnc_symbol

Locked_TG <- as.data.frame(TG$hgnc_symbol)
Locked_TG$Included <- 0
names(Locked_TG) <- c( "Gene", "Included" )
Locked_TG$Gene <- as.character( Locked_TG$Gene ) 
row.names(Locked_TG) <- Locked_TG$Gene

Locked_TG <- Locked_TG[ Locked_TG$Gene != 'NA', ]

for( G in names(Target)){
  eval(parse(text=paste0( 'Genes <- getBM(filters = \'ensembl_gene_id\', attributes = c(\'ensembl_gene_id\', \'hgnc_symbol\'), values = Target$', G, ', mart = mart)' )))

  GN <- Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol
  eval(parse(text=paste0('TargetGN$', G, ' <-  Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol')))

  eval(parse(text=paste0('Locked_TG[TargetGN$', G, ',]$Included <- 1')))
  #foo<- enrichr(Locked_TG, dbs)
  eval(parse(text=paste0('ENRICH$', G, ' <-  enrichr( Locked_TG[ Locked_TG$Included ==1,]$Gene, dbs)')))

  Locked_TG$Included <- 0
}
#TMP <- enrichr( GN, dbs)
for( G in names(Target)){
  for( version in dbs ){
    eval(parse(text=paste0( 'temp <- ENRICH$', G, '$', version )))
    temp <- temp[ temp$Adjusted.P.value < 0.05, ]
    eval(parse(text=paste0( 'ENRICH$', G, '$', version, ' <- temp' )))
  }
}

```
```{r clusterP}
library( clusterProfiler )
library(enrichplot)

organism = "org.Hs.eg.db"
BiocManager::install(organism, character.only = TRUE)
library(organism, character.only = TRUE)
library(DOSE)

Enrich_PLOTS <- list()
for( G in names(Target)){

  eval(parse(text=paste0( 'Genes <- getBM(filters = \'ensembl_gene_id\', attributes = c(\'ensembl_gene_id\', \'hgnc_symbol\'), values = Target$', G, ', mart = mart)' )))

  GN <- Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol
eval(parse(text=paste0('TargetGN$', G, ' <-  Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol')))

  eval(parse(text=paste0('Locked_TG[TargetGN$', G, ',]$Included <- 1')))

  eval(parse(text=paste0( 'Genes <- getBM(filters = \'ensembl_gene_id\', attributes = c(\'ensembl_gene_id\', \'hgnc_symbol\', \'entrezgene_id\'), values = Target$', G, ', mart = mart)' )))

  Locked_TG$Gene

  #sample_test <- enrichGO( Genes$entrezgene_id, OrgDb=organism, pvalueCutoff=1, qvalueCutoff=1)

  Locked_TG$ENSG <- TG[ Locked_TG$Gene, ]$ensembl_gene_id
  gene.df <- bitr( Locked_TG$ENSG, fromType = "ENSEMBL", toType = c("ENSEMBL", "SYMBOL", "ENTREZID"), OrgDb = org.Hs.eg.db)
  gene.df$Tot <- paste0( gene.df$ENSEMBL, "_", gene.df$SYMBOL, "_", gene.df$ENTREZID )
  #'select()' returned 1:many mapping between keys and columns
  #1.91% of input gene IDs are fail to map...

  Gsubset <- eval(parse(text=paste0('Target$', G )))
  Gsubset <- Gsubset[ Gsubset %in% gene.df$ENSEMBL ]
  ego <- enrichGO(gene          = Gsubset,
                universe      = gene.df$ENSEMBL,
                OrgDb         = org.Hs.eg.db,
                #keyType       = 'SYMBOL',
                keyType       = 'ENSEMBL',
                ont           = "ALL",
                pAdjustMethod = "BH",
                pvalueCutoff  = 0.01,
                qvalueCutoff  = 0.05
              )
  if( dim(summary(ego))[1] >1 ){
    eval(parse(text=paste0( 'Enrich_PLOTS$', G, ' <- list()')))
    eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Dot <- clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)' )))
    eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Net <- cnetplot(ego, foldChange=NULL)' )))
    eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Erich <- enrichplot::emapplot(ego, showCategory = 10)' )))
  }else{}
}

```

```{r CellTypeSpecificity}
Lake <- read.csv( file=syn_temp$get('syn21563069')$path, header = T )
Lake <- as.data.frame( data.table::fread( file=syn_temp$get('syn21563069')$path ) )

Total_Genes <- c( colnames( Partials$TREM2$DLPFC ),
                  colnames( Partials$TREM2$FP ),
                  colnames( Partials$TREM2$IFG ),
                  colnames( Partials$TREM2$PHG ),
                  colnames( Partials$TREM2$STG ),
                  colnames( Partials$TREM2$TCX )
)
#Take only genes in all expression sets:
Total_Genes <- names(table(Total_Genes)[ table(Total_Genes) == 6])                  
Total_Genes <- Total_Genes[ (Total_Genes == 'SeedGene') == F ]

mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")
genes <- Lake$Gene
Lake_genes <- getBM(filters = 'hgnc_symbol', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = genes, mart = mart)
Lake_genes$Tot <- paste0( Lake_genes$ensembl_gene_id, "_", Lake_genes$hgnc_symbol )
Lake_genes <- Lake_genes[ !duplicated(Lake_genes$Tot), ]
row.names(Lake_genes) <- Lake_genes$ensembl_gene_id

#filter for Lake Et. Al genes in RNA-Seq
Lake_genes <- Lake_genes[ Lake_genes$ensembl_gene_id %in% Total_Genes,]
#row.names(Lake_genes) <- Lake_genes$hgnc_symbol

#TIMM23B entry Mis-named ENSG as TIMM23:
Lake_genes[ Lake_genes$Tot == 'ENSG00000265354_TIMM23B', ]$ensembl_gene_id <- "ENSG00000204152"
Lake_genes[ Lake_genes$Tot == 'ENSG00000265354_TIMM23B', ]$Tot <- "ENSG00000204152_TIMM23B"
Lake_genes <- Lake_genes[ !duplicated(Lake_genes$Tot), ]
row.names(Lake_genes) <- Lake_genes$hgnc_symbol

#Add ENSGs to Lake data:
Lake$ENSG <- Lake_genes[ Lake$Gene, ]$ensembl_gene_id

#Throw out Lake Genes not able to be translated: 4.74%
Lake <- Lake[grepl('ENSG', Lake$ENSG)==T,]

#Cell_type ENSG List
CellTypeGenes <- list()
for( Name in names(table(Lake$Cluster)) ){
  eval(parse(text=paste0( 'CellTypeGenes$', Name, ' <- Lake[ Lake$Cluster == \'', Name,'\',]$ENSG' )))
}

#Re-Define Partial Cor Gene Sets:
GSE_Target <- list()
for( Gene in names(NewPartials)){
  eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- vector()' )))
  for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
    Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
    Rs <- Temp[,'SeedGene']
    row.names(Temp) <- Temp[, 'SeedGene']
    Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
    Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
     #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
    if( dim(Temp)[2] > 1 ){

    }else{
      Cs<-row.names(Temp)
      Temp <- data.table::transpose(Temp)
      row.names(Temp) <- Rs
      colnames(Temp) <- Cs
    }
    for( RName in row.names(Temp) ){

      Selct <- Temp[ RName, Temp[ RName, ]>0 ]

      Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
      Vals <- c( Vals, -1*Vals )
      M <- mean( Vals )
      S <- sd( Vals )
      #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
      FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
      SDs <- FIND[ dim(FIND)[1], 2]
      if( Gene %in% c( "TREM2")){
        SDs <- 0.7
      }else{
        if( Gene %in% c( 'APOC1')){
          SDs <- 1.7
        }else{
          SDs <- 1.3
        }
      }
      Lim <- M + SDs*S
      Adds <- colnames( Selct[ , Selct > Lim ] )
      eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- c(GSE_Target$', Gene, ', Adds)'  )))
    }
  }
}

# Cell Type enrichment by binomial test:
Actuals_Pval <- as.data.frame( matrix( 0, length( names(GSE_Target) ), length( names(CellTypeGenes) )) )
colnames(Actuals_Pval) <- names(CellTypeGenes) 
row.names(Actuals_Pval) <- names(GSE_Target)
Actuals_OR <- Actuals_Pval

for( G in names(GSE_Target)){
  eval(parse(text=paste0( 'N <- length( GSE_Target$', G, ')')))
  eval(parse(text=paste0( 'Genes <- GSE_Target$', G )))
  Genes <- Genes[ (Genes %in% Total_Genes) == T ]
  #Calc Actual Overlap
  for( CT in colnames(Actuals_Pval) ){
    #eval(parse(text=paste0( 'Actuals[ \'', G,'\',\'', CT,'\'] <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])')))
    eval(parse(text=paste0( 'Perc <- length(CellTypeGenes$', CT, ')/length( Total_Genes )')))
    eval(parse(text=paste0( 'Emp_Perc <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])/length( Genes )')))

    if( length( eval(parse(text=paste0('table(Genes %in% CellTypeGenes$', CT, ')' ))) ) > 1 ){ 
      eval(parse(text=paste0( 'N <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])' )))
      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))

      Foo <- binom.test( x=N, n=SIZE, p=Perc, alternative = c("two.sided") )
      #Poo <- prop.test(x=N, n=SIZE, p=Perc, alternative = "two.sided", correct = TRUE)

      if( Emp_Perc > Perc ){
        OR <- Emp_Perc/Perc
      }else{
        OR <- -1*( Perc/Emp_Perc )
      }
      #Foo$p.value

      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
    }else{
      Emp_Perc <- 0
      eval(parse(text=paste0( 'N <- 0' )))
      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))

      Foo <- binom.test( N, SIZE, Perc )
      if( Emp_Perc == 0){
        OR <- NA
      }else{
        if( Emp_Perc > Perc ){
          OR <- Emp_Perc/Perc
        }else{
          OR <- -1*( Perc/Emp_Perc )
        }
      }
      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
    }
  }
  Leng <- dim( Actuals_Pval )[2]
  eval(parse(text=paste0( 'Actuals_Pval[ \'', G, '\', ] <- p.adjust(Actuals_Pval[ \'', G, '\', ], method = \'fdr\', n = ', Leng,' )' )))
}

test_labels <- Actuals_Pval
test_labels[ test_labels< 0.05] <- "*"
test_labels[ test_labels > 0.05] <- ""

lin <- LIN
lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7 )
gG <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
  geom_point() + 
  geom_line() +
  geom_vline(data = lin, aes(xintercept = LIN, col=`Seed Gene`),linetype='dashed' ) +
  ylab("Partially Correlated Genes Included") +
  xlab("Standard Deviation Cutoff")

gG

library(RColorBrewer)
library(grDevices)
cols <- colorRampPalette(c( "deepskyblue4", "darkslategray2", "white", "darkgoldenrod2", "red"))(100)

Lake_HeatMap <- pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, 
                    display_numbers = test_labels, fontsize_number=40)

setEPS()
postscript( 'LakeHeatMap.eps' )
  pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)
dev.off()

```
```{r CellTypeSpecificity_Mathys}
Mathy <- read.csv( file=syn_temp$get('syn21785650')$path, header = T )
#Mathy <- as.data.frame( data.table::fread( file=syn_temp$get('syn21563069')$path ) )

Total_Genes <- c( colnames( Partials$TREM2$DLPFC ),
                  colnames( Partials$TREM2$FP ),
                  colnames( Partials$TREM2$IFG ),
                  colnames( Partials$TREM2$PHG ),
                  colnames( Partials$TREM2$STG ),
                  colnames( Partials$TREM2$TCX )
)
#Take only genes in all expression sets:
Total_Genes <- names(table(Total_Genes)[ table(Total_Genes) == 6])                  
Total_Genes <- Total_Genes[ (Total_Genes == 'SeedGene') == F ]

mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")
genes <- Mathy$gene.name
Mathy_genes <- getBM(filters = 'hgnc_symbol', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = genes, mart = mart)

Mathy_genes$Tot <- paste0( Mathy_genes$ensembl_gene_id, "_", Mathy_genes$hgnc_symbol )
Mathy_genes <- Mathy_genes[ !duplicated(Mathy_genes$Tot), ]
row.names(Mathy_genes) <- Mathy_genes$ensembl_gene_id

#filter for Mathys Et. Al genes in RNA-Seq
Mathy_genes <- Mathy_genes[ Mathy_genes$ensembl_gene_id %in% Total_Genes,]
row.names(Mathy_genes) <- Mathy_genes$hgnc_symbol

#Add ENSGs to Lake data:
Mathy$ENSG <- Mathy_genes[ Mathy$gene.name, ]$ensembl_gene_id

#Throw out Mathys Genes not able to be translated: 3.78%
Mathy <- Mathy[grepl('ENSG', Mathy$ENSG)==T,]

#Cell_type ENSG List
CellTypeGenes <- list()
for( Name in names(table(Mathy$subpopulation)) ){
  eval(parse(text=paste0( 'CellTypeGenes$', Name, ' <- Mathy[ Mathy$subpopulation == \'', Name,'\',]$ENSG' )))
}

#Re-Define Partial Cor Gene Sets:
GSE_Target <- list()
for( Gene in names(NewPartials)){
  eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- vector()' )))
  for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
    Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
    Rs <- Temp[,'SeedGene']
    row.names(Temp) <- Temp[, 'SeedGene']
    Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
    Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
     #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
    if( dim(Temp)[2] > 1 ){

    }else{
      Cs<-row.names(Temp)
      Temp <- data.table::transpose(Temp)
      row.names(Temp) <- Rs
      colnames(Temp) <- Cs
    }
    for( RName in row.names(Temp) ){

      Selct <- Temp[ RName, Temp[ RName, ]>0 ]

      Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
      Vals <- c( Vals, -1*Vals )
      M <- mean( Vals )
      S <- sd( Vals )
      #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
      FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
      SDs <- FIND[ dim(FIND)[1], 2]
      if( Gene %in% c( "TREM2")){
        SDs <- 0.7
      }else{
        if( Gene %in% c( 'APOC1')){
          SDs <- 1.7
        }else{
          SDs <- 1.3
        }
      }
      Lim <- M + SDs*S
      Adds <- colnames( Selct[ , Selct > Lim ] )
      eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- c(GSE_Target$', Gene, ', Adds)'  )))
    }
  }
}

# Cell Type enrichment by binomial test:
Actuals_Pval <- as.data.frame( matrix( 0, length( names(GSE_Target) ), length( names(CellTypeGenes) )) )
colnames(Actuals_Pval) <- names(CellTypeGenes) 
row.names(Actuals_Pval) <- names(GSE_Target)
Actuals_OR <- Actuals_Pval

for( G in names(GSE_Target)){
  eval(parse(text=paste0( 'N <- length( GSE_Target$', G, ')')))
  eval(parse(text=paste0( 'Genes <- GSE_Target$', G )))
  Genes <- Genes[ (Genes %in% Total_Genes) == T ]
  #Calc Actual Overlap
  for( CT in colnames(Actuals_Pval) ){
    #eval(parse(text=paste0( 'Actuals[ \'', G,'\',\'', CT,'\'] <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])')))
    eval(parse(text=paste0( 'Perc <- length(CellTypeGenes$', CT, ')/length( Total_Genes )')))
    eval(parse(text=paste0( 'Emp_Perc <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])/length( Genes )')))

    if( length( eval(parse(text=paste0('table(Genes %in% CellTypeGenes$', CT, ')' ))) ) > 1 ){ 
      eval(parse(text=paste0( 'N <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])' )))
      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))

      Foo <- binom.test( x=N, n=SIZE, p=Perc, alternative = c("two.sided") )
      #Poo <- prop.test(x=N, n=SIZE, p=Perc, alternative = "two.sided", correct = TRUE)

      if( Emp_Perc > Perc ){
        OR <- Emp_Perc/Perc
      }else{
        OR <- -1*( Perc/Emp_Perc )
      }
      #Foo$p.value

      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
    }else{
      Emp_Perc <- 0
      eval(parse(text=paste0( 'N <- 0' )))
      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))

      Foo <- binom.test( N, SIZE, Perc )
      if( Emp_Perc == 0){
        OR <- NA
      }else{
        if( Emp_Perc > Perc ){
          OR <- Emp_Perc/Perc
        }else{
          OR <- -1*( Perc/Emp_Perc )
        }
      }
      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
    }
  }
  Leng <- dim( Actuals_Pval )[2]
  eval(parse(text=paste0( 'Actuals_Pval[ \'', G, '\', ] <- p.adjust(Actuals_Pval[ \'', G, '\', ], method = \'fdr\', n = ', Leng,' )' )))
}

test_labels <- Actuals_Pval
test_labels[ test_labels< 0.05] <- "*"
test_labels[ test_labels > 0.05] <- ""

lin <- LIN
lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7 )
Mathys_G <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
  geom_point() + 
  geom_line() +
  geom_vline(data = lin, aes(xintercept = LIN, col=`Seed Gene`),linetype='dashed' ) +
  ylab("Partially Correlated Genes Included") +
  xlab("Standard Deviation Cutoff")

Mathys_G

setEPS()
postscript( 'STDEV_Cutoff.eps' )
  Mathys_G
dev.off()

#Actuals_OR <- Actuals_OR[colSums(!is.na(Actuals_OR)) > 1]
Actuals_OR[is.na(Actuals_OR)] <- 0
test_labels <- test_labels[ , colnames(Actuals_OR)]

makeColorRampPalette <- function(colors, cutoff.fraction, num.colors.in.palette)
{
  stopifnot(length(colors) == 4)
  ramp1 <- colorRampPalette(colors[1:2])(num.colors.in.palette * cutoff.fraction)
  ramp2 <- colorRampPalette(colors[3:4])(num.colors.in.palette * (1 - cutoff.fraction))
  return(c(ramp1, ramp2))
}

library(RColorBrewer)
library(grDevices)
cols <- colorRampPalette(c("navyblue", "deepskyblue4", "darkslategray2", "white", "darkgoldenrod2", "red"))(100)

Mathys_HeatMap <- pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)

setEPS()
postscript( 'MathysHeatMap.eps' )
  pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)
dev.off()

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-04-22 code/CMC_ACC_Exp_DataProcessing_V3.Rmd
update

--- 2020-02-07 code/CMC_ACC_Exp_DataProcessing_V2.Rmd
@@
 
-ProbGenes <- c("ENSG00000234593", "ENSG00000092847", "ENSG00000232878", "ENSG00000134256", "ENSG00000143393", "ENSG00000162736", "ENSG00000143156", "ENSG00000203737", "ENSG00000232036", "ENSG00000153827","ENSG00000234661", "ENSG00000131370", "ENSG00000281708", "ENSG00000242103", "ENSG00000279311", "ENSG00000249252", "ENSG00000170180", "ENSG00000240083", "ENSG00000249175", "ENSG00000229688", "ENSG00000105953", "ENSG00000146707", "ENSG00000253420", "ENSG00000279608", "ENSG00000232807", "ENSG00000119946", "ENSG00000236991", "ENSG00000177951", "ENSG00000250644", "ENSG00000158077", "ENSG00000110104", "ENSG00000149452", "ENSG00000255345", "ENSG00000254705", "ENSG00000256533", "ENSG00000249028", "ENSG00000285627", "ENSG00000111215", "ENSG00000212128", "ENSG00000066117", "ENSG00000123297", "ENSG00000270048", "ENSG00000251536", "ENSG00000237263", "ENSG00000102796", "ENSG00000258469", "ENSG00000140009", "ENSG00000259370", "ENSG00000137764", "ENSG00000127578", "ENSG00000263072", "ENSG00000261528", "ENSG00000261872", "ENSG00000198453", "ENSG00000189164", "ENSG00000149488", "ENSG00000233993", "ENSG00000100991", "ENSG00000100982", "ENSG00000243646", "ENSG00000239282", "ENSG00000068354", "ENSG00000271356", "ENSG00000241101", "ENSG00000248624", "ENSG00000227017", "ENSG00000240395", "ENSG00000285933", "ENSG00000256064", "ENSG00000177699", "ENSG00000278090", "ENSG00000264529", "ENSG00000243978", "ENSG00000225828", "ENSG00000116525", "ENSG00000225767", "ENSG00000229359", "ENSG00000143257", "ENSG00000143643", "ENSG00000272865", "ENSG00000235760", "ENSG00000227331", "ENSG00000229056", "ENSG00000183977", "ENSG00000239926", "ENSG00000239997", "ENSG00000279349", "ENSG00000229638", "ENSG00000250243", "ENSG00000249212", "ENSG00000250361", "ENSG00000250910", "ENSG00000283355", "ENSG00000251634", "ENSG00000061455", "ENSG00000285605", "ENSG00000285868", "ENSG00000235859", "ENSG00000228735", "ENSG00000205485", "ENSG00000236018", "ENSG00000260721", "ENSG00000169946", "ENSG00000234740", "ENSG00000136925", "ENSG00000237461", "ENSG00000182752", "ENSG00000205696", "ENSG00000285852", "ENSG00000178440", "ENSG00000107819", "ENSG00000131620", "ENSG00000256589", "ENSG00000256682", "ENSG00000213363", "ENSG00000110887", "ENSG00000126216", "ENSG00000258648", "ENSG00000196553", "ENSG00000250130", "ENSG00000259619", "ENSG00000236194", "ENSG00000263089", "ENSG00000235552", "ENSG00000278971", "ENSG00000222460", "ENSG00000235347", "ENSG00000185448", "ENSG00000233204", "ENSG00000184616", "ENSG00000238184", "ENSG00000274322", "ENSG00000235038", "ENSG00000230470", "ENSG00000234601", "ENSG00000277769", "ENSG00000232131", "ENSG00000235631", "ENSG00000272076", "ENSG00000168828", "ENSG00000279822", "ENSG00000235010", "ENSG00000280379", "ENSG00000286067", "ENSG00000279628", "ENSG00000265316", "ENSG00000277829", "ENSG00000223799", "ENSG00000231875", "ENSG00000227232", "ENSG00000160679", "ENSG00000236440", "ENSG00000206341", "ENSG00000138071", "ENSG00000131507", "ENSG00000179151", "ENSG00000263326", "ENSG00000109111", "ENSG00000166317", "ENSG00000219433" )
+ProbGenes <- c( "ENSG00000227232", "ENSG00000225828", "ENSG00000116525", "ENSG00000092847", "ENSG00000225767", "ENSG00000229359", "ENSG00000143393", "ENSG00000160679", "ENSG00000162736", "ENSG00000143257", "ENSG00000143156", "ENSG00000203737", "ENSG00000232036", "ENSG00000143643", "ENSG00000272865", "ENSG00000235760", "ENSG00000138071", "ENSG00000236440", "ENSG00000227331", "ENSG00000229056", "ENSG00000153827", "ENSG00000234661", "ENSG00000131370", "ENSG00000183977", "ENSG00000281708", "ENSG00000239926", "ENSG00000239997", "ENSG00000279349", "ENSG00000242103", "ENSG00000229638", "ENSG00000249252", "ENSG00000250243", "ENSG00000249212", "ENSG00000250361", "ENSG00000250910", "ENSG00000283355", "ENSG00000251634", "ENSG00000131507", "ENSG00000285605", "ENSG00000206341", "ENSG00000229688", "ENSG00000235859", "ENSG00000105953", "ENSG00000228735", "ENSG00000205485", "ENSG00000146707", "ENSG00000236018", "ENSG00000260721", "ENSG00000169946", "ENSG00000253420", "ENSG00000234740", "ENSG00000279608", "ENSG00000136925", "ENSG00000237461", "ENSG00000182752", "ENSG00000205696", "ENSG00000285852", "ENSG00000178440", "ENSG00000119946", "ENSG00000107819", "ENSG00000236991", "ENSG00000177951", "ENSG00000110104", "ENSG00000149452", "ENSG00000131620", "ENSG00000255345", "ENSG00000254705", "ENSG00000256533", "ENSG00000285627", "ENSG00000256589", "ENSG00000111215", "ENSG00000256682", "ENSG00000212128", "ENSG00000066117", "ENSG00000123297", "ENSG00000213363", "ENSG00000110887", "ENSG00000270048", "ENSG00000102796", "ENSG00000126216", "ENSG00000258648", "ENSG00000258469", "ENSG00000140009", "ENSG00000196553", "ENSG00000250130", "ENSG00000259619", "ENSG00000259370", "ENSG00000137764", "ENSG00000179151", "ENSG00000263072", "ENSG00000261528", "ENSG00000263326", "ENSG00000109111", "ENSG00000236194", "ENSG00000261872", "ENSG00000263089", "ENSG00000235552", "ENSG00000278971", "ENSG00000198453", "ENSG00000189164", "ENSG00000233993", "ENSG00000100991", "ENSG00000222460", "ENSG00000100982", "ENSG00000243646", "ENSG00000235347", "ENSG00000068354", "ENSG00000233204", "ENSG00000184616", "ENSG00000238184", "ENSG00000274322", "ENSG00000235038", "ENSG00000230470", "ENSG00000234601", "ENSG00000271356", "ENSG00000241101", "ENSG00000248624", "ENSG00000277769", "ENSG00000232131", "ENSG00000227017", "ENSG00000235631", "ENSG00000240395", "ENSG00000272076", "ENSG00000168828", "ENSG00000279822", "ENSG00000235010", "ENSG00000285933", "ENSG00000280379", "ENSG00000286067", "ENSG00000279628", "ENSG00000177699", "ENSG00000265316", "ENSG00000277829", "ENSG00000223799", "ENSG00000231875", "ENSG00000234593", "ENSG00000232878", "ENSG00000134256", "ENSG00000279311", "ENSG00000170180", "ENSG00000240083", "ENSG00000249175", "ENSG00000061455", "ENSG00000285868", "ENSG00000232807", "ENSG00000166317", "ENSG00000250644", "ENSG00000158077", "ENSG00000249028", "ENSG00000251536", "ENSG00000237263", "ENSG00000127578", "ENSG00000149488", "ENSG00000239282", "ENSG00000185448", "ENSG00000256064", "ENSG00000278090", "ENSG00000264529", "ENSG00000243978", "ENSG00000219433")
 
-fooOld <- c('ENSG00000227232', 'ENSG00000248527', 'ENSG00000285812', 'ENSG00000272455', 'ENSG00000215915', 'ENSG00000269737', 'ENSG00000157911', 'ENSG00000226029', 'ENSG00000121775', 'ENSG00000225828', 'ENSG00000116525', 'ENSG00000197982', 'ENSG00000285728', 'ENSG00000225767', 'ENSG00000229359', 'ENSG00000270629', 'ENSG00000160679', 'ENSG00000177954', 'ENSG00000227741', 'ENSG00000143257', 'ENSG00000236535', 'ENSG00000118194', 'ENSG00000143862', 'ENSG00000240219', 'ENSG00000123838', 'ENSG00000272645', 'ENSG00000143643', 'ENSG00000223694', 'ENSG00000272865', 'ENSG00000286216', 'ENSG00000179270', 'ENSG00000235760', 'ENSG00000144031', 'ENSG00000115282', 'ENSG00000232931', 'ENSG00000236440', 'ENSG00000227331', 'ENSG00000272211', 'ENSG00000229056', 'ENSG00000144410', 'ENSG00000144452', 'ENSG00000152056', 'ENSG00000183977', 'ENSG00000230409', 'ENSG00000172940', 'ENSG00000232354', 'ENSG00000281691', 'ENSG00000162267', 'ENSG00000189283', 'ENSG00000239926', 'ENSG00000239997', 'ENSG00000279349', 'ENSG00000285943', 'ENSG00000241278', 'ENSG00000240695', 'ENSG00000114113', 'ENSG00000240875', 'ENSG00000206120', 'ENSG00000229638', 'ENSG00000225473', 'ENSG00000230732', 'ENSG00000242686', 'ENSG00000249592', 'ENSG00000013810', 'ENSG00000284727', 'ENSG00000249212', 'ENSG00000251022', 'ENSG00000250361', 'ENSG00000250910', 'ENSG00000164105', 'ENSG00000283355', 'ENSG00000261360', 'ENSG00000274441', 'ENSG00000152669', 'ENSG00000205571', 'ENSG00000251634', 'ENSG00000171530', 'ENSG00000061455', 'ENSG00000164406', 'ENSG00000285605', 'ENSG00000241112', 'ENSG00000285868', 'ENSG00000241956', 'ENSG00000124588', 'ENSG00000189134', 'ENSG00000206341', 'ENSG00000204227', 'ENSG00000156639', 'ENSG00000272137', 'ENSG00000146242', 'ENSG00000255330', 'ENSG00000118514', 'ENSG00000146576', 'ENSG00000235859', 'ENSG00000183696', 'ENSG00000228735', 'ENSG00000234500', 'ENSG00000274080', 'ENSG00000205485', 'ENSG00000121716', 'ENSG00000271664', 'ENSG00000260555', 'ENSG00000236018', 'ENSG00000260721', 'ENSG00000249258', 'ENSG00000158815', 'ENSG00000197181', 'ENSG00000253200', 'ENSG00000134013', 'ENSG00000250979', 'ENSG00000253948', 'ENSG00000169946', 'ENSG00000253372', 'ENSG00000104529', 'ENSG00000234740', 'ENSG00000164970', 'ENSG00000237159', 'ENSG00000274026', 'ENSG00000136925', 'ENSG00000237461', 'ENSG00000196739', 'ENSG00000182752', 'ENSG00000286196', 'ENSG00000234771', 'ENSG00000280474', 'ENSG00000214402', 'ENSG00000197070', 'ENSG00000205696', 'ENSG00000285852', 'ENSG00000285737', 'ENSG00000188234', 'ENSG00000204172', 'ENSG00000178440', 'ENSG00000166343', 'ENSG00000229990', 'ENSG00000236552', 'ENSG00000155287', 'ENSG00000107819', 'ENSG00000273521', 'ENSG00000203772', 'ENSG00000177595', 'ENSG00000117983', 'ENSG00000247595', 'ENSG00000254622', 'ENSG00000162236', 'ENSG00000213465', 'ENSG00000110025', 'ENSG00000131620', 'ENSG00000241170', 'ENSG00000186174', 'ENSG00000186166', 'ENSG00000240970', 'ENSG00000254428', 'ENSG00000254909', 'ENSG00000110811', 'ENSG00000111664', 'ENSG00000111678', 'ENSG00000205885', 'ENSG00000256589', 'ENSG00000256682', 'ENSG00000247903', 'ENSG00000257433', 'ENSG00000139631', 'ENSG00000185482', 'ENSG00000123329', 'ENSG00000166987', 'ENSG00000178498', 'ENSG00000224713', 'ENSG00000213363', 'ENSG00000110887', 'ENSG00000257097', 'ENSG00000251497', 'ENSG00000279500', 'ENSG00000279283', 'ENSG00000198553', 'ENSG00000043355', 'ENSG00000126216', 'ENSG00000233695', 'ENSG00000258515', 'ENSG00000270433', 'ENSG00000276698', 'ENSG00000257986', 'ENSG00000258648', 'ENSG00000258682', 'ENSG00000196553', 'ENSG00000100632', 'ENSG00000258376', 'ENSG00000258891', 'ENSG00000183648', 'ENSG00000202191', 'ENSG00000223403', 'ENSG00000246451', 'ENSG00000201992', 'ENSG00000215252', 'ENSG00000243789', 'ENSG00000242866', 'ENSG00000250130', 'ENSG00000259619', 'ENSG00000247982', 'ENSG00000255346', 'ENSG00000246877', 'ENSG00000169752', 'ENSG00000274376', 'ENSG00000255769', 'ENSG00000249487', 'ENSG00000261505', 'ENSG00000261123', 'ENSG00000259895', 'ENSG00000279520', 'ENSG00000262312', 'ENSG00000188897', 'ENSG00000243716', 'ENSG00000166851', 'ENSG00000224310')
-
- tmp<-c(              'ENSG00000262155', 'ENSG00000260853', 'ENSG00000279789', 'ENSG00000156858', 'ENSG00000261439', 'ENSG00000089505', 'ENSG00000280334', 'ENSG00000280214', 'ENSG00000196436', 'ENSG00000140905', 'ENSG00000280182', 'ENSG00000226180', 'ENSG00000224888', 'ENSG00000170296', 'ENSG00000263934', 'ENSG00000266385', 'ENSG00000073605', 'ENSG00000236194', 'ENSG00000266967', 'ENSG00000262265', 'ENSG00000121104', 'ENSG00000243678', 'ENSG00000263089', 'ENSG00000263499', 'ENSG00000213246', 'ENSG00000172809', 'ENSG00000279382', 'ENSG00000262580', 'ENSG00000235552', 'ENSG00000263847', 'ENSG00000278983', 'ENSG00000278971', 'ENSG00000273218', 'ENSG00000268189', 'ENSG00000279203', 'ENSG00000279716', 'ENSG00000280332', 'ENSG00000267419', 'ENSG00000105185', 'ENSG00000239382', 'ENSG00000267053', 'ENSG00000233527', 'ENSG00000267254', 'ENSG00000171777', 'ENSG00000105221', 'ENSG00000268460', 'ENSG00000063177', 'ENSG00000104852', 'ENSG00000074219', 'ENSG00000167608', 'ENSG00000267838', 'ENSG00000177732', 'ENSG00000088832', 'ENSG00000131044', 'ENSG00000101421', 'ENSG00000222460', 'ENSG00000183798', 'ENSG00000101104', 'ENSG00000124172', 'ENSG00000286018', 'ENSG00000160224', 'ENSG00000223901', 'ENSG00000239415', 'ENSG00000234409', 'ENSG00000250479', 'ENSG00000279738', 'ENSG00000205702', 'ENSG00000226450', 'ENSG00000182841', 'ENSG00000279175', 'ENSG00000280434', 'ENSG00000235347', 'ENSG00000170638', 'ENSG00000185448', 'ENSG00000271199', 'ENSG00000198960', 'ENSG00000286000', 'ENSG00000241489', 'ENSG00000213397', 'ENSG00000198938', 'ENSG00000137970', 'ENSG00000230470', 'ENSG00000234781', 'ENSG00000233204', 'ENSG00000214389', 'ENSG00000235631', 'ENSG00000280379', 'ENSG00000279628', 'ENSG00000276663', 'ENSG00000263551', 'ENSG00000265316', 'ENSG00000231875', 'ENSG00000235790', 'ENSG00000242516', 'ENSG00000272040', 'ENSG00000250472', 'ENSG00000281706', 'ENSG00000184616', 'ENSG00000285581', 'ENSG00000238184', 'ENSG00000258136', 'ENSG00000136378', 'ENSG00000140682', 'ENSG00000279251', 'ENSG00000108375', 'ENSG00000279917', 'ENSG00000269318', 'ENSG00000270804', 'ENSG00000274322', 'ENSG00000235958', 'ENSG00000235038', 'ENSG00000228686', 'ENSG00000058673', 'ENSG00000234601', 'ENSG00000236549', 'ENSG00000091181', 'ENSG00000145020', 'ENSG00000248734', 'ENSG00000277769', 'ENSG00000146285', 'ENSG00000232131', 'ENSG00000228495', 'ENSG00000231760', 'ENSG00000272076', 'ENSG00000168828', 'ENSG00000279822', 'ENSG00000235010', 'ENSG00000250397', 'ENSG00000255159', 'ENSG00000258102', 'ENSG00000286067', 'ENSG00000274317', 'ENSG00000180662', 'ENSG00000259499', 'ENSG00000261207', 'ENSG00000175311', 'ENSG00000260751', 'ENSG00000261291', 'ENSG00000278668', 'ENSG00000266598', 'ENSG00000280248', 'ENSG00000276952', 'ENSG00000277829', 'ENSG00000223799', 'ENSG00000213790', 'ENSG00000271916', 'ENSG00000249863', 'ENSG00000267655', 'ENSG00000133872', 'ENSG00000224689','ENSG00000255389', 'ENSG00000253230', 'ENSG00000247137', 'ENSG00000170906', 'ENSG00000182195' )
-
- #ProbGenes <- c(ProbGenes,tmp)
 ```
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
-
-FactorCovariates <- c('Individual_ID','FlowcellBatch', "Institution", "Reported_Gender", "LibraryBatch", "Tissue", "Dx.Tissue", "Dx", "RibozeroBatch")
+FactorCovariates <- c('Individual_ID', 'tBatch', 'FlowcellBatch', "Institution", "Reported_Gender", "LibraryBatch", "Tissue", "Dx.Tissue", "Dx", "RibozeroBatch")
 #_#FactorCovariates <- c('Individual_ID', "Institution","Dx.Tissue", "Reported_Gender", "Dx", "RibozeroBatch")
-ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
+ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "TotalReads", "ExpProfEfficiency", "rRNARate","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5") #####
 
@@
 #counts <- counts[ , METADATA$SampleID]
+METADATA$tBatch <- gsub( '/', '_', gsub( "\\)", "", gsub( "\\)_", "_", gsub( " \\(", "_", paste0(METADATA$LibraryBatch,"_", METADATA$FlowcellBatch, "_", METADATA$RibozeroBatch) ))))
 
@@
 ```{r filter.genes}
-
-COUNT<-counts[,METADATA$SampleID]
+COUNT<-counts[,as.character(METADATA$SampleID)]
 row.names(COVARIATES) <- METADATA$SampleID
@@
 
+COVARIATES1$tBatch <- as.factor(as.character(COVARIATES1$tBatch))
 COVARIATES1$Institution <- as.factor(as.character(COVARIATES1$Institution))
@@
 COVARIATES1$Ancestry <- as.factor(as.character(METADATA[row.names(COVARIATES1),]$Ethnicity))
+COVARIATES1$Block <- as.factor(as.character(sample(c(1:50), dim(COVARIATES1)[1], replace = TRUE, prob = NULL)))
+
+#COVARIATES1 <- COVARIATES1[,(colnames(COVARIATES1) %in% c("RibozeroBatch","FlowcellBatch", "tBatch")) == F ] #"LibraryBatch"
 
@@
 ```{r iterative.norm, results='asis'}
+COVARIATES1$Block <- as.factor(as.character(sample(c(1:50), dim(COVARIATES1)[1], replace = TRUE, prob = NULL)))
 
 # Primary variable of interest
-postAdjustCovars = c('Institution', 'FlowcellBatch', 'Reported_Gender');
-#postAdjustCovars = c('Institution', 'Reported_Gender');
+# postAdjustCovars = c('Institution', 'FlowcellBatch', 'Reported_Gender');
+#_#postAdjustCovars = c('Dx', 'RIN', 'IntronicRate')
+postAdjustCovars = c( 'IntronicRate', 'RIN', 'ExpProfEfficiency' ) #'MappedReads'
+
 # Assign residual covariates
-residualCovars = setdiff(preAdjustedSigCovars$significantCovars, 
-                         c(postAdjustCovars, primaryVariable, 'Individual_ID'))
+#residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, 'Individual_ID', 'Block'))
+residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, 'Ancestry', 'Block'))
 residualSigCovars = preAdjustedSigCovars
+#covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars][ (names(preAdjustedSigCovars$Effects.significantCovars[residualCovars]) %in% 'tBatch') == F ]
 covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
@@
 
-COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 485, replace = TRUE, prob = NULL)))
-
 loopCount = 0 
 while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
-  COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 485, replace = TRUE, prob = NULL)))
+  #COVARIATES1$Block <- as.factor(as.character(sample(c(1:50), 485, replace = TRUE, prob = NULL)))
   writeLines(paste0('Working on Loop: ', loopCount))
@@
   correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
-
-                                             block = COVARIATES1$Block,
+                                             block = COVARIATES1$Ancestry,
                                              method = 'lmer')
@@
                                 design=DM1$design, plot=F, 
-
-                                block = COVARIATES1$Block, 
+                                block = COVARIATES1$Ancestry, 
                                 correlation = correlation$cor)
@@
                               weights = VOOM.GENE_EXPRESSION$weights,
-
-                              block = COVARIATES1$Block, 
+                              block = COVARIATES1$Ancestry, 
                               correlation = correlation$cor)
@@
                          c(postAdjustCovars, primaryVariable, 'Individual_ID', notEstimable))
-
-  residCovars <- residCovars[ (residCovars == 'Tissue') == F ]
+  residCovars <- residCovars[ (residCovars == 'Tissue') == F ] #& (residCovars == 'FlowcellBatch') == F  & (residCovars == 'RibozeroBatch') == F & (residCovars == 'LibraryBatch') == F  ]
 
@@
   residualSigCovars = runPCAandPlotCorrelations(expr, 
-
-                                                COVARIATES[, residCovars, drop=F], 
+                                                COVARIATES1[, residCovars[(residCovars %in% 'tBatch') == F], drop=F], 
                                                 'adjusted design(voom-normalized)',
@@
                         design = DESIGN.NET, plot=F,
-                        block = COVARIATES$Donor_ID, 
+                        block = COVARIATES1$Ancestry, 
                         correlation = correlation$cor)
@@
                      design = VOOM.NET.WEIGHTS$design,
-                     block = COVARIATES$Donor_ID, 
+                     block = COVARIATES1$Ancestry, 
                      correlation = correlation$cor)
@@
 ```{r sva.adjust}
+#FactorCovariates <- c("Individual_ID", "FlowcellBatch", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
 
-FactorCovariates <- c("Individual_ID", "FlowcellBatch", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
-ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
+FactorCovariates <- c("Individual_ID", "Institution", "Reported_Gender",  "Dx.Tissue", "Dx", "LibraryBatch") #, "tBatch","LibraryBatch", RibozeroBatch")
+#####_FactorCovariates <- c("Individual_ID", "tBatch", "FlowcellBatch", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx" ,            "RibozeroBatch")
+
+ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")#
+
+#####_ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected",     "ExpProfEfficiency", "rRNARate", "AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
+
 COVARIATES1[,FactorCovariates] = lapply(COVARIATES1[,FactorCovariates], factor)
@@
                     design=DESIGN$design, plot=F,
-
-                    block = COVARIATES1$Block, 
+                    block = COVARIATES1$Ancestry, 
                     correlation = correlation$cor)
@@
             design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
-            block = COVARIATES1$Block, 
+            block = COVARIATES1$Ancestry, 
             correlation = correlation$cor)
@@
 # Get (null) design matrix
-MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
+#MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
+MODEL0 = DESIGN$design[,-grep('RIN',colnames(DESIGN$design))]
 MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
@@
                         design = cbind(MODEL1, SURR.VAR), plot=F,
-                        block = COVARIATES1$Block, 
+                        block = COVARIATES1$Ancestry, 
                         correlation = correlation$cor)
@@
                      design = VOOM.SVA.WEIGHTS$design,
-                     block = COVARIATES1$Block, 
+                     block = COVARIATES1$Ancestry, 
                      correlation = correlation$cor)
@@
 createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing_V2.Rmd",
-
                                           parentId ="syn21478397",

### 2020-04-22 code/GeneSet_Expansion.Rmd
update

@@
 
-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V2<-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V2+500000
-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V3<-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1"), ]$V3-500000
+row.names(Regions) <- Regions$V4
+
+Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1","CEACAM19","CLPTM1"), ]$V2 <- Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1","CEACAM19","CLPTM1"), ]$V2+500000
+Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1","CEACAM19","CLPTM1"), ]$V3<-Regions[ c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1","CEACAM19","CLPTM1"), ]$V3-500000
 
@@
 
-row.names(Regions) <- Regions$V4
+#row.names(Regions) <- Regions$V4
 
@@
 for( name in as.character(Regions$V4) ){
+
   filterlist <- paste0( Regions[ name, ]$V1, ':', Regions[ name, ]$V2, ':', Regions[ name, ]$V3 )
@@
  #for( Tissue in names(ExpressionDS)){
- for( Tissue in c('FP','TCX')){
+ for( Tissue in names(ExpressionDS) ){
   message(paste0("Working on: ", Tissue))
@@
 
-Trans  <- c("ENSG00000095970", "ENSG00000198087", "ENSG00000109919", "ENSG00000074266", "ENSG00000130208", "ENSG00000103550")
-names(Trans) <- c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1", 'KNOP1')
+Trans  <- c("ENSG00000095970", "ENSG00000198087", "ENSG00000109919", "ENSG00000074266", "ENSG00000130208", "ENSG00000103550", "ENSG00000186567", "ENSG00000104853")
+names(Trans) <- c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1", 'KNOP1', "CEACAM19", "CLPTM1")
 
@@
 
-Cuts <- matrix(0, 101,6)
+Cuts <- matrix(0, 101,length(names(Partials)))
 colnames( Cuts ) <- names(Partials)
@@
 #10% of the targets remaining at the second Standard Deviation
-CutoffVal <- round( Y[18,1:6]/10 )
+CutoffVal <- round( Y[18,1:8]/10 )
 LIN <- rep(0, length(names(CutoffVal)))
@@
 LIN$`Seed Gene` <- row.names(LIN)
-LIN$LIN <-c( 1, 1, 1, 1, 1, 1 )
-LIN$LIN <- c( 1.4, 1.5, 0.4, 1.1,1.1,1.5)
+#LIN$LIN <-c( 1, 1, 1, 1, 1, 1 )
+LIN$LIN <- c( 0.7, 1.3, 1.3, 1.3, 1.3, 1.7, 1.3, 1.3)
 
@@
 ggsave(g, file="Cutoffs.eps", device="eps")
-system('synapse store --parentid syn21590299 --name Partial_Correlation_Decay Cutoffs.eps')
+system('synapse store --parentid syn21818446 --name Partial_Correlation_Decay Cutoffs.eps')
 g
@@
 ###Find Top 200 Targets:
-REF <- c( 1.0, 1.3, 1.7, 1.7, 2.2, 2.2  )
+REF <- c( 0.7, 1.3, 1.3, 1.3, 1.3, 1.7, 1.3, 1.3 )
 names( REF ) <- names(NewPartials)
@@
 
+Total_Genes <- c( colnames( Partials$TREM2$DLPFC ),
+                  colnames( Partials$TREM2$FP ),
+                  colnames( Partials$TREM2$IFG ),
+                  colnames( Partials$TREM2$PHG ),
+                  colnames( Partials$TREM2$STG ),
+                  colnames( Partials$TREM2$TCX )
+)
+#Take only genes in all expression sets:
+Total_Genes <- names(table(Total_Genes)[ table(Total_Genes) == 6])                  
+Total_Genes <- Total_Genes[ (Total_Genes == 'SeedGene') == F ]
+
 TG <- getBM(filters = 'ensembl_gene_id', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = Total_Genes, mart = mart)
@@
 ```{r clusterP}
+
+parentId = 'syn18936948';
+activityName = 'Gene Set Enrichment';
+activityDescription = 'Figure 4: gene set enrichment of genes implicated in TWAS regions';
+thisFileName <- 'GeneSet_Expansion.Rmd'
+# Github link
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+
+CODE <- syn_temp$store(synapseclient$Folder(name = "Gene Set Enrichment Plots", parentId = parentId))
+
 library( clusterProfiler )
@@
 
+Enrich_Run <- function( cutoffs ){
+  #'@cutoffs a named vector of SD cutoff valutes for genes
+  SD_Store <- rep(NA,length(names(NewPartials)))
+  names(SD_Store) <- names(NewPartials)
+
+  Target <- list()
+  for( Gene in names(NewPartials)){
+    eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
+    for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
+      Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
+      Rs <- Temp[,'SeedGene']
+      row.names(Temp) <- Temp[, 'SeedGene']
+      Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
+      Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
+       #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
+      if( dim(Temp)[2] > 1 ){
+
+      }else{
+        Cs<-row.names(Temp)
+        Temp <- data.table::transpose(Temp)
+        row.names(Temp) <- Rs
+        colnames(Temp) <- Cs
+      }
+      for( RName in row.names(Temp) ){
+
+        Selct <- Temp[ RName, Temp[ RName, ]>0 ]
+
+        Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
+        Vals <- c( Vals, -1*Vals )
+        M <- mean( Vals )
+        S <- sd( Vals )
+        #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
+        FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
+        SDs <- FIND[ dim(FIND)[1], 2]
+
+        eval( parse( text = paste0( 'SDs <- cutoffs[\'', Gene,'\']' )))
+        eval( parse( text = paste0( 'SD_Store[\'', Gene,'\'] <- ', SDs )))
+        Lim <- M + SDs*S
+        Adds <- colnames( Selct[ , Selct > Lim ] )
+        eval(parse(text=paste0( 'Target$', Gene, ' <- c(Target$', Gene, ', Adds)'  )))
+      }
+    }
+  }
+
+  for( RName in names(Target) ){
+     eval(parse(text=paste0( 'Target$', RName, ' <- Target$', RName, '[!duplicated(Target$', RName, ')]'  )))
+  }
+
   organism = "org.Hs.eg.db"
-BiocManager::install(organism, character.only = TRUE)
+  #BiocManager::install(organism, character.only = TRUE)
   library(organism, character.only = TRUE)
@@
 
-  Locked_TG$Gene
+    #Locked_TG$Gene
 
@@
                 )
-  if( dim(summary(ego))[1] >1 ){
+
+    eval(parse(text=paste0( 'SD_Used <- as.numeric(cutoffs[\'', G, '\'])' )))
+    if( dim(as.data.frame(ego))[1] >1 ){
+      cluster_summary <- data.frame(ego)
+      write.csv(cluster_summary , file = paste0("EnrichmentResults_", G, "_Stdevs_", SD_Used,".csv"), row.names=FALSE)
+
+      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentResults_", G, "_Stdevs_", SD_Used,".csv"), name = paste0("EnrichmentResults_", G, "_Stdevs_", SD_Used), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
       eval(parse(text=paste0( 'Enrich_PLOTS$', G, ' <- list()')))
+      # Dotplot
       eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Dot <- clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)' )))
+      pdf(file = paste0("EnrichmentDotPlot_", G, "_Stdevs_", SD_Used,".pdf"), width = 14, height = 7)
+         print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+      dev.off()
+
+      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", G, "_Stdevs_", SD_Used,".pdf"), name = paste0("EnrichmentDotPlot_", G, "_Stdevs_", SD_Used), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+      # Net Plot
       eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Net <- cnetplot(ego, foldChange=NULL)' )))
+
+      pdf(file = paste0("EnrichmentNetPlot_", G, "_Stdevs_", SD_Used,".pdf"), width = 7, height = 7)
+         print( cnetplot(ego, foldChange=NULL))
+      dev.off()
+
+      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", G, "_Stdevs_", SD_Used,".pdf"), name = paste0("EnrichmentNetPlot_", G, "_Stdevs_", SD_Used), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+      # Enrichment Plot
       eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Erich <- enrichplot::emapplot(ego, showCategory = 10)' )))
+
+      pdf(file = paste0("EnrichmentEnrichPlot_", G, "_Stdevs_", SD_Used,".pdf"), width = 7, height = 7)
+        print( enrichplot::emapplot(ego, showCategory = 10) )
+      dev.off()
+
+      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentEnrichPlot_", G, "_Stdevs_", SD_Used,".pdf"), name = paste0("EnrichmentEnrichPlot_", G, "_Stdevs_", SD_Used,".pdf"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
     }else{}
   }
+}
+
+#Run Enrichment at Broad Cutoffs:
+input <- c( TREM2 = 0.8, 
+            CD2AP= 0.8, 
+            MTCH2= 0.8, 
+            EED= 0.8, 
+            KNOP1= 0.8, 
+            APOC1= 0.8,
+            CEACAM19= 0.8,
+            CLPTM1= 0.8
+          )
+Enrich_Run( input )
+
+#Run Enrichment at Narrow Cutoffs:
+input <- c( TREM2 = 2.8, 
+            CD2AP = 2.8, 
+            MTCH2 = 2.8, 
+            EED = 2.8, 
+            KNOP1 = 2.8, 
+            APOC1 = 2.8,
+            CEACAM19= 2.8,
+            CLPTM1= 2.8
+          )
+Enrich_Run( input )
+
+#Run Enrichment at Custom Cutoffs:
+input <- c( TREM2 = 0.8, 
+            #CD2AP = 2, 
+            CD2AP = 1,
+            MTCH2 = 0.4, 
+            EED = 2, 
+            KNOP1 = 2, 
+            APOC1 = 1.7,
+            CEACAM19= 2,
+            CLPTM1= 2
+          )
+Enrich_Run( input )
+#if( Gene %in% c( "TREM2")){
+          #SDs <- 0.7
+          #SDs <- 2.8
+        #}else{
+          #if( Gene %in% c( 'APOC1')){
+            #SDs <- 1.7
+            #SDs <- 2.8
+          #}else{
+            #SDs <- 1.3
+            #SDs <- 2.8
+          #}
+        #}
+        #if( Gene %in% c( "EED")){
+          #SDs <- 0.5
+        #}else{
+          #if( Gene %in% c( "KNOP1")){
+           # SDs <- 0.8
+          #}else{
+            #if( Gene %in% c( 'MTCH2') ){
+              #SDs <- 0.5
+              #SDs <- 0.4
+              #SDs <- 1.5
+            #}else{
+              #if( Gene %in% c( 'TREM2')){
+                #SDs <- 1.4
+              #}else{
+                #SDs <- 1.5
+              #}
+            #}
+          #}
+        #}
 
@@
 lin <- LIN
-lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7 )
+lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7,1.3,1.3 )
 gG <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
@@
 
-setEPS()
-postscript( 'LakeHeatMap.eps' )
-  pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)
+save_pheatmap_pdf <- function(x, filename, width=7, height=7) {
+   stopifnot(!missing(x))
+   stopifnot(!missing(filename))
+   pdf(filename, width=width, height=height)
+   grid::grid.newpage()
+   grid::grid.draw(x$gtable)
    dev.off()
+}
+
+save_pheatmap_pdf(Lake_HeatMap, "Lake_HeatMap.pdf")
 
@@
 lin <- LIN
-lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7 )
+lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7,1.3,1.3 )
 Mathys_G <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
@@
 Mathys_HeatMap <- pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)
-
-setEPS()
-postscript( 'MathysHeatMap.eps' )
-  pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)
-dev.off()
+save_pheatmap_pdf(Mathys_HeatMap, "Mathys_HeatMap.pdf")
+
+parentId = 'syn18936948';
+activityName = 'Gene Set Enrichment';
+activityDescription = 'Figure 4: gene set enrichment of genes implicated in TWAS regions';
+thisFileName <- 'GeneSet_Expansion.Rmd'
+# Github link
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+
+CODE <- syn_temp$store(synapseclient$Folder(name = "Gene Set Enrichment Plots", parentId = parentId))
+
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='STDEV_Cutoff.eps', name = 'StDev Cutoff values of Partial Correlations', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Lake_HeatMap.pdf', name = 'Lake et.al CellType Specificity', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Mathys_HeatMap.pdf', name = 'Mathys et.al CellType Specificity', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
 

### 2020-04-30 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

---
title: "MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Iterative Model"
author: "Addapted from Kelsey Montgomery"
date: "11/8/2019"
output: html_document
---

Date of analysis update: "`r date()`"

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
##It is assumed your working directory is "~/ampad-DiffExp/gene_level_analysis"
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(stringr)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(glmnet)
library(githubr) # get the package from devtools::install_github('brian-bot/githubr')
library(knitr)
library(doParallel)
library(foreach)
library(sva)
#library(reticulate)
library(R.utils)
library(data.table)

cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
# Source modified utility functions from limma and sva package
source('~/TWAS/utilityFunctions/parallelDuplicateCorrelation.R')
source('~/TWAS/utilityFunctions/irwsva.build.R')
source('~/TWAS/utilityFunctions/f.pvalue.R')
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

### Problem Genes in the iterative normalization:
```{r prob.genes, cache=TRUE, include=FALSE}

#ProbGenes <- c("ENSG00000234593", "ENSG00000092847", "ENSG00000232878", "ENSG00000134256", "ENSG00000143393", "ENSG00000162736", "ENSG00000143156", "ENSG00000203737", "ENSG00000232036", "ENSG00000153827","ENSG00000234661", "ENSG00000131370", "ENSG00000281708", "ENSG00000242103", "ENSG00000279311", "ENSG00000249252", "ENSG00000170180", "ENSG00000240083", "ENSG00000249175", "ENSG00000229688", "ENSG00000105953", "ENSG00000146707", "ENSG00000253420", "ENSG00000279608", "ENSG00000232807", "ENSG00000119946", "ENSG00000236991", "ENSG00000177951", "ENSG00000250644", "ENSG00000158077", "ENSG00000110104", "ENSG00000149452", "ENSG00000255345", "ENSG00000254705", "ENSG00000256533", "ENSG00000249028", "ENSG00000285627", "ENSG00000111215", "ENSG00000212128", "ENSG00000066117", "ENSG00000123297", "ENSG00000270048", "ENSG00000251536", "ENSG00000237263", "ENSG00000102796", "ENSG00000258469", "ENSG00000140009", "ENSG00000259370", "ENSG00000137764", "ENSG00000127578", "ENSG00000263072", "ENSG00000261528", "ENSG00000261872", "ENSG00000198453", "ENSG00000189164", "ENSG00000149488", "ENSG00000233993", "ENSG00000100991", "ENSG00000100982", "ENSG00000243646", "ENSG00000239282", "ENSG00000068354", "ENSG00000271356", "ENSG00000241101", "ENSG00000248624", "ENSG00000227017", "ENSG00000240395", "ENSG00000285933", "ENSG00000256064", "ENSG00000177699", "ENSG00000278090", "ENSG00000264529", "ENSG00000243978", "ENSG00000225828", "ENSG00000116525", "ENSG00000225767", "ENSG00000229359", "ENSG00000143257", "ENSG00000143643", "ENSG00000272865", "ENSG00000235760", "ENSG00000227331", "ENSG00000229056", "ENSG00000183977", "ENSG00000239926", "ENSG00000239997", "ENSG00000279349", "ENSG00000229638", "ENSG00000250243", "ENSG00000249212", "ENSG00000250361", "ENSG00000250910", "ENSG00000283355", "ENSG00000251634", "ENSG00000061455", "ENSG00000285605", "ENSG00000285868", "ENSG00000235859", "ENSG00000228735", "ENSG00000205485", "ENSG00000236018", "ENSG00000260721", "ENSG00000169946", "ENSG00000234740", "ENSG00000136925", "ENSG00000237461", "ENSG00000182752", "ENSG00000205696", "ENSG00000285852", "ENSG00000178440", "ENSG00000107819", "ENSG00000131620", "ENSG00000256589", "ENSG00000256682", "ENSG00000213363", "ENSG00000110887", "ENSG00000126216", "ENSG00000258648", "ENSG00000196553", "ENSG00000250130", "ENSG00000259619", "ENSG00000236194", "ENSG00000263089", "ENSG00000235552", "ENSG00000278971", "ENSG00000222460", "ENSG00000235347", "ENSG00000185448", "ENSG00000233204", "ENSG00000184616", "ENSG00000238184", "ENSG00000274322", "ENSG00000235038", "ENSG00000230470", "ENSG00000234601", "ENSG00000277769", "ENSG00000232131", "ENSG00000235631", "ENSG00000272076", "ENSG00000168828", "ENSG00000279822", "ENSG00000235010", "ENSG00000280379", "ENSG00000286067", "ENSG00000279628", "ENSG00000265316", "ENSG00000277829", "ENSG00000223799", "ENSG00000231875", "ENSG00000227232", "ENSG00000160679", "ENSG00000236440", "ENSG00000206341", "ENSG00000138071", "ENSG00000131507", "ENSG00000179151", "ENSG00000263326", "ENSG00000109111", "ENSG00000166317", "ENSG00000219433" )

#fooOld <- c('ENSG00000227232', 'ENSG00000248527', 'ENSG00000285812', 'ENSG00000272455', 'ENSG00000215915', 'ENSG00000269737', 'ENSG00000157911', 'ENSG00000226029', 'ENSG00000121775', 'ENSG00000225828', 'ENSG00000116525', 'ENSG00000197982', 'ENSG00000285728', 'ENSG00000225767', 'ENSG00000229359', 'ENSG00000270629', 'ENSG00000160679', 'ENSG00000177954', 'ENSG00000227741', 'ENSG00000143257', 'ENSG00000236535', 'ENSG00000118194', 'ENSG00000143862', 'ENSG00000240219', 'ENSG00000123838', 'ENSG00000272645', 'ENSG00000143643', 'ENSG00000223694', 'ENSG00000272865', 'ENSG00000286216', 'ENSG00000179270', 'ENSG00000235760', 'ENSG00000144031', 'ENSG00000115282', 'ENSG00000232931', 'ENSG00000236440', 'ENSG00000227331', 'ENSG00000272211', 'ENSG00000229056', 'ENSG00000144410', 'ENSG00000144452', 'ENSG00000152056', 'ENSG00000183977', 'ENSG00000230409', 'ENSG00000172940', 'ENSG00000232354', 'ENSG00000281691', 'ENSG00000162267', 'ENSG00000189283', 'ENSG00000239926', 'ENSG00000239997', 'ENSG00000279349', 'ENSG00000285943', 'ENSG00000241278', 'ENSG00000240695', 'ENSG00000114113', 'ENSG00000240875', 'ENSG00000206120', 'ENSG00000229638', 'ENSG00000225473', 'ENSG00000230732', 'ENSG00000242686', 'ENSG00000249592', 'ENSG00000013810', 'ENSG00000284727', 'ENSG00000249212', 'ENSG00000251022', 'ENSG00000250361', 'ENSG00000250910', 'ENSG00000164105', 'ENSG00000283355', 'ENSG00000261360', 'ENSG00000274441', 'ENSG00000152669', 'ENSG00000205571', 'ENSG00000251634', 'ENSG00000171530', 'ENSG00000061455', 'ENSG00000164406', 'ENSG00000285605', 'ENSG00000241112', 'ENSG00000285868', 'ENSG00000241956', 'ENSG00000124588', 'ENSG00000189134', 'ENSG00000206341', 'ENSG00000204227', 'ENSG00000156639', 'ENSG00000272137', 'ENSG00000146242', 'ENSG00000255330', 'ENSG00000118514', 'ENSG00000146576', 'ENSG00000235859', 'ENSG00000183696', 'ENSG00000228735', 'ENSG00000234500', 'ENSG00000274080', 'ENSG00000205485', 'ENSG00000121716', 'ENSG00000271664', 'ENSG00000260555', 'ENSG00000236018', 'ENSG00000260721', 'ENSG00000249258', 'ENSG00000158815', 'ENSG00000197181', 'ENSG00000253200', 'ENSG00000134013', 'ENSG00000250979', 'ENSG00000253948', 'ENSG00000169946', 'ENSG00000253372', 'ENSG00000104529', 'ENSG00000234740', 'ENSG00000164970', 'ENSG00000237159', 'ENSG00000274026', 'ENSG00000136925', 'ENSG00000237461', 'ENSG00000196739', 'ENSG00000182752', 'ENSG00000286196', 'ENSG00000234771', 'ENSG00000280474', 'ENSG00000214402', 'ENSG00000197070', 'ENSG00000205696', 'ENSG00000285852', 'ENSG00000285737', 'ENSG00000188234', 'ENSG00000204172', 'ENSG00000178440', 'ENSG00000166343', 'ENSG00000229990', 'ENSG00000236552', 'ENSG00000155287', 'ENSG00000107819', 'ENSG00000273521', 'ENSG00000203772', 'ENSG00000177595', 'ENSG00000117983', 'ENSG00000247595', 'ENSG00000254622', 'ENSG00000162236', 'ENSG00000213465', 'ENSG00000110025', 'ENSG00000131620', 'ENSG00000241170', 'ENSG00000186174', 'ENSG00000186166', 'ENSG00000240970', 'ENSG00000254428', 'ENSG00000254909', 'ENSG00000110811', 'ENSG00000111664', 'ENSG00000111678', 'ENSG00000205885', 'ENSG00000256589', 'ENSG00000256682', 'ENSG00000247903', 'ENSG00000257433', 'ENSG00000139631', 'ENSG00000185482', 'ENSG00000123329', 'ENSG00000166987', 'ENSG00000178498', 'ENSG00000224713', 'ENSG00000213363', 'ENSG00000110887', 'ENSG00000257097', 'ENSG00000251497', 'ENSG00000279500', 'ENSG00000279283', 'ENSG00000198553', 'ENSG00000043355', 'ENSG00000126216', 'ENSG00000233695', 'ENSG00000258515', 'ENSG00000270433', 'ENSG00000276698', 'ENSG00000257986', 'ENSG00000258648', 'ENSG00000258682', 'ENSG00000196553', 'ENSG00000100632', 'ENSG00000258376', 'ENSG00000258891', 'ENSG00000183648', 'ENSG00000202191', 'ENSG00000223403', 'ENSG00000246451', 'ENSG00000201992', 'ENSG00000215252', 'ENSG00000243789', 'ENSG00000242866', 'ENSG00000250130', 'ENSG00000259619', 'ENSG00000247982', 'ENSG00000255346', 'ENSG00000246877', 'ENSG00000169752', 'ENSG00000274376', 'ENSG00000255769', 'ENSG00000249487', 'ENSG00000261505', 'ENSG00000261123', 'ENSG00000259895', 'ENSG00000279520', 'ENSG00000262312', 'ENSG00000188897', 'ENSG00000243716', 'ENSG00000166851', 'ENSG00000224310')

 #tmp<-c(              'ENSG00000262155', 'ENSG00000260853', 'ENSG00000279789', 'ENSG00000156858', 'ENSG00000261439', 'ENSG00000089505', 'ENSG00000280334', 'ENSG00000280214', 'ENSG00000196436', 'ENSG00000140905', 'ENSG00000280182', 'ENSG00000226180', 'ENSG00000224888', 'ENSG00000170296', 'ENSG00000263934', 'ENSG00000266385', 'ENSG00000073605', 'ENSG00000236194', 'ENSG00000266967', 'ENSG00000262265', 'ENSG00000121104', 'ENSG00000243678', 'ENSG00000263089', 'ENSG00000263499', 'ENSG00000213246', 'ENSG00000172809', 'ENSG00000279382', 'ENSG00000262580', 'ENSG00000235552', 'ENSG00000263847', 'ENSG00000278983', 'ENSG00000278971', 'ENSG00000273218', 'ENSG00000268189', 'ENSG00000279203', 'ENSG00000279716', 'ENSG00000280332', 'ENSG00000267419', 'ENSG00000105185', 'ENSG00000239382', 'ENSG00000267053', 'ENSG00000233527', 'ENSG00000267254', 'ENSG00000171777', 'ENSG00000105221', 'ENSG00000268460', 'ENSG00000063177', 'ENSG00000104852', 'ENSG00000074219', 'ENSG00000167608', 'ENSG00000267838', 'ENSG00000177732', 'ENSG00000088832', 'ENSG00000131044', 'ENSG00000101421', 'ENSG00000222460', 'ENSG00000183798', 'ENSG00000101104', 'ENSG00000124172', 'ENSG00000286018', 'ENSG00000160224', 'ENSG00000223901', 'ENSG00000239415', 'ENSG00000234409', 'ENSG00000250479', 'ENSG00000279738', 'ENSG00000205702', 'ENSG00000226450', 'ENSG00000182841', 'ENSG00000279175', 'ENSG00000280434', 'ENSG00000235347', 'ENSG00000170638', 'ENSG00000185448', 'ENSG00000271199', 'ENSG00000198960', 'ENSG00000286000', 'ENSG00000241489', 'ENSG00000213397', 'ENSG00000198938', 'ENSG00000137970', 'ENSG00000230470', 'ENSG00000234781', 'ENSG00000233204', 'ENSG00000214389', 'ENSG00000235631', 'ENSG00000280379', 'ENSG00000279628', 'ENSG00000276663', 'ENSG00000263551', 'ENSG00000265316', 'ENSG00000231875', 'ENSG00000235790', 'ENSG00000242516', 'ENSG00000272040', 'ENSG00000250472', 'ENSG00000281706', 'ENSG00000184616', 'ENSG00000285581', 'ENSG00000238184', 'ENSG00000258136', 'ENSG00000136378', 'ENSG00000140682', 'ENSG00000279251', 'ENSG00000108375', 'ENSG00000279917', 'ENSG00000269318', 'ENSG00000270804', 'ENSG00000274322', 'ENSG00000235958', 'ENSG00000235038', 'ENSG00000228686', 'ENSG00000058673', 'ENSG00000234601', 'ENSG00000236549', 'ENSG00000091181', 'ENSG00000145020', 'ENSG00000248734', 'ENSG00000277769', 'ENSG00000146285', 'ENSG00000232131', 'ENSG00000228495', 'ENSG00000231760', 'ENSG00000272076', 'ENSG00000168828', 'ENSG00000279822', 'ENSG00000235010', 'ENSG00000250397', 'ENSG00000255159', 'ENSG00000258102', 'ENSG00000286067', 'ENSG00000274317', 'ENSG00000180662', 'ENSG00000259499', 'ENSG00000261207', 'ENSG00000175311', 'ENSG00000260751', 'ENSG00000261291', 'ENSG00000278668', 'ENSG00000266598', 'ENSG00000280248', 'ENSG00000276952', 'ENSG00000277829', 'ENSG00000223799', 'ENSG00000213790', 'ENSG00000271916', 'ENSG00000249863', 'ENSG00000267655', 'ENSG00000133872', 'ENSG00000224689','ENSG00000255389', 'ENSG00000253230', 'ENSG00000247137', 'ENSG00000170906', 'ENSG00000182195' )

 #ProbGenes <- c(ProbGenes,tmp)
```

### Data download
#### Obtain count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(syn_temp$get(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(syn_temp$get(id, version = version)$path, data.table = F)
}
# Download reprocessed counts
CountDwnld <- function( ID ){
  counts = ID
  counts = downloadFile(counts) %>% data.frame()
  #_# Fix  Row Names of Counts
  counts$Chr <- NULL
  counts$Start <- NULL
  counts$End <- NULL
  counts$Strand <- NULL
  row.names(counts) <- counts$Geneid #  do.call( rbind, strsplit(counts$Geneid,"[.]") )[,1]
  return( counts )
}
#_Deprecated_# counts = 'syn21071622'
#ACC:
ACC_counts <- CountDwnld( 'syn16783557' )
#PFC:
DLPFC_counts = CountDwnld( 'syn16783508' )
ALL_USED_IDs = c('syn16783557','syn16783508')

if( all( row.names(ACC_counts) %in% row.names(DLPFC_counts) ) ){
  gene_lengths = ACC_counts[,c("Geneid", "Length")]
  ACC_counts$Length <- NULL
  DLPFC_counts$Length <- NULL
  gene_lengths <- rename(gene_lengths, gene_id = Geneid)
  counts <- merge(ACC_counts, DLPFC_counts[,colnames(DLPFC_counts) != 'Geneid'], by=0)
}else{
  warning('Expression Rows not equal')
}

#row.names(counts) <- counts$Geneid #  do.call( rbind, strsplit(counts$Geneid,"[.]") )[,1]

# Parse gene lengths

# Get ancestry vector calculated using gemtools
ANCESTRY_ID = 'syn2511399'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = ANCESTRY_ID
ANCESTRY = downloadFile(ANCESTRY_ID) %>% 
  plyr::rename(c('DNA_report..Genotyping.Sample_ID' = 'SNP_report:Genotyping_Sample_ID'))
# Get genotype ids from synapse
GENOTYPE_ID = 'syn16816490'
ALL_USED_IDs = c(ALL_USED_IDs, GENOTYPE_ID)
GENOTYPE = downloadFile(GENOTYPE_ID) %>% 
  dplyr::select(Individual_ID, `SNP_report:Genotyping_Sample_ID`) %>%
  dplyr::inner_join(ANCESTRY)
#Get Metadata
#--syn16783596

metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 13)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, Ethnicity, Age_of_Death, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))
METADATA = metadata %>%
  dplyr::left_join(GENOTYPE) %>%
  dplyr::rename(PMI = `PMI_(in_hours)`,
                Sample_ID = Sample_RNA_ID,
                ReportExclude = `rnaSeq_report:Exclude?`,
                SampleID = Sample_RNA_ID,
                LibraryBatch = `rnaSeq_report:Library_Batch`,
                FlowcellBatch = `rnaSeq_report:Flowcell_Batch`,
                RibozeroBatch = `rnaSeq_report:Ribozero_Batch`,
                Tissue = `rnaSeq_dissection:Brain_Region`,
                MappedReads = `rnaSeq_report:Mapped_Reads`,
                IntragenicRate = `rnaSeq_report:Intragenic_Rate`, 
                IntronicRate = `rnaSeq_report:Intronic_Rate`, 
                IntergenicRate = `rnaSeq_report:Intergenic_Rate`, 
                GenesDetected = `rnaSeq_report:Genes_Detected`,
                ExpProfEfficiency = `rnaSeq_report:Expression_Profiling_Efficiency`, 
                rRNARate = `rnaSeq_report:rRNA_Rate`,
                TotalReads = `rnaSeq_report:Total_Reads`, 
                AlignmentRate = `rnaSeq_report:Percent_Aligned`,
                RIN = `rnaSeq_isolation:RIN`) %>%
  dplyr::select(SampleID, Individual_ID, Institution, Reported_Gender,Sex, Ethnicity, Age_of_Death, PMI, Dx, 
                RIN, ReportExclude, EV.1, EV.2, EV.3, EV.4, EV.5,
                LibraryBatch, FlowcellBatch, RibozeroBatch, Tissue, MappedReads, TotalReads, GenesDetected, AlignmentRate,
                IntragenicRate, IntergenicRate, IntronicRate, ExpProfEfficiency, rRNARate) %>% 
  dplyr::filter(Institution %in% c("MSSM", "Penn", "Pitt")) %>% 
  dplyr::filter(SampleID %in% colnames(counts), !is.na(SampleID)) %>%
  dplyr::mutate(Dx = forcats::fct_recode(Dx,  Other = "AFF", Other = "BP", Control = "Control", SCZ = "SCZ"))

#Load this alignments Seq Stats:
AltMeta <- 'syn16783596'
altACC = downloadFile_version(AltMeta, version = 1)
AltMeta <- 'syn16783867'
altPFCC = downloadFile_version(AltMeta, version = 1)
alt <- rbind(altACC, altPFCC)

colnames(alt) <- c('cnt', 'ID', 'TotalReads', 'MappedReads','GenesDetected', 'TranscriptsDetected', 'AlignmentRate', 
                   'IntragenicRate', 'IntronicRate', 'IntergenicRate', 'ExpProfEfficiency', 'rRNARate')

#Get rid of FlowcellBatch
METADATA <- METADATA[ , colnames(METADATA) != 'FlowcellBatch' ]
METADATA <- METADATA[ !duplicated(METADATA),]
row.names(METADATA) <- METADATA$SampleID
row.names(alt) <- alt$ID
METADATA <- METADATA[  row.names(alt), ]

#Now copy in relevant New Seq Stats:
METADATA$MappedReads <- alt[ row.names(METADATA), ]$MappedReads
METADATA$TotalReads <- alt[ row.names(METADATA), ]$TotalReads
METADATA$GenesDetected <- alt[ row.names(METADATA), ]$GenesDetected
METADATA$AlignmentRate <- alt[ row.names(METADATA), ]$AlignmentRate
METADATA$IntragenicRate <- alt[ row.names(METADATA), ]$IntragenicRate
METADATA$IntergenicRate <- alt[ row.names(METADATA), ]$IntergenicRate
METADATA$IntronicRate <- alt[ row.names(METADATA), ]$IntronicRate
METADATA$ExpProfEfficiency <- alt[ row.names(METADATA), ]$ExpProfEfficiency
METADATA$rRNARate <- alt[ row.names(METADATA), ]$rRNARate
```

### Data preprocessing
```{r preprocess.data}
ind = METADATA$SampleID[which(METADATA$ReportExclude == 1)]
writeLines(paste('Following',length(ind),'samples are marked exclude'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Ethnicity) | is.na(METADATA$Institution) | is.na(METADATA$Dx)]
writeLines(paste('Following', length(ind), 'counts are missing clinical metadata'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$PMI)]
writeLines(paste('Following', length(ind), 'counts are missing PMI'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Reported_Gender)]
writeLines(paste('Following', length(ind), 'counts are missing gender'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind)) 
ind = METADATA$SampleID [is.na(METADATA$Age_of_Death)]
writeLines(paste('Following', length(ind), 'counts are missing age of death'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind))
ind = METADATA$SampleID [is.na(METADATA$EV.1)]
writeLines(paste('Following', length(ind), 'counts are missing ancestry information'))
writeLines(paste(ind, collapse = ', '))
METADATA <- METADATA  %>% dplyr::filter(!(SampleID %in% ind))
```

```{r preprocess.data1, results='asis'}
# Match covariates to expression data
indToRetain = intersect(METADATA$SampleID, colnames(counts))
rownames(counts) <- counts$Geneid
counts = counts[,indToRetain]
rownames(METADATA) = METADATA$SampleID
METADATA = METADATA[indToRetain,]
METADATA %>% 
  group_by(Dx, Tissue) %>% 
  summarise(count = n()) %>% 
  spread(Tissue, count) %>%
  kable()
#_# Add in Dx.TissueSource
METADATA = METADATA %>%
  dplyr::mutate(Dx.Tissue = paste(Dx, Tissue, sep = '.')) %>%
  dplyr::mutate(Dx.TissueSource = paste(Dx, Tissue, Institution, sep = '.'))
```

```{r gene.param}
## Get GC content from biomart
backgroundGenes = data.frame(gene_id = rownames(counts)) %>%
  dplyr::mutate(id = gene_id) %>%
  tidyr::separate(id, c('ensembl_gene_id','position'), sep = '\\.')
# Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
# Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "percentage_gene_gc_content", "gene_biotype", "chromosome_name"),
                       filters = "ensembl_gene_id", values = backgroundGenes$ensembl_gene_id,
                       mart = mart)
GENE.GC.CONT = Ensemble2HGNC %>%
  dplyr::left_join(backgroundGenes) %>% 
  dplyr::select(gene_id, percentage_gene_gc_content, chromosome_name) %>%
  unique
rownames(GENE.GC.CONT) = GENE.GC.CONT$gene_id
```

### Sex Check
```{r Reported_Gender_plots}
counts$gene_id = rownames(counts) 
REPORTED.GENDER.COUNTS = GENE.GC.CONT %>% 
  left_join(counts) %>%
  dplyr::select(-one_of("percentage_gene_gc_content")) %>%
  filter(chromosome_name == "X" |chromosome_name == "Y") %>% 
  tidyr::gather(key = item, value = value, -c(gene_id, chromosome_name)) %>%
  mutate(value = log(value)) %>%
  rename(`counts(log)`= value) %>% 
  rename(SampleID = item) %>%
  left_join(METADATA[,c("SampleID", "Reported_Gender")]) %>% 
  rename(`Reported Gender` = Reported_Gender) 
##XIST and UTY expression 
#ENSG00000229807.10 and ENSG00000183878.15 
#ENSG00000229807.11
FILT <- REPORTED.GENDER.COUNTS %>% 
  #_#filter(gene_id == "ENSG00000229807.11" | gene_id == "ENSG00000183878.15") %>% 
  filter(gene_id == "ENSG00000229807.10" | gene_id == "ENSG00000183878.15") %>% 
  dplyr::select(-one_of("chromosome_name")) %>% 
  tidyr::spread(key = gene_id, value = `counts(log)`) %>% 
  #_#mutate(XIST = as.numeric(`ENSG00000229807.11`)) %>% 
  mutate(XIST = as.numeric(`ENSG00000229807.10`)) %>% 
  mutate(UTY = as.numeric(`ENSG00000183878.15`))
p = ggplot(FILT, aes (x= XIST, y = UTY)) 
p = p + geom_point(aes(color=`Reported Gender`)) 
p
```

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering}
#primaryVariable <- c("Tissue.SourceDiagnosis", "Tissue.Diagnosis", "Tissue.APOE4")
primaryVariable <- c("Dx.TissueSource", "Dx.Tissue")
#_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
#_#Removed 'FlowCellBatch' and FactorCovariates
FactorCovariates <- c('Individual_ID', "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
#_#FactorCovariates <- c('Individual_ID', "Institution","Dx.Tissue", "Reported_Gender", "Dx", "RibozeroBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

#METADATA <- METADATA[ METADATA$Tissue == 'DLPFC', ]
#counts <- counts[ , METADATA$SampleID]

# Find inter relation between factor covariates
METADATA <- METADATA[ !duplicated(METADATA), ]
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
rownames(COVARIATES) <- METADATA$ID
# Convert factor covariates to factors
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
```
Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, cache=FALSE, fig.width=10, fig.height=6}
COVARIATES.CORRELATION = getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left', padding  = unit(c(18,2,2,18), 'mm'))
```
### Explore metadata
```{r data.explore, cache=FALSE, fig.width = 12, fig.height = 8}

##--Combo--##METADATA <- METADATA[ METADATA$Tissue == 'ACC', ]
counts <- counts[ , METADATA$SampleID]
##--Combo--##COVARIATES=COVARIATES[ COVARIATES$Tissue == 'ACC' ,]
my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = RIN)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + my.theme
# AgeAtDeath
p[[2]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(Age_of_Death))) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('Age_of_Death') + my.theme
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(PMI))) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI') + my.theme
# Ribosomal bases
p[[4]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(rRNARate))) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Fraction of Ribosomal Bases') + my.theme
# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(IntronicRate))) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + my.theme
# Intergenic bases
p[[6]] = ggplot(COVARIATES, aes(x = Dx.Tissue, y = as.numeric(IntergenicRate))) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Intergenic Bases') + my.theme
multiplot(plotlist = p, cols = 3)
```

### Filter genes
* Remove genes that have less than 1 cpm counts in at least 50% of samples per Tissue x Diagnosis
* Remove genes with missing gene length and percentage GC content
```{r filter.genes}

COUNT<-counts[,METADATA$SampleID]
row.names(COVARIATES) <- METADATA$SampleID

Unis <- do.call(rbind, strsplit(as.character(row.names(COUNT)), '\\.'))[,1]
dups <- Unis[ duplicated(Unis) ]
Prosps <- do.call(rbind, strsplit(as.character(row.names(COUNT)), '\\.'))
Prosps <- Prosps[ (Prosps[,1] %in% dups) == F,]
keeps <- paste0( Prosps[,1], '.', Prosps[,2] )

COUNT <- COUNT[ keeps, ]

row.names(COUNT) <- do.call(rbind, strsplit(as.character(row.names(COUNT)), '\\.'))[,1]

#colnames(COVARIATES)[1] <- 'SampleID'
#colnames(COUNT) <- paste0( "CMC_", gsub("RNA_BP_PFC_","",colnames(COUNT)) )
#colnames(COUNT) <- gsub("RNA_PFC_","",colnames(COUNT)) 
#colnames(COUNT) <- gsub("RNA_ACC_","",colnames(COUNT)) 
#colnames(COUNT) <- gsub("BP_","",colnames(COUNT)) 
#tmp <- do.call(rbind, strsplit(colnames(COUNT), '_'))
#tmp[,3] <- str_pad(tmp[,3], 3, pad = "0")
#colnames(COUNT) <- paste0(tmp[,1], '_', tmp[,2], '_',tmp[,3])
#COVARIATES$SampleID <- as.character(COVARIATES$SampleID)
#row.names(COVARIATES) <- COVARIATES$SampleID
#table(METADATA$SampleID %in% colnames(COUNT))
#table(colnames(COUNT) %in% METADATA$SampleID )

genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Dx.Tissue), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)

    #processed.counts = getGeneFilteredGeneExprMatrix(COUNT[,METADATA$SampleID],
                                                     #MIN_GENE_CPM=1, 
                                                     #MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)

GENE.PARAM = syn_temp$get('syn21156161', version = 3)$path %>% 
  read.table(sep = '\t', header = T, stringsAsFactors = F)
#row.names(GENE.PARAM) <- GENE.PARAM$ensembl_gene_id
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene.length) %>% unique()
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gc_content) %>% unique()
rownames(GENE.GC) = GENE.GC$ensembl_gene_id

genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gc_content)]) %>%
  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene.length)]) %>%
  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))

PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
                                                 MIN_GENE_CPM=0, 
                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
# Check gene biotype
## Define biomart object
mart <- useMart(biomart = "ENSEMBL_MART_ENSEMBL", host = "jul2019.archive.ensembl.org", dataset = "hsapiens_gene_ensembl")
## Query biomart
Ensemble2HGNC <- getBM(attributes = c("ensembl_gene_id", "hgnc_symbol", "gene_biotype"),
                       filters = "ensembl_gene_id", 
                       values = PROCESSED_COUNTS$filteredExprMatrix$genes,
                       mart = mart)
summary(factor(Ensemble2HGNC$gene_biotype)) %>%
  rownameToFirstColumn('Biotype') %>%
  dplyr::rename(fraction = DF) %>%
  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
  dplyr::filter(fraction >= 0.01) %>%
  kable
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

### Library Normalisation
Library normalisation is performed using cqn (conditional quantile normalisation)
```{r cqn}
row.names(GENE.GC) <- GENE.GC$ensembl_gene_id
row.names(GENE.LEN) <- GENE.LEN$ensembl_gene_id
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gc_content'],
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'gene.length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Outlier Analysis
#### Sample outliers
Outlier analysis is performed before library normalisation with raw cpm counts
```{r outlier.analysis, cache = FALSE, fig.width = 10}
#indToRemove = c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX",
#                '1950_TCX', '1950_CER', '1925_TCX', '1957_CER')
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  dplyr::mutate(label = SampleID) %>%
  tidyr::separate(Dx.Tissue, c('Diagnosis', 'Tissue'), sep = '\\.')
#plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Institution, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") 
p <- p + facet_grid(Tissue~.+Diagnosis, scales = 'free')
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Dx.Tissue, c('Tissue', 'Diagnosis'), sep = '\\.')
indToRemove <- ''
p = ggplot(tmp1 %>%
             #dplyr::filter(SampleID %in% indToRemove) %>%
             droplevels(),
           aes(x = logCPM)) + geom_density() 
p = p + theme(legend.position = 'top') + facet_grid(Tissue~.+Diagnosis)
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = COVARIATES %>%
  dplyr::group_by(Dx.Tissue) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::separate(Dx.Tissue, c('Diagnosis', 'Tissue'), sep = '\\.') %>%
  tidyr::spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are: `r kable(tmp)`

#### Gene outliers
Assign NA values to genes that are above and below 3 std deviation of its distribution
```{r winsorise.data}
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
#_# CQN.GENE_EXPRESSION$E = LOG.CPM[ (row.names(LOG.CPM) %in% ProbGenes) == F, ]
CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6

dim(NEW.COUNTS)
#_# NEW.COUNTS <- NEW.COUNTS[ (row.names(NEW.COUNTS) %in% ProbGenes) == F, ]
dim(NEW.COUNTS)
```

### Sample clustering
PCA based clustering of samples
```{r decompse.normalise.data, cache=FALSE, fig.height=8, fig.width=8, results='asis', cache=FALSE}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  tidyr::separate(Dx.Tissue, c( 'Diagnosis', 'Tissue'), sep = '\\.')
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Institution, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") + facet_grid(Tissue+.~Diagnosis, scales = 'free_y')
p
```

Tree based clustering of samples
```{r decompse.normalise.data.1, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
COVARIATES.tmp = (COVARIATES[,c(FactorCovariates), drop = F])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.no.na)))
for( i in 1:dim(COVARIATES.tmp)[2]){
  COVARIATES.tmp[,i] <- as.numeric(COVARIATES.tmp[,i])
}
COVARIATES.tmp <- COVARIATES.tmp[,2:dim(COVARIATES.tmp)[2]]
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE, fig.height=10, fig.width=20}
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              rownameToFirstColumn('SampleID')) %>%
  tidyr::separate(Dx.Tissue, c( 'Diagnosis', 'Tissue' ), sep = '\\.')
p = ggplot(tmp1, aes(x = logCPM)) + geom_density() 
p = p + theme(legend.position = 'NONE') + facet_grid(Tissue+.~Diagnosis, scale = 'free')
p
```

Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.no.na))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
```{r preadj.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
#CQN.GENE_EXPRESSION$E.no.na <- as.data.frame(CQN.GENE_EXPRESSION$E.no.na)

row.names(METADATA) <- METADATA$SampleID
COVARIATES1 <- COVARIATES[ , (colnames(COVARIATES) %in% 'Tissue') == F]

COVARIATES1[ ,(colnames(COVARIATES1) %in% c('IntragenicRate', 'FlowcellBatch', 'SampID', 'MappedReads', 'AlignmentRate', 'LibraryBatch' )) ==F ]

COVARIATES1$Institution <- as.factor(as.character(COVARIATES1$Institution))
COVARIATES1$Individual_ID <- as.factor(as.character(COVARIATES1$Individual_ID))
#_#COVARIATES1$FlowcellBatch <- as.factor(as.character(COVARIATES1$FlowcellBatch))
COVARIATES1$Reported_Gender <- as.factor(as.character(COVARIATES1$Reported_Gender))
COVARIATES1$Dx.Tissue <- as.factor(as.character(COVARIATES1$Dx.Tissue))
COVARIATES1$RibozeroBatch <- as.factor(as.character(COVARIATES1$RibozeroBatch))
COVARIATES1$LibraryBatch <- as.factor(as.character(COVARIATES1$LibraryBatch))
#COVARIATES1$SampID <- as.factor(as.character(row.names(COVARIATES1)))
COVARIATES1$Ancestry <- as.factor(as.character(METADATA[row.names(COVARIATES1),]$Ethnicity))

preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
                                                 COVARIATES1,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preadj.covariates.plot, cache=FALSE, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Normalisation (iterative design)
Since many covariates are correlated, re-normalising and re-adjusting COUNTS with an iterative design matrix.

NOTE:
1. Using a mixed effect model where random effect is chosen as Individual_ID
2. Adding Source, FLOWCELL and Gender a priori to variable selection
3. Primary variable of interest Tissue.Diagnosis is excluded from the pool of available covariates for selection
```{r iterative.norm, results='asis'}

# Primary variable of interest
postAdjustCovars = c('Institution', 'Reported_Gender') #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
#postAdjustCovars = c('Institution', 'Reported_Gender');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, 'Individual_ID'))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
notEstimable = c()

#COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 496, replace = TRUE, prob = NULL)))

loopCount = 0 
while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
  ##__##COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 496, replace = TRUE, prob = NULL)))
  writeLines(paste0('Working on Loop: ', loopCount))
  writeLines(paste('Using following covariates in the model:',
                   paste(postAdjustCovars, collapse=', '),
                   'as fixed effects and Individual_ID/Institution as random effect'))

  # Post adjusted design matrix
  DM1 = getDesignMatrix(COVARIATES1[,postAdjustCovars,drop=F],Intercept = F)
  DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

  # Estimate voom weights for dispersion control
  cnts = NEW.COUNTS; cnts[is.na(cnts)] = 0
  VOOM.GENE_EXPRESSION = voom(cnts, design=DM1$design, 
                              plot=F, na.rm = T)

  # Calculate correlation values of random effects
  VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E
  correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
                                             block = COVARIATES1$Individual_ID,
                                             ##__##block = COVARIATES1$Individual_ID,
                                             method = 'lmer')
  # correlation = list(); correlation$cor = 0.3819258

  if (!is.nan(correlation$cor)){
    # Re-estimate voom weights
    VOOM.GENE_EXPRESSION = voom(cnts, 
                                design=DM1$design, plot=F, 
                                block = COVARIATES1$Individual_ID,
                                ##__##block = COVARIATES1$Individual_ID,
                                correlation = correlation$cor)

    # Fit linear model using new weights and new design
    VOOM.ADJUSTED.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                              design = DM1$design,
                              weights = VOOM.GENE_EXPRESSION$weights,
                              block = COVARIATES1$Individual_ID, 
                              ##__##block = COVARIATES1$Individual_ID,
                              correlation = correlation$cor)

    # Residuals after normalisation
    RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,
                                                  CQN.GENE_EXPRESSION$E)
  } else {
    notEstimable = c(notEstimable, postAdjustCovars[length(postAdjustCovars)])
    postAdjustCovars = postAdjustCovars[1:(length(postAdjustCovars)-1)]
  }

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates),
                         c(postAdjustCovars, primaryVariable, 'Individual_ID', notEstimable))

  residCovars <- residCovars[ (residCovars == 'Tissue') == F ]

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  expr = RESIDUAL.GENE_EXPRESSION; expr[is.na(expr)] = 0
  #_# no issue with prob genes now
  #residualSigCovars = runPCAandPlotCorrelations(expr[ (row.names(expr) %in% ProbGenes) == F, ], 
                                        #        COVARIATES1[, residCovars, drop=F], 
                                        #        'adjusted design(voom-normalized)',
                                        #        isKeyPlot=TRUE)
  writeLines(paste0('Residule Calc for Loop: ', loopCount))
  residualSigCovars = runPCAandPlotCorrelations(expr,

                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

  # Add postadjusted covariates (if any)
  residCovars = setdiff(residualSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, notEstimable))
  covariatesEffects = residualSigCovars$Effects.significantCovars[residCovars]

  postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects)))
  loopCount = loopCount + 1
}
modelStr <- paste(paste(gsub('_','\\\\_',postAdjustCovars), collapse=', '),
                  'as fixed effects')
tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`

### Sanity check
```{r residual.adj, cache=FALSE, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
residualSigCovars = runPCAandPlotCorrelations(expr, 
                                              COVARIATES1,
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
residualSigCovars[["PC_res"]][[2]]$plotData
```

Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(expr))
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
PCA of residual data
```{r decompse.normalise.data2.1, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(expr, scale.=T, center = T)
# Plot first 4 PCs
plotdata <- data.frame(Individual_ID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
#COVARIATES$SampleID <- COVARIATES$Individual_ID
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'Individual_ID')) %>%
  tidyr::separate(Dx.Tissue, c('Diagnosis','Region'), sep = '\\.') %>% 
  dplyr::mutate(Region = factor(Region),
                Institution = factor(Institution))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=Institution, color=Diagnosis, size=RIN))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(Region~., scales = 'free_y')
p
```
Tree based clustering of residual data
```{r decompse.normalise.data2.2, cache=FALSE, fig.height=8, fig.width=12, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp<-COVARIATES
COVARIATES.tmp$Tissue <- as.character( METADATA[ row.names(COVARIATES.tmp), ]$Tissue )
COVARIATES.tmp$Tissue <- as.factor(COVARIATES.tmp$Tissue)
COVARIATES.tmp = data.matrix( COVARIATES.tmp[,c(FactorCovariates,"Tissue")] )
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(expr)))
COVARIATES.tmp <- COVARIATES.tmp[,2:dim(COVARIATES.tmp)[2]]
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Adjust data with covariates for Network Analysis
Identified covariates are regressed out from the expression matrix for network analysis
```{r network.adjust}
# Get design matrix
DESIGN.NET = getDesignMatrix(COVARIATES[, postAdjustCovars, drop = F], Intercept = F)
DESIGN.NET = DESIGN.NET$design[,linColumnFinder(DESIGN.NET$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.NET.WEIGHTS = voom(cnts, design=DESIGN.NET, plot=F)
# Re-estimate voom weights
VOOM.NET.WEIGHTS = voom(cnts, 
                        design = DESIGN.NET, plot=F,
                        block = COVARIATES$Donor_ID, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.NET.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.NET.FIT = lmFit(VOOM.NET.WEIGHTS$E,
                     weights = VOOM.NET.WEIGHTS$weights,
                     design = VOOM.NET.WEIGHTS$design,
                     block = COVARIATES$Donor_ID, 
                     correlation = correlation$cor)
# Residuals after normalisation
RESIDUAL.NET.GENE_EXPRESSION = residuals.MArrayLM(VOOM.NET.FIT,
                                                  CQN.GENE_EXPRESSION$E)
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (Tissue.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
# remove  "FlowcellBatch",
FactorCovariates <- c("Individual_ID", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
COVARIATES1[,FactorCovariates] = lapply(COVARIATES1[,FactorCovariates], factor)
COVARIATES1[,ContCovariates] = lapply(COVARIATES1[,ContCovariates], as.character)
COVARIATES1[,ContCovariates] = lapply(COVARIATES1[,ContCovariates], as.numeric)

# Get design matrix
DESIGN = getDesignMatrix(COVARIATES1[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)

#_#DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,

                    block = COVARIATES1$Block, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS$E,
            weights = VOOM.WEIGHTS$weights,
            design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
            block = COVARIATES1$Block, 
            correlation = correlation$cor)

# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]
# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$E)
# Compute actual variance of all principal components
expr = RESIDUAL.SVA.GENE_EXPRESSION
expr[is.na(expr)] = 0
tmp = svd(expr)
actual.var = tmp$d^2/sum(tmp$d^2)
# Compute permuted variance of all principal components
permuted.var = foreach(i = 1:20, .combine = rbind) %dopar% {
  tmp.residual = t(apply(expr, 1, sample, replace = FALSE))
  tmp = svd(tmp.residual)
  permuted.var = tmp$d^2/sum(tmp$d^2)
}
permuted.var = apply(permuted.var, 2, mean)
NUM.SV = sum(actual.var >= permuted.var[1])
# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.2)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p
# Estimate surrogate variables
SURR.VAR = irwsva.build(CQN.GENE_EXPRESSION$E.no.na,
                        MODEL1, MODEL0, n.sv = NUM.SV, 
                        B = 30, tol = 1e-20)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(MODEL1)
# Estimate voom weights for dispersion control
VOOM.SVA.WEIGHTS = voom(cnts, design=cbind(MODEL1, SURR.VAR), plot=F)
# Re-estimate voom weights
VOOM.SVA.WEIGHTS = voom(cnts, 
                        design = cbind(MODEL1, SURR.VAR), plot=F,
                        block = COVARIATES1$Block, 
                        correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.SVA.WEIGHTS$E = CQN.GENE_EXPRESSION$E
VOOM.SVA.FIT = lmFit(VOOM.SVA.WEIGHTS$E,
                     weights = VOOM.SVA.WEIGHTS$weights,
                     design = VOOM.SVA.WEIGHTS$design,
                     block = COVARIATES1$Block, 
                     correlation = correlation$cor)
# Residuals after normalisation
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(VOOM.SVA.FIT,
                                                  CQN.GENE_EXPRESSION$E)
# Add variable of interest back to the residuals
varsToAddIn = grep("Tissue.Diagnosis", colnames(MODEL1), value = T)
RESIDUAL.SVA.GENE_EXPRESSION = RESIDUAL.SVA.GENE_EXPRESSION + 
  VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
```

```{r EXP_Val, include=FALSE, eval=TRUE, cache=FALSE}
################################################################################
#CMC ACC DATA
library(stringr)

Associated <- function( Tissue ){
  #'@Tissue either "ACC", or "PFC"

  Impute <-  as.data.frame( read.table(syn_temp$get('syn21442621')$path, header = T, sep = '\t', row.names = 1 ))
  row.names(Impute)  <- Impute$IID
  Impute <- Impute[ , colnames(Impute)[ (grepl("ENSG", colnames(Impute))) == T ] ]
  Impute <- as.data.frame(t(Impute))
  colnames(Impute) <- gsub( "BP_", "", gsub("0_", "CMC_", colnames(Impute) ))

  #Exp--
  Exp <- RESIDUAL.SVA.GENE_EXPRESSION #as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
  rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
  #_# Exp_ACC <- Exp[ ,(grepl("_ACC_", colnames(Exp)))==T ]
  #_# Exp_ACC <- Exp[ ,(grepl("_PFC_", colnames(Exp)))==T ]
  Exp_temp <- Exp[ ,(grepl(paste0("_", Tissue, "_"), colnames(Exp)))==T ]
  #ID--
  ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
  table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )

  #_# colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
  #_# colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
  if( Tissue == 'PFC' ){
    colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
  }else{
    if( Tissue == 'ACC' ){
      colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
    }else{
      warning('Inproper Tissue Specified')
    }
  }
  Exp <- Exp_temp
  #Sync Names
  Padder <- function( names ){
    #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
    foo <- do.call( rbind, strsplit(names, '_'))
    foo[,3] <- str_pad(foo[,3], 5, pad = "0")
    return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
  }
  colnames(Exp) <- Padder( colnames(Exp) )
  colnames(Impute) <- Padder( colnames(Impute) )

  #Align Matices
  Impute <- Impute[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
  Exp <- Exp[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
  Impute <- Impute[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
  Exp <- Exp[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]

  Correlation <- matrix(0, dim(Exp)[1], 3)
  row.names(Correlation) <- row.names(Impute)
  colnames(Correlation) <- c( "Z", "Correlation", "P-Val")

  Exp <- Exp[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
  Impute <- Impute[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]

  for( Gene in row.names(Impute) ){
    temp <- na.omit(cbind( as.numeric(Impute[Gene,]), as.numeric(Exp[Gene,]) ))
    foo <- cor.test( temp[,1], temp[,2] , method = "kendall")
    Correlation[ Gene, ] <- c( as.numeric(foo$statistic), as.numeric(foo$estimate), as.numeric(foo$p.value) )
  }

  Correlation <- cbind( Correlation, "Log10_Pval"= -log10(Correlation[,3]))
  Correlation <- cbind( Correlation, "FDR"= p.adjust( Correlation[,3], method = "fdr", n = 13650) )
  Correlation <- cbind( Correlation, "BH"= p.adjust( Correlation[,3], method = "BH", n = 13650) )
  Correlation <- cbind( Correlation, "BF"= p.adjust( Correlation[,3], method = "bonferroni", n = 13650) )

  Correlation <- cbind( Correlation, "FDR_W_Only"= p.adjust( Correlation[,3], method = "fdr", n = dim(Correlation)[1]) )
  Correlation <- cbind( Correlation, "BH_W_Only"= p.adjust( Correlation[,3], method = "BH", n = dim(Correlation)[1]) )
  Correlation <- cbind( Correlation, "BF_W_Only"= p.adjust( Correlation[,3], method = "bonferroni", n = dim(Correlation)[1]) )

  Correlation <- as.data.frame(Correlation)
  Correlation$Sig <- 'NO'
  Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'
  Tab <- table(Correlation$Sig)

  setEPS()
  postscript( paste0( Tissue, "_Val.eps" ), onefile = TRUE)
    ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
  dev.off()
  Sig <- ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)")

  setEPS()
  postscript(paste0( Tissue, "_Cor_All.eps"), onefile = TRUE)
    hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1, col = 'grey45',
        main="Correlation of All 6643 Matched Genes in CMC ACC")
  dev.off()
  Total_Hist <- hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1, col = 'grey45',
        main="Correlation of All 6643 Matched Genes in CMC ACC")

  setEPS()
  postscript(paste0( Tissue, "_Cor_gt5Perc.eps"), onefile = TRUE)
    hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
        breaks = 100, 
        xlab = 'Correlation',
        col = 'grey45',
        las = 1,
        main="Correlation of Genes with FDR Corrected P-Value < 0.05")
  dev.off()
  Filt_Hist <- hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
        breaks = 100, 
        xlab = 'Correlation',
        col = 'grey45',
        las = 1,
        main="Correlation of Genes with FDR Corrected P-Value < 0.05")
  return(list( TAB=Tab, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
}

ACC_Plots <- Associated( 'ACC' )
PFC_Plots <- Associated( 'PFC' )

```

#### Imputed Expression Component Validation in DLPFC
```{r Plot, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
# Significant after correction for multiple comparisons:
print(PFC_Plots$TAB)

print("Log PValue versus Correlation:")
PFC_Plots$Sig

print("All Correlations:")
plot(PFC_Plots$Tot)

print("Significant Correlations:")
plot(PFC_Plots$Filt)
```

#### Imputed Expression Component Validation in ACC
```{r Plot, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
# Significant after correction for multiple comparisons:
print(ACC_Plots$TAB)

print("Log PValue versus Correlation:")
ACC_Plots$Sig

print("All Correlations:")
plot(ACC_Plots$Tot)

print("Significant Correlations:")
plot(ACC_Plots$Filt)
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'Covariate and Diagnosis Regression';
activityDescription = 'CMC Covariate analysis and Regresison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation';
thisFileName <- 'CMC_Both_Exp_DataProcessing_V2.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'CMC Covariate and Diagnosis Regression';
activityDescription = 'CMC Covariate analysis and Regrssion of Diagnosis of aligned effective counts with GRCh38 with CQN normalisation CMC';
CODE <- syn_temp$store(synapseclient$Folder(name = "CMC_Analysis", parentId = parentId))

#Set Used SynIDs For Provenance
#Syns_Used <- c("")

# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  tissueTypeAbrv	= NULL, 
  study = 'CMC', 
  organism = 'HomoSapiens',
  consortium	= 'CMC',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh38'
)

#TODO add provenance used = Syns_Used,

# Store SVA results
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CMC_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForeQTL'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

#Upload Plots:
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.eps', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_All.eps', name = 'Histogram of all correlation values for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_gt5Perc.eps', name = 'Histogram of Significant correlation values for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'ACC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.eps', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Cor_All.eps', name = 'Histogram of all correlation values for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Cor_gt5Perc.eps', name = 'Histogram of Significant correlation values for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "CMC_ExpVal_DataProcessing.Rmd",
                                          parentId ="syn18936948",
                                          #parentId ="syn21478397",
                                          folderName = 'CMC_Analysis')
```

### 2020-04-30 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

@@
 #### Imputed Expression Component Validation in DLPFC
-```{r Plot, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
+```{r PlotDLPFC, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
 # Significant after correction for multiple comparisons:
@@
 #### Imputed Expression Component Validation in ACC
-```{r Plot, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
+```{r PlotACC, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
 # Significant after correction for multiple comparisons:

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

@@
 activityDescription = 'CMC Covariate analysis and Regresison of AD Diagnosis of aligned effective counts with GRCh38 with CQN normalisation';
-thisFileName <- 'CMC_Both_Exp_DataProcessing_V2.Rmd'
+thisFileName <- 'CMC_ExpVal_DataProcessing.Rmd'
 # Github link

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

@@
   cache = TRUE)
-```
-
-### Problem Genes in the iterative normalization:
-```{r prob.genes, cache=TRUE, include=FALSE}
-
-#ProbGenes <- c("ENSG00000234593", "ENSG00000092847", "ENSG00000232878", "ENSG00000134256", "ENSG00000143393", "ENSG00000162736", "ENSG00000143156", "ENSG00000203737", "ENSG00000232036", "ENSG00000153827","ENSG00000234661", "ENSG00000131370", "ENSG00000281708", "ENSG00000242103", "ENSG00000279311", "ENSG00000249252", "ENSG00000170180", "ENSG00000240083", "ENSG00000249175", "ENSG00000229688", "ENSG00000105953", "ENSG00000146707", "ENSG00000253420", "ENSG00000279608", "ENSG00000232807", "ENSG00000119946", "ENSG00000236991", "ENSG00000177951", "ENSG00000250644", "ENSG00000158077", "ENSG00000110104", "ENSG00000149452", "ENSG00000255345", "ENSG00000254705", "ENSG00000256533", "ENSG00000249028", "ENSG00000285627", "ENSG00000111215", "ENSG00000212128", "ENSG00000066117", "ENSG00000123297", "ENSG00000270048", "ENSG00000251536", "ENSG00000237263", "ENSG00000102796", "ENSG00000258469", "ENSG00000140009", "ENSG00000259370", "ENSG00000137764", "ENSG00000127578", "ENSG00000263072", "ENSG00000261528", "ENSG00000261872", "ENSG00000198453", "ENSG00000189164", "ENSG00000149488", "ENSG00000233993", "ENSG00000100991", "ENSG00000100982", "ENSG00000243646", "ENSG00000239282", "ENSG00000068354", "ENSG00000271356", "ENSG00000241101", "ENSG00000248624", "ENSG00000227017", "ENSG00000240395", "ENSG00000285933", "ENSG00000256064", "ENSG00000177699", "ENSG00000278090", "ENSG00000264529", "ENSG00000243978", "ENSG00000225828", "ENSG00000116525", "ENSG00000225767", "ENSG00000229359", "ENSG00000143257", "ENSG00000143643", "ENSG00000272865", "ENSG00000235760", "ENSG00000227331", "ENSG00000229056", "ENSG00000183977", "ENSG00000239926", "ENSG00000239997", "ENSG00000279349", "ENSG00000229638", "ENSG00000250243", "ENSG00000249212", "ENSG00000250361", "ENSG00000250910", "ENSG00000283355", "ENSG00000251634", "ENSG00000061455", "ENSG00000285605", "ENSG00000285868", "ENSG00000235859", "ENSG00000228735", "ENSG00000205485", "ENSG00000236018", "ENSG00000260721", "ENSG00000169946", "ENSG00000234740", "ENSG00000136925", "ENSG00000237461", "ENSG00000182752", "ENSG00000205696", "ENSG00000285852", "ENSG00000178440", "ENSG00000107819", "ENSG00000131620", "ENSG00000256589", "ENSG00000256682", "ENSG00000213363", "ENSG00000110887", "ENSG00000126216", "ENSG00000258648", "ENSG00000196553", "ENSG00000250130", "ENSG00000259619", "ENSG00000236194", "ENSG00000263089", "ENSG00000235552", "ENSG00000278971", "ENSG00000222460", "ENSG00000235347", "ENSG00000185448", "ENSG00000233204", "ENSG00000184616", "ENSG00000238184", "ENSG00000274322", "ENSG00000235038", "ENSG00000230470", "ENSG00000234601", "ENSG00000277769", "ENSG00000232131", "ENSG00000235631", "ENSG00000272076", "ENSG00000168828", "ENSG00000279822", "ENSG00000235010", "ENSG00000280379", "ENSG00000286067", "ENSG00000279628", "ENSG00000265316", "ENSG00000277829", "ENSG00000223799", "ENSG00000231875", "ENSG00000227232", "ENSG00000160679", "ENSG00000236440", "ENSG00000206341", "ENSG00000138071", "ENSG00000131507", "ENSG00000179151", "ENSG00000263326", "ENSG00000109111", "ENSG00000166317", "ENSG00000219433" )
-
-#fooOld <- c('ENSG00000227232', 'ENSG00000248527', 'ENSG00000285812', 'ENSG00000272455', 'ENSG00000215915', 'ENSG00000269737', 'ENSG00000157911', 'ENSG00000226029', 'ENSG00000121775', 'ENSG00000225828', 'ENSG00000116525', 'ENSG00000197982', 'ENSG00000285728', 'ENSG00000225767', 'ENSG00000229359', 'ENSG00000270629', 'ENSG00000160679', 'ENSG00000177954', 'ENSG00000227741', 'ENSG00000143257', 'ENSG00000236535', 'ENSG00000118194', 'ENSG00000143862', 'ENSG00000240219', 'ENSG00000123838', 'ENSG00000272645', 'ENSG00000143643', 'ENSG00000223694', 'ENSG00000272865', 'ENSG00000286216', 'ENSG00000179270', 'ENSG00000235760', 'ENSG00000144031', 'ENSG00000115282', 'ENSG00000232931', 'ENSG00000236440', 'ENSG00000227331', 'ENSG00000272211', 'ENSG00000229056', 'ENSG00000144410', 'ENSG00000144452', 'ENSG00000152056', 'ENSG00000183977', 'ENSG00000230409', 'ENSG00000172940', 'ENSG00000232354', 'ENSG00000281691', 'ENSG00000162267', 'ENSG00000189283', 'ENSG00000239926', 'ENSG00000239997', 'ENSG00000279349', 'ENSG00000285943', 'ENSG00000241278', 'ENSG00000240695', 'ENSG00000114113', 'ENSG00000240875', 'ENSG00000206120', 'ENSG00000229638', 'ENSG00000225473', 'ENSG00000230732', 'ENSG00000242686', 'ENSG00000249592', 'ENSG00000013810', 'ENSG00000284727', 'ENSG00000249212', 'ENSG00000251022', 'ENSG00000250361', 'ENSG00000250910', 'ENSG00000164105', 'ENSG00000283355', 'ENSG00000261360', 'ENSG00000274441', 'ENSG00000152669', 'ENSG00000205571', 'ENSG00000251634', 'ENSG00000171530', 'ENSG00000061455', 'ENSG00000164406', 'ENSG00000285605', 'ENSG00000241112', 'ENSG00000285868', 'ENSG00000241956', 'ENSG00000124588', 'ENSG00000189134', 'ENSG00000206341', 'ENSG00000204227', 'ENSG00000156639', 'ENSG00000272137', 'ENSG00000146242', 'ENSG00000255330', 'ENSG00000118514', 'ENSG00000146576', 'ENSG00000235859', 'ENSG00000183696', 'ENSG00000228735', 'ENSG00000234500', 'ENSG00000274080', 'ENSG00000205485', 'ENSG00000121716', 'ENSG00000271664', 'ENSG00000260555', 'ENSG00000236018', 'ENSG00000260721', 'ENSG00000249258', 'ENSG00000158815', 'ENSG00000197181', 'ENSG00000253200', 'ENSG00000134013', 'ENSG00000250979', 'ENSG00000253948', 'ENSG00000169946', 'ENSG00000253372', 'ENSG00000104529', 'ENSG00000234740', 'ENSG00000164970', 'ENSG00000237159', 'ENSG00000274026', 'ENSG00000136925', 'ENSG00000237461', 'ENSG00000196739', 'ENSG00000182752', 'ENSG00000286196', 'ENSG00000234771', 'ENSG00000280474', 'ENSG00000214402', 'ENSG00000197070', 'ENSG00000205696', 'ENSG00000285852', 'ENSG00000285737', 'ENSG00000188234', 'ENSG00000204172', 'ENSG00000178440', 'ENSG00000166343', 'ENSG00000229990', 'ENSG00000236552', 'ENSG00000155287', 'ENSG00000107819', 'ENSG00000273521', 'ENSG00000203772', 'ENSG00000177595', 'ENSG00000117983', 'ENSG00000247595', 'ENSG00000254622', 'ENSG00000162236', 'ENSG00000213465', 'ENSG00000110025', 'ENSG00000131620', 'ENSG00000241170', 'ENSG00000186174', 'ENSG00000186166', 'ENSG00000240970', 'ENSG00000254428', 'ENSG00000254909', 'ENSG00000110811', 'ENSG00000111664', 'ENSG00000111678', 'ENSG00000205885', 'ENSG00000256589', 'ENSG00000256682', 'ENSG00000247903', 'ENSG00000257433', 'ENSG00000139631', 'ENSG00000185482', 'ENSG00000123329', 'ENSG00000166987', 'ENSG00000178498', 'ENSG00000224713', 'ENSG00000213363', 'ENSG00000110887', 'ENSG00000257097', 'ENSG00000251497', 'ENSG00000279500', 'ENSG00000279283', 'ENSG00000198553', 'ENSG00000043355', 'ENSG00000126216', 'ENSG00000233695', 'ENSG00000258515', 'ENSG00000270433', 'ENSG00000276698', 'ENSG00000257986', 'ENSG00000258648', 'ENSG00000258682', 'ENSG00000196553', 'ENSG00000100632', 'ENSG00000258376', 'ENSG00000258891', 'ENSG00000183648', 'ENSG00000202191', 'ENSG00000223403', 'ENSG00000246451', 'ENSG00000201992', 'ENSG00000215252', 'ENSG00000243789', 'ENSG00000242866', 'ENSG00000250130', 'ENSG00000259619', 'ENSG00000247982', 'ENSG00000255346', 'ENSG00000246877', 'ENSG00000169752', 'ENSG00000274376', 'ENSG00000255769', 'ENSG00000249487', 'ENSG00000261505', 'ENSG00000261123', 'ENSG00000259895', 'ENSG00000279520', 'ENSG00000262312', 'ENSG00000188897', 'ENSG00000243716', 'ENSG00000166851', 'ENSG00000224310')
-
- #tmp<-c(              'ENSG00000262155', 'ENSG00000260853', 'ENSG00000279789', 'ENSG00000156858', 'ENSG00000261439', 'ENSG00000089505', 'ENSG00000280334', 'ENSG00000280214', 'ENSG00000196436', 'ENSG00000140905', 'ENSG00000280182', 'ENSG00000226180', 'ENSG00000224888', 'ENSG00000170296', 'ENSG00000263934', 'ENSG00000266385', 'ENSG00000073605', 'ENSG00000236194', 'ENSG00000266967', 'ENSG00000262265', 'ENSG00000121104', 'ENSG00000243678', 'ENSG00000263089', 'ENSG00000263499', 'ENSG00000213246', 'ENSG00000172809', 'ENSG00000279382', 'ENSG00000262580', 'ENSG00000235552', 'ENSG00000263847', 'ENSG00000278983', 'ENSG00000278971', 'ENSG00000273218', 'ENSG00000268189', 'ENSG00000279203', 'ENSG00000279716', 'ENSG00000280332', 'ENSG00000267419', 'ENSG00000105185', 'ENSG00000239382', 'ENSG00000267053', 'ENSG00000233527', 'ENSG00000267254', 'ENSG00000171777', 'ENSG00000105221', 'ENSG00000268460', 'ENSG00000063177', 'ENSG00000104852', 'ENSG00000074219', 'ENSG00000167608', 'ENSG00000267838', 'ENSG00000177732', 'ENSG00000088832', 'ENSG00000131044', 'ENSG00000101421', 'ENSG00000222460', 'ENSG00000183798', 'ENSG00000101104', 'ENSG00000124172', 'ENSG00000286018', 'ENSG00000160224', 'ENSG00000223901', 'ENSG00000239415', 'ENSG00000234409', 'ENSG00000250479', 'ENSG00000279738', 'ENSG00000205702', 'ENSG00000226450', 'ENSG00000182841', 'ENSG00000279175', 'ENSG00000280434', 'ENSG00000235347', 'ENSG00000170638', 'ENSG00000185448', 'ENSG00000271199', 'ENSG00000198960', 'ENSG00000286000', 'ENSG00000241489', 'ENSG00000213397', 'ENSG00000198938', 'ENSG00000137970', 'ENSG00000230470', 'ENSG00000234781', 'ENSG00000233204', 'ENSG00000214389', 'ENSG00000235631', 'ENSG00000280379', 'ENSG00000279628', 'ENSG00000276663', 'ENSG00000263551', 'ENSG00000265316', 'ENSG00000231875', 'ENSG00000235790', 'ENSG00000242516', 'ENSG00000272040', 'ENSG00000250472', 'ENSG00000281706', 'ENSG00000184616', 'ENSG00000285581', 'ENSG00000238184', 'ENSG00000258136', 'ENSG00000136378', 'ENSG00000140682', 'ENSG00000279251', 'ENSG00000108375', 'ENSG00000279917', 'ENSG00000269318', 'ENSG00000270804', 'ENSG00000274322', 'ENSG00000235958', 'ENSG00000235038', 'ENSG00000228686', 'ENSG00000058673', 'ENSG00000234601', 'ENSG00000236549', 'ENSG00000091181', 'ENSG00000145020', 'ENSG00000248734', 'ENSG00000277769', 'ENSG00000146285', 'ENSG00000232131', 'ENSG00000228495', 'ENSG00000231760', 'ENSG00000272076', 'ENSG00000168828', 'ENSG00000279822', 'ENSG00000235010', 'ENSG00000250397', 'ENSG00000255159', 'ENSG00000258102', 'ENSG00000286067', 'ENSG00000274317', 'ENSG00000180662', 'ENSG00000259499', 'ENSG00000261207', 'ENSG00000175311', 'ENSG00000260751', 'ENSG00000261291', 'ENSG00000278668', 'ENSG00000266598', 'ENSG00000280248', 'ENSG00000276952', 'ENSG00000277829', 'ENSG00000223799', 'ENSG00000213790', 'ENSG00000271916', 'ENSG00000249863', 'ENSG00000267655', 'ENSG00000133872', 'ENSG00000224689','ENSG00000255389', 'ENSG00000253230', 'ENSG00000247137', 'ENSG00000170906', 'ENSG00000182195' )
-
- #ProbGenes <- c(ProbGenes,tmp)
 ```

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

@@
   setEPS()
-  postscript( paste0( Tissue, "_Val.eps" ), onefile = TRUE)
-    ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
+  #postscript( paste0( Tissue, "_Val.eps" ), onefile = TRUE)
+    #ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
+      #geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
+      #theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
+  #dev.off()
+
+  ggsave( filename=Tissue, "_Val.eps",
+    plot = ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
       geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
-      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
-  dev.off()
+      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") ,
+    device = "pdf",
+    path = NULL,
+    scale = 1,
+    width = 14,
+    height = 7,
+    units = "in",
+    dpi = 300,
+    limitsize = TRUE
+  )
+
   Sig <- ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

@@
   rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
-  #_# Exp_ACC <- Exp[ ,(grepl("_ACC_", colnames(Exp)))==T ]
-  #_# Exp_ACC <- Exp[ ,(grepl("_PFC_", colnames(Exp)))==T ]
   Exp_temp <- Exp[ ,(grepl(paste0("_", Tissue, "_"), colnames(Exp)))==T ]
@@
 
-  #_# colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
-  #_# colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
   if( Tissue == 'PFC' ){
@@
 
-  setEPS()
-  #postscript( paste0( Tissue, "_Val.eps" ), onefile = TRUE)
-    #ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
-      #geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
-      #theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
-  #dev.off()
-
-  ggsave( filename=Tissue, "_Val.eps",
+  ggsave( filename=paste0( Tissue, "_Val.pdf" ),
     plot = ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
@@
 #Upload Plots:
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.eps', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.pdf', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'ACC'
@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.eps', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.pdf', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'DLPFC'

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

@@
     scale = 1,
-    width = 14,
+    width = 21,
     height = 7,

### 2020-05-04 code/CMC_ExpVal_DataProcessing.Rmd
Validation

@@
 # Primary variable of interest
-postAdjustCovars = c('Institution', 'Reported_Gender') #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
+postAdjustCovars = c('Institution', 'Reported_Gender', 'Dx' ) #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
 #postAdjustCovars = c('Institution', 'Reported_Gender');
@@
 
+  message( paste0(Tissue, ' Mean Correlatioon: ', mean(Correlation$Correlation)) )
+  message( paste0(Tissue, ' Mean Std. Dev: ', sd(Correlation$Correlation)) )
+
   ggsave( filename=paste0( Tissue, "_Val.pdf" ),
@@
     scale = 1,
-    width = 21,
-    height = 7,
+    width = 25,
+    height = 8.75,
     units = "in",
@@
 
+#### Down Sample the DLPFC to look like ACC
+```{r DownSample, cache=FALSE, fig.height=10, fig.width=8, results='asis'}
+Tissue <- 'PFC'
+
+Impute <-  as.data.frame( read.table(syn_temp$get('syn21442621')$path, header = T, sep = '\t', row.names = 1 ))
+row.names(Impute)  <- Impute$IID
+Impute <- Impute[ , colnames(Impute)[ (grepl("ENSG", colnames(Impute))) == T ] ]
+Impute <- as.data.frame(t(Impute))
+colnames(Impute) <- gsub( "BP_", "", gsub("0_", "CMC_", colnames(Impute) ))
+
+#Exp--
+Exp <- RESIDUAL.SVA.GENE_EXPRESSION #as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
+rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
+Exp_temp <- Exp[ ,(grepl(paste0("_", Tissue, "_"), colnames(Exp)))==T ]
+#ID--
+ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
+table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )
+
+if( Tissue == 'PFC' ){
+  colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
+}else{
+  if( Tissue == 'ACC' ){
+    colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
+  }else{
+    warning('Inproper Tissue Specified')
+  }
+}
+Exp <- Exp_temp
+#Sync Names
+Padder <- function( names ){
+  #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
+  foo <- do.call( rbind, strsplit(names, '_'))
+  foo[,3] <- str_pad(foo[,3], 5, pad = "0")
+  return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
+}
+colnames(Exp) <- Padder( colnames(Exp) )
+colnames(Impute) <- Padder( colnames(Impute) )
+
+#Align Matices
+Impute <- Impute[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
+Exp <- Exp[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
+Impute <- Impute[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
+Exp <- Exp[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
+
+Perm <- function( Exp, Impute ){  
+  Template <- colnames(Exp)[ colnames(Exp) %in% colnames(Impute) ]
+  SAMP <- sample(Template, 381, replace = FALSE, prob = NULL)
+  Impute <- Impute[ , SAMP ]
+  Exp <- Exp[ , SAMP ]
+
+  Correlation <- matrix(0, dim(Exp)[1], 3)
+  row.names(Correlation) <- row.names(Impute)
+  colnames(Correlation) <- c( "Z", "Correlation", "P-Val")
+
+  Exp <- Exp[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
+  Impute <- Impute[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
+
+  for( Gene in row.names(Impute) ){
+    temp <- na.omit(cbind( as.numeric(Impute[Gene,]), as.numeric(Exp[Gene,]) ))
+    foo <- cor.test( temp[,1], temp[,2] , method = "kendall")
+    Correlation[ Gene, ] <- c( as.numeric(foo$statistic), as.numeric(foo$estimate), as.numeric(foo$p.value) )
+  }
+
+  Correlation <- cbind( Correlation, "Log10_Pval"= -log10(Correlation[,3]))
+  Correlation <- cbind( Correlation, "FDR"= p.adjust( Correlation[,3], method = "fdr", n = 13650) )
+  Correlation <- cbind( Correlation, "BH"= p.adjust( Correlation[,3], method = "BH", n = 13650) )
+  Correlation <- cbind( Correlation, "BF"= p.adjust( Correlation[,3], method = "bonferroni", n = 13650) )
+
+  Correlation <- cbind( Correlation, "FDR_W_Only"= p.adjust( Correlation[,3], method = "fdr", n = dim(Correlation)[1]) )
+  Correlation <- cbind( Correlation, "BH_W_Only"= p.adjust( Correlation[,3], method = "BH", n = dim(Correlation)[1]) )
+  Correlation <- cbind( Correlation, "BF_W_Only"= p.adjust( Correlation[,3], method = "bonferroni", n = dim(Correlation)[1]) )
+
+  Correlation <- as.data.frame(Correlation)
+  Correlation$Sig <- 'NO'
+  Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'
+  Tab <- table(Correlation$Sig)
+  return( t(as.data.frame(Tab))['Freq',] )
+}
+
+set.seed(42)
+P <- 100
+temp <- foreach( i=1:P ) %dopar% Perm( Exp, Impute )
+Ps <- do.call( rbind, temp )
+Ps <- as.data.frame( Ps )
+Ps$V1 <- as.numeric(as.character(Ps$V1))
+Ps$V2 <- as.numeric(as.character(Ps$V2))
+
+MEAN <- mean( Ps[ , 2 ]/(  Ps[ , 2 ] +  Ps[ , 1 ]) )
+print( paste0('Mean Downsampled Validation: ', MEAN ))
+SD <- sd( Ps[ , 2 ]/(  Ps[ , 2 ] +  Ps[ , 1 ]))
+error <- qt(0.975, df=dim(Ps)[1]-1)*sd( Ps[ , 2 ]/(  Ps[ , 2 ] +  Ps[ , 1 ]) )/sqrt( dim(Ps)[1] )
+
+```
+
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
@@
 #Set Used SynIDs For Provenance
-#Syns_Used <- c("")
+Syns_Used <- c('syn21444814', 'syn21442621', 'syn16816490', 'syn16816488', 'syn21156161', 'syn16783596', 'syn16783867', 'syn2511399', 'syn16783557','syn16783508', 'syn16783557' )
 
@@
 
-#TODO add provenance used = Syns_Used,
-
 # Store SVA results
 write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'CMC_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
   write.table(file = 'CMC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='CMC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 #Upload Plots:
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.pdf', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Val.pdf', name = 'LogP value as a function of correlation for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'ACC'
@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_All.eps', name = 'Histogram of all correlation values for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_All.eps', name = 'Histogram of all correlation values for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'ACC'
@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_gt5Perc.eps', name = 'Histogram of Significant correlation values for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ACC_Cor_gt5Perc.eps', name = 'Histogram of Significant correlation values for ACC', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'ACC'
@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.pdf', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Val.pdf', name = 'LogP value as a function of correlation for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'DLPFC'
@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Cor_All.eps', name = 'Histogram of all correlation values for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Cor_All.eps', name = 'Histogram of all correlation values for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'DLPFC'
@@
 
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Cor_gt5Perc.eps', name = 'Histogram of Significant correlation values for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='PFC_Cor_gt5Perc.eps', name = 'Histogram of Significant correlation values for DLPFC', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
   all.annotations$tissueTypeAbrv = 'DLPFC'

### 2020-05-07 code/CMC_ExpVal_DataProcessing.Rmd
Update validationcode

@@
 
-                    block = COVARIATES1$Block, 
+                    block = COVARIATES1$Individual_ID, 
                     correlation = correlation$cor)
@@
             design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
-            block = COVARIATES1$Block, 
+            block = COVARIATES1$Individual_ID, 
             correlation = correlation$cor)
@@
                         design = cbind(MODEL1, SURR.VAR), plot=F,
-                        block = COVARIATES1$Block, 
+                        block = COVARIATES1$Individual_ID, 
                         correlation = correlation$cor)
@@
                      design = VOOM.SVA.WEIGHTS$design,
-                     block = COVARIATES1$Block, 
+                     block = COVARIATES1$Individual_ID, 
                      correlation = correlation$cor)
@@
 ################################################################################
+
 #CMC ACC DATA
@@
         main="Correlation of Genes with FDR Corrected P-Value < 0.05")
-  return(list( TAB=Tab, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
+  return(list( TAB=Tab, Correlation=Correlation, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
 }
@@
 PFC_Plots <- Associated( 'PFC' )
-
+#save.image('Completed_Validation_Analysis.RData')
 ```
@@
 
+#ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Completed_Validation_Analysis.RData', name = 'RData object of analysis for ACC Validation', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
+#  all.annotations$tissueTypeAbrv = 'Analysis'
+#  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
 ```

### 2020-05-11 code/GeneSet_Expansion.Rmd
ReDo GeneSet enrichment

@@
 library(reshape2)
+library(biomaRt)
+library(data.table)
 
@@
 ```
+
+```{r Selected, echo=FALSE}
+#Average the partial correlation statistics across the data  frames
+
+GENEs <- NULL
+for( tissue in names(Partials$TREM2) ){
+  GENEs <- eval(parse( text=paste0('c(GENEs, colnames(Partials$TREM2$',tissue,'))') ))
+  GENEs <- GENEs[ !duplicated(GENEs) ]
+}
+
+GENEs <- GENEs[ GENEs != 'SeedGene' ]
+ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = 'ensembl.org')
+ensembl <- useDataset('hsapiens_gene_ensembl', mart = ensembl)
+
+Top50_Cor <- function( ENSG, Targets, Tissues, Part, ensembl ){
+  #'@ENSG the target gene ID to collect partials on eg. 'ENSG00000095970'
+  #'@Targets a vector of ENSG names to scan eg. GENEs
+  #'@Tissues charater vector of tissues to scan eg. c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  )
+  #'@Part a partial correlation list  eg. Partials$TREM2
+  #'@ensembl ensembl object eg. ensembl
+
+  Examine <- matrix( NA, length(Targets), length(Tissues)+1 )
+  Examine <- apply(Examine, 2, as.numeric)
+  row.names(Examine) <- Targets
+  colnames(Examine) <- c( Tissues, "Avg" )
+
+  for( Tis in Tissues ){
+    eval(parse( text= paste0( 'Examine[ colnames(Part$\'', Tis,'\')[ colnames(Part$\'', Tis,'\') !=\'SeedGene\' ],\'', Tis, '\' ]  <- as.numeric( Part$\'', Tis, '\'[ Part$\'', Tis,'\'[ ,\'SeedGene\'] == \'', ENSG, '\' , colnames(Part$\'', Tis,'\') != \'SeedGene\' ])' ) ))
+  }
+
+  Examine[, 'Avg' ] <- apply( Examine[ , 1:(dim(Examine)[2]-1) ], 1, mean )
+  Examine <- Examine[ order(-Examine[,'Avg']), ]
+
+  #message(paste0("1"))  
+  #ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = 'ensembl.org')
+  #message(paste0("2"))
+  #ensembl <- useDataset('hsapiens_gene_ensembl', mart = ensembl)
+  #message(paste0("3"))
+  gene_ids <- row.names( Examine )[1:50]
+
+  attrs <- c("ensembl_gene_id", "hgnc_symbol")
+  Trans <- getBM(filters = 'ensembl_gene_id',
+                            attributes = attrs,
+                            values = gene_ids,
+                            mart = ensembl )
+
+  return( Trans$hgnc_symbol[ Trans$hgnc_symbol != "" ] )
+}
+
+Top50 <- list()
+Top50$Trem <- Top50_Cor( 'ENSG00000095970', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$TREM2, ensembl )
+Top50$CD2AP <- Top50_Cor( 'ENSG00000198087', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$CD2AP, ensembl )
+Top50$MTCH2 <- Top50_Cor( 'ENSG00000109919', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$MTCH2, ensembl )
+Top50$EED <- Top50_Cor( 'ENSG00000074266', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$EED, ensembl )
+Top50$KNOP1 <- Top50_Cor( 'ENSG00000103550', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$KNOP1, ensembl )
+Top50$APOC1 <- Top50_Cor( 'ENSG00000130208', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$APOC1, ensembl )
+Top50$CEACAM19 <- Top50_Cor( 'ENSG00000186567', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$CEACAM19 , ensembl )
+Top50$CLPTM1 <- Top50_Cor( 'ENSG00000104853', GENEs, c( "FP", "TCX", "DLPFC", "IFG", "PHG", "STG"  ), Partials$CLPTM1, ensembl )
+```
+
+```{r SIF_Load, echo=FALSE}
+reticulate::use_python("/usr/bin/python", required = TRUE)
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login( )
+
+SIFs <- c('syn21914055')
+names(SIFs) <- c('All')
+
+#Load and Add names: SIFs
+boot <- function( i ){
+  foo <- read.table( file=syn_temp$get( SIFs[i] )$path , header = F, sep='\t' )
+  foo$Pathway <- as.character( i ) 
+  return(foo)
+}
+
+Loader <- function( SIFs){
+  #'@SIFs An object that has SynID values and named for the database
+  ##  Each Syn ID is a SIF format file
+
+  total <- list()
+  Trial <- for( i in names(SIFs) ){
+    temp <- boot( i )
+    #eval(parse(text=paste0( 'total$', as.character(NAMES[i]), ' <- temp' )))
+    total[[i]] <- temp
+  }
+
+  Total <- do.call(rbind, total)
+  Total <- Total[ , c("V1", "V3", "V2", "Pathway") ]
+  colnames(Total) <- c("from", "to", "interaction", "pathway")
+
+  #Caluclate how many times this intereactcion was found in all databases:
+  Total$Occurance <- paste0( Total$from, '-', Total$to, ':', Total$interaction )
+  foo <- paste0( Total$from, '-', Total$to, ':', Total$interaction )
+  TabFoo <- table(foo)
+  Total$Occurance <-  as.numeric( TabFoo[ Total$Occurance ] )
+
+  Genes <- c( as.character(Total$from), as.character(Total$to) )
+  Genes <- Genes[ !duplicated(Genes) ]
+  Genes <- as.data.frame( Genes )
+
+  #Make the pathway column into a list object
+  #library(dplyr)
+  #library(reshape)
+
+  Total$UniqCol <- paste0( as.character(Total$from),':', as.character(Total$to),'-', as.character(Total$interaction) )
+  dt <- data.table(Total[, c('UniqCol','pathway')])
+  DT <- dt[,lapply(.SD, function(col) paste(col, collapse=", ")), by=.(UniqCol)]
+
+  sinl<-DT
+
+  foo <- as.data.frame( DT )
+  poo <- as.list( strsplit(as.character(foo$pathway),',') )
+  names(poo) <- foo$UniqCol
+
+  totals <- Total[ !duplicated(Total$UniqCol), ]
+  pathways <- poo
+
+  table(names(pathways) == as.character(totals$UniqCol))
+  table( as.character(totals$UniqCol) == names(pathways) )
+
+  totals$PATH <- pathways
+  totals$PATH <- lapply( totals$PATH,
+                 function(x) gsub(" ","", x)
+               )
+
+  Total <- totals[,c("from", "to", "interaction", "Occurance", "UniqCol", "PATH")]
+  colnames(Total) <- c("from", "to", "interaction", "Occurance", "UniqCol", "pathway")
+  return( Total )
+}
+
+Total <- Loader(SIFs)
+Total$from <- as.character(Total$from)
+Total$to <- as.character(Total$to)
+Total$UniqCol <- as.character(Total$UniqCol)
+dim(Total)
+table(table( Total$UniqCol ))
+#Filter out the :CHEBI
+Total <- Total[ (grepl( ':CHEBI', Total$UniqCol) == F) , ]
+
+#Remove Repeat interactions?
+Total$Partners <- paste0(Total$from, ":", Total$to )
+Total <- Total[ !duplicated(Total$Partners), ]
+
+```
+
+```{r SIF_Expand, echo=FALSE}
+Expand_gt1 <- list()
+Expand_gt2 <- list()
+
+#Convert Brain Expressed to Gene names
+ensembl = useEnsembl(biomart = "ensembl", dataset = "hsapiens_gene_ensembl" )
+GENEsyb <- getBM(attributes = c('hgnc_symbol'), 
+      filters = 'ensembl_gene_id', 
+      values = GENEs, 
+      mart = ensembl)
+
+for( nam in names(Top50) ){
+  genes <- eval(parse(text=paste0( 'Top50$', nam )))
+  Exp <- c( Total[ Total$from %in% genes | Total$to %in% genes, ]$from, 
+            Total[ Total$from %in% genes | Total$to %in% genes, ]$to
+          )
+
+  #Filt out molecule intereactions and split into conservative and non conservative
+  gt1 <- names( table(Exp)[ table(Exp) > 1 ] )
+  gt1 <- gt1[ grepl( 'CHEBI:', gt1) == F ]
+  gt2 <- names( table(Exp)[ table(Exp) > 2 ] )
+  gt2 <- gt2[ grepl( 'CHEBI:', gt2) == F ]
+
+  #Filt for brain expressed Genese
+  eval(parse(text=paste0( 'Expand_gt1$', nam, ' = gt1[ gt1 %in% GENEsyb[,\'hgnc_symbol\'] ] ' )))
+  eval(parse(text=paste0( 'Expand_gt2$', nam, ' = gt2[ gt2 %in% GENEsyb[,\'hgnc_symbol\'] ] ' )))
+}
+
+library( clusterProfiler )
+library(enrichplot)
+library(enrichR)
+library(org.Hs.eg.db)
+
+parentId = 'syn18936948';
+activityName = 'Gene Set Enrichment';
+activityDescription = 'Figure 4 & Supplement: gene set enrichment of genes implicated in TWAS regions';
+thisFileName <- 'GeneSet_Expansion.Rmd'
+# Github link
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+
+CODE <- syn_temp$store(synapseclient$Folder(name = "Gene Set Enrichment Plots", parentId = parentId))
+
+for( name in names(Expand_gt2)){
+  eval(parse(text=paste0('set <- Expand_gt2$', 'name' )))
+  ego <- enrichGO(gene            = set,
+                    universe      = GENEsyb[,'hgnc_symbol'],
+                    OrgDb         = org.Hs.eg.db,
+                    keyType      = 'SYMBOL',
+                    ont           = "ALL",
+                    pAdjustMethod = "BH",
+                    pvalueCutoff  = 0.01,
+                    qvalueCutoff  = 0.05
+                  )
+
+  clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)
+  cnetplot(ego, foldChange=NULL)
+
+  Dot <- clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)
+  Net <- cnetplot(ego, foldChange=NULL)
+
+  pdf(file = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), width = 14, height = 7)
+    print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+  dev.off()
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), name = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 2 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+  pdf(file = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), width = 14, height = 7)
+    print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+  dev.off()
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), name = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 2 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+}
+
+for( name in names(Expand_gt1)){
+  eval(parse(text=paste0('set <- Expand_gt1$', 'name' )))
+  ego <- enrichGO(gene            = set,
+                    universe      = GENEsyb[,'hgnc_symbol'],
+                    OrgDb         = org.Hs.eg.db,
+                    keyType      = 'SYMBOL',
+                    ont           = "ALL",
+                    pAdjustMethod = "BH",
+                    pvalueCutoff  = 0.01,
+                    qvalueCutoff  = 0.05
+                  )
+
+  clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)
+  cnetplot(ego, foldChange=NULL)
+
+  Dot <- clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)
+  Net <- cnetplot(ego, foldChange=NULL)
+
+  pdf(file = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), width = 14, height = 7)
+    print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+  dev.off()
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), name = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 1 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+  pdf(file = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), width = 14, height = 7)
+    print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+  dev.off()
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), name = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 1 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+
+}
+
+```
+
+##### Deprecated:
 ```{r SDcutOff }
@@
 library(enrichplot)
+library(enrichR)
 

### 2020-05-12 code/GeneSet_Expansion.Rmd
ReDo GeneSet enrichment

@@
 for( name in names(Expand_gt2)){
-  eval(parse(text=paste0('set <- Expand_gt2$', 'name' )))
+  eval(parse(text=paste0('set <- Expand_gt2$', name )))
   ego <- enrichGO(gene            = set,
@@
 for( name in names(Expand_gt1)){
-  eval(parse(text=paste0('set <- Expand_gt1$', 'name' )))
+  eval(parse(text=paste0('set <- Expand_gt1$', name )))
   ego <- enrichGO(gene            = set,

### 2020-05-14 code/GeneSet_Expansion.Rmd
ReDo GeneSet enrichment

@@
   dev.off()
-  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), name = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 2 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), name = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 2 times"), parentId=CODE$properties$id ), activityName = activityName, executed = as.character(c(ExpressionDS,thisFile)), activityDescription = activityDescription)
 
   pdf(file = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), width = 14, height = 7)
-    print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+    print( cnetplot(ego, foldChange=NULL) )
   dev.off()
-  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), name = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 2 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt2.pdf"), name = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 2 times"), parentId=CODE$properties$id ), activityName = activityName, executed = as.character(c(ExpressionDS,thisFile)), activityDescription = activityDescription)
 }
@@
   dev.off()
-  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), name = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 1 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), name = paste0("EnrichmentDotPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 1 times"), parentId=CODE$properties$id ), activityName = activityName, executed = as.character(c(ExpressionDS,thisFile)), activityDescription = activityDescription)
 
   pdf(file = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), width = 14, height = 7)
-    print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
+   print( cnetplot(ego, foldChange=NULL) )
   dev.off()
-  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), name = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 1 times"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_gt1.pdf"), name = paste0("EnrichmentNetPlot_", name, "_GeneSetSize_", length(set),"_Gene apperars gt 1 times"), parentId=CODE$properties$id ), activityName = activityName, executed = as.character(c(ExpressionDS,thisFile)), activityDescription = activityDescription)
 
@@
 ```
-
-##### Deprecated:
-```{r SDcutOff }
-library(doParallel)
-library(parallel)
-
-#Core Correlation:
-Narrow <- list()
-
-#Filter out un-named genes:
-for( Gene in names(Candidates)){
-  eval(parse(text=paste0( 'Candidates$', Gene, ' <- Candidates$', Gene, '[ (Candidates$', Gene, '$hgnc_symbol == \'\' )==F, ]' )))
-}
-
-Trans  <- c("ENSG00000095970", "ENSG00000198087", "ENSG00000109919", "ENSG00000074266", "ENSG00000130208", "ENSG00000103550", "ENSG00000186567", "ENSG00000104853")
-names(Trans) <- c("TREM2", "CD2AP", "MTCH2", "EED", "APOC1", 'KNOP1', "CEACAM19", "CLPTM1")
-
-#Find Partials to Nominated Target gene:
-##Filter out un-named genes (Wont work in Enrichr):
-for( Gene in names(Candidates) ){
-  for( Tissue in names(Study) ){
-    eval(parse(text=paste0( 'Candidates$', Gene, '$', Tissue, ' <- NA')))
-    eval(parse(text=paste0( 'row.names( Candidates$', Gene, ') <- Candidates$', Gene, '$ensembl_gene_id')))
-
-    for( G in eval(parse(text=paste0( 'Candidates$', Gene, '$ensembl_gene_id' ))) ){
-      #[\'', G ,'\' ]
-
-      eval(parse(text=paste0( 'Temp <- Partials$', Gene , '$', Tissue, '[ Partials$', Gene , '$', Tissue, '[,\'SeedGene\'] == \'', Trans[Gene],'\',]' )))
-      if( (G %in% names( Temp ))==TRUE){
-        eval(parse(text=paste0( 'Candidates$', Gene, '[ \'',G,'\',\'', Tissue, '\'] <- as.numeric(Temp[\'',G,'\'])' )))
-      }else{}
-
-    }
-  }
-}
-
-#Average Partial Correlation to Nominated Target accross the 6 tissues
-for( Gene in names(Candidates) ){
-  eval(parse(text=paste0( 'Candidates$', Gene,'$MEAN <- apply( Candidates$', Gene,'[,c(\'DLPFC\', \'TCX\', \'FP\', \'IFG\', \'PHG\', \'STG\')], 1, mean)')))
-}
-
-for( Gene in names(Partials)){
-  eval(parse(text=paste0( 'Narrow$', Gene, ' <- vector()' )))
-  #OK#_eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.01, ]' )))
-
-  #OK#_eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.004, ]' )))
-  eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.1, ]' )))
-  #eval(parse(text=paste0( 'Keepz <- Candidates$', Gene, '[ Candidates$', Gene, '$MEAN > 0.002, ]' )))
-  Keepz <- Keepz[ complete.cases(Keepz),]
-  Keeps <- Keepz$ensembl_gene_id
-
-  for(Tissue in names( ExpressionDS ) ){
-    eval(parse(text=paste0( 'Tarz <- colnames(Partials$', Gene,'$', Tissue,')[ colnames(Partials$', Gene,'$', Tissue,') %in% Keeps]')))
-
-    #eval(parse(text=paste0('TarENS <- Candidates$', Gene, '[ Candidates$', Gene, '$hgnc_symbol == \'', Gene, '\' ,]$ensembl_gene_id' )))
-    eval(parse(text=paste0( 'Lookup <- Partials$', Gene,'$', Tissue, '[ Partials$', Gene,'$', Tissue, '[,\'SeedGene\'] == \'', Tarz, '\', Tarz ]' )))
-
-    eval(parse(text=paste0( 'Narrow$', Gene, ' <- c( Narrow$', Gene, ', names( Lookup))' )))
-  }
-  eval(parse(text=paste0( 'Narrow$', Gene, ' <- Narrow$', Gene, '[ !duplicated(Narrow$', Gene, ')]' )))
-}
-
-##Isolate Narrow Partials Or not.. 
-NewPartials <- list()
-for( Gene in names(Partials)){
-  eval(parse(text=paste0( 'NewPartials$', Gene, ' <- list()' )))
-  for(Tissue in names( ExpressionDS ) ){
-    eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue, ' <-  Partials$', Gene, '$', Tissue, '[ Partials$', Gene, '$', Tissue, '[,\'SeedGene\'] %in% Narrow$', Gene, ', ]')))
-    #eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue, ' <- Partials$', Gene, '$', Tissue)))
-  }
-}
-
-####Only keep genes with all 6 tissue correlations
-for( Gene in names(NewPartials)){
-  if( is.matrix( eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue ))) ) ){
-    eval(parse(text=paste0( 'foo <- c( NewPartials$', Gene, '$DLPFC[,\'SeedGene\'], NewPartials$', Gene, '$TCX[,\'SeedGene\'], NewPartials$', Gene, '$FP[,\'SeedGene\'], NewPartials$', Gene, '$IFG[,\'SeedGene\'], NewPartials$', Gene, '$STG[,\'SeedGene\'], NewPartials$', Gene, '$PHG[,\'SeedGene\'])')))
-  }else{
-    eval(parse(text=paste0( 'foo <- c( NewPartials$', Gene, '$DLPFC[\'SeedGene\'], NewPartials$', Gene, '$TCX[\'SeedGene\'], NewPartials$', Gene, '$FP[\'SeedGene\'], NewPartials$', Gene, '$IFG[\'SeedGene\'], NewPartials$', Gene, '$STG[\'SeedGene\'], NewPartials$', Gene, '$PHG[\'SeedGene\'])')))
-  }
-  foo <- foo[ !duplicated(foo) ]
-  Tib <- rep(0, length(foo))
-  names(Tib) <- foo
-
-  for(Tissue in names( ExpressionDS ) ){
-    if( is.matrix( eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue ))) ) ){
-      eval(parse(text=paste0( 'Tib[ NewPartials$', Gene, '$', Tissue, '[ ,\'SeedGene\' ]] <- Tib[ NewPartials$', Gene, '$', Tissue, '[ ,\'SeedGene\' ]] + 1')))
-    }else{
-      eval(parse(text=paste0( 'Tib[ NewPartials$', Gene, '$', Tissue, '[ \'SeedGene\' ]] <- as.numeric( Tib[ NewPartials$', Gene, '$', Tissue, '[ \'SeedGene\' ]]) + 1')))
-    }
-  }
-  for(Tissue in names( ExpressionDS ) ){
-      if( is.matrix( eval(parse(text=paste0('NewPartials$', Gene, '$', Tissue ))) ) ){
-        eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue, '<- NewPartials$', Gene, '$', Tissue, '[ NewPartials$', Gene, '$', Tissue, '[ ,\'SeedGene\' ] %in% names(Tib[Tib>3]),]')))
-      }else{
-        eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue, ' <- NewPartials$', Gene, '$', Tissue, '[ NewPartials$', Gene, '$', Tissue, '[ \'SeedGene\' ] %in% names(Tib[Tib>3])]')))
-        eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue, ' <- t(as.matrix( NewPartials$', Gene, '$', Tissue, '))')))
-      }
-  }
-}
-
-Cuts <- matrix(0, 101,length(names(Partials)))
-colnames( Cuts ) <- names(Partials)
-row.names( Cuts ) <-  seq( from=0, to=10, by=.1 )
-
-mark<-Sys.time()
-#_#Target <- list()
-Y <- foreach( i=row.names( Cuts ), .combine=rbind ) %dopar% {
-  Tar <- vector()
-  Target <- list()
-  for( Gene in names(NewPartials)){
-  #_#eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
-  #foreach( i=row.names( Cuts ), .combine=rbind ) %dopar% {
-    #_#
-    eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
-    #_#
-    for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
-      Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
-
-      if( dim(Temp)[1] > 1 ){
-        row.names(Temp) <- Temp[, 'SeedGene']
-        Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
-        Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
-      }else{
-        #row.names(Temp) <- as.character( Temp[, 'SeedGene'] )
-        Cs<-as.character( Temp[, 'SeedGene'] )
-        Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
-        Rs <- row.names(Temp)
-        Temp <- data.table::transpose(Temp)
-        row.names(Temp) <- Cs
-        colnames(Temp) <- Rs
-
-        Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
-      }
-
-      for( RName in row.names(Temp) ){
-        Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-        Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
-        Vals <- c( Vals, -1*Vals )
-        M <- mean( Vals )
-        S <- sd( Vals )
-        Lim <- M+as.numeric(i)*S
-        Adds <- colnames( Selct[ , Selct > Lim ] )
-        #Throw in any genes with more than 1 Parital corelation to the core set
-       # if( dim(Temp)[1] > 1){
-       #   Adds <- c(Adds, names(Temp[, colSums(Temp != 0) > 2 ]) )
-        #  Adds <- Adds[ !duplicated(Adds) ]
-        #}
-        eval(parse(text=paste0( 'Target$', Gene, ' <- c(Target$', Gene, ', Adds)'  )))
-      }
-    }
-    #Log Gene Lengths
-
-  } 
-  for(Ok in names(NewPartials)){
-      eval(parse(text=paste0( 'LENG <-length(Target$', Ok, '[!duplicated(Target$', Ok, ')])'  )))
-      eval(parse(text=paste0(  'Tar <- c(Tar, ',  LENG,')')))
-  }
-    names(Tar) <- names(NewPartials)
-    Extra <- 'StDevs'
-    eval(parse(text=paste0(  'Tar[\'', Extra, '\'] <- ',  i)))
-    return( Tar )
-}
-Sys.time()-mark
-#Narrow_sink <- Y
-data.table::fwrite(Y, file='NarrowPartial_Expanded_Numbers.csv', row.names=F, col.names=T)
-
-APOC1_Names <- list()
-for(Tissue in names(NewPartials$APOC1) ){
-  eval(parse(text=paste0('foo <- NewPartials$APOC1$', Tissue)))
-  row.names( foo ) <- foo[,'SeedGene']
-  foo <- foo[ , (colnames(foo) %in% 'SeedGene') == F ]
-  foo <- as.data.frame(foo)
-  foo[] <- lapply(foo, function(x) as.numeric(as.character(x)))
-
-  Count <- do.call( rbind, lapply(foo, function(x){ length(which(x==0))/length(x)}))
-  eval(parse(text=paste0('APOC1_Names$',Tissue ,' <- names(Count[ Count < 0.76,])')))
-}
-
-foo <- c( APOC1_Names$DLPFC, APOC1_Names$TCX, APOC1_Names$FP, APOC1_Names$IFG, APOC1_Names$STG, APOC1_Names$PHG )
-length( foo )
-
-poo <- names( table(foo)[table(foo)>1] )
-moo <-   NewPartials$APOC1$DLPFC[,"SeedGene"]
-
-PLOT_y <- reshape::melt(as.data.frame(Y), id=c("StDevs") )
-colnames(PLOT_y) <- c( "StDevs", "Seed Gene", "value" )
-library(ggplot2)
-
-###Should I Look only at genes correlated with target gene??
-
-#10% of the targets remaining at the second Standard Deviation
-CutoffVal <- round( Y[18,1:8]/10 )
-LIN <- rep(0, length(names(CutoffVal)))
-names(LIN) <- names(CutoffVal)
-for(tar in names(CutoffVal)){
-  eval(parse(text=paste0( 'LIN[\'', tar, '\'] <- Y[ Y[,\'', tar, '\'] < CutoffVal[tar], ][1,\'StDevs\']')))
-}
-
-LIN <- as.data.frame(LIN)
-LIN$`Seed Gene` <- row.names(LIN)
-#LIN$LIN <-c( 1, 1, 1, 1, 1, 1 )
-LIN$LIN <- c( 0.7, 1.3, 1.3, 1.3, 1.3, 1.7, 1.3, 1.3)
-
-g <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
-  geom_point() + 
-  geom_line() +
-  geom_vline(data = LIN, aes(xintercept = LIN, col=`Seed Gene`),linetype='dashed' ) +
-  ylab("Partially Correlated Genes Included") +
-  xlab("Standard Deviation Cutoff")
-
-ggsave(g, file="Cutoffs.eps", device="eps")
-system('synapse store --parentid syn21818446 --name Partial_Correlation_Decay Cutoffs.eps')
-g
-
-###Find Top 200 Targets:
-REF <- c( 0.7, 1.3, 1.3, 1.3, 1.3, 1.7, 1.3, 1.3 )
-names( REF ) <- names(NewPartials)
-
-Target <- list()
-for( Gene in names(NewPartials)){
-  eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
-  for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
-    Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
-    Rs <- Temp[,'SeedGene']
-    row.names(Temp) <- Temp[, 'SeedGene']
-    Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
-    Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
-     #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-    if( dim(Temp)[2] > 1 ){
-
-    }else{
-      Cs<-row.names(Temp)
-      Temp <- data.table::transpose(Temp)
-      row.names(Temp) <- Rs
-      colnames(Temp) <- Cs
-    }
-    for( RName in row.names(Temp) ){
-
-      Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-
-      Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
-      Vals <- c( Vals, -1*Vals )
-      M <- mean( Vals )
-      S <- sd( Vals )
-      #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
-      FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
-      SDs <- FIND[ dim(FIND)[1], 2]
-
-      #if( Gene %in% c( "TREM2")){
-        #SDs <- 0.7
-      #}else{
-        #if( Gene %in% c( 'APOC1')){
-          #SDs <- 1.7
-        #}else{
-          #SDs <- 1.3
-        #}
-      #}
-      if( Gene %in% c( "EED")){
-        SDs <- 0.5
-      }else{
-        if( Gene %in% c( "KNOP1")){
-          SDs <- 0.8
-        }else{
-          if( Gene %in% c( 'MTCH2') ){
-            #SDs <- 0.5
-            SDs <- 0.4
-            #SDs <- 1.5
-          }else{
-            if( Gene %in% c( 'TREM2')){
-              SDs <- 1.4
-            }else{
-              SDs <- 1.5
-            }
-          }
-        }
-      }
-      Lim <- M + SDs*S
-      Adds <- colnames( Selct[ , Selct > Lim ] )
-      eval(parse(text=paste0( 'Target$', Gene, ' <- c(Target$', Gene, ', Adds)'  )))
-    }
-  }
-}
-
-for( RName in names(Target) ){
-   eval(parse(text=paste0( 'Target$', RName, ' <- Target$', RName, '[!duplicated(Target$', RName, ')]'  )))
-}
-
-#```
-#```{r EnrichR}
-
-library(enrichR)
-dbs <- listEnrichrDbs()
-
-dbs <- c("GO_Molecular_Function_2018", 
-         "WikiPathways_2019_Human",
-         "GO_Cellular_Component_2018",
-         "GO_Biological_Process_2018") #, "ProteomicsDB_2020", "KEGG_2019_Human", "DSigDB","TRRUST_Transcription_Factors_2019")
-
-mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")
-
-TargetGN <- list()
-ENRICH <- list()
-
-Total_Genes <- c( colnames( Partials$TREM2$DLPFC ),
-                  colnames( Partials$TREM2$FP ),
-                  colnames( Partials$TREM2$IFG ),
-                  colnames( Partials$TREM2$PHG ),
-                  colnames( Partials$TREM2$STG ),
-                  colnames( Partials$TREM2$TCX )
-)
-#Take only genes in all expression sets:
-Total_Genes <- names(table(Total_Genes)[ table(Total_Genes) == 6])                  
-Total_Genes <- Total_Genes[ (Total_Genes == 'SeedGene') == F ]
-
-TG <- getBM(filters = 'ensembl_gene_id', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = Total_Genes, mart = mart)
-TG <- TG[ TG$ensembl_gene_id !='ENSG00000265354',] 
-TG$Tot <- paste0( TG$ensembl_gene_id, '_', TG$hgnc_symbol )
-TG <- TG[ !duplicated(TG$Tot), ]
-TG <- TG[ TG$hgnc_symbol != "", ]
-row.names(TG) <- TG$hgnc_symbol
-
-Locked_TG <- as.data.frame(TG$hgnc_symbol)
-Locked_TG$Included <- 0
-names(Locked_TG) <- c( "Gene", "Included" )
-Locked_TG$Gene <- as.character( Locked_TG$Gene ) 
-row.names(Locked_TG) <- Locked_TG$Gene
-
-Locked_TG <- Locked_TG[ Locked_TG$Gene != 'NA', ]
-
-for( G in names(Target)){
-  eval(parse(text=paste0( 'Genes <- getBM(filters = \'ensembl_gene_id\', attributes = c(\'ensembl_gene_id\', \'hgnc_symbol\'), values = Target$', G, ', mart = mart)' )))
-
-  GN <- Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol
-  eval(parse(text=paste0('TargetGN$', G, ' <-  Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol')))
-
-  eval(parse(text=paste0('Locked_TG[TargetGN$', G, ',]$Included <- 1')))
-  #foo<- enrichr(Locked_TG, dbs)
-  eval(parse(text=paste0('ENRICH$', G, ' <-  enrichr( Locked_TG[ Locked_TG$Included ==1,]$Gene, dbs)')))
-
-  Locked_TG$Included <- 0
-}
-#TMP <- enrichr( GN, dbs)
-for( G in names(Target)){
-  for( version in dbs ){
-    eval(parse(text=paste0( 'temp <- ENRICH$', G, '$', version )))
-    temp <- temp[ temp$Adjusted.P.value < 0.05, ]
-    eval(parse(text=paste0( 'ENRICH$', G, '$', version, ' <- temp' )))
-  }
-}
-
-```
-```{r clusterP}
-
-parentId = 'syn18936948';
-activityName = 'Gene Set Enrichment';
-activityDescription = 'Figure 4: gene set enrichment of genes implicated in TWAS regions';
-thisFileName <- 'GeneSet_Expansion.Rmd'
-# Github link
-thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
-thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
-
-CODE <- syn_temp$store(synapseclient$Folder(name = "Gene Set Enrichment Plots", parentId = parentId))
-
-library( clusterProfiler )
-library(enrichplot)
-library(enrichR)
-
-Enrich_Run <- function( cutoffs ){
-  #'@cutoffs a named vector of SD cutoff valutes for genes
-  SD_Store <- rep(NA,length(names(NewPartials)))
-  names(SD_Store) <- names(NewPartials)
-
-  Target <- list()
-  for( Gene in names(NewPartials)){
-    eval(parse(text=paste0( 'Target$', Gene, ' <- vector()' )))
-    for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
-      Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
-      Rs <- Temp[,'SeedGene']
-      row.names(Temp) <- Temp[, 'SeedGene']
-      Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
-      Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
-       #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-      if( dim(Temp)[2] > 1 ){
-
-      }else{
-        Cs<-row.names(Temp)
-        Temp <- data.table::transpose(Temp)
-        row.names(Temp) <- Rs
-        colnames(Temp) <- Cs
-      }
-      for( RName in row.names(Temp) ){
-
-        Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-
-        Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
-        Vals <- c( Vals, -1*Vals )
-        M <- mean( Vals )
-        S <- sd( Vals )
-        #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
-        FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
-        SDs <- FIND[ dim(FIND)[1], 2]
-
-        eval( parse( text = paste0( 'SDs <- cutoffs[\'', Gene,'\']' )))
-        eval( parse( text = paste0( 'SD_Store[\'', Gene,'\'] <- ', SDs )))
-        Lim <- M + SDs*S
-        Adds <- colnames( Selct[ , Selct > Lim ] )
-        eval(parse(text=paste0( 'Target$', Gene, ' <- c(Target$', Gene, ', Adds)'  )))
-      }
-    }
-  }
-
-  for( RName in names(Target) ){
-     eval(parse(text=paste0( 'Target$', RName, ' <- Target$', RName, '[!duplicated(Target$', RName, ')]'  )))
-  }
-
-  organism = "org.Hs.eg.db"
-  #BiocManager::install(organism, character.only = TRUE)
-  library(organism, character.only = TRUE)
-  library(DOSE)
-
-  Enrich_PLOTS <- list()
-  for( G in names(Target)){
-
-    eval(parse(text=paste0( 'Genes <- getBM(filters = \'ensembl_gene_id\', attributes = c(\'ensembl_gene_id\', \'hgnc_symbol\'), values = Target$', G, ', mart = mart)' )))
-
-    GN <- Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol
-  eval(parse(text=paste0('TargetGN$', G, ' <-  Genes[ (Genes$hgnc_symbol %in% "") ==F,]$hgnc_symbol')))
-
-    eval(parse(text=paste0('Locked_TG[TargetGN$', G, ',]$Included <- 1')))
-
-    eval(parse(text=paste0( 'Genes <- getBM(filters = \'ensembl_gene_id\', attributes = c(\'ensembl_gene_id\', \'hgnc_symbol\', \'entrezgene_id\'), values = Target$', G, ', mart = mart)' )))
-
-    #Locked_TG$Gene
-
-    #sample_test <- enrichGO( Genes$entrezgene_id, OrgDb=organism, pvalueCutoff=1, qvalueCutoff=1)
-
-    Locked_TG$ENSG <- TG[ Locked_TG$Gene, ]$ensembl_gene_id
-    gene.df <- bitr( Locked_TG$ENSG, fromType = "ENSEMBL", toType = c("ENSEMBL", "SYMBOL", "ENTREZID"), OrgDb = org.Hs.eg.db)
-    gene.df$Tot <- paste0( gene.df$ENSEMBL, "_", gene.df$SYMBOL, "_", gene.df$ENTREZID )
-    #'select()' returned 1:many mapping between keys and columns
-    #1.91% of input gene IDs are fail to map...
-
-    Gsubset <- eval(parse(text=paste0('Target$', G )))
-    Gsubset <- Gsubset[ Gsubset %in% gene.df$ENSEMBL ]
-    ego <- enrichGO(gene          = Gsubset,
-                  universe      = gene.df$ENSEMBL,
-                  OrgDb         = org.Hs.eg.db,
-                  #keyType       = 'SYMBOL',
-                  keyType       = 'ENSEMBL',
-                  ont           = "ALL",
-                  pAdjustMethod = "BH",
-                  pvalueCutoff  = 0.01,
-                  qvalueCutoff  = 0.05
-                )
-
-    eval(parse(text=paste0( 'SD_Used <- as.numeric(cutoffs[\'', G, '\'])' )))
-    if( dim(as.data.frame(ego))[1] >1 ){
-      cluster_summary <- data.frame(ego)
-      write.csv(cluster_summary , file = paste0("EnrichmentResults_", G, "_Stdevs_", SD_Used,".csv"), row.names=FALSE)
-
-      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentResults_", G, "_Stdevs_", SD_Used,".csv"), name = paste0("EnrichmentResults_", G, "_Stdevs_", SD_Used), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-      eval(parse(text=paste0( 'Enrich_PLOTS$', G, ' <- list()')))
-      # Dotplot
-      eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Dot <- clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30)' )))
-      pdf(file = paste0("EnrichmentDotPlot_", G, "_Stdevs_", SD_Used,".pdf"), width = 14, height = 7)
-         print( clusterProfiler::dotplot(ego, x = "GeneRatio", showCategory=30) )
-      dev.off()
-
-      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentDotPlot_", G, "_Stdevs_", SD_Used,".pdf"), name = paste0("EnrichmentDotPlot_", G, "_Stdevs_", SD_Used), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-      # Net Plot
-      eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Net <- cnetplot(ego, foldChange=NULL)' )))
-
-      pdf(file = paste0("EnrichmentNetPlot_", G, "_Stdevs_", SD_Used,".pdf"), width = 7, height = 7)
-         print( cnetplot(ego, foldChange=NULL))
-      dev.off()
-
-      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentNetPlot_", G, "_Stdevs_", SD_Used,".pdf"), name = paste0("EnrichmentNetPlot_", G, "_Stdevs_", SD_Used), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-      # Enrichment Plot
-      eval(parse(text=paste0( 'Enrich_PLOTS$', G, '$Erich <- enrichplot::emapplot(ego, showCategory = 10)' )))
-
-      pdf(file = paste0("EnrichmentEnrichPlot_", G, "_Stdevs_", SD_Used,".pdf"), width = 7, height = 7)
-        print( enrichplot::emapplot(ego, showCategory = 10) )
-      dev.off()
-
-      ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path=paste0("EnrichmentEnrichPlot_", G, "_Stdevs_", SD_Used,".pdf"), name = paste0("EnrichmentEnrichPlot_", G, "_Stdevs_", SD_Used,".pdf"), parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-    }else{}
-  }
-}
-
-#Run Enrichment at Broad Cutoffs:
-input <- c( TREM2 = 0.8, 
-            CD2AP= 0.8, 
-            MTCH2= 0.8, 
-            EED= 0.8, 
-            KNOP1= 0.8, 
-            APOC1= 0.8,
-            CEACAM19= 0.8,
-            CLPTM1= 0.8
-          )
-Enrich_Run( input )
-
-#Run Enrichment at Narrow Cutoffs:
-input <- c( TREM2 = 2.8, 
-            CD2AP = 2.8, 
-            MTCH2 = 2.8, 
-            EED = 2.8, 
-            KNOP1 = 2.8, 
-            APOC1 = 2.8,
-            CEACAM19= 2.8,
-            CLPTM1= 2.8
-          )
-Enrich_Run( input )
-
-#Run Enrichment at Custom Cutoffs:
-input <- c( TREM2 = 0.8, 
-            #CD2AP = 2, 
-            CD2AP = 1,
-            MTCH2 = 0.4, 
-            EED = 2, 
-            KNOP1 = 2, 
-            APOC1 = 1.7,
-            CEACAM19= 2,
-            CLPTM1= 2
-          )
-Enrich_Run( input )
-#if( Gene %in% c( "TREM2")){
-          #SDs <- 0.7
-          #SDs <- 2.8
-        #}else{
-          #if( Gene %in% c( 'APOC1')){
-            #SDs <- 1.7
-            #SDs <- 2.8
-          #}else{
-            #SDs <- 1.3
-            #SDs <- 2.8
-          #}
-        #}
-        #if( Gene %in% c( "EED")){
-          #SDs <- 0.5
-        #}else{
-          #if( Gene %in% c( "KNOP1")){
-           # SDs <- 0.8
-          #}else{
-            #if( Gene %in% c( 'MTCH2') ){
-              #SDs <- 0.5
-              #SDs <- 0.4
-              #SDs <- 1.5
-            #}else{
-              #if( Gene %in% c( 'TREM2')){
-                #SDs <- 1.4
-              #}else{
-                #SDs <- 1.5
-              #}
-            #}
-          #}
-        #}
-
-```
-
-```{r CellTypeSpecificity}
-Lake <- read.csv( file=syn_temp$get('syn21563069')$path, header = T )
-Lake <- as.data.frame( data.table::fread( file=syn_temp$get('syn21563069')$path ) )
-
-Total_Genes <- c( colnames( Partials$TREM2$DLPFC ),
-                  colnames( Partials$TREM2$FP ),
-                  colnames( Partials$TREM2$IFG ),
-                  colnames( Partials$TREM2$PHG ),
-                  colnames( Partials$TREM2$STG ),
-                  colnames( Partials$TREM2$TCX )
-)
-#Take only genes in all expression sets:
-Total_Genes <- names(table(Total_Genes)[ table(Total_Genes) == 6])                  
-Total_Genes <- Total_Genes[ (Total_Genes == 'SeedGene') == F ]
-
-mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")
-genes <- Lake$Gene
-Lake_genes <- getBM(filters = 'hgnc_symbol', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = genes, mart = mart)
-Lake_genes$Tot <- paste0( Lake_genes$ensembl_gene_id, "_", Lake_genes$hgnc_symbol )
-Lake_genes <- Lake_genes[ !duplicated(Lake_genes$Tot), ]
-row.names(Lake_genes) <- Lake_genes$ensembl_gene_id
-
-#filter for Lake Et. Al genes in RNA-Seq
-Lake_genes <- Lake_genes[ Lake_genes$ensembl_gene_id %in% Total_Genes,]
-#row.names(Lake_genes) <- Lake_genes$hgnc_symbol
-
-#TIMM23B entry Mis-named ENSG as TIMM23:
-Lake_genes[ Lake_genes$Tot == 'ENSG00000265354_TIMM23B', ]$ensembl_gene_id <- "ENSG00000204152"
-Lake_genes[ Lake_genes$Tot == 'ENSG00000265354_TIMM23B', ]$Tot <- "ENSG00000204152_TIMM23B"
-Lake_genes <- Lake_genes[ !duplicated(Lake_genes$Tot), ]
-row.names(Lake_genes) <- Lake_genes$hgnc_symbol
-
-#Add ENSGs to Lake data:
-Lake$ENSG <- Lake_genes[ Lake$Gene, ]$ensembl_gene_id
-
-#Throw out Lake Genes not able to be translated: 4.74%
-Lake <- Lake[grepl('ENSG', Lake$ENSG)==T,]
-
-#Cell_type ENSG List
-CellTypeGenes <- list()
-for( Name in names(table(Lake$Cluster)) ){
-  eval(parse(text=paste0( 'CellTypeGenes$', Name, ' <- Lake[ Lake$Cluster == \'', Name,'\',]$ENSG' )))
-}
-
-#Re-Define Partial Cor Gene Sets:
-GSE_Target <- list()
-for( Gene in names(NewPartials)){
-  eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- vector()' )))
-  for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
-    Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
-    Rs <- Temp[,'SeedGene']
-    row.names(Temp) <- Temp[, 'SeedGene']
-    Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
-    Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
-     #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-    if( dim(Temp)[2] > 1 ){
-
-    }else{
-      Cs<-row.names(Temp)
-      Temp <- data.table::transpose(Temp)
-      row.names(Temp) <- Rs
-      colnames(Temp) <- Cs
-    }
-    for( RName in row.names(Temp) ){
-
-      Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-
-      Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
-      Vals <- c( Vals, -1*Vals )
-      M <- mean( Vals )
-      S <- sd( Vals )
-      #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
-      FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
-      SDs <- FIND[ dim(FIND)[1], 2]
-      if( Gene %in% c( "TREM2")){
-        SDs <- 0.7
-      }else{
-        if( Gene %in% c( 'APOC1')){
-          SDs <- 1.7
-        }else{
-          SDs <- 1.3
-        }
-      }
-      Lim <- M + SDs*S
-      Adds <- colnames( Selct[ , Selct > Lim ] )
-      eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- c(GSE_Target$', Gene, ', Adds)'  )))
-    }
-  }
-}
-
-# Cell Type enrichment by binomial test:
-Actuals_Pval <- as.data.frame( matrix( 0, length( names(GSE_Target) ), length( names(CellTypeGenes) )) )
-colnames(Actuals_Pval) <- names(CellTypeGenes) 
-row.names(Actuals_Pval) <- names(GSE_Target)
-Actuals_OR <- Actuals_Pval
-
-for( G in names(GSE_Target)){
-  eval(parse(text=paste0( 'N <- length( GSE_Target$', G, ')')))
-  eval(parse(text=paste0( 'Genes <- GSE_Target$', G )))
-  Genes <- Genes[ (Genes %in% Total_Genes) == T ]
-  #Calc Actual Overlap
-  for( CT in colnames(Actuals_Pval) ){
-    #eval(parse(text=paste0( 'Actuals[ \'', G,'\',\'', CT,'\'] <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])')))
-    eval(parse(text=paste0( 'Perc <- length(CellTypeGenes$', CT, ')/length( Total_Genes )')))
-    eval(parse(text=paste0( 'Emp_Perc <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])/length( Genes )')))
-
-    if( length( eval(parse(text=paste0('table(Genes %in% CellTypeGenes$', CT, ')' ))) ) > 1 ){ 
-      eval(parse(text=paste0( 'N <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])' )))
-      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))
-
-      Foo <- binom.test( x=N, n=SIZE, p=Perc, alternative = c("two.sided") )
-      #Poo <- prop.test(x=N, n=SIZE, p=Perc, alternative = "two.sided", correct = TRUE)
-
-      if( Emp_Perc > Perc ){
-        OR <- Emp_Perc/Perc
-      }else{
-        OR <- -1*( Perc/Emp_Perc )
-      }
-      #Foo$p.value
-
-      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
-      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
-    }else{
-      Emp_Perc <- 0
-      eval(parse(text=paste0( 'N <- 0' )))
-      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))
-
-      Foo <- binom.test( N, SIZE, Perc )
-      if( Emp_Perc == 0){
-        OR <- NA
-      }else{
-        if( Emp_Perc > Perc ){
-          OR <- Emp_Perc/Perc
-        }else{
-          OR <- -1*( Perc/Emp_Perc )
-        }
-      }
-      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
-      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
-    }
-  }
-  Leng <- dim( Actuals_Pval )[2]
-  eval(parse(text=paste0( 'Actuals_Pval[ \'', G, '\', ] <- p.adjust(Actuals_Pval[ \'', G, '\', ], method = \'fdr\', n = ', Leng,' )' )))
-}
-
-test_labels <- Actuals_Pval
-test_labels[ test_labels< 0.05] <- "*"
-test_labels[ test_labels > 0.05] <- ""
-
-lin <- LIN
-lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7,1.3,1.3 )
-gG <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
-  geom_point() + 
-  geom_line() +
-  geom_vline(data = lin, aes(xintercept = LIN, col=`Seed Gene`),linetype='dashed' ) +
-  ylab("Partially Correlated Genes Included") +
-  xlab("Standard Deviation Cutoff")
-
-gG
-
-library(RColorBrewer)
-library(grDevices)
-cols <- colorRampPalette(c( "deepskyblue4", "darkslategray2", "white", "darkgoldenrod2", "red"))(100)
-
-Lake_HeatMap <- pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, 
-                    display_numbers = test_labels, fontsize_number=40)
-
-save_pheatmap_pdf <- function(x, filename, width=7, height=7) {
-   stopifnot(!missing(x))
-   stopifnot(!missing(filename))
-   pdf(filename, width=width, height=height)
-   grid::grid.newpage()
-   grid::grid.draw(x$gtable)
-   dev.off()
-}
-
-save_pheatmap_pdf(Lake_HeatMap, "Lake_HeatMap.pdf")
-
-```
-```{r CellTypeSpecificity_Mathys}
-Mathy <- read.csv( file=syn_temp$get('syn21785650')$path, header = T )
-#Mathy <- as.data.frame( data.table::fread( file=syn_temp$get('syn21563069')$path ) )
-
-Total_Genes <- c( colnames( Partials$TREM2$DLPFC ),
-                  colnames( Partials$TREM2$FP ),
-                  colnames( Partials$TREM2$IFG ),
-                  colnames( Partials$TREM2$PHG ),
-                  colnames( Partials$TREM2$STG ),
-                  colnames( Partials$TREM2$TCX )
-)
-#Take only genes in all expression sets:
-Total_Genes <- names(table(Total_Genes)[ table(Total_Genes) == 6])                  
-Total_Genes <- Total_Genes[ (Total_Genes == 'SeedGene') == F ]
-
-mart <- useMart("ensembl", host="grch37.ensembl.org", dataset = "hsapiens_gene_ensembl")
-genes <- Mathy$gene.name
-Mathy_genes <- getBM(filters = 'hgnc_symbol', attributes = c('ensembl_gene_id', 'hgnc_symbol'), values = genes, mart = mart)
-
-Mathy_genes$Tot <- paste0( Mathy_genes$ensembl_gene_id, "_", Mathy_genes$hgnc_symbol )
-Mathy_genes <- Mathy_genes[ !duplicated(Mathy_genes$Tot), ]
-row.names(Mathy_genes) <- Mathy_genes$ensembl_gene_id
-
-#filter for Mathys Et. Al genes in RNA-Seq
-Mathy_genes <- Mathy_genes[ Mathy_genes$ensembl_gene_id %in% Total_Genes,]
-row.names(Mathy_genes) <- Mathy_genes$hgnc_symbol
-
-#Add ENSGs to Lake data:
-Mathy$ENSG <- Mathy_genes[ Mathy$gene.name, ]$ensembl_gene_id
-
-#Throw out Mathys Genes not able to be translated: 3.78%
-Mathy <- Mathy[grepl('ENSG', Mathy$ENSG)==T,]
-
-#Cell_type ENSG List
-CellTypeGenes <- list()
-for( Name in names(table(Mathy$subpopulation)) ){
-  eval(parse(text=paste0( 'CellTypeGenes$', Name, ' <- Mathy[ Mathy$subpopulation == \'', Name,'\',]$ENSG' )))
-}
-
-#Re-Define Partial Cor Gene Sets:
-GSE_Target <- list()
-for( Gene in names(NewPartials)){
-  eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- vector()' )))
-  for( Tissue in eval(parse(text=paste0( 'names(NewPartials$', Gene, ')'  ))) ){
-    Temp <- eval(parse(text=paste0( 'NewPartials$', Gene, '$', Tissue )))
-    Rs <- Temp[,'SeedGene']
-    row.names(Temp) <- Temp[, 'SeedGene']
-    Temp <- as.data.frame( Temp[ ,(colnames(Temp) %in% 'SeedGene') == F ] )
-    Temp[] <- lapply(Temp, function(x) as.numeric(as.character(x)))
-     #Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-    if( dim(Temp)[2] > 1 ){
-
-    }else{
-      Cs<-row.names(Temp)
-      Temp <- data.table::transpose(Temp)
-      row.names(Temp) <- Rs
-      colnames(Temp) <- Cs
-    }
-    for( RName in row.names(Temp) ){
-
-      Selct <- Temp[ RName, Temp[ RName, ]>0 ]
-
-      Vals <- as.vector( as.numeric(as.character( Selct[ 1 , Selct[1,] < 1 ] ) ))
-      Vals <- c( Vals, -1*Vals )
-      M <- mean( Vals )
-      S <- sd( Vals )
-      #Lim <- M + as.numeric( LIN[ Gene,]$LIN )*S
-      FIND <- Y[ ,c(Gene,"StDevs")][ Y[ ,c(Gene,"StDevs")][,1] > 200, ]
-      SDs <- FIND[ dim(FIND)[1], 2]
-      if( Gene %in% c( "TREM2")){
-        SDs <- 0.7
-      }else{
-        if( Gene %in% c( 'APOC1')){
-          SDs <- 1.7
-        }else{
-          SDs <- 1.3
-        }
-      }
-      Lim <- M + SDs*S
-      Adds <- colnames( Selct[ , Selct > Lim ] )
-      eval(parse(text=paste0( 'GSE_Target$', Gene, ' <- c(GSE_Target$', Gene, ', Adds)'  )))
-    }
-  }
-}
-
-# Cell Type enrichment by binomial test:
-Actuals_Pval <- as.data.frame( matrix( 0, length( names(GSE_Target) ), length( names(CellTypeGenes) )) )
-colnames(Actuals_Pval) <- names(CellTypeGenes) 
-row.names(Actuals_Pval) <- names(GSE_Target)
-Actuals_OR <- Actuals_Pval
-
-for( G in names(GSE_Target)){
-  eval(parse(text=paste0( 'N <- length( GSE_Target$', G, ')')))
-  eval(parse(text=paste0( 'Genes <- GSE_Target$', G )))
-  Genes <- Genes[ (Genes %in% Total_Genes) == T ]
-  #Calc Actual Overlap
-  for( CT in colnames(Actuals_Pval) ){
-    #eval(parse(text=paste0( 'Actuals[ \'', G,'\',\'', CT,'\'] <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])')))
-    eval(parse(text=paste0( 'Perc <- length(CellTypeGenes$', CT, ')/length( Total_Genes )')))
-    eval(parse(text=paste0( 'Emp_Perc <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])/length( Genes )')))
-
-    if( length( eval(parse(text=paste0('table(Genes %in% CellTypeGenes$', CT, ')' ))) ) > 1 ){ 
-      eval(parse(text=paste0( 'N <- as.numeric( table( Genes %in% CellTypeGenes$', CT, ')[\'TRUE\'])' )))
-      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))
-
-      Foo <- binom.test( x=N, n=SIZE, p=Perc, alternative = c("two.sided") )
-      #Poo <- prop.test(x=N, n=SIZE, p=Perc, alternative = "two.sided", correct = TRUE)
-
-      if( Emp_Perc > Perc ){
-        OR <- Emp_Perc/Perc
-      }else{
-        OR <- -1*( Perc/Emp_Perc )
-      }
-      #Foo$p.value
-
-      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
-      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
-    }else{
-      Emp_Perc <- 0
-      eval(parse(text=paste0( 'N <- 0' )))
-      eval(parse(text=paste0( 'SIZE <- length( CellTypeGenes$', CT, ')' )))
-
-      Foo <- binom.test( N, SIZE, Perc )
-      if( Emp_Perc == 0){
-        OR <- NA
-      }else{
-        if( Emp_Perc > Perc ){
-          OR <- Emp_Perc/Perc
-        }else{
-          OR <- -1*( Perc/Emp_Perc )
-        }
-      }
-      eval(parse(text=paste0( 'Actuals_Pval[ \'', G,'\',\'', CT,'\'] <- Foo$p.value')))
-      eval(parse(text=paste0( 'Actuals_OR[ \'', G,'\',\'', CT,'\'] <- OR')))
-    }
-  }
-  Leng <- dim( Actuals_Pval )[2]
-  eval(parse(text=paste0( 'Actuals_Pval[ \'', G, '\', ] <- p.adjust(Actuals_Pval[ \'', G, '\', ], method = \'fdr\', n = ', Leng,' )' )))
-}
-
-test_labels <- Actuals_Pval
-test_labels[ test_labels< 0.05] <- "*"
-test_labels[ test_labels > 0.05] <- ""
-
-lin <- LIN
-lin$LIN <- c( 0.7, 1.3,1.3,1.3,1.3,1.7,1.3,1.3 )
-Mathys_G <- ggplot( data=PLOT_y, aes( x=StDevs, y=value, col=`Seed Gene`)) + 
-  geom_point() + 
-  geom_line() +
-  geom_vline(data = lin, aes(xintercept = LIN, col=`Seed Gene`),linetype='dashed' ) +
-  ylab("Partially Correlated Genes Included") +
-  xlab("Standard Deviation Cutoff")
-
-Mathys_G
-
-setEPS()
-postscript( 'STDEV_Cutoff.eps' )
-  Mathys_G
-dev.off()
-
-#Actuals_OR <- Actuals_OR[colSums(!is.na(Actuals_OR)) > 1]
-Actuals_OR[is.na(Actuals_OR)] <- 0
-test_labels <- test_labels[ , colnames(Actuals_OR)]
-
-makeColorRampPalette <- function(colors, cutoff.fraction, num.colors.in.palette)
-{
-  stopifnot(length(colors) == 4)
-  ramp1 <- colorRampPalette(colors[1:2])(num.colors.in.palette * cutoff.fraction)
-  ramp2 <- colorRampPalette(colors[3:4])(num.colors.in.palette * (1 - cutoff.fraction))
-  return(c(ramp1, ramp2))
-}
-
-library(RColorBrewer)
-library(grDevices)
-cols <- colorRampPalette(c("navyblue", "deepskyblue4", "darkslategray2", "white", "darkgoldenrod2", "red"))(100)
-
-Mathys_HeatMap <- pheatmap::pheatmap( as.matrix(Actuals_OR), col=cols, cluster_cols=F, display_numbers = test_labels, fontsize_number=40)
-save_pheatmap_pdf(Mathys_HeatMap, "Mathys_HeatMap.pdf")
-
-parentId = 'syn18936948';
-activityName = 'Gene Set Enrichment';
-activityDescription = 'Figure 4: gene set enrichment of genes implicated in TWAS regions';
-thisFileName <- 'GeneSet_Expansion.Rmd'
-# Github link
-thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
-thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
-
-CODE <- syn_temp$store(synapseclient$Folder(name = "Gene Set Enrichment Plots", parentId = parentId))
-
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='STDEV_Cutoff.eps', name = 'StDev Cutoff values of Partial Correlations', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Lake_HeatMap.pdf', name = 'Lake et.al CellType Specificity', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Mathys_HeatMap.pdf', name = 'Mathys et.al CellType Specificity', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-
-```
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

---
  title: "Summary-data-based Mendelian Randomization Jansen etal Summary stats"
author: "Jake Gockley"
date: "01/17/2019"
header-includes:
  - \usepackage{multicol}
  - \newcommand{\btwocol}{\begin{multicols}{2}}
  - \newcommand{\etwocol}{\end{multicols}}
output:
  html_document: default
pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(readr)
library(snpStats)
library(sem)
library(parallel)
```

```{r code, eval=TRUE, cache=FALSE, include=TRUE}
#Pull eQTL Data
system( 'synapse get syn16984815' )
#Pull Weights
#system('aws s3 cp s3://jkg-s3-synapseencryptedexternalbucket-zszdd03ghnb2/ROSMAP/TWAS_2019_12_02_PanCortex_DiagnosisRegressed_Weights/ All_Data/ALL/ --recursive')
#system('rm All_Data/ALL/*.hsq')
system('synapse get -r syn21363795 --downloadLocation All_Data/ALL/ ')
system('rm All_Data/ALL/*.hsq')
#PullGenos
system('synapse get syn20820120 --downloadLocation Binary_Cleaned/')
system('synapse get syn20820121 --downloadLocation Binary_Cleaned/')
system('synapse get syn20820122 --downloadLocation Binary_Cleaned/')
#GWAS - Jansen et al
system('synapse get syn22043376 --downloadLocation .')
#Expression
system('synapse get syn21011186 --downloadLocation .')
Exp <- read.table('ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', header = T, sep='\t')
#LoadKunkle
Jan <- read.table('Jansen_TWAS_Format_SummaryStat.txt', header =T, sep="")
#Try the MR for one gene
load("All_Data/ALL/ENSG00000130208.wgt.RDat")
PLINK <- read.plink(bed = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bed' ,
                    bim = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bim',
                    fam = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.fam' 
)
#Filter Kunkle for relevant SNPS by their IDS
K <- Jan[ Jan$MarkerName %in% PLINK$map$snp.name, ]
row.names(K) <- K$MarkerName
mygwas<-K[,c(3:5,9,6:8)]
colnames(mygwas) <- c("SNP", "A1", 'A2', "freq", "b", "se", "p" )
mygwas$n <- rep( 2003, dim(mygwas)[1] )
write.table(snps$V2, 'snp.list', row.names=F, col.names=F, quote=F, sep='\t')
write.table(mygwas, 'mygwas.ma', row.names=F, col.names=T, quote=F, sep='\t')
if('plink' %in% list.files() ){}else{
system('wget http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20200107.zip')
system('unzip plink_linux_x86_64_20200107.zip')
}
if('smr_Linux' %in% list.files() ){}else{
system('wget https://cnsgenomics.com/software/smr/download/smr_Linux.zip')
system('unzip smr_Linux.zip')
}
system( './plink -bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --extract snp.list --make-bed --out Temp_plink')
system( './smr_Linux --bfile Temp_plink --gwas-summary mygwas.ma --beqtl-summary myeqtl --out mymulti --smr-multi')
#make the eqtl data into BESD format
EQTL <- read.csv( 'Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv', header = T )
EQTl <- EQTL[ as.character(EQTL$snpid ) %in% as.character(PLINK$map$snp.name) , ]
EQtl <- EQTl[ as.character(EQTl$gene ) %in% as.character(Exp$TargetID) , ]
EQTL_sink <- EQTL
EQTL <- EQtl
#SNP gene beta t-stat p-value FDR
EQTL$geneSymbol <- as.character(EQTL$geneSymbol)
EQTL$gene <- as.character(EQTL$gene)
EQTL[ as.character(EQTL$geneSymbol) =="",]$geneSymbol <- EQTL[ as.character(EQTL$geneSymbol) =="",]$gene
EQTL$snpid <- as.character(EQTL$snpid)
EQTL$DUP <- paste0( as.character(EQTL$snpid), '_', as.character(EQTL$gene))
EQTL_deDup <- EQTL[ !duplicated(EQTL$DUP), ]
##LOAD EXPRESSION AND BIM
###FILTER FOR RELEVANT SNP-GENEs
##### wExp <- read.table(file = 'WeightList/MaterWeight.lst', sep = "", header = T)
#EQTL_deDup <- EQTL_deDup[ EQTL_deDup$snpid %in% as.character(PLINK$bim[,2]), ]
#EQTL_deDup <- EQTL_deDup[ EQTL_deDup$gene %in% as.character(Exp[,2]), ]
Repo <- function( n ){
  #'@Mat eg. EQTL_deDup 
  #'@n eg a number
  if( EQTL_deDup[n,]$geneSymbol == ""){
    EQTL_deDup[n,]$geneSymbol <- EQTL_deDup[n,]$gene
  }else{}
}
REPS <- row.names( EQTL_deDup[ EQTL_deDup$geneSymbol == "", ] )
eqtl <- EQTL_deDup[ , c('snpid', 'geneSymbol', 'beta', 'statistic', 'pvalue', 'beta') ]
colnames(eqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 'p-value', 'FDR' )
write.table( eqtl, file = 'mateQTL_geneN.txt', col.names = T, row.names=F, quote=F, sep='\t' )

Eeqtl <- EQTL_deDup[ , c('snpid', 'gene', 'beta', 'statistic', 'pvalue', 'beta') ]
colnames(Eeqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 'p-value', 'FDR' )
write.table( Eeqtl, file = 'mateQTL_ensgN.txt', col.names = T, row.names=F, quote=F, sep='\t' )

system( './smr_Linux --eqtl-summary mateQTL_ensgN.txt --matrix-eqtl-format --make-besd --out mybesd_ensgN' )
system( './smr_Linux --eqtl-summary mateQTL_geneN.txt --matrix-eqtl-format --make-besd --out mybesd_geneN' )
##Fix the ,esi and .epi files
AleleSelect <- function( Row ){
  if( Row[4] > 0 ){
    Eff <- as.character(Row[9])
    Unaff <- as.character(c(Row[6],Row[7])[ (c(Row[6],Row[7]) %in% Eff) == F ])
  }else{
    Unaff <- as.character(Row[9])
    Eff <- as.character(c(Row[6],Row[7])[ (c(Row[6],Row[7]) %in% Unaff) == F ])
  }
  if(Eff == Row[7]){
    Freq <- Row[8]
  }else{
    Freq <- 1-as.numeric(Row[8])
  }

  return( c(as.character(Eff),as.character(Unaff),as.character(Freq)) )
}
ESiProcess <- function( Fil ){
  #'@Fil the loaded .esi file (ie File)
  ESi_info <- EQTL_deDup[ !duplicated(EQTL_deDup$snpid), c("chromosome", "snpLocation", "snpid", "statistic", "beta", "A1", "A2", "A2freq", "expressionIncreasingAllele")]
  row.names(ESi_info) <- ESi_info$snpid
  Fil$V1 <- as.character(ESi_info[ as.character( Fil$V2 ), ]$chromosome)
  Fil$V4 <- as.character(ESi_info[ as.character( Fil$V2 ), ]$snpLocation)

  ESi_info$A1 <- as.character(ESi_info$A1)
  ESi_info$A2 <- as.character(ESi_info$A2)
  ESi_info$expressionIncreasingAllele <- as.character(ESi_info$expressionIncreasingAllele)

  temp <- t( apply(ESi_info, 1, AleleSelect) )
  Fil[,5:7] <- temp[ as.character(Fil$V2),]
  return(Fil)
}
File <- read.table(file='mybesd_ensgN.esi', header=F, sep='\t')
File2 <- ESiProcess( File )
write.table(File2, file='mybesd_ensgN.esi', col.names=F, row.names = F, quote=F, sep='\t')
File <- read.table(file='mybesd_geneN.esi', header=F, sep='\t')
File2 <- ESiProcess( File )
write.table(File2, file='mybesd_geneN.esi', col.names=F, row.names = F, quote=F, sep='\t')
#ESPI
row.names(Exp) <- as.character(Exp$TargetID)
Exp$TargetID <- as.character(Exp$TargetID)
Exp$Gene_Symbol <- as.character(Exp$Gene_Symbol)
EQTL_deDup$gene <- as.character(EQTL_deDup$gene)
EQTL_deDup$geneSymbol <- as.character(EQTL_deDup$geneSymbol)
EQTL_deDup$chromosome <- as.character(EQTL_deDup$chromosome)
EQTL_deDup$strand <- as.character(EQTL_deDup$strand)
#Split EQTL_deDup into special data frames to reference
EQTL_deDup_GN <- EQTL_deDup[ !duplicated(EQTL_deDup$geneSymbol), ]
EQTL_deDup_ENSG <- EQTL_deDup[ !duplicated(EQTL_deDup$gene), ]

ESpProcess <- function( Name ){
  #'@Name row with gene name or ENSG in column 2
  if(Name[2] %in% EQTL_deDup_ENSG$gene){
    Row <- EQTL_deDup_ENSG[ EQTL_deDup_ENSG$gene %in% Name[2], ][1,]
  }else{
    Row <- EQTL_deDup_GN[ EQTL_deDup_GN$geneSymbol %in% Name[2], ][1,]
  }
  st <- c('+', '-')
  names(st) <- c("1","-1")

  return( c( as.character(Row[1]), 
             as.character(Name[2]), 
             as.character("0"), 
             as.character(Exp[ as.character(Row[5]), 4]),
             as.character(Name[2]),
             as.character(st[Row[,15]])  
             ) 
          )
}
File <- read.table(file='mybesd_geneN.epi', header=F, sep='\t')
File$V2 <- as.character(File$V2)
foo <- t( apply(File, 1, ESpProcess ) )
write.table( foo, file='mybesd_geneN.epi', row.names=F, col.names=F, quote = F, sep='\t' )
File <- read.table(file='mybesd_ensgN.epi', header=F, sep='\t')
File$V2 <- as.character(File$V2)
foo <- t( apply(File, 1, ESpProcess ) )
write.table( foo, file='mybesd_ensgN.epi', row.names=F, col.names=F, quote = F, sep='\t' )
Genes <- c("APOC1", "EED", "CD2AP", "CEACAM19", "CLPTM1", "MTCH2", "TREM2", "KNOP1", "POLR2E", "POLR2G", "ZNF660", "MADD", "PVRL2", "PVR", "TMEM223", "NUP160", "PTPRJ", "C1QTNF4")
ENSG <- c
write.table(EQTL_deDup_GN[ EQTL_deDup_GN$geneSymbol %in% Genes, ]$gene, "myprobe.list", row.names=F, col.names=F, quote=F, sep='\t')
library(doParallel)
library(foreach)
#Start Master File
system( 'echo "probeID ProbeChr  Gene  Probe_bp  topSNP  topSNP_chr  topSNP_bp A1  A2  Freq  b_GWAS  se_GWAS tp_GWAS b_eQTL  se_eQTL p_eQTL  b_SMR se_SMR  p_SMR p_SMR_multi p_HEIDI nsnp_HEIDI" > Compiled_SMR.tsv')
#List <- read.table( 'WeightList/MaterWeight.lst', header = T, sep='')
List <- cbind(list.files('All_Data/ALL/'), paste0( 'All_Data/ALL/', list.files('All_Data/ALL/') ))
List[,1] <- gsub('.wgt.RDat','',List[,1])
List <- as.data.frame(List)
colnames(List) <- c('ID','WGT')
#i <- 1
#List <- as.data.frame(List)
#colnames(List) <- 'WGT'
Runner <- function( i ){
  #Load Gene Info
  load(as.character( List$WGT )[i])
  Probe <- as.character( List$ID )[i]
  SNPs <- snps$V2
  #Save Temp Files
  write.table(Probe, paste0("myprobe_", Probe, ".list"), row.names=F, col.names=F, sep="\t", quote=F)
  write.table(SNPs, paste0("mysnp_", Probe, ".list"), row.names=F, col.names=F, sep="\t", quote=F)
  #Run Model
  system( paste0("./smr_Linux --bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --gwas-summary mygwas.ma --thread-num 1 --beqtl-summary mybesd_ensgN --ld-upper-limit 1 --out temp_Ensg_", Probe, " --extract-snp mysnp_", Probe, ".list --extract-probe myprobe_", Probe, ".list --peqtl-heidi 0 --ld-multi-snp 1 --smr-multi --peqtl-smr 1 --set-wind 2000 "))
  #Pull Info
  system( paste0("grep -v 'probeID' temp_Ensg_", Probe, ".msmr >> Compiled_SMR.tsv") )
  #remove Temp Info
  system( paste0("rm myprobe_", Probe, ".list") )
  system( paste0("rm mysnp_", Probe, ".list") )
  system( paste0("rm temp_Ensg_", Probe, ".*") )
}
cl <- makeCluster(  parallel::detectCores()-2 )
registerDoParallel(cl)

foo <- Sys.time()
  foreach(i=1:length(List$ID[List$ID != 'SYNAPSE_METADATA_MANIFEST.tsv'])[1]) %dopar% Runner( i )
Sys.time()-foo

stopCluster(cl)

system( 'awk \'{print $1"\t"$2"\t"$3"\t"$4"\t"$5"\t"$6"\t"$7"\t"$8"\t"$9"\t"$10"\t"$11"\t"$12"\t"$13"\t"$14"\t"$15"\t"$16"\t"$17"\t"$18"\t"$19"\t"$20"\t"$21"\t"$22}\' Compiled_SMR.tsv > temp.tsv') 
system('mv temp.tsv Compiled_SMR.tsv')
Table<-read.table(file='Compiled_SMR.tsv', , sep='\t', header=T)
system( 'awk -F \',\' \'{ print $5"\t"$6 }\' Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv | sort | uniq | grep -v \'geneSymbol\' > Translate.txt')
Trans <- read.table( file='Translate.txt', sep ="\t", header=F)
row.names(Trans) <- Trans$V1
Trans$V1 <- as.character(Trans$V1) 
Trans$V2 <- as.character(Trans$V2) 
Trans[ is.na(Trans$V2), ]$V2 <- Trans[ is.na(Trans$V2), ]$V1
Trans[ Trans$V2 == "", ]$V2 <- Trans[ Trans$V2 == "", ]$V1
Table$Gene <- as.character(Table$Gene)
Table$probeID <- as.character(Table$probeID)
Table$Gene <- Trans[Table$probeID,]$V2
write.table(Table, file='Final_SMR_TWAS_Jansen_Validation.tsv', row.names=F, col.names=T, quote=F, sep ='\t')
```

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'Mendelian Randomization';
activityDescription = 'Validation of TWAS associations via SMR analysis';
thisFileName <- 'SMR.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
activityName = 'Mendelian Randomization';
activityDescription = 'Validation of TWAS associations via SMR analysis';
CODE <- syn_temp$store(synapseclient$Folder(name = "Summary-data-based Mendelian Randomization", parentId = parentId))
# Set annotations
all.annotations = list(
  dataType = 'analysis',
  dataSubType = 'SMR_Validation_Tests',
  summaryLevel = 'gene',
  assay	 = 'TWAS',
  tissueTypeAbrv	= c('NA'), 
  study = c('ROSMAP','MSBB', 'Mayo'),
  organism = 'HomoSapiens',
  consortium	=  c('ROSMAP','MSBB', 'Mayo') ,
  normalizationStatus	= TRUE,
  normalizationType	= 'NA',
  rnaquantification = 'NA',
  genomeAssemblyID = 'hg19'
)
# Store SMR
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Final_SMR_TWAS_Jansen_Validation.tsv', name = 'SMR Values', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
all.annotations$dataSubType = 'Summary Stats'
syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
```

### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()
setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "SMR.Rmd",
                                  parentId ="syn18936948",
                                  folderName = 'Summary-data-based Mendelian Randomization')
```

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

@@
 activityDescription = 'Validation of TWAS associations via SMR analysis';
-thisFileName <- 'SMR.Rmd'
+thisFileName <- 'Jansen_SMR.Rmd'
 # Github link
@@
 source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
-createAndKnitToFolderEntityClient(file = "SMR.Rmd",
+createAndKnitToFolderEntityClient(file = "Jansen_SMR.Rmd",
                                   parentId ="syn18936948",

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

@@
 activityDescription = 'Validation of TWAS associations via SMR analysis';
-CODE <- syn_temp$store(synapseclient$Folder(name = "Summary-data-based Mendelian Randomization", parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = "Jansen_SMR", parentId = parentId))
 # Set annotations

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn18936948';
+parentId = 'syn22050453';
 activityName = 'Mendelian Randomization';
@@
 createAndKnitToFolderEntityClient(file = "Jansen_SMR.Rmd",
-                                  parentId ="syn18936948",
+                                  parentId ="syn22050453",
                                   folderName = 'Summary-data-based Mendelian Randomization')

### 2020-05-16 code/Jansen_SMR.Rmd
Jansen SMR

@@
 
-system( 'awk \'{print $1"\t"$2"\t"$3"\t"$4"\t"$5"\t"$6"\t"$7"\t"$8"\t"$9"\t"$10"\t"$11"\t"$12"\t"$13"\t"$14"\t"$15"\t"$16"\t"$17"\t"$18"\t"$19"\t"$20"\t"$21"\t"$22}\' Compiled_SMR.tsv > temp.tsv') 
-system('mv temp.tsv Compiled_SMR.tsv')
+#system( 'awk \'{print $1"\t"$2"\t"$3"\t"$4"\t"$5"\t"$6"\t"$7"\t"$8"\t"$9"\t"$10"\t"$11"\t"$12"\t"$13"\t"$14"\t"$15"\t"$16"\t"$17"\t"$18"\t"$19"\t"$20"\t"$21"\t"$22}\' Compiled_SMR.tsv > temp.tsv') 
+#system('mv temp.tsv Compiled_SMR.tsv')
 Table<-read.table(file='Compiled_SMR.tsv', , sep='\t', header=T)
@@
                                   parentId ="syn22050453",
-                                  folderName = 'Summary-data-based Mendelian Randomization')
+                                  folderName = 'Jansen_SMR')
 ```

### 2020-06-10 code/CMC_ACC_Exp_DataProcessing_V2020_04_28.Rmd
Initial Repo Clean

--- 2020-02-07 code/CMC_ACC_Exp_DataProcessing_V2.Rmd
@@
 library(R.utils)
+library(data.table)
 
@@
 # Download reprocessed counts
-counts = 'syn21071622'
+#_Deprecated_# counts = 'syn21071622'
+counts = 'syn16783557'
 ALL_USED_IDs = counts
 counts = downloadFile(counts) %>% data.frame()
+#_# Fix  Row Names of Counts
 counts$Chr <- NULL
@@
 counts$Strand <- NULL
+
+row.names(counts) <- counts$Geneid #  do.call( rbind, strsplit(counts$Geneid,"[.]") )[,1]
+
 # Parse gene lengths
@@
 counts$Length <- NULL
+#counts$Geneid <- NULL
 gene_lengths <- rename(gene_lengths, gene_id = Geneid)
+
 # Get ancestry vector calculated using gemtools
@@
 #Get Metadata
+#--syn16783596
+
 metadata = 'syn16816488' 
@@
   dplyr::mutate(Dx = forcats::fct_recode(Dx,  Other = "AFF", Other = "BP", Control = "Control", SCZ = "SCZ"))
+
+#Load this alignments Seq Stats:
+AltMeta <- 'syn16783596'
+alt = downloadFile_version(AltMeta, version = 1)
+colnames(alt) <- c('cnt', 'ID', 'TotalReads', 'MappedReads','GenesDetected', 'TranscriptsDetected', 'AlignmentRate', 
+                   'IntragenicRate', 'IntronicRate', 'IntergenicRate', 'ExpProfEfficiency', 'rRNARate')
+
+#Get rid of FlowcellBatch
+METADATA <- METADATA[ , colnames(METADATA) != 'FlowcellBatch' ]
+METADATA <- METADATA[ !duplicated(METADATA),]
+row.names(METADATA) <- METADATA$SampleID
+row.names(alt) <- alt$ID
+METADATA <- METADATA[  row.names(alt), ]
+
+#Now copy in relevant New Seq Stats:
+METADATA$MappedReads <- alt[ row.names(METADATA), ]$MappedReads
+METADATA$TotalReads <- alt[ row.names(METADATA), ]$TotalReads
+METADATA$GenesDetected <- alt[ row.names(METADATA), ]$GenesDetected
+METADATA$AlignmentRate <- alt[ row.names(METADATA), ]$AlignmentRate
+METADATA$IntragenicRate <- alt[ row.names(METADATA), ]$IntragenicRate
+METADATA$IntergenicRate <- alt[ row.names(METADATA), ]$IntergenicRate
+METADATA$IntronicRate <- alt[ row.names(METADATA), ]$IntronicRate
+METADATA$ExpProfEfficiency <- alt[ row.names(METADATA), ]$ExpProfEfficiency
+METADATA$rRNARate <- alt[ row.names(METADATA), ]$rRNARate
 ```
@@
 FILT <- REPORTED.GENDER.COUNTS %>% 
-  filter(gene_id == "ENSG00000229807.11" | gene_id == "ENSG00000183878.15") %>% 
+  #_#filter(gene_id == "ENSG00000229807.11" | gene_id == "ENSG00000183878.15") %>% 
+  filter(gene_id == "ENSG00000229807.10" | gene_id == "ENSG00000183878.15") %>% 
   dplyr::select(-one_of("chromosome_name")) %>% 
   tidyr::spread(key = gene_id, value = `counts(log)`) %>% 
-  mutate(XIST = as.numeric(`ENSG00000229807.11`)) %>% 
+  #_#mutate(XIST = as.numeric(`ENSG00000229807.11`)) %>% 
+  mutate(XIST = as.numeric(`ENSG00000229807.10`)) %>% 
   mutate(UTY = as.numeric(`ENSG00000183878.15`))
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
-
-FactorCovariates <- c('Individual_ID','FlowcellBatch', "Institution", "Reported_Gender", "LibraryBatch", "Tissue", "Dx.Tissue", "Dx", "RibozeroBatch")
+#_#Removed 'FlowCellBatch'
+FactorCovariates <- c('Individual_ID', "Institution", "Reported_Gender", "LibraryBatch", "Tissue", "Dx.Tissue", "Dx", "RibozeroBatch")
 #_#FactorCovariates <- c('Individual_ID', "Institution","Dx.Tissue", "Reported_Gender", "Dx", "RibozeroBatch")
@@
 }) %>% t
-CQN.GENE_EXPRESSION$E = LOG.CPM[ (row.names(LOG.CPM) %in% ProbGenes) == F, ]
+#_# CQN.GENE_EXPRESSION$E = LOG.CPM[ (row.names(LOG.CPM) %in% ProbGenes) == F, ]
 CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
@@
 dim(NEW.COUNTS)
-NEW.COUNTS <- NEW.COUNTS[ (row.names(NEW.COUNTS) %in% ProbGenes) == F, ]
+#_# NEW.COUNTS <- NEW.COUNTS[ (row.names(NEW.COUNTS) %in% ProbGenes) == F, ]
 dim(NEW.COUNTS)
@@
 COVARIATES1$Individual_ID <- as.factor(as.character(COVARIATES1$Individual_ID))
-COVARIATES1$FlowcellBatch <- as.factor(as.character(COVARIATES1$FlowcellBatch))
+#_#COVARIATES1$FlowcellBatch <- as.factor(as.character(COVARIATES1$FlowcellBatch))
 COVARIATES1$Reported_Gender <- as.factor(as.character(COVARIATES1$Reported_Gender))
@@
 # Primary variable of interest
-postAdjustCovars = c('Institution', 'FlowcellBatch', 'Reported_Gender');
+postAdjustCovars = c('Institution', 'Reported_Gender'); #'FlowcellBatch'
 #postAdjustCovars = c('Institution', 'Reported_Gender');
@@
 
-COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 485, replace = TRUE, prob = NULL)))
+COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 496, replace = TRUE, prob = NULL)))
 
@@
 while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
-  COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 485, replace = TRUE, prob = NULL)))
+  ##__##COVARIATES1$Block <- as.factor(as.character(sample(c(1:200), 496, replace = TRUE, prob = NULL)))
   writeLines(paste0('Working on Loop: ', loopCount))
@@
   correlation = parallelDuplicateCorrelation(VOOM.GENE_EXPRESSION,
-
                                              block = COVARIATES1$Block,
+                                             ##__##block = COVARIATES1$Individual_ID,
                                              method = 'lmer')
@@
                                 design=DM1$design, plot=F, 
-
                                 block = COVARIATES1$Block,
+                                ##__##block = COVARIATES1$Individual_ID,
                                 correlation = correlation$cor)
@@
                               weights = VOOM.GENE_EXPRESSION$weights,
-
                               block = COVARIATES1$Block, 
+                              ##__##block = COVARIATES1$Individual_ID,
                               correlation = correlation$cor)
@@
 ```{r sva.adjust}
-
-FactorCovariates <- c("Individual_ID", "FlowcellBatch", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
+# remove  "FlowcellBatch",
+FactorCovariates <- c("Individual_ID", "Institution", "Reported_Gender", "LibraryBatch", "Dx.Tissue", "Dx", "RibozeroBatch")
 ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate", "GenesDetected", "ExpProfEfficiency", "rRNARate", "TotalReads","AlignmentRate", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")
@@
 ```
+
+```{r ACC_Val, include=FALSE, eval=TRUE, cache=FALSE}
+################################################################################
+#CMC ACC DATA
+library(stringr)
+
+Impute <-  as.data.frame( read.table(syn_temp$get('syn21442621')$path, header = T, sep = '\t', row.names = 1 ))
+row.names(Impute)  <- Impute$IID
+Impute <- Impute[ , colnames(Impute)[ (grepl("ENSG", colnames(Impute))) == T ] ]
+Impute <- as.data.frame(t(Impute))
+colnames(Impute) <- gsub( "BP_", "", gsub("0_", "CMC_", colnames(Impute) ))
+
+#Exp--
+Exp <- RESIDUAL.SVA.GENE_EXPRESSION #as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
+rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
+Exp_ACC <- Exp[ ,(grepl("_ACC_", colnames(Exp)))==T ]
+
+#ID--
+ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
+table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )
+
+colnames(Exp_ACC) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_ACC) ))))
+Exp <- Exp_ACC
+#Sync Names
+Padder <- function( names ){
+  #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
+  foo <- do.call( rbind, strsplit(names, '_'))
+  foo[,3] <- str_pad(foo[,3], 5, pad = "0")
+  return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
+}
+colnames(Exp) <- Padder( colnames(Exp) )
+colnames(Impute) <- Padder( colnames(Impute) )
+
+#Align Matices
+Impute <- Impute[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
+Exp <- Exp[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
+Impute <- Impute[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
+Exp <- Exp[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
+
+Correlation <- matrix(0, dim(Exp)[1], 3)
+row.names(Correlation) <- row.names(Impute)
+colnames(Correlation) <- c( "Z", "Correlation", "P-Val")
+
+Exp <- Exp[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
+Impute <- Impute[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
+
+for( Gene in row.names(Impute) ){
+  temp <- na.omit(cbind( as.numeric(Impute[Gene,]), as.numeric(Exp[Gene,]) ))
+  foo <- cor.test( temp[,1], temp[,2] , method = "kendall")
+  Correlation[ Gene, ] <- c( as.numeric(foo$statistic), as.numeric(foo$estimate), as.numeric(foo$p.value) )
+}
+
+Correlation <- cbind( Correlation, "Log10_Pval"= -log10(Correlation[,3]))
+Correlation <- cbind( Correlation, "FDR"= p.adjust( Correlation[,3], method = "fdr", n = 13650) )
+Correlation <- cbind( Correlation, "BH"= p.adjust( Correlation[,3], method = "BH", n = 13650) )
+Correlation <- cbind( Correlation, "BF"= p.adjust( Correlation[,3], method = "bonferroni", n = 13650) )
+
+Correlation <- cbind( Correlation, "FDR_W_Only"= p.adjust( Correlation[,3], method = "fdr", n = dim(Correlation)[1]) )
+Correlation <- cbind( Correlation, "BH_W_Only"= p.adjust( Correlation[,3], method = "BH", n = dim(Correlation)[1]) )
+Correlation <- cbind( Correlation, "BF_W_Only"= p.adjust( Correlation[,3], method = "bonferroni", n = dim(Correlation)[1]) )
+
+Correlation <- as.data.frame(Correlation)
+Correlation$Sig <- 'NO'
+Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'
+table(Correlation$Sig)
+
+setEPS()
+postscript("ACC_Val.eps", onefile = TRUE)
+  ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
+    geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
+    theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") 
+dev.off()
+ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
+    geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
+    theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)")
+
+setEPS()
+postscript("ACC_Cor_All.eps", onefile = TRUE)
+  hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1,
+      main="Correlation of All 6643 Matched Genes in CMC ACC")
+dev.off()
+hist( Correlation$Correlation, breaks = 100, xlab = 'Correlation', las = 1,
+      main="Correlation of All 6643 Matched Genes in CMC ACC")
+
+setEPS()
+postscript("ACC_Cor_gt5Perc.eps", onefile = TRUE)
+  hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
+      breaks = 100, 
+      xlab = 'Correlation', 
+      las = 1,
+      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
+dev.off()
+hist( Correlation[Correlation$FDR_W_Only < 0.05, ]$Correlation, 
+      breaks = 100, 
+      xlab = 'Correlation', 
+      las = 1,
+      main="Correlation of Genes with FDR Corrected P-Value < 0.05")
+```

### 2020-06-10 code/CMC_ExpVal_DataProcessing_deprecated.Rmd
Initial Repo Clean

--- 2020-05-07 code/CMC_ExpVal_DataProcessing.Rmd
@@
 
-# Primary variable of interest
-postAdjustCovars = c('Institution', 'Reported_Gender', 'Dx' ) #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
+# Primary variable of interest - , 'Dx'- 
+postAdjustCovars = c('Institution', 'Reported_Gender' ) #c('Institution', 'Reported_Gender'); #'FlowcellBatch'
 #postAdjustCovars = c('Institution', 'Reported_Gender');
@@
 
+#InstitutionPitt Reported_GenderMale DxOther DxControl DxSCZ
+
 # Get design matrix
@@
 
-#_#DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
+DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
 # Estimate voom weights for dispersion control
@@
             weights = VOOM.WEIGHTS$weights,
+            #_#design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)[ colnames(VOOM.NET.FIT) %in% colnames(VOOM.WEIGHTS$design)] ],
             design = VOOM.WEIGHTS$design[,colnames(VOOM.NET.FIT)],
@@
 ################################################################################
-
 #CMC ACC DATA
@@
   #'@Tissue either "ACC", or "PFC"
-
-  Impute <-  as.data.frame( read.table(syn_temp$get('syn21442621')$path, header = T, sep = '\t', row.names = 1 ))
-  row.names(Impute)  <- Impute$IID
-  Impute <- Impute[ , colnames(Impute)[ (grepl("ENSG", colnames(Impute))) == T ] ]
-  Impute <- as.data.frame(t(Impute))
-  colnames(Impute) <- gsub( "BP_", "", gsub("0_", "CMC_", colnames(Impute) ))
-
-  #Exp--
-  Exp <- RESIDUAL.SVA.GENE_EXPRESSION #as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
-  rownames(Exp) <- do.call( rbind, strsplit(row.names(Exp),'\\.'))[,1]
-  Exp_temp <- Exp[ ,(grepl(paste0("_", Tissue, "_"), colnames(Exp)))==T ]
-  #ID--
-  ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
-  table(colnames(Exp) %in% ID$RNAseq.Sample_RNA_ID )
-
-  if( Tissue == 'PFC' ){
-    colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_PFC_", "_", gsub( "PFC_BP_", "", colnames(Exp_temp) ))))
-  }else{
-    if( Tissue == 'ACC' ){
-      colnames(Exp_temp) <- paste0( "CMC_", gsub( "RNA_", "", gsub("_RNA_ACC_", "_", gsub( "ACC_BP_", "", colnames(Exp_temp) ))))
-    }else{
-      warning('Inproper Tissue Specified')
-    }
-  }
-  Exp <- Exp_temp
-  #Sync Names
-  Padder <- function( names ){
-    #'@names format of 'CMC_PITT_XXXX' ie colnames(Exp)
-    foo <- do.call( rbind, strsplit(names, '_'))
-    foo[,3] <- str_pad(foo[,3], 5, pad = "0")
-    return( paste0(foo[,1], "_", foo[,2], "_", foo[,3] ) )
-  }
-  colnames(Exp) <- Padder( colnames(Exp) )
-  colnames(Impute) <- Padder( colnames(Impute) )
-
-  #Align Matices
-  Impute <- Impute[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
-  Exp <- Exp[ ,colnames(Impute)[ colnames(Impute) %in% colnames(Exp) ] ]
-  Impute <- Impute[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
-  Exp <- Exp[ row.names(Impute)[ row.names(Impute) %in% row.names(Exp) ] ,]
-
-  Correlation <- matrix(0, dim(Exp)[1], 3)
-  row.names(Correlation) <- row.names(Impute)
-  colnames(Correlation) <- c( "Z", "Correlation", "P-Val")
-
-  Exp <- Exp[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
-  Impute <- Impute[ , colnames(Impute)[colnames(Impute) %in% colnames(Exp)] ]
-
-  for( Gene in row.names(Impute) ){
-    temp <- na.omit(cbind( as.numeric(Impute[Gene,]), as.numeric(Exp[Gene,]) ))
-    foo <- cor.test( temp[,1], temp[,2] , method = "kendall")
-    Correlation[ Gene, ] <- c( as.numeric(foo$statistic), as.numeric(foo$estimate), as.numeric(foo$p.value) )
-  }
-
-  Correlation <- cbind( Correlation, "Log10_Pval"= -log10(Correlation[,3]))
-  Correlation <- cbind( Correlation, "FDR"= p.adjust( Correlation[,3], method = "fdr", n = 13650) )
-  Correlation <- cbind( Correlation, "BH"= p.adjust( Correlation[,3], method = "BH", n = 13650) )
-  Correlation <- cbind( Correlation, "BF"= p.adjust( Correlation[,3], method = "bonferroni", n = 13650) )
-
-  Correlation <- cbind( Correlation, "FDR_W_Only"= p.adjust( Correlation[,3], method = "fdr", n = dim(Correlation)[1]) )
-  Correlation <- cbind( Correlation, "BH_W_Only"= p.adjust( Correlation[,3], method = "BH", n = dim(Correlation)[1]) )
-  Correlation <- cbind( Correlation, "BF_W_Only"= p.adjust( Correlation[,3], method = "bonferroni", n = dim(Correlation)[1]) )
-
-  Correlation <- as.data.frame(Correlation)
-  Correlation$Sig <- 'NO'
-  Correlation[ Correlation$FDR_W_Only < 0.05 & Correlation$Correlation > 0 , ]$Sig <- 'YES'
-  Tab <- table(Correlation$Sig)
-
+ Tab
   message( paste0(Tissue, ' Mean Correlatioon: ', mean(Correlation$Correlation)) )
@@
         main="Correlation of Genes with FDR Corrected P-Value < 0.05")
-  return(list( TAB=Tab, Correlation=Correlation, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
+  return(list( TAB=Tab, Sig = Sig, Tot=Total_Hist, Filt=Filt_Hist ))
 }
@@
 PFC_Plots <- Associated( 'PFC' )
-#save.image('Completed_Validation_Analysis.RData')
+
 ```
@@
 
-#ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Completed_Validation_Analysis.RData', name = 'RData object of analysis for ACC Validation', parentId=CODE$properties$id ), activityName = activityName, executed = c( Syns_Used, thisFile) , activityDescription = activityDescription)
-#  all.annotations$tissueTypeAbrv = 'Analysis'
-#  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
-
 ```

### 2020-06-10 code/FUSION.compute_weights_Parallel.R
Removing ignored files

@@ -1,384 +1,0 @@
-# ==== TODO
-# * Make sure BLUP/BSLMM weights are being scaled properly based on MAF
-
-suppressMessages(library("optparse"))
-suppressMessages(library('plink2R'))
-suppressMessages(library('glmnet'))
-suppressMessages(library('methods'))
-
-option_list = list(
-  make_option("--bfile", action="store", default=NA, type='character',
-              help="Path to PLINK binary input file prefix (minus bed/bim/fam) [required]"),
-  make_option("--out", action="store", default=NA, type='character',
-              help="Path to output files [required]"),
-  make_option("--tmp", action="store", default=NA, type='character',
-              help="Path to temporary files [required]"),
-  make_option("--pheno", action="store", default=NA, type='character',
-              help="Path to molecular phenotype file (PLINK format) [optional, taken from bfile otherwise]"),
-  make_option("--PATH_plink", action="store", default="plink", type='character',
-              help="Path to plink executable [%default]"),
-  make_option("--PATH_gcta", action="store", default="gcta_nr_robust", type='character',
-              help="Path to plink executable [%default]"),
-  make_option("--PATH_gemma", action="store", default="gemma", type='character',
-              help="Path to plink executable [%default]"),
-  make_option("--covar", action="store", default=NA, type='character',
-              help="Path to quantitative covariates (PLINK format) [optional]"),
-  make_option("--resid", action="store_true", default=FALSE,
-              help="Also regress the covariates out of the genotypes [default: %default]"),              
-  make_option("--hsq_p", action="store", default=0.01, type='double',
-              help="Minimum heritability p-value for which to compute weights [default: %default]"),
[…]

### 2020-06-10 code/Make_PositionFile_WG.py
add position code

@@ -1,0 +1,89 @@
+#!/usr/bin/python
+
+import sys
+import os
+import re
+import argparse
+import warnings
+
+#Make the .POS file from the weights list and the list of gene starts and stops to FUSION.Assoc.R script
+#'@USAGE': python ../Make_PositionFile.py -GA /fusion_twas-master/Training_CV_Groups/GenePos_Files/Chr21.txt -WL K9.lst -P WEIGHTS/chr21_Weights/ALL/ALL. -T .wgt.RDat -C 21 -o chr21_K9.pos
+def get_args():
+	'''This function will parse and return command-line arguments'''
+	
+	# Assign description to the help doc
+	parser = argparse.ArgumentParser(
+		description='This Script Procces MPRA Read data')
+
+	#Specify arguments
+	parser.add_argument(
+		'-WL', '--WeightsList', type=str, help="List of Weights", required=True)
+	parser.add_argument(
+		'-GA', '--GeneAnnots', type=str, help="List of Gene Annotations", required=True)
+	parser.add_argument(
+		'-P', '--Preceed', type=str, help="String to trim preceeding the ENSG # of the weights list", required=True)
+	parser.add_argument(
+		'-T', '--Trail', type=str, help="String to trim Trailing the ENSG # of the weights list", required=True)
+	parser.add_argument(
+		'-C', '--Chr', type=str, help="Chromosmoe", required=False)
+	#Pipeline output file Necessary in all modes			
+	parser.add_argument(
+		'-o', '--out', type=str, help='Specify the out file to store Pipeline Log', required=True)
+
+	#Array for all arguments passed to script
+	args = parser.parse_args()
+	
+	#Assign args to variables	
+	WL = args.WeightsList
+	GA = args.GeneAnnots
+	
+	P = args.Preceed
+	T = args.Trail
+
+	Chr = args.Chr
+	O = args.out
+
+	# Return all variable values
+	return WL, GA, P, T, Chr, O
+
+#Match return values from get_arguments() and assign to their respective variables
+WL, GA, P, T, Chr, O = get_args()
+
+if Chr == "ALL":
+	Chr = [ str(range(1,23)) ]
+else:
+	pass
+
+GRef = {}
[…]

### 2020-06-10 code/Make_PositionFile_WG.py
credit code

@@ -1,4 +1,5 @@
 #!/usr/bin/python
+#Altered code from: Gusev et al. “Integrative approaches for large-scale transcriptome-wide association studies” 2016 Nature Genetics
 
 import sys
 import os

### 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
Full Code Process

---
title: Covariate Analysis of ROSMAP Reprocessed counts
author: 'JKG - Adapted from: Thanneer Perumal'
output: html_notebook
editor_options:
  chunk_output_type: console
---
Date of analysis update: "`r date()`"

| *Synapse ID* | *File Name* |
|  -----------------------------------------  |   ---------                      |
| syn3382527.7 | | 
| syn4300313.1 | | 
| ----Old Lengths syn8449369.2 | | 
| syn21156161 | | 
| syn7116000.1 | | 
| ----OLDCOUNTS syn8691134.1 | | 
| ----OLDCOUNTS syn21075911 | | 
| syn23593968 | | 
| ----SynID Translator | | 
| syn21075913 | | 
| syn3191087.3 | | 
| ----OLDMetrics syn8698240.2 Version 2 | | 
| syn21075912  | | 
| Full MetaData | |
| syn23573928 ||

### Load Libraries
```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file
## Load required libraries
library(CovariateAnalysis) # get the package from devtools::install_github('th1vairam/CovariateAnalysis@dev')
library(data.table)
library(plyr)
library(tidyverse)
library(psych)
library(limma)
library(edgeR)
library(biomaRt)
library(RColorBrewer)
library(cqn)
library(knitr)
library(doParallel)
library(foreach)
library(githubr)
cl = makeCluster(detectCores()-2)
registerDoParallel(cl)
options(xtable.type="html")
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE)
```

### Data download
Obtain count matrix and metadata from synapse
```{r download.data}
# Download expression data
COUNT_ID <- 'syn23593968';
ALL_USED_IDs <- COUNT_ID
COUNT_OBJ <- syn_temp$get(COUNT_ID, version = 1)
#COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
COUNT <- as.data.frame(data.table::fread(COUNT_OBJ$path, header=T, sep='\t', check.names = F))#, row.names = 1)
row.names(COUNT) <- as.character(COUNT$feature)
COUNT <- COUNT[ ,(colnames(COUNT) %in% 'feature')==F ]
COUNT <- as.matrix(COUNT)

Provenance <- 'syn21075913'
Prov <- syn_temp$get(Provenance, version = 1)
ALL_USED_IDs[length(ALL_USED_IDs)+1] = Provenance
Translator <- read.csv(Prov$path, header=T, row.names = 1)
#colnames(COUNT) <- as.character( Translator[ colnames(COUNT), ][,2] )

#COUNT <- COUNT[ row.names(COUNT)[ (row.names(COUNT) %in% c('N_unmapped', 'N_multimapping', 'N_noFeature', 'N_ambiguous'))==F] , ]
#COUNT[,grep('150_120419', colnames(COUNT))[2]] = NULL

#Need to filter low counts here to remove the PAR_Y Regions
COUNT <- COUNT[ rowSums(COUNT[,] > 0) / (ncol(COUNT)) >= 0.05, ]

# Convert rownames of counts from tracking id to ensemble gene id
tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
  dplyr::mutate(ID = Gene.ID) %>%
  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
rownames(tmp) = tmp$Gene.ID
rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']

# Download expression data
Meta_ID <- 'syn23573928';
ALL_USED_IDs <- c( Meta_ID, ALL_USED_IDs )
Meta_OBJ <- syn_temp$get( Meta_ID, version = 2 )
Meta <- read.csv( Meta_OBJ$path, header=T, check.names = F, row.names = 1 )

#Filter Out Sample Swaps
Meta <- Meta[ Meta$FailQC_SampleSwapped == 0, ]
COUNT <- COUNT[ ,row.names(Meta) ]

 # table( Meta$tissue, Meta$study )      
 #       MAP ROS
 # ACC   387 338
 # DLPFC 639 463
 # PCC   388 265

METADATA <- Meta[ ,c( "individualID", "apoe4", "batch", "notes", "tissue", "diagnosis", "race", "pmi", "sex", "race", "spanish", "braaksc", "ceradsc", "cogdx", "dcfdx_lv", "pmi", "rincontinuous", "rin2", "age_death", "pct_pf_reads_aligned", "pct_coding_bases", "pct_intergenic_bases", "pct_intronic_bases" ) ]

GENE.PARAM <- syn_temp$get('syn23625835', version = 4)$path %>% 
  data.table::fread(data.table = T)
ALL_USED_IDs = c(ALL_USED_IDs, 'syn23625835')
GENE.LEN = dplyr::select(GENE.PARAM, ensembl_gene_id, gene_length) %>% 
  unique() 
rownames(GENE.LEN) = GENE.LEN$ensembl_gene_id
GENE.GC = dplyr::select(GENE.PARAM, ensembl_gene_id, percentage_gene_gc_content) %>% 
  unique() 
rownames(GENE.GC) = GENE.GC$ensembl_gene_id

#Might need to rename
#percentage_gc_content - gene.length
```

### Data preprocessing
```{r preprocess.data, cache=TRUE}
# Remove samples with no cogdx, RIN, PMI scores and age_death
METADATA <- METADATA[, (colnames(METADATA)%in%'pmi.1')==F]

colnames(METADATA)[ colnames(METADATA) == 'race.1' ] <- 'race'
colnames(METADATA)[ colnames(METADATA) == 'rincontinuous' ] <- 'rin'

METADATA <- as.data.frame( cbind( Sampleid = row.names(METADATA), METADATA[ ,colnames(METADATA) ] ))

METADATA <- METADATA %>%
  ungroup %>%
  dplyr::filter(Sampleid %in% colnames(COUNT)) %>%
  dplyr::filter(!is.na(cogdx), !is.na(braaksc), !is.na(ceradsc)) %>%
  dplyr::filter(!is.na(rin)) %>%
  dplyr::filter(!is.na(pct_intronic_bases)) %>%
  dplyr::filter(!is.na(pmi)) %>%
  dplyr::filter(!is.na(age_death)) %>%
  as.data.frame()

# Add harmonised case-control status
METADATA$cogdx <- as.numeric(METADATA$cogdx)
METADATA$braaksc <- as.numeric(METADATA$braaksc)
METADATA$ceradsc <- as.numeric(METADATA$ceradsc)

METADATA$Diagnosis = 'OTHER'
METADATA$Diagnosis[METADATA$cogdx == 1 & METADATA$braaksc <= 3 & METADATA$ceradsc >= 3] = 'CONTROL'
METADATA$Diagnosis[METADATA$cogdx == 4 & METADATA$braaksc >= 4 & METADATA$ceradsc <= 2] = 'AD'

METADATA <- METADATA[ , (colnames(METADATA) %in% "diagnosis") == F ]

```
Dorsolateral prefrontal cortex of `r dim(COUNT)[2]` subjects from the ROS and MAP cohorts are used for the analysis. Following sample are removed due to missing metadata `r paste(removedIDs, collapse = ',')`

### Covariate clustering
Determine relationship between covariates
```{r covariates.clustering, cache=FALSE}
METADATA$Tissue.Diagnosis = paste(METADATA$tissue, METADATA$Diagnosis, sep = '.')
METADATA$Tissue.APOE4 = paste(METADATA$tissue, METADATA$apoe4, sep = '.')

primaryVariable <- c("cogdx", "Tissue.Diagnosis", "Tissue.APOE4", "dcfdx_lv", "braaksc", "ceradsc" )

#"Diagnosis", "apoe4",
FactorCovariates <- c( "Sampleid", "Tissue.Diagnosis", "Tissue.APOE4", "individualID", "Diagnosis", "batch", "sex", "race", "spanish", "cogdx", "cogdx", "ceradsc", "braaksc", "notes", "tissue", "dcfdx_lv" )

ContCovariates <- c( "rin", "rin2", "age_death", "pmi", "pct_pf_reads_aligned", 
                     "pct_coding_bases", "pct_intronic_bases", "pct_intergenic_bases" )

# Find inter relation between factor covariates
COVARIATES = METADATA[,c(FactorCovariates,ContCovariates),drop=F]
COVARIATES <- data.frame(lapply(COVARIATES,function(x){x <- sapply(x,function(y){str_replace_all(as.character(y),'\\+','')})}))
rownames(COVARIATES) <- METADATA$Sampleid
# Convert factor covariates to factors
#_#COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.character)
COVARIATES[,ContCovariates] = lapply(COVARIATES[,ContCovariates], as.numeric)
if('cogdx.1' %in% colnames(COVARIATES)){
  COVARIATES <- COVARIATES[ ,(colnames(COVARIATES) %in% 'cogdx.1')==F ]
}
COVARIATES <- COVARIATES[ ,(colnames(COVARIATES) %in% 'Sampleid')==F ]
```

Correlation/association between covariates at an FDR <= 0.1
```{r covariates.correlation, cache=FALSE, fig.width=9, fig.height=6}
COVARIATES.CORRELATION = CovariateAnalysis::getAssociationStatistics(COVARIATES, PVAL = 0.05)
draw(COVARIATES.CORRELATION$plot, heatmap_legend_side = 'left', padding  = unit(c(18,2,2,18), 'mm')) 
```

### Explore metadata
```{r data.explore, cache=FALSE, fig.width = 10, fig.height = 14}
my.theme = theme(legend.position = 'top', axis.text.x = element_text(angle = 90, hjust = 1))
# RIN
p = list()
p[[1]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = rin)) + geom_boxplot()
p[[1]] = p[[1]] + ggtitle('RIN') + my.theme
# Age Of Death
p[[2]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(age_death))) + geom_boxplot()
p[[2]] = p[[2]] + ggtitle('AOD') + my.theme
# PMI
p[[3]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(pmi))) + geom_boxplot()
p[[3]] = p[[3]] + ggtitle('PMI') + my.theme
# Ribosomal bases
p[[4]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(pct_pf_reads_aligned))) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Percent of pf aligned reads Bases') + my.theme
# Intronic bases
p[[5]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(pct_intronic_bases))) + geom_boxplot()
p[[5]] = p[[5]] + ggtitle('Fraction Intronic Bases') + my.theme
# Intergenic bases
p[[6]] = ggplot(COVARIATES, aes(x = Tissue.Diagnosis, y = as.numeric(pct_intergenic_bases))) + geom_boxplot()
p[[6]] = p[[6]] + ggtitle('Fraction Intergenic Bases') + my.theme
multiplot(plotlist = p, cols = 3)
```

### Filter genes
* Remove genes that have less than 1 cpm counts in at least 50% of samples per Diagnosis
* Remove genes with missing gene length and percentage GC content
```{r filter.genes}
genesToAnalyze = COVARIATES %>%
  rownameToFirstColumn('SampleID') %>%
  dlply(.(Tissue.Diagnosis), .fun = function(mtd, count){
    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
                                                     MIN_GENE_CPM=1, 
                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
    processed.counts$filteredExprMatrix$genes
  }, COUNT)
genesToAnalyze = unlist(genesToAnalyze) %>% 
  unique() %>%
  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gene_gc_content)]) %>%
  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene_length)]) %>%
  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))
PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
                                                 MIN_GENE_CPM=0, 
                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)

Ensemble2HGNC <- GENE.PARAM[ GENE.PARAM$ensembl_gene_id %in% PROCESSED_COUNTS$filteredExprMatrix$genes$genes, ]

summary(factor(Ensemble2HGNC$gene_biotype)) %>%
  rownameToFirstColumn('Biotype') %>%
  dplyr::rename(fraction = DF) %>%
  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
  dplyr::filter(fraction >= 0.01) %>%
  kable
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

### Library Normalisation
Library normalisation is performed using cqn (conditional quantile normalisation)
```{r cqn}
GENE.GC <- as.data.frame(GENE.GC)
row.names(GENE.GC) <- GENE.GC$ensembl_gene_id
GENE.LEN <- as.data.frame(GENE.LEN)
row.names(GENE.LEN) <- GENE.LEN$ensembl_gene_id
# Compute offset for gene length and gc content
CQN.GENE_EXPRESSION = cqn(PROCESSED_COUNTS$filteredExprMatrix$counts, 
                          x = GENE.GC[ PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'percentage_gene_gc_content'],#$percentage_gene_gc_content,
                          lengths = GENE.LEN[PROCESSED_COUNTS$filteredExprMatrix$genes$genes, 'gene_length'],
                          lengthMethod = "smooth", 
                          verbose = FALSE)
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$y + CQN.GENE_EXPRESSION$offset
```

### Outlier Analysis
#### Sample outliers
Outlier analysis is performed before library normalisation with raw cpm counts
```{r outlier.analysis, cache = FALSE, fig.width = 10}
indToRemove = c('380_120503', '500_120515')
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID')) %>%
  dplyr::mutate(label = SampleID) %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.')
plotdata$label[!(plotdata$SampleID %in% indToRemove)] = ''
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(shape=notes, color=batch, size=rin))
p <- p + theme_bw() + theme(legend.position="top") 
p <- p + facet_grid(Tissue~.+Diagnosis, scales = 'free')
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p

# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  dplyr::left_join(COVARIATES %>%
                     rownameToFirstColumn('SampleID'))
p = ggplot(tmp1 %>%
             dplyr::filter(SampleID %in% indToRemove),
           aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'top')
p
indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
COVARIATES = COVARIATES[indToRetain,]
tmp = COVARIATES %>%
  tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.') %>%
  dplyr::group_by(Diagnosis, Tissue) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

Based on the expression pattern following samples were tagged as outliers: `r paste(indToRemove, collapse = ', ')`

Distribution of samples are: `r kable(tmp)`

#### Gene outliers
Assign NA values to genes that are above and below 3 std deviation of its distribution
```{r winsorise.data}
# Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
LOG.CPM = apply(CQN.GENE_EXPRESSION$E, 1, function(x){
  mn = mean(x, na.rm = T)
  std.dev = sd(x, na.rm = T)

  x[x < (mn-3*std.dev)] = NA
  x[x > (mn+3*std.dev)] = NA
  return(x)
}) %>% t
CQN.GENE_EXPRESSION$E = LOG.CPM
CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
LIB.SIZE = colSums(PROCESSED_COUNTS$filteredExprMatrix$counts)
NEW.COUNTS = (2^LOG.CPM) * t(replicate(dim(LOG.CPM)[1], LIB.SIZE))/1e6
```

### Sample clustering
PCA based clustering of samples
```{r decompse.normalise.data, cache=FALSE, fig.height=8, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
# Plot first 2 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata[row.names(COVARIATES),], rownameToFirstColumn(COVARIATES, 'SampleID'))
p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=batch, shape=notes, size=rin))
p <- p + theme_bw() + theme(legend.position="right")+ facet_grid(.~tissue, scales = 'free_y')
p
```

Tree based clustering of samples
```{r decompse.normalise.data.1, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES.tmp = data.matrix(COVARIATES[,c("tissue", "notes","batch", "sex", "Tissue.Diagnosis")])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(CQN.GENE_EXPRESSION$E.no.na)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Distribution of samples (log cpm)
```{r lcpm.dist, cache=FALSE, fig.height=10, fig.width=20}
# Plot abberent distribution of logcpm counts
tmp1 = CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('Gene.ID') %>%
  tidyr::gather(SampleID, logCPM, -Gene.ID) %>%
  left_join(COVARIATES %>%
              tidyr::separate(Tissue.Diagnosis, c('Tissue', 'Diagnosis'), sep = '\\.') %>%
              rownameToFirstColumn('SampleID'))
p = ggplot(tmp1, aes(x = logCPM, color = SampleID)) + geom_density() 
p = p + theme(legend.position = 'NONE') + facet_grid(.~Diagnosis, scale = 'free')
p
```

Coexpression of genes 
```{r coexp1, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(CQN.GENE_EXPRESSION$E.no.na))
Temp_hist <- hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates are used to find significant covariates
```{r preadj.covariates, cache=FALSE}
COVARIATES <- COVARIATES[, (colnames(COVARIATES) %in% c("tissue"))==F] %>% 
  tidyr::separate(Tissue.APOE4, c('Tissue', 'apoe4'), sep = '\\.') %>%
  tidyr::separate(Tissue.Diagnosis, c('tissue', 'Diagnosis'), sep = '\\.')
COVARIATES$Tissue.APOE4 <- as.factor( paste0(as.character(COVARIATES$tissue), 
                                             '.', 
                                             as.character(COVARIATES$apoe4) ) )
COVARIATES$Tissue.Diagnosis <- as.factor( paste0(as.character(COVARIATES$tissue) ,
                                                 '.', 
                                                 as.character(COVARIATES$Diagnosis) ) )
# Find correlation between PC's of gene expression with covariates
COVARIATES <- COVARIATES[,  c( "individualID", "tissue", "Diagnosis", 'Tissue.Diagnosis', 'Tissue.APOE4',
                                                     "race", "spanish", "braaksc", "ceradsc",
                                                     "cogdx", "dcfdx_lv", "apoe4", "sex", "batch",
                                                     "notes", "pmi", "rin", "rin2", "age_death",
                                                     "pct_pf_reads_aligned","pct_pf_reads_aligned",
                                                     "pct_intronic_bases", "pct_intronic_bases",
                               "pct_intergenic_bases", "pct_coding_bases"
                                                              )]
COVARIATES$tissue <- as.factor(COVARIATES$tissue)
COVARIATES$Diagnosis <- as.factor(COVARIATES$Diagnosis)
COVARIATES$apoe4 <- as.factor(COVARIATES$apoe4)

COVARIATES <- COVARIATES[colnames(CQN.GENE_EXPRESSION$E.no.na),]

COVARIATES <- COVARIATES[ , colnames(COVARIATES)[grepl('[.]1',colnames(COVARIATES))==F ]]

preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E.no.na, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

Significant covariates to adjust at FDR 0.1 are `r preAdjustedSigCovars$significantCovars`
```{r preadj.covariates.plot, cache=FALSE, fig.width=12, fig.height=8}
preAdjustedSigCovars[["PC_res"]][[2]]$plotData
```

### Normalisation (iterative design)
Since many covariates are correlated, re-normalising and re-adjusting COUNTS with an iterative design matrix
1. Adding Batch and Sex a priori to variable selection
2. Primary variable of interest Diagnosis is excluded from the pool of available covariates for selection
```{r iterative.norm, cache=FALSE, results='asis'}
# Primary variable of interest
postAdjustCovars = c('batch', 'sex');
# Assign residual covariates
residualCovars = setdiff(preAdjustedSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, 'individualID', 'tissue' ))
residualSigCovars = preAdjustedSigCovars
covariatesEffects = preAdjustedSigCovars$Effects.significantCovars[residualCovars]

#_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
loopCount = 0 
while(length(residualSigCovars$significantCovars)!=0 && loopCount <= 20){
  writeLines(paste('Using following covariates in the model:',
                   paste(postAdjustCovars, collapse=', '),
                   'as fixed effects'))

  # Post adjusted design matrix
  DM1 = getDesignMatrix(COVARIATES[,postAdjustCovars,drop=F],Intercept = F)
  DM1$design = DM1$design[,linColumnFinder(DM1$design)$indepCols]

  # Estimate voom weights for dispersion control
  cnts = NEW.COUNTS
  cnts[is.na(cnts)] = 0
  VOOM.GENE_EXPRESSION = voom(cnts, 
                              design=DM1$design, 
                              plot=F,
                              na.rm = T)

  # Fit linear model using new weights and new design
  VOOM.ADJUSTED.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                            design = DM1$design,
                            weights = VOOM.GENE_EXPRESSION$weights)

  # Residuals after normalisation
  RESIDUAL.GENE_EXPRESSION = residuals.MArrayLM(VOOM.ADJUSTED.FIT,
                                                CQN.GENE_EXPRESSION$E)

  # Residual covariates to choose from
  residCovars <- setdiff(c(FactorCovariates,ContCovariates), c(postAdjustCovars, primaryVariable, "individualID", "Sampleid"))

  # Find PC of residual gene expression and significant covariates that are highly correlated with PCs
  expr = RESIDUAL.GENE_EXPRESSION
  expr[is.na(expr)] = 0
  residualSigCovars = runPCAandPlotCorrelations(expr, 
                                                COVARIATES[, residCovars, drop=F], 
                                                'adjusted design(voom-normalized)',
                                                isKeyPlot=TRUE)

  # Add postadjusted covariates (if any)
  residCovars = setdiff(residualSigCovars$significantCovars, c(postAdjustCovars, primaryVariable, "tissue"))
  covariatesEffects = residualSigCovars$Effects.significantCovars[residCovars]

  postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects)))
  loopCount = loopCount + 1
}
modelStr <- paste(paste(gsub('_','\\\\_',postAdjustCovars), collapse=', '),
                  'as fixed effects')
tmp <- paste('Using following covariates in the final model:', modelStr)
```
`r tmp`

### Sanity check
```{r residual.adj, cache=FALSE, fig.width=12, fig.height=8}
# Find PC of residual gene expression and significant covariates that are highly correlated with PCs
#COVARIATES$tissue <- as.factor(COVARIATES$tissue)
#COVARIATES$Diagnosis <- as.factor(COVARIATES$Diagnosis)
#COVARIATES$Tissue <- as.factor(COVARIATES$Tissue)
#COVARIATES$apoe4 <- as.factor(COVARIATES$apoe4)

#COVARIATES <- COVARIATES[ ,(colnames(COVARIATES) %in% 'pct_intronic_bases.1')==F ]
residualSigCovars = runPCAandPlotCorrelations(expr, 
                                              COVARIATES[colnames(expr),],
                                              'adjusted design(voom-normalized)',
                                              isKeyPlot=TRUE)
residualSigCovars[["PC_res"]][[2]]$plotData
```
Coexpression of genes 
```{r coexp2, cache=FALSE, fig.height=5, fig.width=5}
cr = cor(t(expr))
Temp_Histb <- hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
hist(cr, main = 'Distribution of correlation between genes', xlab = 'Correlation')
```
PCA of residual data
```{r decompse.normalise.data2.1, cache=FALSE, fig.height=6, fig.width=8, results='asis'}
# Find principal components of expression to plot
PC <- prcomp(expr, scale.=T, center = T)
# Plot first 4 PCs
plotdata <- data.frame(SampleID=rownames(PC$rotation), 
                       PC1=PC$rotation[,1], 
                       PC2=PC$rotation[,2])
plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, 'SampleID'))
p <- ggplot(plotdata, aes(x=PC1, y=PC2)) 
p <- p + geom_point(aes(color=batch, shape=notes, size=rin))
p <- p + theme_bw() + theme(legend.position="right") + facet_grid(.~tissue, scales = 'free_y')
p
```
Tree based clustering of residual data
```{r decompse.normalise.data2.2, cache=FALSE, fig.height=6, fig.width=10, results='asis'}
# Eucledian tree based analysis
COVARIATES$Tissue.Diagnosis <- as.factor( paste0( COVARIATES$tissue, '.', COVARIATES$Diagnosis) )
COVARIATES$Tissue.APOE4 <-as.factor( paste0( COVARIATES$tissue, '.', COVARIATES$apoe4) )
COVARIATES.tmp = data.matrix(COVARIATES[,c('batch', 'tissue', 'apoe4', 'Diagnosis','sex', primaryVariable)])
COVARIATES.tmp[is.na(COVARIATES.tmp)] = 0
tree = hclust(as.dist(t(expr)))
cols = WGCNA::labels2colors(COVARIATES.tmp);
WGCNA::plotDendroAndColors(tree, 
                           colors = cols, 
                           dendroLabels = FALSE, 
                           abHeight = 0.80, 
                           main = "Sample dendrogram",
                           groupLabels = colnames(COVARIATES.tmp))
```

### Adjust data with covariates for Network Analysis
Identified covariates are regressed out from the expression matrix for network analysis
```{r network.adjust}
# Get design matrix
DESIGN.NET = getDesignMatrix(COVARIATES[, postAdjustCovars, drop = F], Intercept = F)
DESIGN.NET = DESIGN.NET$design[,linColumnFinder(DESIGN.NET$design)$indepCols]
# Estimate voom weights for dispersion control
cnts = NEW.COUNTS
cnts[is.na(cnts)] = 0
VOOM.NET.WEIGHTS = voom(cnts, design=DESIGN.NET, plot=F)
# Fit linear model using new weights and new design
VOOM.NET.FIT = lmFit(CQN.GENE_EXPRESSION$E,
                     design = DESIGN.NET,
                     weights = VOOM.NET.WEIGHTS$weights)
# Residuals after normalisation
RESIDUAL.NET.GENE_EXPRESSION = residuals.MArrayLM(VOOM.NET.FIT,
                                                  CQN.GENE_EXPRESSION$E)
```

### SVA Adjustments for eQTL analysis
Conditioned on primary variable (Tissue.Diagnosis) and identified covariates estimate surrogate variables using SVA package
```{r sva.adjust, cache=FALSE }
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Estimate voom weights for dispersion control
cnts = NEW.COUNTS
cnts[is.na(cnts)] = 0
VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
# Fit linear model using new weights and new design
FIT = lmFit(CQN.GENE_EXPRESSION$E,
            design = DESIGN$design,
            weights = VOOM.WEIGHTS$weights)
# Get (null) design matrix
MODEL0 = DESIGN$design[,-grep(primaryVariable[2],colnames(DESIGN$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DESIGN$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]
# Calculate the number of surrogate variables (be method)
# NUM.SV = sva::num.sv(CQN.GENE_EXPRESSION$E, MODEL1, method = 'be', seed = 123456, B = 30)
# Get residuals from differential expression model
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(FIT, CQN.GENE_EXPRESSION$E)
# Compute actual variance of all principal components
expr = RESIDUAL.SVA.GENE_EXPRESSION
expr[is.na(expr)] = 0
tmp = svd(expr)
actual.var = tmp$d^2/sum(tmp$d^2)
# Compute permuted variance of all principal components
permuted.var = foreach(i = 1:20, .combine = rbind) %dopar% {
  tmp.residual = t(apply(expr, 1, sample, replace = FALSE))
  tmp = svd(tmp.residual)
  permuted.var = tmp$d^2/sum(tmp$d^2)
}
permuted.var = apply(permuted.var, 2, mean)
NUM.SV = sum(actual.var >= permuted.var[1])
# Plot variance components
var.comp = data.frame(component = 1:length(actual.var), 
                      residual = actual.var, 
                      permuted.residual = permuted.var) %>%
  tidyr::gather(data, value, -component)
p = ggplot(var.comp %>% filter(component <= round(NUM.SV*1.3)), aes(x = component, y = value, color = data)) + geom_point()
p = p + geom_hline(yintercept=permuted.var[1], linetype = 'dashed') + xlab('Singular Dimension Index')
p = p + geom_vline(xintercept=NUM.SV, linetype = 'dashed') + ylab('Fraction of Variance Explained')
p = p + theme(legend.position = c(0.8, 0.8), legend.title = element_blank())
p

# Estimate surrogate variables
SURR.VAR = sva::sva(CQN.GENE_EXPRESSION$E.no.na, 
                    MODEL1, MODEL0, n.sv = NUM.SV, B = 30)$sv
SURR.VAR = data.frame(SURR.VAR)
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
rownames(SURR.VAR) = rownames(MODEL1)
# Re-estimate voom weights
VOOM.SVA.WEIGHTS = voom(cnts, 
                        design = cbind(MODEL1, SURR.VAR), plot=F)
# Fit linear model using new weights and new design
VOOM.SVA.FIT = lmFit(CQN.GENE_EXPRESSION$E, 
                     design = cbind(MODEL1, SURR.VAR),
                     weights = VOOM.SVA.WEIGHTS$weights)
# Residuals after normalisation
RESIDUAL.SVA.GENE_EXPRESSION = residuals.MArrayLM(VOOM.SVA.FIT,
                                                  CQN.GENE_EXPRESSION$E)
# Add variable of interest back to the residuals
varsToAddIn = grep("Diagnosis", colnames(MODEL1), value = T)
RESIDUAL.SVA.GENE_EXPRESSION = RESIDUAL.SVA.GENE_EXPRESSION + 
  VOOM.SVA.FIT$coefficients[,varsToAddIn] %*% t(VOOM.SVA.FIT$design[,varsToAddIn])
```

### Differential expression analysis (with cogdx as primary variable)
Differential expression is performed on the primary variable by controlling for covariates identified above

Interpretation of cogdx scores
1. NCI, No cognitive impairment (No impaired domains)
2. MCI, Mild cognitive impairment (One impaired domain) and NO other cause of CI
3. MCI, Mild cognitive impairment (One impaired domain) AND another cause of CI
4. AD, Alzheimer's disease and NO other cause of CI (NINCDS PROB AD)
5. AD, Alzheimer's disease AND another cause of CI (NINCDS POSS AD)
6. Other dementia. Other primary cause of dementia

Genes that are differentially expressed at an FDR <= 0.05 are
```{r diff.exp, fig.height=6, fig.width=18, cache=FALSE}

COVARIATES.tmp = COVARIATES
COVARIATES.tmp$Tissue.cogdx <- as.factor(paste0( COVARIATES.tmp$tissue, '.', COVARIATES.tmp$cogdx ))
"tissue"
DESIGN = getDesignMatrix( COVARIATES.tmp[, c("Tissue.cogdx", postAdjustCovars[ (postAdjustCovars %in% c( "dcfdx_lv","braaksc","ceradsc" ))==F ]), drop = F], Intercept = F)
ind = grep('tissue', colnames(DESIGN$design))

DESIGN$design[,ind] = DESIGN$design[,ind] * as.numeric(COVARIATES.tmp[,'cogdx'])
colnames(DESIGN$design)[ind] = paste0(colnames(DESIGN$design),'cogdx')
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES$individualIdentifier, 
                    correlation = correlation$cor)

VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS)
# Fit contrast
contrast = makeContrasts(contrasts = c("Tissue.cogdxACC.2-Tissue.cogdxACC.1",
                                       "Tissue.cogdxACC.4-Tissue.cogdxACC.1",
                                       "Tissue.cogdxACC.4-Tissue.cogdxACC.2",
                                       "Tissue.cogdxDLPFC.2-Tissue.cogdxDLPFC.1",
                                       "Tissue.cogdxDLPFC.4-Tissue.cogdxDLPFC.1",
                                       "Tissue.cogdxDLPFC.4-Tissue.cogdxDLPFC.2",
                                       "Tissue.cogdxPCC.2-Tissue.cogdxPCC.1",
                                       "Tissue.cogdxPCC.4-Tissue.cogdxPCC.1",
                                       "Tissue.cogdxPCC.4-Tissue.cogdxPCC.2"),
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
# Get differnetial expression
DE = lapply(1:9, function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = gsub("Tissue.","", colnames(contrast))
DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('Tissue','',Comparison),
                Study = 'ROSMAP',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  dplyr::rename(Tissue = Comparison) %>%
  dplyr::mutate(Comparison = Tissue) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
              unique())

DE$Tissue <- gsub( 'cogdx','', do.call(rbind, strsplit( do.call(rbind,strsplit(DE$Tissue,'-'))[,2],
                                      '[.]'))[,1])
DE$Comparison <- gsub( 'ACC.','', DE$Comparison)
DE$Comparison <- gsub( 'PCC.','', DE$Comparison)
DE$Comparison <- gsub( 'DLPFC.','', DE$Comparison)

DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
tmp = DE %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue) %>%
  group_by(Tissue, Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)
p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position = 'top')
p = p + facet_grid(Comparison+.~Tissue, scales = 'free')
p
all.diff.exp = list(cogdx = DE)
all.fit = list(cogdx = FIT)
```

### Differential expression analysis (with Diagnosis as primary variable)
Differential expression is performed on the primary variable by controlling for covariates identified above

Interpretation of Diagnosis
1. AD: cogdx = 4, braaksc >= 4 and ceradsc <= 2
2. CONTROL: cogdx = 1, braaksc <= 3 and ceradsc >= 3
3. OTHER: All the other samples

Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
```{r diff.exp1, fig.height=6, fig.width=18, cache=FALSE}
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], postAdjustCovars[ (postAdjustCovars %in% c( "dcfdx_lv","braaksc","ceradsc" ))==F ]), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES$individualIdentifier, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS)
# Fit contrast
cntr = c()
for (region in c('ACC','PCC','DLPFC')){
  tmp = combn(paste0('Tissue.Diagnosis', region, '.', c('AD', 'OTHER', 'CONTROL')),2)
  cntr = c(cntr, apply(tmp, 2, paste, collapse = '-'))
}
contrast = makeContrasts(contrasts=cntr,
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
# Get differnetial expression
DE = lapply(1:9, function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = colnames(contrast)
DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
                Study = 'ROSMAP',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
  tidyr::separate(from.state, c('Tissue','reference'), sep = '\\.') %>%
  tidyr::separate(to.state, c('Tissue1','against'), sep = '\\.') %>%
  dplyr::mutate(Comparison = paste(reference, against, sep = '-')) %>%
  dplyr::select(-Tissue1) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
tmp = DE %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue) %>%
  group_by(Tissue, Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)
p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
p = p + facet_grid(Tissue+.~Comparison, scales = 'fixed')
p
all.diff.exp = c(all.diff.exp, list(Diagnosis = DE))
all.fit = c(all.fit, list(Diagnosis = FIT))
```

### Associate differential expression results with gc content, gene length and average expression
```{r associate.de, fig.height=10, fig.width=15}
pl = list()
pl[[1]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
                 aes(x = log10(gene_length), y = logFC, color = Direction)) + geom_point() 
pl[[1]] = pl[[1]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = log10(gene_length), y = logFC))
pl[[1]] = pl[[1]] + facet_grid(Tissue~.+Comparison) + scale_color_manual(values = c('green','grey','red'))
pl[[1]] = pl[[1]] + theme(legend.position = 'top')
pl[[2]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
                 aes(x = percentage_gene_gc_content, y = logFC, color = Direction)) + geom_point()
pl[[2]] = pl[[2]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = percentage_gene_gc_content, y = logFC))
pl[[2]] = pl[[2]] + facet_grid(Tissue~.+Comparison) + scale_color_manual(values = c('green','grey','red'))
pl[[2]] = pl[[2]] + theme(legend.position = 'top')
pl[[3]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
                 aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
pl[[3]] = pl[[3]] + geom_smooth(method = 'loess', inherit.aes = FALSE, aes(x = AveExpr, y = logFC))
pl[[3]] = pl[[3]] + facet_grid(Tissue~.+Comparison) + scale_color_manual(values = c('green','grey','red'))
pl[[3]] = pl[[3]] + theme(legend.position = 'top')
multiplot(plotlist = pl, cols = 3)

```

### Differential expression analysis (with APOE status as primary variable)
Differential expression is performed on the primary variable by controlling for covariates identified above

Interpretation of apoe_genotype
1. 0: No apoe4 allele
2. 1: 1 apoe4 allele
3. 2: 2 apoe4 allele

Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
```{r diff.exp2, fig.height=6, fig.width=18, cache=FALSE}
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[3], postAdjustCovars[ (postAdjustCovars %in% c( "dcfdx_lv","braaksc","ceradsc" ))==F ]), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES$individualIdentifier, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS)
# Fit contrast
cntr = c()
for (region in c('ACC','PCC','DLPFC')){
  tmp = combn(paste0('Tissue.APOE4', region, '.', c('0', '1', '2')),2)
  cntr = c(cntr, apply(tmp, 2, paste, collapse = '-'))
}
contrast = makeContrasts(contrasts=cntr,
                         levels = colnames(FIT$coefficients))
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = colnames(contrast)

DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('Tissue.APOE4','',Comparison),
                Study = 'ROSMAP',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  tidyr::separate(Comparison, c('from.state','to.state'), sep = '-') %>%
  tidyr::separate(from.state, c('Tissue','reference'), sep = '\\.') %>%
  tidyr::separate(to.state, c('Tissue1','against'), sep = '\\.') %>%
  dplyr::mutate(Comparison = paste(reference, against, sep = '-')) %>%
  dplyr::select(-Tissue1) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
tmp = DE %>%
  dplyr::select(ensembl_gene_id, Comparison, Direction, Tissue) %>%
  group_by(Tissue, Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)
p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
p = p + facet_grid(Tissue+.~Comparison, scales = 'fixed')
p
all.diff.exp = c(all.diff.exp, list(APOE4 = DE))
all.fit = c(all.fit, list(APOE4 = FIT))
```

### Differential expression analysis (with Diagnosis and Sex) 
Differential expression is performed on the Diagnosis x Sex variable by controlling for covariates identified above

Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
```{r diff.exp3, fig.height=6, fig.width=18, cache=FALSE}
## Modeling Diagnosis, msex and age_death conjointly
COVARIATES$Tissue.Diagnosis.SEX = paste(COVARIATES$Tissue.Diagnosis,COVARIATES$sex, sep = '.') %>% factor
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c('Tissue.Diagnosis.SEX', setdiff(postAdjustCovars, 'SEX')), drop = F], Intercept = F)
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES$individualIdentifier, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS)
cntr = c('Tissue.Diagnosis.SEXACC.AD.male-Tissue.Diagnosis.SEXACC.CONTROL.male',
         'Tissue.Diagnosis.SEXACC.AD.female-Tissue.Diagnosis.SEXACC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXACC.AD.male+0.5*Tissue.Diagnosis.SEXACC.AD.female
         -0.5*Tissue.Diagnosis.SEXACC.CONTROL.male-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXACC.AD.female+0.5*Tissue.Diagnosis.SEXACC.CONTROL.female
         -0.5*Tissue.Diagnosis.SEXACC.AD.male-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXACC.AD.female-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female
         -0.5*Tissue.Diagnosis.SEXACC.AD.male+0.5*Tissue.Diagnosis.SEXACC.CONTROL.male',
         'Tissue.Diagnosis.SEXDLPFC.AD.male-Tissue.Diagnosis.SEXDLPFC.CONTROL.male',
         'Tissue.Diagnosis.SEXDLPFC.AD.female-Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.male+0.5*Tissue.Diagnosis.SEXDLPFC.AD.female
         -0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.male-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.female+0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female
         -0.5*Tissue.Diagnosis.SEXDLPFC.AD.male-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.female-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female
         -0.5*Tissue.Diagnosis.SEXDLPFC.AD.male+0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.male',
         'Tissue.Diagnosis.SEXPCC.AD.male-Tissue.Diagnosis.SEXPCC.CONTROL.male',
         'Tissue.Diagnosis.SEXPCC.AD.female-Tissue.Diagnosis.SEXPCC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXPCC.AD.male+0.5*Tissue.Diagnosis.SEXPCC.AD.female
         -0.5*Tissue.Diagnosis.SEXPCC.CONTROL.male-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXPCC.AD.female+0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female
         -0.5*Tissue.Diagnosis.SEXPCC.AD.male-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female',
         '0.5*Tissue.Diagnosis.SEXPCC.AD.female-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female
         -0.5*Tissue.Diagnosis.SEXPCC.AD.male+0.5*Tissue.Diagnosis.SEXPCC.CONTROL.male')
contrast = makeContrasts(contrasts=cntr,
                         levels = colnames(FIT$coefficients))
colnames(contrast) = c('ACC.AD.MALE-ACC.CONTROL.MALE',
                       'ACC.AD.FEMALE-ACC.CONTROL.FEMALE',
                       'ACC.AD.ALL-ACC.CONTROL.ALL',
                       'ACC.ALL.FEMALE-ACC.ALL.MALE',
                       'ACC.ALL.ALL-ACC.ALL.ALL',
                       'DLPFC.AD.MALE-DLPFC.CONTROL.MALE',
                       'DLPFC.AD.FEMALE-DLPFC.CONTROL.FEMALE',
                       'DLPFC.AD.ALL-DLPFC.CONTROL.ALL',
                       'DLPFC.ALL.FEMALE-DLPFC.ALL.MALE',
                       'DLPFC.ALL.ALL-DLPFC.ALL.ALL',
                       'PCC.AD.MALE-PCC.CONTROL.MALE',
                       'PCC.AD.FEMALE-PCC.CONTROL.FEMALE',
                       'PCC.AD.ALL-PCC.CONTROL.ALL',
                       'PCC.ALL.FEMALE-PCC.ALL.MALE',
                       'PCC.ALL.ALL-PCC.ALL.ALL'
                       )
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = colnames(contrast)
DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
                Study = 'ROSMAP',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
DE$Tissue <- do.call( rbind, strsplit( DE$Comparison, '[.]'))[,1]
DE$Comparison <- gsub('DLPFC.', '',gsub('ACC.', '', gsub('PCC.', '',  DE$Comparison )))
tmp = DE %>%
  dplyr::select(ensembl_gene_id, Tissue, Comparison, Direction) %>%
  group_by(Tissue, Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)
DE$Tissue <- do.call( rbind, strsplit( DE$Comparison, '[.]'))[,1]
all.diff.exp = c(all.diff.exp, list(Diagnosis.SEX = DE))
all.fit = c(all.fit, list(Diagnosis.SEX = FIT))
```

### Differential expression analysis (with Diagnosis and AOD)
Differential expression is performed on the Diagnosis x AOD variable by controlling for covariates identified above

Genes that are differentially expressed at an FDR <= 0.05 and folde change of 1.2 are
```{r diff.exp4, fig.height=6, fig.width=18, cache=FALSE}
# Get design matrix
DESIGN = getDesignMatrix(COVARIATES[, c(primaryVariable[2], setdiff(postAdjustCovars, 'age_death')), drop = F], Intercept = F)
ind = grep('Diagnosis', colnames(DESIGN$design))
DESIGN$design[,ind] = DESIGN$design[,ind] * COVARIATES[rownames(DESIGN$design),'age_death']
DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]

colnames(DESIGN$design)[ind[1:9]] = gsub('Tissue.Diagnosis', '', paste0(colnames(DESIGN$design)[ind[1:9]], '.age_death'))
# Re-estimate voom weights
VOOM.WEIGHTS = voom(cnts,
                    design=DESIGN$design, plot=F,
                    block = COVARIATES$individualIdentifier, 
                    correlation = correlation$cor)
# Fit linear model using new weights and new design
VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
FIT = lmFit(VOOM.WEIGHTS)
cntr = c("ACC.AD.age_death-ACC.CONTROL.age_death",
         "0.5*ACC.AD.age_death+0.5*ACC.CONTROL.age_death",
         "DLPFC.AD.age_death-DLPFC.CONTROL.age_death",
         "0.5*DLPFC.AD.age_death+0.5*DLPFC.CONTROL.age_death",
         "PCC.AD.age_death-PCC.CONTROL.age_death",
         "0.5*PCC.AD.age_death+0.5*PCC.CONTROL.age_death"
        )

contrast = makeContrasts(contrasts=cntr,
                         levels = colnames(FIT$coefficients))
colnames(contrast) = c("ACC.AD.AOD-ACC.CONTROL.AOD",
                       "ACC.ALL.AOD",
                       "DLPFC.AD.AOD-DLPFC.CONTROL.AOD",
                       "DLPFC.ALL.AOD",
                       "PCC.AD.AOD-PCC.CONTROL.AOD",
                       "PCC.ALL.AOD"
                      )
FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
FIT.CONTR = eBayes(FIT.CONTR)
# Get differnetial expression
DE = lapply(1:dim(contrast)[2], function(i, FIT){
  topTable(FIT, coef=i, number = 50000, confint = T) %>%
    rownameToFirstColumn('ensembl_gene_id')
}, FIT.CONTR)
names(DE) = colnames(contrast)
DE = DE %>% 
  rbindlist(idcol = 'Comparison') %>%
  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
                Study = 'ROSMAP',
                Direction = logFC/abs(logFC),
                Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
                Direction = as.character(Direction)) %>%
  left_join(GENE.PARAM %>%
              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
              unique())
DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
DE$Tissue <- do.call( rbind, strsplit( DE$Comparison, '[.]'))[,1]
DE$Comparison <- gsub('DLPFC.', '',gsub('ACC.', '', gsub('PCC.', '',  DE$Comparison )))
tmp = DE %>%
  dplyr::select(ensembl_gene_id, Tissue, Comparison, Direction) %>%
  group_by(Tissue, Comparison, Direction) %>%
  dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
  spread(Direction, FDR_0_05_FC_1.2) 
kable(tmp)
all.diff.exp = c(all.diff.exp, list(Diagnosis.AOD = DE))
all.fit = c(all.fit, list(Diagnosis.AOD = FIT))
```

```{r NeuroPath_DataClean, include=FALSE, cache=TRUE}
EXP <- t( RESIDUAL.SVA.GENE_EXPRESSION )
FullMeta <- COVARIATES
PartialMeta <- FullMeta[ ,c('tissue', 'ceradsc', 'braaksc', 'cogdx', 'dcfdx_lv' ) ]
table( row.names(PartialMeta) == row.names(EXP) )

#### Setup and Run Models

NeuroPath_Calc <- function( GN, Path, Exp, Tiss ){
  #'@GN a character ENSG Gene name eg 'ENSG00000227232'
  #'@Path the character string of Neuropath column to use for model eg. EITHER: 'ceradsc', 'braaksc', 'c', 'dcfdx_lv'
  #'@Exp
  #'@Tiss eg. 'ACC', 'PCC', 'DLPFC'

  Dat <- as.data.frame( cbind( PartialMeta[ PartialMeta$tissue == Tiss ,], 
                               Gene = scale( as.numeric(Exp[ (row.names(PartialMeta[ PartialMeta$tissue == Tiss ,])) ,GN]) ) ), stringsAsFactors = F )

  Dat$ceradsc <- as.factor(Dat$ceradsc)
  Dat$braaksc <- as.factor(Dat$braaksc)
  Dat$cogdx <- as.factor(Dat$cogdx)
  Dat$dcfdx_lv <- as.factor(Dat$dcfdx_lv)

  m <- eval(parse(text=paste0( 'MASS::polr(', Path, '~ Gene, data = Dat, Hess=TRUE)' )))
  ctable <- coef(summary(m))

  p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2
  ctable <- cbind(ctable, "p value" = p)
  #ERROR is HERE:
  ci <- confint(m)

  names( GN ) <- 'Gene'
  PVal <- p['Gene']
  names( PVal ) <- 'PVal'
  OR <- exp(coef(m))
  names( OR ) <- 'OR'
  CI <- exp(cbind(OR = coef(m), ci))[,2]
  Tissue <- Tiss
  return( c( GN, Tissue, OR, CI, PVal ) )
}

#assign gne names to a variable to iterate over
temp<-colnames(EXP)

#BRAAK
Path <- 'braaksc'
mark<-Sys.time()
BRAAK_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
Sys.time() - mark

mark<-Sys.time()
BRAAK_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
Sys.time() - mark

mark<-Sys.time()
BRAAK_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
Sys.time() - mark

BRAAK <- rbind( BRAAK_ACC, BRAAK_PCC, BRAAK_DLPFC )

#CERAD
Path <- 'ceradsc'
mark<-Sys.time()
CERAD_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
Sys.time() - mark
mark<-Sys.time()
CERAD_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
Sys.time() - mark
mark<-Sys.time()
CERAD_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
Sys.time() - mark

CERAD <- rbind( CERAD_ACC, CERAD_PCC, CERAD_DLPFC )

#COGDX
Path <- 'cogdx'
mark<-Sys.time()
cogdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
Sys.time() - mark
mark<-Sys.time()
cogdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
Sys.time() - mark
mark<-Sys.time()
cogdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
Sys.time() - mark

cogdx <- rbind( cogdx_ACC, cogdx_PCC, cogdx_DLPFC )

#DCFDX_LV
Path <- 'dcfdx_lv'
mark<-Sys.time()
dcfdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' ) 
Sys.time() - mark
mark<-Sys.time()
dcfdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' ) 
Sys.time() - mark
mark<-Sys.time()
dcfdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' ) 
Sys.time() - mark

dcfdx <- rbind( dcfdx_ACC, dcfdx_PCC, dcfdx_DLPFC )
```

```{r NeuroPath_Finish, include=FALSE, cache=TRUE}
####--Pick Up Here--###

My.P.Adj <- function (p, method = p.adjust.methods, n = length(p)){
    method <- match.arg(method)
    if (method == "fdr") 
        method <- "BH"
    nm <- names(p)
    p <- as.numeric(p)
    p0 <- setNames(p, nm)
    if (all(nna <- !is.na(p))) 
        nna <- TRUE
    p <- p[nna]
    lp <- length(p)
    #stopifnot(n >= lp)
    if (n <= 1) 
        return(p0)
    if (n == 2 && method == "hommel") 
        method <- "hochberg"
    p0[nna] <- switch(method, bonferroni = pmin(1, n * p), holm = {
        i <- seq_len(lp)
        o <- order(p)
        ro <- order(o)
        pmin(1, cummax((n + 1L - i) * p[o]))[ro]
    }, hommel = {
        if (n > lp) p <- c(p, rep.int(1, n - lp))
        i <- seq_len(n)
        o <- order(p)
        p <- p[o]
        ro <- order(o)
        q <- pa <- rep.int(min(n * p/i), n)
        for (j in (n - 1L):2L) {
            ij <- seq_len(n - j + 1L)
            i2 <- (n - j + 2L):n
            q1 <- min(j * p[i2]/(2L:j))
            q[ij] <- pmin(j * p[ij], q1)
            q[i2] <- q[n - j + 1L]
            pa <- pmax(pa, q)
        }
        pmax(pa, p)[if (lp < n) ro[1L:lp] else ro]
    }, hochberg = {
        i <- lp:1L
        o <- order(p, decreasing = TRUE)
        ro <- order(o)
        pmin(1, cummin((n + 1L - i) * p[o]))[ro]
    }, BH = {
        i <- lp:1L
        o <- order(p, decreasing = TRUE)
        ro <- order(o)
        pmin(1, cummin(n/i * p[o]))[ro]
    }, BY = {
        i <- lp:1L
        o <- order(p, decreasing = TRUE)
        ro <- order(o)
        q <- sum(1/(1L:n))
        pmin(1, cummin(q * n/i * p[o]))[ro]
    }, none = p)
    p0
}

Cleaner <- function( DF, type ){
  colnames(DF)[2] <- 'Tissue'
  DF <- as.data.frame( DF, stringsAsFactors=F )
  DF$OR <- as.numeric(DF$OR)
  DF$Tissue <- as.factor(DF$Tissue)

  DF$`2.5 %` <- as.numeric(DF$`2.5 %`)
  DF$`97.5 %` <- as.numeric(DF$`97.5 %`)
  DF$PVal <- as.numeric(DF$PVal)
  DF$PVal_Adj <- NA
  for( Tis in levels(DF$Tissue) ){

    DF[as.character(DF$Tissue) == Tis,]$PVal_Adj <- apply( as.matrix(DF[as.character(DF$Tissue) == Tis,]$PVal), 
                                                           1,  
                                                           p.adjust, 
                                                           method='fdr', 
                                                           n=dim( DF[as.character(DF$Tissue) == Tis,])[1]
                                                          )
  }

  DF$NeuroPath <- type
  return(DF)
}
BRAAK <- Cleaner( BRAAK, 'BRAAK' )
CERAD <- Cleaner( CERAD, 'CERAD' )
dcfdx <- Cleaner( dcfdx, 'DCFDX' )
cogdx <- Cleaner( cogdx, 'COGDX' )
Master <- as.data.frame( rbind( BRAAK,CERAD,dcfdx,cogdx ), stringsAsFactors=F )

Master <- Master[, c( 'Gene', 'Tissue', 'OR', '2.5 %', '97.5 %', 'PVal', 'PVal_Adj', 'NeuroPath' ) ] 
colnames(Master) <- c( 'ENSG', 'Tissue', 'OddsRatio', 'CI_Lower', 'CI_Upper', 'PVal', 'PVal_Adj', 'NeuroPath_Type' )

print( paste0( 'Significantly associated genes by Neuropath Score: ' ))
table(Master[ Master$PVal_Adj < 0.05, ]$Tissue, Master[ Master$PVal_Adj < 0.05, ]$NeuroPath_Type) 
#print( paste0( 'Frequency of Gene Across Significance to Neuropath Score: '))
#table(table( Master[ Master$PVal_Adj < 0.05, ]$ENSG)) 
#print( paste0( 'Significantly associated genes by Neuropath Score with an Odds Ratio < 1: ',
#               table(Master[ Master$PVal_Adj < 0.05, ]$OddsRatio < 1 )['TRUE'] ))
#print( paste0( 'Significantly associated genes by Neuropath Score with an Odds Ratio > 1: ',
#               table(Master[ Master$PVal_Adj < 0.05, ]$OddsRatio > 1 )['TRUE'] ))
#print( 'Significantly associated genes by Neuropath Score with an Odds Ratio > 1 by Score Type: ')
#table(Master[ Master$PVal_Adj < 0.05, ]$OddsRatio > 1, Master[ Master$PVal_Adj < 0.05, ]$NeuroPath_Type ) 
# Store results
#write.csv(Master, file = '~/NeuroPath_Regression/Neuropathology_Scores.csv',  row.names =F)

```

```{r synapse.parameters, include=FALSE, cache=TRUE}
#parentId = 'syn21277617';
activityName = 'Covariate Regression';
activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
thisFileName <- '2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=TRUE}
activityName = 'Covariate Regression';
activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';

CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))

Syns_Used <- c( "syn23625835", "syn23625835",
                "syn23573928", "syn21075913",
                "syn23593968"
              )
# Set annotations
all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay	 = 'RNAseq',
  tissueTypeAbrv	= 'DLPFC', 
  study = 'ROSMAP', 
  organism = 'HomoSapiens',
  consortium	= 'ROSMAP',
  normalizationStatus	= TRUE,
  normalizationType	= 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh37'
)
# Store SVA results
write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Corrected.tsv', sep = '\t', quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Corrected.tsv', name = 'Normalised, covariates, and surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForeQTL'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'ROSMAP_SVA_Covariates.tsv', row.names = F, sep = '\t', quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'covariates'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store Estimated counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'estimatedCounts'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store logCPM
CQN.GENE_EXPRESSION$y %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'filteredLCPM'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'offset'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store design matrix
MODEL1 %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'designMatrix'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store surrogate variables
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'surrogateVariables'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store residual gene expression for network analysis
RESIDUAL.NET.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Diff_Exp'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store NeuroPath results
write.csv(Master, file = '~/NeuroPath_Regression/Neuropathology_Scores.csv',  row.names =F)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='~/NeuroPath_Regression/Neuropathology_Scores.csv', name = 'Neuropath Scores', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'Diff_Exp'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

# Store all differential expression models
save(all.fit, file = 'ROSMAP_Models.RData')
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Models.RData', name = 'All Limma Models', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  all.annotations$dataSubType = 'RData'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)

stopCluster(cl)
```

```{r DelFiles, echo=T, results='hide'}
system('rm *.tsv')
```
### R Source Code
[Github](`r thisFile`)

```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
reticulate::use_python("/usr/bin/python", required = TRUE)
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "ROSMAP_Regress_hg38.Rmd",
                                          parentId ="syn21277617",
                                          folderName = 'ROSMAP')

```

### 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
Recomit

@@
 ```{r DelFiles, echo=T, results='hide'}
-system('rm *.tsv')
+#system('rm *.tsv')
 ```
@@
 
+#_ Set this Variable to filter Rin > 5 _#
+RIN_Filt <- FALSE
+#_ Set this Variable to use sageseqr vals _#
+SageSeqR <- FALSE
+
 setwd("~/TWAS/code/")

### 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
recommit

@@
 
-CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = 'Full_RosMap_OldCode', parentId = parentId))
 
@@
 
-createAndKnitToFolderEntityClient(file = "ROSMAP_Regress_hg38.Rmd",
-                                          parentId ="syn21277617",
+createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd",
+                                          parentId ="syn23640229",
                                           folderName = 'ROSMAP')

### 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
recommit

--- 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
@@
 ```
-Dorsolateral prefrontal cortex of `r dim(COUNT)[2]` subjects from the ROS and MAP cohorts are used for the analysis.
-Following sample are removed due to missing metadata `r paste(removedIDs, collapse = ',')`
+Dorsolateral prefrontal cortex of `r dim(COUNT)[2]` subjects from the ROS and MAP cohorts are used for the analysis. Following sample are removed due to missing metadata
 
@@
 
-CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = folderName, parentId = parentId))
 
@@
 
-createAndKnitToFolderEntityClient(file = "ROSMAP_Regress_hg38.Rmd",
-                                          parentId ="syn21277617",
-                                          folderName = 'ROSMAP')
-
-```
+createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd",
+                                          parentId ="syn23640229",
+                                          folderName = 'Full_RosMap_OldCode')
+
+```

### 2020-12-16 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
recommit

@@
 Meta <- read.csv( Meta_OBJ$path, header=T, check.names = F, row.names = 1 )
+
+#Filter for Rin Here#
 
@@
 temp<-colnames(EXP)
-
+```
+```{r NeuroPath_Associtation_1_1, include=FALSE, cache=TRUE}
 #BRAAK
@@
 mark<-Sys.time()
-BRAAK_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
+BRAAK_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )}, error=function(e) NULL)
 Sys.time() - mark
-
+```
+```{r NeuroPath_Associtation_1_2, include=FALSE, cache=TRUE}
 mark<-Sys.time()
-BRAAK_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
+BRAAK_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )}, error=function(e) NULL)
 Sys.time() - mark
-
+```
+
+```{r NeuroPath_Associtation_1_3, include=FALSE, cache=TRUE}
 mark<-Sys.time()
-BRAAK_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
+BRAAK_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )}, error=function(e) NULL)
 Sys.time() - mark
@@
 BRAAK <- rbind( BRAAK_ACC, BRAAK_PCC, BRAAK_DLPFC )
-
+```
+```{r NeuroPath_Associtation_2_1, include=FALSE, cache=TRUE}
 #CERAD
@@
 mark<-Sys.time()
-CERAD_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
+CERAD_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )}, error=function(e) NULL)
 Sys.time() - mark
+```
+```{r NeuroPath_Associtation_2_2, include=FALSE, cache=TRUE}
 mark<-Sys.time()
-CERAD_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
+CERAD_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )}, error=function(e) NULL)
 Sys.time() - mark
+```
+```{r NeuroPath_Associtation_2_3, include=FALSE, cache=TRUE}
+
 mark<-Sys.time()
-CERAD_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
+CERAD_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )}, error=function(e) NULL)
 Sys.time() - mark
@@
 CERAD <- rbind( CERAD_ACC, CERAD_PCC, CERAD_DLPFC )
+```
+```{r NeuroPath_Associtation_3_1, include=FALSE, cache=TRUE}
 
@@
 mark<-Sys.time()
-cogdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
+cogdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )}, error=function(e) NULL)
 Sys.time() - mark
+```
+```{r NeuroPath_Associtation_3_2, include=FALSE, cache=TRUE}
+
 mark<-Sys.time()
-cogdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
+cogdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )}, error=function(e) NULL)
 Sys.time() - mark
+```
+```{r NeuroPath_Associtation_3_3, include=FALSE, cache=TRUE}
+
 mark<-Sys.time()
-cogdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
+cogdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )}, error=function(e) NULL)
 Sys.time() - mark
+```
+
+```{r NeuroPath_Associtation_4_1, include=FALSE, cache=TRUE}
 
@@
 mark<-Sys.time()
-dcfdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' )
+dcfdx_ACC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'ACC' ) }, error=function(e) NULL)
 Sys.time() - mark
+```
+```{r NeuroPath_Associtation_4_2, include=FALSE, cache=TRUE}
+
 mark<-Sys.time()
-dcfdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' )
+dcfdx_PCC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'PCC' ) }, error=function(e) NULL)
 Sys.time() - mark
+```
+```{r NeuroPath_Associtation_4_3, include=FALSE, cache=TRUE}
 mark<-Sys.time()
-dcfdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' )
+dcfdx_DLPFC <- foreach( i=1:length(colnames(EXP)), .export=c( 'Path', 'EXP', 'temp'), .packages = c('foreign', 'MASS', 'Hmisc'), .combine = 'rbind' ) %dopar% tryCatch({NeuroPath_Calc( GN=temp[i],Path=Path, Exp=EXP, Tiss = 'DLPFC' ) }, error=function(e) NULL)
 Sys.time() - mark
@@
 ```{r NeuroPath_Finish, include=FALSE, cache=TRUE}
-####--Pick Up Here--###
-
-My.P.Adj <- function (p, method = p.adjust.methods, n = length(p)){
-    method <- match.arg(method)
-    if (method == "fdr") 
-        method <- "BH"
-    nm <- names(p)
-    p <- as.numeric(p)
-    p0 <- setNames(p, nm)
-    if (all(nna <- !is.na(p))) 
-        nna <- TRUE
-    p <- p[nna]
-    lp <- length(p)
-    #stopifnot(n >= lp)
-    if (n <= 1) 
-        return(p0)
-    if (n == 2 && method == "hommel") 
-        method <- "hochberg"
-    p0[nna] <- switch(method, bonferroni = pmin(1, n * p), holm = {
-        i <- seq_len(lp)
-        o <- order(p)
-        ro <- order(o)
-        pmin(1, cummax((n + 1L - i) * p[o]))[ro]
-    }, hommel = {
-        if (n > lp) p <- c(p, rep.int(1, n - lp))
-        i <- seq_len(n)
-        o <- order(p)
-        p <- p[o]
-        ro <- order(o)
-        q <- pa <- rep.int(min(n * p/i), n)
-        for (j in (n - 1L):2L) {
-            ij <- seq_len(n - j + 1L)
-            i2 <- (n - j + 2L):n
-            q1 <- min(j * p[i2]/(2L:j))
-            q[ij] <- pmin(j * p[ij], q1)
-            q[i2] <- q[n - j + 1L]
-            pa <- pmax(pa, q)
-        }
-        pmax(pa, p)[if (lp < n) ro[1L:lp] else ro]
-    }, hochberg = {
-        i <- lp:1L
-        o <- order(p, decreasing = TRUE)
-        ro <- order(o)
-        pmin(1, cummin((n + 1L - i) * p[o]))[ro]
-    }, BH = {
-        i <- lp:1L
-        o <- order(p, decreasing = TRUE)
-        ro <- order(o)
-        pmin(1, cummin(n/i * p[o]))[ro]
-    }, BY = {
-        i <- lp:1L
-        o <- order(p, decreasing = TRUE)
-        ro <- order(o)
-        q <- sum(1/(1L:n))
-        pmin(1, cummin(q * n/i * p[o]))[ro]
-    }, none = p)
-    p0
-}
 
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-#parentId = 'syn21277617';
+parentId = '"syn23640229"';
 activityName = 'Covariate Regression';
@@
 
-CODE <- syn_temp$store(synapseclient$Folder(name = folderName, parentId = parentId))
+CODE <- syn_temp$store(synapseclient$Folder(name = "Full_RosMap_OldCode", parentId = "syn23640229"))
 
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_eCounts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
@@
 rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
-  write.table(file = 'ROSMAP_DLPFC_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'Diff_Exp'

### 2020-12-16 code/2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd
recommit

--- 2020-12-16 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
@@
 #Filter for Rin Here#
+Meta[ Meta$RIN >= 5 | Meta$sampleid %in% c('380_120503','500_120515'), ]
 
@@
 #write.csv(Master, file = '~/NeuroPath_Regression/Neuropathology_Scores.csv',  row.names =F)
-
 ```
@@
 activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- '2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd'
+thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38'
 # Github link
@@
 
-CODE <- syn_temp$store(synapseclient$Folder(name = "Full_RosMap_OldCode", parentId = "syn23640229"))
+CODE <- syn_temp$store(synapseclient$Folder(name = "RinOver5_RosMap_OldCode", parentId = "syn23640229"))
 
@@
 
-createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd",
+createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38",
                                           parentId ="syn23640229",
-                                          folderName = 'Full_RosMap_OldCode')
-
-```
+                                          folderName = 'RinOver5_RosMap_OldCode')
+
+```

### 2020-12-16 code/2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd
recommit

@@
 activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38'
+thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd'
 # Github link
@@
 
-createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38",
+createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd",
                                           parentId ="syn23640229",

### 2020-12-21 code/2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd
SageSeqrRin

--- 2020-12-16 code/2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd
@@
 Obtain count matrix and metadata from synapse
-```{r download.data}
+```{r download.data, eval=TRUE}
 # Download expression data
-COUNT_ID <- 'syn23593968';
-ALL_USED_IDs <- COUNT_ID
-COUNT_OBJ <- syn_temp$get(COUNT_ID, version = 1)
+##_##COUNT_ID <- 'syn23593968';
+##_##ALL_USED_IDs <- COUNT_ID
+##_##COUNT_OBJ <- syn_temp$get(COUNT_ID, version = 1)
 #COUNT <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F, row.names = 1)
-COUNT <- as.data.frame(data.table::fread(COUNT_OBJ$path, header=T, sep='\t', check.names = F))#, row.names = 1)
-row.names(COUNT) <- as.character(COUNT$feature)
-COUNT <- COUNT[ ,(colnames(COUNT) %in% 'feature')==F ]
-COUNT <- as.matrix(COUNT)
-
-Provenance <- 'syn21075913'
-Prov <- syn_temp$get(Provenance, version = 1)
-ALL_USED_IDs[length(ALL_USED_IDs)+1] = Provenance
-Translator <- read.csv(Prov$path, header=T, row.names = 1)
+##_##COUNT <- as.data.frame(data.table::fread(COUNT_OBJ$path, header=T, sep='\t', check.names = F))#, row.names = 1)
+##_##row.names(COUNT) <- as.character(COUNT$feature)
+##_##COUNT <- COUNT[ ,(colnames(COUNT) %in% 'feature')==F ]
+##_##COUNT <- as.matrix(COUNT)
+
+#Toss Zero variance genes post residual correct
+##_##COUNT <- COUNT[ (row.names(COUNT) %in% c("ENSG00000239467", "ENSG00000005486", "ENSG00000160972", "ENSG00000165886", "ENSG00000002330", "ENSG00000149823", "ENSG00000139722", "ENSG00000169217", "ENSG00000127774", "ENSG00000122490", "ENSG00000130881", "ENSG00000126005", "ENSG00000171222", "ENSG00000070413", "ENSG00000211459")) == F, ]
+
+##_##Provenance <- 'syn21075913'
+##_##Prov <- syn_temp$get(Provenance, version = 1)
+##_##ALL_USED_IDs[length(ALL_USED_IDs)+1] = Provenance
+##_##Translator <- read.csv(Prov$path, header=T, row.names = 1)
 #colnames(COUNT) <- as.character( Translator[ colnames(COUNT), ][,2] )
@@
 #Need to filter low counts here to remove the PAR_Y Regions
-COUNT <- COUNT[ rowSums(COUNT[,] > 0) / (ncol(COUNT)) >= 0.05, ]
+##_##COUNT <- COUNT[ rowSums(COUNT[,] > 0) / (ncol(COUNT)) >= 0.05, ]
 
 # Convert rownames of counts from tracking id to ensemble gene id
-tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
-  dplyr::mutate(ID = Gene.ID) %>%
-  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
-rownames(tmp) = tmp$Gene.ID
-rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
+##_##tmp = data.frame(Gene.ID = rownames(COUNT)) %>%
+##_##  dplyr::mutate(ID = Gene.ID) %>%
+##_##  tidyr::separate(ID, c('ensembl_gene_id', 'position'), sep = '\\.')
+##_##rownames(tmp) = tmp$Gene.ID
+##_##rownames(COUNT) = tmp[rownames(COUNT), 'ensembl_gene_id']
 
 # Download expression data
-Meta_ID <- 'syn23573928';
-ALL_USED_IDs <- c( Meta_ID, ALL_USED_IDs )
-Meta_OBJ <- syn_temp$get( Meta_ID, version = 2 )
-Meta <- read.csv( Meta_OBJ$path, header=T, check.names = F, row.names = 1 )
+##_##Meta_ID <- 'syn23573928';
+##_##ALL_USED_IDs <- c( Meta_ID, ALL_USED_IDs )
+##_##Meta_OBJ <- syn_temp$get( Meta_ID, version = 2 )
+##_##Meta <- read.csv( Meta_OBJ$path, header=T, check.names = F, row.names = 1 )
 
 #Filter for Rin Here#
-Meta[ Meta$RIN >= 5 | Meta$sampleid %in% c('380_120503','500_120515'), ]
+##_##Meta <- Meta[ Meta$RIN >= 5 | Meta$sampleid %in% c('380_120503','500_120515'), ]
 
 #Filter Out Sample Swaps
-Meta <- Meta[ Meta$FailQC_SampleSwapped == 0, ]
-COUNT <- COUNT[ ,row.names(Meta) ]
+##_##Meta <- Meta[ Meta$FailQC_SampleSwapped == 0, ]
+##_##COUNT <- COUNT[ ,row.names(Meta) ]
 
@@
 
+COUNT_ID <- 'syn23662102';
+ALL_USED_IDs <- COUNT_ID
+COUNT_OBJ <- syn_temp$get(COUNT_ID, version = 1)
+COUNT <- load(COUNT_OBJ$path)
+
+COUNT <- cqn_counts$counts
+
+CQN.GENE_EXPRESSION <- cqn_counts
+# Download expression data
+Meta_ID <- 'syn23662101';
+ALL_USED_IDs <- c( Meta_ID, ALL_USED_IDs )
+Meta_OBJ <- syn_temp$get( Meta_ID, version = 1 )
+Meta <- load( Meta_OBJ$path )
+
+Meta <- clean_md
 METADATA <- Meta[ ,c( "individualID", "apoe4", "batch", "notes", "tissue", "diagnosis", "race", "pmi", "sex", "race", "spanish", "braaksc", "ceradsc", "cogdx", "dcfdx_lv", "pmi", "rincontinuous", "rin2", "age_death", "pct_pf_reads_aligned", "pct_coding_bases", "pct_intergenic_bases", "pct_intronic_bases" ) ]
@@
 # Remove samples with no cogdx, RIN, PMI scores and age_death
-METADATA <- METADATA[, (colnames(METADATA)%in%'pmi.1')==F]
-
-colnames(METADATA)[ colnames(METADATA) == 'race.1' ] <- 'race'
-colnames(METADATA)[ colnames(METADATA) == 'rincontinuous' ] <- 'rin'
-
-METADATA <- as.data.frame( cbind( Sampleid = row.names(METADATA), METADATA[ ,colnames(METADATA) ] ))
-
-METADATA <- METADATA %>%
-  ungroup %>%
-  dplyr::filter(Sampleid %in% colnames(COUNT)) %>%
-  dplyr::filter(!is.na(cogdx), !is.na(braaksc), !is.na(ceradsc)) %>%
-  dplyr::filter(!is.na(rin)) %>%
-  dplyr::filter(!is.na(pct_intronic_bases)) %>%
-  dplyr::filter(!is.na(pmi)) %>%
-  dplyr::filter(!is.na(age_death)) %>%
-  as.data.frame()
+##_##METADATA <- METADATA[, (colnames(METADATA)%in%'pmi.1')==F]
+
+##_##colnames(METADATA)[ colnames(METADATA) == 'race.1' ] <- 'race'
+##_##colnames(METADATA)[ colnames(METADATA) == 'rincontinuous' ] <- 'rin'
+
+##_##METADATA <- as.data.frame( cbind( Sampleid = row.names(METADATA), METADATA[ ,colnames(METADATA) ] ))
+
+##_####_##METADATA <- METADATA %>%
+##_##  ungroup %>%
+##_##  dplyr::filter(Sampleid %in% colnames(COUNT)) %>%
+##_##  dplyr::filter(!is.na(cogdx), !is.na(braaksc), !is.na(ceradsc)) %>%
+##_##  dplyr::filter(!is.na(rin)) %>%
+##_##  dplyr::filter(!is.na(pct_intronic_bases)) %>%
+##_##  dplyr::filter(!is.na(pmi)) %>%
+##_##  dplyr::filter(!is.na(age_death)) %>%
+##_##  as.data.frame()
 
 # Add harmonised case-control status
-METADATA$cogdx <- as.numeric(METADATA$cogdx)
-METADATA$braaksc <- as.numeric(METADATA$braaksc)
-METADATA$ceradsc <- as.numeric(METADATA$ceradsc)
-
-METADATA$Diagnosis = 'OTHER'
-METADATA$Diagnosis[METADATA$cogdx == 1 & METADATA$braaksc <= 3 & METADATA$ceradsc >= 3] = 'CONTROL'
-METADATA$Diagnosis[METADATA$cogdx == 4 & METADATA$braaksc >= 4 & METADATA$ceradsc <= 2] = 'AD'
-
-METADATA <- METADATA[ , (colnames(METADATA) %in% "diagnosis") == F ]
+##_##METADATA$cogdx <- as.numeric(METADATA$cogdx)
+##_##METADATA$braaksc <- as.numeric(METADATA$braaksc)
+##_##METADATA$ceradsc <- as.numeric(METADATA$ceradsc)
+
+##_##METADATA$Diagnosis = 'OTHER'
+##_##METADATA$Diagnosis[METADATA$cogdx == 1 & METADATA$braaksc <= 3 & METADATA$ceradsc >= 3] = 'CONTROL'
+##_##METADATA$Diagnosis[METADATA$cogdx == 4 & METADATA$braaksc >= 4 & METADATA$ceradsc <= 2] = 'AD'
+
+##_##METADATA <- METADATA[ , (colnames(METADATA) %in% "diagnosis") == F ]
 
@@
 ```{r covariates.clustering, cache=FALSE}
+METADATA$rin <- METADATA$rincontinuous
+METADATA$Sampleid <- row.names(METADATA)
+METADATA$Diagnosis <- METADATA$diagnosis
 METADATA$Tissue.Diagnosis = paste(METADATA$tissue, METADATA$Diagnosis, sep = '.')
@@
 ```{r filter.genes}
-genesToAnalyze = COVARIATES %>%
-  rownameToFirstColumn('SampleID') %>%
-  dlply(.(Tissue.Diagnosis), .fun = function(mtd, count){
-    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
-                                                     MIN_GENE_CPM=1, 
-                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
-    processed.counts$filteredExprMatrix$genes
-  }, COUNT)
-genesToAnalyze = unlist(genesToAnalyze) %>% 
-  unique() %>%
-  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gene_gc_content)]) %>%
-  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene_length)]) %>%
-  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))
-PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
-                                                 MIN_GENE_CPM=0, 
-                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
-
-Ensemble2HGNC <- GENE.PARAM[ GENE.PARAM$ensembl_gene_id %in% PROCESSED_COUNTS$filteredExprMatrix$genes$genes, ]
-
+##_##genesToAnalyze = COVARIATES %>%
+##_##  rownameToFirstColumn('SampleID') %>%
+##_##  dlply(.(Tissue.Diagnosis), .fun = function(mtd, count){
+##_##    processed.counts = getGeneFilteredGeneExprMatrix(count[,mtd$SampleID],
+##_##                                                     MIN_GENE_CPM=1, 
+##_##                                                     MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0.5)
+##_##    processed.counts$filteredExprMatrix$genes
+##_##  }, COUNT)
+#filter out non-variable genes post residual removal
+
+##_##genesToAnalyze = unlist(genesToAnalyze) %>% 
+##_##  unique() %>%
+##_##  intersect(GENE.GC$ensembl_gene_id[!is.na(GENE.GC$percentage_gene_gc_content)]) %>%
+##_##  intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene_length)]) %>%
+##_##  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous")) %>%
+##_##  setdiff( c("ENSG00000239467", "ENSG00000005486", "ENSG00000160972", "ENSG00000165886", "ENSG00000002330", "ENSG00000149823", "ENSG00000139722", "ENSG00000169217", "ENSG00000127774", "ENSG00000122490", "ENSG00000130881", "ENSG00000126005", "ENSG00000171222", "ENSG00000070413", "ENSG00000211459") )
+
+#18404
+#vs
+#18415
+##_##PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
+##_##                                                 MIN_GENE_CPM=0, 
+##_##                                                 MIN_SAMPLE_PERCENT_WITH_MIN_GENE_CPM=0)
+
+#_#Make Empty Processed Counts object:
+PROCESSED_COUNTS <- list()
+##_## Ensemble2HGNC <- GENE.PARAM[ GENE.PARAM$ensembl_gene_id %in% PROCESSED_COUNTS$filteredExprMatrix$genes$genes, ] 
+Ensemble2HGNC <- GENE.PARAM[ GENE.PARAM$ensembl_gene_id %in% row.names(cqn_counts$counts), ] 
 summary(factor(Ensemble2HGNC$gene_biotype)) %>%
@@
   dplyr::rename(fraction = DF) %>%
-  dplyr::mutate(fraction = fraction/dim(PROCESSED_COUNTS$filteredExprMatrix$genes)[1]) %>%
+  dplyr::mutate(fraction = fraction/dim(cqn_counts$counts)[1]) %>%
   dplyr::filter(fraction >= 0.01) %>%
@@
 ```
-Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples
+Processing `r dim(cqn_counts$counts)[1]` genes in `r dim(cqn_counts$counts)[2]` samples
 
@@
 Library normalisation is performed using cqn (conditional quantile normalisation)
-```{r cqn}
+```{r cqn, eval=FALSE}
 GENE.GC <- as.data.frame(GENE.GC)
@@
 p
-indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
-PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
-CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
-COVARIATES = COVARIATES[indToRetain,]
+##_##indToRetain = setdiff(colnames(PROCESSED_COUNTS$filteredExprMatrix$counts), indToRemove)
+##_##PROCESSED_COUNTS$filteredExprMatrix$counts = PROCESSED_COUNTS$filteredExprMatrix$counts[,indToRetain]
+##_##CQN.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION$E[,indToRetain]
+##_##COVARIATES = COVARIATES[indToRetain,]
 tmp = COVARIATES %>%
@@
   tidyr::spread(Diagnosis, count)
+PROCESSED_COUNTS$filteredExprMatrix <- cqn_counts$counts
 ```
@@
 Assign NA values to genes that are above and below 3 std deviation of its distribution
-```{r winsorise.data}
+```{r winsorise.data, eval=FALSE}
 # Set gene counts in specific samples that are deviating 3 sd from other samples to 3SD limit
@@
 # Find principal components of expression to plot
+##_## Reassign to new
+LIB.SIZE = colSums( cqn_counts$counts )
+####NEW.COUNTS = cqn_counts$E
+NEW.COUNTS = cqn_counts$counts
+CQN.GENE_EXPRESSION$E.no.na = CQN.GENE_EXPRESSION$E
+CQN.GENE_EXPRESSION$E.no.na[is.na(CQN.GENE_EXPRESSION$E.no.na)] = 0
+
 PC <- prcomp(CQN.GENE_EXPRESSION$E.no.na, scale.=T, center = T)
@@
 activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38'
+thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd'
 # Github link
@@
 
-CODE <- syn_temp$store(synapseclient$Folder(name = "RinOver5_RosMap_OldCode", parentId = "syn23640229"))
+CODE <- syn_temp$store(synapseclient$Folder(name = "RinOver5_RosMap_sageseqr", parentId = "syn23640229"))
 
@@
 
-createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38",
+createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd",
                                           parentId ="syn23640229",
-                                          folderName = 'RinOver5_RosMap_OldCode')
-
-```
+                                          folderName = 'RinOver5_RosMap_sageseqr')
+
+```

### 2020-12-21 code/2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd
SageSeqrRin

@@
 for (region in c('ACC','PCC','DLPFC')){
-  tmp = combn(paste0('Tissue.Diagnosis', region, '.', c('AD', 'OTHER', 'CONTROL')),2)
+  tmp = combn(paste0('Tissue.Diagnosis', region, '.', c('AD', 'other', 'control')),2)
   cntr = c(cntr, apply(tmp, 2, paste, collapse = '-'))
@@
 pl = list()
-pl[[1]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
+pl[[1]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-control'), 
                  aes(x = log10(gene_length), y = logFC, color = Direction)) + geom_point() 
@@
 pl[[1]] = pl[[1]] + theme(legend.position = 'top')
-pl[[2]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
+pl[[2]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-control'), 
                  aes(x = percentage_gene_gc_content, y = logFC, color = Direction)) + geom_point()
@@
 pl[[2]] = pl[[2]] + theme(legend.position = 'top')
-pl[[3]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-CONTROL'), 
+pl[[3]] = ggplot(DE %>% dplyr::filter(Comparison == 'AD-control'), 
                  aes(x = AveExpr, y = logFC, color = Direction)) + geom_point()
@@
 COVARIATES$Tissue.Diagnosis.SEX = paste(COVARIATES$Tissue.Diagnosis,COVARIATES$sex, sep = '.') %>% factor
+
 # Get design matrix
-DESIGN = getDesignMatrix(COVARIATES[, c('Tissue.Diagnosis.SEX', setdiff(postAdjustCovars, 'SEX')), drop = F], Intercept = F)
+DESIGN = getDesignMatrix(COVARIATES[, c('Tissue.Diagnosis.SEX', setdiff(postAdjustCovars, 'Sex')), drop = F], Intercept = F)
 DESIGN$design = DESIGN$design[,linColumnFinder(DESIGN$design)$indepCols]
-# Re-estimate voom weights
-VOOM.WEIGHTS = voom(cnts,
-                    design=DESIGN$design, plot=F,
-                    block = COVARIATES$individualIdentifier, 
-                    correlation = correlation$cor)
+colnames(DESIGN$design) = gsub('Tissue.Diagnosis.SEX','',colnames(DESIGN$design))
+# Estimate voom weights for dispersion control
+VOOM.WEIGHTS = voom(cnts, design=DESIGN$design, plot=F)
 # Fit linear model using new weights and new design
-VOOM.WEIGHTS$E = CQN.GENE_EXPRESSION$E
-FIT = lmFit(VOOM.WEIGHTS)
-cntr = c('Tissue.Diagnosis.SEXACC.AD.male-Tissue.Diagnosis.SEXACC.CONTROL.male',
-         'Tissue.Diagnosis.SEXACC.AD.female-Tissue.Diagnosis.SEXACC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXACC.AD.male+0.5*Tissue.Diagnosis.SEXACC.AD.female
-         -0.5*Tissue.Diagnosis.SEXACC.CONTROL.male-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXACC.AD.female+0.5*Tissue.Diagnosis.SEXACC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXACC.AD.male-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXACC.AD.female-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXACC.AD.male+0.5*Tissue.Diagnosis.SEXACC.CONTROL.male',
-         'Tissue.Diagnosis.SEXDLPFC.AD.male-Tissue.Diagnosis.SEXDLPFC.CONTROL.male',
-         'Tissue.Diagnosis.SEXDLPFC.AD.female-Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.male+0.5*Tissue.Diagnosis.SEXDLPFC.AD.female
-         -0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.male-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.female+0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXDLPFC.AD.male-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.female-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXDLPFC.AD.male+0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.male',
-         'Tissue.Diagnosis.SEXPCC.AD.male-Tissue.Diagnosis.SEXPCC.CONTROL.male',
-         'Tissue.Diagnosis.SEXPCC.AD.female-Tissue.Diagnosis.SEXPCC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXPCC.AD.male+0.5*Tissue.Diagnosis.SEXPCC.AD.female
-         -0.5*Tissue.Diagnosis.SEXPCC.CONTROL.male-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXPCC.AD.female+0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXPCC.AD.male-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXPCC.AD.female-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXPCC.AD.male+0.5*Tissue.Diagnosis.SEXPCC.CONTROL.male')
-contrast = makeContrasts(contrasts=cntr,
+FIT = lmFit(CQN.GENE_EXPRESSION$E,
+            design = DESIGN$design,
+            weights = VOOM.WEIGHTS$weights)
+
+contrast = makeContrasts(contrasts=c("(ACC.AD.female+ ACC.AD.male)/2-( ACC.control.female+ACC.control.male)/2",
+                                     "(ACC.AD.female+ ACC.control.female)/2-( ACC.AD.male+ACC.control.male)/2",
+                                     "(ACC.AD.female- ACC.control.female)/2-( ACC.AD.male-ACC.control.male)/2",
+                                     "ACC.AD.female- ACC.control.female",
+                                     "ACC.AD.male- ACC.control.male",
+                                     "( DLPFC.AD.female+ DLPFC.AD.male)/2-( DLPFC.control.female+ DLPFC.control.male)/2",
+                                     "( DLPFC.AD.female+ DLPFC.control.female)/2-( DLPFC.AD.male+ DLPFC.control.male)/2",
+                                     "( DLPFC.AD.female- DLPFC.control.female)/2-( DLPFC.AD.male- DLPFC.control.male)/2",
+                                     "DLPFC.AD.female- DLPFC.control.female",
+                                     "DLPFC.AD.male- DLPFC.control.male",
+                                     "( PCC.AD.female+ PCC.AD.male)/2-( PCC.control.female+ PCC.control.male)/2",
+                                     "( PCC.AD.female+ PCC.control.female)/2-( PCC.AD.male+ PCC.control.male)/2",
+                                     "( PCC.AD.female- PCC.control.female)/2-( PCC.AD.male- PCC.control.male)/2",
+                                     "PCC.AD.female- PCC.control.female",
+                                     "PCC.AD.male- PCC.control.male"),
                          levels = colnames(FIT$coefficients))
-colnames(contrast) = c('ACC.AD.MALE-ACC.CONTROL.MALE',
-                       'ACC.AD.FEMALE-ACC.CONTROL.FEMALE',
-                       'ACC.AD.ALL-ACC.CONTROL.ALL',
-                       'ACC.ALL.FEMALE-ACC.ALL.MALE',
-                       'ACC.ALL.ALL-ACC.ALL.ALL',
-                       'DLPFC.AD.MALE-DLPFC.CONTROL.MALE',
-                       'DLPFC.AD.FEMALE-DLPFC.CONTROL.FEMALE',
-                       'DLPFC.AD.ALL-DLPFC.CONTROL.ALL',
-                       'DLPFC.ALL.FEMALE-DLPFC.ALL.MALE',
-                       'DLPFC.ALL.ALL-DLPFC.ALL.ALL',
-                       'PCC.AD.MALE-PCC.CONTROL.MALE',
-                       'PCC.AD.FEMALE-PCC.CONTROL.FEMALE',
-                       'PCC.AD.ALL-PCC.CONTROL.ALL',
-                       'PCC.ALL.FEMALE-PCC.ALL.MALE',
-                       'PCC.ALL.ALL-PCC.ALL.ALL'
-                       )
 FIT.CONTR = contrasts.fit(FIT, contrasts=contrast)
@@
 }, FIT.CONTR)
-names(DE) = colnames(contrast)
+names(DE) = c('ACC-AD-CONTROL','ACC-FEMALE-MALE','ACC-AD-CONTROL.IN.FEMALE-MALE','ACC-AD-CONTROL.IN.FEMALE', 'ACC-AD-CONTROL.IN.MALE',
+              'DLPFC-AD-CONTROL','DLPFC-FEMALE-MALE','DLPFC-AD-CONTROL.IN.FEMALE-MALE','DLPFC-AD-CONTROL.IN.FEMALE', 'DLPFC-AD-CONTROL.IN.MALE',
+              'PCC-AD-CONTROL','PCC-FEMALE-MALE','PCC-AD-CONTROL.IN.FEMALE-MALE','PCC-AD-CONTROL.IN.FEMALE', 'PCC-AD-CONTROL.IN.MALE')
 DE = DE %>% 
   rbindlist(idcol = 'Comparison') %>%
-  dplyr::mutate(Comparison = gsub('Tissue.Diagnosis','',Comparison),
-                Study = 'ROSMAP',
+  left_join(GENE.PARAM %>%
+              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
+              unique()) %>%
+  dplyr::mutate(Study = 'ROSMAP', Region = 'DLPFC',
                 Direction = logFC/abs(logFC),
                 Direction = factor(Direction, c(-1,1), c('-1' = 'DOWN', '1' = 'UP')),
-                Direction = as.character(Direction)) %>%
-  left_join(GENE.PARAM %>%
-              dplyr::select(ensembl_gene_id, hgnc_symbol, percentage_gene_gc_content, gene_length) %>%
-              unique())
+                Direction = as.character(Direction))
 DE$Direction[DE$adj.P.Val > 0.05 | abs(DE$logFC) < log2(1.2)] = 'NONE'
-DE$Tissue <- do.call( rbind, strsplit( DE$Comparison, '[.]'))[,1]
-DE$Comparison <- gsub('DLPFC.', '',gsub('ACC.', '', gsub('PCC.', '',  DE$Comparison )))
+writeLines('Differentially expressed genes at an FDR 0.05 and logFC 1.2')
 tmp = DE %>%
-  dplyr::select(ensembl_gene_id, Tissue, Comparison, Direction) %>%
-  group_by(Tissue, Comparison, Direction) %>%
+  dplyr::select(ensembl_gene_id, Region, Comparison, Direction) %>%
+  group_by(Comparison, Direction) %>%
   dplyr::summarise(FDR_0_05_FC_1.2 = length(unique(ensembl_gene_id))) %>%
@@
 kable(tmp)
-DE$Tissue <- do.call( rbind, strsplit( DE$Comparison, '[.]'))[,1]
-all.diff.exp = c(all.diff.exp, list(Diagnosis.SEX = DE))
-all.fit = c(all.fit, list(Diagnosis.SEX = FIT))
+p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
+p = p + scale_color_manual(values = c('green','grey','red')) + theme(legend.position='top')
+p = p + facet_grid(Region+.~Comparison, scales = 'fixed')
+p
+
+all.diff.exp = c(all.diff.exp, list(Diagnosis.Sex = DE))
+all.fit = c(all.fit, list(Diagnosis.Sex = FIT))
 ```
@@
 FIT = lmFit(VOOM.WEIGHTS)
-cntr = c("ACC.AD.age_death-ACC.CONTROL.age_death",
-         "0.5*ACC.AD.age_death+0.5*ACC.CONTROL.age_death",
-         "DLPFC.AD.age_death-DLPFC.CONTROL.age_death",
-         "0.5*DLPFC.AD.age_death+0.5*DLPFC.CONTROL.age_death",
-         "PCC.AD.age_death-PCC.CONTROL.age_death",
-         "0.5*PCC.AD.age_death+0.5*PCC.CONTROL.age_death"
+cntr = c("ACC.AD.age_death-ACC.control.age_death",
+         "0.5*ACC.AD.age_death+0.5*ACC.control.age_death",
+         "DLPFC.AD.age_death-DLPFC.control.age_death",
+         "0.5*DLPFC.AD.age_death+0.5*DLPFC.control.age_death",
+         "PCC.AD.age_death-PCC.control.age_death",
+         "0.5*PCC.AD.age_death+0.5*PCC.control.age_death"
         )

### 2020-12-22 code/2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd
recommit
rerun

@@
 
+#Toss Zero variance genes post residual correct
+COUNT <- COUNT[ (row.names(COUNT) %in% c("ENSG00000239467", "ENSG00000005486", "ENSG00000160972", "ENSG00000165886", "ENSG00000002330", "ENSG00000149823", "ENSG00000139722", "ENSG00000169217", "ENSG00000127774", "ENSG00000122490", "ENSG00000130881", "ENSG00000126005", "ENSG00000171222", "ENSG00000070413", "ENSG00000211459")) == F, ]
+
 Provenance <- 'syn21075913'
@@
 #Filter for Rin Here#
-Meta[ Meta$RIN >= 5 | Meta$sampleid %in% c('380_120503','500_120515'), ]
+Meta <- Meta[ Meta$RIN >= 5 | Meta$sampleid %in% c('380_120503','500_120515'), ]
 
@@
   }, COUNT)
+#filter out non-variable genes post residual removal
+
 genesToAnalyze = unlist(genesToAnalyze) %>% 
@@
   intersect(GENE.LEN$ensembl_gene_id[!is.na(GENE.LEN$gene_length)]) %>%
-  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous"))
+  setdiff(c("N_unmapped", "N_multimapping", "N_noFeature", "N_ambiguous")) %>%
+  setdiff( c("ENSG00000239467", "ENSG00000005486", "ENSG00000160972", "ENSG00000165886", "ENSG00000002330", "ENSG00000149823", "ENSG00000139722", "ENSG00000169217", "ENSG00000127774", "ENSG00000122490", "ENSG00000130881", "ENSG00000126005", "ENSG00000171222", "ENSG00000070413", "ENSG00000211459") )
+
+#18404
+#vs
+#18415
 PROCESSED_COUNTS = getGeneFilteredGeneExprMatrix(COUNT[genesToAnalyze, ], 
@@
 FIT = lmFit(VOOM.WEIGHTS)
-cntr = c('Tissue.Diagnosis.SEXACC.AD.male-Tissue.Diagnosis.SEXACC.CONTROL.male',
-         'Tissue.Diagnosis.SEXACC.AD.female-Tissue.Diagnosis.SEXACC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXACC.AD.male+0.5*Tissue.Diagnosis.SEXACC.AD.female
-         -0.5*Tissue.Diagnosis.SEXACC.CONTROL.male-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXACC.AD.female+0.5*Tissue.Diagnosis.SEXACC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXACC.AD.male-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXACC.AD.female-0.5*Tissue.Diagnosis.SEXACC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXACC.AD.male+0.5*Tissue.Diagnosis.SEXACC.CONTROL.male',
-         'Tissue.Diagnosis.SEXDLPFC.AD.male-Tissue.Diagnosis.SEXDLPFC.CONTROL.male',
-         'Tissue.Diagnosis.SEXDLPFC.AD.female-Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.male+0.5*Tissue.Diagnosis.SEXDLPFC.AD.female
-         -0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.male-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.female+0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXDLPFC.AD.male-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXDLPFC.AD.female-0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXDLPFC.AD.male+0.5*Tissue.Diagnosis.SEXDLPFC.CONTROL.male',
-         'Tissue.Diagnosis.SEXPCC.AD.male-Tissue.Diagnosis.SEXPCC.CONTROL.male',
-         'Tissue.Diagnosis.SEXPCC.AD.female-Tissue.Diagnosis.SEXPCC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXPCC.AD.male+0.5*Tissue.Diagnosis.SEXPCC.AD.female
-         -0.5*Tissue.Diagnosis.SEXPCC.CONTROL.male-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXPCC.AD.female+0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXPCC.AD.male-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female',
-         '0.5*Tissue.Diagnosis.SEXPCC.AD.female-0.5*Tissue.Diagnosis.SEXPCC.CONTROL.female
-         -0.5*Tissue.Diagnosis.SEXPCC.AD.male+0.5*Tissue.Diagnosis.SEXPCC.CONTROL.male')
-contrast = makeContrasts(contrasts=cntr,
+
+colnames(FIT$coefficients) <- gsub( 'Tissue.Diagnosis.SEX','',colnames(FIT$coefficients))
+# Fit contrast
+contrast = makeContrasts(contrasts=c("(ACC.AD.female+ACC.AD.male)/2-(ACC.CONTROL.female+ACC.CONTROL.male)/2",
+                                     "(ACC.AD.female+ACC.CONTROL.female)/2-(ACC.AD.male+ACC.CONTROL.male)/2",
+                                     "(ACC.AD.female-ACC.CONTROL.female)/2-(ACC.AD.male-ACC.CONTROL.male)/2",
+                                     "ACC.AD.female-ACC.CONTROL.female",
+                                     "ACC.AD.male-ACC.CONTROL.male",
+                                     "(DLPFC.AD.female+DLPFC.AD.male)/2-(DLPFC.CONTROL.female+DLPFC.CONTROL.male)/2",
+                                     "(DLPFC.AD.female+DLPFC.CONTROL.female)/2-(DLPFC.AD.male+DLPFC.CONTROL.male)/2",
+                                     "(DLPFC.AD.female-DLPFC.CONTROL.female)/2-(DLPFC.AD.male-DLPFC.CONTROL.male)/2",
+                                     "DLPFC.AD.female-DLPFC.CONTROL.female",
+                                     "DLPFC.AD.male-DLPFC.CONTROL.male",
+                                     "(PCC.AD.female+PCC.AD.male)/2-(PCC.CONTROL.female+PCC.CONTROL.male)/2",
+                                     "(PCC.AD.female+PCC.CONTROL.female)/2-(PCC.AD.male+PCC.CONTROL.male)/2",
+                                     "(PCC.AD.female-PCC.CONTROL.female)/2-(PCC.AD.male-PCC.CONTROL.male)/2",
+                                     "PCC.AD.female-PCC.CONTROL.female",
+                                     "PCC.AD.male-PCC.CONTROL.male"),
                          levels = colnames(FIT$coefficients))

### 2020-12-23 code/2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd
update CasevCntrl

@@
 Meta <- load( Meta_OBJ$path )
+
+clean_md$diagnosis <- as.character('OTHER')
+clean_md$diagnosis[ as.numeric(as.character(clean_md$cogdx)) == 1 & 
+                    as.numeric(as.character(clean_md$braaksc)) <= 3 & 
+                    as.numeric(as.character(clean_md$ceradsc)) >= 3] <- as.character('CONTROL')
+
+clean_md$diagnosis[as.numeric(as.character(clean_md$cogdx)) == 4&
+                   as.numeric(as.character(clean_md$braaksc)) >= 4 & 
+                   as.numeric(as.character(clean_md$ceradsc)) <= 2] = as.character('AD')
+clean_md$diagnosis <- as.factor(clean_md$diagnosis)
+
+import_metadata$diagnosis <- as.character('OTHER')
+import_metadata$diagnosis[ as.numeric(as.character(import_metadata$cogdx)) == 1 & 
+                           as.numeric(as.character(import_metadata$braaksc)) <= 3 &
+                           as.numeric(as.character(import_metadata$ceradsc)) >= 3 ] = 'CONTROL'
+
+import_metadata$diagnosis[ as.numeric(as.character(import_metadata$cogdx)) == 4 & 
+                           as.numeric(as.character(import_metadata$braaksc)) >= 4 & 
+                           as.numeric(as.character(import_metadata$ceradsc)) <= 2] = 'AD'
+import_metadata$diagnosis <- as.factor(import_metadata$diagnosis)
 

### 2020-12-28 code/2020_12_09_ROSMAP_RinEQGt5_TWASDiagnosis_Regress_hg38.Rmd
TWAS ROSMAP

--- 2020-12-22 code/2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd
@@
 #_# ADD DIAGNOSIS HERE TO REGRESS FOR TWAS
-postAdjustCovars = c(postAdjustCovars, names(which.max(covariatesEffects))) %>% unique()
+postAdjustCovars = c(postAdjustCovars,"Diagnosis", names(which.max(covariatesEffects))) %>% unique()
 loopCount = 0 
@@
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = '"syn23640229"';
+parentId = 'syn20798011';
 activityName = 'Covariate Regression';
 activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd'
+thisFileName <- '2020_12_09_ROSMAP_RinEQGt5_TWASDiagnosis_Regress_hg38.Rmd'
 # Github link
@@
 activityName = 'Covariate Regression';
-activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-
-CODE <- syn_temp$store(synapseclient$Folder(name = "RinOver5_RosMap_OldCode", parentId = "syn23640229"))
-
-Syns_Used <- c( "syn23625835", "syn23625835",
-                "syn23573928", "syn21075913",
-                "syn23593968"
-              )
+activityDescription = 'Covariate analysis and Regression of AD Diagnosis and aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
+CODE <- syn_temp$store(synapseclient$Folder(name = "Full_RosMap_RinOver5", parentId = parentId))
+
+Syns_Used <- ALL_USED_IDs
 # Set annotations
@@
   assay	 = 'RNAseq',
-  tissueTypeAbrv	= 'DLPFC', 
+  tissueTypeAbrv	= c('ACC','PCC','DLPFC'), 
   study = 'ROSMAP', 
@@
   rnaquantification = 'RSEM',
-  genomeAssemblyID = 'GRCh37'
+  genomeAssemblyID = 'GRCh38'
 )
 # Store SVA results
-write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Corrected.tsv', sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Corrected.tsv', name = 'Normalised, covariates, and surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(RESIDUAL.SVA.GENE_EXPRESSION, file = 'ROSMAP_SVA_Diagnosis_Corrected.tsv', sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Corrected.tsv', name = 'Normalised, covariates, surrogate and Diagnosis variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
-write.table(COVARIATES, file = 'ROSMAP_SVA_Covariates.tsv', row.names = F, sep = '\t', quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+write.table(COVARIATES, file = 'ROSMAP_SVA_Diagnosis_Covariates.tsv', row.names = F, sep = '\t', quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_SVA_Diagnosis_Covariates.tsv', name = 'Covariates', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'covariates'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (filtered raw)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_eCounts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_eCounts.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Counts.tsv', name = 'Counts (estimated)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'estimatedCounts'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'filteredLCPM'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_offset.tsv', name = 'Gene length and GC content offset', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'offset'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_Design.tsv', name = 'Design Matrix', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'designMatrix'
@@
   rownameToFirstColumn('SampleID') %>%
-  write.table(file = 'ROSMAP_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_SurVar.tsv', name = 'Surrogate Variables', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'surrogateVariables'
@@
   rownameToFirstColumn('ensembl_gene_id') %>%
-  write.table(file = 'ROSMAP_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Regressed_netResidualExpression.tsv', name = 'Normalised, and covariates removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  write.table(file = 'ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DLPFC_Diagnosis_Regressed_netResidualExpression.tsv', name = 'Normalised, covariates and Diagnosis removed residual expression (for network analysis)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   all.annotations$dataSubType = 'residualGeneExpForNetAnlz'
-  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
-
-# Store differential expression results
-rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
-  write.table(file = 'ROSMAP_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-  all.annotations$dataSubType = 'Diff_Exp'
-  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
-
-# Store NeuroPath results
-write.csv(Master, file = '~/NeuroPath_Regression/Neuropathology_Scores.csv',  row.names =F)
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='~/NeuroPath_Regression/Neuropathology_Scores.csv', name = 'Neuropath Scores', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-  all.annotations$dataSubType = 'Diff_Exp'
-  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
-
-# Store all differential expression models
-save(all.fit, file = 'ROSMAP_Models.RData')
-ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAP_Models.RData', name = 'All Limma Models', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-  all.annotations$dataSubType = 'RData'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 
-createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd",
-                                          parentId ="syn23640229",
-                                          folderName = 'RinOver5_RosMap_OldCode')
-
-```
+  createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5_TWASDiagnosis_Regress_hg38.Rmd",
+                                          parentId ="syn20798011",
+                                          folderName = 'Full_RosMap_RinOver5')
+
+```

### 2021-01-04 code/Ancestry_PCA_Add_CMC.Rmd
CMC Genos

--- 2019-10-04 code/Ancestry_PCA.Rmd
@@
 ## Pull Plink and Plink2
-```{bash PLINKSetup, results='hide', echo=TRUE}
+run before sourcing markdown file as plink2 binary url keeps changing.
+```{bash PLINKSetup, results='hide', eval=F, echo=TRUE}
 mkdir ~/TWAS/bin
@@
 unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
-wget -q -P ~/TWAS/bin  http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191002.zip
-unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191002.zip
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191005.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191005.zip
+
+wget -q -P ~/TWAS/code http://www.compgen.pitt.edu/GemTools/GemTools.R
 
@@
 
-##Pull VCF Files from Synapse
+##Pull VCF Files from Synapse & Convert VCFs to plink
 mkdir VCF
-synapse get -r syn11707204 --downloadLocation VCF/
-
-##Convert VCFs to plink
 mkdir GWAS_Plink
 
-rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_X*
-rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_Y*
-rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_others*
-rm -r VCF/WGS_JointCalling/
-rm VCF/SYNAPSE_METADATA_MANIFEST.tsv
+declare -A SynArr
+Arr["1"]=syn11714454
+Arr["2"]=syn11714459
+Arr["3"]=syn11714456
+Arr["4"]=syn11714491
+Arr["5"]=syn11714462
+Arr["6"]=syn11714481
+Arr["7"]=syn11714486
+Arr["8"]=syn11714490
+Arr["9"]=syn11714471
+Arr["10"]=syn11714487
+Arr["11"]=syn11714464
+Arr["12"]=syn11714494
+Arr["13"]=syn11714485
+Arr["14"]=syn11714482
+Arr["15"]=syn11714499
+Arr["16"]=syn11714474
+Arr["17"]=syn11714473
+Arr["18"]=syn11714493
+Arr["19"]=syn11714451
+Arr["20"]=syn11714496
+Arr["21"]=syn11714458
+Arr["22"]=syn11714483
 
-#Convert to PLINK
-for i in {22..1}
+declare -A SynArr
+ARR["1"]=syn11714463
+ARR["2"]=syn11714480
+ARR["3"]=syn11714492
+ARR["4"]=syn11714452
+ARR["5"]=syn11714488
+ARR["6"]=syn11714484
+ARR["7"]=syn11714465
+ARR["8"]=syn11714475
+ARR["9"]=syn11714450
+ARR["10"]=syn11714479
+ARR["11"]=syn11714477
+ARR["12"]=syn11714468
+ARR["13"]=syn11714469
+ARR["14"]=syn11714470
+ARR["15"]=syn11714461
+ARR["16"]=syn11714455
+ARR["17"]=syn11714467
+ARR["18"]=syn11714495
+ARR["19"]=syn11714497
+ARR["20"]=syn11714478
+ARR["21"]=syn11714460
+ARR["22"]=syn11714472
+
+for i in {1..22}
 do
+
+	synapse get ${Arr[$i]} --downloadLocation VCF/
+  synapse get ${ARR[$i]} --downloadLocation VCF/
   plink --vcf VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.gz --threads $CORES --make-bed --silent --allow-no-sex --snps-only --out GWAS_Plink/MSSB_Chr_$i
-  #rm VCF/NIA_JG_1898_samples_GRM_WGS_b37_JointAnalysis01_2017-12-08_$i\.recalibrated_variants.MSSM.vcf.*
+  rm VCF/*.vcf.gz
+  rm VCF/*.vcf.gz.tbi
 done
-#rm -r VCF/
 
@@
 ### Finalize the MSBB LD SNP-Set Derived from WGS
-```{bash FinalizeMSBB, echo=T, results='hide', cache = FALSE  }
+```{bash FinalizeMSBB, echo=T, results='hide', cache = FALSE}
 #source /root/.bashrc
@@
 
+#Make Room for ROMAP Data
+rm -r VCF/
+rm -r GWAS_Plink/
+
 #Synapse gets:
-declare -A SynArr
+declare -A arr
 arr["1"]=syn5879161
@@
 
+plink --bfile MSBB_Preliminary_Genos --write-snplist --out KEEPERS
+
 #Loop Through chromosomes and Process
 for i in {1..22}
+#for i in {2..12}
 do
@@
   #Convert to plink hard calls 
-	plink2 --threads $CORES --fam Updated_Actual_Fam.fam --silent --import-dosage plink.out.dosage format=1 --hard-call-threshold 0.1 --make-bed --out AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$chr
+	plink2 --threads $CORES --fam Updated_Actual_Fam.fam --silent --import-dosage plink.out.dosage format=1 --hard-call-threshold 0.1 --make-bed --extract KEEPERS.snplist --out AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$chr
 
@@
 rm b.txt
-##Merge Chromsomes in Plink Format 
-echo AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr2 > MergedGWAS.txt
+
+plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr1 --bmerge AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr2.bed AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr2.bim AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr2.fam --make-bed --allow-no-sex --out ROSMAP_Temp
+
+rm ROSMAP_Temp.log
+mv ROSMAP_Temp.bed Temp.bed
+mv ROSMAP_Temp.bim Temp.bim
+mv ROSMAP_Temp.fam Temp.fam
+
+rm Broad_AffymetrixGenechip6_Imputed_chr2.bed
+rm Broad_AffymetrixGenechip6_Imputed_chr2.bim
+rm Broad_AffymetrixGenechip6_Imputed_chr2.fam
+rm Broad_AffymetrixGenechip6_Imputed_chr1.bed
+rm Broad_AffymetrixGenechip6_Imputed_chr1.bim
+rm Broad_AffymetrixGenechip6_Imputed_chr1.fam
+
 for i in {3..22}
 do
-    echo AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i >> MergedGWAS.txt
+
+  plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i --bmerge Temp.bed Temp.bim Temp.fam --make-bed --allow-no-sex --extract KEEPERS.snplist --out ROSMAP_Temp
+
+  #Remove the old indv chr files
+  #rm AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i\.bed
+  #rm AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i\.bim
+  #rm AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i\.fam
+  #rm AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr$i\.log
+
+  #Move New Back to Temp
+  mv ROSMAP_Temp.bed Temp.bed
+  mv ROSMAP_Temp.bim Temp.bim
+  mv ROSMAP_Temp.fam Temp.fam
+  mv ROSMAP_Temp.log Temp.log
+
 done
 
-plink --threads $CORES --bfile AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr1 --silent --merge-list MergedGWAS.txt  --make-bed --allow-no-sex --out ROSMAP_Temp
+mv Temp.bed ROSMAP_Temp.bed 
+mv Temp.bim ROSMAP_Temp.bim 
+mv Temp.fam ROSMAP_Temp.fam 
+mv Temp.log ROSMAP_Temp.log
 
-rm -r AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr*
-rm MergedGWAS.txt
+```
+
+#### Temp Break
+```{bash FOO, echo=T, results='hide', cache = FALSE}
+PATH=$PATH:~/TWAS/bin/
+CORES=`expr $(nproc) - 2`
+
+#rm -r AMP-AD_ROSMAP_Rush-Broad_AffymetrixGenechip6_Imputed_chr*
+#rm MergedGWAS.txt
 
@@
 plink --threads $CORES --bfile ROSMAP_Temp --extract RosMapKeeps.txt --silent --make-bed --allow-no-sex --out ROSMAP_temp
-rm ROSMAP_Temp.*
+#rm ROSMAP_Temp.*
 rm RSIDS.txt
@@
 
+##CMC Genotypes
+```{bash CMC, cache = FALSE, echo=T, results='hide'}
+CORES=`expr $(nproc) - 2`
+PATH=$PATH:~/TWAS/bin/
+
+#Pull Data with needed SNPS only and fiter GTEx for that SNP List
+synapse get syn20835005
+synapse get syn20835007
+synapse get syn20834996
+plink --threads $CORES --bfile All_CEU_ToTrainForTWAS --write-snplist
+
+mkdir CMC_Genos
+synapse get syn10537112 --recursive --downloadLocation CMC_Genos/
+
+mkdir CMC_Filt_Genos
+touch merge.txt
+#Pull out Snps
+for i in {1..22}
+  do
+    #--positions plink.snplist 
+    bcftools norm --threads $CORES --rm-dup snps -Oz CMC_Genos/CMC_chr$i.dose.vcf.gz > CMC_Filt_Genos/Filt_CMC_chr$i.dose.vcf.gz
+    vcftools --gzvcf CMC_Filt_Genos/Filt_CMC_chr$i.dose.vcf.gz --plink --out CMC_Filt_Genos/Init_Filtered_chr$i
+    echo 'CMC_Filt_Genos/Init_Filtered_chr'$i'.ped CMC_Filt_Genos/Init_Filtered_chr'$i'.map' >> merge.txt
+  done
+grep -v 'chr1.ped' merge.txt > foo
+mv foo merge.txt
+
+#Merge Genotype
+plink --threads $CORES --file CMC_Filt_Genos/Init_Filtered_chr1 --merge-list merge.txt --make-bed --out Merged_Initial_CMC_Geno
+
+#Remove old Map/Ped Files
+rm CMC_Filt_Genos/Init_Filtered_chr*.map
+rm CMC_Filt_Genos/Init_Filtered_chr*.ped
+```
+
+### ReName the CMC SNPS so the can be combined
+```{python ReNamer_ONE, echo=F, results='hide',python.reticulate=T}
+import sys
+import os
+import re
+
+InFile = 'All_CEU_ToTrainForTWAS.bim'
+InFileb = 'Merged_Initial_CMC_Geno.bim' #LDREF_FiltSNPs.bim
+
+RS_IDs = {}
+RS_Pos = {}
+
+F1 = open(InFile)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
+	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
+F1.close()
+
+#Open Output
+OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )
+
+F1 = open(InFileb)
+for line in F1:
+	LINE = line.rstrip('\r\n')
+	lst = LINE.split('\t')
+	if( ''.join([ lst[0], "_", lst[3] ]) in RS_IDs):
+		Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
+		Entry = '\t'.join([ lst[0], Name, lst[2], lst[3], lst[4], lst[5] ])
+		print >>OUT, Entry
+	else:
+		print >>OUT, LINE
+
+F1.close()
+OUT.close()
+```
+
 ##Merge the Genotype Sets and Preform PCA
@@
 CORES=`expr $(nproc) - 2`
+
+#Replace CMC names with renamed
+mv Merged_Initial_CMC_GenoRenamed.bim Merged_Initial_CMC_Geno.bim
 
@@
 plink --threads $CORES --bfile Mayo_Preliminary_Genos --silent --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out Mayo_4_Merge
+plink --threads $CORES --bfile Merged_Initial_CMC_Geno --silent --exclude Total_Remove.snplist --extract All_CommonSNPs.snplist --make-bed --out CMC_4_Merge
 
@@
 echo "Mayo_4_Merge" >> Merge.list
+echo "CMC_4_Merge" >> Merge.list
 
@@
 ## Prep Input for Cluster Based on Ancestry
-```{bash CLustPrep, cache = FALSE}
-source /root/.bashrc
-PATH=$PATH:/home/jgockley/TWAS/TWAS/bin/
+```{bash CLustPrep, echo=T, cache = FALSE}
+#source /root/.bashrc
+PATH=$PATH:~/TWAS/bin/
 CORES=`expr $(nproc) - 2`
-wget http://www.compgen.pitt.edu/GemTools/GemTools.R
+#wget http://www.compgen.pitt.edu/GemTools/GemTools.R
 
@@
 rm peds.txt
-AllSnps4GemClust.*
 ```
@@
 ##Plot PCA
-```{r PlotPCA, cache = FALSE, echo=FALSE}
+```{r PlotPCA, cache=FALSE, echo=FALSE}
 library(ggplot2)
@@
 library(data.table)
+system( 'wget http://www.compgen.pitt.edu/GemTools/GemTools.R' )
 source('GemTools.R')
@@
 row.names(Ref1000G) <- paste0(Ref1000G[,1], "_",Ref1000G[,2] )
+CMC <- read.table(file = "CMC_4_Merge.fam", header =F, sep =" ")
+row.names(CMC) <- paste0(CMC[,1], "_",CMC[,2] )
 
@@
 names(Gs) <- row.names(Ref1000G)
+CMCs  = rep("CMC", length(row.names(CMC)) )
+names(CMCs) <- row.names(CMC)
 
@@
 
-SampleCohort <- c( RMs, MSBs, Mays, CEUs, YRIs, CHBs, JPTs)
+SampleCohort <- c( RMs, MSBs, Mays, CMCs, CEUs, YRIs, CHBs, JPTs)
 pcs$SampleCohort <- as.factor( SampleCohort[ row.names(pcs) ] )
-pcs$SampleCohort <- factor(pcs$SampleCohort, levels = c("MAYO", "MSBB", "ROSMAP", "YRI", "CHB", "CEU", "JPT"))
+pcs$SampleCohort <- factor(pcs$SampleCohort, levels = c("MAYO", "MSBB", "ROSMAP", "CMC", "YRI", "CHB", "CEU", "JPT"))
 
-SampleType <- c( RMs, MSBs, Mays, Gs )
+SampleType <- c( RMs, MSBs, Mays, Gs, CMCs )
 pcs$SampleType <- as.factor( SampleType[ row.names(pcs) ] )
@@
 #multiplot(plotlist = p, rows = 3)
+
+p[[4]] = ggplot(pcs[pcs$SampleCohort %in% c( 'CEU', 'JPT', 'CHB', 'YRI', 'CMC' ),], aes( PC1, PC2) ) + geom_point( aes(colour = SampleCohort, shape = SampleType), cex=.8, alpha = 4/10)
+p[[4]] = p[[4]] + xlab(paste0( "PC1 ", signif( PC1_Var_exp*100, 3), "%" )) 
+p[[4]] = p[[4]] + ylab(paste0( "PC2 ", signif( PC2_Var_exp*100, 3), "%" ))  
+p[[4]] = p[[4]] + ggtitle("CMC Ancestry PCA Analysis") + theme(plot.title = element_text(hjust = 0.5))
+#multiplot(plotlist = p, rows = 3)
+
 p[[1]]
@@
 p[[3]]
+p[[4]]
 
@@
 #Only Consider Comps that explain > 1% of Variance
-Upper <- as.numeric(table(Comps[,1]/sum(Comps[,1])>0.01)["TRUE"])
+Upper <- as.numeric(table(Comps[,1]/sum(Comps[,1])>0.02)["TRUE"])
 EC_foo.cluster = clusterGem(gnt = gnt, id = ids, min.dim = 3, max.dim = Upper)
 
+# EC_foo.cluster = clusterGem(gnt = gnt, id = ids, min.dim = 3, max.dim = 3)
 Refs <- pcs[ pcs$SampleType == '1000G', ]
@@
 CEU_Clusters <- c(names( table(EC_foo.cluster$clusters[ names(EC_foo.cluster$clusters) %in% names(CEUs) == T ]) ))
+CEU_Clusters <- c(names( table(EC_foo.cluster$clusters[ names(EC_foo.cluster$clusters) %in% row.names(CEU) == T ]) ))
+
 pcs <- cbind( pcs, Cluster = EC_foo.cluster$clusters)
@@
 activityDescription = 'Processing and Analysis of WGS and Genotype data along with ancestry analysis with 1000 genome\'s CEU, CHB, YRI, and JPT populations';
-thisFileName <- 'Ancestry_PCA.Rmd'
+thisFileName <- 'Ancestry_PCA_Add_CMC.Rmd'
 # Github link
@@
 parentId = 'syn18936948';
-activityName = 'Ancestry Analysis';
-activityDescription = 'Processing and Analysis of WGS and Genotype data along with ancestry analysis with 1000 genome\'s CEU, CHB, YRI, and JPT populations';
+activityName = 'Ancestry Analysis with CMC';
+activityDescription = 'Processing and Analysis of WGS and Genotype data from MAYO, CMC, MSBB, and ROSMAP along with ancestry analysis with 1000 genome\'s CEU, CHB, YRI, and JPT populations';
 
-# Code WTF is this??
-CODE <- Folder(name = "Ancestry_Analysis", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Analysis_with_CMC", parentId = parentId))
 
@@
                "syn5879827", "syn5879828", "syn5879830", "syn5879832", "syn5879834", 
-               "syn5879835", "syn5879836", "syn5879837", "syn5879838", "syn20809809")
+               "syn5879835", "syn5879836", "syn5879837", "syn5879838", "syn20809809",
+               "syn20835005", "syn20835007", "syn20834996")
 
@@
   assay	 = c('Genotype Array', "WGS"),
-  tissueTypeAbrv	= c('TCX', "FP", 'IFG', 'PHG', 'STG', 'DLPFC', 'CBE'), 
+  tissueTypeAbrv	= c('TCX', 'ACC', 'PCC', "FP", 'IFG', 'PHG', 'STG', 'DLPFC', 'CBE'), 
   study = c('MAYO', 'ROSMAP', 'MSBB'), 
@@
   rnaquantification = '',
-  genomeAssemblyID = 'GRCh37'
+  genomeAssemblyID = 'GRCh38'
 )
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryClustered_INDVs.tsv', name = 'Samples Clustered to CEU Ancestry', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-EXP.all.annotations$dataSubType = 'CEU_INDV'
+  all.annotations$dataSubType = 'CEU_INDV'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Total_PCA.eigenvec', name = 'PCA Eigen Vectors', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-EXP.all.annotations$dataSubType = 'EigenVecs'
+  all.annotations$dataSubType = 'EigenVecs'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Total_PCA.eigenval', name = 'PCA Eigen Values', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-EXP.all.annotations$dataSubType = 'EigenValues'
+  all.annotations$dataSubType = 'EigenValues'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ###Store Genos Seperatly 
-CODE <- Folder(name = "Ancestry_Clustered_Genotypes", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Clustered_Genotypes_with_CMC", parentId = parentId))
 
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.bed', name = 'Genotype Bed File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-EXP.all.annotations$dataSubType = 'GWAS'
+  all.annotations$dataSubType = 'GWAS'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.bim', name = 'Genotype Bim File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-EXP.all.annotations$dataSubType = 'GWAS'
+  all.annotations$dataSubType = 'GWAS'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.fam', name = 'Genotype Fam File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-  EXP.all.annotations$dataSubType = 'GWAS'
+  all.annotations$dataSubType = 'GWAS'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.nosex', name = 'Genotype nosex File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-  EXP.all.annotations$dataSubType = 'GWAS'
+  all.annotations$dataSubType = 'GWAS'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='CEU_AncestryMatched_Genotypes.log', name = 'Genotype log File', parentId=CODE$properties$id ), used = Syns_Used, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
-  EXP.all.annotations$dataSubType = 'GWAS'
+  all.annotations$dataSubType = 'GWAS'
   syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
@@
 
-```{bash Clean, echo=T, eval=F, results='hide'}
-rm -r ~/TWAS/bin/
+```{bash Clean, echo=F, results='hide'}
+#rm -r ~/TWAS/bin/
+rm -r 1000G_RefSamps/
 rm *.bed
@@
 rm *.log
+rm *.nosex
 rm *.tsv
 rm *list
-rm -r VCF/
-rm -r GWAS_Plink/
+rm *.txt
+rm *.panel
+rm *.irem
+rm *.eigen*
+rm *.prune.*
+rm *.missnp
+rm *.out
+rm AllSnps4GemClust.*
 ```
@@
 
-createAndKnitToFolderEntityClient(file = "Ancestry_PCA.Rmd",
+createAndKnitToFolderEntityClient(file = "Ancestry_PCA_Add_CMC.Rmd",
                                           parentId ="syn18936948",
-                                          folderName = 'Ancestry_Analysis')
+                                          folderName = 'Ancestry_Analysis_with_CMC')
 ```

### 2021-01-09 code/ProcessData_CMC.Rmd
New Process Data

---
title: "Process RNA-Seq and Genotype Data for TWAS"
author: "JKG"
date: "9/25/2019"
output: pdf_document
  chunk_output_type: console
---

```{r libs, include=FALSE}
knitr::opts_chunk$set(
  echo=FALSE,
  warning=FALSE,
  message=FALSE,
  error = FALSE,
  tidy = FALSE,
  cache = TRUE,
  results='hide')
#library(reticulate)
```
##Before running 
Run the following in docker exec -it <CONTAINER> /bin/bash 
chmod 777 /root/
mv TWAS/ /home/<USR>/TWAS/
chown -hR <GID>:<USR> /home/<USR>/TWAS/
Create a ~/.synapseConfig file in the container, but do not push a container containing your credentials file to Docker Hub!!!

## Login to Synapse Will need to replace with your credentials
```{bash Login, echo=T, results='hide', eval=FALSE}
#source /root/.bashrc
synapse login -u <USR> -p <PSWD> --rememberMe

#Alternativly you can setup a credentials file as such:
touch ~/.synapseConfig
echo "[authentication]" >> ~/.synapseConfig
echo "username = <USR>" >> ~/.synapseConfig
echo "password = <PASWD>" >> ~/.synapseConfig
```

```{bash PLINKSetup, results='hide', eval=FALSE, echo=TRUE}
mkdir ~/TWAS/bin
wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20190617.zip 
unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191015.zip
unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191015.zip

rm ~/TWAS/bin/*.zip
rm ~/TWAS/bin/toy.*
rm ~/TWAS/bin/LICENSE
```

## MSBB RNA-Seq: Label Brain Regions, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
```{r MSBBRNA, results='hide', echo=TRUE, cache = FALSE}
library(data.table)

Process_MSBB <- function( dna, exp, id){
  #'@dna synID of Geno samples eg 'syn11384608'
  #'@exp synID of expression data eg 'syn8485026'
  #'@id synID of RNA id translators  eg. 'syn6100548'

  DNA <- fread(syn_temp$get(dna)$path)
  Expression <- read.table(syn_temp$get(exp)$path, header=T, row.names = 1)
  IDs <- fread(syn_temp$get(id)$path)
  sink <- Expression

  #Make sample IDs the row names
  IDs <- IDs[ IDs$Action != 'Exclude', ]
  ###Convert to Z-Value by Tissue
  Regions <- names( table(IDs$BrodmannArea) ) 
  for( BM in Regions ){
    temp <- Expression[ ,colnames(Expression)[ colnames(Expression) %in% IDs[ IDs$BrodmannArea == BM, ]$sampleIdentifier] ]
    foo <- apply(temp, 1, scale)
    foo <- t(foo)
    colnames(foo) <- colnames(temp)
    Expression[ , colnames(foo)] <- foo [, colnames(foo)]
  }

  IDs <- IDs[ (IDs$sampleIdentifier %in% colnames(Expression)) == T, ]
  Expression <- Expression[ , colnames(Expression)[(colnames(Expression) %in% IDs$sampleIdentifier) == T] ]
  INDVs <- IDs[ IDs$fileType=='fastq' , ]

  DNA <- as.data.frame(DNA)
  DNA[ is.na(DNA$individualIdentifier)==T,]$individualIdentifier <- DNA[ is.na(DNA$individualIdentifier)==T,]$individualIdentifier.inferred
  DNA <- DNA[ complete.cases(DNA$individualIdentifier), ]
  DNA <- DNA[ DNA$Action != "Exclude", ]
  row.names(DNA) <- DNA$individualIdentifier

  INDVs <- IDs[ !duplicated(IDs$sampleIdentifier) ]
  INDVs <- INDVs[ (INDVs$individualIdentifier %in% DNA$individualIdentifier) == T, ]

  DNA <- as.data.frame(DNA)
  DNA <- DNA[ complete.cases(DNA$individualIdentifier), ]
  row.names(DNA) <- DNA$individualIdentifier

  INDVs <- as.data.frame(INDVs)
  INDVs$GenoID <- DNA[ INDVs$individualIdentifier, ]$sampleIdentifier
  INDVs$NewID <- paste0( INDVs$BrodmannArea, '_' , INDVs$GenoID )
  row.names(INDVs) <- INDVs$sampleIdentifier
  INDVs[ colnames(Expression), ]$NewID

  Expression <- Expression[ , colnames(Expression)[(colnames(Expression) %in% INDVs$sampleIdentifier) == T] ]
  INDVs <- as.data.frame(INDVs)
  row.names(INDVs) <- INDVs$sampleIdentifier
  colnames(Expression) <- INDVs[ colnames(Expression), ]$NewID

  return( Expression )
}

Norm_Resid_MSBB <- Process_MSBB('syn11384608', 'syn8485026', 'syn6100548')
dCorrect_Resid_MSBB <- Process_MSBB('syn11384608', 'syn20801798', 'syn6100548')
```

## Mayo RNA-Seq: Remove Cerebellum, Filter for INDV. w/Genotype Data, Rename Samples with Genotype ID 
```{r MayoRNA, results='hide', echo=TRUE, cache = FALSE}
#Get Geno Names From FAM File  #-old:syn20820122
FAM <- as.data.frame(fread( syn_temp$get('syn23674977')$path))
FAM <- FAM[ (grepl('ROS', FAM[,1])) == F , ]
FAM <- FAM[ (grepl('MAP', FAM[,1])) == F , ]
FAM <- FAM[ (grepl('ROS', FAM[,2])) == F , ]
FAM <- FAM[ (grepl('MAP', FAM[,2])) == F , ]
FAM <- FAM[ FAM[,1] == 0, ]

#Filter Expression Samples by Presence of a Genotype
Mayo_filt <- function( syn, fam, Type ){
  #'@syn A synID for the RNA Seq eg. 'syn20801999' or 'syn20801991'
  #'@fam A fam file eg. FAM
  #'@Type fread = 0 read.table=1

  #syn <- 'syn20801991'
  #fam <- FAM
  #Type <- 1

  fam <- FAM
  if( Type == 0){
    RNA <- read.table( syn_temp$get(syn)$path)
    colnames(RNA) <- gsub('_TCX', '_a', colnames(RNA))
    colnames(RNA) <- gsub('X', '', colnames(RNA))
    colnames(RNA) <- gsub('_a', '_TCX', colnames(RNA))
    RNA <- cbind( 'ensembl_gene_id' = row.names(RNA), RNA[,colnames(RNA)] )
    RNA <- RNA[ , colnames(RNA)[(grepl('_TCX', colnames(RNA))==T)] ]
  }else{
    RNA <- as.data.frame( fread( syn_temp$get(syn)$path ) )
    row.names(RNA) <- RNA$ensembl_gene_id
    RNA <- RNA[ , colnames(RNA)[(grepl('_TCX', colnames(RNA))==T)] ]
  }
  colnames( RNA ) <- gsub( '_TCX', '', colnames( RNA ) )
  colnames( RNA ) <- paste0( '0_', colnames( RNA ) )

  ## Z-Scale
  foo <- as.matrix(RNA)
  foo <- apply(RNA, 1, scale)
  foo <- t(foo)
  colnames(foo) <- colnames(RNA)
  #Expression[ , colnames(foo)] <- foo [, colnames(foo)]

  RNA <- foo[ , colnames(foo)[ (colnames(foo) %in% paste0( FAM[,1], "_", FAM[,2] )) == T ] ]
  return(RNA)
}
Norm_Resid_MAYO <- Mayo_filt( 'syn8466825', FAM, 1 )
dCorrect_Resid_MAYO <- Mayo_filt( 'syn20801991', FAM, 0 )
```

## ROSMAP RNA-Seq: Filter for INDV. w/Genotype Data and Rename Samples with Genotype ID 
```{r ROSMAPoRNA, results='hide', echo=TRUE, cache = FALSE}
#SVA: 'syn8456704'
#SVA+Diag: 'syn20800652'
Ros_Filt <- function(Exp, name, Trans, Fam, Var){
  #'@Exp the expression matrix eg. 'syn23666495'
  #'@name another name file eg. 'syn5879839'
  #'@Trans 'syn3382527'
  #'@Fam a .fam file of the ROS samps syn23674977
  #'@Var 1=Nondiagnosis correcte 0=Diagnosis Corrected
  # eg. Ros_Filt( 'syn23666495', 'syn5879839', 'syn3382527','syn23674977')

  FAM <- as.data.frame(fread( syn_temp$get(Fam)$path))
  Fam <- FAM[ (grepl('ROS', FAM[,1])) == T | (grepl('MAP', FAM[,1])) == T | (grepl('ROS', FAM[,2])) == T | (grepl('MAP', FAM[,2])) == T, ]
  InvFam <- FAM[ (grepl('ROS', FAM[,1])) == F & (grepl('MAP', FAM[,1])) == F & (grepl('ROS', FAM[,2])) == F & (grepl('MAP', FAM[,2])) == F, ]
  Fam[,1] <- Fam[,2]

  #Need to assign sex to MSBB and Mayo
  NAMED_FAM <- rbind( InvFam[1:dim(InvFam)[1], ],  Fam[1:dim(Fam)[1], ] )

  if(Var == 1){
    #Exp <- as.data.frame( fread(syn_temp$get(Exp)$path, row.names=1) )
     Exp <- as.data.frame( read.table(syn_temp$get(Exp)$path) )
     colnames(Exp) <- gsub('X','', colnames(Exp))
     Exp <- cbind(row.names(Exp), Exp[1:dim(Exp)[2]])
     colnames(Exp)[1] <- 'ensembl_gene_id'
  }else{
    if(Var == 0){
        #Exp <- as.data.frame( read.table(syn_temp$get('syn20800652')$path) )
        Exp <- as.data.frame( read.table(syn_temp$get(Exp)$path) )
        colnames(Exp) <- gsub('X','', colnames(Exp))
        Exp <- cbind(row.names(Exp), Exp[1:dim(Exp)[2]])
        colnames(Exp)[1] <- 'ensembl_gene_id'
    }else{}
  }
  Trans <- fread(syn_temp$get(Trans)$path)
  Trans <- Trans[ Trans$gwas_id != "", ]
  names <- as.data.frame(fread(syn_temp$get(name)$path))
  Trans <- Trans[ (Trans$gwas_id  %in%  names[,2]) == T, ]
  #Trans <- Trans[ (Trans$rnaseq_id == "") == F, ]
  #Trans <- Trans[ !duplicated(Trans$rnaseq_id), ]

  ## Z-Scale - *By Tissue*
  Covariates <- read.table( syn_temp$get('syn23666496')$path, header=T, sep='\t' )
  #row.names(Covariates) <- do.call( rbind, strsplit( as.character(Covariates$SampleID),  "[.]" ))[,1]
  row.names(Covariates) <- as.character( Covariates$SampleID )
  colnames(Exp) <- gsub( '[.]', '-', colnames(Exp) )
  row.names( Exp ) <- Exp$ensembl_gene_id
  Exp <- Exp[ , (colnames( Exp ) %in% "ensembl_gene_id") == F ]

  Covariates$tissue <- as.character(Covariates$tissue)

  for( tis in c( 'DLPFC', 'ACC', 'PCC' )){
    foo <- as.matrix(Exp[ ,as.character(Covariates[ Covariates$tissue == tis, ]$SampleID) ])
    foo <- apply(as.matrix(Exp[ ,as.character(Covariates[ Covariates$tissue == tis, ]$SampleID) ]), 1, scale)
    foo <- t(foo)
    colnames(foo) <- colnames(as.matrix(Exp[ ,as.character(Covariates[ Covariates$tissue == tis, ]$SampleID) ]))
    eval( parse( text = paste0( 'foo_', tis, ' <- foo' ) ))
  }

  foo <- cbind( foo_DLPFC, foo_ACC, foo_PCC )
  row.names( foo ) <- row.names( Exp )
  foo <- foo[ , as.character(row.names(Covariates)) ]

  #Filter for matched RNA-Seq and GWAS samples
  Mast_RNA_Meta <- read.csv( syn_temp$get('syn23573928')$path )
  Mast_RNA_Meta <- Mast_RNA_Meta[ Mast_RNA_Meta$specimenID %in% colnames(foo), ]

  Mast_RNA_Meta <- Mast_RNA_Meta[ Mast_RNA_Meta$projid %in% Trans$projid, ]
  row.names(Mast_RNA_Meta) <- as.character(Mast_RNA_Meta$specimenID)
  Exp <- foo[ , colnames(foo)[ (colnames(foo) %in% as.character(Mast_RNA_Meta$specimenID)) == T] ]

  #Filter the translator with GWAS IDs to relevant unique entries of Project IDs
  Trans <- as.data.frame( Trans[ as.character(Trans$projid ) %in% as.character(Mast_RNA_Meta$projid), ] )
  Trans$Unis <- paste0( Trans$projid, '_', Trans$gwas_id )
  Trans <- Trans[ !duplicated(Trans$Unis), ]
  row.names(Trans) <- Trans$projid

  #Replace expression names...
  #Find Resequenced Samples and keep the sample with the highest RIN Value
  DOO <- paste0(as.character( Trans[ as.character( Mast_RNA_Meta[ colnames(Exp), ]$projid_repaired ), ]$gwas_id),
  '_',
  as.character( Mast_RNA_Meta[ colnames(Exp), ]$tissue))
  Mast_RNA_Meta$interesting <- paste0( as.character(Mast_RNA_Meta$individualid), "_",
                                       as.character(Mast_RNA_Meta$projid_repaired), "_",
                                       as.character(Mast_RNA_Meta$tissue))
  IntDups <- Mast_RNA_Meta$interesting[duplicated(Mast_RNA_Meta$interesting)]
  Mast_RNA_Meta$KEEPS <- 1
  for( entry in IntDups){
    temp <- Mast_RNA_Meta[ Mast_RNA_Meta$interesting == entry, c( 'specimenID','RIN') ]
    Mast_RNA_Meta[ as.character(temp[which.max(temp$RIN),]$specimenID),]$KEEPS <- 0
  }
  Mast_RNA_Meta <- Mast_RNA_Meta[ Mast_RNA_Meta$KEEPS == 1, ]
  Exp <- Exp[ , (colnames(Exp) %in% row.names(Mast_RNA_Meta)) == T ]

  colnames(Exp) <- paste0(as.character( Trans[ as.character( Mast_RNA_Meta[ colnames(Exp), ]$projid_repaired ), ]$gwas_id),
  '_',
  as.character( Mast_RNA_Meta[ colnames(Exp), ]$tissue))

  return(Exp)
}

# , , syn23674977
Norm_Resid_RM <-Ros_Filt( 'syn23643705', 'syn5879839', 'syn3382527','syn20820122', 1)
dNorm_Resid_RM <-Ros_Filt( 'syn23666495', 'syn5879839', 'syn3382527','syn20820122', 0)
```

## Process CMC Data
```{r CMC, results='hide', echo=TRUE, cache=TRUE}
#Exp
Exp_PFC <- as.data.frame( read.table( syn_temp$get('syn21470926')$path, header = T, sep = '\t', row.names = 1 ))
rownames(Exp_PFC) <- do.call( rbind, strsplit(row.names(Exp_PFC),'\\.'))[,1]
Exp_ACC <- as.data.frame( read.table( syn_temp$get('syn21483472')$path, header = T, sep = '\t', row.names = 1 ))
rownames(Exp_ACC) <- do.call( rbind, strsplit(row.names(Exp_ACC),'\\.'))[,1]

keep <- row.names(Exp_ACC)[ row.names(Exp_ACC) %in% row.names(Exp_PFC) ]
Exp <- cbind( Exp_ACC[keep,], Exp_PFC[keep,] )

#ID--
ID <- read.csv( syn_temp$get('syn21444814')$path, header = T )
colnames(Exp) <- gsub( 'RNA_','',colnames(Exp) )

Adjuster <- function( input ){
  #'@input a column name from the CMC expression dataframe
    NameString <- do.call( c, strsplit( input, '_' ) )
    if( length(NameString) == 3 ){
      #Rearange traditional name
      result <- paste0( NameString[1], '_',
                        NameString[3], '_',
                        NameString[2]
                        )
    }else{
      if( length(NameString) == 4 ){
      #Rearrange the BPs
        if( NameString[3] == 'BP' ){
          result <- paste0( NameString[1], '_',
                        NameString[3], '_',
                        NameString[4], '_',
                        NameString[2]
                        )
        }else{
          if( NameString[2] == 'BP' ){
            result <- paste0( NameString[1], '_',
                        NameString[2], '_',
                        NameString[4], '_',
                        NameString[3]
                        )
          }else{
            warning(paste0( input,' Breaks BP Name Convention'))
          }
        }
      }else{
        warning(paste0( input,' Breaks Name Convention'))
      }
    }
}

CMC_RNA_Sample_Trans <-  cbind( OG_Name = names( sapply( colnames(Exp), Adjuster )), 
                                ReNamed = sapply( colnames(Exp), Adjuster )
)
CMC_RNA_Sample_Trans <- as.data.frame(CMC_RNA_Sample_Trans, stringsAsFactors=F)

CMC_RNA_Sample_Trans$GWAS_Match <- gsub( '_PFC', '', CMC_RNA_Sample_Trans$ReNamed  )
CMC_RNA_Sample_Trans$GWAS_Match <- gsub( '_ACC', '', CMC_RNA_Sample_Trans$GWAS_Match  )

colnames(Exp) <- CMC_RNA_Sample_Trans[ colnames(Exp), ]$ReNamed

Exp_ACC <- Exp[, colnames(Exp)[grepl('_ACC',colnames(Exp))] ]
Exp_PFC <- Exp[, colnames(Exp)[grepl('_PFC',colnames(Exp))] ]

Scaled_PFC_Exp <- t(scale(t(Exp_PFC)))
Scaled_ACC_Exp <- t(scale(t(Exp_ACC)))

Scaled_Exp <- cbind(  Scaled_ACC_Exp,Scaled_PFC_Exp )

```

## Merge RNA-Seq: Merge and Annotate RNA-Seq
* Remove genes on Chr X, Chr Y, Chr M 
* Check for no Patch Contig Nonsense
* Print Sample ID List
* Filter Genotypes for RNA Samples
```{r Merge RNASeq, results='hide', echo=TRUE, cache = FALSE}
#Common Genes:
GNames <- names( table(c( row.names(Scaled_Exp), row.names(Norm_Resid_MSBB), row.names(Norm_Resid_MAYO), row.names(Norm_Resid_RM)  ))[ table(c( row.names(Norm_Resid_MSBB), row.names(Scaled_Exp), row.names(Norm_Resid_MAYO), row.names(Norm_Resid_RM)  )) == 4] )
dGNames <- names( table(c( row.names(dCorrect_Resid_MSBB), row.names(Scaled_Exp), row.names(dCorrect_Resid_MAYO), row.names(dNorm_Resid_RM)  ))[ table(c( row.names(dCorrect_Resid_MSBB), row.names(Scaled_Exp), row.names(dCorrect_Resid_MAYO), row.names(dNorm_Resid_RM)  )) == 4] )

#row.names(Scaled_Exp)
#Combine Into One DataFrame
Comb <- function( MSBB, Mayo, RM, cmc, Names){
  #'@MSBB The MSBB Expression Set Data Frame
  #'@Mayo The Mayo Expression Set Data Frame
  #'@RM The ROSMAP Expression Set Data Frame
  #'@Names Gene names Vector
  #MSBB <- dCorrect_Resid_MSBB
  #Mayo <- dCorrect_Resid_MAYO
  #RM <- dNorm_Resid_RM
  #Names <- dGNames

  #row.names(MSBB) <- as.character(MSBB$ensembl_gene_id)
  #row.names(Mayo) <- as.character(Mayo$ensembl_gene_id)
  #row.names(RM) <- as.character(RM$ensembl_gene_id)

  #MSBB <- MSBB[ GNames ,2:dim(MSBB)[2] ]
  #Mayo <- Mayo[ GNames ,2:dim(Mayo)[2] ]
  #RM <- RM[ GNames ,2:dim(RM)[2] ]

  Out <- cbind( MSBB[Names,],#[ ,1:dim(MSBB)[2] ],
                Mayo[Names, ],#[ ,1:dim(Mayo)[2] ],
                cmc[Names, ],
                RM[Names, ]#[, 1:dim(RM)[2] ]
  )

  return( Out )
}

Norm_Resid <- Comb( Norm_Resid_MSBB, Norm_Resid_MAYO, Norm_Resid_RM, Scaled_Exp, GNames )
Diag_Resid <- Comb( dCorrect_Resid_MSBB,  dCorrect_Resid_MAYO, dNorm_Resid_RM, Scaled_Exp, dGNames )

#Annotate for TWAS
hg19 <- as.data.frame(fread(syn_temp$get('syn20826610')$path))
hg19 <- hg19[ hg19[,1] %in% row.names( Norm_Resid ), ]
row.names(hg19) <- hg19[,1]

#Filter out the 231 Genes that don't have coherent annotations between GRCH38 and GRCH 37
Norm_Resid <- Norm_Resid[ (row.names(Norm_Resid) %in% row.names(hg19)) == T, ]
Diag_Resid <- Diag_Resid[ (row.names(Diag_Resid) %in% row.names(hg19)) == T, ]

#Finalize
Norm_Resid <- as.data.frame( cbind( 
               TargetID = row.names(Norm_Resid), 
               Gene_Symbol = row.names(Norm_Resid),
               Chr = hg19[row.names(Norm_Resid), ][,2] , 
               Coord = hg19[ row.names(Norm_Resid), ][,3],
               Norm_Resid[ ,1:dim(Norm_Resid)[2]
             ]) )

Diag_Resid <- as.data.frame(cbind( 
               TargetID = row.names(Diag_Resid), 
               Gene_Symbol = row.names(Diag_Resid),
               Chr = hg19[row.names(Diag_Resid), ][,2] , 
               Coord = hg19[ row.names(Diag_Resid), ][,3],
               Diag_Resid[ ,1:dim(Diag_Resid)[2]
             ]) )

#Filter out the ~ ChrX, MT, and Patch genes
Norm_Resid <- Norm_Resid[ (as.character(Norm_Resid$Chr) %in% c('MT', 'X', as.character(Norm_Resid$Chr)[ grepl('PATCH', as.character(Norm_Resid$Chr)) == T])) == F, ]
Diag_Resid <- Diag_Resid[ (as.character(Diag_Resid$Chr) %in% c('MT', 'X', as.character(Diag_Resid$Chr)[ grepl('PATCH', as.character(Diag_Resid$Chr)) == T])) == F, ]

#Order:
Norm_Resid <- Norm_Resid[ with(Norm_Resid, order( Chr, Coord)), ]
Diag_Resid <- Diag_Resid[ with(Diag_Resid, order( Chr, Coord)), ]

#Filter for CEU Ancestry Matched Training Cohort
Tot_Samps <- cbind( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))], 
                    colnames(Norm_Resid)[5:length(colnames(Norm_Resid))]
                    #_#do.call( rbind, strsplit( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))],  "_" ))[,2]
                  )
for( SUB in c('BM22_', 'BM10_', 'BM36_','BM44_', '_ACC', '_PFC', '_PCC', '_DLPFC' )){
  Tot_Samps[,2] <- gsub( SUB, '', Tot_Samps[,2] )
}
Tot_Samps[,2][ grepl("^0_",Tot_Samps[,2])  ] <- gsub("^0_","",Tot_Samps[,2][ grepl("^0_",Tot_Samps[,2])] )
write.table(Tot_Samps, file="ALL_RNASamplesComb.tsv", col.names =F, row.names=F, sep=" ", quote=F)

#Output the ROSMAP INDV CEU Matched Training Cohort
ROS <- colnames(Norm_Resid)[ grepl('ROS', colnames(Norm_Resid)) == T | grepl('MAP', colnames(Norm_Resid)) == T ]
ROS_Norm_Resid <- Norm_Resid[ ,c("TargetID", "Gene_Symbol", "Chr", "Coord", ROS) ]
ROS_Diag_Resid <- Diag_Resid[ ,c("TargetID", "Gene_Symbol", "Chr", "Coord", ROS) ]

ROS_Samps <- cbind( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],
                    do.call( rbind, strsplit( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],  "_" ))[,1]
                  )
write.table(ROS_Samps, file="ROS_RNASamples.tsv", col.names =F, row.names=F, sep=" ", quote=F)
```

## Fix FamFile
```{r FamFix, results='hide', echo=TRUE, cache=TRUE}
#Old- syn20820122
#_#syn23674977

FAM <- as.data.frame(fread( syn_temp$get('syn23674977')$path))
MSBB <- as.data.frame(fread( syn_temp$get('syn11384608')$path))
MSBB_Clin <- as.data.frame(fread( syn_temp$get('syn6101474', version=4)$path))
ROSMAP <- as.data.frame(fread( syn_temp$get('syn3191087')$path))
row.names(ROSMAP) <- ROSMAP$projid
ROSMAP_ID <- as.data.frame(fread( syn_temp$get('syn3382527')$path))
MAYO <- as.data.frame(fread( syn_temp$get('syn19164046')$path))
mayo <- as.data.frame(fread( syn_temp$get('syn19164050')$path))

#Fix CMC Names
FAM[,1] <- gsub( '0_PITT_', 'PITT_', gsub( '0_Pitt_', 'Pitt_', gsub( '0_PENN_', 'PENN_', gsub( '0_MSSM_', 'MSSM_', FAM[,1] ))))
FAM[,2] <- gsub( '0_PITT_', 'PITT_', gsub( '0_Pitt_', 'Pitt_', gsub( '0_PENN_', 'PENN_', gsub( '0_MSSM_', 'MSSM_', FAM[,2] ))))
FAM[,1] <- gsub( 'Pitt_', 'PITT_', FAM[,1] )
FAM[,2] <- gsub( 'Pitt_', 'PITT_', FAM[,2] )

#MSBB 
row.names(MSBB) <- MSBB$sampleIdentifier
name <- FAM[ FAM$V2 %in% row.names(MSBB) == T, ]$V2
MSBB <- MSBB[name,]

row.names(MSBB_Clin) <- MSBB_Clin$individualIdentifier

MSBB_Clin <- cbind(MSBB_Clin[MSBB$individualIdentifier,1:dim(MSBB_Clin)[2]], MSBB[,1:dim(MSBB)[2] ] )
row.names(MSBB_Clin) <- MSBB_Clin$sampleIdentifier

MSBB_Clin$Diagnosis <- -9
for( i in 1:length(row.names(MSBB_Clin))){
  if( is.na(MSBB_Clin[ i,]$CDR) ==  F & is.na(MSBB_Clin[ i,]$bbscore) ==  F & is.na(MSBB_Clin[ i,]$NP.1) ==  F ){
    if( MSBB_Clin[ i,]$CDR >= 1 & MSBB_Clin[ i,]$bbscore > 3 & MSBB_Clin[ i,]$NP.1 > 1 ){
      MSBB_Clin[ i,]$Diagnosis <- 2
    }else{
      if(MSBB_Clin[ i,]$CDR < 1 & MSBB_Clin[ i,]$bbscore < 4 & MSBB_Clin[ i,]$NP.1 < 2){
        MSBB_Clin[ i,]$Diagnosis <- 1
      }else{}
    }
  }
}

Sex<-c(1,2)
names(Sex) <- c('M', 'F')
MSBB$SEX.inferred <- Sex[MSBB$SEX.inferred]
row.names(FAM)<-FAM$V2

FAM[ row.names(MSBB), ]$V5 <- MSBB$SEX.inferred
FAM[ row.names(MSBB_Clin), ]$V6 <- MSBB_Clin$Diagnosis

#Mayo
mayo <- mayo[complete.cases(mayo$Gender),]
MAYO <- MAYO[complete.cases(MAYO$Sex),]

NewMayo <- as.data.frame( rbind( cbind( MAYO$SampleID,MAYO$Sex,as.character(MAYO$Diagnosis)), cbind( mayo$SampleID,mayo$Gender, as.character(mayo$Diagnosis))) )
NewMayo<- NewMayo[!duplicated(NewMayo),]
NewMayo <- as.data.frame( cbind( as.character(NewMayo$V1),as.character(NewMayo$V2), gsub("_CER","",gsub("_TCX","",NewMayo$V1)), as.character(NewMayo$V3)) )
NewMayo$V2 <- Sex[as.character( NewMayo$V2 )]

names <- FAM[ FAM$V1 == 0 ,]$V2
NewMayo <- NewMayo[ !duplicated(NewMayo$V3), ]
row.names(NewMayo) <- NewMayo$V3
NewMayo <- NewMayo[ names, ]

Aff <- c(-9,-9,1,2)
names(Aff) <- c("Pathologic Aging", "PSP", "Control", "AD")
FAM[ names ,]$V6 <- as.numeric(Aff[as.character(NewMayo[ names, ]$V4)])
FAM[ names ,]$V5 <- NewMayo[ names, ]$V2

#Fix the Final
FAM[ '1957',]$V5 <- 2
FAM[ '1957',]$V6 <- -9
FAM[ '1950',]$V5 <- 2
FAM[ '1950',]$V6 <- -9

#Fix ROSMAP Names
FAM[ grepl('ROS', FAM$V2) == T  | grepl('MAP', FAM$V2) == T , ]$V1 <- FAM[ grepl('ROS', FAM$V2) == T  | grepl('MAP', FAM$V2) == T , ]$V2

#_# Old - Look only combining the MSBB Samps 
#FAM$V1 <- paste0( FAM$V1, "_", FAM$V2 )
FAM[ FAM[,1] == 0, ][,1] <- paste0( FAM[ FAM[,1] == 0, ][,1], "_", FAM[ FAM[,1] == 0, ][,2] )

#Write New FAM to file
write.table(FAM, file='New_Fam.fam', row.names = F, col.names=F, quote=F, sep=" ")

##  Assemble the IDV. to Expand -- MSBB
#tail(FAM[ FAM$V1[ grepl('ROS', FAM$V1) == F ] $ FAM$V1[ grepl('MAP', FAM$V1) == F ] ,])
# & FAM$V1[ grepl('ROS', FAM$V1) == F ]
MSBB_List <- FAM[ (dim(NewMayo)[1]+1):dim(FAM)[1], ]
MSBB_List <-  MSBB_List[ grepl('MSSM', MSBB_List$V1) == F ,]
MSBB_List <-  MSBB_List[ grepl('PITT', MSBB_List$V1) == F ,]
MSBB_List <-  MSBB_List[ grepl('Pitt', MSBB_List$V1) == F ,]
MSBB_List <-  MSBB_List[ grepl('PENN', MSBB_List$V1) == F ,]
MSBB_List <- MSBB_List[1:dim(MSBB)[1],]

#MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('MAP', MSBB_List$V1) == F ] ,]
#MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('ROS', MSBB_List$V1) == F ] ,]

write.table( MSBB_List[,1:2], file="MSBB_SamplesToExpand.txt", quote = F, row.names = F, col.names = F, sep = "\t" )

##  Assemble the IDV. to Expand -- CMC
CMC_List <- FAM[ (dim(NewMayo)[1]+1):dim(FAM)[1], ]
CMC_List <-  CMC_List[ grepl('MSSM', CMC_List$V1) | grepl('PITT', CMC_List$V1) |
grepl('PENN', CMC_List$V1) , ]

write.table( CMC_List[,1:2], file="CMC_SamplesToExpand.txt", quote = F, row.names = F, col.names = F, sep = "\t" )

##  Assemble the IDV. to Expand -- ROSMAP
RosMap_List <-  FAM[ grepl('MAP', FAM$V1) | grepl('ROS', FAM$V1), 1:3 ]

write.table( RosMap_List , file="ROSMAP_SamplesToExpand.txt", quote = F, row.names = F, col.names = F, sep = "\t" )
```

## Filter Genotype data
```{bash FilterGenos, results='hide', echo=TRUE, cache=TRUE}
#source /root/.bashrc
export PATH=$PATH:~/TWAS/bin/
CORES=`expr $(nproc) - 2`

#Pull Geno-data
synapse get syn23674975 #syn20820120
synapse get syn23674976 #syn20820121
#Old - syn20820122 syn23674977
synapse get syn23674977

#Copy over FAM File with Sex Info:
cp New_Fam.fam CEU_AncestryMatched_Genotypes.fam

############################################################################################
##--## expand the MSBB Samples by tissue
#Extract the MSBB Samples to duplicate and rename to match tissues --silent
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep MSBB_SamplesToExpand.txt --silent --recode --out MSBB_Intermediate

#ReName MSBB to get FID and IIDs
awk '{for(i=0;i<4;i++)print}' MSBB_Intermediate.ped > temp

gawk -v m=1 -v n=1 -v el='BM10' 'NR % m == 0 { $n = el"_"$2 } 1' temp > foo
gawk -v m=2 -v n=1 -v el='BM22' 'NR % m == 0 { $n = el"_"$2 } 1' foo > temp
gawk -v m=3 -v n=1 -v el='BM36' 'NR % m == 0 { $n = el"_"$2 } 1' temp > foo
gawk -v m=4 -v n=1 -v el='BM44' 'NR % m == 0 { $n = el"_"$2 } 1' foo > temp
mv temp MSBB_Intermediate.ped
rm foo
plink --threads $CORES --file MSBB_Intermediate --silent --make-bed --out MSBB_Expanded

#ReName ALL to get FID and IIDs
#_#plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --silent --recode --out temp
#_#gawk -v m=1 -v n=1 'NR % m == 0 { if( $2 ~ /MAP/ || $2 ~ /ROS/ ) { $n = $2"_"$2 }else{ $n = $1 } } 1' temp.ped > foo
#gawk -v m=1 -v n=1 'NR % m == 0 { $n = $1"_"$2 } 1' temp.ped > foo2

#_#mv foo temp.ped
#_#plink --threads $CORES --file temp --silent --make-bed --out CEU_AncestryMatched_Genotypes

#Merge
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --bmerge MSBB_Expanded --silent --make-bed --out Rebuilt
plink --threads $CORES --bfile Rebuilt --remove MSBB_SamplesToExpand.txt --silent --make-bed --out CEU_AncestryMatched_Genotypes

#rm Rebuilt.*
#rm MSBB_Expanded.*
#rm temp.*
############################################################################################
##--## expand the CMC Samples by tissue
#Extract the CMC Samples to duplicate and rename to match tissues --silent
sed -i 's/Pitt/PITT/g' CEU_AncestryMatched_Genotypes.fam
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep CMC_SamplesToExpand.txt --make-bed --out CMC_IntermediateA
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep CMC_SamplesToExpand.txt --make-bed --out CMC_IntermediateB

awk '{ print $1"_ACC\t"$2"\t"$3"\t"$4"\t"$5"\t"$6 }' CMC_IntermediateA.fam > foo
mv foo CMC_IntermediateA.fam
awk '{ print $1"_PFC\t"$2"\t"$3"\t"$4"\t"$5"\t"$6 }' CMC_IntermediateB.fam > foo
mv foo CMC_IntermediateB.fam

plink --bfile CMC_IntermediateA --bmerge CMC_IntermediateB.bed CMC_IntermediateB.bim CMC_IntermediateB.fam --make-bed --out CMC_Expanded
rm CMC_IntermediateA.*
rm CMC_IntermediateB.*

#Merge
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --bmerge CMC_Expanded --silent --make-bed --out Rebuilt
plink --threads $CORES --bfile Rebuilt --remove CMC_SamplesToExpand.txt --silent --make-bed --out CEU_AncestryMatched_Genotypes
####################################################################################################
##--## expand the ROSMAP Samples by tissue
#Extract the ROSMAP Samples to duplicate and rename to match tissues --silent
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROSMAP_SamplesToExpand.txt --make-bed --out ROSMAP_IntermediateA
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROSMAP_SamplesToExpand.txt --make-bed --out ROSMAP_IntermediateB
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROSMAP_SamplesToExpand.txt --make-bed --out ROSMAP_IntermediateC

awk '{ print $1"_ACC\t"$2"\t"$3"\t"$4"\t"$5"\t"$6 }' ROSMAP_IntermediateA.fam > foo
mv foo ROSMAP_IntermediateA.fam
awk '{ print $1"_DLPFC\t"$2"\t"$3"\t"$4"\t"$5"\t"$6 }' ROSMAP_IntermediateB.fam > foo
mv foo ROSMAP_IntermediateB.fam
awk '{ print $1"_PCC\t"$2"\t"$3"\t"$4"\t"$5"\t"$6 }' ROSMAP_IntermediateC.fam > foo
mv foo ROSMAP_IntermediateC.fam

plink --bfile ROSMAP_IntermediateA --bmerge ROSMAP_IntermediateB.bed ROSMAP_IntermediateB.bim ROSMAP_IntermediateB.fam --make-bed --out ROSMAP_ExpandedA
plink --bfile ROSMAP_ExpandedA --bmerge ROSMAP_IntermediateC.bed ROSMAP_IntermediateC.bim ROSMAP_IntermediateC.fam --make-bed --out ROSMAP_Expanded
rm ROSMAP_IntermediateA.*
rm ROSMAP_IntermediateB.*
rm ROSMAP_IntermediateC.*
rm ROSMAP_ExpandedA.*

#Merge
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --bmerge ROSMAP_Expanded --silent --make-bed --out Rebuilt
plink --threads $CORES --bfile Rebuilt --remove ROSMAP_SamplesToExpand.txt --silent --make-bed --out CEU_AncestryMatched_Genotypes
########################################################################################################################

#Extract CEU
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ALL_RNASamplesComb.tsv --silent --make-bed --out All_CEU_ToTrainForTWAS

#Extract ROS_Only:
plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROS_RNASamples.tsv --silent --make-bed --out ROSMAPonly_CEU_ToTrainForTWAS
```

```{r sanitycheck, include=TRUE, echo=TRUE}
FAM <- as.data.frame(fread('All_CEU_ToTrainForTWAS.fam'))
row.names(FAM) <- FAM[,1]
table(row.names(FAM) %in% colnames(Diag_Resid))
Diag_Resid_train <- Diag_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]
Norm_Resid_train <- Norm_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]

FAM <- as.data.frame(fread('ROSMAPonly_CEU_ToTrainForTWAS.fam'))
row.names(FAM) <- FAM[,1]
table(row.names(FAM) %in% colnames(ROS_Diag_Resid))
ROS_Diag_Resid_train <- ROS_Diag_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]
ROS_Norm_Resid_train <- ROS_Norm_Resid[ , c("TargetID","Gene_Symbol","Chr","Coord", row.names(FAM) )]

Diag_Resid_train <- Diag_Resid_train[ (Diag_Resid_train$Chr %in% c(1:22)) == T, ]
Norm_Resid_train <- Norm_Resid_train[ (Norm_Resid_train$Chr %in% c(1:22)) == T, ]

ROS_Diag_Resid_train <- ROS_Diag_Resid_train[ (ROS_Diag_Resid_train$Chr %in% c(1:22)) == T, ]
ROS_Norm_Resid_train <- ROS_Norm_Resid_train[ (ROS_Norm_Resid_train$Chr %in% c(1:22)) == T, ]
```

## Annotate CMC Sex in FAM Files
```{r download.data, cache=TRUE}
library(dplyr)

downloadFile <- function(id){
  fread(syn_temp$get(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(syn_temp$get(id, version = version)$path, data.table = F)
}
counts = 'syn21071622'
ALL_USED_IDs = counts
counts = downloadFile(counts) %>% data.frame()
counts$Chr <- NULL
counts$Start <- NULL
counts$End <- NULL
counts$Strand <- NULL
# Parse gene lengths
gene_lengths = counts[,c("Geneid", "Length")]
counts$Length <- NULL
gene_lengths <- rename(gene_lengths, gene_id = Geneid)
# Get ancestry vector calculated using gemtools
ANCESTRY_ID = 'syn2511399'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = ANCESTRY_ID
ANCESTRY = downloadFile(ANCESTRY_ID) %>% 
  plyr::rename(c('DNA_report..Genotyping.Sample_ID' = 'SNP_report:Genotyping_Sample_ID'))
# Get genotype ids from synapse
GENOTYPE_ID = 'syn16816490'
ALL_USED_IDs = c(ALL_USED_IDs, GENOTYPE_ID)
GENOTYPE = downloadFile(GENOTYPE_ID) %>% 
  dplyr::select(Individual_ID, `SNP_report:Genotyping_Sample_ID`) %>%
  dplyr::inner_join(ANCESTRY)

#Get Metadata
metadata = 'syn16816488' 
ALL_USED_IDs[length(ALL_USED_IDs)+1] = metadata
metadata = downloadFile_version(metadata, version = 13)  %>% 
  dplyr::select(Individual_ID, Institution, Reported_Gender, Sex, Ethnicity, Age_of_Death, `PMI_(in_hours)`, Dx,
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_report:Ribozero_Batch', 'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch','rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned'))
METADATA = metadata %>%
  dplyr::left_join(GENOTYPE) %>%
  dplyr::rename(PMI = `PMI_(in_hours)`,
                GWAS_ID = `SNP_report:Genotyping_Sample_ID`,
                Sample_ID = Sample_RNA_ID,
                ReportExclude = `rnaSeq_report:Exclude?`,
                SampleID = Sample_RNA_ID,
                LibraryBatch = `rnaSeq_report:Library_Batch`,
                FlowcellBatch = `rnaSeq_report:Flowcell_Batch`,
                RibozeroBatch = `rnaSeq_report:Ribozero_Batch`,
                Tissue = `rnaSeq_dissection:Brain_Region`,
                MappedReads = `rnaSeq_report:Mapped_Reads`,
                IntragenicRate = `rnaSeq_report:Intragenic_Rate`, 
                IntronicRate = `rnaSeq_report:Intronic_Rate`, 
                IntergenicRate = `rnaSeq_report:Intergenic_Rate`, 
                GenesDetected = `rnaSeq_report:Genes_Detected`,
                ExpProfEfficiency = `rnaSeq_report:Expression_Profiling_Efficiency`, 
                rRNARate = `rnaSeq_report:rRNA_Rate`,
                TotalReads = `rnaSeq_report:Total_Reads`, 
                AlignmentRate = `rnaSeq_report:Percent_Aligned`,
                RIN = `rnaSeq_isolation:RIN`) %>%
  dplyr::select(SampleID, GWAS_ID, Individual_ID, Institution, Reported_Gender,Sex, Ethnicity, Age_of_Death, PMI, Dx, 
                RIN, ReportExclude, EV.1, EV.2, EV.3, EV.4, EV.5,
                LibraryBatch, FlowcellBatch, RibozeroBatch, Tissue, MappedReads, TotalReads, GenesDetected, AlignmentRate,
                IntragenicRate, IntergenicRate, IntronicRate, ExpProfEfficiency, rRNARate) %>% 
  dplyr::filter(Institution %in% c("MSSM", "Penn", "Pitt")) %>% 
  dplyr::filter(SampleID %in% colnames(counts), !is.na(SampleID)) %>%
  dplyr::mutate(Dx = forcats::fct_recode(Dx,  Other = "AFF", Other = "BP", Control = "Control", SCZ = "SCZ"))

#METADATA$Individual_ID <- gsub( 'CMC_','',METADATA$Individual_ID )
METADATA$GWAS_ID <- gsub( 'Pitt', 'PITT', METADATA$GWAS_ID )
METADATA <- METADATA[ !duplicated(METADATA$GWAS_ID), ]
METADATA <- METADATA[ is.na(METADATA$GWAS_ID)==F,]
row.names( METADATA ) <- METADATA$GWAS_ID
SEX <- c(1,2,0)
names(SEX) <- c("XY","XX","XXY")
###Total CEU Genotype
FAM <- as.data.frame(fread('CEU_AncestryMatched_Genotypes.fam'))
#table( FAM[,2][ grepl( 'PENN',FAM[,2] ) | grepl( 'PITT',FAM[,2] ) | grepl( 'MSSM',FAM[,2] ) ] %in% METADATA$GWAS_ID)

FAM[ grepl( 'PENN',FAM[,2] ) | grepl( 'PITT',FAM[,2] ) | grepl( 'MSSM',FAM[,2] ), 5 ] <- SEX[ METADATA[ FAM[,2][ grepl( 'PENN',FAM[,2] ) | grepl( 'PITT',FAM[,2] ) | grepl( 'MSSM',FAM[,2] ) ] , 'Sex'] ]
write.table(FAM, file='CEU_AncestryMatched_Genotypes.fam', row.names = F, col.names=F, quote=F, sep=" ")

###CEU Genos to train
FAM <- as.data.frame(fread('All_CEU_ToTrainForTWAS.fam'))

FAM[ grepl( 'PENN',FAM[,2] ) | grepl( 'PITT',FAM[,2] ) | grepl( 'MSSM',FAM[,2] ), 5 ] <- SEX[ METADATA[ FAM[,2][ grepl( 'PENN',FAM[,2] ) | grepl( 'PITT',FAM[,2] ) | grepl( 'MSSM',FAM[,2] ) ] , 'Sex'] ]
write.table(FAM, file='All_CEU_ToTrainForTWAS.fam', row.names = F, col.names=F, quote=F, sep=" ")

```

## Push Results to Synapse -- Contained in ProcessData.Rmd if needed for reference
```{r synapse.parameters.head, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
parentId = 'syn18936948';
activityName = 'CMC Additional ROSMAP Processed TWAS Training Data';
activityDescription = 'Data from processing and hamonizing CEU ancestry matched Genotypes with available RNA-Seq profiles which were aligned to GRCh38 but annotated with hg19 TSS sites here';
thisFileName <- 'ProcessData_CMC.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

```{r synapse.parameters, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
activityName = 'CMC Additional ROSMAP Processed TWAS Training Data';
activityDescription = 'Data from processing and hamonizing CEU ancestry matched Genotypes with available RNA-Seq profiles';

CODE <- syn_temp$store(synapseclient$Folder(name = "Processed_TWAS_Training_Data_with_CMC", parentId = parentId))

#Set Used SynIDs For Provenance
Syns_Used <- c("syn5223705", "syn8698211", "syn3817650", "syn8690904", 
"syn6126119", "syn8698214", "syn8449369", "syn6126114", "syn6145639", "syn8690799"
)

# Set annotations
EXP.all.annotations = list(
  dataType = 'mRNA',
  dataSubType = 'geneExp',
  summaryLevel = 'gene',
  assay  = 'RNAseq',
  tissueTypeAbrv  = c('TCX', 'DLPFC', 'PFG', 'STG', 'IFG', 'FP'), 
  study = c('MAYO','MSBB', 'ROSMAP'), 
  organism = 'HomoSapiens',
  consortium  = 'AMPAD',
  normalizationStatus = TRUE,
  normalizationType = 'CQN',
  rnaquantification = 'RSEM',
  genomeAssemblyID = 'GRCh38'
)
# Set annotations
Var.all.annotations = list(
  dataType = 'Variant',
  dataSubType = 'SNP',
  summaryLevel = 'Nucleotide',
  assay  = 'Genotype Array',
  tissueTypeAbrv  = c('Whole Blood'), 
  study = c('MAYO','MSBB', 'ROSMAP'), 
  organism = 'HomoSapiens',
  consortium  = 'AMPAD',
  genomeAssemblyID = 'GRCh37'
)

Basic.annotations = list(
  dataType = 'Induvidual List',
  dataSubType = 'Plink PatientID Filter',
  study = c('MAYO','MSBB', 'ROSMAP'), 
  organism = 'HomoSapiens',
  consortium  = 'AMPAD'
)

## TOTAL SVA-only Exp
write.table(Norm_Resid, file="ALL_RNA_Seq_SVAadusted.tsv", col.names =T, row.names=F, sep="\t", quote=F)
Syns_Used_SVA_EXP <- c('syn11384608', 'syn8485026', 'syn6100548', 'syn8456704', 'syn5879839', 'syn3382527','syn23674977', 'syn8466825')

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted.tsv', name = 'Total RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)

## TOTAL Diagnosis Exp
write.table(Diag_Resid, file="ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =T, row.names=F, sep="\t", quote=F)
Syns_Used_Diagnosis_EXP <- c('syn20801991', 'syn11384608', 'syn20801798', 'syn6100548',  'syn20800652', 'syn5879839', 'syn3382527','syn23674977')

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'Total RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
    EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
    syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)

## CEU SVA-only Exp
write.table(Norm_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted.tsv", col.names =T, row.names=F, sep="\t", quote=F)
Syns_Used_SVA_EXP <- c('syn11384608', 'syn8485026', 'syn6100548', 'syn8456704', 'syn5879839', 'syn3382527','syn23674977', 'syn8466825')

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)

## CEU Diagnosis Exp
write.table(Diag_Resid_train, file="ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =T, row.names=F, sep="\t", quote=F)
Syns_Used_Diagnosis_EXP <- c('syn20801991', 'syn11384608', 'syn20801798', 'syn6100548',  'syn20800652', 'syn5879839', 'syn3382527','syn23674977')

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)

#ROSMAP only Expression
  ## CEU SVA-only Exp -- ROSMAP Only
write.table(ROS_Norm_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted.tsv", col.names =T, row.names=F, sep="\t", quote=F)
Syns_Used_SVA_EXP <- c('syn8456704', 'syn5879839', 'syn3382527','syn23674977' )

ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ROS_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU ROSMAP Only RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
  EXP.all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)

  ## CEU Diagnosis Exp -- ROSMAP Only
write.table(ROS_Diag_Resid_train, file="ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv", col.names =T, row.names=F, sep="\t", quote=F)
Syns_Used_Diagnosis_EXP <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn23674977')
ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ROS_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU ROSMAP Only RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
  EXP.all.annotations$tissueTypeAbrv = 'DLPFC'
  syn_temp$setAnnotations(ENRICH_OBJ, annotations = EXP.all.annotations)

#ALL INDV
 ##Check that order is correct between file lists
  #table(paste0(Tot_Samps[,1], '_', Tot_Samps[,2]) == colnames(Diag_Resid)[ 5:length(colnames(Diag_Resid))])
Syns <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn23674977')
ENRICH_OBJ_Tot_list <- syn_temp$store( synapseclient$File( path='ALL_RNASamplesComb.tsv', name = 'All Indv with RNA-Seq Profiles in AMP-Ad For Filtering', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  syn_temp$setAnnotations(ENRICH_OBJ_Tot_list, annotations = Basic.annotations)

#ROSMAP INDV
 ##Check that order is correct between file lists
  #table(paste0(ROS_Samps[,1], '_', ROS_Samps[,2]) == colnames(ROS_Norm_Resid)[ 5:length(colnames(ROS_Norm_Resid))])
Syns <- c( 'syn20800652', 'syn5879839', 'syn3382527','syn23674977')
ENRICH_OBJ_RM_List <- syn_temp$store( synapseclient$File( path='ROS_RNASamples.tsv', name = 'ROSMAP Indv with RNA-Seq Profiles in AMP-Ad For Filtering', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
  syn_temp$setAnnotations(ENRICH_OBJ_RM_List, annotations = Basic.annotations)

###PLINK ALL -- STORE IN SEPERATE FOLDER INCASE PHI LIMITATIONS APPLY LATER
  CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Clustered_Genotypes_with_CMC", parentId = parentId))
  Syns <- c( 'syn23674975', 'syn23674976', 'syn23674977', ENRICH_OBJ_Tot_list$properties$id  )
#FAM  
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.fam', name = 'All Matched CEU Genotype FAM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#BED
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.bed', name = 'All Matched CEU Genotype BED', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#LOG
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.log', name = 'All Matched CEU Genotype LOG', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#BIM
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='All_CEU_ToTrainForTWAS.bim', name = 'All Matched CEU Genotype BIM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#PLINK Rosmap
  Syns <- c( 'syn20800652', 'syn5879839', 'syn3382527', ENRICH_OBJ_RM_List$properties$id)
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.fam', name = 'ROSMAP Matched CEU Genotype FAM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#BED
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.bed', name = 'ROSMAP Matched CEU Genotype BED', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#LOG
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.log', name = 'ROSMAP Matched CEU Genotype LOG', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

#BIM
ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='ROSMAPonly_CEU_ToTrainForTWAS.bim', name = 'ROSMAP Matched CEU Genotype BIM', parentId=CODE$properties$id ), used = Syns, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
syn_temp$setAnnotations(ENRICH_OBJ, annotations = Var.all.annotations)

```

```{bash Clean, echo=T, results='hide'}
#rm -r ~/TWAS/bin/
rm *.bed
rm *.fam
rm *.bim
rm *.log
rm *.tsv
rm MSBB_SamplesToExpand.txt
rm *.map
rm *.ped
```

### R Source Code
[Github](`r thisFile`)

##Knit to Synapse
```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
synapseclient <- reticulate::import("synapseclient")
syn_temp <- synapseclient$Synapse()
syn_temp$login()

library(data.table)

setwd("~/TWAS/code/")
source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")

createAndKnitToFolderEntityClient(file = "ProcessData.Rmd",
                                          parentId ="syn18936948",
                                          folderName = 'Processed_TWAS_Training_Data_with_CMC')
```

### 2021-01-09 code/ProcessData_CMC.Rmd
New Process Data

@@
 
-## Push Results to Synapse -- Contained in ProcessData.Rmd if needed for reference
+## Push Results to Synapse -- Contained in ProcessData_CMC.Rmd if needed for reference
 ```{r synapse.parameters.head, include=FALSE, results='hide', echo=FALSE, cache=TRUE}
@@
 
-createAndKnitToFolderEntityClient(file = "ProcessData.Rmd",
+createAndKnitToFolderEntityClient(file = "ProcessData_CMC.Rmd",
                                           parentId ="syn18936948",

### 2023-10-10 code/Funct.R
clean

@@ -1,456 +1,0 @@
-# Load Libraries and se working directory 
-##  devtools::install_github('blogsdon/spike/spike/')
-library(spike)
-library(pheatmap)
-library(parallel)
-library(doParallel)
-library(spike)
-library(bcv)
-library(reshape2)
-library(biomaRt)
-library(UpSetR)
-library(ComplexHeatmap)
-#install.packages("enrichR")
-library(enrichR)
-setwd( config$filedir )
-
-
-reticulate::use_python("/usr/bin/python", required = TRUE)
-synapseclient <- reticulate::import("synapseclient")
-syn_temp <- synapseclient$Synapse()
-syn_temp$login()
-
-setwd("~/TWAS/code/")
-source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
-source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
-#createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing_V2.Rmd",
-#                                  parentId ="syn21478397",
-#                                  folderName = 'ACC')
-
-Genes <- c( "APOC1", "CD2AP", "EED", "CEACAM19", "MTCH2", "TREM2", "CLPTM1", "KNOP1" )
-ENSGS <- c( "ENSG00000130208", "ENSG00000198087", "ENSG00000074266", "ENSG00000186567", "ENSG00000109919", "ENSG00000095970", "ENSG00000104853", "ENSG00000103550" )
-names(ENSGS) <- Genes
-# Set Github Provenance links
-thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
-
-CODE <- syn_temp$store(synapseclient$Folder(name = 'Partial Correlations', parentId = 'syn18936948'))
-
-#SynIDs of expression data to pull from
-ExpressionDS <- c('syn21291908','syn21292041','syn21285564','syn21285564','syn21285564','syn21285564','syn21291908')
-names( ExpressionDS ) <- c('CBE', 'DLPFC', 'FP', 'IFG', 'PHG', 'STG', 'TCX')
-
-#Study ID Translator
[…]

### 2023-10-10 code/GeneLengthQuant.R

@@ -1,93 +1,0 @@
-library(readr)
-library(BioMart)
-
-synapseclient <- reticulate::import("synapseclient")
-syn_temp <- synapseclient$Synapse()
-syn_temp$login()
-
-#countz <- readr::read_tsv(syn_temp$get(foo, version = 1))
-COUNT_OBJ <- syn_temp$get("syn21075911", version = 1)
-countz <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F)
-
-myGetGeneLengthAndGCContent <- function(id, ver){
-  
-  org = 'hsa'
-  id.type = 'ensembl_gene_id'
-  host = ver
-  
-  message("Connecting to BioMart ...")
-  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
-  ds <- listDatasets(ensembl)[, "dataset"]
-  ds <- grep(paste0("^", org), ds, value = TRUE)
-  
-  if (length(ds) == 0){
-    stop(paste("Mart not found for:", org))
-  } else if (length(ds) > 1) {
-    message("Found several marts")
-    sapply(ds, function(d) message(paste(which(ds == d), d, sep = ": ")))
-    n <- readline(paste0("Choose mart (1-", length(ds), ") : "))
-    ds <- ds[as.integer(n)]
-  }
-  
-  ensembl <- useDataset(ds, mart = ensembl)
-  message(paste0("Downloading sequence", ifelse(length(id) > 1, "s", ""), " ..."))
-  if (length(id) > 100)
-    message("This may take a few minutes ...")
-  attrs <- c(id.type, "ensembl_exon_id", "chromosome_name", "exon_chrom_start", "exon_chrom_end")
-  coords <- getBM(filters = id.type, attributes = attrs, values = id, mart = ensembl)
-  id <- unique(coords[, id.type])
-  coords <- sapply(id, function(i) {
-    i.coords <- coords[coords[, 1] == i, 3:5]
-    g <- GRanges(i.coords[, 1], IRanges(i.coords[, 2], i.coords[, 3]))
-    return(g)
-  })
-  coords <- lapply(coords[id], reduce)
-  len <- plyr::ldply(coords, function(x) sum(IRanges::width(x)), .id = 'ensembl_gene_id') %>%
-    dplyr::rename(gne.length = V1)
-  
[…]

### 2023-10-10 code/FUSION.compute_weights_Parallel_V2.R
clean

@@ -90,7 +90,7 @@ weights.bslmm = function( input , bv_type , snp , out=NA ) {
 weights.lasso = function( input , hsq , snp , out=NA ) {
 	if ( is.na(out) ) out = paste(input,".LASSO",sep='')
 
-	arg = paste( opt$PATH_plink , " --allow-no-sex --bfile " , input , " --lasso " , hsq , " --threads 5 --silent --out " , out , sep='' )
+	arg = paste( opt$PATH_plink , " --allow-no-sex --bfile " , input , " --lasso " , hsq , " --threads 16 --silent --out " , out , sep='' )
 	system( arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT )
 	if ( !file.exists(paste(out,".lasso",sep='')) ) {
 	cat( paste(out,".lasso",sep='') , " LASSO output did not exist\n" )
@@ -251,7 +251,7 @@ if ( !is.na(opt$covar) ) {
 
 geno.file = opt$tmp
 # recode to the intersection of samples and new phenotype
-arg = paste( opt$PATH_plink ," --allow-no-sex --bfile ",opt$bfile," --pheno ",pheno.file," --keep ",pheno.file," --threads 5 --silent --make-bed --out ",geno.file,sep='')
+arg = paste( opt$PATH_plink ," --allow-no-sex --bfile ",opt$bfile," --pheno ",pheno.file," --keep ",pheno.file," --threads 16 --silent --make-bed --out ",geno.file,sep='')
 system(arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)
 
 # --- HERITABILITY ANALYSIS
@@ -259,7 +259,7 @@ if ( is.na(opt$hsq_set) ) {
 if ( opt$verbose >= 1 ) cat("### Estimating heritability\n")
 
 # 1. generate GRM
-arg = paste( opt$PATH_plink," --allow-no-sex --bfile ",opt$tmp," --make-grm-bin --threads 5 --silent --out ",opt$tmp,sep='')
+arg = paste( opt$PATH_plink," --allow-no-sex --bfile ",opt$tmp," --make-grm-bin --threads 16 --silent --out ",opt$tmp,sep='')
 system(arg , ignore.stdout=SYS_PRINT,ignore.stderr=SYS_PRINT)
 
 # 2. estimate heritability
@@ -392,7 +392,7 @@ for ( i in 1:opt$crossval ) {
[…]

### 2023-10-10 code/2020_12_09_ROSMAP_FullCohort_sageseqr_hg38.Rmd
Revert "Trim"

--- 2020-12-23 code/2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd
@@
 
-COUNT_ID <- 'syn23662102';
+COUNT_ID <- 'syn23643275';
 ALL_USED_IDs <- COUNT_ID
@@
 # Download expression data
-Meta_ID <- 'syn23662101';
+Meta_ID <- 'syn23643273';
 ALL_USED_IDs <- c( Meta_ID, ALL_USED_IDs )
@@
 
-clean_md$diagnosis <- as.character('OTHER')
+clean_md$diagnosis <- as.character('other')
 clean_md$diagnosis[ as.numeric(as.character(clean_md$cogdx)) == 1 & 
                     as.numeric(as.character(clean_md$braaksc)) <= 3 & 
-                    as.numeric(as.character(clean_md$ceradsc)) >= 3] <- as.character('CONTROL')
+                    as.numeric(as.character(clean_md$ceradsc)) >= 3] <- as.character('control')
 
@@
 
-import_metadata$diagnosis <- as.character('OTHER')
+import_metadata$diagnosis <- as.character('other')
 import_metadata$diagnosis[ as.numeric(as.character(import_metadata$cogdx)) == 1 & 
                            as.numeric(as.character(import_metadata$braaksc)) <= 3 &
-                           as.numeric(as.character(import_metadata$ceradsc)) >= 3 ] = 'CONTROL'
+                           as.numeric(as.character(import_metadata$ceradsc)) >= 3 ] = 'control'
 
@@
 activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
-thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd'
+thisFileName <- '2020_12_09_ROSMAP_FullCohort_sageseqr_hg38.Rmd'
 # Github link
@@
 
-CODE <- syn_temp$store(synapseclient$Folder(name = "RinOver5_RosMap_sageseqr", parentId = "syn23640229"))
-
-Syns_Used <- c( "syn23625835", "syn23625835",
-                "syn23573928", "syn21075913",
-                "syn23593968"
+CODE <- syn_temp$store(synapseclient$Folder(name = "Full_RosMap_sageseqr", parentId = "syn23640229"))
+
+Syns_Used <- c( "syn23643275", "syn23643273",
+                "syn23625835", "syn21075913"
+
               )
@@
 
-  createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_sageseqr_hg38.Rmd",
+  createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_FullCohort_sageseqr_hg38.Rmd",
                                             parentId ="syn23640229",
-                                            folderName = 'RinOver5_RosMap_sageseqr')
-
-```
+                                            folderName = 'Full_RosMap_sageseqr')
+
+```

### 2023-10-10 code/Ancestry_PCA.Rmd
Revert "Trim"

@@
 CORES=`expr $(nproc) - 2`
+
+#Make Room for ROMAP Data
+rm -r VCF/
+rm -r GWAS_Plink/
 
@@
 
-# Code WTF is this??
-CODE <- Folder(name = "Ancestry_Analysis", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Analysis", parentId = parentId))
 
@@
 ###Store Genos Seperatly 
-CODE <- Folder(name = "Ancestry_Clustered_Genotypes", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "Ancestry_Clustered_Genotypes", parentId = parentId))
 

### 2023-10-10 code/SMR.Rmd
Revert "Trim"

@@
 ---
-  title: "Summary-data-based Mendelian Randomization" author: "Jake Gockley" date: "01/17/2019" header-includes:
-  - \usepackage{multicol} - \newcommand{\btwocol}{\begin{multicols}{2}} - \newcommand{\etwocol}{\end{multicols}} output:
-  html_document: default pdf_document: default ---
+  title: "Summary-data-based Mendelian Randomization"
+author: "Jake Gockley"
+date: "01/17/2019"
+header-includes:
+  - \usepackage{multicol}
+  - \newcommand{\btwocol}{\begin{multicols}{2}}
+  - \newcommand{\etwocol}{\end{multicols}}
+output:
+  html_document: default
+pdf_document: default
+---
 
-```{r setup, include=FALSE} knitr::opts_chunk$set(echo = F) library(readr) library(snpStats) library(sem) ``` ```{r code, eval=TRUE, cache=FALSE, 
-include=TRUE}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = F)
+library(readr)
+library(snpStats)
+library(sem)
+library(parallel)
+```
+
+```{r code, eval=TRUE, cache=FALSE, include=TRUE}
+
 #Pull eQTL Data
 system( 'synapse get syn16984815' )
+
 #Pull Weights
-system('aws s3 cp s3://jkg-s3-synapseencryptedexternalbucket-zszdd03ghnb2/ROSMAP/TWAS_2019_12_02_PanCortex_DiagnosisRegressed_Weights/ All_Data/ALL/ 
---recursive') system('rm All_Data/ALL/*.hsq')
+#system('aws s3 cp s3://jkg-s3-synapseencryptedexternalbucket-zszdd03ghnb2/ROSMAP/TWAS_2019_12_02_PanCortex_DiagnosisRegressed_Weights/ All_Data/ALL/ --recursive')
+#system('rm All_Data/ALL/*.hsq')
+system('synapse get -r syn21363795 --downloadLocation All_Data/ALL/ ')
+system('rm All_Data/ALL/*.hsq')
+
 #PullGenos
-system('synapse get syn20820120 --downloadLocation Binary_Cleaned/') system('synapse get syn20820121 --downloadLocation Binary_Cleaned/') system('synapse 
-get syn20820122 --downloadLocation Binary_Cleaned/')
+system('synapse get syn20820120 --downloadLocation Binary_Cleaned/')
+system('synapse get syn20820121 --downloadLocation Binary_Cleaned/')
+system('synapse get syn20820122 --downloadLocation Binary_Cleaned/')
+
 #GWAS
 system('synapse get syn18999109 --downloadLocation .')
+
 #Expression
-system('synapse get syn21011186 --downloadLocation .') Exp <- read.table('ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', header = T, sep='\t')
+system('synapse get syn21011186 --downloadLocation .')
+Exp <- read.table('ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', header = T, sep='\t')
+
 #LoadKunkle
 Kunk <- read.table('Kunkle_etal_2019_IGAP_Summary_statistics.with_allelefreqs.txt', header =T, sep="")
+
 #Try the MR for one gene
-load("All_Data/ALL/ENSG00000130208.wgt.RDat") PLINK <- read.plink(bed = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bed' ,
+load("All_Data/ALL/ENSG00000130208.wgt.RDat")
+PLINK <- read.plink(bed = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bed' ,
                     bim = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.bim',
-                    fam = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.fam' )
+                    fam = 'Binary_Cleaned/CEU_AncestryMatched_Genotypes.fam' 
+)
+
 #Filter Kunkle for relevant SNPS by their IDS
-K <- Kunk[ Kunk$MarkerName %in% PLINK$map$snp.name, ] row.names(K) <- K$MarkerName mygwas<-K[,c(3:5,9,6:8)] colnames(mygwas) <- c("SNP", "A1", 'A2', "freq", 
-"b", "se", "p" ) mygwas$n <- rep( 2003, dim(mygwas)[1] ) write.table(snps$V2, 'snp.list', row.names=F, col.names=F, quote=F, sep='\t') write.table(mygwas, 
-'mygwas.ma', row.names=F, col.names=T, quote=F, sep='\t') system( 'plink -bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --extract snp.list --make-bed 
---out Temp_plink') system( './smr_Linux --bfile Temp_plink --gwas-summary mygwas.ma --beqtl-summary myeqtl --out mymulti --smr-multi')
+K <- Kunk[ Kunk$MarkerName %in% PLINK$map$snp.name, ]
+row.names(K) <- K$MarkerName
+mygwas<-K[,c(3:5,9,6:8)]
+colnames(mygwas) <- c("SNP", "A1", 'A2', "freq", "b", "se", "p" )
+mygwas$n <- rep( 2003, dim(mygwas)[1] )
+
+write.table(snps$V2, 'snp.list', row.names=F, col.names=F, quote=F, sep='\t')
+write.table(mygwas, 'mygwas.ma', row.names=F, col.names=T, quote=F, sep='\t')
+
+if('plink' %in% list.files() ){}else{
+system('wget http://s3.amazonaws.com/plink1-assets/plink_linux_x86_64_20200107.zip')
+system('unzip plink_linux_x86_64_20200107.zip')
+}
+if('smr_Linux' %in% list.files() ){}else{
+system('wget https://cnsgenomics.com/software/smr/download/smr_Linux.zip')
+system('unzip smr_Linux.zip')
+}
+system( './plink -bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --extract snp.list --make-bed --out Temp_plink')
+system( './smr_Linux --bfile Temp_plink --gwas-summary mygwas.ma --beqtl-summary myeqtl --out mymulti --smr-multi')
+
 #make the eqtl data into BESD format
-EQTL <- read.csv( 'Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv', header = T ) EQTl <- EQTL[ as.character(EQTL$snpid ) %in% 
-as.character(PLINK$map$snp.name) , ] EQtl <- EQTl[ as.character(EQTl$gene ) %in% as.character(Exp$TargetID) , ] EQTL_sink <- EQTL EQTL <- EQtl
+EQTL <- read.csv( 'Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv', header = T )
+
+EQTl <- EQTL[ as.character(EQTL$snpid ) %in% as.character(PLINK$map$snp.name) , ]
+EQtl <- EQTl[ as.character(EQTl$gene ) %in% as.character(Exp$TargetID) , ]
+
+EQTL_sink <- EQTL
+EQTL <- EQtl
+
 #SNP gene beta t-stat p-value FDR
-EQTL$geneSymbol <- as.character(EQTL$geneSymbol) EQTL$gene <- as.character(EQTL$gene) EQTL[ as.character(EQTL$geneSymbol) =="",]$geneSymbol <- EQTL[ 
-as.character(EQTL$geneSymbol) =="",]$gene EQTL$snpid <- as.character(EQTL$snpid) EQTL$DUP <- paste0( as.character(EQTL$snpid), '_', as.character(EQTL$gene)) 
+EQTL$geneSymbol <- as.character(EQTL$geneSymbol)
+EQTL$gene <- as.character(EQTL$gene)
+EQTL[ as.character(EQTL$geneSymbol) =="",]$geneSymbol <- EQTL[ as.character(EQTL$geneSymbol) =="",]$gene
+
+EQTL$snpid <- as.character(EQTL$snpid)
+EQTL$DUP <- paste0( as.character(EQTL$snpid), '_', as.character(EQTL$gene))
 EQTL_deDup <- EQTL[ !duplicated(EQTL$DUP), ]
+
 ##LOAD EXPRESSION AND BIM
 ###FILTER FOR RELEVANT SNP-GENEs
-wExp <- read.table(file = 'WeightList/MaterWeight.lst', sep = "", header = T)
-#EQTL_deDup <- EQTL_deDup[ EQTL_deDup$snpid %in% as.character(PLINK$bim[,2]), ] EQTL_deDup <- EQTL_deDup[ EQTL_deDup$gene %in% as.character(Exp[,2]), ]
+##### wExp <- read.table(file = 'WeightList/MaterWeight.lst', sep = "", header = T)
+#EQTL_deDup <- EQTL_deDup[ EQTL_deDup$snpid %in% as.character(PLINK$bim[,2]), ]
+#EQTL_deDup <- EQTL_deDup[ EQTL_deDup$gene %in% as.character(Exp[,2]), ]
+
 Repo <- function( n ){
-  #'@Mat eg. EQTL_deDup '@n eg a number
+  #'@Mat eg. EQTL_deDup 
+  #'@n eg a number
   if( EQTL_deDup[n,]$geneSymbol == ""){
@@
 }
-REPS <- row.names( EQTL_deDup[ EQTL_deDup$geneSymbol == "", ] ) eqtl <- EQTL_deDup[ , c('snpid', 'geneSymbol', 'beta', 'statistic', 'pvalue', 'beta') ] 
-colnames(eqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 'p-value', 'FDR' ) write.table( eqtl, file = 'mateQTL_geneN.txt', col.names = T, row.names=F, quote=F, 
-sep='\t' ) Eeqtl <- EQTL_deDup[ , c('snpid', 'gene', 'beta', 'statistic', 'pvalue', 'beta') ] colnames(Eeqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 
-'p-value', 'FDR' ) write.table( Eeqtl, file = 'mateQTL_ensgN.txt', col.names = T, row.names=F, quote=F, sep='\t' ) system( './smr_Linux --eqtl-summary 
-mateQTL_ensgN.txt --matrix-eqtl-format --make-besd --out mybesd_ensgN' ) system( './smr_Linux --eqtl-summary mateQTL_geneN.txt --matrix-eqtl-format 
---make-besd --out mybesd_geneN' )
+
+REPS <- row.names( EQTL_deDup[ EQTL_deDup$geneSymbol == "", ] )
+
+eqtl <- EQTL_deDup[ , c('snpid', 'geneSymbol', 'beta', 'statistic', 'pvalue', 'beta') ]
+colnames(eqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 'p-value', 'FDR' )
+write.table( eqtl, file = 'mateQTL_geneN.txt', col.names = T, row.names=F, quote=F, sep='\t' )
+
+Eeqtl <- EQTL_deDup[ , c('snpid', 'gene', 'beta', 'statistic', 'pvalue', 'beta') ]
+colnames(Eeqtl) <- c( 'SNP', 'gene', 'beta', 't-stat', 'p-value', 'FDR' )
+write.table( Eeqtl, file = 'mateQTL_ensgN.txt', col.names = T, row.names=F, quote=F, sep='\t' )
+
+system( './smr_Linux --eqtl-summary mateQTL_ensgN.txt --matrix-eqtl-format --make-besd --out mybesd_ensgN' )
+system( './smr_Linux --eqtl-summary mateQTL_geneN.txt --matrix-eqtl-format --make-besd --out mybesd_geneN' )
+
 ##Fix the ,esi and .epi files
@@
 }
+
 ESiProcess <- function( Fil ){
   #'@Fil the loaded .esi file (ie File)
-  ESi_info <- EQTL_deDup[ !duplicated(EQTL_deDup$snpid), c("chromosome", "snpLocation", "snpid", "statistic", "beta", "A1", "A2", "A2freq", 
-"expressionIncreasingAllele")]
+  ESi_info <- EQTL_deDup[ !duplicated(EQTL_deDup$snpid), c("chromosome", "snpLocation", "snpid", "statistic", "beta", "A1", "A2", "A2freq", "expressionIncreasingAllele")]
   row.names(ESi_info) <- ESi_info$snpid
@@
 }
-File <- read.table(file='mybesd_ensgN.esi', header=F, sep='\t') File2 <- ESiProcess( File ) write.table(File2, file='mybesd_ensgN.esi', col.names=F, 
-row.names = F, quote=F, sep='\t') File <- read.table(file='mybesd_geneN.esi', header=F, sep='\t') File2 <- ESiProcess( File ) write.table(File2, 
-file='mybesd_geneN.esi', col.names=F, row.names = F, quote=F, sep='\t')
+
+File <- read.table(file='mybesd_ensgN.esi', header=F, sep='\t')
+File2 <- ESiProcess( File )
+write.table(File2, file='mybesd_ensgN.esi', col.names=F, row.names = F, quote=F, sep='\t')
+
+File <- read.table(file='mybesd_geneN.esi', header=F, sep='\t')
+File2 <- ESiProcess( File )
+write.table(File2, file='mybesd_geneN.esi', col.names=F, row.names = F, quote=F, sep='\t')
+
 #ESPI
-row.names(Exp) <- as.character(Exp$TargetID) Exp$TargetID <- as.character(Exp$TargetID) Exp$Gene_Symbol <- as.character(Exp$Gene_Symbol) EQTL_deDup$gene <- 
-as.character(EQTL_deDup$gene) EQTL_deDup$geneSymbol <- as.character(EQTL_deDup$geneSymbol) EQTL_deDup$chromosome <- as.character(EQTL_deDup$chromosome) 
+row.names(Exp) <- as.character(Exp$TargetID)
+Exp$TargetID <- as.character(Exp$TargetID)
+Exp$Gene_Symbol <- as.character(Exp$Gene_Symbol)
+
+EQTL_deDup$gene <- as.character(EQTL_deDup$gene)
+EQTL_deDup$geneSymbol <- as.character(EQTL_deDup$geneSymbol)
+EQTL_deDup$chromosome <- as.character(EQTL_deDup$chromosome)
 EQTL_deDup$strand <- as.character(EQTL_deDup$strand)
+
 #Split EQTL_deDup into special data frames to reference
-EQTL_deDup_GN <- EQTL_deDup[ !duplicated(EQTL_deDup$geneSymbol), ] EQTL_deDup_ENSG <- EQTL_deDup[ !duplicated(EQTL_deDup$gene), ]
+EQTL_deDup_GN <- EQTL_deDup[ !duplicated(EQTL_deDup$geneSymbol), ]
+EQTL_deDup_ENSG <- EQTL_deDup[ !duplicated(EQTL_deDup$gene), ]
 
@@
 }
-File <- read.table(file='mybesd_geneN.epi', header=F, sep='\t') File$V2 <- as.character(File$V2) foo <- t( apply(File, 1, ESpProcess ) ) write.table( foo, 
-file='mybesd_geneN.epi', row.names=F, col.names=F, quote = F, sep='\t' ) File <- read.table(file='mybesd_ensgN.epi', header=F, sep='\t') File$V2 <- 
-as.character(File$V2) foo <- t( apply(File, 1, ESpProcess ) ) write.table( foo, file='mybesd_ensgN.epi', row.names=F, col.names=F, quote = F, sep='\t' ) 
-Genes <- c("APOC1", "EED", "CD2AP", "CEACAM19", "CLPTM1", "MTCH2", "TREM2", "KNOP1", "POLR2E", "POLR2G", "ZNF660", "MADD", "PVRL2", "PVR", "TMEM223", 
-"NUP160", "PTPRJ", "C1QTNF4") ENSG <- c write.table(EQTL_deDup_GN[ EQTL_deDup_GN$geneSymbol %in% Genes, ]$gene, "myprobe.list", row.names=F, col.names=F, 
-quote=F, sep='\t') library(doParallel) library(foreach)
+
+File <- read.table(file='mybesd_geneN.epi', header=F, sep='\t')
+File$V2 <- as.character(File$V2)
+foo <- t( apply(File, 1, ESpProcess ) )
+write.table( foo, file='mybesd_geneN.epi', row.names=F, col.names=F, quote = F, sep='\t' )
+
+File <- read.table(file='mybesd_ensgN.epi', header=F, sep='\t')
+File$V2 <- as.character(File$V2)
+foo <- t( apply(File, 1, ESpProcess ) )
+write.table( foo, file='mybesd_ensgN.epi', row.names=F, col.names=F, quote = F, sep='\t' )
+
+Genes <- c("APOC1", "EED", "CD2AP", "CEACAM19", "CLPTM1", "MTCH2", "TREM2", "KNOP1", "POLR2E", "POLR2G", "ZNF660", "MADD", "PVRL2", "PVR", "TMEM223", "NUP160", "PTPRJ", "C1QTNF4")
+ENSG <- c
+
+write.table(EQTL_deDup_GN[ EQTL_deDup_GN$geneSymbol %in% Genes, ]$gene, "myprobe.list", row.names=F, col.names=F, quote=F, sep='\t')
+
+library(doParallel)
+library(foreach)
+
 #Start Master File
-system( 'echo "probeID ProbeChr Gene Probe_bp topSNP topSNP_chr topSNP_bp A1 A2 Freq b_GWAS se_GWAS tp_GWAS b_eQTL se_eQTL p_eQTL b_SMR se_SMR p_SMR 
-p_SMR_multi p_HEIDI nsnp_HEIDI" > Compiled_SMR.tsv') List <- read.table( 'WeightList/MaterWeight.lst', header = T, sep='')
+system( 'echo "probeID ProbeChr  Gene  Probe_bp  topSNP  topSNP_chr  topSNP_bp A1  A2  Freq  b_GWAS  se_GWAS tp_GWAS b_eQTL  se_eQTL p_eQTL  b_SMR se_SMR  p_SMR p_SMR_multi p_HEIDI nsnp_HEIDI" > Compiled_SMR.tsv')
+
+#List <- read.table( 'WeightList/MaterWeight.lst', header = T, sep='')
+List <- cbind(list.files('All_Data/ALL/'), paste0( 'All_Data/ALL/', list.files('All_Data/ALL/') ))
+List[,1] <- gsub('.wgt.RDat','',List[,1])
+List <- as.data.frame(List)
+colnames(List) <- c('ID','WGT')
 #i <- 1
+#List <- as.data.frame(List)
+#colnames(List) <- 'WGT'
 Runner <- function( i ){
@@
   #Run Model
-  system( paste0("./smr_Linux --bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --gwas-summary mygwas.ma --thread-num 1 --beqtl-summary mybesd_ensgN 
---ld-upper-limit 1 --out temp_Ensg_", Probe, " --extract-snp mysnp_", Probe, ".list --extract-probe myprobe_", Probe, ".list --peqtl-heidi 0 --ld-multi-snp 
-1 --smr-multi --peqtl-smr 1 --set-wind 2000 "))
+  system( paste0("./smr_Linux --bfile Binary_Cleaned/CEU_AncestryMatched_Genotypes --gwas-summary mygwas.ma --thread-num 1 --beqtl-summary mybesd_ensgN --ld-upper-limit 1 --out temp_Ensg_", Probe, " --extract-snp mysnp_", Probe, ".list --extract-probe myprobe_", Probe, ".list --peqtl-heidi 0 --ld-multi-snp 1 --smr-multi --peqtl-smr 1 --set-wind 2000 "))
   #Pull Info
@@
 }
-cl <- makeCluster( detectCores()-2 ) registerDoParallel(cl) foo <- Sys.time()
-  foreach(i=1:dim(List)[1]) %dopar% Runner( i ) Sys.time()-foo stopCluster(cl) Table<-read.table(file='Compiled_SMR.tsv', sep='\t', header=T) system( 'awk 
--F \',\' \'{ print $5"\t"$6 }\' Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv | sort | uniq | grep -v \'geneSymbol\' > Translate.txt') Trans 
-<- read.table( file='Translate.txt', sep ="\t", header=F) row.names(Trans) <- Trans$V1 Trans$V1 <- as.character(Trans$V1) Trans$V2 <- as.character(Trans$V2) 
-Trans[ is.na(Trans$V2), ]$V2 <- Trans[ is.na(Trans$V2), ]$V1 Trans[ Trans$V2 == "", ]$V2 <- Trans[ Trans$V2 == "", ]$V1 Table$Gene <- 
-as.character(Table$Gene) Table$probeID <- as.character(Table$probeID) Table$Gene <- Trans[Table$probeID,]$V2
-write.table(Table, file='Final_SMR_TWAS_Validation.tsv', row.names=F, col.names=T, quote=F, sep ='\t') ```
+
+cl <- makeCluster(  parallel::detectCores()-2 )
+registerDoParallel(cl)
+foo <- Sys.time()
+  foreach(i=1:length(List$ID)[1]) %dopar% Runner( i )
+Sys.time()-foo
+stopCluster(cl)
+
+Table<-read.table(file='Compiled_SMR.tsv', sep='\t', header=T)
+
+system( 'awk -F \',\' \'{ print $5"\t"$6 }\' Cortex_MetaAnalysis_ROSMAP_CMC_HBCC_Mayo_cis_eQTL_release.csv | sort | uniq | grep -v \'geneSymbol\' > Translate.txt')
+Trans <- read.table( file='Translate.txt', sep ="\t", header=F)
+row.names(Trans) <- Trans$V1
+Trans$V1 <- as.character(Trans$V1) 
+Trans$V2 <- as.character(Trans$V2)
+
+Trans[ is.na(Trans$V2), ]$V2 <- Trans[ is.na(Trans$V2), ]$V1
+Trans[ Trans$V2 == "", ]$V2 <- Trans[ Trans$V2 == "", ]$V1
+
+Table$Gene <- as.character(Table$Gene)
+Table$probeID <- as.character(Table$probeID)
+
+Table$Gene <- Trans[Table$probeID,]$V2
+write.table(Table, file='Final_SMR_TWAS_Validation.tsv', row.names=F, col.names=T, quote=F, sep ='\t')
+```
 
 ```{r synapse.parameters, include=FALSE, cache=TRUE}
-parentId = 'syn18936948'; activityName = 'Mendelian Randomization'; activityDescription = 'Validation of TWAS 
-associations via SMR analysis'; thisFileName <- ''
+parentId = 'syn18936948';
+activityName = 'Mendelian Randomization';
+activityDescription = 'Validation of TWAS associations via SMR analysis';
+thisFileName <- 'SMR.Rmd'
 # Github link
-thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master') thisFile <- githubr::getPermlink(repository = thisRepo, 
-repositoryPath=paste0('code/',thisFileName)) ```
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
+```
+
 ### Store files in synapse
-```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE} activityName = 'Mendelian Randomization'; activityDescription = 'Validation of TWAS associations 
-via SMR analysis'; CODE <- syn_temp$store(synapseclient$Folder(name = "Summary-data-based Mendelian Randomization", parentId = parentId))
+```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
+activityName = 'Mendelian Randomization';
+activityDescription = 'Validation of TWAS associations via SMR analysis';
+CODE <- syn_temp$store(synapseclient$Folder(name = "Summary-data-based Mendelian Randomization", parentId = parentId))
+
 # Set annotations
@@
   tissueTypeAbrv	= c('NA'), 
-  study = c('ROSMAP','MSBB', 'Mayo')
+  study = c('ROSMAP','MSBB', 'Mayo'),
   organism = 'HomoSapiens',
@@
   rnaquantification = 'NA',
-  genomeAssemblyID = 'hg19' )
+  genomeAssemblyID = 'hg19'
+)
+
 # Store SMR
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='Final_SMR_TWAS_Validation.tsv', name = 'SMR Values', parentId=CODE$properties$id ), activityName = 
-activityName, executed = thisFile, activityDescription = activityDescription) all.annotations$dataSubType = 'Summary Stats' 
-syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations) ```
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='Final_SMR_TWAS_Validation.tsv', name = 'SMR Values', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+all.annotations$dataSubType = 'Summary Stats'
+syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+```
+
 ### R Source Code
-[Github](`r thisFile`) ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE} reticulate::use_python("/usr/bin/python", required = TRUE) synapseclient <- 
-reticulate::import("synapseclient") syn_temp <- synapseclient$Synapse() syn_temp$login() setwd("~/TWAS/code/") 
-source("~/TWAS/utilityFunctions/knitfile2synapseClient.R") source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R") 
+[Github](`r thisFile`)
+
+```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
+reticulate::use_python("/usr/bin/python", required = TRUE)
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
 createAndKnitToFolderEntityClient(file = "SMR.Rmd",

### 2023-10-10 code/Funct.R

@@ -1,0 +1,456 @@
+# Load Libraries and se working directory 
+##  devtools::install_github('blogsdon/spike/spike/')
+library(spike)
+library(pheatmap)
+library(parallel)
+library(doParallel)
+library(spike)
+library(bcv)
+library(reshape2)
+library(biomaRt)
+library(UpSetR)
+library(ComplexHeatmap)
+#install.packages("enrichR")
+library(enrichR)
+setwd( config$filedir )
+
+
+reticulate::use_python("/usr/bin/python", required = TRUE)
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+#createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing_V2.Rmd",
+#                                  parentId ="syn21478397",
+#                                  folderName = 'ACC')
+
+Genes <- c( "APOC1", "CD2AP", "EED", "CEACAM19", "MTCH2", "TREM2", "CLPTM1", "KNOP1" )
+ENSGS <- c( "ENSG00000130208", "ENSG00000198087", "ENSG00000074266", "ENSG00000186567", "ENSG00000109919", "ENSG00000095970", "ENSG00000104853", "ENSG00000103550" )
+names(ENSGS) <- Genes
+# Set Github Provenance links
+thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
+
+CODE <- syn_temp$store(synapseclient$Folder(name = 'Partial Correlations', parentId = 'syn18936948'))
+
+#SynIDs of expression data to pull from
+ExpressionDS <- c('syn21291908','syn21292041','syn21285564','syn21285564','syn21285564','syn21285564','syn21291908')
+names( ExpressionDS ) <- c('CBE', 'DLPFC', 'FP', 'IFG', 'PHG', 'STG', 'TCX')
+
+#Study ID Translator
[…]

### 2023-10-10 code/GeneLengthQuant.R

@@ -1,0 +1,93 @@
+library(readr)
+library(BioMart)
+
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+#countz <- readr::read_tsv(syn_temp$get(foo, version = 1))
+COUNT_OBJ <- syn_temp$get("syn21075911", version = 1)
+countz <- read.table(COUNT_OBJ$path, header=T, sep='\t', check.names = F)
+
+myGetGeneLengthAndGCContent <- function(id, ver){
+  
+  org = 'hsa'
+  id.type = 'ensembl_gene_id'
+  host = ver
+  
+  message("Connecting to BioMart ...")
+  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
+  ds <- listDatasets(ensembl)[, "dataset"]
+  ds <- grep(paste0("^", org), ds, value = TRUE)
+  
+  if (length(ds) == 0){
+    stop(paste("Mart not found for:", org))
+  } else if (length(ds) > 1) {
+    message("Found several marts")
+    sapply(ds, function(d) message(paste(which(ds == d), d, sep = ": ")))
+    n <- readline(paste0("Choose mart (1-", length(ds), ") : "))
+    ds <- ds[as.integer(n)]
+  }
+  
+  ensembl <- useDataset(ds, mart = ensembl)
+  message(paste0("Downloading sequence", ifelse(length(id) > 1, "s", ""), " ..."))
+  if (length(id) > 100)
+    message("This may take a few minutes ...")
+  attrs <- c(id.type, "ensembl_exon_id", "chromosome_name", "exon_chrom_start", "exon_chrom_end")
+  coords <- getBM(filters = id.type, attributes = attrs, values = id, mart = ensembl)
+  id <- unique(coords[, id.type])
+  coords <- sapply(id, function(i) {
+    i.coords <- coords[coords[, 1] == i, 3:5]
+    g <- GRanges(i.coords[, 1], IRanges(i.coords[, 2], i.coords[, 3]))
+    return(g)
+  })
+  coords <- lapply(coords[id], reduce)
+  len <- plyr::ldply(coords, function(x) sum(IRanges::width(x)), .id = 'ensembl_gene_id') %>%
+    dplyr::rename(gne.length = V1)
+  
[…]

### 2023-10-10 code/utilityFunctions/Parallel_vbsrBootstrap.R

@@ -1,0 +1,40 @@
+pvbsrBootstrap = function(y,x,nsamp=100,cores=8){
+  library(dplyr)
+  n <- length(y)
+  replicateMatrix = sample(1:(n*nsamp),replace=TRUE) %>%
+    matrix(n,nsamp)
+  replicateMatrix = replicateMatrix%%n +1
+  #print(replicateMatrix[1:5,])
+  fxn1 <- function(shuf,y,x){
+    #library(utilityFunctions) return(utilityFunctions::fastlmbeta(y[shuf],x[shuf,])) library(vbsr) y=y[shuf] 
+    #x=x[shuf,]
+    res <- vbsr::vbsr(y[shuf],x[shuf,])
+    
+    ###identify significant features return unpenalized betas
+    baz = rep(0,ncol(x)+1)
+    names(baz) = c('intercept',colnames(x))
+    whichSig = which(res$pval < 0.05/ncol(x))
+    if(length(whichSig)>0){
+      #write a fastlmbeta function that also returns correlation
+      baz2 = c()
+      try(baz2 <- spike::fastlmbeta2(y[shuf],x[shuf,whichSig],colnames(x)[whichSig]),silent=T)
+      if(length(baz2)>0){
+        baz[names(baz2)] <- baz2
+      }
+    }
+    
+    #return(c(res$alpha,res$beta))
+    return(baz)
+  }
+  
+  cl <- parallel::makeCluster(cores)
+  registerDoParallel(cl)
+  #betaMatrix <- foreach(i=1:nsamp,.combine='rbind') %dopar% fxn1(replicateMatrix[,i],y,data.matrix(x))
+  betaMatrix <- t(parallel::parApply(cl,replicateMatrix,2,fxn1,y,data.matrix(x)))
+  #betaMatrix <- t(apply(replicateMatrix,2,fxn1,y,data.matrix(x)))
+  parallel::stopCluster(cl)
+  #colnames(betaMatrix) <- c(colnames(x))
+  return(apply(betaMatrix!=0,2,mean))
+  #return(betaMatrix)
+  
+}

### 2023-10-10 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd

@@
 #Filter for Rin Here#
-
+Meta[ Meta$RIN >= 5 | Meta$sampleid %in% c('380_120503','500_120515'), ]
 #Filter Out Sample Swaps
@@
                                           parentId ="syn23640229",
-                                          folderName = 'Full_RosMap_OldCode')
-
-```
+                                          folderName = 'RinOver5_RosMap_OldCode')
+
+```

### 2023-10-10 code/CMC_DataProcessing.Rmd

@@
 activityDescription = 'Proccessed and Filtered CMC Genotype Data';
-thisFileName <- 'CMC_DataCProcessing.Rmd'
+thisFileName <- 'CMC_DataProcessing.Rmd'
 # Github link
@@
   assay  = 'RNAseq',
-  tissueTypeAbrv  = c(gsub( 'Brain - ', "", names(table(bMeta$SMTSD)))), 
+  tissueTypeAbrv  = c('Multiple Brain'), 
   study = 'CMC', 
@@
 
-```{bash Pull_WGS, results='hide', echo=TRUE, cache=TRUE}
+```{bash cleanup, results='hide', echo=TRUE, cache=TRUE}
 rm *.fam

### 2023-10-10 code/CMC_ExpVal_DataProcessing.Rmd

@@
 #  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
-
 ```

### 2023-10-10 code/Mayo_RegressDiagnosis_4_TWAS.Rmd

@@
 ALL_USED_IDs <- COUNT_TC_ID
-COUNT_TC <- synGet(COUNT_TC_ID, version = 1)$path %>%
+COUNT_TC <- syn_temp$get(COUNT_TC_ID, version = 1)$path %>%
   read.table(header=T, sep='\t', check.names = F, row.names = 1)
@@
 ALL_USED_IDs[length(ALL_USED_IDs)+1] <- COUNT_CE_ID
-COUNT_CE <- synGet(COUNT_CE_ID, version = 1)$path %>%
+COUNT_CE <- syn_temp$get(COUNT_CE_ID, version = 1)$path %>%
   read.table(header=T, sep='\t', check.names = F, row.names = 1)
@@
 
-# Code WTF is this??
-CODE <- Folder(name = "Mayo", parentId = parentId)
-CODE <- synStore(CODE)
+CODE <- syn_temp$store(synapseclient$Folder(name = "Mayo", parentId = parentId))
 
@@
 ```{r knitmd, eval=FALSE, cache=FALSE, include=FALSE}
-library(synapser)
-library(knit2synapse) # get the package from devtools::install_github('Sage-Bionetworks/knit2synapse')
-synLogin()
-knit2synapse::createAndKnitToFolderEntity(file = "/home/jgockley/TWAS/code/Mayo_RegressDiagnosis_4_TWAS.Rmd",
+synapseclient <- reticulate::import("synapseclient")
+syn_temp <- synapseclient$Synapse()
+syn_temp$login()
+
+setwd("~/TWAS/code/")
+source("~/TWAS/utilityFunctions/knitfile2synapseClient.R")
+source("~/TWAS/utilityFunctions/hook_synapseMdSyntax_plot.R")
+
+createAndKnitToFolderEntityClient(file = "Mayo_RegressDiagnosis_4_TWAS.Rmd",
                                           parentId ="syn20798011",
                                           folderName = 'Mayo')
+
 ```

### 2023-10-10 code/ProcessData.Rmd

--- 2019-10-16 code/ProcessData.Rmd
@@
 unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink_linux_x86_64_20190617.zip
-wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191012.zip
-unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191012.zip
+wget -q -P ~/TWAS/bin http://s3.amazonaws.com/plink2-assets/plink2_linux_x86_64_20191015.zip
+unzip -d ~/TWAS/bin/ ~/TWAS/bin/plink2_linux_x86_64_20191015.zip
 
@@
   INDVs$GenoID <- DNA[ INDVs$individualIdentifier, ]$sampleIdentifier
-  INDVs$NewID <- paste0(INDVs$GenoID, '_', INDVs$BrodmannArea )
+  INDVs$NewID <- paste0( INDVs$BrodmannArea, '_' , INDVs$GenoID )
   row.names(INDVs) <- INDVs$sampleIdentifier
@@
 #Filter for CEU Ancestry Matched Training Cohort
-Tot_Samps <- do.call( rbind, strsplit( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))],  "_" ))
+Tot_Samps <- cbind( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))], 
+                    do.call( rbind, strsplit( colnames(Norm_Resid)[5:length(colnames(Norm_Resid))],  "_" ))[,2]
+                  )
 write.table(Tot_Samps, file="ALL_RNASamplesComb.tsv", col.names =F, row.names=F, sep=" ", quote=F)
@@
 
-ROS_Samps <- do.call( rbind, strsplit( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],  "_" ))
+ROS_Samps <- cbind( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],
+                    do.call( rbind, strsplit( colnames(ROS_Norm_Resid)[5:length(colnames(ROS_Norm_Resid))],  "_" ))[,2]
+                  )
 write.table(ROS_Samps, file="ROS_RNASamples.tsv", col.names =F, row.names=F, sep=" ", quote=F)
@@
 row.names(FAM)<-FAM$V2
+
 FAM[ row.names(MSBB), ]$V5 <- MSBB$SEX.inferred
@@
 
+FAM$V1 <- paste0( FAM$V1, "_", FAM$V2 )
 #Write New FAM to file
@@
 
-tail(FAM[ FAM$V1[ grepl('ROS', FAM$V1) == F ] $ FAM$V1[ grepl('MAP', FAM$V1) == F ] ,])
+#tail(FAM[ FAM$V1[ grepl('ROS', FAM$V1) == F ] $ FAM$V1[ grepl('MAP', FAM$V1) == F ] ,])
 # & FAM$V1[ grepl('ROS', FAM$V1) == F ]
-MSBB_List <- FAM[ FAM$V1 != '0', ] 
-MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('MAP', MSBB_List$V1) == F ] ,]
-MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('ROS', MSBB_List$V1) == F ] ,]
+MSBB_List <- FAM[ (dim(NewMayo)[1]+1):dim(FAM)[1], ] 
+MSBB_List <- MSBB_List[1:dim(MSBB)[1],]
+#MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('MAP', MSBB_List$V1) == F ] ,]
+#MSBB_List <- MSBB_List[ MSBB_List$V1[ grepl('ROS', MSBB_List$V1) == F ] ,]
+
 write.table( MSBB_List[,1:2], file="MSBB_SamplesToExpand.txt", quote = F, row.names = F, col.names = F, sep = "\t" )
@@
 #Copy over FAM File with Sex Info:
-mv New_Fam.fam CEU_AncestryMatched_Genotypes.fam
+cp New_Fam.fam CEU_AncestryMatched_Genotypes.fam
 
-#Extract the MSBB Samples to duplicate and rename to match tissues
-plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep MSBB_SamplesToExpand.txt --recode --out MSBB_Intermediate
+#Extract the MSBB Samples to duplicate and rename to match tissues --silent
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep MSBB_SamplesToExpand.txt --silent --recode --out MSBB_Intermediate
 
-#Repeat the rows in the ped file 4 times
+#ReName MSBB to get FID and IIDs
 awk '{for(i=0;i<4;i++)print}' MSBB_Intermediate.ped > temp
 
-gawk -v m=1 -v n=2 -v el='BM10' 'NR % m == 0 { $n = el } 1' temp > foo
-gawk -v m=2 -v n=2 -v el='BM22' 'NR % m == 0 { $n = el } 1' foo > temp
-gawk -v m=3 -v n=2 -v el='BM36' 'NR % m == 0 { $n = el } 1' temp > foo
-gawk -v m=4 -v n=2 -v el='BM44' 'NR % m == 0 { $n = el } 1' foo > temp
+gawk -v m=1 -v n=1 -v el='BM10' 'NR % m == 0 { $n = el"_"$2 } 1' temp > foo
+gawk -v m=2 -v n=1 -v el='BM22' 'NR % m == 0 { $n = el"_"$2 } 1' foo > temp
+gawk -v m=3 -v n=1 -v el='BM36' 'NR % m == 0 { $n = el"_"$2 } 1' temp > foo
+gawk -v m=4 -v n=1 -v el='BM44' 'NR % m == 0 { $n = el"_"$2 } 1' foo > temp
 mv temp MSBB_Intermediate.ped
 rm foo
+plink --threads $CORES --file MSBB_Intermediate --silent --make-bed --out MSBB_Expanded
 
-plink --threads $CORES --file MSBB_Intermediate --make-bed --out MSBB_Expanded
-plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --bmerge MSBB_Expanded --make-bed --out Rebuilt
-plink --threads $CORES --bfile Rebuilt --make-bed --out CEU_AncestryMatched_Genotypes
+#ReName ALL to get FID and IIDs
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --silent --recode --out temp
+gawk -v m=1 -v n=1 'NR % m == 0 { if( $2 ~ /MAP/ || $2 ~ /ROS/ ) { $n = $2"_"$2 }else{ $n = $1 } } 1' temp.ped > foo
+#gawk -v m=1 -v n=1 'NR % m == 0 { $n = $1"_"$2 } 1' temp.ped > foo2
 
-rm Rebuilt.*
-rm MSBB_Expanded.*
+mv foo temp.ped
+plink --threads $CORES --file temp --silent --make-bed --out CEU_AncestryMatched_Genotypes
+
+#Merge
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --bmerge MSBB_Expanded --silent --make-bed --out Rebuilt
+plink --threads $CORES --bfile Rebuilt --silent --make-bed --out CEU_AncestryMatched_Genotypes
+
+#rm Rebuilt.*
+#rm MSBB_Expanded.*
+#rm temp.*
 
@@
 #Extract ROS_Only:
-plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROS_RNASamples.tsv --make-bed --out ROSMAPonly_CEU_ToTrainForTWAS
+plink --threads $CORES --bfile CEU_AncestryMatched_Genotypes --keep ROS_RNASamples.tsv --silent --make-bed --out ROSMAPonly_CEU_ToTrainForTWAS
 ```
@@
 FAM <- as.data.frame(fread('All_CEU_ToTrainForTWAS.fam'))
-row.names(FAM) <- paste0( FAM[,1], '_', FAM[,2] )
+row.names(FAM) <- FAM[,1]
 table(row.names(FAM) %in% colnames(Diag_Resid))
@@
 FAM <- as.data.frame(fread('ROSMAPonly_CEU_ToTrainForTWAS.fam'))
-row.names(FAM) <- paste0( FAM[,1], '_', FAM[,2] )
+row.names(FAM) <- FAM[,1]
 table(row.names(FAM) %in% colnames(ROS_Diag_Resid))
@@
 ROS_Norm_Resid_train <- ROS_Norm_Resid_train[ (ROS_Norm_Resid_train$Chr %in% c(1:22)) == T, ]
-
-colnames(Diag_Resid_train) <- c( colnames(Diag_Resid_train[1:4]), do.call( rbind, strsplit( colnames(Diag_Resid_train[ 5:length(colnames(Diag_Resid_train)) ]), "_") )[,2] )
-
-colnames(Norm_Resid_train) <- c( colnames(Norm_Resid_train[1:4]), do.call( rbind, strsplit( colnames(Norm_Resid_train[ 5:length(colnames(Norm_Resid_train)) ]), "_") )[,2] )
-
-colnames(ROS_Diag_Resid_train) <- c( colnames(ROS_Diag_Resid_train[1:4]), do.call( rbind, strsplit( colnames(ROS_Diag_Resid_train[ 5:length(colnames(ROS_Diag_Resid_train)) ]), "_") )[,2] )
-
-colnames(ROS_Norm_Resid_train) <- c( colnames(ROS_Norm_Resid_train[1:4]), do.call( rbind, strsplit( colnames(ROS_Norm_Resid_train[ 5:length(colnames(ROS_Norm_Resid_train)) ]), "_") )[,2] )
-
 ```
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted.tsv', name = 'Total Merged and region Averaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted.tsv', name = 'Total RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
 EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'Total Merged and region Averaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'Total RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
     EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU Merged and region Averaged RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted.tsv', name = 'CEU RNA-Seq with Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_SVA_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   EXP.all.annotations$dataSubType = 'residualGeneExpForeQTL'
@@
 
-ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU Merged and region Averaged RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+ENRICH_OBJ <- syn_temp$store( synapseclient$File( path='ALL_CEU_RNA_Seq_SVAadusted_DiagnosisRegressed.tsv', name = 'CEU RNA-Seq with Diagnosis Regressed Normalised, covariates, surrogate variable adjusted residual expression (for eQTL)', parentId=CODE$properties$id ), used = Syns_Used_Diagnosis_EXP, activityName = activityName, executed = thisFile, activityDescription = activityDescription)
   EXP.all.annotations$dataSubType = 'residualGeneExpForDiagnosisRegressedeQTL'
@@
 ```{bash Clean, echo=T, results='hide'}
-rm -r ~/TWAS/bin/
+#rm -r ~/TWAS/bin/
 rm *.bed

### 2023-10-10 code/ResultsPlots.Rmd

@@
 
+p <- ggplot(don, aes(x=BPcum, y=-log10(TWAS.P))) +
+
+    #AddSigLine
+    geom_hline(yintercept = -log10( max(Assoc[Assoc$FDR_TWAS.P < 0.05,]$TWAS.P) )) +
+    #p.adjust(7.467145e-06, method='fdr', dim(Assoc)[1] )
+
+    # Show all points
+    geom_point( aes(color=as.factor(CHR)), alpha=0.8, size=1.3) +
+    scale_color_manual(values = rep(c("grey", "black"), 22 )) +
+
+    # custom X axis:
+    scale_x_continuous( name="Chromosome", label = axisdf$CHR, breaks= axisdf$center ) +
+    scale_y_continuous(name="-Log10( TWAS Association P-Value )", expand = c(0, 0), limits=c(0,38) ) +     # remove space between plot area and x axis
+
+    # Add highlighted points
+    geom_point(data = subset(don, is_highlight=="yes"), color="orange", size=2) +
+    geom_point(data = subset(don, is_highlight=="drop"), color="lightslateblue", size=2) +
+    geom_point(data = subset(don, is_highlight=="NS"), color="mediumturquoise", size=2) +
+
+    # Add label using ggrepel to avoid overlapping
+    geom_label_repel( data=subset(don, is_annotate=="yes"), aes(label=Gene), size=2) +
+
+    # Custom the theme:
+    theme_bw() +
+    theme( 
+      legend.position="none",
+      panel.border = element_blank(),
+      panel.grid.major.x = element_blank(),
+      panel.grid.minor.x = element_blank()
+    )
+ggsave("TWAS_Manhattan.eps",p)
+
 pdf(file = "TWAS_qq.pdf")
@@
 dev.off()
+
+setEPS()
+postscript("TWAS_qq.eps", onefile = TRUE)
+qq(Assoc$TWAS.P, bty='n', las=1)
+dev.off()
+
 ```
@@
 
-# Store SVA results
+# PDFs
 ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.pdf', name = 'Twas Gene Association Manhattan Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
@@
 ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_qq.pdf', name = 'Twas Gene Association QQ-Plot', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataSubType = 'QQ-Plot'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+# PDFs
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_Manhattan.eps', name = 'Twas Gene Association Manhattan Plot EPS', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataType = "eps"
+  all.annotations$dataSubType = 'Manhattan Plot'
+  syn_temp$setAnnotations(ENRICH_OBJ, annotations = all.annotations)
+
+ENRICH_OBJ <-  syn_temp$store( synapseclient$File( path='TWAS_qq.eps', name = 'Twas Gene Association QQ-Plot EPS', parentId=CODE$properties$id ), activityName = activityName, executed = thisFile, activityDescription = activityDescription)
+  all.annotations$dataType = "eps"
   all.annotations$dataSubType = 'QQ-Plot'
